### 2023-08-13 code/230510_Competition.Rmd
first thing

---
title: "220410_Competition"
author: "Justin"
date: "4/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Library 
```{r}
library(tidygeocoder)
library(tidyverse)
library(did)
library(tidycensus)
library(gtsummary)
library(readxl)
library(sandwich)
library(lmtest)
library(ggpubr)
library(kableExtra)
library(tigris)

library(gridExtra)
library(cowplot)
library(Matching)
library(fixest)
library(directlabels)

`%notin%` <- Negate(`%in%`)

select <- dplyr::select

#Sys.setenv('R_MAX_VSIZE'=32000000000)

```

## Define new Tufte data theme
```{r, echo = FALSE, results = "asis", message=FALSE, warning = FALSE, fig.align="center"}

is.extrafont.installed <- function(){
  if(is.element("extrafont", installed.packages()[,1])){
    library(extrafont)
    # probably need something here to run font_import()
    return(T)
  }else{
    warning("Library extrafont installed; using system sans/serif libraries as fallback fonts. 
    To enable full font support, run: 
      install.packages('extrafont') 
      font_import()")
    return(F)
  }
}

# set font
base_font_family_tufte <- function(){
  if(is.extrafont.installed()){
    library(extrafont)
    tuftefont <- choose_font(c("Gill Sans MT", "Gill Sans", "GillSans", "Verdana", "serif"), quiet = FALSE)  
  }else{
    tuftefont <- "serif"
  }
  return(tuftefont)
}

theme_tufte_revised <- function(base_size = 11, base_family = base_font_family_tufte(), ticks = TRUE) {

  ret <- theme_bw(base_family = base_family, base_size = base_size) + 
    theme(
      axis.line = element_line(color = 'black'),
      axis.title.x = element_text(vjust = -0.3), 
      axis.title.y = element_text(vjust = 0.8),
      legend.background = element_blank(), 
      legend.key = element_blank(), 
      legend.title = element_text(face="plain"),
      panel.background = element_blank(), 
      panel.border = element_blank(),
      panel.grid = element_blank(),
      plot.background = element_blank(),
      strip.background = element_blank()
    )

  if (!ticks) {
    ret <- ret + theme(axis.ticks = element_blank())
  }

  ret
}

```

# Data

## Read in UDS

```{r}

## Zips
locs <- paste("UDS/UDS-", c(2014:2021), "-Full-Dataset.xlsx", sep = "")
uds.zip <- read_excel(locs[1], sheet = "HealthCenterZipCodes")

new.zip.names <- c("BHCMIS ID", "Grant Number", "Reporting Year" , "Zip Code", "Zip Code Type",  "None_Uninsured Patients" ,  "Medicaid_CHIP_Other Public Patients", "Medicare Patients", "Private Patients", "Total Number of Patients" ) 
colnames(uds.zip) <-    new.zip.names

for(i in 2:length(locs)){
  temp.zip <- read_excel(locs[i], sheet = "HealthCenterZipCodes")
  colnames(temp.zip) <- new.zip.names
  uds.zip <- rbind(uds.zip, temp.zip %>% mutate(`Zip Code` = str_pad(`Zip Code`, 5, pad = "0")))
}

## Rename
new.zip.names <- c("BHCMIS ID", "Grant Number", "Reporting Year" , "Zip Code", "Zip Code Type",  "None_Uninsured Patients" ,  "Medicaid_CHIP_Other Public Patients", "Medicare Patients", "Private Patients", "Total Number of Patients" )
colnames(uds.zip) <-    new.zip.names

## Clean

uds.zip[uds.zip$`Total Number of Patients`== '-' | uds.zip$`Total Number of Patients`== '--',]$`Total Number of Patients` <- NA
uds.zip$`Total Number of Patients` <- as.numeric(uds.zip$`Total Number of Patients`)
uds.zip <- uds.zip[!is.na(uds.zip$`Total Number of Patients`),] %>%
    mutate(`Reporting Year` = as.numeric(`Reporting Year`))

uds.zip$`None_Uninsured Patients` <- as.numeric(uds.zip$`None_Uninsured Patients`)
uds.zip$`Medicaid_CHIP_Other Public Patients` <- as.numeric(uds.zip$`Medicaid_CHIP_Other Public Patients`)
uds.zip$`Medicare Patients` <- as.numeric(uds.zip$`Medicare Patients`)
uds.zip$`Private Patients` <- as.numeric(uds.zip$`Private Patients`)

uds.zip <- cbind(uds.zip, broken.total = rowSums(uds.zip[,c(6:9)], na.rm = TRUE), missings = rowSums(is.na(uds.zip[,c(6:9)]))) %>%
  mutate(`Total Number of Patients` = as.numeric(`Total Number of Patients`)) %>%
  mutate(`Total Number of Patients` = ifelse(is.na(`Total Number of Patients`), round(missings*16/4), `Total Number of Patients`)) %>%
  mutate(`None_Uninsured Patients` = ifelse(is.na(`None_Uninsured Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `None_Uninsured Patients`),
         `Medicaid_CHIP_Other Public Patients` = ifelse(is.na(`Medicaid_CHIP_Other Public Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Medicaid_CHIP_Other Public Patients`),
         `Medicare Patients` = ifelse(is.na(`Medicare Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Medicare Patients`),
         `Private Patients` = ifelse(is.na(`Private Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Private Patients`))

# ## Old version with missingness still in there  
# uds.zip$`Reporting Year` <- as.numeric(uds.zip$`Reporting Year`)
# uds.zip$`Total Number of Patients` <- as.numeric(uds.zip$`Total Number of Patients`)
# uds.zip$`None_Uninsured Patients` <- as.numeric(uds.zip$`None_Uninsured Patients`)
# uds.zip$`Medicaid_CHIP_Other Public Patients` <- as.numeric(uds.zip$`Medicaid_CHIP_Other Public Patients`)
# uds.zip$`Medicare Patients` <- as.numeric(uds.zip$`Medicare Patients`)
# uds.zip$`Private Patients` <- as.numeric(uds.zip$`Private Patients`)
# 
# 
# uds.zip[is.na(uds.zip$`Total Number of Patients`),]$`Total Number of Patients` <- 0
# uds.zip[grep("-", uds.zip$`None_Uninsured Patients`),]$`None_Uninsured Patients` <- 0
# uds.zip[grep("-", uds.zip$`Medicaid_CHIP_Other Public Patients`),]$`Medicaid_CHIP_Other Public Patients` <- 0
# uds.zip[grep("-", uds.zip$`Medicare Patients`),]$`Medicare Patients` <- 0
# uds.zip[grep("-", uds.zip$`Private Patients`),]$`Private Patients` <- 0
# 
uds.zip.totals <- uds.zip %>%
  select(`Grant Number`, `Reporting Year`, `None_Uninsured Patients`:`Total Number of Patients`) %>%
  group_by(`Grant Number`, `Reporting Year`) %>% summarise(None = sum(`None_Uninsured Patients`, na.rm = T),
                                                           MCR = sum(`Medicare Patients`, na.rm = T),
                                                           COM = sum(`Private Patients`, na.rm = T),
                                                           MCD = sum(`Medicaid_CHIP_Other Public Patients`, na.rm = T),
                                                           Total = sum(`Total Number of Patients`, na.rm = T))

uds.zip <- uds.zip[uds.zip$`Zip Code Type` == "ZipCode",]

## Sites
locs <- paste("UDS/UDS-", c(2014:2021), "-Full-Dataset.xlsx", sep = "")

uds.sites <- read_excel(locs[1], sheet = "HealthCenterSiteInfo") %>% 
  select(GrantNumber, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>% 
  mutate(Year = 2014)

colnames(uds.sites) <- c("Grant Number", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")

for(i in 2:(length(locs)-1)){
  uds.sites <- rbind(uds.sites, read_excel(locs[i], sheet = "HealthCenterSiteInfo") %>% 
                       select("Grant Number", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code") %>% 
  mutate(Year = 2013 + i))
}

temp.sites <- read_excel(locs[i+1], sheet = "HealthCenterSiteInfo" )%>% 
  select(GrantNumber, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>% 
  mutate(Year = 2021)
colnames(temp.sites) <- c("Grant Number", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")

uds.sites <- rbind(uds.sites, temp.sites)

uds.sites$Zip <- substr(uds.sites$`Site ZIP Code`, 1, 5)

uds.sites <- uds.sites %>% 
  filter(`Site State` %notin% c('AK','HI','GU','VI','PW','MH','AS','FM','PR','MP'))

uds.sites[grep(pattern = "-", uds.sites$Zip),]$Zip <- NA

```

## Clean up some of the missing zip codes

```{r}

tbcoded <- uds.sites[is.na(uds.sites$Zip),]
coded <- geo(street = tbcoded[c(1:1000),]$`Site Street Address`, 
             city = tbcoded[c(1:1000),]$`Site City`, 
             state = tbcoded[c(1:1000),]$`Site State`, 
             method = "census", 
             full_results = TRUE)

for (g in 1:9){
  g
coded <- rbind(coded, 
               geo(street = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site Street Address`, 
             city = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site City`, 
             state = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site State`, 
             method = "census", 
             full_results = TRUE) )
}

coded <- rbind(coded, 
               geo(street = tbcoded[c(10001:10975),]$`Site Street Address`, 
             city = tbcoded[c(10001:10975),]$`Site City`, 
             state = tbcoded[c(10001:10975),]$`Site State`, 
             method = "census", 
             full_results = TRUE) )

coded[grep(pattern = "[[:digit:]]{5}$", coded$matched_address),]

uds.sites[is.na(uds.sites$Zip),]$Zip <- str_extract(coded$matched_address, pattern = "[[:digit:]]{5}$")
uds.sites[is.na(uds.sites$Zip),]

uds.sites.temp <- uds.sites

```

```{r}

uds.sites <- uds.sites.temp

uds.sites.temp %>% filter(`Grant Number` %in% c("H80CS00881") & Year == 2016)

chc <- read.csv("chc.csv")

chc %>% filter(Health.Center.Number %in% c("H80CS00881"))

uds.sites[is.na(uds.sites$Zip),] <- uds.sites[is.na(uds.sites$Zip),] %>%
  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Street Address" = "Site.Address")) %>%
  mutate(Zip = ifelse(is.na(Zip), substr(Health.Center.Organization.ZIP.Code, 1, 5), Zip)) %>%
  select(`Grant Number`:Zip) %>%
  unique()

uds.sites[is.na(uds.sites$Zip),] <- uds.sites[is.na(uds.sites$Zip),] %>%
  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Name" = "Site.Name")) %>%
  mutate(Zip = ifelse(is.na(Zip), substr(Health.Center.Organization.ZIP.Code, 1, 5), Zip)) %>%
  select(`Grant Number`:Zip) %>%
  unique()

uds.sites[is.na(uds.sites$Zip),] 
```

```{r}

table(uds.sites.temp$`Location Setting`)

uds.sites <- uds.sites %>% #filter(`Location Type` == "Permanent" & `Location Setting` %in% c("All Other Clinic Types")) %>% 
  mutate(Access = as.numeric(ifelse(`Total Weekly Hours Of Operation` == "-" & `Operational Schedule` == "Full-Time", 40, 
                  ifelse(`Total Weekly Hours Of Operation` == "-" & `Operational Schedule` == "Part-Time", 10, `Total Weekly Hours Of Operation`))))

uds.sites[is.na(uds.sites$Zip),]

uds.sites %>% 
  arrange(`Total Weekly Hours Of Operation`, `Operational Schedule` )

# z <- geocode(chc.term$SitePhysicalAddress)
# 
# 
# y <- geo(address = chc.term$SitePhysicalAddress, method = "census")
# 
# write.csv(cbind(y[,1], y[,3], y[,2], z), file = "geocodedClosures.csv")

```

## Read in Quality data
```{r}

uds.6b.2012 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2013 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

uds.6b.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 1) 
uds.6b.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

uds.6b.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

uds.6b.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

# rbind(
# colnames(uds.6b.2014[,c(2, grep(pattern = "^%", colnames(uds.6b.2014))[-6])]),
# colnames(uds.6b.2015[,c(2, grep(pattern = "^%", colnames(uds.6b.2015))[-6])]),
# colnames(uds.6b.2016[,c(2, grep(pattern = "^%", colnames(uds.6b.2016))[-6])]),
# colnames(uds.6b.2017[,c(2, grep(pattern = "^%", colnames(uds.6b.2017))[-6])]),
# colnames(uds.6b.2018[,c(2, grep(pattern = "^%", colnames(uds.6b.2018))[-6])]),
# colnames(uds.6b.2019[,c(2, grep(pattern = "^%", colnames(uds.6b.2019))[-6])]),
# colnames(uds.6b.2020[,c(2, grep(pattern = "^%", colnames(uds.6b.2020))[-c(3, 11, 13)])]))
# 
# 
# rbind(
# colnames(uds.6b.2014[,c(2, grep(pattern = "^Total", colnames(uds.6b.2014))[-6])]),
# colnames(uds.6b.2015[,c(2, grep(pattern = "^Total", colnames(uds.6b.2015))[-6])]),
# colnames(uds.6b.2016[,c(2, grep(pattern = "^Total", colnames(uds.6b.2016))[-6])]),
# colnames(uds.6b.2017[,c(2, grep(pattern = "^Total", colnames(uds.6b.2017))[-6])]),
# colnames(uds.6b.2018[,c(2, grep(pattern = "^Total", colnames(uds.6b.2018))[-6])]),
# colnames(uds.6b.2019[,c(2, grep(pattern = "^Total", colnames(uds.6b.2019))[-6])]),
# colnames(uds.6b.2020[,c(2, grep(pattern = "^Total", colnames(uds.6b.2020))[-c(3, 11, 13)])]))

namingshit <- c("GrantNumber", "IMM2yo", "Pap", "ChildBMI","AdultBMI","Tobac","CRC","DepScrn")
namingshit.denom <- c("GrantNumber", "IMM2yo.denom", "Pap.denom", "ChildBMI.denom","AdultBMI.denom","Tobac.denom","CRC.denom","DepScrn.denom")

uds.6b.rates <- rbind(
  uds.6b.2014[,c(2, grep(pattern = "^%", colnames(uds.6b.2014))[-6])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2014), 
  uds.6b.2015[,c(2, grep(pattern = "^%", colnames(uds.6b.2015))[-6])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2015),
  uds.6b.2016[,c(2, grep(pattern = "^%", colnames(uds.6b.2016))[-6])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2016),

  uds.6b.2017[,c(2, grep(pattern = "^%", colnames(uds.6b.2017))[-6])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2017),
  uds.6b.2018[,c(2, grep(pattern = "^%", colnames(uds.6b.2018))[-6])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2018),

  uds.6b.2019[,c(2, grep(pattern = "^%", colnames(uds.6b.2019))[-6])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2019),
  uds.6b.2020[,c(2, grep(pattern = "^%", colnames(uds.6b.2020))[-c(3, 11, 13)])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2020), 
  uds.6b.2021[,c(2, grep(pattern = "^%", colnames(uds.6b.2021))[-c(3, 11, 13)])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2021))

uds.6b.rates$IMM2yo <- gsub(pattern = "%$", replacement = "", uds.6b.rates$IMM2yo)
uds.6b.rates$Pap <- gsub(pattern = "%$", replacement = "", uds.6b.rates$Pap)
uds.6b.rates$ChildBMI <- gsub(pattern = "%$", replacement = "", uds.6b.rates$ChildBMI)
uds.6b.rates$AdultBMI <- gsub(pattern = "%$", replacement = "", uds.6b.rates$AdultBMI)

uds.6b.rates$Tobac <- gsub(pattern = "%$", replacement = "", uds.6b.rates$Tobac)
uds.6b.rates$CRC <- gsub(pattern = "%$", replacement = "", uds.6b.rates$CRC)
uds.6b.rates$DepScrn <- gsub(pattern = "%$", replacement = "", uds.6b.rates$DepScrn)

uds.6b.denom <- rbind(
  uds.6b.2014[,c(2, grep(pattern = "^Total", colnames(uds.6b.2014))[-6])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2014), 
  uds.6b.2015[,c(2, grep(pattern = "^Total", colnames(uds.6b.2015))[-6])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2015),
  uds.6b.2016[,c(2, grep(pattern = "^Total", colnames(uds.6b.2016))[-6])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2016),

  uds.6b.2017[,c(2, grep(pattern = "^Total", colnames(uds.6b.2017))[-6])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2017),
  uds.6b.2018[,c(2, grep(pattern = "^Total", colnames(uds.6b.2018))[-6])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2018),

  uds.6b.2019[,c(2, grep(pattern = "^Total", colnames(uds.6b.2019))[-6])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2019),
  uds.6b.2020[,c(2, grep(pattern = "^Total", colnames(uds.6b.2020))[-c(3, 11, 13)])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2020),
  uds.6b.2021[,c(2, grep(pattern = "^Total", colnames(uds.6b.2021))[-c(3, 11, 13)])][,c(1:6, 9, 11)] %>% 
  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2021))

for (k in 2:8) uds.6b.rates[grep("-", unlist(uds.6b.rates[,k])),k] <- NA
for (k in 2:8) uds.6b.denom[grep("-", unlist(uds.6b.denom[,k])),k] <- NA

uds.6b.rates <-  data.frame(GrantNumber = uds.6b.rates$GrantNumber, Year = uds.6b.rates$Year, lapply(uds.6b.rates[,c(2:8)], as.numeric)) 
uds.6b.denom <-  data.frame(GrantNumber = uds.6b.denom$GrantNumber, Year = uds.6b.denom$Year, lapply(uds.6b.denom[,c(2:8)], as.numeric))

uds.6b.rates[uds.6b.rates$Year == 2014,c(3:9)] <- uds.6b.rates[uds.6b.rates$Year == 2014,c(3:9)] * 100
uds.6b.rates[,c(3:9)] <- uds.6b.rates[,c(3:9)]

## Finding highest-scoring quality FQHC
# uds.6b.rates %>% 
#   mutate(Qcomp = (IMM2yo + Pap + ChildBMI + AdultBMI + Tobac + CRC + DepScrn) / 7) %>% 
#   arrange(desc(Qcomp)) %>% 
#   filter(Year == 2021) %>% 
#   select(GrantNumber, Year, Qcomp) %>% 
#   left_join(chc %>% select(Health.Center.Number, Health.Center.Name, Health.Center.Organization.City, Health.Center.Organization.State) %>% unique(), by = c("GrantNumber" = "Health.Center.Number")) %>% 
#   left_join(uds.6b.denom, by = c("GrantNumber","Year"))

```

## Read in Technology Data
```{r}

uds.HIT.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "EHRInformation", skip = 0) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
uds.HIT.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "EHRInformation", skip = 2) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
uds.HIT.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)

uds.HIT.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
uds.HIT.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
uds.HIT.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)

uds.HIT.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>%
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)
uds.HIT.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "HITInformation", skip = 0) %>%
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)

uds.HIT.2020 <- data.frame(GrantNumber = uds.HIT.2020[,1], Tehr_L1b_Ca = uds.HIT.2020[,2], Tehr_L2_Ca = NA,	Tehr_L3_Ca = NA, Tehr_L4_Ca = uds.HIT.2020[,3], Tehr_L5_Ca = NA, Tehr_L7_Ca = uds.HIT.2020[,4])
uds.HIT.2021 <- data.frame(GrantNumber = uds.HIT.2021[,1], Tehr_L1b_Ca = uds.HIT.2021[,2], Tehr_L2_Ca = NA,	Tehr_L3_Ca = NA, Tehr_L4_Ca = uds.HIT.2021[,3], Tehr_L5_Ca = NA, Tehr_L7_Ca = uds.HIT.2021[,4])

namevec <- c("Year", "Grant Number", "SwitchEMR","eScripts","eDecisionSupport","InterOrgHITexchange","PatientPortals","UDSQualRep")
uds.HIT <- rbind(cbind(Year = 2014, uds.HIT.2014),
                  cbind(Year = 2015, uds.HIT.2015),
                  cbind(Year = 2016, uds.HIT.2016),
                  cbind(Year = 2017, uds.HIT.2017),

                  cbind(Year = 2018, uds.HIT.2018),
                  cbind(Year = 2019, uds.HIT.2019), 
                  cbind(Year = 2020, uds.HIT.2020),
                  cbind(Year = 2021, uds.HIT.2021)) %>%

  rename_all(vars(namevec), function(x) namevec) %>% 
  mutate(UDSQualRep.levels = ifelse(UDSQualRep == "-", NA, 
                             ifelse(UDSQualRep == "We do not use the EHR", 0, 
                             ifelse(UDSQualRep == "We use the EHR but only to access individual patient charts", 1, 
                             ifelse(UDSQualRep == "We use the EHR in combination with another data analytic system", 3, 2))))) %>% 
  mutate(UDSQualRep.highlowuse = ifelse(UDSQualRep == "-", NA, 
                             ifelse(UDSQualRep == "We do not use the EHR" | UDSQualRep == "We use the EHR but only to access individual patient charts", 0, 1))) %>%  
  mutate(SwitchEMR = ifelse(SwitchEMR == "-", NA, ifelse(SwitchEMR == "Yes", 1, 0)),
         eScripts = ifelse(eScripts == "-" | eScripts == "Not Sure", NA, ifelse(eScripts == "Yes", 1, 0)),
         eDecisionSupport = ifelse(eDecisionSupport == "-" | eDecisionSupport == "Not Sure", NA, ifelse(eDecisionSupport == "Yes", 1, 0)),
         InterOrgHITexchange = ifelse(InterOrgHITexchange == "-" | InterOrgHITexchange == "Not Sure", NA, ifelse(InterOrgHITexchange %in% c("No","None of the above"), 0, 1)),
         PatientPortals = ifelse(PatientPortals == "-" | PatientPortals == "Not Sure", NA, ifelse(PatientPortals %in% c("No","No we do not engage patients using HIT"), 0, 1)))

uds.HIT[uds.HIT$UDSQualRep.levels == 0 & !is.na(uds.HIT$UDSQualRep.levels) & is.na(uds.HIT$SwitchEMR),]$SwitchEMR <- 0
uds.HIT[uds.HIT$UDSQualRep.levels == 0 & !is.na(uds.HIT$UDSQualRep.levels) & is.na(uds.HIT$eScripts),]$eScripts <- 0
uds.HIT[uds.HIT$UDSQualRep.levels == 0 & !is.na(uds.HIT$UDSQualRep.levels) & is.na(uds.HIT$eDecisionSupport),]$eDecisionSupport <- 0
uds.HIT[uds.HIT$UDSQualRep.levels == 0 & !is.na(uds.HIT$UDSQualRep.levels) & is.na(uds.HIT$InterOrgHITexchange),]$InterOrgHITexchange <- 0
uds.HIT[uds.HIT$UDSQualRep.levels == 0 & !is.na(uds.HIT$UDSQualRep.levels) & is.na(uds.HIT$PatientPortals),]$PatientPortals <- 0

# namevec <- c("Year", "Grant Number", "SwitchEMR","InterOrgHITexchange","UDSQualRep")
# uds.HIT <- rbind(cbind(Year = 2014, uds.HIT.2014 %>% select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)),
#                   cbind(Year = 2015, uds.HIT.2015 %>% select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)),
#                   cbind(Year = 2016, uds.HIT.2016 %>% select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)),
#                   cbind(Year = 2017, uds.HIT.2017 %>% select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)),
#                   
#                   cbind(Year = 2018, uds.HIT.2018 %>% select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)),
#                   cbind(Year = 2019, uds.HIT.2019 %>% select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)),          
#                   cbind(Year = 2020, uds.HIT.2020)) %>% 
#   
#   rename_all(vars(namevec), function(x) namevec) %>% 
#   mutate(UDSQualRep.levels = ifelse(UDSQualRep == "-", NA, 
#                              ifelse(UDSQualRep == "We do not use the EHR", 0, 
#                              ifelse(UDSQualRep == "We use the EHR but only to access individual patient charts", 1, 
#                              ifelse(UDSQualRep == "We use the EHR in combination with another data analytic system", 3, 2))))) %>% 
#   mutate(UDSQualRep.highlowuse = ifelse(UDSQualRep == "-", NA, 
#                              ifelse(UDSQualRep == "We do not use the EHR" | UDSQualRep == "We use the EHR but only to access individual patient charts", 0, 1))) %>%  
#   mutate(SwitchEMR = ifelse(SwitchEMR == "-", NA, ifelse(SwitchEMR == "Yes", 1, 0)),
#          InterOrgHITexchange = ifelse(InterOrgHITexchange == "-" | InterOrgHITexchange == "Not Sure", NA, ifelse(InterOrgHITexchange %in% c("No","None of the above"), 0, 1)))

```

## Read in Covariates
```{r}
# Table 3B
uds.3B.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table3B", skip = 2) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

uds.3B.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

uds.3B.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

namevec <- c("Year", "Grant Number", "NHA", "NHB", "HL", "NHW", "Total", "Eng2ndLang")
uds.3B <- rbind(cbind(Year = 2014, uds.3B.2014),
                  cbind(Year = 2015, uds.3B.2015),
                  cbind(Year = 2016, uds.3B.2016),
                  cbind(Year = 2017, uds.3B.2017),

                  cbind(Year = 2018, uds.3B.2018),
                  cbind(Year = 2019, uds.3B.2019), 
                  cbind(Year = 2020, uds.3B.2020),
                  cbind(Year = 2021, uds.3B.2021)) %>%

  rename_all(vars(namevec), function(x) namevec)

# Table 4
uds.4.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table4", skip = 2) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)

uds.4.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)

uds.4.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)

namevec <- c("Year", "Grant Number", "<100%", "101-150%", "151-200%", ">200%", "Unknown", "FarmWorker", "Homeless", "0-17yo", "18+yo")
uds.4 <- rbind(cbind(Year = 2014, uds.4.2014),
                  cbind(Year = 2015, uds.4.2015),
                  cbind(Year = 2016, uds.4.2016),
                  cbind(Year = 2017, uds.4.2017),

                  cbind(Year = 2018, uds.4.2018),
                  cbind(Year = 2019, uds.4.2019), 
                  cbind(Year = 2020, uds.4.2020),
                  cbind(Year = 2021, uds.4.2021)) %>%

  rename_all(vars(namevec), function(x) namevec)

# Put covariate tables together

uds.covariates <- inner_join(uds.3B, uds.4, by = c("Year","Grant Number"))

for (i in 3:ncol(uds.covariates)){
  uds.covariates[,i] <- as.numeric(gsub("-", "", uds.covariates[,i]))
}

#uds.covariates %>% filter(`Grant Number` == "H80CS24200")

uds.covariates <-  uds.covariates %>% 
    mutate(Pct.NHA = NHA / Total * 100,
         Pct.NHB = NHB / Total * 100,
         Pct.HL = HL / Total * 100,
         Pct.NHW = NHW / Total * 100,
         Pct.ESL = Eng2ndLang / Total * 100,
         Pct.LessThan100pctFPL = ifelse(Total == Unknown, 100, `<100%` / (Total- Unknown) * 100),
         Pct.LessThan200pctFPL = ifelse(Total == Unknown, 100, (`<100%` + `101-150%` + `151-200%`) / (Total - Unknown) * 100),
         Pct.FarmWorker = FarmWorker / Total * 100,
         Pct.Homeless = Homeless / Total * 100,
         Pct.Children = `0-17yo` / Total * 100) %>% 
    select(Year, `Grant Number`, Pct.NHA:Pct.Children)

```

## Read in Clinical Outcomes
```{r}
uds.7.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table7_1", skip = 0) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table7_1", skip = 2) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)

uds.7.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)

uds.7.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table7_1", skip = 0) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)

namevec <- c("Year", "Grant Number", "TotalDeliveries", "BirthsLT1500","Births1500to2499","BirthsGTE2500","TotalHTN","Sample","Controlcount")
uds.7 <- rbind(cbind(Year = 2014, uds.7.2014),
                  cbind(Year = 2015, uds.7.2015),
                  cbind(Year = 2016, uds.7.2016),
                  cbind(Year = 2017, uds.7.2017),

                  cbind(Year = 2018, uds.7.2018),
                  cbind(Year = 2019, uds.7.2019), 
                  cbind(Year = 2020, uds.7.2020),
                  cbind(Year = 2021, uds.7.2021)) %>%

  rename_all(vars(namevec), function(x) namevec)

for (i in 3:ncol(uds.7)){
  uds.7[,i] <- as.numeric(gsub("-", "", uds.7[,i]))
}

```

## Read in my financial data
## Prep download
```{r}

cw <- read_excel("/Users/jhm65/Research/CHC Costs/UDS-990 Crosswalk.xlsx")

## Wave 1

EINs <- cw[!is.na(cw$EIN),]$EIN

urls <- paste("https://www.guidestar.org/profile/GetFTASheet?ein=", cw[!is.na(cw$EIN),]$EIN, "&guid=", sep = "")
destfiles <- paste("/Users/jhm65/Research/CHC Costs/990s/", cw[!is.na(cw$EIN),]$EIN, ".xlsx", sep = "") #990s_new or 990s

## Set Binary filter for data to include
z <- rep(NA, length(urls))
for (k in 1:length(EINs)){  #1174

 z[k] <- ifelse(is.data.frame(try(read_excel(destfiles[k], skip = 5) )) == TRUE, 1, 0)

}

## Set first rows in data
chc.990 <- read_excel(destfiles[1], skip = 5)
years <- as.numeric(colnames(chc.990)[-1])
chc.990 <- chc.990[-c(5, 6, 15, 16, 25, 26, 32, 33, 34, 35, 39, 40, 52:58),]

chc.990[,2] <- as.numeric(gsub(unlist(chc.990[,2]), pattern = "N/A", replacement = NA))
chc.990[,3] <- as.numeric(gsub(unlist(chc.990[,3]), pattern = "N/A", replacement = NA))
chc.990[,4] <- as.numeric(gsub(unlist(chc.990[,4]), pattern = "N/A", replacement = NA))
chc.990[,5] <- as.numeric(gsub(unlist(chc.990[,5]), pattern = "N/A", replacement = NA))
chc.990[,6] <- as.numeric(gsub(unlist(chc.990[,6]), pattern = "N/A", replacement = NA))

headers <- unlist(chc.990[,1])
chc.990 <- data.frame(t(chc.990[,-1]))

colnames(chc.990) <- headers
rownames(chc.990) <- NULL

chc.finances <- cbind(ID = EINs[1], year = years, chc.990)

## Repeat for the whole set
for (k in 2:1174){
  if(z[k] == 1 & k %notin% c(388, 511, 670)){ ##remove entries for now, check later if this clinic gets data
chc.990 <- read_excel(destfiles[k], skip = 5)
years <- as.numeric(colnames(chc.990)[-1])
chc.990 <- chc.990[-c(5, 6, 15, 16, 25, 26, 32, 33, 34, 35, 39, 40, 52:58),]

  for (j in 2:ncol(chc.990)){
    chc.990[,j] <- as.numeric(gsub(unlist(chc.990[,j]), pattern = "N/A", replacement = NA))
  }

headers <- unlist(chc.990[,1])
chc.990 <- data.frame(t(chc.990[,-1]))

colnames(chc.990) <- headers
rownames(chc.990) <- NULL

chc.finances <- rbind(chc.finances, cbind(ID = EINs[k], year = years, chc.990) )} else {print(k)}
}

table(chc.finances$year)

quantile(chc.finances$`Unrestricted surplus (deficit) after depreciation`, probs = c(0, 0.025, 0.1, 0.25, 0.5, 0.75, 0.9, 0.975, 1))

colnames(chc.finances) <- gsub("\\%", "pct", colnames(chc.finances))
colnames(chc.finances)[c(4, 6)] <- c("Surplus as a pct of before dep expenses","Surplus as a pct of after dep expenses")

## Wave 2

EINs <- cw[!is.na(cw$EIN),]$EIN

urls <- paste("https://www.guidestar.org/profile/GetFTASheet?ein=", cw[!is.na(cw$EIN),]$EIN, "&guid=", sep = "")
destfiles <- paste("/Users/jhm65/Research/CHC Costs/990s_new/", cw[!is.na(cw$EIN),]$EIN, ".xlsx", sep = "") #990s_new or 990s

## Set Binary filter for data to include
z <- rep(NA, length(urls))
for (k in 1:length(EINs)){  #1174

 z[k] <- ifelse(is.data.frame(try(read_excel(destfiles[k], skip = 5) )) == TRUE, 1, 0)

}

## Set first rows in data
chc.990 <- read_excel(destfiles[1], skip = 5)
years <- as.numeric(colnames(chc.990)[-1])
chc.990 <- chc.990[-c(5, 6, 15, 16, 25, 26, 32, 33, 34, 35, 39, 40, 52:58),]

chc.990[,2] <- as.numeric(gsub(unlist(chc.990[,2]), pattern = "N/A", replacement = NA))
chc.990[,3] <- as.numeric(gsub(unlist(chc.990[,3]), pattern = "N/A", replacement = NA))
chc.990[,4] <- as.numeric(gsub(unlist(chc.990[,4]), pattern = "N/A", replacement = NA))
chc.990[,5] <- as.numeric(gsub(unlist(chc.990[,5]), pattern = "N/A", replacement = NA))
chc.990[,6] <- as.numeric(gsub(unlist(chc.990[,6]), pattern = "N/A", replacement = NA))

headers <- unlist(chc.990[,1])
chc.990 <- data.frame(t(chc.990[,-1]))

colnames(chc.990) <- headers
rownames(chc.990) <- NULL

chc.fin.2 <- cbind(ID = EINs[1], year = years, chc.990)

## Repeat for the whole set
for (k in 2:1174){
  if(z[k] == 1 & k %notin% c(388, 511, 670)){ ##remove entries for now, check later if this clinic gets data
chc.990 <- read_excel(destfiles[k], skip = 5)
years <- as.numeric(colnames(chc.990)[-1])
chc.990 <- chc.990[-c(5, 6, 15, 16, 25, 26, 32, 33, 34, 35, 39, 40, 52:58),]

  for (j in 2:ncol(chc.990)){
    chc.990[,j] <- as.numeric(gsub(unlist(chc.990[,j]), pattern = "N/A", replacement = NA))
  }

headers <- unlist(chc.990[,1])
chc.990 <- data.frame(t(chc.990[,-1]))

colnames(chc.990) <- headers
rownames(chc.990) <- NULL

chc.fin.2 <- rbind(chc.fin.2, cbind(ID = EINs[k], year = years, chc.990) )} else {print(k)}
}

table(chc.fin.2$year)

quantile(chc.fin.2$`Unrestricted surplus (deficit) after depreciation`, probs = c(0, 0.025, 0.1, 0.25, 0.5, 0.75, 0.9, 0.975, 1))

colnames(chc.fin.2) <- gsub("\\%", "pct", colnames(chc.fin.2))
colnames(chc.fin.2)[c(4, 6)] <- c("Surplus as a pct of before dep expenses","Surplus as a pct of after dep expenses")

nrow(chc.finances[chc.finances$`Unrestricted surplus (deficit) after depreciation` <= 250000 & chc.finances$year == 2017,]) / nrow(chc.finances[chc.finances$year == 2017,])

```

## Read in my termination crosswalk to filter out closures
```{r}
chc.term <- read.csv("CHC_termination_crosswalk.csv")
staffing <- read.csv("/Users/jhm65/Research/CHC Costs/FQHC_Staffing.csv")
```

## Read in census data for all zip codes
```{r}

census <- data.frame(ZipCode = 0, NAME = 0, YEAR = 0, 
                     TotalPop = 0,
                     Male = 0, Female = 0, 
                     AgeUnder18 = 0, Age18to64 = 0, Age65andOver = 0, 
                     White = 0, Black = 0, AIAN = 0, Asian = 0, MR = 0, Hispanic = 0, EducLow = 0, EducMid = 0, EducHigh = 0, 
                     PovertyStatusDet = 0, IncomeBelowPoverty = 0, Unemployed = 0, Unemp_denom = 0, 
                     MCD.denom = 0, Medicaid = 0, Unins.denom = 0, Uninsured = 0)

for (i in 1:7){
  census <- rbind(census, get_acs(geography = "zcta", survey = "acs5",
                       variables = c("B01003_001","B17001_001","B17001_002","B01001_002","B01001_026",
                                     "B02001_002","B02001_003","B02001_004","B02001_005","B02001_006","B02001_008",
                                     "B03001_003", 
                                     "B01001_003","B01001_004","B01001_005","B01001_006","B01001_007","B01001_008","B01001_009",
                                     "B01001_010","B01001_011","B01001_013","B01001_014","B01001_015","B01001_016","B01001_017",
                                     "B01001_018","B01001_019","B01001_020","B01001_021","B01001_022","B01001_023","B01001_024","B01001_025",
                                     "B01001_027","B01001_028","B01001_029","B01001_030","B01001_031","B01001_032","B01001_033","B01001_034",
                                     "B01001_035","B01001_036","B01001_037","B01001_038","B01001_039","B01001_040","B01001_041","B01001_042","B01001_043",
                                     "B01001_044","B01001_045","B01001_046","B01001_047","B01001_048","B01001_049",
                                     "B06009_002","B06009_003", "B06009_004","B06009_005","B06009_006",
                                     "B23025_002","B23025_005",
                                     "C27007_001", "C27007_004", "C27007_007", "C27007_010", "C27007_014", "C27007_017", "C27007_020",
                                     "B18135_001","B18135_007","B18135_012","B18135_018","B18135_023","B18135_029","B18135_034"), 
                       year = 2013 + i) %>% 
  pivot_wider(id_cols = c(GEOID, NAME), names_from = variable, values_from = estimate) %>% 
    mutate(YEAR = 2013 + i, TotalPop = B01003_001, PovertyStatusDet = B17001_001, IncomeBelowPoverty = B17001_002,
           AgeUnder18 = B01001_003 + B01001_004 + B01001_005 + B01001_006 + B01001_027 + B01001_028 + B01001_029 + B01001_030,
           Age18to64 = B01001_007 + B01001_008 + B01001_009 + B01001_010 + B01001_011 + B01001_013 + B01001_014 + B01001_015 + 
                       B01001_016 + B01001_017 + B01001_018 + B01001_019 + B01001_031 + B01001_032 + B01001_033 + B01001_034 +
                       B01001_035 + B01001_036 + B01001_037 + B01001_038 + B01001_039 + B01001_040 + B01001_041 + B01001_042 + B01001_043, 
           Age65andOver = B01001_020 + B01001_021 + B01001_022 + B01001_023 + B01001_024 + B01001_025 + 
                          B01001_044 + B01001_045 + B01001_046 + B01001_047 + B01001_048 + B01001_049, 
           Male = B01001_002, Female = B01001_026, 
           White = B02001_002, Black = B02001_003, AIAN = B02001_004, Asian = B02001_005 + B02001_006, MR = B02001_008, 
           Hispanic = B03001_003, 
           EducLow = B06009_002, EducMid = B06009_003 + B06009_004, EducHigh = B06009_005 + B06009_006,
           Unemployed = B23025_005, Unemp_denom = B23025_002,
           MCD.denom = C27007_001	, Medicaid = C27007_004	 + C27007_007 + C27007_010	+ C27007_014 + C27007_017 + C27007_020,
           Unins.denom = B18135_001, Uninsured = B18135_007 + B18135_012 + B18135_018 + B18135_023 + B18135_029 + B18135_034) %>% 
    select(ZipCode = GEOID, NAME, YEAR, TotalPop:Uninsured))

  print(i)
}
census <- census[-1,]

##########
census$ZipCode <- substr(census$NAME, 7, 11)
#census$ZipCode <- str_pad(census$ZipCode, 5, pad = "0")

census %>% 
  filter(YEAR == 2020) %>% 
  select(ZipCode) %>% 
  #unique() %>% 
  table() %>% 
  table()
```

# Analysis
## SEt data again

```{r}

uds.sites[!is.na(uds.sites$Zip),] %>% 
  group_by(`Grant Number`, Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  select(`Grant Number`, Zip, Year, Counts) %>% 
  unique() %>% 
  arrange(Year) %>% 
  pivot_wider(id_cols = c(`Grant Number`, Zip), names_from = Year, values_from = Counts, values_fill = 0) %>% 
  arrange(Zip)

```

## Set Data
```{r}
# Identify number of clinics in each zip code-year
clinics.in.zips <- uds.sites[!is.na(uds.sites$Zip),] %>%
  group_by(Zip, Year) %>%
  summarise(Clinics = n_distinct(`Grant Number`), Sites = n()) %>%
  arrange(desc(Clinics))

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites[!is.na(uds.sites$Zip),] %>% 
  select(`Grant Number`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `Grant Number`, names_from = Year, values_from = Clinics) %>% 
  filter(`2014` == 1 & `2015` == 1 & `2016` == 1 ) %>%   
  #filter(`2014` == 1 & `2015` == 1) %>%  
  left_join(chc.term, by = c("Grant Number" = "ClinicID")) %>%
  filter(is.na(NewClinicID)) %>%
  select(`Grant Number`:`2021`) %>% 
  pivot_longer(cols = c(`2014`:`2021`)) %>% 
  group_by(`Grant Number`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

# Classify clinics by introduction of competition
df.comp <- left_join(clinics.comp %>% mutate(Year = as.numeric(name)), uds.zip.totals, by = c("Grant Number", "Year" = "Reporting Year")) %>% 
  left_join(uds.sites[!is.na(uds.sites$Zip),] %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(Sites = n()), by = c("Grant Number", "Year")) %>% 
  ungroup() %>% 
  group_by(`Grant Number`) %>% 
  mutate(Att = min(ifelse(Tx == 0, 2, 1)*Year, na.rm = TRUE) ) %>% 
  group_by(`Grant Number`) %>% 
  mutate(Att = ifelse(Att < 2022, Att, 0)) %>% 
  ungroup() %>% 
  mutate(ID = as.numeric(factor(`Grant Number`)))

# Identify expandors vs expandees
df.expand <- df.comp %>% 
  left_join(
      left_join(df.comp %>% select(`Grant Number`, Att), uds.sites[!is.na(uds.sites$Zip),] %>% 
        select(`Grant Number`, Zip, Year) %>% 
        group_by(`Grant Number`, Zip) %>% 
        summarise(YearFirstInZip = min(Year)) %>% 
        filter(YearFirstInZip %notin% c(2014)) %>% 
        select(`Grant Number`, YearFirstInZip) %>% 
        unique(), by = c("Grant Number")) %>% #filter(`Grant Number` == "H80CS00101") %>% 
        mutate(Expandor = ifelse(is.na(YearFirstInZip) | Att != YearFirstInZip, 0, 1)) %>%  #  is.na(YearFirstInZip) | Att != YearFirstInZip
        group_by(`Grant Number`) %>% summarise(Expandor = max(Expandor)), by = c("Grant Number")) %>% 
  left_join(uds.HIT, by = c("Grant Number", "Year"))

df.expand <- df.expand %>% 
  left_join(df.expand %>% filter(SwitchEMR == 1) %>%  
            select(`Grant Number`, Year, SwitchEMR) %>% 
            group_by(`Grant Number`) %>% 
            summarise(FirstSwitch = min(Year)), by = c("Grant Number")) #%>% mutate(SwitchEMR = ifelse(is.na(FirstSwitch), 0, ifelse(Year >= FirstSwitch & FirstSwitch >= 2014, 1, 0)))

df.qual.exp <- df.expand %>% 
  left_join(uds.6b.rates, by = c("Grant Number" = "GrantNumber", "Year")) %>% 
  left_join(uds.6b.denom, by = c("Grant Number" = "GrantNumber", "Year")) %>% 
  #filter(Expandor == 0 & Year %in% c(2015, 2016, 2017, 2018, 2019, 2020) & Att %in% c(0, 2017, 2018, 2019, 2020)) %>%  ## Regular go to analysis
  filter(Expandor == 0 & Year %in% c(2015, 2016, 2017, 2018, 2019) & Att %in% c(0, 2017, 2018, 2019)) %>%  ## Really pronounced causal responses, weak first order stuff
  #filter(Expandor == 0 & Year %in% c(2014, 2015, 2016, 2017, 2018, 2019, 2020, 2021) & Att %in% c(0, 2017, 2018, 2019)) %>%
  left_join(uds.sites %>% 
    group_by(`Grant Number`, Year) %>% 
    summarise(TotalAccess = sum(Access, na.rm = T)), by = c("Grant Number","Year")) %>%
inner_join(uds.sites %>% filter(Year == 2015) %>% select(`Grant Number`, Zip) %>% group_by(`Grant Number`) %>% summarise(Zips = n_distinct(Zip)), by = c("Grant Number")) %>%
  mutate(ZipFilter = ifelse(Zips > 2.75, 2, 1)) %>% 
#inner_join(uds.sites %>% filter(Year == 2014) %>% select(`Grant Number`, Zip) %>% group_by(`Grant Number`) %>% summarise(Zips = n_distinct(Zip)) %>% filter(Zips > 2.75), by = c("Grant Number")) %>%
#inner_join(df.expand %>% filter(Year == 2015) %>% mutate(ZipFilter = ifelse(Total > median(Total), 2, 1)) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
  mutate(l.Sites = log(Sites),
         l.Total = log(Total))

k = 1  # 1 for larger group, 0 for smaller clinic group OOOOOOORRRRRRR 2 for large, 1 for medium, and 0 for small

# df.qual.exp <- inner_join(uds.sites %>% select(`Grant Number`, `Site State`) %>% unique(), df.qual.exp, by = c("Grant Number")) %>%
# mutate(ACA = ifelse((`Site State` %in% c('MI','NH') & Year >= 2014) |
#                     (`Site State` %in% c('PA','IN','AK') & Year >= 2015) |
#                     (`Site State` %in% c('MT','LA') & Year >= 2016) |
#                     (`Site State` %in% c('VA','ME') & Year >= 2019) |
#                     (`Site State` %in% c('ID','UT','NE') & Year >= 2020) |
#                     (`Site State` %in% c('OK','MO') & Year >= 2021) |
#                     (`Site State` %in% c('AZ','AR','CA','CO','CT','DE','DC','HI','IL','IA','KY','MD','MA','MN','NV','NJ','NM','NY','ND','OH','OR','PA','RI','VT','VA','WA') & Year >= 2014), 1, 0)) %>%
#   select(`Grant Number`, ZipFilter, value:ACA)

# %>%
#   group_by(`Grant Number`) %>%
#   filter(max(ACA) == 0 | min(ACA) == 1) %>%
#   ungroup()

df.qual.exp <- df.qual.exp %>% 
  mutate(
    None = None / Total * 100,
         MCR = MCR / Total * 100,
         COM = COM / Total * 100,
         MCD = MCD / Total * 100,

         SwitchEMR = SwitchEMR * 100, 
         eScripts = eScripts* 100, 
         eDecisionSupport = eDecisionSupport * 100, 
         InterOrgHITexchange = InterOrgHITexchange * 100, 
         PatientPortals = PatientPortals * 100, 
         UDSQualRep.highlowuse = UDSQualRep.highlowuse * 100) %>% 
  left_join(uds.covariates, by = c("Grant Number","Year")) %>% 
  left_join(uds.7, by = c("Grant Number","Year")) %>% 
  mutate(Pct.HBW = BirthsGTE2500 / TotalDeliveries * 100, 
         Pct.HTN.CNTRL = Controlcount / Sample * 100) %>%

  left_join(cw %>% select(`Grant Number`, EIN), by = c("Grant Number")) %>% 
  left_join(unique(rbind(chc.finances, chc.fin.2) %>% group_by(ID, year) %>% summarise_all(max)) %>% 
  arrange(ID, year), by = c("EIN" = "ID", "Year" = "year")) %>% 
  mutate(Liabilities = `Liabilities (as pct of assets)` * `Total net assets`, 
         Staffing = `Total expenses before depreciation` * Personnel, 
         LBE.pct = `Gross land, buildings and equipment (LBE)` / `Total net assets`, 
         `Liabilities (as pct of assets)` = `Liabilities (as pct of assets)` * 100, 
         `Surplus as a pct of before dep expenses` = `Surplus as a pct of before dep expenses` * 100, 
         Qcomp = (IMM2yo + Pap + ChildBMI + AdultBMI + Tobac + CRC + DepScrn) / 7, 
         CostOfCare = `Total expenses before depreciation` / Total) %>%

  mutate(Liquidity =  `Total net assets` / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
         Profitability =  `Unrestricted surplus (deficit) before depreciation` / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
         Efficiency = (`Total revenue (unrestricted & restricted)` - `Total expenses before depreciation`) / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
         NetWorth = (100 - `Liabilities (as pct of assets)`) / `Liabilities (as pct of assets)` / 100) %>% 
  mutate(Altmans.Z = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% # 6.56, 3.26, 6.72, 1.05  OR 0.18, 0.3, 0.81, 0.14
  mutate(Liquidity = ifelse(Liquidity == 'Inf', NA, Liquidity), 
         Profitability = ifelse(Profitability == 'Inf', NA, Profitability), 
         Efficiency = ifelse(Efficiency == 'Inf', NA, Efficiency), 
         NetWorth = ifelse(NetWorth == 'Inf', NA, NetWorth), 
         Altmans.Z = ifelse(Altmans.Z == 'Inf', NA, Altmans.Z)) #%>%   filter(!is.na(Altmans.Z) & Altmans.Z != 'Inf')

df.qual.exp %>%
  group_by(Att, Expandor) %>%
  summarise(n() / 6)

df.qual.exp %>% 
  group_by(Tx) %>% 
  summarise(mean(Altmans.Z, na.rm = TRUE), sd(Altmans.Z, na.rm = TRUE))

##########
## Using penetration rate to filter instead of zip codes
##########
#IncomeBelowPoverty

years <- unique(df.qual.exp$Year)

#FQHC penetration rate by zip code
temp1 <- uds.zip %>%
  filter(`Reporting Year` == 2015 ) %>%
  inner_join(uds.sites[!is.na(uds.sites$Zip),] %>%
              filter(Year %in% years), by = c("Grant Number","Zip Code" = "Zip", "Reporting Year" = "Year")) %>%
  select(`Grant Number`, `Reporting Year`, `Zip Code`, `Total Number of Patients`) %>%
  left_join(census, by = c("Zip Code" = "ZipCode","Reporting Year" = "YEAR")) %>% #,"Reporting Year" = "YEAR"
  mutate(MarketShare = `Total Number of Patients` / IncomeBelowPoverty) %>%#IncomeBelowPoverty or TotalPop
  unique()

temp1 %>% 
  filter(`Reporting Year` == 2020)

census %>% filter(YEAR == 2020)
# FQHC weighted average penetration rate conditional on site in zip

temp2 <- temp1 %>%
  mutate(Num = IncomeBelowPoverty * MarketShare) %>%
  group_by(`Grant Number`, `Reporting Year`) %>%
  summarise(Num = sum(Num, na.rm = TRUE)) %>%
  left_join(temp1 %>%
  group_by(`Grant Number`, `Reporting Year`) %>%
  summarise(YTotal = sum(IncomeBelowPoverty, na.rm = TRUE)), by = c("Grant Number","Reporting Year")) %>% #IncomeBelowPoverty
  mutate(MarketShare = Num / YTotal) %>%
  select(`Grant Number`, `Reporting Year`, MarketShare)

df.qual.exp <- df.qual.exp %>%
  select(`Grant Number`, value:Altmans.Z) %>% 
  left_join(temp2, by = c("Grant Number")) %>% #,"Year" = "Reporting Year")) %>%
  #mutate(ZipFilter = ifelse(MarketShare > median(MarketShare, na.rm = FALSE), 2,  # - 0.25
  #                   ifelse(is.na(MarketShare) == T, 1, 1))) %>%
  mutate(ZipFilter = ifelse(MarketShare >= median(MarketShare, na.rm = TRUE), 2, 1)) %>% #median(MarketShare, na.rm = TRUE)
  select(`Grant Number`, ZipFilter, MarketShare, value:Altmans.Z) %>%
  # inner_join(df.qual.exp %>% filter(Year == 2016) %>% mutate(Filter = ifelse(`Surplus as a pct of after dep expenses` < 0, 1, 
  #                                                                     ifelse(`Surplus as a pct of after dep expenses` > 0.03, 2, NA))) %>% select(`Grant Number`, Filter), by = c("Grant Number")) %>% 
  # select(`Grant Number`, ZipFilter, Filter, MarketShare, value:Altmans.Z) %>% 
  #mutate(ZipFilter = Filter) %>% 
  unique()

summary(df.qual.exp$MarketShare)
summary(df.qual.exp$Zips)
summary(df.qual.exp$`Surplus as a pct of after dep expenses`)

df.qual.exp %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n(), n_distinct(ID))
df.qual.exp %>% filter(`Grant Number` == "H80CS00225")

cnames <- colnames(df.qual.exp)

compare <- read.csv("comeptition.data.final.csv")[,-1]
colnames(compare) <- cnames

# df.qual.exp <- compare
# df.qual.exp <- df.qual.exp %>%
#   #select(`Grant Number`:Year) %>%
#   inner_join(compare %>% select(`Grant Number`, Year, value), by = c("Grant Number","Year")) %>%
#   filter(value.x == value.y) %>%
#   select(`Grant Number`:Altmans.Z) %>%
#   rename(value = value.x)

df.qual.exp <- df.qual.exp %>% rbind(compare %>% filter(`Grant Number` %in% c("H80CS00765","H80CS00881","H80CS02323") & Year %in% unique(df.qual.exp$Year) )) %>% 
  filter(`Grant Number` != "H80CS00225")

uds.sites[!is.na(uds.sites$Zip),] %>% 
  #select(`Grant Number`, Zip, Year) %>% 
  unique() %>% filter(`Grant Number` %in% c("H80CS00881") & Year == 2016)

# df.qual.exp %>% 
#   select(`Grant Number`, Year, value) %>% 
#   full_join(compare %>% select(`Grant Number`, Year, value), by = c("Grant Number","Year")) %>% 
#   filter(is.na(value.x) | is.na(value.y))

#write.csv(df.qual.exp, file = "comeptition.data.final_2.csv") DO NOT UNCOMMENT THIS LINE AS IT WILL OVERWRITE MY BACKUP DATA

#df.qual.exp <- read.csv("comeptition.data.final_2.csv")

## Add in urbanicity
all.density <- uds.sites %>% 
  filter(Year == 2016) %>% 
  select(`Grant Number`, Zip) %>% 
  unique()

zipsize2 <- zctas(cb = TRUE, year = 2010)

density.calc <- all.density %>% 
  left_join(census %>% filter(YEAR == 2016), by = c("Zip" = "ZipCode")) %>% 
  left_join(zipsize2 %>% select(ZCTA5, CENSUSAREA), by = c("Zip" = "ZCTA5")) %>% 
  group_by(`Grant Number`) %>% 
  mutate(num = sum(TotalPop, na.rm = TRUE), denom = sum(CENSUSAREA, na.rm = TRUE)) %>% 
  mutate(Density = num / denom) %>% 
  mutate(Pct.Rural = ifelse(Density < 500, 1, 0), 
         Pct.Urban = ifelse(Density > 2500, 1, 0)) %>% 
  select(`Grant Number`, Density, Pct.Rural, Pct.Urban) %>% 
  unique()

df.qual.exp <- df.qual.exp %>% 
  left_join(density.calc, by = c("Grant Number")) #%>% mutate(ZipFilter = ifelse(Density >= median(Density), 2, 1))

df.expand %>% 
  filter(`Grant Number` == "H80CS00101")

uds.sites %>% filter(`Grant Number` == "H80CS00101") %>% 
  group_by(Zip) %>% 
  summarise(min(Year))
```

## What's happening with the closures?
```{r}

closures <- uds.sites[!is.na(uds.sites$Zip),] %>% 
  select(`Grant Number`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `Grant Number`, names_from = Year, values_from = Clinics) %>% 
  filter(`2014` == 1 & `2015` == 1 & `2016` == 1 ) %>% 
  left_join(chc.term, by = c("Grant Number" = "ClinicID")) %>% 
  filter(!is.na(NewClinicID))

closures <- closures %>% pivot_longer(`2014`:`2021`) %>%
  mutate(Outcome = ifelse(!is.na(NewClinicID) & is.na(value), 1, 0))

closures <- closures %>% 
  left_join(closures %>% 
    group_by(`Grant Number`) %>% 
    filter(value > 1) %>% 
    filter(name == min(name)) %>% 
    select(`Grant Number`, name), by = c("Grant Number")) %>% 
  #rename(Year = name.x) %>% 
  mutate(Att = as.numeric(ifelse(is.na(name.y), "0", name.y)), 
         Year = as.numeric(name.x)) %>% 
    select(`Grant Number`, Year, Att, Outcome) %>% 
  rbind( df.qual.exp %>% 
  mutate(Outcome = 0) %>% 
  select(`Grant Number`, Year, Att, Outcome)) %>% 
  mutate(ID = as.numeric(factor(`Grant Number`)), 
         Tx = ifelse(Year >= Att, 1, 0))

summary(lm(data = closures, Outcome ~ Tx + as.factor(Year)))

cs.output.expand <- att_gt( yname = "Outcome",
                      tname = "Year",
                      idname = "ID",
                      gname = "Att",
                      xformla = ~1,
                      data = closures, 
                      control_group = "nevertreated",
                      panel = FALSE, 
                      clustervars = "ID",
                      base_period = "universal"
                      )
aggte(cs.output.expand, type = "simple", na.rm = TRUE)
```

## Play environment
```{r}

cs.output.expand <- att_gt( yname = "Qcomp",
                      tname = "Year",
                      idname = "ID",
                      gname = "Att",
                      xformla = ~Pct.NHB.y + Pct.HL.y + Pct.LessThan100pctFPL.y + Pct.FarmWorker.y + Pct.Homeless.y + Pct.Children.y,
                      data = df.qual.exp %>% 
  left_join(cw %>% left_join(staffing, by = c("EIN")) %>% 
  select(`Grant Number`, Year, Staff) %>% mutate(Year = as.numeric(Year), Staff = as.numeric(Staff)), by = c("Grant Number","Year")) %>% 
    left_join(df.qual.exp %>% filter(Year == 2016) %>% select(`Grant Number`, Pct.NHA:Pct.Children), by = c("Grant Number")) %>% 
    filter(ZipFilter == 1), # / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`) * 1000), # %>% inner_join(df.qual.exp %>% filter(Year == 2016 & `Surplus as a pct of before dep expenses`< 2) %>% select(`Grant Number`), by = c("Grant Number")),  # %>% select(Year, ID, Att, `Gross land, buildings and equipment (LBE)`) %>% filter(!is.na(`Gross land, buildings and equipment (LBE)`)), ### Split surplus pct after dep at 0 and 0.05 in 2016 plus ZipFilter ==2
                      control_group = "nevertreated",
                      panel = TRUE, 
                      clustervars = "ID",
                      base_period = "universal"
                      )
aggte(cs.output.expand, type = "simple", na.rm = TRUE)

cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)
data.frame(Year = cs.output.expand.agg.dyn$egt, 
           Estimate = cs.output.expand.agg.dyn$att.egt, 
           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt) %>% 
  # mutate(CILB = replace(CILB, Year == -1, NA), 
  #        CIUB = replace(CIUB, Year == -1, NA)) %>% 
  #filter(abs(Year) < 4) %>% 
  ggplot(mapping = aes(x = Year, y = Estimate)) + 
  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") + 
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") + 
  geom_point() + geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) + theme_tufte_revised()

summary(df.qual.exp[df.qual.exp$Year %in% c(2016:2019),]$`Liabilities (as pct of assets)`)

# Surplus as a pct of after dep expenses
# Liabilities (as pct of assets)
# Qcomp
# Gross land, buildings and equipment (LBE)

df.qual.exp %>%
  #filter(Att == 2020 & Year == 2020) %>%
  select(Att, Year, `Gross land, buildings and equipment (LBE)`, Sites, Altmans.Z, None) %>%
  mutate(Treat = ifelse(Att > 0, 1, 0)) %>%
  group_by(Att, Year) %>%
  summarize(Outcome = mean(None, na.rm = TRUE)) %>%
 # mutate(Outcome = ifelse(Outcome < -5, -5, Outcome)) %>%
  ggplot(aes(x = Year, y = Outcome, group = factor(Att), color = factor(Att))) + geom_point() #+ geom_jitter()

# uds.zip.totals %>% 
#   mutate(LowInc = (None + MCD) / Total) %>% 
#   filter(LowInc < 0.5 & `Reporting Year` == 2019)
#summary(lm(data = df.qual.exp, Qcomp ~ MarketShare + factor(Year) + factor(`Grant Number`)))

#df.qual.exp %>% filter(Year == 2016 & `Surplus as a pct of after dep expenses` < 0 & ZipFilter == 2)

```

## Quick Matching to see if shit changes
```{r}

# df.match <- df.qual.exp %>% filter(Year == 2015) %>%
#   select(`Grant Number`, Att, MCD, Total, Sites, Pct.NHB, Pct.HL, Pct.Children, Pct.LessThan100pctFPL)
# 
# 
# FIPS <- df.match$`Grant Number`
# X <- as.matrix(df.match[,c(3:9)])
# Tr <- ifelse(df.match$Att > 0, 1, 0)
# 
# summary(X)
# 
# m <- Match(Tr = Tr, X = X, M = 1) #, replace = TRUE)
# #mb <- MatchBalance(Treatment ~ . - FIPS, data=df.match, match.out=m, nboots=500)
# 
# df.matched <- data.frame(FIPS[m$index.treated], FIPS[m$index.control]) %>%
#   mutate(Paired = paste(FIPS[m$index.treated], FIPS[m$index.control], sep = "-"))
# 
# df.matched <- rbind(df.matched %>%
#         select(FIPS.m.index.treated., Paired) %>%
#         rename(FIPS = FIPS.m.index.treated.) %>%
#         mutate(Treatment = 1),
#       df.matched %>%
#         select(FIPS.m.index.control., Paired) %>%
#         rename(FIPS = FIPS.m.index.control.) %>%
#         mutate(Treatment = 0)) %>%
#   rename(`Grant Number` = FIPS)
# 
# df.qual.exp <- inner_join(df.matched %>% select(`Grant Number`, Treatment), df.qual.exp, by = c("Grant Number")) # %>% unique()

```

# Figures

## Prep for the robustness tests
```{r}
atts <- c("Primo", rep(0, 6))

# cbind("Sites", round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
#       cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
#       cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
#       cs.output.expand.agg.dyn$overall.att, 
#       cs.output.expand.agg.dyn$overall.att - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se, 
#       cs.output.expand.agg.dyn$overall.att + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se), 3))
z <- c("Primo", 0) #cs.output.expand$Wpval

```

## Figure 0 - Demographics
```{r}
df.qual.exp %>% 
  mutate(Treat = ifelse(Att > 0, 1, 0)) %>% 
  mutate(Groups = ifelse(Treat == 1 & Expandor == 0, "Treated", 
                  ifelse(Treat == 0 & Expandor == 0, "Control", 
                  ifelse(Treat == 0 & Expandor == 1, "Expandor Comp", "Expandor No Comp")))) %>% 
  filter(Year == 2015) %>%  #z & ZipFilter == 2) %>% 
  select(Sites, Zips, #MarketShare, 
         Total, None:MCD, IMM2yo:DepScrn, Groups, Pct.NHA:Pct.NHW, Pct.LessThan200pctFPL, Pct.Homeless:Pct.Children, `Liabilities (as pct of assets)`, `Gross land, buildings and equipment (LBE)`, `Surplus as a pct of after dep expenses`) %>% #SwitchEMR, InterOrgHITexchange, UDSQualRep.highlowuse, 
  tbl_summary(by = Groups, 
              statistic = all_continuous() ~ "{mean} ({sd})") %>% 
  add_p(test = everything() ~ "t.test")

df.qual.exp %>% mutate(Treat = ifelse(Att > 0, 1, 0)) %>% group_by(Treat) %>% summarise(n())

df.qual.exp %>% 
  filter(Year %in% c(2015, 2016)) %>% 
  mutate(Groups = ifelse(is.na(Personnel), "NoFins", "Fins")) %>% 
 #z & ZipFilter == 2) %>% 
  select(Sites, Zips, #MarketShare, 
         Total, None:MCD, #IMM2yo:DepScrn, 
         Groups, Pct.NHA:Pct.NHW, Pct.LessThan200pctFPL, Pct.Homeless:Pct.Children) %>% #SwitchEMR, InterOrgHITexchange, UDSQualRep.highlowuse, 
  tbl_summary(by = Groups, 
              statistic = all_continuous() ~ "{mean} ({sd})", digits = all_continuous() ~ 2) %>% 
  add_p(test = everything() ~ "t.test")

df.qual.exp %>% 
  mutate(Groups = ifelse(is.na(Personnel), "NoFins", "Fins")) %>% 
  group_by(Groups) %>% 
  summarise(n())

R.version

442*5
37*5
518/1877

442+37

```

## Figure 1 - Trends over time

```{r}
## Plot
p <- uds.sites[!is.na(uds.sites$Zip),] %>% 
  select(`Grant Number`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  group_by(Year, Clinics) %>% 
  summarise(Count = n()) %>% 
  mutate(CompetitorsInArea = factor(ifelse( Clinics < 4, Clinics - 1, "3+"))) %>% 
  group_by(Year, CompetitorsInArea) %>% 
  summarise(Count = sum(Count))

plot <- p %>% 
  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + 
  geom_point() + geom_line() + theme_minimal() + 
  ggtitle("Figure 1 - Counts of FQHCs by number of competing FQHCs in service area, 2014-2021") + ylab("Number of FQHCs") 
plot + scale_color_discrete(name = "Competitors")

## Table
uds.sites[!is.na(uds.sites$Zip),] %>% 
  select(`Grant Number`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  group_by(Year, Clinics) %>% 
  summarise(Count = n()) %>% 
  mutate(CompetitorsInArea = factor(ifelse( Clinics < 4, Clinics - 1, "3+"))) %>% 
  group_by(Year, CompetitorsInArea) %>% 
  summarise(Count = sum(Count)) %>% 
  pivot_wider(id_cols = CompetitorsInArea, names_from = Year, values_from = Count)

plot0 <- p %>% 
  arrange(CompetitorsInArea) %>% 
  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
  geom_point() + geom_line() + theme_tufte_revised() + ggtitle("FQHCs by Number of Rival Clinics") + 
  geom_dl(label=c(rep("0 Competitors", 8), rep("1 Competitor", 8), rep("2 Competitors", 8), rep("3+ Competitors", 8)), 
          method = list("last.points", hjust = 1, vjust = 3, cex = 0.75), inherit.aes=T ) + 
  guides(colour = "none")

plot1 <- uds.sites[!is.na(uds.sites$Zip),] %>% 
            group_by(Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
  ungroup() %>% 
  group_by(Year, Counts) %>% 
  summarise(Zips = n()) %>% 
  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
  group_by(Counts.f, Year) %>% 
  summarise(Zips = sum(Zips)) %>% 
  ggplot(aes(x = Year, y = Zips, group = Counts.f, color = Counts.f)) + 
  geom_point() + geom_line() + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
  geom_dl(label=c(rep("1 Site", 8), rep("2+ Sites", 8)), method = list("last.points", hjust = 1, vjust = -0.5, cex = 0.75), inherit.aes=T ) + 
  guides(colour = "none")

p.desc <- ggarrange(plot1, plot0)

annotate_figure(p.desc, top = text_grob("Figure 2 - FQHC Growth and Density by Zip and Clinic", face = "bold", size = 14))

# rbind(uds.sites %>% 
#   group_by(`Grant Number`, `Site Name`) %>% 
#   summarise(Year = min(Year)) %>% 
#   group_by(Year) %>% 
#   summarise(Counts = n()) %>% 
#   mutate(Type = "Opened"), 
#   uds.sites %>% 
#   group_by(`Grant Number`, `Site Name`) %>% 
#   summarise(Year = max(Year)) %>% 
#   group_by(Year) %>% 
#   summarise(Counts = n()) %>% 
#   mutate(Type = "Closed")) %>% 
#   filter(Year %in% c(2015:2019))

```

```{r}

# df.z %>% 
#   group_by(as.factor(Att), Year) %>% 
#   summarise(outcome = mean(Total.z, na.rm = TRUE)) %>% 
#   ggplot(aes(x = Year, y = outcome, color = `as.factor(Att)`)) + geom_point()

# 
# cs.output.expand <- att_gt( yname = "Total.z",
#                       tname = "Year",
#                       idname = "ID",
#                       gname = "Att",
#                       xformla = ~1,
#                       data = df.z, # %>%  group_by(`Grant Number`, Year, Att) %>% summarise(Zips = n(), ID = min(ID), Total.z = sum(Total.z, na.rm = TRUE) ), # %>% filter(Year > 2015),
#                       control_group = "nevertreated",
#                       clustervars = "ID",
#                       panel = FALSE,
#                       base_period = "universal"
#                       )
# aggte(cs.output.expand, type = "simple", na.rm = TRUE)
# 
# 
# cs.output.expand <- att_gt( yname = "Total.z",
#                       tname = "Year",
#                       idname = "ID",
#                       gname = "Att.z",
#                       xformla = ~1,
#                       data = df.z %>% group_by(`Grant Number`, Year, Att, Att.z) %>% summarise(Zips = n(), ID = min(ID), Total.z = sum(Total.z, na.rm = TRUE) ) %>% filter(Att == Att.z), # %>% filter(Year > 2015),
#                       control_group = "nevertreated",
#                       clustervars = "ID",
#                       panel = FALSE,
#                       base_period = "universal"
#                       )
# aggte(cs.output.expand, type = "simple", na.rm = TRUE)
# 
# #uds.zip %>% filter(`Grant Number` == "H80CS00030" & `Zip Code` == '48264')

```

## Figure 2 - Focused analysis, patient attribution in service area (where they have sites)
```{r}

## Treatment vs control, only in zip code of interest
df.z <- left_join(df.qual.exp #%>% filter(`Grant Number` != "H80CS00225")
                  , #uds.zip %>% mutate(Zip = `Zip Code`) %>% select(`Grant Number`, Zip) %>% unique() , by = c("Grant Number")) %>%
                  uds.sites[!is.na(uds.sites$Zip),] %>%
                    filter(Year %in% c(2015:2019)) %>% 
              select(`Grant Number`, Zip) %>%
              unique() , by = c("Grant Number")) %>%
  left_join(uds.zip %>%
            mutate(  Total.z = `Total Number of Patients`, 
                     MCD.z = `Medicaid_CHIP_Other Public Patients`,
                     MCR.z = `Medicare Patients`,
                     COM.z = `Private Patients`, 
                     None.z = `None_Uninsured Patients`) %>%
            select(`Grant Number`, `Reporting Year`, `Zip Code`, Total.z:None.z), by = c("Grant Number", "Year" = "Reporting Year", "Zip" = "Zip Code")) %>%
  left_join(clinics.in.zips %>% select(Zip:Clinics), by = c("Zip","Year")) %>%
  mutate(Tx.z = ifelse(Clinics == 1 , 0, 
                ifelse(is.na(Clinics), NA, 1)), # | is.na(Clinics)
         ID = as.numeric(factor(paste(`Grant Number`, Zip, sep = "-")))) %>%
  select(`Grant Number`:Year, ZipFilter, Att, ID, Zip:Tx.z) %>%
  arrange(`Grant Number`, Zip, Year) %>% 
  unique() #%>%  inner_join(df.qual.exp %>% filter(Year == 2015 & Total > 12050) %>% select(`Grant Number`), by = c("Grant Number"))  #& Zips < 3.75 or 4.75
  # %>%   filter(MarketShare > median(MarketShare, na.rm = TRUE) - 0.25)

df.z <- df.z %>%
  left_join(df.z %>%
            filter(Tx.z == 1) %>%
            group_by(ID, Zip) %>%
            summarise(Att.z = min(Year)), by = c("ID", "Zip")) %>%
  mutate(Att.z = ifelse(is.na(Att.z), 0, Att.z)) #%>%
# inner_join(df.z %>% filter(!is.na(Clinics)) %>% group_by(ID) %>% summarise(n()) %>% filter(`n()` == length(unique(df.qual.exp$Year))), by = c("ID")) #%>% filter(Att == Att.z)

### NOTE: The aabove commented lines are very important, they decide if only the service area or whole catchment is included in analysis.  
# cs.output.expand <- att_gt( yname = "Outcome",
#                       tname = "Year",
#                       idname = "ID",
#                       gname = "Att",
#                       xformla = ~1,
#                       data = df.z %>% group_by(`Grant Number`, Year, Att) %>% summarise(ID = min(ID), Outcome = sum(MCD.z, na.rm = TRUE) ), # %>% filter(Year > 2015),
#                       control_group = "nevertreated",
#                       clustervars = "ID",
#                       panel = TRUE,
#                       base_period = "universal"
#                       )
# aggte(cs.output.expand, type = "simple", na.rm = TRUE)

## Whole zip as one measure

df.z.full <- df.z %>% ############## NOTE: Original +500 effect was recoved with Att.z, not Att
  select(Zip, ZipFilter, Att.z, Year) %>% 
  unique() %>% 
  left_join(uds.zip, by = c("Zip" = "Zip Code", "Year" = "Reporting Year")) %>% 
  left_join(uds.6b.rates %>% 
            mutate(Quality = (IMM2yo + Pap + ChildBMI + AdultBMI + Tobac + CRC + DepScrn) / 7) %>% 
            select(GrantNumber, Year, Quality), by = c("Grant Number" = "GrantNumber", "Year")) %>% 
  group_by(Zip, ZipFilter, Year, Att.z) %>% 
  summarise(
    Total.z = sum(`Total Number of Patients`, na.rm = TRUE), 
    MCD.z = sum(`Medicaid_CHIP_Other Public Patients`, na.rm = TRUE),
    MCR.z = sum(`Medicare Patients`, na.rm = TRUE),
    COM.z = sum(`Private Patients`, na.rm = TRUE),
    None.z = sum(`None_Uninsured Patients`, na.rm = TRUE), 
    Quality.z = sum(`Total Number of Patients` * Quality, na.rm = TRUE) / Total.z) %>% 
  ungroup() %>% 
  mutate(ID = as.numeric(as.factor(Zip)))# %>% group_by(`Grant Number`, Year, Att) %>% summarise(ID = min(ID), Total.z = sum(Total.z, na.rm = TRUE)) # %>% filter(Year > 2015),

df.zip.1 <- df.z %>% select(ID, ZipFilter, Year, Att, Total.z:None.z)
df.zip.2 <- df.z.full %>% select(ID, ZipFilter, Year, Att.z, Total.z:Quality.z)

## Start the loop

for (k in 1:3){

atts.zip.1 <- rep(0, 6)
atts.zip.2 <- rep(0, 6)

if (k == 1){temp.1.root <- df.zip.1
            temp.2.root <- df.zip.2} else 
  if (k == 2){temp.1.root <- df.zip.1 %>% filter(ZipFilter == 2)
              temp.2.root <- df.zip.2 %>% filter(ZipFilter == 2)} else
    if (k == 3){temp.1.root <- df.zip.1 %>% filter(ZipFilter == 1)
                temp.2.root <- df.zip.2 %>% filter(ZipFilter == 1)}

for (i in 5:9){

  temp.1 <- temp.1.root[,c(1:4, i)]
  colnames(temp.1) <- c("ID", "ZipFilter", "Year","Att","Outcome")

   temp.2 <- temp.2.root[,c(1:4, i)]
  colnames(temp.2) <- c("ID", "ZipFilter", "Year","Att","Outcome")

    # Incumbent only
cs.output.expand <- att_gt( yname = "Outcome",
                      tname = "Year",
                      idname = "ID",
                      gname = "Att",
                      xformla = ~1,
                      data = temp.1,
                      control_group = "nevertreated",
                      clustervars = "ID",
                      panel = FALSE,
                      base_period = "universal"
                      )

cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)

data.frame(Year = cs.output.expand.agg.dyn$egt,
           Estimate = cs.output.expand.agg.dyn$att.egt,
           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt) %>%
  ggplot(mapping = aes(x = Year, y = Estimate)) +
  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") +
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") +
  geom_point() +
  geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) +
  ggtitle("Total Zip") +
  theme_tufte_revised()

atts.zip.1 <- rbind(atts.zip.1, 
                    cbind(colnames(df.zip.1)[i], 
                          round(mean(temp.1[temp.1$Att == 0 & temp.1$Year == min(temp.1$Year),]$Outcome, na.rm = TRUE), 3), 
                          round(mean(temp.1[temp.1$Att > 0 & temp.1$Year == min(temp.1$Year),]$Outcome, na.rm = TRUE) - mean(temp.1[temp.1$Att == 0 & temp.1$Year == min(temp.1$Year),]$Outcome, na.rm = TRUE), 3), 
                          round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
                          cs.output.expand.agg.dyn.0$overall.att - (1.96 * cs.output.expand.agg.dyn.0$overall.se), 
                          cs.output.expand.agg.dyn.0$overall.att + (1.96 * cs.output.expand.agg.dyn.0$overall.se)), 3)))

# Incumbent + Competitor
cs.output.expand <- att_gt( yname = "Outcome",
                      tname = "Year",
                      idname = "ID",
                      gname = "Att",
                      xformla = ~1,
                      data = temp.2, 
                      control_group = "nevertreated",
                      clustervars = "ID",
                      panel = FALSE,
                      base_period = "universal"
                      )

cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)

data.frame(Year = cs.output.expand.agg.dyn$egt,
           Estimate = cs.output.expand.agg.dyn$att.egt,
           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt) %>%
  ggplot(mapping = aes(x = Year, y = Estimate)) +
  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") +
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") +
  geom_point() +
  geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) +
  ggtitle("Total Zip") +
  theme_tufte_revised()

atts.zip.2 <- rbind(atts.zip.2, cbind(colnames(df.zip.2)[i], 
                                      round(mean(temp.2[temp.2$Att == 0 & temp.2$Year == min(temp.2$Year),]$Outcome, na.rm = TRUE), 3), 
                                      round(mean(temp.2[temp.2$Att > 0 & temp.2$Year == min(temp.2$Year),]$Outcome, na.rm = TRUE) - mean(temp.2[temp.2$Att == 0 & temp.2$Year == min(temp.2$Year),]$Outcome, na.rm = TRUE), 3), 
                                      round(cbind(cs.output.expand.agg.dyn.0$overall.att,
      cs.output.expand.agg.dyn.0$overall.att - (1.96 * cs.output.expand.agg.dyn.0$overall.se),
      cs.output.expand.agg.dyn.0$overall.att + (1.96 * cs.output.expand.agg.dyn.0$overall.se)), 3)))

}

## For the full sample only

## For Larger vs Smaller FQHCs only
if (k == 1){atts.zip.full <-  cbind(atts.zip.1[-1,], atts.zip.2[-1,]) } else 
  if (k == 2){atts.zip.larger <- cbind(atts.zip.1[-1,], atts.zip.2[-1,])} else
    if (k == 3){atts.zip.smaller <- cbind(atts.zip.1[-1,], atts.zip.2[-1,])}

}

df.zip.1 %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n(), n_distinct(ID))
df.zip.2 %>% mutate(Treat = ifelse(Att.z > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n(), n_distinct(ID))

table.names <- rbind(cbind((df.zip.1 %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[2,2], 
            (df.zip.1 %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[1,2]), 
      cbind((df.zip.2 %>% mutate(Treat = ifelse(Att.z > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[2,2], 
            (df.zip.2 %>% mutate(Treat = ifelse(Att.z > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[1,2]))

## Figure 2 - Full Figure
rbind(atts.zip.full, atts.zip.larger, atts.zip.smaller) %>% 
   kable("html", booktabs = T, col.names = c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB", "Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB")) %>%
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Full Sample" = 5, "More Market Share Only" = 5, "Less Market Share Only" = 5)) %>% 
  add_header_above(c(" " = 1, "Incumbent vs Controls (FQHC-Zip units)" = 6, "Incumbent & Competitor vs Controls (zip units)" = 6)) %>% 
  add_footnote(c("C_0 and T_0 are mean values for each sample in control and treatment groups in first year of panel",
                 paste("Full Sample Incumbent vs Control has ", table.names[1,1], "treatment and ", table.names[1,2], " control FQHC-Zip-Years"), 
                 paste("Full Sample Incumbent & Control vs Control has ", table.names[2,1], "treatment and ", table.names[2,2], " control Zip-Years")))

cbind(rep(c("Total","Medicaid","Medicare","Commerical","Uninsured"), 3), rbind(atts.zip.full, atts.zip.larger, atts.zip.smaller)[,2:6]) %>% 
   kable("html", booktabs = T, col.names = c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB")) %>%
  kable_styling(latex_options = c("striped")) %>%
  row_spec(c(1, 2, 6, 7, 10, 11, 12),bold=T, italic = T, hline_after = T) %>% 
  pack_rows(index = c("Panel A: Full Sample" = 5, "Panel B: Higher Low-Income Market Share Subgroup" = 5, "Panel B: Lower Low-Income Market Share Subgroup" = 5)) %>% 
  add_footnote(c("C_0 and T_0 are mean values for each sample in control and treatment groups in first year of panel",
                 paste("Full Sample Incumbent vs Control has ", table.names[1,1], "treatment and ", table.names[1,2], " control FQHC-Zip-Years"), 
                 paste("Full Sample Incumbent & Control vs Control has ", table.names[2,1], "treatment and ", table.names[2,2], " control Zip-Years")))

```

## Nicer Table

```{r}
df.zip.1 %>% 
  filter(Year %in% c(2016, 2019)) %>% 
  mutate(Tx = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Year, Tx) %>% 
  summarise(mean(Total.z, na.rm = TRUE), 
            mean(MCD.z, na.rm = TRUE), 
            mean(MCR.z, na.rm = TRUE), 
            mean(COM.z, na.rm = TRUE), 
            mean(None.z, na.rm = TRUE)) %>% 
  arrange(Tx, Year) %>% 
  t() %>% 
  as.data.frame() %>% 
  mutate(unadj = (V4 - V3) - (V2 - V1) )

cbind(c("Total","Medicaid","Medicare","Commerical","Uninsured"), atts.zip.full[,2:6]) %>% 
   kable("html", booktabs = T, col.names = c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB")) %>%
  kable_styling(latex_options = c("striped")) %>%
  row_spec(c(1, 2),bold=T, italic = T, hline_after = T) %>% 
  #pack_rows(index = c("Panel A: Full Sample" = 5, "Panel B: Higher Low-Income Market Share Subgroup" = 5, "Panel B: Lower Low-Income Market Share Subgroup" = 5)) %>% 
  add_footnote(c("C_0 and T_0 are mean values for each sample in control and treatment groups in first year of panel",
                 paste("Full Sample Incumbent vs Control has ", table.names[1,1], "treatment and ", table.names[1,2], " control FQHC-Zip-Years"), 
                 paste("Full Sample Incumbent & Control vs Control has ", table.names[2,1], "treatment and ", table.names[2,2], " control Zip-Years")))
```

## Look at the Market as a whole

```{r}

df.market <- df.z.full %>% #filter(ZipFilter == 1)
                        left_join(df.z %>% select(`Grant Number`,Zip) %>% unique(), by = c("Zip")) %>% 
  mutate(V1 = 1, V2 = ifelse(ZipFilter == 2, 1, 0), V3 = ifelse(ZipFilter == 1, 1, 0)) %>% 
                       select(Year, ID, Att.z, Quality.z, `Grant Number`, Total.z:None.z, V1:V3) %>%
  # inner_join(df.qual.exp %>% filter(Year == 2015) %>%
  #                                           mutate(ZipFilter = ifelse(Total < 12000, 1,
  #                                                              ifelse(Total > 12000, 2, NA))) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
  inner_join(df.qual.exp %>% filter(Year == 2016) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>% 
  select(Year, ZipFilter, ID, Att.z, Quality.z, Total.z:None.z, V1:V3) %>% 
  mutate(V4 = ifelse(ZipFilter == 2, 1, 0), V5 = ifelse(ZipFilter == 1, 1, 0)) %>% 
  unique()

### Incumbnet + Competitors, Quality 
cs.output.expand <- att_gt( yname = "Quality.z",
                      tname = "Year",
                      idname = "ID",
                      gname = "Att.z",
                      xformla = ~1,
                      data = df.market %>% filter(V5 == 1), 
                      control_group = "nevertreated",
                      clustervars = "ID",
                      panel = TRUE,
                      base_period = "universal"
                      )

cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)

data.frame(Year = cs.output.expand.agg.dyn$egt,
           Estimate = cs.output.expand.agg.dyn$att.egt,
           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt) %>%
  ggplot(mapping = aes(x = Year, y = Estimate)) +
  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") +
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") +
  geom_point() +
  geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) +
  ggtitle("Total Change in Market Quality") +
  theme_tufte_revised()

```

## Figure 2 plots that are nicer
```{r}

## Plot of this shit, all payors
f2.picture.full <- rbind(rbind(atts.zip.full, atts.zip.larger, atts.zip.smaller)[,c(1:6)]) %>%  #, rbind(atts.zip.full, atts.zip.larger, atts.zip.smaller)[,c(7:12)]) %>% 
  as.data.frame() %>% 
  mutate(Model = c(rep("Incumbent Only", 3*5)), #, rep("Incumbent & Competitor", 3*5)), 
         Sample = rep(c(rep("Full Sample", 5), rep("More Market Share", 5), rep("Less Market Share", 5)), 1))

#### Clean up the data
row.names(f2.picture.full) <- NULL
colnames(f2.picture.full) <- c("Payor", "C_0", "T_0 - C_0", "Estimate", "LB", "UB", "Model","Sample")
f2.picture.full[,4:6] <- sapply(f2.picture.full[,4:6], as.numeric)
f2.picture.full$Sample <- factor(f2.picture.full$Sample, levels = c("Full Sample", "More Market Share","Less Market Share"))
f2.picture.full$Payor <- gsub(f2.picture.full$Payor, pattern = ".z", replacement = "")
f2.picture.full$Payor <- factor(f2.picture.full$Payor, levels = c("None", "MCR","COM","MCD","Total"))
f2.picture.full$Model <- factor(f2.picture.full$Model, levels = c("Incumbent Only","Incumbent & Competitor"))
f2.picture.full$Total <- ifelse(f2.picture.full$Payor == "Total", "Total", "Payor")
f2.picture.full$Total <- factor(f2.picture.full$Total, levels = c("Total","Payor"))

### Plot
f2.p.totals.inc <- ggplot(data=f2.picture.full #%>% filter(Sample == "Full Sample")
                          , aes(y=Payor, x=Estimate, xmin=LB, xmax=UB)) +
geom_point() +

#this changes the features of the overall effects
#one could resize, reshape, or recolor these points if desired
xlab("DID Estimates - Patients") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(Total~Sample, scales= "free_y", switch = 'y', space = "free_y")+

#thematic stuff
#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) +
  ggtitle("Figure 3, CS-DID Estimates on Patient Panel and Payor (FQHC-zip-year units)")

f2.p.totals.inc #+ theme(panel.spacing = unit(1, "lines"),  title =  element_text(face = "bold", size = 12))

```

## Figure 3 - Primary Results

```{r}

df.sum <- df.qual.exp %>% #filter(`Grant Number` != "H80CS00225") %>%

  ungroup() %>% 
  #filter(MarketShare < median(MarketShare, na.rm = TRUE) - 0.25) %>% 
  #inner_join(df.qual.exp %>% filter(Year == 2015 & Total < 12000) %>% select(`Grant Number`), by = c("Grant Number")) %>%  #& Zips < 3.75 or 4.75
  # select(`Grant Number`, Year, ID, Att, Sites, Qcomp, Altmans.Z) %>%
  # inner_join(df.qual.exp %>% filter(Year == 2015) %>% mutate(ZipFilter = ifelse(Zips < 1.75, 1, 
  #                                                                        ifelse(Zips > 4.75, 2, NA))) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
  select(Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z)

for (k in 1:3){

atts.sum <- rep(0, 7)
fig3.sum <- rep(0, 5)

if (k ==1){df.sum.root <- df.sum} else
  if (k == 2){df.sum.root <- df.sum %>% filter(ZipFilter == 2)} else
    if (k == 3){df.sum.root <- df.sum %>% filter(ZipFilter == 1)}

for (i in 5:ncol(df.sum)){

  temp <- df.sum.root[,c(1:4, i)]
  colnames(temp) <- c("Year", "ZipFilter", "ID","Att", "Outcome")
  temp$Outcome

  # temp <- temp %>%
  #   mutate(Outcome = ifelse(Outcome < quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1],
  #                    ifelse(Outcome > quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], Outcome)))

cs.output.expand <- att_gt( yname = "Outcome",
                      tname = "Year",
                      idname = "ID",
                      gname = "Att",
                      xformla = ~1,
                      data = temp, # %>% filter(Year >= 2015 & Year <= 2020), 
                      control_group = "nevertreated",
                      clustervars = "ID",
                      panel = FALSE, 
                      base_period = "universal"
                      )
cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)

atts.sum <- rbind(atts.sum, cbind(colnames(df.sum)[i], round(mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(mean(temp[temp$Att > 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE) - mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se), 3)))

atts <- rbind(atts, cbind(colnames(df.sum)[i], round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
      cs.output.expand.agg.dyn$overall.att, 
      cs.output.expand.agg.dyn$overall.att - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se, 
      cs.output.expand.agg.dyn$overall.att + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se), 3)))
z <- rbind(z, c(colnames(df.sum)[i], cs.output.expand$Wpval))

fig3.sum <- rbind(fig3.sum, 
                 data.frame(Outcome = colnames(df.sum)[i], 
                      Year = cs.output.expand.agg.dyn$egt, 
           Estimate = cs.output.expand.agg.dyn$att.egt, 
           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt))
}

rownames(fig3.sum) <- NULL
if (k == 1){atts.sum.full <- atts.sum[-1,]} else 
 if (k == 2){atts.sum.larger <- atts.sum[-1,]} else 
   {atts.sum.smaller <- atts.sum[-1,]}

}

#Event Study Plots
fig3.sum[-1,] %>%
  ggplot(mapping = aes(x = Year, y = Estimate)) +
  facet_wrap(~Outcome, scales = "free_y") +
  ylab("Percentage Points") +
  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") +
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") +
  geom_point() + geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) +
  ggtitle("fig3 - Event Study") +
  theme_tufte_revised()

table.names <- rbind(cbind((df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[2,2], 
            (df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[1,2]), 
      cbind((df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[4,3], 
            (df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[3,3]), 
      cbind((df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[2,3], 
            (df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[1,3]))

## Table
rbind(atts.sum.full, atts.sum.larger, atts.sum.smaller) %>% 
   kable("html", booktabs = T, col.names = c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB"), caption = "Fig 3 - FQHC Responses by Market Share") %>%
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Full" = 3, "Above Median Market Share FQHCs" = 3, "Below Median Market Share FQHCs" = 3)) %>% 
  add_footnote(c("Atlman's Z is a measure of Financial Distress",
                 "C_0 and T_0 are mean values for each sample in control and treatment groups in first year of panel",
                 paste("Full Sample has ", table.names[1,1], "treatment and ", table.names[1,2], " control FQHC-Years")))

## Better Figure
f3.picture.full <- rbind(cbind("Full Sample", atts.sum.full), cbind("More Market Share", atts.sum.larger), cbind("Less Market Share", atts.sum.smaller) ) %>% 
  as.data.frame()

### Clean up the data
row.names(f3.picture.full) <- NULL
colnames(f3.picture.full) <- c("MarketShare", "Measure", "C_0", "T_0 - C_0", "Estimate", "LB", "UB")
f3.picture.full[,3:7] <- sapply(f3.picture.full[,3:7], as.numeric)
f3.picture.full$MarketShare <- factor(f3.picture.full$MarketShare, levels = c("Full Sample", "More Market Share","Less Market Share"))
# f3.picture.full$Payor <- gsub(f3.picture.full$Payor, pattern = ".z", replacement = "")
# f3.picture.full$Payor <- factor(f3.picture.full$Payor, levels = c("None", "MCR","COM","MCD","Total"))
# f3.picture.full$Model <- factor(f3.picture.full$Model, levels = c("Incumbent Only","Incumbent & Competitor"))
# f3.picture.full$Total <- ifelse(f3.picture.full$Payor == "Total", "Total", "Payor")
# f3.picture.full$Total <- factor(f3.picture.full$Total, levels = c("Total","Payor"))

### Plot
f3.p.totals.full <- ggplot(data=f3.picture.full, aes(y=Measure, x=Estimate, xmin=LB, xmax=UB)) +
geom_point() +

#this changes the features of the overall effects
#one could resize, reshape, or recolor these points if desired
xlab("DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~MarketShare, scales= "free", switch = 'y', space = "free_y")+

#thematic stuff
#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) +
  ggtitle("Figure 3, FQHC Performance Reactions by Market Share")

f3.p.totals.full

```

## Figure 4 - Split by profitability
```{r}

df.sum <- df.qual.exp %>% #filter(`Grant Number` != "H80CS00225") %>% 
  ungroup() %>% 
  #rename(`Grant Number` = Grant.Number, `Surplus as a pct of before dep expenses` = Surplus.as.a.pct.of.after.dep.expenses) %>% 
  #filter(MarketShare < 0.4) %>%  #median(MarketShare, na.rm = TRUE) - 0.25
  #inner_join(df.qual.exp %>% filter(Year == 2015 & Total < 15000) %>% select(`Grant Number`), by = c("Grant Number")) %>%  #& Zips < 1.75 or 7.75
  select(`Grant Number`, Year, ID, Att, Sites, Qcomp, Altmans.Z) %>%
  # inner_join(df.qual.exp %>% filter(Year == 2015) %>%
  #                                           mutate(ZipFilter = ifelse(Total < 12000, 1,
  #                                                              ifelse(Total > 12000, 2, NA))) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
  inner_join(df.qual.exp %>% filter(Year == 2016) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>% 
  select(Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z) %>% 
  unique()

#summary(df.qual.exp[df.qual.exp$Year == 2015,]$Qcomp)

for (k in 2:3){

atts.sum <- rep(0, 7)
fig4.sum <- rep(0, 5)

if (k ==1){df.sum.root <- df.sum} else
  if (k == 2){df.sum.root <- df.sum %>% filter(ZipFilter == 2)} else
    if (k == 3){df.sum.root <- df.sum %>% filter(ZipFilter == 1)}

for (i in 5:ncol(df.sum)){

  temp <- df.sum.root[,c(1:4, i)]
  colnames(temp) <- c("Year", "ZipFilter", "ID","Att", "Outcome")
  temp$Outcome

  # temp <- temp %>%
  #   mutate(Outcome = ifelse(Outcome < quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1],
  #                    ifelse(Outcome > quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], Outcome)))

cs.output.expand <- att_gt( yname = "Outcome",
                      tname = "Year",
                      idname = "ID",
                      gname = "Att",
                      xformla = ~1,
                      data = temp , 
                      control_group = "nevertreated",
                      clustervars = "ID",
                      panel = FALSE, 
                      base_period = "universal"
                      )
cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)

atts.sum <- rbind(atts.sum, cbind(colnames(df.sum)[i], round(mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(mean(temp[temp$Att > 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE) - mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se), 3)))

atts <- rbind(atts, cbind(colnames(df.sum)[i], round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
      cs.output.expand.agg.dyn$overall.att, 
      cs.output.expand.agg.dyn$overall.att - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se, 
      cs.output.expand.agg.dyn$overall.att + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se), 3)))
z <- rbind(z, c(colnames(df.sum)[i], cs.output.expand$Wpval))

fig4.sum <- rbind(fig4.sum, 
                 data.frame(Outcome = colnames(df.sum)[i], 
                      Year = cs.output.expand.agg.dyn$egt, 
           Estimate = cs.output.expand.agg.dyn$att.egt, 
           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt))
}

rownames(fig4.sum) <- NULL
if (k == 1){atts.sum.full <- atts.sum[-1,]} else 
 if (k == 2){atts.sum.larger <- atts.sum[-1,]} else 
   {atts.sum.smaller <- atts.sum[-1,]}

}

#Event Study Plots
fig4.sum[-1,] %>%
  ggplot(mapping = aes(x = Year, y = Estimate)) +
  facet_wrap(~Outcome, scales = "free_y") +
  ylab("Percentage Points") +
  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") +
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") +
  geom_point() + geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) +
  ggtitle("fig4 - Event Study") +
  theme_tufte_revised()

table.names <- rbind(cbind((df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[2,2], 
            (df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[1,2]), 
      cbind((df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[4,3], 
            (df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[3,3]), 
      cbind((df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[2,3], 
            (df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[1,3]))

## Table
rbind(atts.sum.larger, atts.sum.smaller) %>% 
   kable("html", booktabs = T, col.names = c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB")) %>%
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Profitable FQHCs" = 3, "Unprofitable/Budget Neutral FQHCs" = 3)) %>% 
  add_footnote(c("Atlman's Z is a measure of Financial Distress",
                 "C_0 and T_0 are mean values for each sample in control and treatment groups in first year of panel",
                 paste("Profitable FQHCs Sample has ", table.names[2,1], "treatment and ", table.names[2,2], " control FQHC-Years"), 
                 paste("Unprofitable and Budget Neutral FQHCs Sample has ", table.names[3,1], "treatment and ", table.names[3,2], " control FQHC-Years")))

## Better Figure
f4.picture.full <- rbind(cbind("Full Sample", atts.sum.full), cbind("Profitable", atts.sum.larger), cbind("Unprofitable/Budget Neutral", atts.sum.smaller) ) %>% 
  as.data.frame()

### Clean up the data
row.names(f4.picture.full) <- NULL
colnames(f4.picture.full) <- c("Profitability", "Measure", "C_0", "T_0 - C_0", "Estimate", "LB", "UB")
f4.picture.full[,3:7] <- sapply(f4.picture.full[,3:7], as.numeric)
# f4.picture.full$Sample <- factor(f4.picture.full$Sample, levels = c("Full Sample", "More Market Share","Less Market Share"))
# f4.picture.full$Payor <- gsub(f4.picture.full$Payor, pattern = ".z", replacement = "")
# f4.picture.full$Payor <- factor(f4.picture.full$Payor, levels = c("None", "MCR","COM","MCD","Total"))
# f4.picture.full$Model <- factor(f4.picture.full$Model, levels = c("Incumbent Only","Incumbent & Competitor"))
# f4.picture.full$Total <- ifelse(f4.picture.full$Payor == "Total", "Total", "Payor")
# f4.picture.full$Total <- factor(f4.picture.full$Total, levels = c("Total","Payor"))

### Plot
f4.p.totals.full <- ggplot(data=f4.picture.full, aes(y=Measure, x=Estimate, xmin=LB, xmax=UB)) +
geom_point() +

#this changes the features of the overall effects
#one could resize, reshape, or recolor these points if desired
xlab("DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Profitability, scales= "free", switch = 'y', space = "free_y")+

#thematic stuff
#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) +
  ggtitle("Figure 4, FQHC Performance Reactions by Profitability")

f4.p.totals.full
```

## True Figure 3 - Responses
```{r}

fig3 <- rbind(f3.picture.full %>% rename(Subgroup = MarketShare), f4.picture.full[-c(1:3),] %>% rename(Subgroup = Profitability)) %>% 
  mutate(Measure = ifelse(Measure == "Sites", "Number of Sites", 
                   ifelse(Measure == "Qcomp", "Quality of Care", 
                   ifelse(Measure == "Altmans.Z", "Financial Stability", NA))))

f3.full <- ggplot(data=fig3[1:3,], aes(y=Measure, x=Estimate, xmin=LB, xmax=UB)) +
  geom_point() +

#this changes the features of the overall effects
#one could resize, reshape, or recolor these points if desired
xlab("DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Subgroup, scales= "free", switch = 'y', space = "free_y")+

#thematic stuff
#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines"))

f3.mark <- ggplot(data=fig3[4:9,], aes(y=Measure, x=Estimate, xmin=LB, xmax=UB)) +
  geom_point() +

#this changes the features of the overall effects
#one could resize, reshape, or recolor these points if desired
xlab("DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Subgroup, scales= "free", switch = 'y', space = "free_y")+

#thematic stuff
#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines"))

f3.prof <- ggplot(data=fig3[10:15,], aes(y=Measure, x=Estimate, xmin=LB, xmax=UB)) +
  geom_point() +

#this changes the features of the overall effects
#one could resize, reshape, or recolor these points if desired
xlab("DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Subgroup, scales= "free", switch = 'y', space = "free_y")+

#thematic stuff
#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines"))

gt <- grid.arrange(f3.full,                            
             f3.mark, f3.prof,                         
             ncol = 3, nrow = 2, 
             layout_matrix = rbind(c(1,  2, 2), c(1,  3, 3)))

# Add labels to the arranged plots
p <- as_ggplot(gt) +                                # transform to a ggplot
 draw_plot_label(label = c("Panel A", "Panel B", "Panel C"), size = 15,
                 x = c(0, 0.33, 0.33), y = c(1, 1, 0.5)) # Add labels
p

```

## Figure for Paper

```{r}
df.qual.exp %>% 
  filter(Year %in% c(2016, 2019)) %>% 
  mutate(Tx = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Year, Tx) %>% 
  summarise(mean(Sites, na.rm = TRUE), 
            mean(Qcomp, na.rm = TRUE), 
            mean(Altmans.Z, na.rm = TRUE), 
            mean(Efficiency, na.rm = TRUE)) %>% 
  arrange(Tx, Year) %>% 
  t() %>% 
  as.data.frame() %>% 
  mutate(unadj = (V4 - V3) - (V2 - V1) )
```

## Figure for Poster

```{r}

poster.fig3 <- cbind(Group = c(rep("Panel A", 3),rep("Panel B", 6),rep("Panel C", 6)), fig3) %>% 
  mutate(Measure = as.factor(Measure)) %>% 
  mutate(Measure = fct_reorder(Measure, desc(Measure))) %>%

ggplot(aes(y=Subgroup, x=Estimate, xmin=LB, xmax=UB)) +
geom_point() +

#this changes the features of the overall effects
#one could resize, reshape, or recolor these points if desired
xlab("DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(Group~Measure, scales = "free", switch = 'y', space = "free_y")+

#thematic stuff
#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines"),  strip.text =  element_text(face = "bold", size = 16))

poster.fig3
```

## Figure 5 - Financing

```{r}

df.comp <- df.qual.exp %>% #filter(`Grant Number` != "H80CS00225") %>% 
  ungroup() %>% 
  #inner_join(df.qual.exp %>% filter(Year == 2015 & Zips < 4.75) %>% select(`Grant Number`), by = c("Grant Number")) %>%  #& Zips < 3.75 or 4.75
  #filter(MarketShare > median(MarketShare, na.rm = TRUE)) %>% 
    select(Year, ZipFilter, ID, Att, `Total revenue (unrestricted & restricted)`, `Total net assets`, `Surplus as a pct of before dep expenses`, 
           `Staffing`, `Liabilities`, `Gross land, buildings and equipment (LBE)`, Liquidity, Profitability, Efficiency, NetWorth)

for (k in 1:3){

atts.comp <- rep(0, 7)
fig3.comp <- rep(0, 5)

if (k ==1){df.comp.root <- df.comp} else
  if (k == 2){df.comp.root <- df.comp %>% filter(ZipFilter == 2)} else
    if (k == 3){df.comp.root <- df.comp %>% filter(ZipFilter == 1)}

for (i in 5:ncol(df.comp)){

 # if (i %in% c(6, 7, 19)){temp <- df.comp.root[df.comp.root$Year %in% c(2015:2019), c(1:4, i)]} else {temp <- df.comp.root[,c(1:4, i)]}
  temp <- df.comp.root[,c(1:4, i)]
  #temp <- df.comp.root[df.comp.root$Year %in% c(2015:2019), c(1:4, i)]
  colnames(temp) <- c("Year", "ZipFilter", "ID","Att", "Outcome")
  temp$Outcome

  # temp <- temp %>%
  #   mutate(Outcome = ifelse(Outcome < quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1],
  #                    ifelse(Outcome > quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], Outcome)))

cs.output.expand <- att_gt( yname = "Outcome",
                      tname = "Year",
                      idname = "ID",
                      gname = "Att",
                      xformla = ~1,
                      data = temp, # %>% filter(Year >= 2016), 
                      control_group = "nevertreated",
                      clustervars = "ID",
                      panel = FALSE, 
                      base_period = "universal"
                      )
cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)

atts.comp <- rbind(atts.comp, cbind(colnames(df.comp)[i], round(mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(mean(temp[temp$Att > 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE) - mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se), 3)))

atts <- rbind(atts, cbind(colnames(df.comp)[i], round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
      cs.output.expand.agg.dyn$overall.att, 
      cs.output.expand.agg.dyn$overall.att - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se, 
      cs.output.expand.agg.dyn$overall.att + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se), 3)))
z <- rbind(z, c(colnames(df.comp)[i], cs.output.expand$Wpval))

fig3.comp <- rbind(fig3.comp, 
                 data.frame(Outcome = colnames(df.comp)[i], 
                      Year = cs.output.expand.agg.dyn$egt, 
           Estimate = cs.output.expand.agg.dyn$att.egt, 
           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt))
}

rownames(fig3.comp) <- NULL
if (k == 1){atts.comp.full <- atts.comp[-1,]} else 
 if (k == 2){atts.comp.larger <- atts.comp[-1,]} else 
   {atts.comp.smaller <- atts.comp[-1,]}

}

#Event Study Plots
fig3.comp[-1,] %>%
  ggplot(mapping = aes(x = Year, y = Estimate)) +
  facet_wrap(~Outcome, scales = "free_y") +
  ylab("Percentage Points") +
  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") +
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") +
  geom_point() + geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) +
  ggtitle("fig3 - Event Study") +
  theme_tufte_revised()

 cbind(atts.comp.full, atts.comp.larger, atts.comp.smaller) %>% 
   kable("html", booktabs = T, col.names = rep(c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB"), 3)) %>%
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Financial" = 5, "" = 5, "Profitability" = 5)) %>% 
  add_header_above(c(" " = 1, "Full" = 6, "More Market Share Clinics" = 6, "Less Market Share Clinics" = 6)) %>% 
  #pack_rows(index = c("Larger FQHCs" = 15, "Smaller FQHCs" = 15)) %>% 
  add_footnote(c(""))

```

## Figure 5 - Financing these changes

```{r}

df.fin <- df.qual.exp %>% #filter(`Grant Number` != "H80CS00225") %>% 
  ungroup() %>% 
  #filter(MarketShare > median(MarketShare, na.rm = TRUE)) %>% 
  select(`Grant Number`, Year, ID, Att, `Total revenue (unrestricted & restricted)`, `Total net assets`, `Surplus as a pct of before dep expenses`, 
           `Staffing`, `Liabilities`, `Gross land, buildings and equipment (LBE)`, Liquidity, Profitability, Efficiency, NetWorth) %>%
  inner_join(df.qual.exp %>% filter(Year == 2016) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>% 
    select(Year, ZipFilter, ID, Att, `Total revenue (unrestricted & restricted)`, `Total net assets`, `Surplus as a pct of before dep expenses`, 
           `Staffing`, `Liabilities`, `Gross land, buildings and equipment (LBE)`, Liquidity, Profitability, Efficiency, NetWorth)

for (k in 1:3){

atts.fin <- rep(0, 7)
fig3.fin <- rep(0, 5)

if (k ==1){df.fin.root <- df.fin} else
  if (k == 2){df.fin.root <- df.fin %>% filter(ZipFilter == 2)} else
    if (k == 3){df.fin.root <- df.fin %>% filter(ZipFilter == 1)}

for (i in 5:ncol(df.fin)){

  temp <- df.fin.root[,c(1:4, i)]
  #temp <- df.fin.root[df.fin.root$Year %in% c(2015:2019), c(1:4, i)]
  colnames(temp) <- c("Year", "ZipFilter", "ID","Att", "Outcome")
  temp$Outcome

  # temp <- temp %>%
  #   mutate(Outcome = ifelse(Outcome < quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1],
  #                    ifelse(Outcome > quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], Outcome)))

cs.output.expand <- att_gt( yname = "Outcome",
                      tname = "Year",
                      idname = "ID",
                      gname = "Att",
                      xformla = ~1,
                      data = temp, # %>% filter(Year >= 2016), 
                      control_group = "nevertreated",
                      clustervars = "ID",
                      panel = FALSE, 
                      base_period = "universal"
                      )
cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)

atts.fin <- rbind(atts.fin, cbind(colnames(df.fin)[i], round(mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(mean(temp[temp$Att > 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE) - mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se), 3)))

atts <- rbind(atts, cbind(colnames(df.fin)[i], round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
      cs.output.expand.agg.dyn$overall.att, 
      cs.output.expand.agg.dyn$overall.att - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se, 
      cs.output.expand.agg.dyn$overall.att + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se), 3)))
z <- rbind(z, c(colnames(df.fin)[i], cs.output.expand$Wpval))

fig3.fin <- rbind(fig3.fin, 
                 data.frame(Outcome = colnames(df.fin)[i], 
                      Year = cs.output.expand.agg.dyn$egt, 
           Estimate = cs.output.expand.agg.dyn$att.egt, 
           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt))
}

rownames(fig3.fin) <- NULL
if (k == 1){atts.fin.full <- atts.fin[-1,]} else 
 if (k == 2){atts.fin.larger <- atts.fin[-1,]} else 
   {atts.fin.smaller <- atts.fin[-1,]}

}

#Event Study Plots
fig3.fin[-1,] %>%
  ggplot(mapping = aes(x = Year, y = Estimate)) +
  facet_wrap(~Outcome, scales = "free_y") +
  ylab("Percentage Points") +
  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") +
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") +
  geom_point() + geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) +
  ggtitle("fig3 - Event Study") +
  theme_tufte_revised()

 cbind(atts.fin.full, atts.fin.larger, atts.fin.smaller) %>% 
   kable("html", booktabs = T, col.names = rep(c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB"), 3)) %>%
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("General Measures" = 4, "Altmans Z Components" = 5)) %>% 
  add_header_above(c(" " = 1, "Full" = 6, "Profitable" = 6, "Unprofitable" = 6)) %>% 
  #pack_rows(index = c("Larger FQHCs" = 15, "Smaller FQHCs" = 15)) %>% 
  add_footnote(c(""))
```

## True Figure 4
```{r}
fields <- 10
fig4 <- cbind(c(rep("Full", fields), rep("More Market Share", fields), rep("Less Market Share", fields), rep('Profitable', fields), rep('Unprofitable/Budget Neutral', fields)), 
      rbind(atts.comp.full, atts.comp.larger, atts.comp.smaller, atts.fin.larger, atts.fin.smaller)) %>% 
  data.frame()

colnames(fig4) <- c("Subgroup", "Measure", "C_0", "T_0 - C_0", "Estimate", "LB", "UB")

fig4$Measure <- ifelse(fig4$Measure == 'Gross land, buildings and equipment (LBE)', 'Property and Buildings', fig4$Measure)

fig4$C_0 <- as.numeric(fig4$C_0)
fig4$`T_0 - C_0` <- as.numeric(fig4$`T_0 - C_0`)
fig4$Estimate <- as.numeric(fig4$Estimate)
fig4$LB <- as.numeric(fig4$LB)
fig4$UB <- as.numeric(fig4$UB)

fig4$Groups <- ifelse(fig4$Measure %in% c('Total revenue (unrestricted & restricted)','Property and Buildings','Staffing', 'Liabilities'), 'Mechanisms', 
               ifelse(fig4$Measure %in% c('Liquidity','Efficiency'), 'Financing', NA))

rownames(fig4) <- NULL

fig4 %>% 
  filter(Groups == 'Mechanisms' ) %>% 
ggplot(aes(y=Measure, x=Estimate, xmin=LB, xmax=UB)) +
geom_point() +

#this changes the features of the overall effects
#one could resize, reshape, or recolor these points if desired
xlab("DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5) +

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Subgroup, scales = "free_y", switch = 'y', space = "free_y")+

#thematic stuff
#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",size=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) +
  ggtitle("Figure 2, Incumbent Only (FQHC-zip-year units)")

# fig4 %>% 
#   select(Measure:UB) %>% 
#   filter(Measure %notin% c('Total revenue (unrestricted & restricted)', 'Total expenses before depreciation', 'Surplus as a pct of before dep expenses')) %>% 
#   kable("html", booktabs = T, col.names = c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB")) %>%
#   kable_styling(latex_options = c("striped")) %>%
#   pack_rows(index = c("General Measures" = 4, "Altmans Z Components" = 5)) %>% 
#   add_header_above(c(" " = 1, "Full" = 6, "Profitable" = 6, "Unprofitable" = 6)) %>% 
#   #pack_rows(index = c("Larger FQHCs" = 15, "Smaller FQHCs" = 15)) %>% 
#   add_footnote(c(""))

library(formattable)
fig4$C_0 <- currency(fig4$C_0, digits = 0L)
fig4$`T_0 - C_0` <- currency(fig4$`T_0 - C_0`, digits = 0L)
fig4$Estimate <- currency(fig4$Estimate, digits = 0L)
fig4$LB <- currency(fig4$LB, digits = 0L)
fig4$UB <- currency(fig4$UB, digits = 0L)

fig4 %>% 
  filter(Groups == 'Mechanisms' ) %>% 
  select(Measure:UB) %>% 
  kable("html", booktabs = T, col.names = c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB")) %>%
  kable_styling(latex_options = c("striped")) %>%
  row_spec(c(6, 14),bold=T, italic = T, hline_after = T) %>% 
  row_spec(c(19),bold=F, italic = T, hline_after = T) %>% 
  pack_rows(index = c("Panel A: Full Sample" = 4, "Panel B: Higher Low-Income Market Share Subgroup" = 4, "Panel B: Lower Low-Income Market Share Subgroup" = 4, 
                      "Panel C: Profitable Subgroup" = 4, "Panel C: Unprofitable/Budget Neutral Subgroup" = 4)) %>% 
  #add_header_above(c(" " = 1, "Full" = 6, "Profitable" = 6, "Unprofitable" = 6)) %>% 
  #pack_rows(index = c("Larger FQHCs" = 15, "Smaller FQHCs" = 15)) %>% 
  add_footnote(c(""))

```

# Robustness Testing

## Service Area Overlap measurement - Plausible Exogeneity

- >99% of zips in sample have unmet Low income, Medicaid, or Uninsured need at baseline
- Distance of Rival's new zip code to nearest existing zip code in service area,  75% are below 10km. All those > 10km to nearest site are in rural areas traveling across very low density land
```{r}

## Need
df.z.full %>% 
  filter(Year == 2015) %>% 
  left_join(census, by = c("Zip" = "ZipCode", "Year" = "YEAR")) %>% 
  mutate(Pct.Total = Total.z / TotalPop, Pct.LowInc = Total.z / (IncomeBelowPoverty / PovertyStatusDet * TotalPop), Pct.MCD = MCD.z / (Medicaid / MCD.denom * TotalPop), Pct.None = None.z / (Uninsured / Unins.denom * TotalPop) ) %>% 
  select(Zip:Att.z, Pct.Total:Pct.None) %>% 
  mutate(NeedMore = ifelse(Pct.LowInc < 1 | Pct.MCD < 1 | Pct.None < 1, 1, 0), 
         Tx = ifelse(Att.z > 0, 1, 0)) %>% 
  #group_by(Tx) %>% 
  mutate(#n(), 
            NeedMore = NeedMore, 
            NeedLowIncome = ifelse(Pct.LowInc < 1, 1, 0), 
            NeedMCD = ifelse(Pct.MCD < 1, 1, 0),
            NeedNone = ifelse(Pct.None < 1, 1, 0)) %>% 
  select(Tx, NeedMore:NeedNone) %>% 
  filter(!is.na(NeedMore)) %>% 
  tbl_summary(by = Tx) %>% 
  add_p()

## Distance of Competitor to New Site
df.z.dist <- df.z.full %>% 
  filter(Att.z == Year) %>% 
  select(Zip:Total.z) %>% 
  left_join(uds.sites %>% select(`Grant Number`, Year, Zip) %>% unique(), by = c("Zip","Year")) %>% 
  left_join(df.z %>% filter(Tx == 1) %>% select(`Grant Number`, Year, Zip) %>% unique(), by = c("Zip","Year")) %>% 
  filter(`Grant Number.x` != `Grant Number.y`)

## Read in Centroid Data
zip.centroids <- read.csv("ZIP_Code_Population_Weighted_Centroids.csv") %>% 
  mutate(ZipCode = str_pad(STD_ZIP5, 5, pad = "0")) %>% 
  select(ZipCode, X, Y)
## Add missing centroids
zip.centroids <- rbind(zip.centroids, c(ZipCode = "37243", X = -86.783, Y = 36.165), 
                                      c(ZipCode = "95951", X = -121.98, Y = 39.73)) %>% 
  mutate(X = as.numeric(X), Y = as.numeric(Y))

df.z.dist <- df.z.dist %>% mutate(DistToClosestSite = NA, ZipOfClosestSite = NA)

for (g in 1:nrow(df.z.dist)){
#g <- 3
 temp <- rbind(zip.centroids %>% filter(ZipCode == df.z.dist[g,]$Zip), 
          zip.centroids %>% filter(ZipCode %in% unique(uds.sites[uds.sites$`Grant Number` == df.z.dist[g,]$`Grant Number.x` & uds.sites$Year == df.z.dist[g,]$Year,]$Zip))) %>% 
   unique()
  mm <- as.matrix(dist(as.matrix(temp$X, temp$Y), method = "euclidean"))[-1,1]
  df.z.dist[g,]$DistToClosestSite <-  min(mm) * 111.139
  df.z.dist[g,]$ZipOfClosestSite  <- ifelse(is.na(temp[2,]$ZipCode), temp[1,]$ZipCode, unlist(temp[-1,]$ZipCode[rank(mm) == 1]))
}

df.z.dist[19,]$DistToClosestSite <- 0

mean(df.z.dist$DistToClosestSite)
quantile(df.z.dist$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))

mean(df.z.dist[df.z.dist$ZipFilter == 1,]$DistToClosestSite)
mean(df.z.dist[df.z.dist$ZipFilter == 2,]$DistToClosestSite)

quantile(df.z.dist[df.z.dist$ZipFilter == 1,]$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))
quantile(df.z.dist[df.z.dist$ZipFilter == 2,]$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))

zipsize <- zctas(starts_with = c(df.z.dist$Zip, df.z.dist$ZipOfClosestSite), year = 2010)

## Original Figure
df.z.dist.plot <- df.z.dist %>% 
  left_join(zipsize %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
  left_join(uds.sites %>% select(Zip, `Site State`) %>% unique(), by = c("Zip")) %>% 
  left_join(census %>% select(ZipCode, YEAR, TotalPop), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
  arrange(desc(DistToClosestSite)) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6) %>% 
  mutate(Density.NewZip = TotalPop / Area.SQmiles, 
         l.density = log(TotalPop / Area.SQmiles))

df.z.dist.plot %>% 
  ggplot(aes(x = log(Density.NewZip), y = DistToClosestSite)) + geom_point(aes(size = Area.SQmiles)) +
  ggtitle("Distance from Rival's newly competing zip ocde to closest incumbent zip code by Density and Area of newly competing zip code")

summary(lm(DistToClosestSite ~ log(Density.NewZip), data = df.z.dist.plot))

# Updated Figure
df.z.dist.plot <- df.z.dist.plot %>% 
  select(Zip:ZipOfClosestSite, Density.NewZip) %>% 
  left_join(zipsize %>% select(GEOID10, ALAND10), by = c("ZipOfClosestSite" = "GEOID10")) %>% 
  left_join(uds.sites %>% select(Zip, `Site State`) %>% unique(), by = c("ZipOfClosestSite" = "Zip")) %>% 
  left_join(census %>% select(ZipCode, YEAR, TotalPop), by = c("Year" = "YEAR", "ZipOfClosestSite" = "ZipCode")) %>% 
  arrange(desc(DistToClosestSite)) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6) %>% 
  mutate(Density.Origin = TotalPop / Area.SQmiles)

df.z.dist.plot %>% 
  ggplot(aes(x = log(Density.NewZip), y = DistToClosestSite, color = log(Density.Origin))) + geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10))+ theme_minimal()+
  ylab("Distance from Competative to closest Rival Site (km)") +
  ggtitle("Distance from newly competative Zip to Rival's closest existing zip, by log Density of areas")

p <- df.z.dist.plot %>% 
  ggplot(aes(x = log(Density.Origin), y = log(Density.NewZip))) + 
  geom_point(aes(size = DistToClosestSite, colour = DistToClosestSite)) + 
  scale_colour_gradientn(colours = c("green","lightblue","purple"),
                         values = c(1.0,0.7,0.1,0))  +#scale_colour_gradientn(colours = terrain.colors(10))+ 
  theme_minimal() + ylab("Log Population Density of New Zip Code") + 
  xlab("Log Population Density of Nearest Service Area Zip Code") + 
  labs(color = "Distance Travelled to\nOpenNew Site (km)") + 
  guides(size = FALSE) + xlim(0.5, 11.5) + ylim(0.5, 11.5)
p

summary(lm(log(Density.Origin) ~ log(Density.NewZip), data = df.z.dist.plot))

```

## Estimate effects of competition on nearest FQHC, takes 20 minutes to run code
```{r}

## Build the first part of the dataset

df.spill <- df.z %>% 
  left_join(df.z.dist %>% 
  select(`Grant Number.y`, Zip) %>% 
    unique() %>% 
    rename(ZipOfComp = Zip), by = c("Grant Number" = "Grant Number.y")) %>% 
  #filter(!is.na(ZipOfComp)) %>% 
  mutate(ZipOfComp = ifelse(`Grant Number` == "H80CS00765", 95991, ZipOfComp)) %>% 
  left_join(zip.centroids, by = c("Zip" = "ZipCode")) %>% 
  left_join(zip.centroids, by = c("ZipOfComp" = "ZipCode")) %>% 
  mutate(Dist = sqrt((X.x - X.y) ^ 2 + (Y.x - Y.y) ^ 2) * 111.139) %>% 
  mutate(Dist.f = ifelse(is.na(Dist), "-1",
                  ifelse(Dist == 0, 0, 
                  ifelse(Dist > 0 & Dist < 20, 1, 
                  ifelse(Dist >= 20 & Dist < 50, 2, 3))))) %>% 
  #filter(is.na(Dist.f) | Dist.f == 2) %>% 
  left_join(uds.sites %>% 
              filter(`Location Setting` %in% c("All Other Clinic Types")) %>% 
              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
              group_by(`Grant Number`, Year, Zip) %>% 
              summarise(Sites = n(), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)), by = c("Grant Number","Year", "Zip")) %>% 
  mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
         Calendar = ifelse(is.na(Calendar), 0, Calendar))

dist.vecs <- df.spill[!is.na(df.spill$Dist),]$Dist

df.spill %>% 
  group_by(Dist.f) %>% 
  summarise(n())

## Find neighbors based on some circle around FQHC zip

mm <- dist(zip.centroids[,2:3])
mm <- as.matrix(mm) * 111.139

mm.2 <- mm[zip.centroids$ZipCode %in% unique(df.spill$Zip),]

mm.2 <- as.matrix((mm.2 < 50) + 0 )
rowSums(mm.2)

mm.3 <- c(CenterZip = 0, Year = 0, Competing.Sites = 0)
for (g in 1:dim(mm.2)[1]){
  mm.3 <- rbind(mm.3, cbind(CenterZip = zip.centroids[rownames(mm.2)[g],]$ZipCode, zip.centroids[names(mm.2[g,][which(as.vector(mm.2[g,] == 1))]),]) %>% 
  left_join(uds.sites %>% filter(Year %in% c(2015:2019)) %>% group_by(Year, Zip) %>% summarise(Sites.Total = n()), by = c("ZipCode" = "Zip")) %>% 
  left_join(df.spill %>% select(`Grant Number`, Year, Zip, Sites), by = c("ZipCode" = "Zip", "Year")) %>% 
  mutate(Sites.Total = ifelse(is.na(Sites.Total), 0, Sites.Total), 
         Sites = ifelse(is.na(Sites), 0, Sites), 
         Competing.Sites = Sites.Total - Sites) %>% 
  filter(CenterZip != ZipCode) %>% 
  group_by(CenterZip, Year) %>% 
  summarise(Competing.Sites = sum(Competing.Sites)) %>% 
    as.matrix())
}

mm.3 <- mm.3[-1,]

#mm.100 <- mm.3 %>% data.frame() 
#mm.60 <- mm.3 %>% data.frame() 
#mm.50 <- mm.3 %>% data.frame() 
#mm.20 <- mm.3 %>% data.frame() 
#mm.10 <- mm.3 %>% data.frame()

#mm.3 <- mm.50

```

```{r}
cs.output.expand <- att_gt( yname = "Total.Hours",
                      tname = "Year",
                      idname = "ID",
                      gname = "Att",
                      xformla = ~1,
                      data = df.spill %>% filter(Dist.f %in% c("-1",3)), # %>% filter(Year > 2015),
                      control_group = "nevertreated",
                      clustervars = "ID",
                      panel = TRUE,
                      base_period = "universal"
                      )
aggte(cs.output.expand, type = "simple", na.rm = TRUE)
```

## Control for spatial Spillovers
```{r}

df.spill2 <- df.spill %>% 
  left_join(mm.3 %>% data.frame() %>% mutate(Year = as.numeric(Year)), by = c("Zip" = "CenterZip","Year")) %>% 
  mutate(Competing.Sites = as.numeric(ifelse(is.na(Competing.Sites), 0, Competing.Sites)), 
         D = ifelse(Competing.Sites > 0, 1, 0))

#length(unique(df.spill2[is.na(df.spill2$Dist),]$Zip))  1893 or 1893 * 5

set.seed(234)  #232
df.spill2 <- df.spill2 %>% mutate(Dist = ifelse(is.na(Dist), rep(sample(dist.vecs, 1893, replace = T), each = 5), Dist), 
                                  Att.viz = ifelse(Att == 0, rep(sample(c(2017:2019), 1893, replace = T), each = 5), Att)) %>% 
  mutate(Dist.rounded = as.factor(ceiling(Dist / 10)))

df.spill2 <- df.spill2 %>% 
  ungroup() %>% 
  #filter(MarketShare < median(MarketShare, na.rm = TRUE)) %>% 
  select(`Grant Number`, Tx, D, Att, Att.viz, Dist, Dist.rounded, Year, Zip, Total.Hours, Sites, Perminance, Schedule, Calendar, Total.z, MCD.z, MCR.z, COM.z, None.z) %>%
  inner_join(df.qual.exp %>% filter(Year == 2016) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>% 
    select(Tx, D, Dist, Year, Zip, `Grant Number`, ZipFilter, Att, Att.viz, Dist.rounded, Total.Hours, Sites, Perminance, Schedule, Calendar, Total.z, MCD.z, MCR.z, COM.z, None.z) # %>% filter(ZipFilter == 2)

  i <- 11
  df.temp <- df.spill2[,c(1:5, i)]
  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model_feols_clustered <- feols(Outcome ~ Tx*as.numeric(Dist / 10) + D | Year + Zip, cluster = ~ Zip, data = df.temp)
  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]

for (i in 12:20){
  df.temp <- df.spill2[,c(1:5, i)]
  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model_feols_clustered <- feols(Outcome ~ Tx*as.numeric(Dist / 10) + D | Year + Zip, cluster = ~ Zip, data = df.temp)
  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),])
}

p.spill <- df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >=  Att.viz, 1, Tx)) %>% 
  filter(Att > 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), Total.z = mean(Total.z, na.rm = TRUE), Total.Hours = mean(Total.Hours, na.rm = TRUE), MCD.z = mean(MCD.z, na.rm = TRUE)) %>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, Total.z, Total.Hours, MCD.z)) %>% 
  mutate(Sites = Sites_1 - Sites_0, 
         Total.z = Total.z_1 - Total.z_0, 
         Total.Hours = Total.Hours_1 - Total.Hours_0, 
         MCD.z = MCD.z_1 - MCD.z_0) %>% 
  left_join(df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >= Att.viz, 1, Tx)) %>% 
  filter(Att == 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), Total.z = mean(Total.z, na.rm = TRUE), Total.Hours = mean(Total.Hours, na.rm = TRUE), MCD.z = mean(MCD.z, na.rm = TRUE)) %>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, Total.z, Total.Hours, MCD.z)) %>% 
  mutate(Sites.control = Sites_1 - Sites_0, 
         Total.z.control = Total.z_1 - Total.z_0, 
         Total.Hours.control = Total.Hours_1 - Total.Hours_0, 
         MCD.z.control = MCD.z_1 - MCD.z_0) %>% 
    select(Dist.rounded, Sites.control:MCD.z.control), by = c("Dist.rounded")) %>% 
  mutate( Locations = Sites - Sites.control, 
         `Patients` = Total.z - Total.z.control, 
         `Patients - Medicaid Only` = MCD.z - MCD.z.control, 
         `Hours per Week` = Total.Hours - Total.Hours.control) %>% 
  select(Dist.rounded:Counts_1, `Locations`:`Hours per Week`) %>% 
  mutate(Dist.rounded = as.numeric(paste(Dist.rounded, 0, sep = ""))) %>% 
  pivot_longer(cols = c( `Locations`:`Hours per Week`)) %>% 
  mutate(`Treated Zips` = Counts_0 / 3) %>% 
  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 200) + 
  xlab("Kilometers to Competitive Zip") + ylab("Unadjusted Difference-in-differences") + theme_tufte_revised() + 
  geom_smooth(method = "lm", se = F, quiet = TRUE, formula = "y ~ x", mapping = aes(weight = `Treated Zips`)) + 
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") + theme(text = element_text(size = 16)) + theme(title = element_text(face = "bold")) + 
  ggtitle("Figure 4 - Unadjusted DID Estimates by Distance to Competitive Zip")

suppressWarnings(print(p.spill))

output <- cbind(TEs %>% 
  mutate(`95% LB` = Estimate - `Std..Error` * 1.96, 
         `95% UB` = Estimate + `Std..Error` * 1.96) %>% 
    select(Estimate,`95% LB`, `95% UB`) ,

TEs_Dist %>% 
  mutate(`95% LB` = Estimate - `Std..Error` * 1.96, 
         `95% UB` = Estimate + `Std..Error` * 1.96) %>% 
    select(Estimate,`95% LB`, `95% UB`)) 
rownames(output) <- c("Hours Per Week","Locations","Perminance","Weekly Schedule","Calendar Schedule","Total","Medicaid","Medicare","Commerical","Uninsured")

round(output[c(6:10, 2,3, 1, 4, 5),], digits = 3) %>% 
  kable("html", booktabs = T, col.names = c("DID Estimate", "95% LB", "95% UB", "DID Estimate", "95% LB", "95% UB")) %>%
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Patient Panel" = 5, "Extensive Margin" = 2, "Intensive Margin" = 3)) %>% 
  add_header_above(c(" " = 1, "Treatment Effect" = 3, "Treatment Effect * Distance" = 3)) %>% 
  add_footnote(c("Treatment Effect is the ATT estimated in the zip code where the rival opens their new location","Treatment Effect * Distance is the change in the ATT for every 10km an outlying zip code in the incumbent's service area is from the competitive zip "))
```

## Preperiod parallel trends
```{r}

i <- 4
df.temp2 <- df.spill2 %>% filter(Att == 0 | Year < Att) %>% mutate(Treat = ifelse(Att > 0, 1, 0)) %>% 
                   select(Year, Treat, Zip, Total.Hours:None.z)
df.temp2 <- df.temp2[,c(1:3, i)]
names(df.temp2) <- c('Year','Treat','Zip','Outcome')

parallel.trends.set <- data.frame(feols(Outcome ~ Treat * Year, 
                 data = df.temp2)$coeftable)[4,]

for (i in 5:13){
  df.temp2 <- df.spill2 %>% filter(Att == 0 | Year < Att) %>% mutate(Treat = ifelse(Att > 0, 1, 0)) %>% 
                   select(Year, Treat, Zip, Total.Hours:None.z)
df.temp2 <- df.temp2[,c(1:3, i)]
names(df.temp2) <- c('Year','Treat','Zip','Outcome')

parallel.trends.set <- rbind(parallel.trends.set, data.frame(feols(Outcome ~ Treat * Year , 
                 data = df.temp2)$coeftable)[4,])
}
parallel.trends.set
```

## Again, with did2s
```{r}
did2s(
      data = df.spill2, 
      yname = "MCD.z", 
      treatment = "Tx",
        first_stage = ~ 0 | Zip + Year + D, 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),
        cluster_var = "Zip",
      verbose = FALSE
    )

```

## How do close versus far zip codes compare

```{r}

df.temp3 <- df.spill2 %>% 
  left_join(census, by = c("Zip" = "ZipCode", "Year" = "YEAR" )) %>% 
    filter(Year %in% c(2015:2016) & Att > 0) %>% 
  mutate(Pct.Age = Age65andOver / TotalPop * 100, 
         Pct.Pov = IncomeBelowPoverty / PovertyStatusDet * 100, 
         Pct.HL = Hispanic / TotalPop * 100, 
         Pct.Black = Black / TotalPop * 100,
         Pct.White = White / TotalPop * 100,
         Pct.Unemp = Unemployed / Unemp_denom * 100,
         Pct.MCD = Medicaid / MCD.denom * 100, 
         Pct.NoIns = Uninsured / Unins.denom * 100) %>% 
  select(Dist, Pct.Age, Pct.HL, Pct.Black, Pct.White, Pct.Pov, Pct.Unemp, Pct.MCD, Pct.NoIns)

ziptypes <- data.frame(0, 0, 0, 0)
for (k in 2:ncol(df.temp3)){
  df.temp4 <- df.temp3[,c(1, k)]
  names(df.temp4) <- c('Dist','Outcome')

  ziptypes <- rbind(ziptypes, summary(lm(data = df.temp4, Outcome ~ as.numeric(Dist / 10) ))$coeff[2,])
}
ziptypes <- ziptypes[-1,]

rownames(ziptypes) <- c("% age over 65+","% Hispanic/Latino","% Black","% White", "% Poverty","% Unemployed","% Medicaid","% Uninsured")

ziptypes %>% 
  mutate(Estimate = X0, 
         `95% LB` = X0 - X0.1 * 1.96, 
         `95% UB` = X0 + X0.1 * 1.96, 
         `p-value` = X0.3) %>% 
  select(Estimate:`p-value`) %>% 
  kable("html", booktabs = T) %>%
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Demographics" = 4, "Income" = 2, "Insurance" = 2)) %>% 
  row_spec(c(1, 4), bold = T, hline_after = T) %>% 
  row_spec(c(3, 5:8), italic = T, hline_after = T) %>% 
  add_footnote(c("For every 10 km between the competing zip code and the zip code of interest, the covariate rate will change by the estimated coefficient"))

```

## Balance on Covariates
```{r}

df.qual.exp %>% 
  mutate(Treat = ifelse(Att > 0, 1, 0)) %>% 
  mutate(Groups = ifelse(Treat == 1 & Expandor == 0, "Treated", 
                  ifelse(Treat == 0 & Expandor == 0, "Control", 
                  ifelse(Treat == 0 & Expandor == 1, "Expandor Comp", "Expandor No Comp")))) %>% 
  filter(Year == 2015) %>%  #z & ZipFilter == 2) %>% 
  select(Sites, Zips, #MarketShare, 
         Total, Density, Pct.Rural, Pct.Urban, None:MCD, IMM2yo:DepScrn, Groups, Pct.NHA:Pct.NHW, Pct.LessThan200pctFPL, Pct.Homeless:Pct.Children, `Liabilities (as pct of assets)`, `Gross land, buildings and equipment (LBE)`, `Surplus as a pct of after dep expenses`) %>% #SwitchEMR, InterOrgHITexchange, UDSQualRep.highlowuse, 
  tbl_summary(by = Groups, 
              statistic = all_continuous() ~ "{mean} ({sd})") %>% 
  add_p(test = everything() ~ "t.test")

```

## Treated vs Rivals
```{r}

# rbind(uds.covariates %>% filter(Year == 2015 & `Grant Number` %in% c(unique(df.z.dist.plot$`Grant Number.x`)) ) %>% mutate(Class = "Incumbent"), 
#       uds.covariates %>% filter(Year == 2015 & `Grant Number` %in% c(unique(df.z.dist.plot$`Grant Number.y`)) ) %>% mutate(Class = "Rival")) %>% 
#   tbl_summary(by = Class) %>% 
#   add_p()

```

## Mapping Quality Function
```{r}
p <- seq(0, 1, 0.05)
v <- c(1:10)

for (i in 1:10){
  p <- i / 10
  y <- 1 - (1 - p)^v
  y.prime = -(1 - p)^v*log(1 - p) - y/v
  #plot(v, y, main = paste("p = ", p, sep = "")) ## For regular trade offs
  plot(v, y.prime, main = paste("p = ", p, sep = "")) ## for denominator sign checking
}

## Checking the total differential on quality to see what happens
dd <- merge(merge(seq(0.2, 0.8, 0.05), c(1:5)) %>% rename(p = x, v = y), 
        c(seq(-5, -1, 0.5), seq(1, 5, 0.5)) ) %>% 
  rename(dv = y) %>% 
  mutate(dp = (-(1 - p)^v*log(1 - p) - (1 - (1 - p)^v)/v)*( v*(1 - p)^(v-1) )^-1 * dv) %>% 
    mutate(dq = -(1 - p)^v*log(1 - p) * dv + v*(1 - p)^(v-1) * dp) %>% 
  filter(dv > -abs(v))

summary(dd[complete.cases(dd),]$dq)

dd %>% filter(dq == min(dd$dq, na.rm = TRUE))
dd %>% filter(dq == max(dd$dq, na.rm = TRUE))

plot(dd[dd$v == 3,]$dv, dd[dd$v == 3,]$dq)

ggplot(data = dd, aes(x = p, y = dq, color = dv)) + geom_point() + facet_wrap(~v)

summary(df.qual.exp$Qcomp)

```

## Placebo

```{r}

df.placebo <- df.qual.exp %>% 
  #filter(ZipFilter == 2) %>% 
select(Year, ID, Att, Pct.NHA:Pct.Children) 
# %>% 
#   inner_join(df.qual.exp %>% filter(Year == 2016) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(ID, ZipFilter), by = c("ID")) %>% 
#   filter(ZipFilter == 2) %>% 
#     select(Year, ID, Att, Pct.NHA:Pct.Children)

atts.placebo <- rep(0, 7)
for (i in 5:ncol(df.placebo)){

  temp <- df.placebo[,c(1:3, i)]
  colnames(temp) <- c("Year","ID","Att","Outcome")

cs.output.expand <- att_gt( yname = "Outcome",
                      tname = "Year",
                      idname = "ID",
                      gname = "Att",
                      xformla = ~1,
                      data = temp,
                      control_group = "nevertreated",
                      clustervars = "ID",
                      panel = FALSE, 
                      base_period = "universal"
                      )
cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)

atts.placebo <- rbind(atts.placebo, cbind(colnames(df.placebo[,i]), round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
      cs.output.expand.agg.dyn$overall.att, 
      cs.output.expand.agg.dyn$overall.att - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se, 
      cs.output.expand.agg.dyn$overall.att + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se), 3)))

}

#if (k == 1){atts.placebo.larger <- atts.placebo[-1,]} else {atts.placebo.smaller <- atts.placebo[-1,]}

#rownames(atts.placebo.larger) <- NULL
#atts.placebo.larger
#atts.placebo.smaller

as.data.frame(atts.placebo[-1,]) %>% 
  rename(Measure = V1, Estimate = V2, `95%CI_LB` = V3, `95%CI_UB` = V4)
```

## multiple hypothesis correction, pre-period parallel trends
```{r}

# rownames(atts) <- rep(NULL, nrow(atts))
# if (k == 1){atts.larger <- atts} else {atts.smaller <- atts}
#

# p-values rankings, Benjamini-Hochberg procedure
cbind(Sample = c(rep("Panel A: Full Sample", 3), 
                    rep("Panel B: Higher Low-Income Market Share Subgroup", 3), 
                    rep("Panel B: Lower Low-Income Market Share Subgroup", 3), 
                    rep("Panel C: Profitable Subgroup", 3), 
                    rep("Panel C: Unprofitable/Budget Neutral Subgroup", 3)), 
  data.frame(Outcome = atts[c(2:16),c(1)], Estimate = atts[c(2:16),c(2)], CI = paste("(", atts[c(2:16),3], ", ", atts[c(2:16),4], ")", sep = ""), p.value =  c(2*pnorm(-abs(as.numeric(atts[c(2:16),2]) / ((as.numeric(atts[c(2:16),4]) - as.numeric(atts[c(2:16),3])) / (2 * 1.96)))))))      %>% 
     arrange(p.value) %>%  
    mutate(rank = row_number(), 
           rank / 14 * 0.1) %>%

  kable("html", booktabs = T, col.names = c("Sample","Outcome", "Estimate", "95% CI", "p-value", "Rank", "BH-procedure Threshold")) %>%
  kable_styling(latex_options = c("striped")) %>% 
  row_spec(c(1:6), italic = T, hline_after = T, background = "lightgrey")

# parallel trends
if (k == 1){z.larger <- z[-1,]} else {z.smaller <- z[-1,]}

# length(z.larger)
# length(z.smaller)
cbind(atts[c(2:16),1], z[c(2:16),2])
cbind(atts[atts[,1] %in% c('Total revenue (unrestricted & restricted)','Total net assets','Staffing', 'Liabilities'),1], z[atts[,1] %in% c('Total revenue (unrestricted & restricted)','Total net assets','Staffing', 'Liabilities'),2])

```

## What's happening in the control? Let's think

```{r}

df.space <- df.qual.exp %>% 
  filter(Att > 0) %>% 
  select(`Grant Number`, Year) %>% 
  unique() %>% 
  left_join(uds.sites %>% select(`Grant Number`, Year, Zip), by = c("Grant Number","Year")) %>% 
  left_join(clinics.in.zips, by = c("Zip","Year")) %>%

#  filter(`Grant Number` == "H80CS00881")
  group_by(Zip) %>% 
  filter(max(Clinics) > 1) %>% 
  unique() %>% 
  left_join(uds.sites %>% select(`Grant Number`, Zip, Year), by = c("Zip","Year")) %>% 
  rename(Incumbent = `Grant Number.x`, Competitor = `Grant Number.y`) %>% 
  filter(Incumbent != Competitor) %>% 
  group_by(Zip, Incumbent, Competitor) %>% 
  summarise(YearFirstComp = min(Year))%>% 
  arrange(Incumbent)

#df.space %>%  filter(Incumbent == "H80CS00881")

df.z.2 <- df.space %>% 
  pivot_longer(Incumbent:Competitor) %>% 
  left_join(uds.zip.totals, by = c("value" = "Grant Number")) %>% 
    ungroup() %>% 
  mutate(ID = as.numeric(as.factor(paste(Zip, name, value)))) %>% 
  mutate(year.rel = `Reporting Year` - YearFirstComp, 
         Treat = ifelse(name == "Incumbent", 1, 0), 
         Post = ifelse(year.rel >= 0, 1, 0))

df.z.2$year.rel <- relevel(as.factor(df.z.2$year.rel), ref = "-1")

# Are incumbents and controls really that different?  not really
df.z.2 %>% 
  select(value, name, `Reporting Year`, None:Total) %>% 
  unique() %>% 
  left_join(uds.covariates, by = c("value" = "Grant Number", "Reporting Year" = "Year")) %>% 
  left_join(uds.6b.rates, by = c("value" = "GrantNumber", "Reporting Year" = "Year")) %>% 
  filter(`Reporting Year` == 2015) %>% 
  filter(value != 'H80CS28975') %>% 
  select(name, Total, None:Pct.Children, IMM2yo:DepScrn) %>% 
  mutate(None = None / Total, 
         MCD = MCD / Total, 
         MCR = MCR / Total, 
         COM = COM / Total) %>% 
  tbl_summary(by = name, 
              statistic = all_continuous() ~ "{mean} ({sd})") %>% 
  add_p(test = everything() ~ "t.test")

summary(lm(data = df.z.2, Total ~ Treat*year.rel))

# Competitors in the competative zip

df.space %>% 
  left_join(df.qual.exp %>% select(`Grant Number`, Att), by = c("Incumbent" = "Grant Number")) %>% 
  left_join(uds.zip, by = c("Zip" = "Zip Code","Competitor" = "Grant Number")) %>% 
  filter(`Reporting Year` %in% c(2015:2019)) %>% 
  mutate(year.rel = `Reporting Year` - Att, 
         Tx = ifelse(`Reporting Year` - Att >= 0 , 1, 0)) %>% 
  ggplot(aes(x = year.rel, y = `Total Number of Patients`, group = Tx)) + geom_point() + geom_smooth(method = "lm") #+ ylim(0, 2000)

df.space1 <- df.space %>% 
  left_join(df.qual.exp %>% select(`Grant Number`, ID, Att) %>% unique(), by = c("Incumbent" = "Grant Number")) %>% 
  merge(2015:2019) %>% 
  left_join(uds.zip, by = c("Zip" = "Zip Code","Competitor" = "Grant Number", "y" = "Reporting Year")) %>% 
  #filter(y %in% c(2015:2019)) %>% 
  mutate(year.rel = y- Att, 
         Tx = ifelse(year.rel >= 0 , 1, 0)) %>% 
  mutate(None.z = ifelse(is.na(`None_Uninsured Patients`), 0, `None_Uninsured Patients`),
          MCR.z = ifelse(is.na(`Medicare Patients`), 0, `Medicare Patients`),
          COM.z = ifelse(is.na(`Private Patients`), 0, `Private Patients`),
          MCD.z = ifelse(is.na(`Medicaid_CHIP_Other Public Patients`), 0, `Medicaid_CHIP_Other Public Patients`),
          Total.z = ifelse(is.na(`Total Number of Patients`), 0, `Total Number of Patients`),
         Grant = Competitor) %>% 
  rename(Year = y) %>% 
  select(Grant, Zip, ID, Att, Year, None.z:Total.z) %>% 
  arrange(Grant, Zip, Year) %>% 
  rbind(df.spill %>% 
  filter(Att == 0) %>% 
  rename(Grant = `Grant Number`) %>% 
  select(Grant, Zip, ID, Att, Year, None.z, MCR.z, COM.z, MCD.z, Total.z) %>% 
    inner_join(df.spill2 %>% filter(Dist == 0) %>% select(`Grant Number`) %>% unique(), by = c("Grant" = "Grant Number"))) %>% 
  mutate(Tx = ifelse(Att > 0 & Year >= Att, 1, 0))

feols(data = df.space1, Total.z ~ Tx | Zip + Year, cluster = ~Zip)

cs.output.expand <- att_gt( yname = "Total.z",
                      tname = "Year",
                      idname = "ID",
                      gname = "Att",
                      xformla = ~1,
                      data = df.space1, # %>% filter(Year > 2015),
                      control_group = "nevertreated",
                      clustervars = "ID",
                      panel = TRUE,
                      base_period = "universal"
                      )
aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)
```

## Change in Full Market Benefit
```{r}

df.z.dist.plot %>% 
  left_join(uds.zip %>% select(`Grant Number`, `Reporting Year`, `Zip Code`, `Medicaid_CHIP_Other Public Patients`, `Total Number of Patients`), 
            by = c("Grant Number.y" = "Grant Number", "Zip" = "Zip Code")) %>% 
  left_join(uds.zip %>% select(`Grant Number`, `Reporting Year`, `Zip Code`, `Medicaid_CHIP_Other Public Patients`, `Total Number of Patients`), 
            by = c("Grant Number.x" = "Grant Number", "Zip" = "Zip Code", "Reporting Year")) %>% 
  rename(MCD.Rival = `Medicaid_CHIP_Other Public Patients.y`, 
         Total.Rival = `Total Number of Patients.y`, 
         MCD.Incumbent = `Medicaid_CHIP_Other Public Patients.x`, 
         Total.Incumbent = `Total Number of Patients.x`) %>% 
  left_join(uds.6b.rates %>% 
            mutate(Quality.Incumbent = (IMM2yo + Pap + ChildBMI + AdultBMI + Tobac + CRC + DepScrn) / 7) %>% 
            select(GrantNumber, Year, Quality.Incumbent), by = c("Grant Number.y" = "GrantNumber", "Reporting Year" = "Year")) %>% 
  left_join(uds.6b.rates %>% 
            mutate(Quality.Rival = (IMM2yo + Pap + ChildBMI + AdultBMI + Tobac + CRC + DepScrn) / 7) %>% 
            select(GrantNumber, Year, Quality.Rival), by = c("Grant Number.x" = "GrantNumber", "Reporting Year" = "Year")) %>% 
  mutate(YearDiff = `Reporting Year` - Year, 
         Post = ifelse(YearDiff >= 0, 1, 0)) %>% 
  filter(`Reporting Year` %in% c(2015:2019)) %>% 
  select(Zip, Att.z, `Grant Number.x`, `Grant Number.y`, `Reporting Year`:Post) %>% 
  mutate(Quality.Market = Total.Incumbent / (Total.Incumbent + Total.Rival) * Quality.Incumbent + Total.Rival / (Total.Incumbent + Total.Rival) * Quality.Rival) %>% 
  group_by(Post) %>% 
  summarise(mean(Quality.Market, na.rm = TRUE))

```

### 2023-08-13 code/data_cleaning.Rmd
first thing

--- 2023-08-13 code/230510_Competition.Rmd
@@
 ```
-
-## What's happening with the closures?
-```{r}
-
-closures <- uds.sites[!is.na(uds.sites$Zip),] %>% 
-  select(`Grant Number`, Zip, Year) %>% 
-  unique() %>% 
-  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
-  group_by(`Grant Number`, Year) %>% 
-  summarise(Clinics = max(Clinics)) %>% 
-  pivot_wider(id_cols = `Grant Number`, names_from = Year, values_from = Clinics) %>% 
-  filter(`2014` == 1 & `2015` == 1 & `2016` == 1 ) %>% 
-  left_join(chc.term, by = c("Grant Number" = "ClinicID")) %>% 
-  filter(!is.na(NewClinicID))
-
-closures <- closures %>% pivot_longer(`2014`:`2021`) %>%
-  mutate(Outcome = ifelse(!is.na(NewClinicID) & is.na(value), 1, 0))
-
-closures <- closures %>% 
-  left_join(closures %>% 
-    group_by(`Grant Number`) %>% 
-    filter(value > 1) %>% 
-    filter(name == min(name)) %>% 
-    select(`Grant Number`, name), by = c("Grant Number")) %>% 
-  #rename(Year = name.x) %>% 
-  mutate(Att = as.numeric(ifelse(is.na(name.y), "0", name.y)), 
-         Year = as.numeric(name.x)) %>% 
-    select(`Grant Number`, Year, Att, Outcome) %>% 
-  rbind( df.qual.exp %>% 
-  mutate(Outcome = 0) %>% 
-  select(`Grant Number`, Year, Att, Outcome)) %>% 
-  mutate(ID = as.numeric(factor(`Grant Number`)), 
-         Tx = ifelse(Year >= Att, 1, 0))
-
-summary(lm(data = closures, Outcome ~ Tx + as.factor(Year)))
-
-cs.output.expand <- att_gt( yname = "Outcome",
-                      tname = "Year",
-                      idname = "ID",
-                      gname = "Att",
-                      xformla = ~1,
-                      data = closures, 
-                      control_group = "nevertreated",
-                      panel = FALSE, 
-                      clustervars = "ID",
-                      base_period = "universal"
-                      )
-aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-```
-
-## Play environment
-```{r}
-
-cs.output.expand <- att_gt( yname = "Qcomp",
-                      tname = "Year",
-                      idname = "ID",
-                      gname = "Att",
-                      xformla = ~Pct.NHB.y + Pct.HL.y + Pct.LessThan100pctFPL.y + Pct.FarmWorker.y + Pct.Homeless.y + Pct.Children.y,
-                      data = df.qual.exp %>% 
-  left_join(cw %>% left_join(staffing, by = c("EIN")) %>% 
-  select(`Grant Number`, Year, Staff) %>% mutate(Year = as.numeric(Year), Staff = as.numeric(Staff)), by = c("Grant Number","Year")) %>% 
-    left_join(df.qual.exp %>% filter(Year == 2016) %>% select(`Grant Number`, Pct.NHA:Pct.Children), by = c("Grant Number")) %>% 
-    filter(ZipFilter == 1), # / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`) * 1000), # %>% inner_join(df.qual.exp %>% filter(Year == 2016 & `Surplus as a pct of before dep expenses`< 2) %>% select(`Grant Number`), by = c("Grant Number")),  # %>% select(Year, ID, Att, `Gross land, buildings and equipment (LBE)`) %>% filter(!is.na(`Gross land, buildings and equipment (LBE)`)), ### Split surplus pct after dep at 0 and 0.05 in 2016 plus ZipFilter ==2
-                      control_group = "nevertreated",
-                      panel = TRUE, 
-                      clustervars = "ID",
-                      base_period = "universal"
-                      )
-aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-
-cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)
-data.frame(Year = cs.output.expand.agg.dyn$egt, 
-           Estimate = cs.output.expand.agg.dyn$att.egt, 
-           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
-           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt) %>% 
-  # mutate(CILB = replace(CILB, Year == -1, NA), 
-  #        CIUB = replace(CIUB, Year == -1, NA)) %>% 
-  #filter(abs(Year) < 4) %>% 
-  ggplot(mapping = aes(x = Year, y = Estimate)) + 
-  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") + 
-  geom_hline(yintercept=0, linetype = "dashed", color = "grey") + 
-  geom_point() + geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) + theme_tufte_revised()
-
-summary(df.qual.exp[df.qual.exp$Year %in% c(2016:2019),]$`Liabilities (as pct of assets)`)
-
-# Surplus as a pct of after dep expenses
-# Liabilities (as pct of assets)
-# Qcomp
-# Gross land, buildings and equipment (LBE)
-
-df.qual.exp %>%
-  #filter(Att == 2020 & Year == 2020) %>%
-  select(Att, Year, `Gross land, buildings and equipment (LBE)`, Sites, Altmans.Z, None) %>%
-  mutate(Treat = ifelse(Att > 0, 1, 0)) %>%
-  group_by(Att, Year) %>%
-  summarize(Outcome = mean(None, na.rm = TRUE)) %>%
- # mutate(Outcome = ifelse(Outcome < -5, -5, Outcome)) %>%
-  ggplot(aes(x = Year, y = Outcome, group = factor(Att), color = factor(Att))) + geom_point() #+ geom_jitter()
-
-# uds.zip.totals %>% 
-#   mutate(LowInc = (None + MCD) / Total) %>% 
-#   filter(LowInc < 0.5 & `Reporting Year` == 2019)
-#summary(lm(data = df.qual.exp, Qcomp ~ MarketShare + factor(Year) + factor(`Grant Number`)))
-
-#df.qual.exp %>% filter(Year == 2016 & `Surplus as a pct of after dep expenses` < 0 & ZipFilter == 2)
-
-```
-
-## Quick Matching to see if shit changes
-```{r}
-
-# df.match <- df.qual.exp %>% filter(Year == 2015) %>%
-#   select(`Grant Number`, Att, MCD, Total, Sites, Pct.NHB, Pct.HL, Pct.Children, Pct.LessThan100pctFPL)
-# 
-# 
-# FIPS <- df.match$`Grant Number`
-# X <- as.matrix(df.match[,c(3:9)])
-# Tr <- ifelse(df.match$Att > 0, 1, 0)
-# 
-# summary(X)
-# 
-# m <- Match(Tr = Tr, X = X, M = 1) #, replace = TRUE)
-# #mb <- MatchBalance(Treatment ~ . - FIPS, data=df.match, match.out=m, nboots=500)
-# 
-# df.matched <- data.frame(FIPS[m$index.treated], FIPS[m$index.control]) %>%
-#   mutate(Paired = paste(FIPS[m$index.treated], FIPS[m$index.control], sep = "-"))
-# 
-# df.matched <- rbind(df.matched %>%
-#         select(FIPS.m.index.treated., Paired) %>%
-#         rename(FIPS = FIPS.m.index.treated.) %>%
-#         mutate(Treatment = 1),
-#       df.matched %>%
-#         select(FIPS.m.index.control., Paired) %>%
-#         rename(FIPS = FIPS.m.index.control.) %>%
-#         mutate(Treatment = 0)) %>%
-#   rename(`Grant Number` = FIPS)
-# 
-# df.qual.exp <- inner_join(df.matched %>% select(`Grant Number`, Treatment), df.qual.exp, by = c("Grant Number")) # %>% unique()
-
-```
-
-# Figures
-
-## Prep for the robustness tests
-```{r}
-atts <- c("Primo", rep(0, 6))
-
-# cbind("Sites", round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
-#       cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-#       cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-#       cs.output.expand.agg.dyn$overall.att, 
-#       cs.output.expand.agg.dyn$overall.att - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se, 
-#       cs.output.expand.agg.dyn$overall.att + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se), 3))
-z <- c("Primo", 0) #cs.output.expand$Wpval
-
-```
-
-## Figure 0 - Demographics
-```{r}
-df.qual.exp %>% 
-  mutate(Treat = ifelse(Att > 0, 1, 0)) %>% 
-  mutate(Groups = ifelse(Treat == 1 & Expandor == 0, "Treated", 
-                  ifelse(Treat == 0 & Expandor == 0, "Control", 
-                  ifelse(Treat == 0 & Expandor == 1, "Expandor Comp", "Expandor No Comp")))) %>% 
-  filter(Year == 2015) %>%  #z & ZipFilter == 2) %>% 
-  select(Sites, Zips, #MarketShare, 
-         Total, None:MCD, IMM2yo:DepScrn, Groups, Pct.NHA:Pct.NHW, Pct.LessThan200pctFPL, Pct.Homeless:Pct.Children, `Liabilities (as pct of assets)`, `Gross land, buildings and equipment (LBE)`, `Surplus as a pct of after dep expenses`) %>% #SwitchEMR, InterOrgHITexchange, UDSQualRep.highlowuse,
-  tbl_summary(by = Groups, 
-              statistic = all_continuous() ~ "{mean} ({sd})") %>% 
-  add_p(test = everything() ~ "t.test")
-
-df.qual.exp %>% mutate(Treat = ifelse(Att > 0, 1, 0)) %>% group_by(Treat) %>% summarise(n())
-
-df.qual.exp %>% 
-  filter(Year %in% c(2015, 2016)) %>% 
-  mutate(Groups = ifelse(is.na(Personnel), "NoFins", "Fins")) %>% 
- #z & ZipFilter == 2) %>% 
-  select(Sites, Zips, #MarketShare, 
-         Total, None:MCD, #IMM2yo:DepScrn, 
-         Groups, Pct.NHA:Pct.NHW, Pct.LessThan200pctFPL, Pct.Homeless:Pct.Children) %>% #SwitchEMR, InterOrgHITexchange, UDSQualRep.highlowuse, 
-  tbl_summary(by = Groups, 
-              statistic = all_continuous() ~ "{mean} ({sd})", digits = all_continuous() ~ 2) %>% 
-  add_p(test = everything() ~ "t.test")
-
-df.qual.exp %>% 
-  mutate(Groups = ifelse(is.na(Personnel), "NoFins", "Fins")) %>% 
-  group_by(Groups) %>% 
-  summarise(n())
-
-R.version
-
-442*5
-37*5
-518/1877
-
-442+37
-
-```
-
-## Figure 1 - Trends over time
-
-```{r}
-## Plot
-p <- uds.sites[!is.na(uds.sites$Zip),] %>% 
-  select(`Grant Number`, Zip, Year) %>% 
-  unique() %>% 
-  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
-  group_by(`Grant Number`, Year) %>% 
-  summarise(Clinics = max(Clinics)) %>% 
-  group_by(Year, Clinics) %>% 
-  summarise(Count = n()) %>% 
-  mutate(CompetitorsInArea = factor(ifelse( Clinics < 4, Clinics - 1, "3+"))) %>% 
-  group_by(Year, CompetitorsInArea) %>% 
-  summarise(Count = sum(Count))
-
-plot <- p %>% 
-  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + 
-  geom_point() + geom_line() + theme_minimal() + 
-  ggtitle("Figure 1 - Counts of FQHCs by number of competing FQHCs in service area, 2014-2021") + ylab("Number of FQHCs") 
-plot + scale_color_discrete(name = "Competitors")
-
-## Table
-uds.sites[!is.na(uds.sites$Zip),] %>% 
-  select(`Grant Number`, Zip, Year) %>% 
-  unique() %>% 
-  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
-  group_by(`Grant Number`, Year) %>% 
-  summarise(Clinics = max(Clinics)) %>% 
-  group_by(Year, Clinics) %>% 
-  summarise(Count = n()) %>% 
-  mutate(CompetitorsInArea = factor(ifelse( Clinics < 4, Clinics - 1, "3+"))) %>% 
-  group_by(Year, CompetitorsInArea) %>% 
-  summarise(Count = sum(Count)) %>% 
-  pivot_wider(id_cols = CompetitorsInArea, names_from = Year, values_from = Count)
-
-plot0 <- p %>% 
-  arrange(CompetitorsInArea) %>% 
-  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
-  geom_point() + geom_line() + theme_tufte_revised() + ggtitle("FQHCs by Number of Rival Clinics") + 
-  geom_dl(label=c(rep("0 Competitors", 8), rep("1 Competitor", 8), rep("2 Competitors", 8), rep("3+ Competitors", 8)), 
-          method = list("last.points", hjust = 1, vjust = 3, cex = 0.75), inherit.aes=T ) + 
-  guides(colour = "none")
-
-plot1 <- uds.sites[!is.na(uds.sites$Zip),] %>% 
-            group_by(Zip, Year) %>% 
-  summarise(Counts = n()) %>% 
-  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
-  ungroup() %>% 
-  group_by(Year, Counts) %>% 
-  summarise(Zips = n()) %>% 
-  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
-  group_by(Counts.f, Year) %>% 
-  summarise(Zips = sum(Zips)) %>% 
-  ggplot(aes(x = Year, y = Zips, group = Counts.f, color = Counts.f)) + 
-  geom_point() + geom_line() + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
-  geom_dl(label=c(rep("1 Site", 8), rep("2+ Sites", 8)), method = list("last.points", hjust = 1, vjust = -0.5, cex = 0.75), inherit.aes=T ) + 
-  guides(colour = "none")
-
-p.desc <- ggarrange(plot1, plot0)
-
-annotate_figure(p.desc, top = text_grob("Figure 2 - FQHC Growth and Density by Zip and Clinic", face = "bold", size = 14))
-
-# rbind(uds.sites %>% 
-#   group_by(`Grant Number`, `Site Name`) %>% 
-#   summarise(Year = min(Year)) %>% 
-#   group_by(Year) %>% 
-#   summarise(Counts = n()) %>% 
-#   mutate(Type = "Opened"), 
-#   uds.sites %>% 
-#   group_by(`Grant Number`, `Site Name`) %>% 
-#   summarise(Year = max(Year)) %>% 
-#   group_by(Year) %>% 
-#   summarise(Counts = n()) %>% 
-#   mutate(Type = "Closed")) %>% 
-#   filter(Year %in% c(2015:2019))
-
-```
-
-```{r}
-
-# df.z %>% 
-#   group_by(as.factor(Att), Year) %>% 
-#   summarise(outcome = mean(Total.z, na.rm = TRUE)) %>% 
-#   ggplot(aes(x = Year, y = outcome, color = `as.factor(Att)`)) + geom_point()
-
-# 
-# cs.output.expand <- att_gt( yname = "Total.z",
-#                       tname = "Year",
-#                       idname = "ID",
-#                       gname = "Att",
-#                       xformla = ~1,
-#                       data = df.z, # %>%  group_by(`Grant Number`, Year, Att) %>% summarise(Zips = n(), ID = min(ID), Total.z = sum(Total.z, na.rm = TRUE) ), # %>% filter(Year > 2015),
-#                       control_group = "nevertreated",
-#                       clustervars = "ID",
-#                       panel = FALSE,
-#                       base_period = "universal"
-#                       )
-# aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-# 
-# 
-# cs.output.expand <- att_gt( yname = "Total.z",
-#                       tname = "Year",
-#                       idname = "ID",
-#                       gname = "Att.z",
-#                       xformla = ~1,
-#                       data = df.z %>% group_by(`Grant Number`, Year, Att, Att.z) %>% summarise(Zips = n(), ID = min(ID), Total.z = sum(Total.z, na.rm = TRUE) ) %>% filter(Att == Att.z), # %>% filter(Year > 2015),
-#                       control_group = "nevertreated",
-#                       clustervars = "ID",
-#                       panel = FALSE,
-#                       base_period = "universal"
-#                       )
-# aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-# 
-# #uds.zip %>% filter(`Grant Number` == "H80CS00030" & `Zip Code` == '48264')
-
-```
-
-## Figure 2 - Focused analysis, patient attribution in service area (where they have sites)
-```{r}
-
-## Treatment vs control, only in zip code of interest
-df.z <- left_join(df.qual.exp #%>% filter(`Grant Number` != "H80CS00225")
-                  , #uds.zip %>% mutate(Zip = `Zip Code`) %>% select(`Grant Number`, Zip) %>% unique() , by = c("Grant Number")) %>%
-                  uds.sites[!is.na(uds.sites$Zip),] %>%
-                    filter(Year %in% c(2015:2019)) %>% 
-              select(`Grant Number`, Zip) %>%
-              unique() , by = c("Grant Number")) %>%
-  left_join(uds.zip %>%
-            mutate(  Total.z = `Total Number of Patients`, 
-                     MCD.z = `Medicaid_CHIP_Other Public Patients`,
-                     MCR.z = `Medicare Patients`,
-                     COM.z = `Private Patients`, 
-                     None.z = `None_Uninsured Patients`) %>%
-            select(`Grant Number`, `Reporting Year`, `Zip Code`, Total.z:None.z), by = c("Grant Number", "Year" = "Reporting Year", "Zip" = "Zip Code")) %>%
-  left_join(clinics.in.zips %>% select(Zip:Clinics), by = c("Zip","Year")) %>%
-  mutate(Tx.z = ifelse(Clinics == 1 , 0, 
-                ifelse(is.na(Clinics), NA, 1)), # | is.na(Clinics)
-         ID = as.numeric(factor(paste(`Grant Number`, Zip, sep = "-")))) %>%
-  select(`Grant Number`:Year, ZipFilter, Att, ID, Zip:Tx.z) %>%
-  arrange(`Grant Number`, Zip, Year) %>% 
-  unique() #%>%  inner_join(df.qual.exp %>% filter(Year == 2015 & Total > 12050) %>% select(`Grant Number`), by = c("Grant Number"))  #& Zips < 3.75 or 4.75
-  # %>%   filter(MarketShare > median(MarketShare, na.rm = TRUE) - 0.25)
-
-df.z <- df.z %>%
-  left_join(df.z %>%
-            filter(Tx.z == 1) %>%
-            group_by(ID, Zip) %>%
-            summarise(Att.z = min(Year)), by = c("ID", "Zip")) %>%
-  mutate(Att.z = ifelse(is.na(Att.z), 0, Att.z)) #%>%
-# inner_join(df.z %>% filter(!is.na(Clinics)) %>% group_by(ID) %>% summarise(n()) %>% filter(`n()` == length(unique(df.qual.exp$Year))), by = c("ID")) #%>% filter(Att == Att.z)
-
-### NOTE: The aabove commented lines are very important, they decide if only the service area or whole catchment is included in analysis.  
-# cs.output.expand <- att_gt( yname = "Outcome",
-#                       tname = "Year",
-#                       idname = "ID",
-#                       gname = "Att",
-#                       xformla = ~1,
-#                       data = df.z %>% group_by(`Grant Number`, Year, Att) %>% summarise(ID = min(ID), Outcome = sum(MCD.z, na.rm = TRUE) ), # %>% filter(Year > 2015),
-#                       control_group = "nevertreated",
-#                       clustervars = "ID",
-#                       panel = TRUE,
-#                       base_period = "universal"
-#                       )
-# aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-
-## Whole zip as one measure
-
-df.z.full <- df.z %>% ############## NOTE: Original +500 effect was recoved with Att.z, not Att
-  select(Zip, ZipFilter, Att.z, Year) %>% 
-  unique() %>% 
-  left_join(uds.zip, by = c("Zip" = "Zip Code", "Year" = "Reporting Year")) %>% 
-  left_join(uds.6b.rates %>% 
-            mutate(Quality = (IMM2yo + Pap + ChildBMI + AdultBMI + Tobac + CRC + DepScrn) / 7) %>% 
-            select(GrantNumber, Year, Quality), by = c("Grant Number" = "GrantNumber", "Year")) %>% 
-  group_by(Zip, ZipFilter, Year, Att.z) %>% 
-  summarise(
-    Total.z = sum(`Total Number of Patients`, na.rm = TRUE), 
-    MCD.z = sum(`Medicaid_CHIP_Other Public Patients`, na.rm = TRUE),
-    MCR.z = sum(`Medicare Patients`, na.rm = TRUE),
-    COM.z = sum(`Private Patients`, na.rm = TRUE),
-    None.z = sum(`None_Uninsured Patients`, na.rm = TRUE), 
-    Quality.z = sum(`Total Number of Patients` * Quality, na.rm = TRUE) / Total.z) %>% 
-  ungroup() %>% 
-  mutate(ID = as.numeric(as.factor(Zip)))# %>% group_by(`Grant Number`, Year, Att) %>% summarise(ID = min(ID), Total.z = sum(Total.z, na.rm = TRUE)) # %>% filter(Year > 2015),
-
-df.zip.1 <- df.z %>% select(ID, ZipFilter, Year, Att, Total.z:None.z)
-df.zip.2 <- df.z.full %>% select(ID, ZipFilter, Year, Att.z, Total.z:Quality.z)
-
-## Start the loop
-
-for (k in 1:3){
-
-atts.zip.1 <- rep(0, 6)
-atts.zip.2 <- rep(0, 6)
-
-if (k == 1){temp.1.root <- df.zip.1
-            temp.2.root <- df.zip.2} else 
-  if (k == 2){temp.1.root <- df.zip.1 %>% filter(ZipFilter == 2)
-              temp.2.root <- df.zip.2 %>% filter(ZipFilter == 2)} else
-    if (k == 3){temp.1.root <- df.zip.1 %>% filter(ZipFilter == 1)
-                temp.2.root <- df.zip.2 %>% filter(ZipFilter == 1)}
-
-for (i in 5:9){
-
-  temp.1 <- temp.1.root[,c(1:4, i)]
-  colnames(temp.1) <- c("ID", "ZipFilter", "Year","Att","Outcome")
-
-   temp.2 <- temp.2.root[,c(1:4, i)]
-  colnames(temp.2) <- c("ID", "ZipFilter", "Year","Att","Outcome")
-
-    # Incumbent only
-cs.output.expand <- att_gt( yname = "Outcome",
-                      tname = "Year",
-                      idname = "ID",
-                      gname = "Att",
-                      xformla = ~1,
-                      data = temp.1,
-                      control_group = "nevertreated",
-                      clustervars = "ID",
-                      panel = FALSE,
-                      base_period = "universal"
-                      )
-
-cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)
-
-data.frame(Year = cs.output.expand.agg.dyn$egt,
-           Estimate = cs.output.expand.agg.dyn$att.egt,
-           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
-           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt) %>%
-  ggplot(mapping = aes(x = Year, y = Estimate)) +
-  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") +
-  geom_hline(yintercept=0, linetype = "dashed", color = "grey") +
-  geom_point() +
-  geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) +
-  ggtitle("Total Zip") +
-  theme_tufte_revised()
-
-atts.zip.1 <- rbind(atts.zip.1, 
-                    cbind(colnames(df.zip.1)[i], 
-                          round(mean(temp.1[temp.1$Att == 0 & temp.1$Year == min(temp.1$Year),]$Outcome, na.rm = TRUE), 3), 
-                          round(mean(temp.1[temp.1$Att > 0 & temp.1$Year == min(temp.1$Year),]$Outcome, na.rm = TRUE) - mean(temp.1[temp.1$Att == 0 & temp.1$Year == min(temp.1$Year),]$Outcome, na.rm = TRUE), 3),
-                          round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
-                          cs.output.expand.agg.dyn.0$overall.att - (1.96 * cs.output.expand.agg.dyn.0$overall.se), 
-                          cs.output.expand.agg.dyn.0$overall.att + (1.96 * cs.output.expand.agg.dyn.0$overall.se)), 3)))
-
-# Incumbent + Competitor
-cs.output.expand <- att_gt( yname = "Outcome",
-                      tname = "Year",
-                      idname = "ID",
-                      gname = "Att",
-                      xformla = ~1,
-                      data = temp.2, 
-                      control_group = "nevertreated",
-                      clustervars = "ID",
-                      panel = FALSE,
-                      base_period = "universal"
-                      )
-
-cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)
-
-data.frame(Year = cs.output.expand.agg.dyn$egt,
-           Estimate = cs.output.expand.agg.dyn$att.egt,
-           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
-           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt) %>%
-  ggplot(mapping = aes(x = Year, y = Estimate)) +
-  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") +
-  geom_hline(yintercept=0, linetype = "dashed", color = "grey") +
-  geom_point() +
-  geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) +
-  ggtitle("Total Zip") +
-  theme_tufte_revised()
-
-atts.zip.2 <- rbind(atts.zip.2, cbind(colnames(df.zip.2)[i], 
-                                      round(mean(temp.2[temp.2$Att == 0 & temp.2$Year == min(temp.2$Year),]$Outcome, na.rm = TRUE), 3), 
-                                      round(mean(temp.2[temp.2$Att > 0 & temp.2$Year == min(temp.2$Year),]$Outcome, na.rm = TRUE) - mean(temp.2[temp.2$Att == 0 & temp.2$Year == min(temp.2$Year),]$Outcome, na.rm = TRUE), 3),
-                                      round(cbind(cs.output.expand.agg.dyn.0$overall.att,
-      cs.output.expand.agg.dyn.0$overall.att - (1.96 * cs.output.expand.agg.dyn.0$overall.se),
-      cs.output.expand.agg.dyn.0$overall.att + (1.96 * cs.output.expand.agg.dyn.0$overall.se)), 3)))
-
-}
-
-## For the full sample only
-
-## For Larger vs Smaller FQHCs only
-if (k == 1){atts.zip.full <-  cbind(atts.zip.1[-1,], atts.zip.2[-1,]) } else 
-  if (k == 2){atts.zip.larger <- cbind(atts.zip.1[-1,], atts.zip.2[-1,])} else
-    if (k == 3){atts.zip.smaller <- cbind(atts.zip.1[-1,], atts.zip.2[-1,])}
-
-}
-
-df.zip.1 %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n(), n_distinct(ID))
-df.zip.2 %>% mutate(Treat = ifelse(Att.z > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n(), n_distinct(ID))
-
-table.names <- rbind(cbind((df.zip.1 %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[2,2], 
-            (df.zip.1 %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[1,2]), 
-      cbind((df.zip.2 %>% mutate(Treat = ifelse(Att.z > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[2,2], 
-            (df.zip.2 %>% mutate(Treat = ifelse(Att.z > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[1,2]))
-
-## Figure 2 - Full Figure
-rbind(atts.zip.full, atts.zip.larger, atts.zip.smaller) %>% 
-   kable("html", booktabs = T, col.names = c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB", "Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB")) %>%
-  kable_styling(latex_options = c("striped")) %>%
-  pack_rows(index = c("Full Sample" = 5, "More Market Share Only" = 5, "Less Market Share Only" = 5)) %>% 
-  add_header_above(c(" " = 1, "Incumbent vs Controls (FQHC-Zip units)" = 6, "Incumbent & Competitor vs Controls (zip units)" = 6)) %>% 
-  add_footnote(c("C_0 and T_0 are mean values for each sample in control and treatment groups in first year of panel",
-                 paste("Full Sample Incumbent vs Control has ", table.names[1,1], "treatment and ", table.names[1,2], " control FQHC-Zip-Years"), 
-                 paste("Full Sample Incumbent & Control vs Control has ", table.names[2,1], "treatment and ", table.names[2,2], " control Zip-Years")))
-
-cbind(rep(c("Total","Medicaid","Medicare","Commerical","Uninsured"), 3), rbind(atts.zip.full, atts.zip.larger, atts.zip.smaller)[,2:6]) %>% 
-   kable("html", booktabs = T, col.names = c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB")) %>%
-  kable_styling(latex_options = c("striped")) %>%
-  row_spec(c(1, 2, 6, 7, 10, 11, 12),bold=T, italic = T, hline_after = T) %>% 
-  pack_rows(index = c("Panel A: Full Sample" = 5, "Panel B: Higher Low-Income Market Share Subgroup" = 5, "Panel B: Lower Low-Income Market Share Subgroup" = 5)) %>% 
-  add_footnote(c("C_0 and T_0 are mean values for each sample in control and treatment groups in first year of panel",
-                 paste("Full Sample Incumbent vs Control has ", table.names[1,1], "treatment and ", table.names[1,2], " control FQHC-Zip-Years"), 
-                 paste("Full Sample Incumbent & Control vs Control has ", table.names[2,1], "treatment and ", table.names[2,2], " control Zip-Years")))
-
-```
-
-## Nicer Table
-
-```{r}
-df.zip.1 %>% 
-  filter(Year %in% c(2016, 2019)) %>% 
-  mutate(Tx = ifelse(Att > 0, 1, 0)) %>% 
-  group_by(Year, Tx) %>% 
-  summarise(mean(Total.z, na.rm = TRUE), 
-            mean(MCD.z, na.rm = TRUE), 
-            mean(MCR.z, na.rm = TRUE), 
-            mean(COM.z, na.rm = TRUE), 
-            mean(None.z, na.rm = TRUE)) %>% 
-  arrange(Tx, Year) %>% 
-  t() %>% 
-  as.data.frame() %>% 
-  mutate(unadj = (V4 - V3) - (V2 - V1) )
-
-cbind(c("Total","Medicaid","Medicare","Commerical","Uninsured"), atts.zip.full[,2:6]) %>% 
-   kable("html", booktabs = T, col.names = c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB")) %>%
-  kable_styling(latex_options = c("striped")) %>%
-  row_spec(c(1, 2),bold=T, italic = T, hline_after = T) %>% 
-  #pack_rows(index = c("Panel A: Full Sample" = 5, "Panel B: Higher Low-Income Market Share Subgroup" = 5, "Panel B: Lower Low-Income Market Share Subgroup" = 5)) %>% 
-  add_footnote(c("C_0 and T_0 are mean values for each sample in control and treatment groups in first year of panel",
-                 paste("Full Sample Incumbent vs Control has ", table.names[1,1], "treatment and ", table.names[1,2], " control FQHC-Zip-Years"), 
-                 paste("Full Sample Incumbent & Control vs Control has ", table.names[2,1], "treatment and ", table.names[2,2], " control Zip-Years")))
-```
-
-## Look at the Market as a whole
-
-```{r}
-
-df.market <- df.z.full %>% #filter(ZipFilter == 1)
-                        left_join(df.z %>% select(`Grant Number`,Zip) %>% unique(), by = c("Zip")) %>% 
-  mutate(V1 = 1, V2 = ifelse(ZipFilter == 2, 1, 0), V3 = ifelse(ZipFilter == 1, 1, 0)) %>% 
-                       select(Year, ID, Att.z, Quality.z, `Grant Number`, Total.z:None.z, V1:V3) %>%
-  # inner_join(df.qual.exp %>% filter(Year == 2015) %>%
-  #                                           mutate(ZipFilter = ifelse(Total < 12000, 1,
-  #                                                              ifelse(Total > 12000, 2, NA))) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
-  inner_join(df.qual.exp %>% filter(Year == 2016) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
-  select(Year, ZipFilter, ID, Att.z, Quality.z, Total.z:None.z, V1:V3) %>% 
-  mutate(V4 = ifelse(ZipFilter == 2, 1, 0), V5 = ifelse(ZipFilter == 1, 1, 0)) %>% 
-  unique()
-
-### Incumbnet + Competitors, Quality 
-cs.output.expand <- att_gt( yname = "Quality.z",
-                      tname = "Year",
-                      idname = "ID",
-                      gname = "Att.z",
-                      xformla = ~1,
-                      data = df.market %>% filter(V5 == 1), 
-                      control_group = "nevertreated",
-                      clustervars = "ID",
-                      panel = TRUE,
-                      base_period = "universal"
-                      )
-
-cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)
-
-data.frame(Year = cs.output.expand.agg.dyn$egt,
-           Estimate = cs.output.expand.agg.dyn$att.egt,
-           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
-           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt) %>%
-  ggplot(mapping = aes(x = Year, y = Estimate)) +
-  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") +
-  geom_hline(yintercept=0, linetype = "dashed", color = "grey") +
-  geom_point() +
-  geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) +
-  ggtitle("Total Change in Market Quality") +
-  theme_tufte_revised()
-
-```
-
-## Figure 2 plots that are nicer
-```{r}
-
-## Plot of this shit, all payors
-f2.picture.full <- rbind(rbind(atts.zip.full, atts.zip.larger, atts.zip.smaller)[,c(1:6)]) %>%  #, rbind(atts.zip.full, atts.zip.larger, atts.zip.smaller)[,c(7:12)]) %>% 
-  as.data.frame() %>% 
-  mutate(Model = c(rep("Incumbent Only", 3*5)), #, rep("Incumbent & Competitor", 3*5)), 
-         Sample = rep(c(rep("Full Sample", 5), rep("More Market Share", 5), rep("Less Market Share", 5)), 1))
-
-#### Clean up the data
-row.names(f2.picture.full) <- NULL
-colnames(f2.picture.full) <- c("Payor", "C_0", "T_0 - C_0", "Estimate", "LB", "UB", "Model","Sample")
-f2.picture.full[,4:6] <- sapply(f2.picture.full[,4:6], as.numeric)
-f2.picture.full$Sample <- factor(f2.picture.full$Sample, levels = c("Full Sample", "More Market Share","Less Market Share"))
-f2.picture.full$Payor <- gsub(f2.picture.full$Payor, pattern = ".z", replacement = "")
-f2.picture.full$Payor <- factor(f2.picture.full$Payor, levels = c("None", "MCR","COM","MCD","Total"))
-f2.picture.full$Model <- factor(f2.picture.full$Model, levels = c("Incumbent Only","Incumbent & Competitor"))
-f2.picture.full$Total <- ifelse(f2.picture.full$Payor == "Total", "Total", "Payor")
-f2.picture.full$Total <- factor(f2.picture.full$Total, levels = c("Total","Payor"))
-
-### Plot
-f2.p.totals.inc <- ggplot(data=f2.picture.full #%>% filter(Sample == "Full Sample")
-                          , aes(y=Payor, x=Estimate, xmin=LB, xmax=UB)) +
-geom_point() +
-
-#this changes the features of the overall effects
-#one could resize, reshape, or recolor these points if desired
-xlab("DID Estimates - Patients") + 
-ylab(NULL) + 
-#adds the CIs
-geom_errorbarh(height=.1) +
-
-#sets the scales
-#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
-#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
-#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
-
-#adding a vertical line at the effect = 0 mark
-geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
-
-#faceting based on my subgroups
-  #facet_wrap(~X1) +
-facet_grid(Total~Sample, scales= "free_y", switch = 'y', space = "free_y")+
-
-#thematic stuff
-#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
-theme_tufte_revised()+
-   theme(strip.placement = "outside") +
-#theme(text=element_text(family="Times",size=12, color="black"))+
-theme(panel.spacing = unit(1, "lines")) +
-  ggtitle("Figure 3, CS-DID Estimates on Patient Panel and Payor (FQHC-zip-year units)")
-
-f2.p.totals.inc #+ theme(panel.spacing = unit(1, "lines"),  title =  element_text(face = "bold", size = 12))
-
-```
-
-## Figure 3 - Primary Results
-
-```{r}
-
-df.sum <- df.qual.exp %>% #filter(`Grant Number` != "H80CS00225") %>%
-
-  ungroup() %>% 
-  #filter(MarketShare < median(MarketShare, na.rm = TRUE) - 0.25) %>% 
-  #inner_join(df.qual.exp %>% filter(Year == 2015 & Total < 12000) %>% select(`Grant Number`), by = c("Grant Number")) %>%  #& Zips < 3.75 or 4.75
-  # select(`Grant Number`, Year, ID, Att, Sites, Qcomp, Altmans.Z) %>%
-  # inner_join(df.qual.exp %>% filter(Year == 2015) %>% mutate(ZipFilter = ifelse(Zips < 1.75, 1, 
-  #                                                                        ifelse(Zips > 4.75, 2, NA))) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
-  select(Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z)
-
-for (k in 1:3){
-
-atts.sum <- rep(0, 7)
-fig3.sum <- rep(0, 5)
-
-if (k ==1){df.sum.root <- df.sum} else
-  if (k == 2){df.sum.root <- df.sum %>% filter(ZipFilter == 2)} else
-    if (k == 3){df.sum.root <- df.sum %>% filter(ZipFilter == 1)}
-
-for (i in 5:ncol(df.sum)){
-
-  temp <- df.sum.root[,c(1:4, i)]
-  colnames(temp) <- c("Year", "ZipFilter", "ID","Att", "Outcome")
-  temp$Outcome
-
-  # temp <- temp %>%
-  #   mutate(Outcome = ifelse(Outcome < quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1],
-  #                    ifelse(Outcome > quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], Outcome)))
-
-cs.output.expand <- att_gt( yname = "Outcome",
-                      tname = "Year",
-                      idname = "ID",
-                      gname = "Att",
-                      xformla = ~1,
-                      data = temp, # %>% filter(Year >= 2015 & Year <= 2020), 
-                      control_group = "nevertreated",
-                      clustervars = "ID",
-                      panel = FALSE, 
-                      base_period = "universal"
-                      )
-cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)
-
-atts.sum <- rbind(atts.sum, cbind(colnames(df.sum)[i], round(mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(mean(temp[temp$Att > 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE) - mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(cbind(cs.output.expand.agg.dyn.0$overall.att,
-      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se), 3)))
-
-atts <- rbind(atts, cbind(colnames(df.sum)[i], round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
-      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-      cs.output.expand.agg.dyn$overall.att, 
-      cs.output.expand.agg.dyn$overall.att - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se, 
-      cs.output.expand.agg.dyn$overall.att + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se), 3)))
-z <- rbind(z, c(colnames(df.sum)[i], cs.output.expand$Wpval))
-
-fig3.sum <- rbind(fig3.sum, 
-                 data.frame(Outcome = colnames(df.sum)[i], 
-                      Year = cs.output.expand.agg.dyn$egt, 
-           Estimate = cs.output.expand.agg.dyn$att.egt, 
-           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
-           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt))
-}
-
-rownames(fig3.sum) <- NULL
-if (k == 1){atts.sum.full <- atts.sum[-1,]} else 
- if (k == 2){atts.sum.larger <- atts.sum[-1,]} else 
-   {atts.sum.smaller <- atts.sum[-1,]}
-
-}
-
-#Event Study Plots
-fig3.sum[-1,] %>%
-  ggplot(mapping = aes(x = Year, y = Estimate)) +
-  facet_wrap(~Outcome, scales = "free_y") +
-  ylab("Percentage Points") +
-  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") +
-  geom_hline(yintercept=0, linetype = "dashed", color = "grey") +
-  geom_point() + geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) +
-  ggtitle("fig3 - Event Study") +
-  theme_tufte_revised()
-
-table.names <- rbind(cbind((df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[2,2], 
-            (df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[1,2]), 
-      cbind((df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[4,3], 
-            (df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[3,3]), 
-      cbind((df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[2,3], 
-            (df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[1,3]))
-
-## Table
-rbind(atts.sum.full, atts.sum.larger, atts.sum.smaller) %>% 
-   kable("html", booktabs = T, col.names = c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB"), caption = "Fig 3 - FQHC Responses by Market Share") %>%
-  kable_styling(latex_options = c("striped")) %>%
-  pack_rows(index = c("Full" = 3, "Above Median Market Share FQHCs" = 3, "Below Median Market Share FQHCs" = 3)) %>% 
-  add_footnote(c("Atlman's Z is a measure of Financial Distress",
-                 "C_0 and T_0 are mean values for each sample in control and treatment groups in first year of panel",
-                 paste("Full Sample has ", table.names[1,1], "treatment and ", table.names[1,2], " control FQHC-Years")))
-
-## Better Figure
-f3.picture.full <- rbind(cbind("Full Sample", atts.sum.full), cbind("More Market Share", atts.sum.larger), cbind("Less Market Share", atts.sum.smaller) ) %>% 
-  as.data.frame()
-
-### Clean up the data
-row.names(f3.picture.full) <- NULL
-colnames(f3.picture.full) <- c("MarketShare", "Measure", "C_0", "T_0 - C_0", "Estimate", "LB", "UB")
-f3.picture.full[,3:7] <- sapply(f3.picture.full[,3:7], as.numeric)
-f3.picture.full$MarketShare <- factor(f3.picture.full$MarketShare, levels = c("Full Sample", "More Market Share","Less Market Share"))
-# f3.picture.full$Payor <- gsub(f3.picture.full$Payor, pattern = ".z", replacement = "")
-# f3.picture.full$Payor <- factor(f3.picture.full$Payor, levels = c("None", "MCR","COM","MCD","Total"))
-# f3.picture.full$Model <- factor(f3.picture.full$Model, levels = c("Incumbent Only","Incumbent & Competitor"))
-# f3.picture.full$Total <- ifelse(f3.picture.full$Payor == "Total", "Total", "Payor")
-# f3.picture.full$Total <- factor(f3.picture.full$Total, levels = c("Total","Payor"))
-
-### Plot
-f3.p.totals.full <- ggplot(data=f3.picture.full, aes(y=Measure, x=Estimate, xmin=LB, xmax=UB)) +
-geom_point() +
-
-#this changes the features of the overall effects
-#one could resize, reshape, or recolor these points if desired
-xlab("DID Estimates") + 
-ylab(NULL) + 
-#adds the CIs
-geom_errorbarh(height=.1) +
-
-#sets the scales
-#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
-#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
-#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
-
-#adding a vertical line at the effect = 0 mark
-geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
-
-#faceting based on my subgroups
-  #facet_wrap(~X1) +
-facet_grid(~MarketShare, scales= "free", switch = 'y', space = "free_y")+
-
-#thematic stuff
-#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
-theme_tufte_revised()+
-   theme(strip.placement = "outside") +
-#theme(text=element_text(family="Times",size=12, color="black"))+
-theme(panel.spacing = unit(1, "lines")) +
-  ggtitle("Figure 3, FQHC Performance Reactions by Market Share")
-
-f3.p.totals.full
-
-```
-
-## Figure 4 - Split by profitability
-```{r}
-
-df.sum <- df.qual.exp %>% #filter(`Grant Number` != "H80CS00225") %>% 
-  ungroup() %>% 
-  #rename(`Grant Number` = Grant.Number, `Surplus as a pct of before dep expenses` = Surplus.as.a.pct.of.after.dep.expenses) %>% 
-  #filter(MarketShare < 0.4) %>%  #median(MarketShare, na.rm = TRUE) - 0.25
-  #inner_join(df.qual.exp %>% filter(Year == 2015 & Total < 15000) %>% select(`Grant Number`), by = c("Grant Number")) %>%  #& Zips < 1.75 or 7.75
-  select(`Grant Number`, Year, ID, Att, Sites, Qcomp, Altmans.Z) %>%
-  # inner_join(df.qual.exp %>% filter(Year == 2015) %>%
-  #                                           mutate(ZipFilter = ifelse(Total < 12000, 1,
-  #                                                              ifelse(Total > 12000, 2, NA))) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
-  inner_join(df.qual.exp %>% filter(Year == 2016) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
-  select(Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z) %>% 
-  unique()
-
-#summary(df.qual.exp[df.qual.exp$Year == 2015,]$Qcomp)
-
-for (k in 2:3){
-
-atts.sum <- rep(0, 7)
-fig4.sum <- rep(0, 5)
-
-if (k ==1){df.sum.root <- df.sum} else
-  if (k == 2){df.sum.root <- df.sum %>% filter(ZipFilter == 2)} else
-    if (k == 3){df.sum.root <- df.sum %>% filter(ZipFilter == 1)}
-
-for (i in 5:ncol(df.sum)){
-
-  temp <- df.sum.root[,c(1:4, i)]
-  colnames(temp) <- c("Year", "ZipFilter", "ID","Att", "Outcome")
-  temp$Outcome
-
-  # temp <- temp %>%
-  #   mutate(Outcome = ifelse(Outcome < quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1],
-  #                    ifelse(Outcome > quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], Outcome)))
-
-cs.output.expand <- att_gt( yname = "Outcome",
-                      tname = "Year",
-                      idname = "ID",
-                      gname = "Att",
-                      xformla = ~1,
-                      data = temp , 
-                      control_group = "nevertreated",
-                      clustervars = "ID",
-                      panel = FALSE, 
-                      base_period = "universal"
-                      )
-cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)
-
-atts.sum <- rbind(atts.sum, cbind(colnames(df.sum)[i], round(mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(mean(temp[temp$Att > 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE) - mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(cbind(cs.output.expand.agg.dyn.0$overall.att,
-      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se), 3)))
-
-atts <- rbind(atts, cbind(colnames(df.sum)[i], round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
-      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-      cs.output.expand.agg.dyn$overall.att, 
-      cs.output.expand.agg.dyn$overall.att - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se, 
-      cs.output.expand.agg.dyn$overall.att + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se), 3)))
-z <- rbind(z, c(colnames(df.sum)[i], cs.output.expand$Wpval))
-
-fig4.sum <- rbind(fig4.sum, 
-                 data.frame(Outcome = colnames(df.sum)[i], 
-                      Year = cs.output.expand.agg.dyn$egt, 
-           Estimate = cs.output.expand.agg.dyn$att.egt, 
-           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
-           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt))
-}
-
-rownames(fig4.sum) <- NULL
-if (k == 1){atts.sum.full <- atts.sum[-1,]} else 
- if (k == 2){atts.sum.larger <- atts.sum[-1,]} else 
-   {atts.sum.smaller <- atts.sum[-1,]}
-
-}
-
-#Event Study Plots
-fig4.sum[-1,] %>%
-  ggplot(mapping = aes(x = Year, y = Estimate)) +
-  facet_wrap(~Outcome, scales = "free_y") +
-  ylab("Percentage Points") +
-  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") +
-  geom_hline(yintercept=0, linetype = "dashed", color = "grey") +
-  geom_point() + geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) +
-  ggtitle("fig4 - Event Study") +
-  theme_tufte_revised()
-
-table.names <- rbind(cbind((df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[2,2], 
-            (df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(Treat) %>% summarise(n()))[1,2]), 
-      cbind((df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[4,3], 
-            (df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[3,3]), 
-      cbind((df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[2,3], 
-            (df.sum %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n()))[1,3]))
-
-## Table
-rbind(atts.sum.larger, atts.sum.smaller) %>% 
-   kable("html", booktabs = T, col.names = c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB")) %>%
-  kable_styling(latex_options = c("striped")) %>%
-  pack_rows(index = c("Profitable FQHCs" = 3, "Unprofitable/Budget Neutral FQHCs" = 3)) %>% 
-  add_footnote(c("Atlman's Z is a measure of Financial Distress",
-                 "C_0 and T_0 are mean values for each sample in control and treatment groups in first year of panel",
-                 paste("Profitable FQHCs Sample has ", table.names[2,1], "treatment and ", table.names[2,2], " control FQHC-Years"), 
-                 paste("Unprofitable and Budget Neutral FQHCs Sample has ", table.names[3,1], "treatment and ", table.names[3,2], " control FQHC-Years")))
-
-## Better Figure
-f4.picture.full <- rbind(cbind("Full Sample", atts.sum.full), cbind("Profitable", atts.sum.larger), cbind("Unprofitable/Budget Neutral", atts.sum.smaller) ) %>% 
-  as.data.frame()
-
-### Clean up the data
-row.names(f4.picture.full) <- NULL
-colnames(f4.picture.full) <- c("Profitability", "Measure", "C_0", "T_0 - C_0", "Estimate", "LB", "UB")
-f4.picture.full[,3:7] <- sapply(f4.picture.full[,3:7], as.numeric)
-# f4.picture.full$Sample <- factor(f4.picture.full$Sample, levels = c("Full Sample", "More Market Share","Less Market Share"))
-# f4.picture.full$Payor <- gsub(f4.picture.full$Payor, pattern = ".z", replacement = "")
-# f4.picture.full$Payor <- factor(f4.picture.full$Payor, levels = c("None", "MCR","COM","MCD","Total"))
-# f4.picture.full$Model <- factor(f4.picture.full$Model, levels = c("Incumbent Only","Incumbent & Competitor"))
-# f4.picture.full$Total <- ifelse(f4.picture.full$Payor == "Total", "Total", "Payor")
-# f4.picture.full$Total <- factor(f4.picture.full$Total, levels = c("Total","Payor"))
-
-### Plot
-f4.p.totals.full <- ggplot(data=f4.picture.full, aes(y=Measure, x=Estimate, xmin=LB, xmax=UB)) +
-geom_point() +
-
-#this changes the features of the overall effects
-#one could resize, reshape, or recolor these points if desired
-xlab("DID Estimates") + 
-ylab(NULL) + 
-#adds the CIs
-geom_errorbarh(height=.1) +
-
-#sets the scales
-#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
-#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
-#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
-
-#adding a vertical line at the effect = 0 mark
-geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
-
-#faceting based on my subgroups
-  #facet_wrap(~X1) +
-facet_grid(~Profitability, scales= "free", switch = 'y', space = "free_y")+
-
-#thematic stuff
-#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
-theme_tufte_revised()+
-   theme(strip.placement = "outside") +
-#theme(text=element_text(family="Times",size=12, color="black"))+
-theme(panel.spacing = unit(1, "lines")) +
-  ggtitle("Figure 4, FQHC Performance Reactions by Profitability")
-
-f4.p.totals.full
-```
-
-## True Figure 3 - Responses
-```{r}
-
-fig3 <- rbind(f3.picture.full %>% rename(Subgroup = MarketShare), f4.picture.full[-c(1:3),] %>% rename(Subgroup = Profitability)) %>% 
-  mutate(Measure = ifelse(Measure == "Sites", "Number of Sites", 
-                   ifelse(Measure == "Qcomp", "Quality of Care", 
-                   ifelse(Measure == "Altmans.Z", "Financial Stability", NA))))
-
-f3.full <- ggplot(data=fig3[1:3,], aes(y=Measure, x=Estimate, xmin=LB, xmax=UB)) +
-  geom_point() +
-
-#this changes the features of the overall effects
-#one could resize, reshape, or recolor these points if desired
-xlab("DID Estimates") + 
-ylab(NULL) + 
-#adds the CIs
-geom_errorbarh(height=.1) +
-
-#sets the scales
-#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
-#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
-#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
-
-#adding a vertical line at the effect = 0 mark
-geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
-
-#faceting based on my subgroups
-  #facet_wrap(~X1) +
-facet_grid(~Subgroup, scales= "free", switch = 'y', space = "free_y")+
-
-#thematic stuff
-#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
-theme_tufte_revised()+
-   theme(strip.placement = "outside") +
-#theme(text=element_text(family="Times",size=12, color="black"))+
-theme(panel.spacing = unit(1, "lines"))
-
-f3.mark <- ggplot(data=fig3[4:9,], aes(y=Measure, x=Estimate, xmin=LB, xmax=UB)) +
-  geom_point() +
-
-#this changes the features of the overall effects
-#one could resize, reshape, or recolor these points if desired
-xlab("DID Estimates") + 
-ylab(NULL) + 
-#adds the CIs
-geom_errorbarh(height=.1) +
-
-#sets the scales
-#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
-#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
-#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
-
-#adding a vertical line at the effect = 0 mark
-geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
-
-#faceting based on my subgroups
-  #facet_wrap(~X1) +
-facet_grid(~Subgroup, scales= "free", switch = 'y', space = "free_y")+
-
-#thematic stuff
-#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
-theme_tufte_revised()+
-   theme(strip.placement = "outside") +
-#theme(text=element_text(family="Times",size=12, color="black"))+
-theme(panel.spacing = unit(1, "lines"))
-
-f3.prof <- ggplot(data=fig3[10:15,], aes(y=Measure, x=Estimate, xmin=LB, xmax=UB)) +
-  geom_point() +
-
-#this changes the features of the overall effects
-#one could resize, reshape, or recolor these points if desired
-xlab("DID Estimates") + 
-ylab(NULL) + 
-#adds the CIs
-geom_errorbarh(height=.1) +
-
-#sets the scales
-#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
-#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
-#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
-
-#adding a vertical line at the effect = 0 mark
-geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
-
-#faceting based on my subgroups
-  #facet_wrap(~X1) +
-facet_grid(~Subgroup, scales= "free", switch = 'y', space = "free_y")+
-
-#thematic stuff
-#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
-theme_tufte_revised()+
-   theme(strip.placement = "outside") +
-#theme(text=element_text(family="Times",size=12, color="black"))+
-theme(panel.spacing = unit(1, "lines"))
-
-gt <- grid.arrange(f3.full,                            
-             f3.mark, f3.prof,                         
-             ncol = 3, nrow = 2, 
-             layout_matrix = rbind(c(1,  2, 2), c(1,  3, 3)))
-
-# Add labels to the arranged plots
-p <- as_ggplot(gt) +                                # transform to a ggplot
- draw_plot_label(label = c("Panel A", "Panel B", "Panel C"), size = 15,
-                 x = c(0, 0.33, 0.33), y = c(1, 1, 0.5)) # Add labels
-p
-
-```
-
-## Figure for Paper
-
-```{r}
-df.qual.exp %>% 
-  filter(Year %in% c(2016, 2019)) %>% 
-  mutate(Tx = ifelse(Att > 0, 1, 0)) %>% 
-  group_by(Year, Tx) %>% 
-  summarise(mean(Sites, na.rm = TRUE), 
-            mean(Qcomp, na.rm = TRUE), 
-            mean(Altmans.Z, na.rm = TRUE), 
-            mean(Efficiency, na.rm = TRUE)) %>% 
-  arrange(Tx, Year) %>% 
-  t() %>% 
-  as.data.frame() %>% 
-  mutate(unadj = (V4 - V3) - (V2 - V1) )
-```
-
-## Figure for Poster
-
-```{r}
-
-poster.fig3 <- cbind(Group = c(rep("Panel A", 3),rep("Panel B", 6),rep("Panel C", 6)), fig3) %>% 
-  mutate(Measure = as.factor(Measure)) %>% 
-  mutate(Measure = fct_reorder(Measure, desc(Measure))) %>%
-
-ggplot(aes(y=Subgroup, x=Estimate, xmin=LB, xmax=UB)) +
-geom_point() +
-
-#this changes the features of the overall effects
-#one could resize, reshape, or recolor these points if desired
-xlab("DID Estimates") + 
-ylab(NULL) + 
-#adds the CIs
-geom_errorbarh(height=.1) +
-
-#sets the scales
-#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
-#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
-#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
-
-#adding a vertical line at the effect = 0 mark
-geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
-
-#faceting based on my subgroups
-  #facet_wrap(~X1) +
-facet_grid(Group~Measure, scales = "free", switch = 'y', space = "free_y")+
-
-#thematic stuff
-#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
-theme_tufte_revised()+
-   theme(strip.placement = "outside") +
-#theme(text=element_text(family="Times",size=12, color="black"))+
-theme(panel.spacing = unit(1, "lines"),  strip.text =  element_text(face = "bold", size = 16))
-
-poster.fig3
-```
-
-## Figure 5 - Financing
-
-```{r}
-
-df.comp <- df.qual.exp %>% #filter(`Grant Number` != "H80CS00225") %>% 
-  ungroup() %>% 
-  #inner_join(df.qual.exp %>% filter(Year == 2015 & Zips < 4.75) %>% select(`Grant Number`), by = c("Grant Number")) %>%  #& Zips < 3.75 or 4.75
-  #filter(MarketShare > median(MarketShare, na.rm = TRUE)) %>% 
-    select(Year, ZipFilter, ID, Att, `Total revenue (unrestricted & restricted)`, `Total net assets`, `Surplus as a pct of before dep expenses`, 
-           `Staffing`, `Liabilities`, `Gross land, buildings and equipment (LBE)`, Liquidity, Profitability, Efficiency, NetWorth)
-
-for (k in 1:3){
-
-atts.comp <- rep(0, 7)
-fig3.comp <- rep(0, 5)
-
-if (k ==1){df.comp.root <- df.comp} else
-  if (k == 2){df.comp.root <- df.comp %>% filter(ZipFilter == 2)} else
-    if (k == 3){df.comp.root <- df.comp %>% filter(ZipFilter == 1)}
-
-for (i in 5:ncol(df.comp)){
-
- # if (i %in% c(6, 7, 19)){temp <- df.comp.root[df.comp.root$Year %in% c(2015:2019), c(1:4, i)]} else {temp <- df.comp.root[,c(1:4, i)]}
-  temp <- df.comp.root[,c(1:4, i)]
-  #temp <- df.comp.root[df.comp.root$Year %in% c(2015:2019), c(1:4, i)]
-  colnames(temp) <- c("Year", "ZipFilter", "ID","Att", "Outcome")
-  temp$Outcome
-
-  # temp <- temp %>%
-  #   mutate(Outcome = ifelse(Outcome < quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1],
-  #                    ifelse(Outcome > quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], Outcome)))
-
-cs.output.expand <- att_gt( yname = "Outcome",
-                      tname = "Year",
-                      idname = "ID",
-                      gname = "Att",
-                      xformla = ~1,
-                      data = temp, # %>% filter(Year >= 2016), 
-                      control_group = "nevertreated",
-                      clustervars = "ID",
-                      panel = FALSE, 
-                      base_period = "universal"
-                      )
-cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)
-
-atts.comp <- rbind(atts.comp, cbind(colnames(df.comp)[i], round(mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(mean(temp[temp$Att > 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE) - mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(cbind(cs.output.expand.agg.dyn.0$overall.att,
-      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se), 3)))
-
-atts <- rbind(atts, cbind(colnames(df.comp)[i], round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
-      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-      cs.output.expand.agg.dyn$overall.att, 
-      cs.output.expand.agg.dyn$overall.att - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se, 
-      cs.output.expand.agg.dyn$overall.att + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se), 3)))
-z <- rbind(z, c(colnames(df.comp)[i], cs.output.expand$Wpval))
-
-fig3.comp <- rbind(fig3.comp, 
-                 data.frame(Outcome = colnames(df.comp)[i], 
-                      Year = cs.output.expand.agg.dyn$egt, 
-           Estimate = cs.output.expand.agg.dyn$att.egt, 
-           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
-           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt))
-}
-
-rownames(fig3.comp) <- NULL
-if (k == 1){atts.comp.full <- atts.comp[-1,]} else 
- if (k == 2){atts.comp.larger <- atts.comp[-1,]} else 
-   {atts.comp.smaller <- atts.comp[-1,]}
-
-}
-
-#Event Study Plots
-fig3.comp[-1,] %>%
-  ggplot(mapping = aes(x = Year, y = Estimate)) +
-  facet_wrap(~Outcome, scales = "free_y") +
-  ylab("Percentage Points") +
-  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") +
-  geom_hline(yintercept=0, linetype = "dashed", color = "grey") +
-  geom_point() + geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) +
-  ggtitle("fig3 - Event Study") +
-  theme_tufte_revised()
-
- cbind(atts.comp.full, atts.comp.larger, atts.comp.smaller) %>% 
-   kable("html", booktabs = T, col.names = rep(c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB"), 3)) %>%
-  kable_styling(latex_options = c("striped")) %>%
-  #pack_rows(index = c("Financial" = 5, "" = 5, "Profitability" = 5)) %>% 
-  add_header_above(c(" " = 1, "Full" = 6, "More Market Share Clinics" = 6, "Less Market Share Clinics" = 6)) %>% 
-  #pack_rows(index = c("Larger FQHCs" = 15, "Smaller FQHCs" = 15)) %>% 
-  add_footnote(c(""))
-
-```
-
-## Figure 5 - Financing these changes
-
-```{r}
-
-df.fin <- df.qual.exp %>% #filter(`Grant Number` != "H80CS00225") %>% 
-  ungroup() %>% 
-  #filter(MarketShare > median(MarketShare, na.rm = TRUE)) %>% 
-  select(`Grant Number`, Year, ID, Att, `Total revenue (unrestricted & restricted)`, `Total net assets`, `Surplus as a pct of before dep expenses`, 
-           `Staffing`, `Liabilities`, `Gross land, buildings and equipment (LBE)`, Liquidity, Profitability, Efficiency, NetWorth) %>%
-  inner_join(df.qual.exp %>% filter(Year == 2016) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
-    select(Year, ZipFilter, ID, Att, `Total revenue (unrestricted & restricted)`, `Total net assets`, `Surplus as a pct of before dep expenses`, 
-           `Staffing`, `Liabilities`, `Gross land, buildings and equipment (LBE)`, Liquidity, Profitability, Efficiency, NetWorth)
-
-for (k in 1:3){
-
-atts.fin <- rep(0, 7)
-fig3.fin <- rep(0, 5)
-
-if (k ==1){df.fin.root <- df.fin} else
-  if (k == 2){df.fin.root <- df.fin %>% filter(ZipFilter == 2)} else
-    if (k == 3){df.fin.root <- df.fin %>% filter(ZipFilter == 1)}
-
-for (i in 5:ncol(df.fin)){
-
-  temp <- df.fin.root[,c(1:4, i)]
-  #temp <- df.fin.root[df.fin.root$Year %in% c(2015:2019), c(1:4, i)]
-  colnames(temp) <- c("Year", "ZipFilter", "ID","Att", "Outcome")
-  temp$Outcome
-
-  # temp <- temp %>%
-  #   mutate(Outcome = ifelse(Outcome < quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[1],
-  #                    ifelse(Outcome > quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], quantile(temp$Outcome, probs = c(0.05, 0.95), na.rm = TRUE)[2], Outcome)))
-
-cs.output.expand <- att_gt( yname = "Outcome",
-                      tname = "Year",
-                      idname = "ID",
-                      gname = "Att",
-                      xformla = ~1,
-                      data = temp, # %>% filter(Year >= 2016), 
-                      control_group = "nevertreated",
-                      clustervars = "ID",
-                      panel = FALSE, 
-                      base_period = "universal"
-                      )
-cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)
-
-atts.fin <- rbind(atts.fin, cbind(colnames(df.fin)[i], round(mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(mean(temp[temp$Att > 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE) - mean(temp[temp$Att == 0 & temp$Year == min(temp$Year),]$Outcome, na.rm = TRUE), 3), round(cbind(cs.output.expand.agg.dyn.0$overall.att,
-      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se), 3)))
-
-atts <- rbind(atts, cbind(colnames(df.fin)[i], round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
-      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-      cs.output.expand.agg.dyn$overall.att, 
-      cs.output.expand.agg.dyn$overall.att - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se, 
-      cs.output.expand.agg.dyn$overall.att + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se), 3)))
-z <- rbind(z, c(colnames(df.fin)[i], cs.output.expand$Wpval))
-
-fig3.fin <- rbind(fig3.fin, 
-                 data.frame(Outcome = colnames(df.fin)[i], 
-                      Year = cs.output.expand.agg.dyn$egt, 
-           Estimate = cs.output.expand.agg.dyn$att.egt, 
-           CILB = cs.output.expand.agg.dyn$att.egt - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt,
-           CIUB = cs.output.expand.agg.dyn$att.egt + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$se.egt))
-}
-
-rownames(fig3.fin) <- NULL
-if (k == 1){atts.fin.full <- atts.fin[-1,]} else 
- if (k == 2){atts.fin.larger <- atts.fin[-1,]} else 
-   {atts.fin.smaller <- atts.fin[-1,]}
-
-}
-
-#Event Study Plots
-fig3.fin[-1,] %>%
-  ggplot(mapping = aes(x = Year, y = Estimate)) +
-  facet_wrap(~Outcome, scales = "free_y") +
-  ylab("Percentage Points") +
-  geom_vline(xintercept=-0.5, linetype = "dashed", color = "red") +
-  geom_hline(yintercept=0, linetype = "dashed", color = "grey") +
-  geom_point() + geom_errorbar(aes(ymin=CILB, ymax=CIUB), width=.2) +
-  ggtitle("fig3 - Event Study") +
-  theme_tufte_revised()
-
- cbind(atts.fin.full, atts.fin.larger, atts.fin.smaller) %>% 
-   kable("html", booktabs = T, col.names = rep(c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB"), 3)) %>%
-  kable_styling(latex_options = c("striped")) %>%
-  pack_rows(index = c("General Measures" = 4, "Altmans Z Components" = 5)) %>% 
-  add_header_above(c(" " = 1, "Full" = 6, "Profitable" = 6, "Unprofitable" = 6)) %>% 
-  #pack_rows(index = c("Larger FQHCs" = 15, "Smaller FQHCs" = 15)) %>% 
-  add_footnote(c(""))
-```
-
-## True Figure 4
-```{r}
-fields <- 10
-fig4 <- cbind(c(rep("Full", fields), rep("More Market Share", fields), rep("Less Market Share", fields), rep('Profitable', fields), rep('Unprofitable/Budget Neutral', fields)), 
-      rbind(atts.comp.full, atts.comp.larger, atts.comp.smaller, atts.fin.larger, atts.fin.smaller)) %>% 
-  data.frame()
-
-colnames(fig4) <- c("Subgroup", "Measure", "C_0", "T_0 - C_0", "Estimate", "LB", "UB")
-
-fig4$Measure <- ifelse(fig4$Measure == 'Gross land, buildings and equipment (LBE)', 'Property and Buildings', fig4$Measure)
-
-fig4$C_0 <- as.numeric(fig4$C_0)
-fig4$`T_0 - C_0` <- as.numeric(fig4$`T_0 - C_0`)
-fig4$Estimate <- as.numeric(fig4$Estimate)
-fig4$LB <- as.numeric(fig4$LB)
-fig4$UB <- as.numeric(fig4$UB)
-
-fig4$Groups <- ifelse(fig4$Measure %in% c('Total revenue (unrestricted & restricted)','Property and Buildings','Staffing', 'Liabilities'), 'Mechanisms', 
-               ifelse(fig4$Measure %in% c('Liquidity','Efficiency'), 'Financing', NA))
-
-rownames(fig4) <- NULL
-
-fig4 %>% 
-  filter(Groups == 'Mechanisms' ) %>% 
-ggplot(aes(y=Measure, x=Estimate, xmin=LB, xmax=UB)) +
-geom_point() +
-
-#this changes the features of the overall effects
-#one could resize, reshape, or recolor these points if desired
-xlab("DID Estimates") + 
-ylab(NULL) + 
-#adds the CIs
-geom_errorbarh(height=.1) +
-
-#sets the scales
-#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
-#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
-#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
-
-#adding a vertical line at the effect = 0 mark
-geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5) +
-
-#faceting based on my subgroups
-  #facet_wrap(~X1) +
-facet_grid(~Subgroup, scales = "free_y", switch = 'y', space = "free_y")+
-
-#thematic stuff
-#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
-theme_tufte_revised()+
-   theme(strip.placement = "outside") +
-#theme(text=element_text(family="Times",size=12, color="black"))+
-theme(panel.spacing = unit(1, "lines")) +
-  ggtitle("Figure 2, Incumbent Only (FQHC-zip-year units)")
-
-# fig4 %>% 
-#   select(Measure:UB) %>% 
-#   filter(Measure %notin% c('Total revenue (unrestricted & restricted)', 'Total expenses before depreciation', 'Surplus as a pct of before dep expenses')) %>% 
-#   kable("html", booktabs = T, col.names = c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB")) %>%
-#   kable_styling(latex_options = c("striped")) %>%
-#   pack_rows(index = c("General Measures" = 4, "Altmans Z Components" = 5)) %>% 
-#   add_header_above(c(" " = 1, "Full" = 6, "Profitable" = 6, "Unprofitable" = 6)) %>% 
-#   #pack_rows(index = c("Larger FQHCs" = 15, "Smaller FQHCs" = 15)) %>% 
-#   add_footnote(c(""))
-
-library(formattable)
-fig4$C_0 <- currency(fig4$C_0, digits = 0L)
-fig4$`T_0 - C_0` <- currency(fig4$`T_0 - C_0`, digits = 0L)
-fig4$Estimate <- currency(fig4$Estimate, digits = 0L)
-fig4$LB <- currency(fig4$LB, digits = 0L)
-fig4$UB <- currency(fig4$UB, digits = 0L)
-
-fig4 %>% 
-  filter(Groups == 'Mechanisms' ) %>% 
-  select(Measure:UB) %>% 
-  kable("html", booktabs = T, col.names = c("Outcome", "C_0", "T_0 - C_0", "DID Estimate", "LB", "UB")) %>%
-  kable_styling(latex_options = c("striped")) %>%
-  row_spec(c(6, 14),bold=T, italic = T, hline_after = T) %>% 
-  row_spec(c(19),bold=F, italic = T, hline_after = T) %>% 
-  pack_rows(index = c("Panel A: Full Sample" = 4, "Panel B: Higher Low-Income Market Share Subgroup" = 4, "Panel B: Lower Low-Income Market Share Subgroup" = 4, 
-                      "Panel C: Profitable Subgroup" = 4, "Panel C: Unprofitable/Budget Neutral Subgroup" = 4)) %>% 
-  #add_header_above(c(" " = 1, "Full" = 6, "Profitable" = 6, "Unprofitable" = 6)) %>% 
-  #pack_rows(index = c("Larger FQHCs" = 15, "Smaller FQHCs" = 15)) %>% 
-  add_footnote(c(""))
-
-```
-
-# Robustness Testing
-
-## Service Area Overlap measurement - Plausible Exogeneity
-
-- >99% of zips in sample have unmet Low income, Medicaid, or Uninsured need at baseline
-- Distance of Rival's new zip code to nearest existing zip code in service area,  75% are below 10km. All those > 10km to nearest site are in rural areas traveling across very low density land
-```{r}
-
-## Need
-df.z.full %>% 
-  filter(Year == 2015) %>% 
-  left_join(census, by = c("Zip" = "ZipCode", "Year" = "YEAR")) %>% 
-  mutate(Pct.Total = Total.z / TotalPop, Pct.LowInc = Total.z / (IncomeBelowPoverty / PovertyStatusDet * TotalPop), Pct.MCD = MCD.z / (Medicaid / MCD.denom * TotalPop), Pct.None = None.z / (Uninsured / Unins.denom * TotalPop) ) %>%
-  select(Zip:Att.z, Pct.Total:Pct.None) %>% 
-  mutate(NeedMore = ifelse(Pct.LowInc < 1 | Pct.MCD < 1 | Pct.None < 1, 1, 0), 
-         Tx = ifelse(Att.z > 0, 1, 0)) %>% 
-  #group_by(Tx) %>% 
-  mutate(#n(), 
-            NeedMore = NeedMore, 
-            NeedLowIncome = ifelse(Pct.LowInc < 1, 1, 0), 
-            NeedMCD = ifelse(Pct.MCD < 1, 1, 0),
-            NeedNone = ifelse(Pct.None < 1, 1, 0)) %>% 
-  select(Tx, NeedMore:NeedNone) %>% 
-  filter(!is.na(NeedMore)) %>% 
-  tbl_summary(by = Tx) %>% 
-  add_p()
-
-## Distance of Competitor to New Site
-df.z.dist <- df.z.full %>% 
-  filter(Att.z == Year) %>% 
-  select(Zip:Total.z) %>% 
-  left_join(uds.sites %>% select(`Grant Number`, Year, Zip) %>% unique(), by = c("Zip","Year")) %>% 
-  left_join(df.z %>% filter(Tx == 1) %>% select(`Grant Number`, Year, Zip) %>% unique(), by = c("Zip","Year")) %>% 
-  filter(`Grant Number.x` != `Grant Number.y`)
-
-## Read in Centroid Data
-zip.centroids <- read.csv("ZIP_Code_Population_Weighted_Centroids.csv") %>% 
-  mutate(ZipCode = str_pad(STD_ZIP5, 5, pad = "0")) %>% 
-  select(ZipCode, X, Y)
-## Add missing centroids
-zip.centroids <- rbind(zip.centroids, c(ZipCode = "37243", X = -86.783, Y = 36.165), 
-                                      c(ZipCode = "95951", X = -121.98, Y = 39.73)) %>% 
-  mutate(X = as.numeric(X), Y = as.numeric(Y))
-
-df.z.dist <- df.z.dist %>% mutate(DistToClosestSite = NA, ZipOfClosestSite = NA)
-
-for (g in 1:nrow(df.z.dist)){
-#g <- 3
- temp <- rbind(zip.centroids %>% filter(ZipCode == df.z.dist[g,]$Zip), 
-          zip.centroids %>% filter(ZipCode %in% unique(uds.sites[uds.sites$`Grant Number` == df.z.dist[g,]$`Grant Number.x` & uds.sites$Year == df.z.dist[g,]$Year,]$Zip))) %>% 
-   unique()
-  mm <- as.matrix(dist(as.matrix(temp$X, temp$Y), method = "euclidean"))[-1,1]
-  df.z.dist[g,]$DistToClosestSite <-  min(mm) * 111.139
-  df.z.dist[g,]$ZipOfClosestSite  <- ifelse(is.na(temp[2,]$ZipCode), temp[1,]$ZipCode, unlist(temp[-1,]$ZipCode[rank(mm) == 1]))
-}
-
-df.z.dist[19,]$DistToClosestSite <- 0
-
-mean(df.z.dist$DistToClosestSite)
-quantile(df.z.dist$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))
-
-mean(df.z.dist[df.z.dist$ZipFilter == 1,]$DistToClosestSite)
-mean(df.z.dist[df.z.dist$ZipFilter == 2,]$DistToClosestSite)
-
-quantile(df.z.dist[df.z.dist$ZipFilter == 1,]$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))
-quantile(df.z.dist[df.z.dist$ZipFilter == 2,]$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))
-
-zipsize <- zctas(starts_with = c(df.z.dist$Zip, df.z.dist$ZipOfClosestSite), year = 2010)
-
-## Original Figure
-df.z.dist.plot <- df.z.dist %>% 
-  left_join(zipsize %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
-  left_join(uds.sites %>% select(Zip, `Site State`) %>% unique(), by = c("Zip")) %>% 
-  left_join(census %>% select(ZipCode, YEAR, TotalPop), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
-  arrange(desc(DistToClosestSite)) %>% 
-  mutate(Area.SQmiles = ALAND10 / 2.59e6) %>% 
-  mutate(Density.NewZip = TotalPop / Area.SQmiles, 
-         l.density = log(TotalPop / Area.SQmiles))
-
-df.z.dist.plot %>% 
-  ggplot(aes(x = log(Density.NewZip), y = DistToClosestSite)) + geom_point(aes(size = Area.SQmiles)) +
-  ggtitle("Distance from Rival's newly competing zip ocde to closest incumbent zip code by Density and Area of newly competing zip code")
-
-summary(lm(DistToClosestSite ~ log(Density.NewZip), data = df.z.dist.plot))
-
-# Updated Figure
-df.z.dist.plot <- df.z.dist.plot %>% 
-  select(Zip:ZipOfClosestSite, Density.NewZip) %>% 
-  left_join(zipsize %>% select(GEOID10, ALAND10), by = c("ZipOfClosestSite" = "GEOID10")) %>% 
-  left_join(uds.sites %>% select(Zip, `Site State`) %>% unique(), by = c("ZipOfClosestSite" = "Zip")) %>% 
-  left_join(census %>% select(ZipCode, YEAR, TotalPop), by = c("Year" = "YEAR", "ZipOfClosestSite" = "ZipCode")) %>% 
-  arrange(desc(DistToClosestSite)) %>% 
-  mutate(Area.SQmiles = ALAND10 / 2.59e6) %>% 
-  mutate(Density.Origin = TotalPop / Area.SQmiles)
-
-df.z.dist.plot %>% 
-  ggplot(aes(x = log(Density.NewZip), y = DistToClosestSite, color = log(Density.Origin))) + geom_point() +
-  scale_colour_gradientn(colours = terrain.colors(10))+ theme_minimal()+
-  ylab("Distance from Competative to closest Rival Site (km)") +
-  ggtitle("Distance from newly competative Zip to Rival's closest existing zip, by log Density of areas")
-
-p <- df.z.dist.plot %>% 
-  ggplot(aes(x = log(Density.Origin), y = log(Density.NewZip))) + 
-  geom_point(aes(size = DistToClosestSite, colour = DistToClosestSite)) + 
-  scale_colour_gradientn(colours = c("green","lightblue","purple"),
-                         values = c(1.0,0.7,0.1,0))  +#scale_colour_gradientn(colours = terrain.colors(10))+ 
-  theme_minimal() + ylab("Log Population Density of New Zip Code") + 
-  xlab("Log Population Density of Nearest Service Area Zip Code") + 
-  labs(color = "Distance Travelled to\nOpenNew Site (km)") + 
-  guides(size = FALSE) + xlim(0.5, 11.5) + ylim(0.5, 11.5)
-p
-
-summary(lm(log(Density.Origin) ~ log(Density.NewZip), data = df.z.dist.plot))
-
-```
-
-## Estimate effects of competition on nearest FQHC, takes 20 minutes to run code
-```{r}
-
-## Build the first part of the dataset
-
-df.spill <- df.z %>% 
-  left_join(df.z.dist %>% 
-  select(`Grant Number.y`, Zip) %>% 
-    unique() %>% 
-    rename(ZipOfComp = Zip), by = c("Grant Number" = "Grant Number.y")) %>% 
-  #filter(!is.na(ZipOfComp)) %>% 
-  mutate(ZipOfComp = ifelse(`Grant Number` == "H80CS00765", 95991, ZipOfComp)) %>% 
-  left_join(zip.centroids, by = c("Zip" = "ZipCode")) %>% 
-  left_join(zip.centroids, by = c("ZipOfComp" = "ZipCode")) %>% 
-  mutate(Dist = sqrt((X.x - X.y) ^ 2 + (Y.x - Y.y) ^ 2) * 111.139) %>% 
-  mutate(Dist.f = ifelse(is.na(Dist), "-1",
-                  ifelse(Dist == 0, 0, 
-                  ifelse(Dist > 0 & Dist < 20, 1, 
-                  ifelse(Dist >= 20 & Dist < 50, 2, 3))))) %>% 
-  #filter(is.na(Dist.f) | Dist.f == 2) %>% 
-  left_join(uds.sites %>% 
-              filter(`Location Setting` %in% c("All Other Clinic Types")) %>% 
-              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
-                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
-                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
-                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
-                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
-                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
-              group_by(`Grant Number`, Year, Zip) %>% 
-              summarise(Sites = n(), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
-                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)), by = c("Grant Number","Year", "Zip")) %>% 
-  mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
-         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
-         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
-         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
-         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
-         Calendar = ifelse(is.na(Calendar), 0, Calendar))
-
-dist.vecs <- df.spill[!is.na(df.spill$Dist),]$Dist
-
-df.spill %>% 
-  group_by(Dist.f) %>% 
-  summarise(n())
-
-## Find neighbors based on some circle around FQHC zip
-
-mm <- dist(zip.centroids[,2:3])
-mm <- as.matrix(mm) * 111.139
-
-mm.2 <- mm[zip.centroids$ZipCode %in% unique(df.spill$Zip),]
-
-mm.2 <- as.matrix((mm.2 < 50) + 0 )
-rowSums(mm.2)
-
-mm.3 <- c(CenterZip = 0, Year = 0, Competing.Sites = 0)
-for (g in 1:dim(mm.2)[1]){
-  mm.3 <- rbind(mm.3, cbind(CenterZip = zip.centroids[rownames(mm.2)[g],]$ZipCode, zip.centroids[names(mm.2[g,][which(as.vector(mm.2[g,] == 1))]),]) %>% 
-  left_join(uds.sites %>% filter(Year %in% c(2015:2019)) %>% group_by(Year, Zip) %>% summarise(Sites.Total = n()), by = c("ZipCode" = "Zip")) %>% 
-  left_join(df.spill %>% select(`Grant Number`, Year, Zip, Sites), by = c("ZipCode" = "Zip", "Year")) %>% 
-  mutate(Sites.Total = ifelse(is.na(Sites.Total), 0, Sites.Total), 
-         Sites = ifelse(is.na(Sites), 0, Sites), 
-         Competing.Sites = Sites.Total - Sites) %>% 
-  filter(CenterZip != ZipCode) %>% 
-  group_by(CenterZip, Year) %>% 
-  summarise(Competing.Sites = sum(Competing.Sites)) %>% 
-    as.matrix())
-}
-
-mm.3 <- mm.3[-1,]
-
-#mm.100 <- mm.3 %>% data.frame() 
-#mm.60 <- mm.3 %>% data.frame() 
-#mm.50 <- mm.3 %>% data.frame() 
-#mm.20 <- mm.3 %>% data.frame() 
-#mm.10 <- mm.3 %>% data.frame()
-
-#mm.3 <- mm.50
-
-```
-
-```{r}
-cs.output.expand <- att_gt( yname = "Total.Hours",
-                      tname = "Year",
-                      idname = "ID",
-                      gname = "Att",
-                      xformla = ~1,
-                      data = df.spill %>% filter(Dist.f %in% c("-1",3)), # %>% filter(Year > 2015),
-                      control_group = "nevertreated",
-                      clustervars = "ID",
-                      panel = TRUE,
-                      base_period = "universal"
-                      )
-aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-```
-
-## Control for spatial Spillovers
-```{r}
-
-df.spill2 <- df.spill %>% 
-  left_join(mm.3 %>% data.frame() %>% mutate(Year = as.numeric(Year)), by = c("Zip" = "CenterZip","Year")) %>% 
-  mutate(Competing.Sites = as.numeric(ifelse(is.na(Competing.Sites), 0, Competing.Sites)), 
-         D = ifelse(Competing.Sites > 0, 1, 0))
-
-#length(unique(df.spill2[is.na(df.spill2$Dist),]$Zip))  1893 or 1893 * 5
-
-set.seed(234)  #232
-df.spill2 <- df.spill2 %>% mutate(Dist = ifelse(is.na(Dist), rep(sample(dist.vecs, 1893, replace = T), each = 5), Dist), 
-                                  Att.viz = ifelse(Att == 0, rep(sample(c(2017:2019), 1893, replace = T), each = 5), Att)) %>% 
-  mutate(Dist.rounded = as.factor(ceiling(Dist / 10)))
-
-df.spill2 <- df.spill2 %>% 
-  ungroup() %>% 
-  #filter(MarketShare < median(MarketShare, na.rm = TRUE)) %>% 
-  select(`Grant Number`, Tx, D, Att, Att.viz, Dist, Dist.rounded, Year, Zip, Total.Hours, Sites, Perminance, Schedule, Calendar, Total.z, MCD.z, MCR.z, COM.z, None.z) %>%
-  inner_join(df.qual.exp %>% filter(Year == 2016) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
-    select(Tx, D, Dist, Year, Zip, `Grant Number`, ZipFilter, Att, Att.viz, Dist.rounded, Total.Hours, Sites, Perminance, Schedule, Calendar, Total.z, MCD.z, MCR.z, COM.z, None.z) # %>% filter(ZipFilter == 2)
-
-  i <- 11
-  df.temp <- df.spill2[,c(1:5, i)]
-  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
-  model_feols_clustered <- feols(Outcome ~ Tx*as.numeric(Dist / 10) + D | Year + Zip, cluster = ~ Zip, data = df.temp)
-  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
-  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]
-
-for (i in 12:20){
-  df.temp <- df.spill2[,c(1:5, i)]
-  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
-  model_feols_clustered <- feols(Outcome ~ Tx*as.numeric(Dist / 10) + D | Year + Zip, cluster = ~ Zip, data = df.temp)
-  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
-  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),])
-}
-
-p.spill <- df.spill2 %>% 
-  mutate(Treats = ifelse(Att == 0 & Year >=  Att.viz, 1, Tx)) %>% 
-  filter(Att > 0) %>% 
-  group_by(Dist.rounded, Treats) %>% 
-  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), Total.z = mean(Total.z, na.rm = TRUE), Total.Hours = mean(Total.Hours, na.rm = TRUE), MCD.z = mean(MCD.z, na.rm = TRUE)) %>% 
-  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, Total.z, Total.Hours, MCD.z)) %>% 
-  mutate(Sites = Sites_1 - Sites_0, 
-         Total.z = Total.z_1 - Total.z_0, 
-         Total.Hours = Total.Hours_1 - Total.Hours_0, 
-         MCD.z = MCD.z_1 - MCD.z_0) %>% 
-  left_join(df.spill2 %>% 
-  mutate(Treats = ifelse(Att == 0 & Year >= Att.viz, 1, Tx)) %>% 
-  filter(Att == 0) %>% 
-  group_by(Dist.rounded, Treats) %>% 
-  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), Total.z = mean(Total.z, na.rm = TRUE), Total.Hours = mean(Total.Hours, na.rm = TRUE), MCD.z = mean(MCD.z, na.rm = TRUE)) %>% 
-  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, Total.z, Total.Hours, MCD.z)) %>% 
-  mutate(Sites.control = Sites_1 - Sites_0, 
-         Total.z.control = Total.z_1 - Total.z_0, 
-         Total.Hours.control = Total.Hours_1 - Total.Hours_0, 
-         MCD.z.control = MCD.z_1 - MCD.z_0) %>% 
-    select(Dist.rounded, Sites.control:MCD.z.control), by = c("Dist.rounded")) %>% 
-  mutate( Locations = Sites - Sites.control, 
-         `Patients` = Total.z - Total.z.control, 
-         `Patients - Medicaid Only` = MCD.z - MCD.z.control, 
-         `Hours per Week` = Total.Hours - Total.Hours.control) %>% 
-  select(Dist.rounded:Counts_1, `Locations`:`Hours per Week`) %>% 
-  mutate(Dist.rounded = as.numeric(paste(Dist.rounded, 0, sep = ""))) %>% 
-  pivot_longer(cols = c( `Locations`:`Hours per Week`)) %>% 
-  mutate(`Treated Zips` = Counts_0 / 3) %>% 
-  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 200) + 
-  xlab("Kilometers to Competitive Zip") + ylab("Unadjusted Difference-in-differences") + theme_tufte_revised() + 
-  geom_smooth(method = "lm", se = F, quiet = TRUE, formula = "y ~ x", mapping = aes(weight = `Treated Zips`)) + 
-  geom_hline(yintercept=0, linetype = "dashed", color = "grey") + theme(text = element_text(size = 16)) + theme(title = element_text(face = "bold")) + 
-  ggtitle("Figure 4 - Unadjusted DID Estimates by Distance to Competitive Zip")
-
-suppressWarnings(print(p.spill))
-
-output <- cbind(TEs %>% 
-  mutate(`95% LB` = Estimate - `Std..Error` * 1.96, 
-         `95% UB` = Estimate + `Std..Error` * 1.96) %>% 
-    select(Estimate,`95% LB`, `95% UB`) ,
-
-TEs_Dist %>% 
-  mutate(`95% LB` = Estimate - `Std..Error` * 1.96, 
-         `95% UB` = Estimate + `Std..Error` * 1.96) %>% 
-    select(Estimate,`95% LB`, `95% UB`)) 
-rownames(output) <- c("Hours Per Week","Locations","Perminance","Weekly Schedule","Calendar Schedule","Total","Medicaid","Medicare","Commerical","Uninsured")
-
-round(output[c(6:10, 2,3, 1, 4, 5),], digits = 3) %>% 
-  kable("html", booktabs = T, col.names = c("DID Estimate", "95% LB", "95% UB", "DID Estimate", "95% LB", "95% UB")) %>%
-  kable_styling(latex_options = c("striped")) %>%
-  pack_rows(index = c("Patient Panel" = 5, "Extensive Margin" = 2, "Intensive Margin" = 3)) %>% 
-  add_header_above(c(" " = 1, "Treatment Effect" = 3, "Treatment Effect * Distance" = 3)) %>% 
-  add_footnote(c("Treatment Effect is the ATT estimated in the zip code where the rival opens their new location","Treatment Effect * Distance is the change in the ATT for every 10km an outlying zip code in the incumbent's service area is from the competitive zip "))
-```
-
-## Preperiod parallel trends
-```{r}
-
-i <- 4
-df.temp2 <- df.spill2 %>% filter(Att == 0 | Year < Att) %>% mutate(Treat = ifelse(Att > 0, 1, 0)) %>% 
-                   select(Year, Treat, Zip, Total.Hours:None.z)
-df.temp2 <- df.temp2[,c(1:3, i)]
-names(df.temp2) <- c('Year','Treat','Zip','Outcome')
-
-parallel.trends.set <- data.frame(feols(Outcome ~ Treat * Year, 
-                 data = df.temp2)$coeftable)[4,]
-
-for (i in 5:13){
-  df.temp2 <- df.spill2 %>% filter(Att == 0 | Year < Att) %>% mutate(Treat = ifelse(Att > 0, 1, 0)) %>% 
-                   select(Year, Treat, Zip, Total.Hours:None.z)
-df.temp2 <- df.temp2[,c(1:3, i)]
-names(df.temp2) <- c('Year','Treat','Zip','Outcome')
-
-parallel.trends.set <- rbind(parallel.trends.set, data.frame(feols(Outcome ~ Treat * Year , 
-                 data = df.temp2)$coeftable)[4,])
-}
-parallel.trends.set
-```
-
-## Again, with did2s
-```{r}
-did2s(
-      data = df.spill2, 
-      yname = "MCD.z", 
-      treatment = "Tx",
-        first_stage = ~ 0 | Zip + Year + D, 
-        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),
-        cluster_var = "Zip",
-      verbose = FALSE
-    )
-
-```
-
-## How do close versus far zip codes compare
-
-```{r}
-
-df.temp3 <- df.spill2 %>% 
-  left_join(census, by = c("Zip" = "ZipCode", "Year" = "YEAR" )) %>% 
-    filter(Year %in% c(2015:2016) & Att > 0) %>% 
-  mutate(Pct.Age = Age65andOver / TotalPop * 100, 
-         Pct.Pov = IncomeBelowPoverty / PovertyStatusDet * 100, 
-         Pct.HL = Hispanic / TotalPop * 100, 
-         Pct.Black = Black / TotalPop * 100,
-         Pct.White = White / TotalPop * 100,
-         Pct.Unemp = Unemployed / Unemp_denom * 100,
-         Pct.MCD = Medicaid / MCD.denom * 100, 
-         Pct.NoIns = Uninsured / Unins.denom * 100) %>% 
-  select(Dist, Pct.Age, Pct.HL, Pct.Black, Pct.White, Pct.Pov, Pct.Unemp, Pct.MCD, Pct.NoIns)
-
-ziptypes <- data.frame(0, 0, 0, 0)
-for (k in 2:ncol(df.temp3)){
-  df.temp4 <- df.temp3[,c(1, k)]
-  names(df.temp4) <- c('Dist','Outcome')
-
-  ziptypes <- rbind(ziptypes, summary(lm(data = df.temp4, Outcome ~ as.numeric(Dist / 10) ))$coeff[2,])
-}
-ziptypes <- ziptypes[-1,]
-
-rownames(ziptypes) <- c("% age over 65+","% Hispanic/Latino","% Black","% White", "% Poverty","% Unemployed","% Medicaid","% Uninsured")
-
-ziptypes %>% 
-  mutate(Estimate = X0, 
-         `95% LB` = X0 - X0.1 * 1.96, 
-         `95% UB` = X0 + X0.1 * 1.96, 
-         `p-value` = X0.3) %>% 
-  select(Estimate:`p-value`) %>% 
-  kable("html", booktabs = T) %>%
-  kable_styling(latex_options = c("striped")) %>%
-  pack_rows(index = c("Demographics" = 4, "Income" = 2, "Insurance" = 2)) %>% 
-  row_spec(c(1, 4), bold = T, hline_after = T) %>% 
-  row_spec(c(3, 5:8), italic = T, hline_after = T) %>% 
-  add_footnote(c("For every 10 km between the competing zip code and the zip code of interest, the covariate rate will change by the estimated coefficient"))
-
-```
-
-## Balance on Covariates
-```{r}
-
-df.qual.exp %>% 
-  mutate(Treat = ifelse(Att > 0, 1, 0)) %>% 
-  mutate(Groups = ifelse(Treat == 1 & Expandor == 0, "Treated", 
-                  ifelse(Treat == 0 & Expandor == 0, "Control", 
-                  ifelse(Treat == 0 & Expandor == 1, "Expandor Comp", "Expandor No Comp")))) %>% 
-  filter(Year == 2015) %>%  #z & ZipFilter == 2) %>% 
-  select(Sites, Zips, #MarketShare, 
-         Total, Density, Pct.Rural, Pct.Urban, None:MCD, IMM2yo:DepScrn, Groups, Pct.NHA:Pct.NHW, Pct.LessThan200pctFPL, Pct.Homeless:Pct.Children, `Liabilities (as pct of assets)`, `Gross land, buildings and equipment (LBE)`, `Surplus as a pct of after dep expenses`) %>% #SwitchEMR, InterOrgHITexchange, UDSQualRep.highlowuse,
-  tbl_summary(by = Groups, 
-              statistic = all_continuous() ~ "{mean} ({sd})") %>% 
-  add_p(test = everything() ~ "t.test")
-
-```
-
-## Treated vs Rivals
-```{r}
-
-# rbind(uds.covariates %>% filter(Year == 2015 & `Grant Number` %in% c(unique(df.z.dist.plot$`Grant Number.x`)) ) %>% mutate(Class = "Incumbent"), 
-#       uds.covariates %>% filter(Year == 2015 & `Grant Number` %in% c(unique(df.z.dist.plot$`Grant Number.y`)) ) %>% mutate(Class = "Rival")) %>% 
-#   tbl_summary(by = Class) %>% 
-#   add_p()
-
-```
-
-## Mapping Quality Function
-```{r}
-p <- seq(0, 1, 0.05)
-v <- c(1:10)
-
-for (i in 1:10){
-  p <- i / 10
-  y <- 1 - (1 - p)^v
-  y.prime = -(1 - p)^v*log(1 - p) - y/v
-  #plot(v, y, main = paste("p = ", p, sep = "")) ## For regular trade offs
-  plot(v, y.prime, main = paste("p = ", p, sep = "")) ## for denominator sign checking
-}
-
-## Checking the total differential on quality to see what happens
-dd <- merge(merge(seq(0.2, 0.8, 0.05), c(1:5)) %>% rename(p = x, v = y), 
-        c(seq(-5, -1, 0.5), seq(1, 5, 0.5)) ) %>% 
-  rename(dv = y) %>% 
-  mutate(dp = (-(1 - p)^v*log(1 - p) - (1 - (1 - p)^v)/v)*( v*(1 - p)^(v-1) )^-1 * dv) %>% 
-    mutate(dq = -(1 - p)^v*log(1 - p) * dv + v*(1 - p)^(v-1) * dp) %>% 
-  filter(dv > -abs(v))
-
-summary(dd[complete.cases(dd),]$dq)
-
-dd %>% filter(dq == min(dd$dq, na.rm = TRUE))
-dd %>% filter(dq == max(dd$dq, na.rm = TRUE))
-
-plot(dd[dd$v == 3,]$dv, dd[dd$v == 3,]$dq)
-
-ggplot(data = dd, aes(x = p, y = dq, color = dv)) + geom_point() + facet_wrap(~v)
-
-summary(df.qual.exp$Qcomp)
-
-```
-
-## Placebo
-
-```{r}
-
-df.placebo <- df.qual.exp %>% 
-  #filter(ZipFilter == 2) %>% 
-select(Year, ID, Att, Pct.NHA:Pct.Children) 
-# %>% 
-#   inner_join(df.qual.exp %>% filter(Year == 2016) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(ID, ZipFilter), by = c("ID")) %>% 
-#   filter(ZipFilter == 2) %>% 
-#     select(Year, ID, Att, Pct.NHA:Pct.Children)
-
-atts.placebo <- rep(0, 7)
-for (i in 5:ncol(df.placebo)){
-
-  temp <- df.placebo[,c(1:3, i)]
-  colnames(temp) <- c("Year","ID","Att","Outcome")
-
-cs.output.expand <- att_gt( yname = "Outcome",
-                      tname = "Year",
-                      idname = "ID",
-                      gname = "Att",
-                      xformla = ~1,
-                      data = temp,
-                      control_group = "nevertreated",
-                      clustervars = "ID",
-                      panel = FALSE, 
-                      base_period = "universal"
-                      )
-cs.output.expand.agg.dyn.0 <- aggte(cs.output.expand, type = "simple", na.rm = TRUE)
-cs.output.expand.agg.dyn <- aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)
-
-atts.placebo <- rbind(atts.placebo, cbind(colnames(df.placebo[,i]), round(cbind(cs.output.expand.agg.dyn.0$overall.att, 
-      cs.output.expand.agg.dyn.0$overall.att - 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-      cs.output.expand.agg.dyn.0$overall.att + 1.96 * cs.output.expand.agg.dyn.0$overall.se, 
-      cs.output.expand.agg.dyn$overall.att, 
-      cs.output.expand.agg.dyn$overall.att - cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se, 
-      cs.output.expand.agg.dyn$overall.att + cs.output.expand.agg.dyn$crit.val.egt * cs.output.expand.agg.dyn$overall.se), 3)))
-
-}
-
-#if (k == 1){atts.placebo.larger <- atts.placebo[-1,]} else {atts.placebo.smaller <- atts.placebo[-1,]}
-
-#rownames(atts.placebo.larger) <- NULL
-#atts.placebo.larger
-#atts.placebo.smaller
-
-as.data.frame(atts.placebo[-1,]) %>% 
-  rename(Measure = V1, Estimate = V2, `95%CI_LB` = V3, `95%CI_UB` = V4)
-```
-
-## multiple hypothesis correction, pre-period parallel trends
-```{r}
-
-# rownames(atts) <- rep(NULL, nrow(atts))
-# if (k == 1){atts.larger <- atts} else {atts.smaller <- atts}
-#
-
-# p-values rankings, Benjamini-Hochberg procedure
-cbind(Sample = c(rep("Panel A: Full Sample", 3), 
-                    rep("Panel B: Higher Low-Income Market Share Subgroup", 3), 
-                    rep("Panel B: Lower Low-Income Market Share Subgroup", 3), 
-                    rep("Panel C: Profitable Subgroup", 3), 
-                    rep("Panel C: Unprofitable/Budget Neutral Subgroup", 3)), 
-  data.frame(Outcome = atts[c(2:16),c(1)], Estimate = atts[c(2:16),c(2)], CI = paste("(", atts[c(2:16),3], ", ", atts[c(2:16),4], ")", sep = ""), p.value =  c(2*pnorm(-abs(as.numeric(atts[c(2:16),2]) / ((as.numeric(atts[c(2:16),4]) - as.numeric(atts[c(2:16),3])) / (2 * 1.96)))))))      %>%
-     arrange(p.value) %>%  
-    mutate(rank = row_number(), 
-           rank / 14 * 0.1) %>%
-
-  kable("html", booktabs = T, col.names = c("Sample","Outcome", "Estimate", "95% CI", "p-value", "Rank", "BH-procedure Threshold")) %>%
-  kable_styling(latex_options = c("striped")) %>% 
-  row_spec(c(1:6), italic = T, hline_after = T, background = "lightgrey")
-
-# parallel trends
-if (k == 1){z.larger <- z[-1,]} else {z.smaller <- z[-1,]}
-
-# length(z.larger)
-# length(z.smaller)
-cbind(atts[c(2:16),1], z[c(2:16),2])
-cbind(atts[atts[,1] %in% c('Total revenue (unrestricted & restricted)','Total net assets','Staffing', 'Liabilities'),1], z[atts[,1] %in% c('Total revenue (unrestricted & restricted)','Total net assets','Staffing', 'Liabilities'),2])
-
-```
-
-## What's happening in the control? Let's think
-
-```{r}
-
-df.space <- df.qual.exp %>% 
-  filter(Att > 0) %>% 
-  select(`Grant Number`, Year) %>% 
-  unique() %>% 
-  left_join(uds.sites %>% select(`Grant Number`, Year, Zip), by = c("Grant Number","Year")) %>% 
-  left_join(clinics.in.zips, by = c("Zip","Year")) %>%
-
-#  filter(`Grant Number` == "H80CS00881")
-  group_by(Zip) %>% 
-  filter(max(Clinics) > 1) %>% 
-  unique() %>% 
-  left_join(uds.sites %>% select(`Grant Number`, Zip, Year), by = c("Zip","Year")) %>% 
-  rename(Incumbent = `Grant Number.x`, Competitor = `Grant Number.y`) %>% 
-  filter(Incumbent != Competitor) %>% 
-  group_by(Zip, Incumbent, Competitor) %>% 
-  summarise(YearFirstComp = min(Year))%>% 
-  arrange(Incumbent)
-
-#df.space %>%  filter(Incumbent == "H80CS00881")
-
-df.z.2 <- df.space %>% 
-  pivot_longer(Incumbent:Competitor) %>% 
-  left_join(uds.zip.totals, by = c("value" = "Grant Number")) %>% 
-    ungroup() %>% 
-  mutate(ID = as.numeric(as.factor(paste(Zip, name, value)))) %>% 
-  mutate(year.rel = `Reporting Year` - YearFirstComp, 
-         Treat = ifelse(name == "Incumbent", 1, 0), 
-         Post = ifelse(year.rel >= 0, 1, 0))
-
-df.z.2$year.rel <- relevel(as.factor(df.z.2$year.rel), ref = "-1")
-
-# Are incumbents and controls really that different?  not really
-df.z.2 %>% 
-  select(value, name, `Reporting Year`, None:Total) %>% 
-  unique() %>% 
-  left_join(uds.covariates, by = c("value" = "Grant Number", "Reporting Year" = "Year")) %>% 
-  left_join(uds.6b.rates, by = c("value" = "GrantNumber", "Reporting Year" = "Year")) %>% 
-  filter(`Reporting Year` == 2015) %>% 
-  filter(value != 'H80CS28975') %>% 
-  select(name, Total, None:Pct.Children, IMM2yo:DepScrn) %>% 
-  mutate(None = None / Total, 
-         MCD = MCD / Total, 
-         MCR = MCR / Total, 
-         COM = COM / Total) %>% 
-  tbl_summary(by = name, 
-              statistic = all_continuous() ~ "{mean} ({sd})") %>% 
-  add_p(test = everything() ~ "t.test")
-
-summary(lm(data = df.z.2, Total ~ Treat*year.rel))
-
-# Competitors in the competative zip
-
-df.space %>% 
-  left_join(df.qual.exp %>% select(`Grant Number`, Att), by = c("Incumbent" = "Grant Number")) %>% 
-  left_join(uds.zip, by = c("Zip" = "Zip Code","Competitor" = "Grant Number")) %>% 
-  filter(`Reporting Year` %in% c(2015:2019)) %>% 
-  mutate(year.rel = `Reporting Year` - Att, 
-         Tx = ifelse(`Reporting Year` - Att >= 0 , 1, 0)) %>% 
-  ggplot(aes(x = year.rel, y = `Total Number of Patients`, group = Tx)) + geom_point() + geom_smooth(method = "lm") #+ ylim(0, 2000)
-
-df.space1 <- df.space %>% 
-  left_join(df.qual.exp %>% select(`Grant Number`, ID, Att) %>% unique(), by = c("Incumbent" = "Grant Number")) %>% 
-  merge(2015:2019) %>% 
-  left_join(uds.zip, by = c("Zip" = "Zip Code","Competitor" = "Grant Number", "y" = "Reporting Year")) %>% 
-  #filter(y %in% c(2015:2019)) %>% 
-  mutate(year.rel = y- Att, 
-         Tx = ifelse(year.rel >= 0 , 1, 0)) %>% 
-  mutate(None.z = ifelse(is.na(`None_Uninsured Patients`), 0, `None_Uninsured Patients`),
-          MCR.z = ifelse(is.na(`Medicare Patients`), 0, `Medicare Patients`),
-          COM.z = ifelse(is.na(`Private Patients`), 0, `Private Patients`),
-          MCD.z = ifelse(is.na(`Medicaid_CHIP_Other Public Patients`), 0, `Medicaid_CHIP_Other Public Patients`),
-          Total.z = ifelse(is.na(`Total Number of Patients`), 0, `Total Number of Patients`),
-         Grant = Competitor) %>% 
-  rename(Year = y) %>% 
-  select(Grant, Zip, ID, Att, Year, None.z:Total.z) %>% 
-  arrange(Grant, Zip, Year) %>% 
-  rbind(df.spill %>% 
-  filter(Att == 0) %>% 
-  rename(Grant = `Grant Number`) %>% 
-  select(Grant, Zip, ID, Att, Year, None.z, MCR.z, COM.z, MCD.z, Total.z) %>% 
-    inner_join(df.spill2 %>% filter(Dist == 0) %>% select(`Grant Number`) %>% unique(), by = c("Grant" = "Grant Number"))) %>% 
-  mutate(Tx = ifelse(Att > 0 & Year >= Att, 1, 0))
-
-feols(data = df.space1, Total.z ~ Tx | Zip + Year, cluster = ~Zip)
-
-cs.output.expand <- att_gt( yname = "Total.z",
-                      tname = "Year",
-                      idname = "ID",
-                      gname = "Att",
-                      xformla = ~1,
-                      data = df.space1, # %>% filter(Year > 2015),
-                      control_group = "nevertreated",
-                      clustervars = "ID",
-                      panel = TRUE,
-                      base_period = "universal"
-                      )
-aggte(cs.output.expand, type = "dynamic", na.rm = TRUE)
-```
-
-## Change in Full Market Benefit
-```{r}
-
-df.z.dist.plot %>% 
-  left_join(uds.zip %>% select(`Grant Number`, `Reporting Year`, `Zip Code`, `Medicaid_CHIP_Other Public Patients`, `Total Number of Patients`), 
-            by = c("Grant Number.y" = "Grant Number", "Zip" = "Zip Code")) %>% 
-  left_join(uds.zip %>% select(`Grant Number`, `Reporting Year`, `Zip Code`, `Medicaid_CHIP_Other Public Patients`, `Total Number of Patients`), 
-            by = c("Grant Number.x" = "Grant Number", "Zip" = "Zip Code", "Reporting Year")) %>% 
-  rename(MCD.Rival = `Medicaid_CHIP_Other Public Patients.y`, 
-         Total.Rival = `Total Number of Patients.y`, 
-         MCD.Incumbent = `Medicaid_CHIP_Other Public Patients.x`, 
-         Total.Incumbent = `Total Number of Patients.x`) %>% 
-  left_join(uds.6b.rates %>% 
-            mutate(Quality.Incumbent = (IMM2yo + Pap + ChildBMI + AdultBMI + Tobac + CRC + DepScrn) / 7) %>% 
-            select(GrantNumber, Year, Quality.Incumbent), by = c("Grant Number.y" = "GrantNumber", "Reporting Year" = "Year")) %>% 
-  left_join(uds.6b.rates %>% 
-            mutate(Quality.Rival = (IMM2yo + Pap + ChildBMI + AdultBMI + Tobac + CRC + DepScrn) / 7) %>% 
-            select(GrantNumber, Year, Quality.Rival), by = c("Grant Number.x" = "GrantNumber", "Reporting Year" = "Year")) %>% 
-  mutate(YearDiff = `Reporting Year` - Year, 
-         Post = ifelse(YearDiff >= 0, 1, 0)) %>% 
-  filter(`Reporting Year` %in% c(2015:2019)) %>% 
-  select(Zip, Att.z, `Grant Number.x`, `Grant Number.y`, `Reporting Year`:Post) %>% 
-  mutate(Quality.Market = Total.Incumbent / (Total.Incumbent + Total.Rival) * Quality.Incumbent + Total.Rival / (Total.Incumbent + Total.Rival) * Quality.Rival) %>% 
-  group_by(Post) %>% 
-  summarise(mean(Quality.Market, na.rm = TRUE))
-
-```

### 2023-08-13 code/analysis.Rmd
dividing the code

--- 2023-08-13 code/230510_Competition.Rmd
@@
----
-title: "220410_Competition"
-author: "Justin"
-date: "4/10/2022"
-output: html_document
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-# Library 
-```{r}
-library(tidygeocoder)
-library(tidyverse)
-library(did)
-library(tidycensus)
-library(gtsummary)
-library(readxl)
-library(sandwich)
-library(lmtest)
-library(ggpubr)
-library(kableExtra)
-library(tigris)
-
-library(gridExtra)
-library(cowplot)
-library(Matching)
-library(fixest)
-library(directlabels)
-
-`%notin%` <- Negate(`%in%`)
-
-select <- dplyr::select
-
-#Sys.setenv('R_MAX_VSIZE'=32000000000)
-
-```
-
-## Define new Tufte data theme
-```{r, echo = FALSE, results = "asis", message=FALSE, warning = FALSE, fig.align="center"}
-
-is.extrafont.installed <- function(){
-  if(is.element("extrafont", installed.packages()[,1])){
-    library(extrafont)
-    # probably need something here to run font_import()
-    return(T)
-  }else{
-    warning("Library extrafont installed; using system sans/serif libraries as fallback fonts. 
-    To enable full font support, run: 
-      install.packages('extrafont') 
-      font_import()")
-    return(F)
-  }
-}
-
-# set font
-base_font_family_tufte <- function(){
-  if(is.extrafont.installed()){
-    library(extrafont)
-    tuftefont <- choose_font(c("Gill Sans MT", "Gill Sans", "GillSans", "Verdana", "serif"), quiet = FALSE)  
-  }else{
-    tuftefont <- "serif"
-  }
-  return(tuftefont)
-}
-
-theme_tufte_revised <- function(base_size = 11, base_family = base_font_family_tufte(), ticks = TRUE) {
-
-  ret <- theme_bw(base_family = base_family, base_size = base_size) + 
-    theme(
-      axis.line = element_line(color = 'black'),
-      axis.title.x = element_text(vjust = -0.3), 
-      axis.title.y = element_text(vjust = 0.8),
-      legend.background = element_blank(), 
-      legend.key = element_blank(), 
-      legend.title = element_text(face="plain"),
-      panel.background = element_blank(), 
-      panel.border = element_blank(),
-      panel.grid = element_blank(),
-      plot.background = element_blank(),
-      strip.background = element_blank()
-    )
-
-  if (!ticks) {
-    ret <- ret + theme(axis.ticks = element_blank())
-  }
-
-  ret
-}
-
-```
-
-# Data
-
-## Read in UDS
-
-```{r}
-
-## Zips
-locs <- paste("UDS/UDS-", c(2014:2021), "-Full-Dataset.xlsx", sep = "")
-uds.zip <- read_excel(locs[1], sheet = "HealthCenterZipCodes")
-
-new.zip.names <- c("BHCMIS ID", "Grant Number", "Reporting Year" , "Zip Code", "Zip Code Type",  "None_Uninsured Patients" ,  "Medicaid_CHIP_Other Public Patients", "Medicare Patients", "Private Patients", "Total Number of Patients" )
-colnames(uds.zip) <-    new.zip.names
-
-for(i in 2:length(locs)){
-  temp.zip <- read_excel(locs[i], sheet = "HealthCenterZipCodes")
-  colnames(temp.zip) <- new.zip.names
-  uds.zip <- rbind(uds.zip, temp.zip %>% mutate(`Zip Code` = str_pad(`Zip Code`, 5, pad = "0")))
-}
-
-## Rename
-new.zip.names <- c("BHCMIS ID", "Grant Number", "Reporting Year" , "Zip Code", "Zip Code Type",  "None_Uninsured Patients" ,  "Medicaid_CHIP_Other Public Patients", "Medicare Patients", "Private Patients", "Total Number of Patients" )
-colnames(uds.zip) <-    new.zip.names
-
-## Clean
-
-uds.zip[uds.zip$`Total Number of Patients`== '-' | uds.zip$`Total Number of Patients`== '--',]$`Total Number of Patients` <- NA
-uds.zip$`Total Number of Patients` <- as.numeric(uds.zip$`Total Number of Patients`)
-uds.zip <- uds.zip[!is.na(uds.zip$`Total Number of Patients`),] %>%
-    mutate(`Reporting Year` = as.numeric(`Reporting Year`))
-
-uds.zip$`None_Uninsured Patients` <- as.numeric(uds.zip$`None_Uninsured Patients`)
-uds.zip$`Medicaid_CHIP_Other Public Patients` <- as.numeric(uds.zip$`Medicaid_CHIP_Other Public Patients`)
-uds.zip$`Medicare Patients` <- as.numeric(uds.zip$`Medicare Patients`)
-uds.zip$`Private Patients` <- as.numeric(uds.zip$`Private Patients`)
-
-uds.zip <- cbind(uds.zip, broken.total = rowSums(uds.zip[,c(6:9)], na.rm = TRUE), missings = rowSums(is.na(uds.zip[,c(6:9)]))) %>%
-  mutate(`Total Number of Patients` = as.numeric(`Total Number of Patients`)) %>%
-  mutate(`Total Number of Patients` = ifelse(is.na(`Total Number of Patients`), round(missings*16/4), `Total Number of Patients`)) %>%
-  mutate(`None_Uninsured Patients` = ifelse(is.na(`None_Uninsured Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `None_Uninsured Patients`),
-         `Medicaid_CHIP_Other Public Patients` = ifelse(is.na(`Medicaid_CHIP_Other Public Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Medicaid_CHIP_Other Public Patients`),
-         `Medicare Patients` = ifelse(is.na(`Medicare Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Medicare Patients`),
-         `Private Patients` = ifelse(is.na(`Private Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Private Patients`))
-
-# ## Old version with missingness still in there  
-# uds.zip$`Reporting Year` <- as.numeric(uds.zip$`Reporting Year`)
-# uds.zip$`Total Number of Patients` <- as.numeric(uds.zip$`Total Number of Patients`)
-# uds.zip$`None_Uninsured Patients` <- as.numeric(uds.zip$`None_Uninsured Patients`)
-# uds.zip$`Medicaid_CHIP_Other Public Patients` <- as.numeric(uds.zip$`Medicaid_CHIP_Other Public Patients`)
-# uds.zip$`Medicare Patients` <- as.numeric(uds.zip$`Medicare Patients`)
-# uds.zip$`Private Patients` <- as.numeric(uds.zip$`Private Patients`)
-# 
-# 
-# uds.zip[is.na(uds.zip$`Total Number of Patients`),]$`Total Number of Patients` <- 0
-# uds.zip[grep("-", uds.zip$`None_Uninsured Patients`),]$`None_Uninsured Patients` <- 0
-# uds.zip[grep("-", uds.zip$`Medicaid_CHIP_Other Public Patients`),]$`Medicaid_CHIP_Other Public Patients` <- 0
-# uds.zip[grep("-", uds.zip$`Medicare Patients`),]$`Medicare Patients` <- 0
-# uds.zip[grep("-", uds.zip$`Private Patients`),]$`Private Patients` <- 0
-# 
-uds.zip.totals <- uds.zip %>%
-  select(`Grant Number`, `Reporting Year`, `None_Uninsured Patients`:`Total Number of Patients`) %>%
-  group_by(`Grant Number`, `Reporting Year`) %>% summarise(None = sum(`None_Uninsured Patients`, na.rm = T),
-                                                           MCR = sum(`Medicare Patients`, na.rm = T),
-                                                           COM = sum(`Private Patients`, na.rm = T),
-                                                           MCD = sum(`Medicaid_CHIP_Other Public Patients`, na.rm = T),
-                                                           Total = sum(`Total Number of Patients`, na.rm = T))
-
-uds.zip <- uds.zip[uds.zip$`Zip Code Type` == "ZipCode",]
-
-## Sites
-locs <- paste("UDS/UDS-", c(2014:2021), "-Full-Dataset.xlsx", sep = "")
-
-uds.sites <- read_excel(locs[1], sheet = "HealthCenterSiteInfo") %>% 
-  select(GrantNumber, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>% 
-  mutate(Year = 2014)
-
-colnames(uds.sites) <- c("Grant Number", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")
-
-for(i in 2:(length(locs)-1)){
-  uds.sites <- rbind(uds.sites, read_excel(locs[i], sheet = "HealthCenterSiteInfo") %>% 
-                       select("Grant Number", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code") %>%
-  mutate(Year = 2013 + i))
-}
-
-temp.sites <- read_excel(locs[i+1], sheet = "HealthCenterSiteInfo" )%>% 
-  select(GrantNumber, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>% 
-  mutate(Year = 2021)
-colnames(temp.sites) <- c("Grant Number", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")
-
-uds.sites <- rbind(uds.sites, temp.sites)
-
-uds.sites$Zip <- substr(uds.sites$`Site ZIP Code`, 1, 5)
-
-uds.sites <- uds.sites %>% 
-  filter(`Site State` %notin% c('AK','HI','GU','VI','PW','MH','AS','FM','PR','MP'))
-
-uds.sites[grep(pattern = "-", uds.sites$Zip),]$Zip <- NA
-
-```
-
-## Clean up some of the missing zip codes
-
-```{r}
-
-tbcoded <- uds.sites[is.na(uds.sites$Zip),]
-coded <- geo(street = tbcoded[c(1:1000),]$`Site Street Address`, 
-             city = tbcoded[c(1:1000),]$`Site City`, 
-             state = tbcoded[c(1:1000),]$`Site State`, 
-             method = "census", 
-             full_results = TRUE)
-
-for (g in 1:9){
-  g
-coded <- rbind(coded, 
-               geo(street = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site Street Address`, 
-             city = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site City`, 
-             state = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site State`, 
-             method = "census", 
-             full_results = TRUE) )
-}
-
-coded <- rbind(coded, 
-               geo(street = tbcoded[c(10001:10975),]$`Site Street Address`, 
-             city = tbcoded[c(10001:10975),]$`Site City`, 
-             state = tbcoded[c(10001:10975),]$`Site State`, 
-             method = "census", 
-             full_results = TRUE) )
-
-coded[grep(pattern = "[[:digit:]]{5}$", coded$matched_address),]
-
-uds.sites[is.na(uds.sites$Zip),]$Zip <- str_extract(coded$matched_address, pattern = "[[:digit:]]{5}$")
-uds.sites[is.na(uds.sites$Zip),]
-
-uds.sites.temp <- uds.sites
-
-```
-
-```{r}
-
-uds.sites <- uds.sites.temp
-
-uds.sites.temp %>% filter(`Grant Number` %in% c("H80CS00881") & Year == 2016)
-
-chc <- read.csv("chc.csv")
-
-chc %>% filter(Health.Center.Number %in% c("H80CS00881"))
-
-uds.sites[is.na(uds.sites$Zip),] <- uds.sites[is.na(uds.sites$Zip),] %>%
-  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Street Address" = "Site.Address")) %>%
-  mutate(Zip = ifelse(is.na(Zip), substr(Health.Center.Organization.ZIP.Code, 1, 5), Zip)) %>%
-  select(`Grant Number`:Zip) %>%
-  unique()
-
-uds.sites[is.na(uds.sites$Zip),] <- uds.sites[is.na(uds.sites$Zip),] %>%
-  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Name" = "Site.Name")) %>%
-  mutate(Zip = ifelse(is.na(Zip), substr(Health.Center.Organization.ZIP.Code, 1, 5), Zip)) %>%
-  select(`Grant Number`:Zip) %>%
-  unique()
-
-uds.sites[is.na(uds.sites$Zip),] 
-```
-
-```{r}
-
-table(uds.sites.temp$`Location Setting`)
-
-uds.sites <- uds.sites %>% #filter(`Location Type` == "Permanent" & `Location Setting` %in% c("All Other Clinic Types")) %>% 
-  mutate(Access = as.numeric(ifelse(`Total Weekly Hours Of Operation` == "-" & `Operational Schedule` == "Full-Time", 40, 
-                  ifelse(`Total Weekly Hours Of Operation` == "-" & `Operational Schedule` == "Part-Time", 10, `Total Weekly Hours Of Operation`))))
-
-uds.sites[is.na(uds.sites$Zip),]
-
-uds.sites %>% 
-  arrange(`Total Weekly Hours Of Operation`, `Operational Schedule` )
-
-# z <- geocode(chc.term$SitePhysicalAddress)
-# 
-# 
-# y <- geo(address = chc.term$SitePhysicalAddress, method = "census")
-# 
-# write.csv(cbind(y[,1], y[,3], y[,2], z), file = "geocodedClosures.csv")
-
-```
-
-## Read in Quality data
-```{r}
-
-uds.6b.2012 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2013 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
-
-uds.6b.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 1) 
-uds.6b.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
-
-uds.6b.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
-
-uds.6b.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
-
-# rbind(
-# colnames(uds.6b.2014[,c(2, grep(pattern = "^%", colnames(uds.6b.2014))[-6])]),
-# colnames(uds.6b.2015[,c(2, grep(pattern = "^%", colnames(uds.6b.2015))[-6])]),
-# colnames(uds.6b.2016[,c(2, grep(pattern = "^%", colnames(uds.6b.2016))[-6])]),
-# colnames(uds.6b.2017[,c(2, grep(pattern = "^%", colnames(uds.6b.2017))[-6])]),
-# colnames(uds.6b.2018[,c(2, grep(pattern = "^%", colnames(uds.6b.2018))[-6])]),
-# colnames(uds.6b.2019[,c(2, grep(pattern = "^%", colnames(uds.6b.2019))[-6])]),
-# colnames(uds.6b.2020[,c(2, grep(pattern = "^%", colnames(uds.6b.2020))[-c(3, 11, 13)])]))
-# 
-# 
-# rbind(
-# colnames(uds.6b.2014[,c(2, grep(pattern = "^Total", colnames(uds.6b.2014))[-6])]),
-# colnames(uds.6b.2015[,c(2, grep(pattern = "^Total", colnames(uds.6b.2015))[-6])]),
-# colnames(uds.6b.2016[,c(2, grep(pattern = "^Total", colnames(uds.6b.2016))[-6])]),
-# colnames(uds.6b.2017[,c(2, grep(pattern = "^Total", colnames(uds.6b.2017))[-6])]),
-# colnames(uds.6b.2018[,c(2, grep(pattern = "^Total", colnames(uds.6b.2018))[-6])]),
-# colnames(uds.6b.2019[,c(2, grep(pattern = "^Total", colnames(uds.6b.2019))[-6])]),
-# colnames(uds.6b.2020[,c(2, grep(pattern = "^Total", colnames(uds.6b.2020))[-c(3, 11, 13)])]))
-
-namingshit <- c("GrantNumber", "IMM2yo", "Pap", "ChildBMI","AdultBMI","Tobac","CRC","DepScrn")
-namingshit.denom <- c("GrantNumber", "IMM2yo.denom", "Pap.denom", "ChildBMI.denom","AdultBMI.denom","Tobac.denom","CRC.denom","DepScrn.denom")
-
-uds.6b.rates <- rbind(
-  uds.6b.2014[,c(2, grep(pattern = "^%", colnames(uds.6b.2014))[-6])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2014), 
-  uds.6b.2015[,c(2, grep(pattern = "^%", colnames(uds.6b.2015))[-6])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2015),
-  uds.6b.2016[,c(2, grep(pattern = "^%", colnames(uds.6b.2016))[-6])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2016),
-
-  uds.6b.2017[,c(2, grep(pattern = "^%", colnames(uds.6b.2017))[-6])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2017),
-  uds.6b.2018[,c(2, grep(pattern = "^%", colnames(uds.6b.2018))[-6])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2018),
-
-  uds.6b.2019[,c(2, grep(pattern = "^%", colnames(uds.6b.2019))[-6])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2019),
-  uds.6b.2020[,c(2, grep(pattern = "^%", colnames(uds.6b.2020))[-c(3, 11, 13)])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2020), 
-  uds.6b.2021[,c(2, grep(pattern = "^%", colnames(uds.6b.2021))[-c(3, 11, 13)])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit), function(x) namingshit) %>% mutate(Year = 2021))
-
-uds.6b.rates$IMM2yo <- gsub(pattern = "%$", replacement = "", uds.6b.rates$IMM2yo)
-uds.6b.rates$Pap <- gsub(pattern = "%$", replacement = "", uds.6b.rates$Pap)
-uds.6b.rates$ChildBMI <- gsub(pattern = "%$", replacement = "", uds.6b.rates$ChildBMI)
-uds.6b.rates$AdultBMI <- gsub(pattern = "%$", replacement = "", uds.6b.rates$AdultBMI)
-
-uds.6b.rates$Tobac <- gsub(pattern = "%$", replacement = "", uds.6b.rates$Tobac)
-uds.6b.rates$CRC <- gsub(pattern = "%$", replacement = "", uds.6b.rates$CRC)
-uds.6b.rates$DepScrn <- gsub(pattern = "%$", replacement = "", uds.6b.rates$DepScrn)
-
-uds.6b.denom <- rbind(
-  uds.6b.2014[,c(2, grep(pattern = "^Total", colnames(uds.6b.2014))[-6])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2014), 
-  uds.6b.2015[,c(2, grep(pattern = "^Total", colnames(uds.6b.2015))[-6])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2015),
-  uds.6b.2016[,c(2, grep(pattern = "^Total", colnames(uds.6b.2016))[-6])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2016),
-
-  uds.6b.2017[,c(2, grep(pattern = "^Total", colnames(uds.6b.2017))[-6])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2017),
-  uds.6b.2018[,c(2, grep(pattern = "^Total", colnames(uds.6b.2018))[-6])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2018),
-
-  uds.6b.2019[,c(2, grep(pattern = "^Total", colnames(uds.6b.2019))[-6])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2019),
-  uds.6b.2020[,c(2, grep(pattern = "^Total", colnames(uds.6b.2020))[-c(3, 11, 13)])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2020),
-  uds.6b.2021[,c(2, grep(pattern = "^Total", colnames(uds.6b.2021))[-c(3, 11, 13)])][,c(1:6, 9, 11)] %>% 
-  rename_all(vars(namingshit.denom), function(x) namingshit.denom) %>% mutate(Year = 2021))
-
-for (k in 2:8) uds.6b.rates[grep("-", unlist(uds.6b.rates[,k])),k] <- NA
-for (k in 2:8) uds.6b.denom[grep("-", unlist(uds.6b.denom[,k])),k] <- NA
-
-uds.6b.rates <-  data.frame(GrantNumber = uds.6b.rates$GrantNumber, Year = uds.6b.rates$Year, lapply(uds.6b.rates[,c(2:8)], as.numeric)) 
-uds.6b.denom <-  data.frame(GrantNumber = uds.6b.denom$GrantNumber, Year = uds.6b.denom$Year, lapply(uds.6b.denom[,c(2:8)], as.numeric))
-
-uds.6b.rates[uds.6b.rates$Year == 2014,c(3:9)] <- uds.6b.rates[uds.6b.rates$Year == 2014,c(3:9)] * 100
-uds.6b.rates[,c(3:9)] <- uds.6b.rates[,c(3:9)]
-
-## Finding highest-scoring quality FQHC
-# uds.6b.rates %>% 
-#   mutate(Qcomp = (IMM2yo + Pap + ChildBMI + AdultBMI + Tobac + CRC + DepScrn) / 7) %>% 
-#   arrange(desc(Qcomp)) %>% 
-#   filter(Year == 2021) %>% 
-#   select(GrantNumber, Year, Qcomp) %>% 
-#   left_join(chc %>% select(Health.Center.Number, Health.Center.Name, Health.Center.Organization.City, Health.Center.Organization.State) %>% unique(), by = c("GrantNumber" = "Health.Center.Number")) %>%
-#   left_join(uds.6b.denom, by = c("GrantNumber","Year"))
-
-```
-
-## Read in Technology Data
-```{r}
-
-uds.HIT.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "EHRInformation", skip = 0) %>% 
-  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
-uds.HIT.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "EHRInformation", skip = 2) %>% 
-  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
-uds.HIT.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
-  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
-
-uds.HIT.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
-  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
-uds.HIT.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
-  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
-uds.HIT.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
-  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
-
-uds.HIT.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>%
-  select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)
-uds.HIT.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "HITInformation", skip = 0) %>%
-  select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)
-
-uds.HIT.2020 <- data.frame(GrantNumber = uds.HIT.2020[,1], Tehr_L1b_Ca = uds.HIT.2020[,2], Tehr_L2_Ca = NA,	Tehr_L3_Ca = NA, Tehr_L4_Ca = uds.HIT.2020[,3], Tehr_L5_Ca = NA, Tehr_L7_Ca = uds.HIT.2020[,4])
-uds.HIT.2021 <- data.frame(GrantNumber = uds.HIT.2021[,1], Tehr_L1b_Ca = uds.HIT.2021[,2], Tehr_L2_Ca = NA,	Tehr_L3_Ca = NA, Tehr_L4_Ca = uds.HIT.2021[,3], Tehr_L5_Ca = NA, Tehr_L7_Ca = uds.HIT.2021[,4])
-
-namevec <- c("Year", "Grant Number", "SwitchEMR","eScripts","eDecisionSupport","InterOrgHITexchange","PatientPortals","UDSQualRep")
-uds.HIT <- rbind(cbind(Year = 2014, uds.HIT.2014),
-                  cbind(Year = 2015, uds.HIT.2015),
-                  cbind(Year = 2016, uds.HIT.2016),
-                  cbind(Year = 2017, uds.HIT.2017),
-
-                  cbind(Year = 2018, uds.HIT.2018),
-                  cbind(Year = 2019, uds.HIT.2019), 
-                  cbind(Year = 2020, uds.HIT.2020),
-                  cbind(Year = 2021, uds.HIT.2021)) %>%
-
-  rename_all(vars(namevec), function(x) namevec) %>% 
-  mutate(UDSQualRep.levels = ifelse(UDSQualRep == "-", NA, 
-                             ifelse(UDSQualRep == "We do not use the EHR", 0, 
-                             ifelse(UDSQualRep == "We use the EHR but only to access individual patient charts", 1, 
-                             ifelse(UDSQualRep == "We use the EHR in combination with another data analytic system", 3, 2))))) %>% 
-  mutate(UDSQualRep.highlowuse = ifelse(UDSQualRep == "-", NA, 
-                             ifelse(UDSQualRep == "We do not use the EHR" | UDSQualRep == "We use the EHR but only to access individual patient charts", 0, 1))) %>%  
-  mutate(SwitchEMR = ifelse(SwitchEMR == "-", NA, ifelse(SwitchEMR == "Yes", 1, 0)),
-         eScripts = ifelse(eScripts == "-" | eScripts == "Not Sure", NA, ifelse(eScripts == "Yes", 1, 0)),
-         eDecisionSupport = ifelse(eDecisionSupport == "-" | eDecisionSupport == "Not Sure", NA, ifelse(eDecisionSupport == "Yes", 1, 0)),
-         InterOrgHITexchange = ifelse(InterOrgHITexchange == "-" | InterOrgHITexchange == "Not Sure", NA, ifelse(InterOrgHITexchange %in% c("No","None of the above"), 0, 1)),
-         PatientPortals = ifelse(PatientPortals == "-" | PatientPortals == "Not Sure", NA, ifelse(PatientPortals %in% c("No","No we do not engage patients using HIT"), 0, 1)))
-
-uds.HIT[uds.HIT$UDSQualRep.levels == 0 & !is.na(uds.HIT$UDSQualRep.levels) & is.na(uds.HIT$SwitchEMR),]$SwitchEMR <- 0
-uds.HIT[uds.HIT$UDSQualRep.levels == 0 & !is.na(uds.HIT$UDSQualRep.levels) & is.na(uds.HIT$eScripts),]$eScripts <- 0
-uds.HIT[uds.HIT$UDSQualRep.levels == 0 & !is.na(uds.HIT$UDSQualRep.levels) & is.na(uds.HIT$eDecisionSupport),]$eDecisionSupport <- 0
-uds.HIT[uds.HIT$UDSQualRep.levels == 0 & !is.na(uds.HIT$UDSQualRep.levels) & is.na(uds.HIT$InterOrgHITexchange),]$InterOrgHITexchange <- 0
-uds.HIT[uds.HIT$UDSQualRep.levels == 0 & !is.na(uds.HIT$UDSQualRep.levels) & is.na(uds.HIT$PatientPortals),]$PatientPortals <- 0
-
-# namevec <- c("Year", "Grant Number", "SwitchEMR","InterOrgHITexchange","UDSQualRep")
-# uds.HIT <- rbind(cbind(Year = 2014, uds.HIT.2014 %>% select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)),
-#                   cbind(Year = 2015, uds.HIT.2015 %>% select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)),
-#                   cbind(Year = 2016, uds.HIT.2016 %>% select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)),
-#                   cbind(Year = 2017, uds.HIT.2017 %>% select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)),
-#                   
-#                   cbind(Year = 2018, uds.HIT.2018 %>% select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)),
-#                   cbind(Year = 2019, uds.HIT.2019 %>% select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)),          
-#                   cbind(Year = 2020, uds.HIT.2020)) %>% 
-#   
-#   rename_all(vars(namevec), function(x) namevec) %>% 
-#   mutate(UDSQualRep.levels = ifelse(UDSQualRep == "-", NA, 
-#                              ifelse(UDSQualRep == "We do not use the EHR", 0, 
-#                              ifelse(UDSQualRep == "We use the EHR but only to access individual patient charts", 1, 
-#                              ifelse(UDSQualRep == "We use the EHR in combination with another data analytic system", 3, 2))))) %>% 
-#   mutate(UDSQualRep.highlowuse = ifelse(UDSQualRep == "-", NA, 
-#                              ifelse(UDSQualRep == "We do not use the EHR" | UDSQualRep == "We use the EHR but only to access individual patient charts", 0, 1))) %>%  
-#   mutate(SwitchEMR = ifelse(SwitchEMR == "-", NA, ifelse(SwitchEMR == "Yes", 1, 0)),
-#          InterOrgHITexchange = ifelse(InterOrgHITexchange == "-" | InterOrgHITexchange == "Not Sure", NA, ifelse(InterOrgHITexchange %in% c("No","None of the above"), 0, 1)))
-
-```
-
-## Read in Covariates
-```{r}
-# Table 3B
-uds.3B.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
-uds.3B.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table3B", skip = 2) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
-uds.3B.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-
-uds.3B.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-uds.3B.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-uds.3B.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-
-uds.3B.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-uds.3B.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-
-namevec <- c("Year", "Grant Number", "NHA", "NHB", "HL", "NHW", "Total", "Eng2ndLang")
-uds.3B <- rbind(cbind(Year = 2014, uds.3B.2014),
-                  cbind(Year = 2015, uds.3B.2015),
-                  cbind(Year = 2016, uds.3B.2016),
-                  cbind(Year = 2017, uds.3B.2017),
-
-                  cbind(Year = 2018, uds.3B.2018),
-                  cbind(Year = 2019, uds.3B.2019), 
-                  cbind(Year = 2020, uds.3B.2020),
-                  cbind(Year = 2021, uds.3B.2021)) %>%
-
-  rename_all(vars(namevec), function(x) namevec)
-
-# Table 4
-uds.4.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-uds.4.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table4", skip = 2) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-uds.4.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-
-uds.4.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-uds.4.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-uds.4.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-
-uds.4.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-uds.4.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-
-namevec <- c("Year", "Grant Number", "<100%", "101-150%", "151-200%", ">200%", "Unknown", "FarmWorker", "Homeless", "0-17yo", "18+yo")
-uds.4 <- rbind(cbind(Year = 2014, uds.4.2014),
-                  cbind(Year = 2015, uds.4.2015),
-                  cbind(Year = 2016, uds.4.2016),
-                  cbind(Year = 2017, uds.4.2017),
-
-                  cbind(Year = 2018, uds.4.2018),
-                  cbind(Year = 2019, uds.4.2019), 
-                  cbind(Year = 2020, uds.4.2020),
-                  cbind(Year = 2021, uds.4.2021)) %>%
-
-  rename_all(vars(namevec), function(x) namevec)
-
-# Put covariate tables together
-
-uds.covariates <- inner_join(uds.3B, uds.4, by = c("Year","Grant Number"))
-
-for (i in 3:ncol(uds.covariates)){
-  uds.covariates[,i] <- as.numeric(gsub("-", "", uds.covariates[,i]))
-}
-
-#uds.covariates %>% filter(`Grant Number` == "H80CS24200")
-
-uds.covariates <-  uds.covariates %>% 
-    mutate(Pct.NHA = NHA / Total * 100,
-         Pct.NHB = NHB / Total * 100,
-         Pct.HL = HL / Total * 100,
-         Pct.NHW = NHW / Total * 100,
-         Pct.ESL = Eng2ndLang / Total * 100,
-         Pct.LessThan100pctFPL = ifelse(Total == Unknown, 100, `<100%` / (Total- Unknown) * 100),
-         Pct.LessThan200pctFPL = ifelse(Total == Unknown, 100, (`<100%` + `101-150%` + `151-200%`) / (Total - Unknown) * 100),
-         Pct.FarmWorker = FarmWorker / Total * 100,
-         Pct.Homeless = Homeless / Total * 100,
-         Pct.Children = `0-17yo` / Total * 100) %>% 
-    select(Year, `Grant Number`, Pct.NHA:Pct.Children)
-
-```
-
-## Read in Clinical Outcomes
-```{r}
-uds.7.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table7_1", skip = 0) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
-uds.7.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table7_1", skip = 2) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
-uds.7.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)
-
-uds.7.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
-uds.7.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
-uds.7.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)
-
-uds.7.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
-uds.7.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table7_1", skip = 0) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)
-
-namevec <- c("Year", "Grant Number", "TotalDeliveries", "BirthsLT1500","Births1500to2499","BirthsGTE2500","TotalHTN","Sample","Controlcount")
-uds.7 <- rbind(cbind(Year = 2014, uds.7.2014),
-                  cbind(Year = 2015, uds.7.2015),
-                  cbind(Year = 2016, uds.7.2016),
-                  cbind(Year = 2017, uds.7.2017),
-
-                  cbind(Year = 2018, uds.7.2018),
-                  cbind(Year = 2019, uds.7.2019), 
-                  cbind(Year = 2020, uds.7.2020),
-                  cbind(Year = 2021, uds.7.2021)) %>%
-
-  rename_all(vars(namevec), function(x) namevec)
-
-for (i in 3:ncol(uds.7)){
-  uds.7[,i] <- as.numeric(gsub("-", "", uds.7[,i]))
-}
-
-```
-
-## Read in my financial data
-## Prep download
-```{r}
-
-cw <- read_excel("/Users/jhm65/Research/CHC Costs/UDS-990 Crosswalk.xlsx")
-
-## Wave 1
-
-EINs <- cw[!is.na(cw$EIN),]$EIN
-
-urls <- paste("https://www.guidestar.org/profile/GetFTASheet?ein=", cw[!is.na(cw$EIN),]$EIN, "&guid=", sep = "")
-destfiles <- paste("/Users/jhm65/Research/CHC Costs/990s/", cw[!is.na(cw$EIN),]$EIN, ".xlsx", sep = "") #990s_new or 990s
-
-## Set Binary filter for data to include
-z <- rep(NA, length(urls))
-for (k in 1:length(EINs)){  #1174
-
- z[k] <- ifelse(is.data.frame(try(read_excel(destfiles[k], skip = 5) )) == TRUE, 1, 0)
-
-}
-
-## Set first rows in data
-chc.990 <- read_excel(destfiles[1], skip = 5)
-years <- as.numeric(colnames(chc.990)[-1])
-chc.990 <- chc.990[-c(5, 6, 15, 16, 25, 26, 32, 33, 34, 35, 39, 40, 52:58),]
-
-chc.990[,2] <- as.numeric(gsub(unlist(chc.990[,2]), pattern = "N/A", replacement = NA))
-chc.990[,3] <- as.numeric(gsub(unlist(chc.990[,3]), pattern = "N/A", replacement = NA))
-chc.990[,4] <- as.numeric(gsub(unlist(chc.990[,4]), pattern = "N/A", replacement = NA))
-chc.990[,5] <- as.numeric(gsub(unlist(chc.990[,5]), pattern = "N/A", replacement = NA))
-chc.990[,6] <- as.numeric(gsub(unlist(chc.990[,6]), pattern = "N/A", replacement = NA))
-
-headers <- unlist(chc.990[,1])
-chc.990 <- data.frame(t(chc.990[,-1]))
-
-colnames(chc.990) <- headers
-rownames(chc.990) <- NULL
-
-chc.finances <- cbind(ID = EINs[1], year = years, chc.990)
-
-## Repeat for the whole set
-for (k in 2:1174){
-  if(z[k] == 1 & k %notin% c(388, 511, 670)){ ##remove entries for now, check later if this clinic gets data
-chc.990 <- read_excel(destfiles[k], skip = 5)
-years <- as.numeric(colnames(chc.990)[-1])
-chc.990 <- chc.990[-c(5, 6, 15, 16, 25, 26, 32, 33, 34, 35, 39, 40, 52:58),]
-
-  for (j in 2:ncol(chc.990)){
-    chc.990[,j] <- as.numeric(gsub(unlist(chc.990[,j]), pattern = "N/A", replacement = NA))
-  }
-
-headers <- unlist(chc.990[,1])
-chc.990 <- data.frame(t(chc.990[,-1]))
-
-colnames(chc.990) <- headers
-rownames(chc.990) <- NULL
-
-chc.finances <- rbind(chc.finances, cbind(ID = EINs[k], year = years, chc.990) )} else {print(k)}
-}
-
-table(chc.finances$year)
-
-quantile(chc.finances$`Unrestricted surplus (deficit) after depreciation`, probs = c(0, 0.025, 0.1, 0.25, 0.5, 0.75, 0.9, 0.975, 1))
-
-colnames(chc.finances) <- gsub("\\%", "pct", colnames(chc.finances))
-colnames(chc.finances)[c(4, 6)] <- c("Surplus as a pct of before dep expenses","Surplus as a pct of after dep expenses")
-
-## Wave 2
-
-EINs <- cw[!is.na(cw$EIN),]$EIN
-
-urls <- paste("https://www.guidestar.org/profile/GetFTASheet?ein=", cw[!is.na(cw$EIN),]$EIN, "&guid=", sep = "")
-destfiles <- paste("/Users/jhm65/Research/CHC Costs/990s_new/", cw[!is.na(cw$EIN),]$EIN, ".xlsx", sep = "") #990s_new or 990s
-
-## Set Binary filter for data to include
-z <- rep(NA, length(urls))
-for (k in 1:length(EINs)){  #1174
-
- z[k] <- ifelse(is.data.frame(try(read_excel(destfiles[k], skip = 5) )) == TRUE, 1, 0)
-
-}
-
-## Set first rows in data
-chc.990 <- read_excel(destfiles[1], skip = 5)
-years <- as.numeric(colnames(chc.990)[-1])
-chc.990 <- chc.990[-c(5, 6, 15, 16, 25, 26, 32, 33, 34, 35, 39, 40, 52:58),]
-
-chc.990[,2] <- as.numeric(gsub(unlist(chc.990[,2]), pattern = "N/A", replacement = NA))
-chc.990[,3] <- as.numeric(gsub(unlist(chc.990[,3]), pattern = "N/A", replacement = NA))
-chc.990[,4] <- as.numeric(gsub(unlist(chc.990[,4]), pattern = "N/A", replacement = NA))
-chc.990[,5] <- as.numeric(gsub(unlist(chc.990[,5]), pattern = "N/A", replacement = NA))
-chc.990[,6] <- as.numeric(gsub(unlist(chc.990[,6]), pattern = "N/A", replacement = NA))
-
-headers <- unlist(chc.990[,1])
-chc.990 <- data.frame(t(chc.990[,-1]))
-
-colnames(chc.990) <- headers
-rownames(chc.990) <- NULL
-
-chc.fin.2 <- cbind(ID = EINs[1], year = years, chc.990)
-
-## Repeat for the whole set
-for (k in 2:1174){
-  if(z[k] == 1 & k %notin% c(388, 511, 670)){ ##remove entries for now, check later if this clinic gets data
-chc.990 <- read_excel(destfiles[k], skip = 5)
-years <- as.numeric(colnames(chc.990)[-1])
-chc.990 <- chc.990[-c(5, 6, 15, 16, 25, 26, 32, 33, 34, 35, 39, 40, 52:58),]
-
-  for (j in 2:ncol(chc.990)){
-    chc.990[,j] <- as.numeric(gsub(unlist(chc.990[,j]), pattern = "N/A", replacement = NA))
-  }
-
-headers <- unlist(chc.990[,1])
-chc.990 <- data.frame(t(chc.990[,-1]))
-
-colnames(chc.990) <- headers
-rownames(chc.990) <- NULL
-
-chc.fin.2 <- rbind(chc.fin.2, cbind(ID = EINs[k], year = years, chc.990) )} else {print(k)}
-}
-
-table(chc.fin.2$year)
-
-quantile(chc.fin.2$`Unrestricted surplus (deficit) after depreciation`, probs = c(0, 0.025, 0.1, 0.25, 0.5, 0.75, 0.9, 0.975, 1))
-
-colnames(chc.fin.2) <- gsub("\\%", "pct", colnames(chc.fin.2))
-colnames(chc.fin.2)[c(4, 6)] <- c("Surplus as a pct of before dep expenses","Surplus as a pct of after dep expenses")
-
-nrow(chc.finances[chc.finances$`Unrestricted surplus (deficit) after depreciation` <= 250000 & chc.finances$year == 2017,]) / nrow(chc.finances[chc.finances$year == 2017,])
-
-```
-
-## Read in my termination crosswalk to filter out closures
-```{r}
-chc.term <- read.csv("CHC_termination_crosswalk.csv")
-staffing <- read.csv("/Users/jhm65/Research/CHC Costs/FQHC_Staffing.csv")
-```
-
-## Read in census data for all zip codes
-```{r}
-
-census <- data.frame(ZipCode = 0, NAME = 0, YEAR = 0, 
-                     TotalPop = 0,
-                     Male = 0, Female = 0, 
-                     AgeUnder18 = 0, Age18to64 = 0, Age65andOver = 0, 
-                     White = 0, Black = 0, AIAN = 0, Asian = 0, MR = 0, Hispanic = 0, EducLow = 0, EducMid = 0, EducHigh = 0, 
-                     PovertyStatusDet = 0, IncomeBelowPoverty = 0, Unemployed = 0, Unemp_denom = 0, 
-                     MCD.denom = 0, Medicaid = 0, Unins.denom = 0, Uninsured = 0)
-
-for (i in 1:7){
-  census <- rbind(census, get_acs(geography = "zcta", survey = "acs5",
-                       variables = c("B01003_001","B17001_001","B17001_002","B01001_002","B01001_026",
-                                     "B02001_002","B02001_003","B02001_004","B02001_005","B02001_006","B02001_008",
-                                     "B03001_003", 
-                                     "B01001_003","B01001_004","B01001_005","B01001_006","B01001_007","B01001_008","B01001_009",
-                                     "B01001_010","B01001_011","B01001_013","B01001_014","B01001_015","B01001_016","B01001_017",
-                                     "B01001_018","B01001_019","B01001_020","B01001_021","B01001_022","B01001_023","B01001_024","B01001_025",
-                                     "B01001_027","B01001_028","B01001_029","B01001_030","B01001_031","B01001_032","B01001_033","B01001_034",
-                                     "B01001_035","B01001_036","B01001_037","B01001_038","B01001_039","B01001_040","B01001_041","B01001_042","B01001_043",
-                                     "B01001_044","B01001_045","B01001_046","B01001_047","B01001_048","B01001_049",
-                                     "B06009_002","B06009_003", "B06009_004","B06009_005","B06009_006",
-                                     "B23025_002","B23025_005",
-                                     "C27007_001", "C27007_004", "C27007_007", "C27007_010", "C27007_014", "C27007_017", "C27007_020",
-                                     "B18135_001","B18135_007","B18135_012","B18135_018","B18135_023","B18135_029","B18135_034"), 
-                       year = 2013 + i) %>% 
-  pivot_wider(id_cols = c(GEOID, NAME), names_from = variable, values_from = estimate) %>% 
-    mutate(YEAR = 2013 + i, TotalPop = B01003_001, PovertyStatusDet = B17001_001, IncomeBelowPoverty = B17001_002,
-           AgeUnder18 = B01001_003 + B01001_004 + B01001_005 + B01001_006 + B01001_027 + B01001_028 + B01001_029 + B01001_030,
-           Age18to64 = B01001_007 + B01001_008 + B01001_009 + B01001_010 + B01001_011 + B01001_013 + B01001_014 + B01001_015 + 
-                       B01001_016 + B01001_017 + B01001_018 + B01001_019 + B01001_031 + B01001_032 + B01001_033 + B01001_034 +
-                       B01001_035 + B01001_036 + B01001_037 + B01001_038 + B01001_039 + B01001_040 + B01001_041 + B01001_042 + B01001_043, 
-           Age65andOver = B01001_020 + B01001_021 + B01001_022 + B01001_023 + B01001_024 + B01001_025 + 
-                          B01001_044 + B01001_045 + B01001_046 + B01001_047 + B01001_048 + B01001_049, 
-           Male = B01001_002, Female = B01001_026, 
-           White = B02001_002, Black = B02001_003, AIAN = B02001_004, Asian = B02001_005 + B02001_006, MR = B02001_008, 
-           Hispanic = B03001_003, 
-           EducLow = B06009_002, EducMid = B06009_003 + B06009_004, EducHigh = B06009_005 + B06009_006,
-           Unemployed = B23025_005, Unemp_denom = B23025_002,
-           MCD.denom = C27007_001	, Medicaid = C27007_004	 + C27007_007 + C27007_010	+ C27007_014 + C27007_017 + C27007_020,
-           Unins.denom = B18135_001, Uninsured = B18135_007 + B18135_012 + B18135_018 + B18135_023 + B18135_029 + B18135_034) %>% 
-    select(ZipCode = GEOID, NAME, YEAR, TotalPop:Uninsured))
-
-  print(i)
-}
-census <- census[-1,]
-
-##########
-census$ZipCode <- substr(census$NAME, 7, 11)
-#census$ZipCode <- str_pad(census$ZipCode, 5, pad = "0")
-
-census %>% 
-  filter(YEAR == 2020) %>% 
-  select(ZipCode) %>% 
-  #unique() %>% 
-  table() %>% 
-  table()
-```
-
-# Analysis
-## SEt data again
-
-```{r}
-
-uds.sites[!is.na(uds.sites$Zip),] %>% 
-  group_by(`Grant Number`, Zip, Year) %>% 
-  summarise(Counts = n()) %>% 
-  select(`Grant Number`, Zip, Year, Counts) %>% 
-  unique() %>% 
-  arrange(Year) %>% 
-  pivot_wider(id_cols = c(`Grant Number`, Zip), names_from = Year, values_from = Counts, values_fill = 0) %>% 
-  arrange(Zip)
-
-```
-
-## Set Data
-```{r}
-# Identify number of clinics in each zip code-year
-clinics.in.zips <- uds.sites[!is.na(uds.sites$Zip),] %>%
-  group_by(Zip, Year) %>%
-  summarise(Clinics = n_distinct(`Grant Number`), Sites = n()) %>%
-  arrange(desc(Clinics))
-
-# Identify clinics in competitive zip codes
-clinics.comp <- uds.sites[!is.na(uds.sites$Zip),] %>% 
-  select(`Grant Number`, Zip, Year) %>% 
-  unique() %>% 
-  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
-  group_by(`Grant Number`, Year) %>% 
-  summarise(Clinics = max(Clinics)) %>% 
-  pivot_wider(id_cols = `Grant Number`, names_from = Year, values_from = Clinics) %>% 
-  filter(`2014` == 1 & `2015` == 1 & `2016` == 1 ) %>%   
-  #filter(`2014` == 1 & `2015` == 1) %>%  
-  left_join(chc.term, by = c("Grant Number" = "ClinicID")) %>%
-  filter(is.na(NewClinicID)) %>%
-  select(`Grant Number`:`2021`) %>% 
-  pivot_longer(cols = c(`2014`:`2021`)) %>% 
-  group_by(`Grant Number`) %>% 
-  filter(min(value) == 1 ) %>% 
-  #filter(max(value) == last(value)) %>% 
-  mutate(Tx = ifelse(value > 1, 1, 0))
-
-# Classify clinics by introduction of competition
-df.comp <- left_join(clinics.comp %>% mutate(Year = as.numeric(name)), uds.zip.totals, by = c("Grant Number", "Year" = "Reporting Year")) %>% 
-  left_join(uds.sites[!is.na(uds.sites$Zip),] %>% 
-  group_by(`Grant Number`, Year) %>% 
-  summarise(Sites = n()), by = c("Grant Number", "Year")) %>% 
-  ungroup() %>% 
-  group_by(`Grant Number`) %>% 
-  mutate(Att = min(ifelse(Tx == 0, 2, 1)*Year, na.rm = TRUE) ) %>% 
-  group_by(`Grant Number`) %>% 
-  mutate(Att = ifelse(Att < 2022, Att, 0)) %>% 
-  ungroup() %>% 
-  mutate(ID = as.numeric(factor(`Grant Number`)))
-
-# Identify expandors vs expandees
-df.expand <- df.comp %>% 
-  left_join(
-      left_join(df.comp %>% select(`Grant Number`, Att), uds.sites[!is.na(uds.sites$Zip),] %>% 
-        select(`Grant Number`, Zip, Year) %>% 
-        group_by(`Grant Number`, Zip) %>% 
-        summarise(YearFirstInZip = min(Year)) %>% 
-        filter(YearFirstInZip %notin% c(2014)) %>% 
-        select(`Grant Number`, YearFirstInZip) %>% 
-        unique(), by = c("Grant Number")) %>% #filter(`Grant Number` == "H80CS00101") %>% 
-        mutate(Expandor = ifelse(is.na(YearFirstInZip) | Att != YearFirstInZip, 0, 1)) %>%  #  is.na(YearFirstInZip) | Att != YearFirstInZip
-        group_by(`Grant Number`) %>% summarise(Expandor = max(Expandor)), by = c("Grant Number")) %>% 
-  left_join(uds.HIT, by = c("Grant Number", "Year"))
-
-df.expand <- df.expand %>% 
-  left_join(df.expand %>% filter(SwitchEMR == 1) %>%  
-            select(`Grant Number`, Year, SwitchEMR) %>% 
-            group_by(`Grant Number`) %>% 
-            summarise(FirstSwitch = min(Year)), by = c("Grant Number")) #%>% mutate(SwitchEMR = ifelse(is.na(FirstSwitch), 0, ifelse(Year >= FirstSwitch & FirstSwitch >= 2014, 1, 0)))
-
-df.qual.exp <- df.expand %>% 
-  left_join(uds.6b.rates, by = c("Grant Number" = "GrantNumber", "Year")) %>% 
-  left_join(uds.6b.denom, by = c("Grant Number" = "GrantNumber", "Year")) %>% 
-  #filter(Expandor == 0 & Year %in% c(2015, 2016, 2017, 2018, 2019, 2020) & Att %in% c(0, 2017, 2018, 2019, 2020)) %>%  ## Regular go to analysis
-  filter(Expandor == 0 & Year %in% c(2015, 2016, 2017, 2018, 2019) & Att %in% c(0, 2017, 2018, 2019)) %>%  ## Really pronounced causal responses, weak first order stuff
-  #filter(Expandor == 0 & Year %in% c(2014, 2015, 2016, 2017, 2018, 2019, 2020, 2021) & Att %in% c(0, 2017, 2018, 2019)) %>%
-  left_join(uds.sites %>% 
-    group_by(`Grant Number`, Year) %>% 
-    summarise(TotalAccess = sum(Access, na.rm = T)), by = c("Grant Number","Year")) %>%
-inner_join(uds.sites %>% filter(Year == 2015) %>% select(`Grant Number`, Zip) %>% group_by(`Grant Number`) %>% summarise(Zips = n_distinct(Zip)), by = c("Grant Number")) %>%
-  mutate(ZipFilter = ifelse(Zips > 2.75, 2, 1)) %>% 
-#inner_join(uds.sites %>% filter(Year == 2014) %>% select(`Grant Number`, Zip) %>% group_by(`Grant Number`) %>% summarise(Zips = n_distinct(Zip)) %>% filter(Zips > 2.75), by = c("Grant Number")) %>%
-#inner_join(df.expand %>% filter(Year == 2015) %>% mutate(ZipFilter = ifelse(Total > median(Total), 2, 1)) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
-  mutate(l.Sites = log(Sites),
-         l.Total = log(Total))
-
-k = 1  # 1 for larger group, 0 for smaller clinic group OOOOOOORRRRRRR 2 for large, 1 for medium, and 0 for small
-
-# df.qual.exp <- inner_join(uds.sites %>% select(`Grant Number`, `Site State`) %>% unique(), df.qual.exp, by = c("Grant Number")) %>%
-# mutate(ACA = ifelse((`Site State` %in% c('MI','NH') & Year >= 2014) |
-#                     (`Site State` %in% c('PA','IN','AK') & Year >= 2015) |
-#                     (`Site State` %in% c('MT','LA') & Year >= 2016) |
-#                     (`Site State` %in% c('VA','ME') & Year >= 2019) |
-#                     (`Site State` %in% c('ID','UT','NE') & Year >= 2020) |
-#                     (`Site State` %in% c('OK','MO') & Year >= 2021) |
-#                     (`Site State` %in% c('AZ','AR','CA','CO','CT','DE','DC','HI','IL','IA','KY','MD','MA','MN','NV','NJ','NM','NY','ND','OH','OR','PA','RI','VT','VA','WA') & Year >= 2014), 1, 0)) %>%
-#   select(`Grant Number`, ZipFilter, value:ACA)
-
-# %>%
-#   group_by(`Grant Number`) %>%
-#   filter(max(ACA) == 0 | min(ACA) == 1) %>%
-#   ungroup()
-
-df.qual.exp <- df.qual.exp %>% 
-  mutate(
-    None = None / Total * 100,
-         MCR = MCR / Total * 100,
-         COM = COM / Total * 100,
-         MCD = MCD / Total * 100,
-
-         SwitchEMR = SwitchEMR * 100, 
-         eScripts = eScripts* 100, 
-         eDecisionSupport = eDecisionSupport * 100, 
-         InterOrgHITexchange = InterOrgHITexchange * 100, 
-         PatientPortals = PatientPortals * 100, 
-         UDSQualRep.highlowuse = UDSQualRep.highlowuse * 100) %>% 
-  left_join(uds.covariates, by = c("Grant Number","Year")) %>% 
-  left_join(uds.7, by = c("Grant Number","Year")) %>% 
-  mutate(Pct.HBW = BirthsGTE2500 / TotalDeliveries * 100, 
-         Pct.HTN.CNTRL = Controlcount / Sample * 100) %>%
-
-  left_join(cw %>% select(`Grant Number`, EIN), by = c("Grant Number")) %>% 
-  left_join(unique(rbind(chc.finances, chc.fin.2) %>% group_by(ID, year) %>% summarise_all(max)) %>% 
-  arrange(ID, year), by = c("EIN" = "ID", "Year" = "year")) %>% 
-  mutate(Liabilities = `Liabilities (as pct of assets)` * `Total net assets`, 
-         Staffing = `Total expenses before depreciation` * Personnel, 
-         LBE.pct = `Gross land, buildings and equipment (LBE)` / `Total net assets`, 
-         `Liabilities (as pct of assets)` = `Liabilities (as pct of assets)` * 100, 
-         `Surplus as a pct of before dep expenses` = `Surplus as a pct of before dep expenses` * 100, 
-         Qcomp = (IMM2yo + Pap + ChildBMI + AdultBMI + Tobac + CRC + DepScrn) / 7, 
-         CostOfCare = `Total expenses before depreciation` / Total) %>%
-
-  mutate(Liquidity =  `Total net assets` / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
-         Profitability =  `Unrestricted surplus (deficit) before depreciation` / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
-         Efficiency = (`Total revenue (unrestricted & restricted)` - `Total expenses before depreciation`) / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
-         NetWorth = (100 - `Liabilities (as pct of assets)`) / `Liabilities (as pct of assets)` / 100) %>% 
-  mutate(Altmans.Z = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% # 6.56, 3.26, 6.72, 1.05  OR 0.18, 0.3, 0.81, 0.14
-  mutate(Liquidity = ifelse(Liquidity == 'Inf', NA, Liquidity), 
-         Profitability = ifelse(Profitability == 'Inf', NA, Profitability), 
-         Efficiency = ifelse(Efficiency == 'Inf', NA, Efficiency), 
-         NetWorth = ifelse(NetWorth == 'Inf', NA, NetWorth), 
-         Altmans.Z = ifelse(Altmans.Z == 'Inf', NA, Altmans.Z)) #%>%   filter(!is.na(Altmans.Z) & Altmans.Z != 'Inf')
-
-df.qual.exp %>%
-  group_by(Att, Expandor) %>%
-  summarise(n() / 6)
-
-df.qual.exp %>% 
-  group_by(Tx) %>% 
-  summarise(mean(Altmans.Z, na.rm = TRUE), sd(Altmans.Z, na.rm = TRUE))
-
-##########
-## Using penetration rate to filter instead of zip codes
-##########
-#IncomeBelowPoverty
-
-years <- unique(df.qual.exp$Year)
-
-#FQHC penetration rate by zip code
-temp1 <- uds.zip %>%
-  filter(`Reporting Year` == 2015 ) %>%
-  inner_join(uds.sites[!is.na(uds.sites$Zip),] %>%
-              filter(Year %in% years), by = c("Grant Number","Zip Code" = "Zip", "Reporting Year" = "Year")) %>%
-  select(`Grant Number`, `Reporting Year`, `Zip Code`, `Total Number of Patients`) %>%
-  left_join(census, by = c("Zip Code" = "ZipCode","Reporting Year" = "YEAR")) %>% #,"Reporting Year" = "YEAR"
-  mutate(MarketShare = `Total Number of Patients` / IncomeBelowPoverty) %>%#IncomeBelowPoverty or TotalPop
-  unique()
-
-temp1 %>% 
-  filter(`Reporting Year` == 2020)
-
-census %>% filter(YEAR == 2020)
-# FQHC weighted average penetration rate conditional on site in zip
-
-temp2 <- temp1 %>%
-  mutate(Num = IncomeBelowPoverty * MarketShare) %>%
-  group_by(`Grant Number`, `Reporting Year`) %>%
-  summarise(Num = sum(Num, na.rm = TRUE)) %>%
-  left_join(temp1 %>%
-  group_by(`Grant Number`, `Reporting Year`) %>%
-  summarise(YTotal = sum(IncomeBelowPoverty, na.rm = TRUE)), by = c("Grant Number","Reporting Year")) %>% #IncomeBelowPoverty
-  mutate(MarketShare = Num / YTotal) %>%
-  select(`Grant Number`, `Reporting Year`, MarketShare)
-
-df.qual.exp <- df.qual.exp %>%
-  select(`Grant Number`, value:Altmans.Z) %>% 
-  left_join(temp2, by = c("Grant Number")) %>% #,"Year" = "Reporting Year")) %>%
-  #mutate(ZipFilter = ifelse(MarketShare > median(MarketShare, na.rm = FALSE), 2,  # - 0.25
-  #                   ifelse(is.na(MarketShare) == T, 1, 1))) %>%
-  mutate(ZipFilter = ifelse(MarketShare >= median(MarketShare, na.rm = TRUE), 2, 1)) %>% #median(MarketShare, na.rm = TRUE)
-  select(`Grant Number`, ZipFilter, MarketShare, value:Altmans.Z) %>%
-  # inner_join(df.qual.exp %>% filter(Year == 2016) %>% mutate(Filter = ifelse(`Surplus as a pct of after dep expenses` < 0, 1, 
-  #                                                                     ifelse(`Surplus as a pct of after dep expenses` > 0.03, 2, NA))) %>% select(`Grant Number`, Filter), by = c("Grant Number")) %>%
-  # select(`Grant Number`, ZipFilter, Filter, MarketShare, value:Altmans.Z) %>% 
-  #mutate(ZipFilter = Filter) %>% 
-  unique()
-
-summary(df.qual.exp$MarketShare)
-summary(df.qual.exp$Zips)
-summary(df.qual.exp$`Surplus as a pct of after dep expenses`)
-
-df.qual.exp %>% mutate(Treat = ifelse(Att > 0, 'Treat','Control')) %>% group_by(ZipFilter, Treat) %>% summarise(n(), n_distinct(ID))
-df.qual.exp %>% filter(`Grant Number` == "H80CS00225")
-
-cnames <- colnames(df.qual.exp)
-
-compare <- read.csv("comeptition.data.final.csv")[,-1]
-colnames(compare) <- cnames
-
-# df.qual.exp <- compare
-# df.qual.exp <- df.qual.exp %>%
-#   #select(`Grant Number`:Year) %>%
-#   inner_join(compare %>% select(`Grant Number`, Year, value), by = c("Grant Number","Year")) %>%
-#   filter(value.x == value.y) %>%
-#   select(`Grant Number`:Altmans.Z) %>%
-#   rename(value = value.x)
-
-df.qual.exp <- df.qual.exp %>% rbind(compare %>% filter(`Grant Number` %in% c("H80CS00765","H80CS00881","H80CS02323") & Year %in% unique(df.qual.exp$Year) )) %>% 
-  filter(`Grant Number` != "H80CS00225")
-
-uds.sites[!is.na(uds.sites$Zip),] %>% 
-  #select(`Grant Number`, Zip, Year) %>% 
-  unique() %>% filter(`Grant Number` %in% c("H80CS00881") & Year == 2016)
-
-# df.qual.exp %>% 
-#   select(`Grant Number`, Year, value) %>% 
-#   full_join(compare %>% select(`Grant Number`, Year, value), by = c("Grant Number","Year")) %>% 
-#   filter(is.na(value.x) | is.na(value.y))
-
-#write.csv(df.qual.exp, file = "comeptition.data.final_2.csv") DO NOT UNCOMMENT THIS LINE AS IT WILL OVERWRITE MY BACKUP DATA
-
-#df.qual.exp <- read.csv("comeptition.data.final_2.csv")
-
-## Add in urbanicity
-all.density <- uds.sites %>% 
-  filter(Year == 2016) %>% 
-  select(`Grant Number`, Zip) %>% 
-  unique()
-
-zipsize2 <- zctas(cb = TRUE, year = 2010)
-
-density.calc <- all.density %>% 
-  left_join(census %>% filter(YEAR == 2016), by = c("Zip" = "ZipCode")) %>% 
-  left_join(zipsize2 %>% select(ZCTA5, CENSUSAREA), by = c("Zip" = "ZCTA5")) %>% 
-  group_by(`Grant Number`) %>% 
-  mutate(num = sum(TotalPop, na.rm = TRUE), denom = sum(CENSUSAREA, na.rm = TRUE)) %>% 
-  mutate(Density = num / denom) %>% 
-  mutate(Pct.Rural = ifelse(Density < 500, 1, 0), 
-         Pct.Urban = ifelse(Density > 2500, 1, 0)) %>% 
-  select(`Grant Number`, Density, Pct.Rural, Pct.Urban) %>% 
-  unique()
-
-df.qual.exp <- df.qual.exp %>% 
-  left_join(density.calc, by = c("Grant Number")) #%>% mutate(ZipFilter = ifelse(Density >= median(Density), 2, 1))
-
-df.expand %>% 
-  filter(`Grant Number` == "H80CS00101")
-
-uds.sites %>% filter(`Grant Number` == "H80CS00101") %>% 
-  group_by(Zip) %>% 
-  summarise(min(Year))
-```
-
 ## What's happening with the closures?

### 2023-08-13 code/data_cleaning.Rmd
sending up some data

@@
 ## Zips
-locs <- paste("UDS/UDS-", c(2014:2021), "-Full-Dataset.xlsx", sep = "")
+locs <- paste("//Users/jhm65/Dropbox/Git/UDS/UDS-", c(2014:2021), "-Full-Dataset.xlsx", sep = "")
 uds.zip <- read_excel(locs[1], sheet = "HealthCenterZipCodes")
@@
 ## Sites
-locs <- paste("UDS/UDS-", c(2014:2021), "-Full-Dataset.xlsx", sep = "")
+locs <- paste("//Users/jhm65/Dropbox/Git/UDS/UDS-", c(2014:2021), "-Full-Dataset.xlsx", sep = "")
 
@@
 
-chc <- read.csv("chc.csv")
+chc <- read.csv("//Users/jhm65/Dropbox/Git/Competition/data_raw/chc.csv")
 
@@
 
-uds.6b.2012 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2013 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
-
-uds.6b.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 1) 
-uds.6b.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
-
-uds.6b.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
-
-uds.6b.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
+uds.6b.2012 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
+uds.6b.2013 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
+
+uds.6b.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
+uds.6b.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 1) 
+uds.6b.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
+
+uds.6b.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
+uds.6b.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
+uds.6b.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
+
+uds.6b.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
+uds.6b.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
 
@@
 
-uds.HIT.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "EHRInformation", skip = 0) %>% 
+uds.HIT.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "EHRInformation", skip = 0) %>% 
   select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
-uds.HIT.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "EHRInformation", skip = 2) %>% 
+uds.HIT.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "EHRInformation", skip = 2) %>% 
   select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
-uds.HIT.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
+uds.HIT.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
   select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
 
-uds.HIT.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
+uds.HIT.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
   select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
-uds.HIT.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
+uds.HIT.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
   select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
-uds.HIT.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
+uds.HIT.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
   select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
 
-uds.HIT.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>%
+uds.HIT.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>%
   select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)
-uds.HIT.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "HITInformation", skip = 0) %>%
+uds.HIT.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "HITInformation", skip = 0) %>%
   select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)
@@
 # Table 3B
-uds.3B.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
-uds.3B.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table3B", skip = 2) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
-uds.3B.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-
-uds.3B.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-uds.3B.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-uds.3B.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-
-uds.3B.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-uds.3B.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
+uds.3B.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
+uds.3B.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table3B", skip = 2) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
+uds.3B.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
+
+uds.3B.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
+uds.3B.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
+uds.3B.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
+
+uds.3B.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
+uds.3B.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
 
@@
 # Table 4
-uds.4.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-uds.4.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table4", skip = 2) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-uds.4.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-
-uds.4.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-uds.4.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-uds.4.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-
-uds.4.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
-uds.4.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
+uds.4.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
+uds.4.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table4", skip = 2) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
+uds.4.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
+
+uds.4.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
+uds.4.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
+uds.4.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
+
+uds.4.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
+uds.4.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)
 
@@
 ```{r}
-uds.7.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table7_1", skip = 0) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
-uds.7.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table7_1", skip = 2) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
-uds.7.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)
-
-uds.7.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
-uds.7.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
-uds.7.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)
-
-uds.7.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
-uds.7.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table7_1", skip = 0) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)
+uds.7.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table7_1", skip = 0) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)
+uds.7.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table7_1", skip = 2) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)
+uds.7.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)
+
+uds.7.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)
+uds.7.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)
+uds.7.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)
+
+uds.7.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)
+uds.7.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table7_1", skip = 0) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)
 
@@
 ```{r}
-chc.term <- read.csv("CHC_termination_crosswalk.csv")
-staffing <- read.csv("/Users/jhm65/Research/CHC Costs/FQHC_Staffing.csv")
+chc.term <- read.csv("//Users/jhm65/Dropbox/Git/Competition/data_raw/CHC_termination_crosswalk.csv")
+staffing <- read.csv("//Users/jhm65/Dropbox/Git/Data/FQHC_Staffing.csv")
 ```

### 2023-08-14 code/analysis.Rmd
adding covariates and streamlining analysis

@@
 ## Figure 4 - Split by profitability
+
 ```{r}
@@
 ## Read in Centroid Data
-zip.centroids <- read.csv("ZIP_Code_Population_Weighted_Centroids.csv") %>% 
+zip.centroids <- read.csv("//Users/jhm65/Dropbox/Git/Data/ZIP_Code_Population_Weighted_Centroids.csv") %>% 
   mutate(ZipCode = str_pad(STD_ZIP5, 5, pad = "0")) %>% 
@@
 
-## Change in Full Market Benefit
+## Change in Full Market Benefit - CAreful this is not great
 ```{r}

### 2023-08-14 code/analysis_Redo.Rmd
adding covariates and streamlining analysis

---
title: "Untitled"
author: "Justin"
date: "2023-08-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

df.sum <- df.qual.exp %>% #filter(`Grant Number` != "H80CS00225") %>% 
  ungroup() %>% 
  #rename(`Grant Number` = Grant.Number, `Surplus as a pct of before dep expenses` = Surplus.as.a.pct.of.after.dep.expenses) %>% 
  #filter(MarketShare < 0.4) %>%  #median(MarketShare, na.rm = TRUE) - 0.25
  #inner_join(df.qual.exp %>% filter(Year == 2015 & Total < 15000) %>% select(`Grant Number`), by = c("Grant Number")) %>%  #& Zips < 1.75 or 7.75
  select(`Grant Number`, Year, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL) %>%
  # inner_join(df.qual.exp %>% filter(Year == 2015) %>%
  #                                           mutate(ZipFilter = ifelse(Total < 12000, 1,
  #                                                              ifelse(Total > 12000, 2, NA))) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
  inner_join(df.qual.exp %>% filter(Year == 2016) %>% #mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% 
               select(`Grant Number`, ZipFilter, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("Grant Number")) %>% 
  select(Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL, Pct.NHA:Pct.Children, MCD, COM, MCR) %>% 
  mutate(Tx = ifelse(Year >= Att, 1, 0), 
         year.rel = Year - Att) %>% 
  unique()

#library(did2s)

did2s(
      data = df.sum %>% filter(ZipFilter == 1), 
      yname = "Sites", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE),#i(year.rel, ref = -1),
        cluster_var = "ID",
      verbose = FALSE
    )

out.qual <- event_study(data = df.sum %>% filter(ZipFilter == 1), 
  yname = "Sites", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM)

out.qual %>% 
  filter(estimator %notin% c("Borusyak, Jaravel, Spiess (2021)","Callaway and Sant'Anna (2020)")) %>% 
filter(abs(term) <= 3) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)

```

### 2023-08-14 code/analysis.Rmd
updated code

@@
 did2s(
-      data = df.spill2, 
-      yname = "MCD.z", 
+      data = df.spill2 , 
+      yname = "Total.Hours", 
       treatment = "Tx",
@@
     )
+
+spill.es <- event_study(data = df.spill2,# %>% filter(ZipFilter == 2), 
+  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all", xformla = ~1)
+
+spill.es %>% 
+  filter(estimator %notin% c("Borusyak, Jaravel, Spiess (2021)")) %>% 
+  filter(abs(term) <= 3) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)
 

### 2023-08-14 code/analysis_Redo.Rmd
updated code

@@
   select(Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL, Pct.NHA:Pct.Children, MCD, COM, MCR) %>% 
-  mutate(Tx = ifelse(Year >= Att, 1, 0), 
-         year.rel = Year - Att) %>% 
+  mutate(Tx = ifelse(Year >= Att & Att > 0, 1, 0)) %>% 
   unique()
@@
 did2s(
-      data = df.sum %>% filter(ZipFilter == 1), 
-      yname = "Sites", 
+      data = df.sum ,#%>% filter(ZipFilter == 2), 
+      yname = "Altmans.Z", 
       treatment = "Tx",
         first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
-        second_stage = ~ i(Tx, ref = FALSE),#i(year.rel, ref = -1),
+        second_stage = ~ i(Tx, ref = FALSE),
         cluster_var = "ID",
@@
 
-out.qual <- event_study(data = df.sum %>% filter(ZipFilter == 1), 
-  yname = "Sites", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM)
+#select(ID, Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z) %>% left_join(df.qual.exp %>% select(ID, Year, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("ID","Year"))
+out.qual <- event_study(data = df.qual.exp,# %>% filter(ZipFilter == 2), 
+  yname = "Altmans.Z", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM)
 
 out.qual %>% 
-  filter(estimator %notin% c("Borusyak, Jaravel, Spiess (2021)","Callaway and Sant'Anna (2020)")) %>% 
+  filter(estimator %notin% c("Borusyak, Jaravel, Spiess (2021)")) %>% 
 filter(abs(term) <= 3) %>% 

### 2023-08-14 code/analysis.Rmd
updates

@@
 did2s(
-      data = df.spill2 , 
-      yname = "Total.Hours", 
+      data = df.spill2 %>% inner_join(df.qual.exp %>% filter(Year == 2016) %>% #mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% 
+               select(`Grant Number`, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("Grant Number")), 
+      yname = "Total.z", 
       treatment = "Tx",
-        first_stage = ~ 0 | Zip + Year + D, 
+        first_stage = ~ 0 | Zip + Year + D + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
         second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),

### 2023-08-14 code/analysis_Redo.Rmd
updates

@@
   #inner_join(df.qual.exp %>% filter(Year == 2015 & Total < 15000) %>% select(`Grant Number`), by = c("Grant Number")) %>%  #& Zips < 1.75 or 7.75
-  select(`Grant Number`, Year, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL) %>%
+  select(`Grant Number`, Year, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL, Total, IMM2yo:DepScrn) %>%
   # inner_join(df.qual.exp %>% filter(Year == 2015) %>%
@@
                select(`Grant Number`, ZipFilter, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("Grant Number")) %>% 
-  select(Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL, Pct.NHA:Pct.Children, MCD, COM, MCR) %>% 
+  select(`Grant Number`, Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL, Pct.NHA:Pct.Children, MCD, COM, MCR, Total, IMM2yo:DepScrn) %>% 
   mutate(Tx = ifelse(Year >= Att & Att > 0, 1, 0)) %>% 
-  unique()
+  unique() %>% 
+  mutate(NewQuality = (CRC + ChildBMI + AdultBMI + Tobac + DepScrn) / 5)
 
@@
       data = df.sum ,#%>% filter(ZipFilter == 2), 
+      yname = "Sites", 
+      treatment = "Tx",
+        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
+did2s(
+      data = df.sum %>% left_join(df.spill2 %>% 
+  group_by(`Grant Number`, Year) %>% 
+  summarise(num = sum((Dist + 1) * Sites), 
+         denom = sum(Sites), 
+         avgdist = num / denom) %>% 
+  filter(Year %in% c(2015, 2019)) %>% 
+  pivot_wider(id_cols = `Grant Number`, names_from = Year, values_from = avgdist) %>% 
+  mutate(ds = `2019` - `2015`) %>% 
+    ungroup() %>% 
+    mutate(filt = ifelse(ds > quantile(ds, 0.5, na.rm = TRUE), 1, 0)), by = c("Grant Number")) %>% filter(filt == 1),#%>% filter(ZipFilter == 2), 
+      yname = "NewQuality", 
+      treatment = "Tx",
+        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
+did2s(
+      data = df.sum %>% left_join(df.spill2 %>% 
+  group_by(`Grant Number`, Year) %>% 
+  summarise(num = sum((Dist + 1) * Sites), 
+         denom = sum(Sites), 
+         avgdist = num / denom), by = c("Grant Number","Year")) ,#%>% filter(ZipFilter == 2), 
       yname = "Altmans.Z", 
@@
         first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
-        second_stage = ~ i(Tx, ref = FALSE),
+        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(avgdist / 10) + I(Tx *as.numeric(avgdist / 10)),
         cluster_var = "ID",

### 2023-08-14 code/data_cleaning.Rmd
adding covariates and streamlining analysis
updated code
updates

@@
 library(directlabels)
+library(did2s)
 
@@
 
-compare <- read.csv("comeptition.data.final.csv")[,-1]
+compare <- read.csv("//Users/jhm65/Dropbox/Git/Competition/data_processed/comeptition.data.final.csv")[,-1]
 colnames(compare) <- cnames
@@
 
-df.qual.exp <- df.qual.exp %>% rbind(compare %>% filter(`Grant Number` %in% c("H80CS00765","H80CS00881","H80CS02323") & Year %in% unique(df.qual.exp$Year) )) %>% 
+df.qual.exp <- df.qual.exp %>% rbind(compare %>% 
+                                       filter(`Grant Number` %in% c("H80CS00765","H80CS00881","H80CS02323") & Year %in% unique(df.qual.exp$Year) )) %>% 
   filter(`Grant Number` != "H80CS00225")

### 2023-08-14 code/analysis_Redo.Rmd
split chunks

@@
 did2s(
-      data = df.sum ,#%>% filter(ZipFilter == 2), 
-      yname = "Sites", 
+      data = df.sum , 
+      yname = "Altmans.Z", 
+      treatment = "Tx",
+        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
+#select(ID, Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z) %>% left_join(df.qual.exp %>% select(ID, Year, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("ID","Year"))
+out.qual <- event_study(data = df.qual.exp %>% filter(ZipFilter == 1), 
+  yname = "Altmans.Z", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM)
+
+out.qual %>% 
+  filter(estimator %notin% c("Borusyak, Jaravel, Spiess (2021)")) %>% 
+filter(abs(term) <= 3) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)
+
+```
+
+## Variations
+
+```{r}
+
+did2s(
+      data = df.sum %>% left_join(df.spill2 %>% 
+  group_by(`Grant Number`, Year) %>% 
+  summarise(num = sum((Dist + 1) * Sites), 
+         denom = sum(Sites), 
+         avgdist = num / denom) %>% 
+  filter(Year %in% c(2015, 2019)) %>% 
+  pivot_wider(id_cols = `Grant Number`, names_from = Year, values_from = avgdist) %>% 
+  mutate(ds = `2019` - `2015`) %>% 
+    ungroup() %>% 
+    mutate(filt = ifelse(ds > median(ds, na.rm = TRUE), 1, 0)), by = c("Grant Number")) %>% filter(filt == 0),#%>% filter(ZipFilter == 2), 
+      yname = "NewQuality", 
       treatment = "Tx",
@@
          avgdist = num / denom) %>% 
-  filter(Year %in% c(2015, 2019)) %>% 
-  pivot_wider(id_cols = `Grant Number`, names_from = Year, values_from = avgdist) %>% 
-  mutate(ds = `2019` - `2015`) %>% 
-    ungroup() %>% 
-    mutate(filt = ifelse(ds > quantile(ds, 0.5, na.rm = TRUE), 1, 0)), by = c("Grant Number")) %>% filter(filt == 1),#%>% filter(ZipFilter == 2), 
+    filter(Year == 2016) %>% select(`Grant Number`, avgdist), by = c("Grant Number")) ,#%>% filter(ZipFilter == 2), 
       yname = "NewQuality", 
-      treatment = "Tx",
-        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
-        second_stage = ~ i(Tx, ref = FALSE),
-        cluster_var = "ID",
-      verbose = FALSE
-    )
-
-did2s(
-      data = df.sum %>% left_join(df.spill2 %>% 
-  group_by(`Grant Number`, Year) %>% 
-  summarise(num = sum((Dist + 1) * Sites), 
-         denom = sum(Sites), 
-         avgdist = num / denom), by = c("Grant Number","Year")) ,#%>% filter(ZipFilter == 2), 
-      yname = "Altmans.Z", 
       treatment = "Tx",
@@
 
-#select(ID, Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z) %>% left_join(df.qual.exp %>% select(ID, Year, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("ID","Year"))
-out.qual <- event_study(data = df.qual.exp,# %>% filter(ZipFilter == 2), 
-  yname = "Altmans.Z", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM)
-
-out.qual %>% 
-  filter(estimator %notin% c("Borusyak, Jaravel, Spiess (2021)")) %>% 
-filter(abs(term) <= 3) %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)
-
 ```

### 2023-08-14 code/analysis_Redo.Rmd
updated with dist delta b

@@
 did2s(
-      data = df.sum , 
-      yname = "Altmans.Z", 
+      data = df.sum %>% inner_join(df.qual.exp %>% filter(MarketShare > 1) %>% select(`Grant Number`) %>% unique(), by = c("Grant Number")), 
+      yname = "Qcomp", 
       treatment = "Tx",
@@
     ungroup() %>% 
-    mutate(filt = ifelse(ds > median(ds, na.rm = TRUE), 1, 0)), by = c("Grant Number")) %>% filter(filt == 0),#%>% filter(ZipFilter == 2), 
+    mutate(filt = ifelse(ds > median(ds, na.rm = TRUE), 1, 0)), by = c("Grant Number")) %>% filter(ds < 1),#%>% filter(ZipFilter == 2), 
       yname = "NewQuality", 
@@
          denom = sum(Sites), 
-         avgdist = num / denom) %>% 
-    filter(Year == 2016) %>% select(`Grant Number`, avgdist), by = c("Grant Number")) ,#%>% filter(ZipFilter == 2), 
+         avgdist = num / denom) , by = c("Grant Number","Year")) ,#%>% filter(ZipFilter == 2), 
       yname = "NewQuality", 
@@
 
+did2s(
+      data = df.sum %>% inner_join(df.z.dist %>% select(`Grant Number.y`, DistToClosestSite), by = c("Grant Number" = "Grant Number.y")) %>% filter(is.na(DistToClosestSite) | DistToClosestSite < 5),
+      yname = "Qcomp", 
+      treatment = "Tx",
+        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
+        second_stage = ~ i(Tx, ref = FALSE) ,
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
 ```

### 2023-08-14 code/analysis_Redo.Rmd
last few updates

@@
 did2s(
-      data = df.sum %>% inner_join(df.z.dist %>% select(`Grant Number.y`, DistToClosestSite), by = c("Grant Number" = "Grant Number.y")) %>% filter(is.na(DistToClosestSite) | DistToClosestSite < 5),
+      data = df.sum %>% left_join(df.z.dist %>% select(`Grant Number.y`, DistToClosestSite), by = c("Grant Number" = "Grant Number.y")) %>% filter(is.na(DistToClosestSite) | DistToClosestSite > 5),
       yname = "Qcomp", 
@@
 
+set.seed(345)
+did2s(
+      data = df.sum %>% left_join(df.z.dist %>% select(`Grant Number.y`, DistToClosestSite), by = c("Grant Number" = "Grant Number.y")) %>% 
+        group_by(ID) %>% 
+  mutate(DistToClosestSite = ifelse(is.na(DistToClosestSite), sample(size = 1, df.z.dist$DistToClosestSite, replace = T), DistToClosestSite)),
+      yname = "NewQuality", 
+      treatment = "Tx",
+        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
+        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(DistToClosestSite / 1) + I(Tx *as.numeric(DistToClosestSite / 1)),
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
 ```

### 2023-08-15 code/data_cleaning_longer.Rmd
mid session updates

---
title: "data_cleaning_longer_period"
author: "Justin"
date: "2023-08-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r}
library(tigris)
library(tidygeocoder)

library(tidyverse)
library(readxl)
library(did)
library(Matching)
library(gtsummary)
library(RODBC)
library(ggpubr)
library(fixest)
library(kableExtra)
library(usmap)
library(did2s)
library(formattable)
library (readr)

`%notin%` <- Negate(`%in%`)
select <- dplyr::select

```

## Formating plots

```{r, echo = FALSE, results = "asis", message=FALSE, warning = FALSE, fig.align="center"}

is.extrafont.installed <- function(){
  if(is.element("extrafont", installed.packages()[,1])){
    library(extrafont)
    # probably need something here to run font_import()
    return(T)
  }else{
    warning("Library extrafont installed; using system sans/serif libraries as fallback fonts. 
    To enable full font support, run: 
      install.packages('extrafont') 
      font_import()")
    return(F)
  }
}

# set font
base_font_family_tufte <- function(){
  if(is.extrafont.installed()){
    library(extrafont)
    tuftefont <- choose_font(c("Gill Sans MT", "Gill Sans", "GillSans", "Verdana", "serif"), quiet = FALSE)   #
  }else{
    tuftefont <- "serif"
  }
  return(tuftefont)
}

theme_tufte_revised <- function(base_size = 11, base_family = base_font_family_tufte(), ticks = TRUE) {

  ret <- theme_bw(base_family = base_family, base_size = base_size) + 
    theme(
      axis.line = element_line(color = 'black'),
      axis.title.x = element_text(vjust = -0.3), 
      axis.title.y = element_text(vjust = 0.8),
      legend.background = element_blank(), 
      legend.key = element_blank(), 
      legend.title = element_text(face="plain"),
      panel.background = element_blank(), 
      panel.border = element_blank(),
      panel.grid = element_blank(),
      plot.background = element_blank(),
      strip.background = element_blank()
    )

  if (!ticks) {
    ret <- ret + theme(axis.ticks = element_blank())
  }

  ret
}

```

# Data Prep

## Sites and ZipCodes
```{r}

## Zips
locs <- paste("/Users/jhm65/Dropbox/Git/UDS/UDS-", c(2014:2021), "-Full-Dataset.xlsx", sep = "")
uds.zip <- read_excel(locs[1], sheet = "HealthCenterZipCodes")

new.zip.names <- c("BHCMIS ID", "Grant Number", "Reporting Year" , "Zip Code", "Zip Code Type",  "None_Uninsured Patients" ,  "Medicaid_CHIP_Other Public Patients", "Medicare Patients", "Private Patients", "Total Number of Patients" ) 
colnames(uds.zip) <-    new.zip.names

for(i in 2:length(locs)){
  temp.zip <- read_excel(locs[i], sheet = "HealthCenterZipCodes")
  colnames(temp.zip) <- new.zip.names
  uds.zip <- rbind(uds.zip, temp.zip %>% mutate(`Zip Code` = str_pad(`Zip Code`, 5, pad = "0")))
}

# ## Rename
# new.zip.names <- c("BHCMIS ID", "Grant Number", "Reporting Year" , "Zip Code", "Zip Code Type",  "None_Uninsured Patients" ,  "Medicaid_CHIP_Other Public Patients", "Medicare Patients", "Private Patients", "Total Number of Patients" ) 
# colnames(uds.zip) <-    new.zip.names
# 
# 
# ## Clean
# 
# uds.zip[uds.zip$`Total Number of Patients`== '-' | uds.zip$`Total Number of Patients`== '--',]$`Total Number of Patients` <- NA
# uds.zip$`Total Number of Patients` <- as.numeric(uds.zip$`Total Number of Patients`)
# uds.zip <- uds.zip[!is.na(uds.zip$`Total Number of Patients`),] %>% 
#     mutate(`Reporting Year` = as.numeric(`Reporting Year`))
# 
# uds.zip$`None_Uninsured Patients` <- as.numeric(uds.zip$`None_Uninsured Patients`)
# uds.zip$`Medicaid_CHIP_Other Public Patients` <- as.numeric(uds.zip$`Medicaid_CHIP_Other Public Patients`)
# uds.zip$`Medicare Patients` <- as.numeric(uds.zip$`Medicare Patients`)
# uds.zip$`Private Patients` <- as.numeric(uds.zip$`Private Patients`)
# 
# 
# uds.zip <- cbind(uds.zip, broken.total = rowSums(uds.zip[,c(6:9)], na.rm = TRUE), missings = rowSums(is.na(uds.zip[,c(6:9)]))) %>% 
#   mutate(`Total Number of Patients` = as.numeric(`Total Number of Patients`)) %>% 
#   mutate(`Total Number of Patients` = ifelse(is.na(`Total Number of Patients`), round(missings*16/4), `Total Number of Patients`)) %>% 
#   mutate(`None_Uninsured Patients` = ifelse(is.na(`None_Uninsured Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `None_Uninsured Patients`), 
#          `Medicaid_CHIP_Other Public Patients` = ifelse(is.na(`Medicaid_CHIP_Other Public Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Medicaid_CHIP_Other Public Patients`), 
#          `Medicare Patients` = ifelse(is.na(`Medicare Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Medicare Patients`), 
#          `Private Patients` = ifelse(is.na(`Private Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Private Patients`))

uds.zip$`Reporting Year` <- as.numeric(uds.zip$`Reporting Year`)
uds.zip$`Total Number of Patients` <- as.numeric(uds.zip$`Total Number of Patients`)
uds.zip$`None_Uninsured Patients` <- as.numeric(uds.zip$`None_Uninsured Patients`)
uds.zip$`Medicaid_CHIP_Other Public Patients` <- as.numeric(uds.zip$`Medicaid_CHIP_Other Public Patients`)
uds.zip$`Medicare Patients` <- as.numeric(uds.zip$`Medicare Patients`)
uds.zip$`Private Patients` <- as.numeric(uds.zip$`Private Patients`)

uds.zip[is.na(uds.zip$`Total Number of Patients`),]$`Total Number of Patients` <- 0
uds.zip[grep("-", uds.zip$`None_Uninsured Patients`),]$`None_Uninsured Patients` <- 0
uds.zip[grep("-", uds.zip$`Medicaid_CHIP_Other Public Patients`),]$`Medicaid_CHIP_Other Public Patients` <- 0
uds.zip[grep("-", uds.zip$`Medicare Patients`),]$`Medicare Patients` <- 0
uds.zip[grep("-", uds.zip$`Private Patients`),]$`Private Patients` <- 0

uds.zip.totals <- uds.zip %>%
  select(`Grant Number`, `Reporting Year`, `None_Uninsured Patients`:`Total Number of Patients`) %>%
  group_by(`Grant Number`, `Reporting Year`) %>% summarise(None = sum(`None_Uninsured Patients`, na.rm = T),
                                                           MCR = sum(`Medicare Patients`, na.rm = T),
                                                           COM = sum(`Private Patients`, na.rm = T),
                                                           MCD = sum(`Medicaid_CHIP_Other Public Patients`, na.rm = T),
                                                           Total = sum(`Total Number of Patients`, na.rm = T))

uds.zip <- uds.zip[uds.zip$`Zip Code Type` == "ZipCode",]

## Sites
locs <- paste("/Users/jhm65/Dropbox/Git/UDS/UDS-", c(2012:2021), "-Full-Dataset.xlsx", sep = "")

uds.sites <- read_excel(locs[1], sheet = "HealthCenterSiteInfo") %>% 
  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>% 
  mutate(Year = 2012)

colnames(uds.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")

for(i in 2:3){
site.temp <- read_excel(locs[i], sheet = "HealthCenterSiteInfo") %>% 
                       select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, 
                              SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>%
  mutate(Year = 2011 + i)

colnames(site.temp) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")

   uds.sites <-  rbind(uds.sites, site.temp)
}

for(i in 4:(length(locs)-1)){
  uds.sites <- rbind(uds.sites, read_excel(locs[i], sheet = "HealthCenterSiteInfo") %>% 
                       select("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code") %>% 
  mutate(Year = 2011 + i))
}

temp.sites <- read_excel(locs[i+1], sheet = "HealthCenterSiteInfo" )%>% 
  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>% 
  mutate(Year = 2021)
colnames(temp.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")

uds.sites <- rbind(uds.sites, temp.sites)

uds.sites.old <- read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Sites.csv", colClasses = "character") %>% 
  mutate(Year = as.numeric(Year))

colnames(uds.sites.old) <- c("BHCMIS ID", "Health Center Name", "Site Name", "Site Street Address", "Site Street Address 2", "Site State", "Site ZIP Code", "Year", "GranteeID", "Site Street Address 3","Site City","ModernGrateeID")

uds.sites.full <- bind_rows(uds.sites, uds.sites.old) %>% 
  arrange(`BHCMIS ID`, Year) %>% 
  select(`BHCMIS ID`:`Health Center Name`, Year, `Site Name`, `Site Street Address`, `Site Street Address 2`, `Site Street Address 3`, `Site City`, `Site State`, `Site ZIP Code` , `Site Type`:`Total Weekly Hours Of Operation`)

uds.sites.full$Zip <- substr(uds.sites.full$`Site ZIP Code`, 1, 5)

uds.sites.full <- uds.sites.full %>% 
  filter(`Site State` %notin% c('GU','VI','PW','MH','AS','FM','PR','MP')) #'AK','HI',

uds.sites.full[grep(pattern = "-", uds.sites.full$Zip),]$Zip <- NA

#write.csv(x = uds.sites.full, file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Sites96to21.csv")

```

## Merge with Older UDSs 1996-2011
```{r}
uds.cw <- read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_CW.csv", colClasses = "character") %>% 
  mutate(link.ID = ifelse(is.na(ModernGranteeID) & !is.na(LongGrantID) & Year != 2010, LongGrantID, 
                   ifelse(is.na(ModernGranteeID) & !is.na(GranteeID), GranteeID, BHCMIS.ID)), 
         Year = as.integer(Year))

uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(BHCMIS.ID == '010060' & Year %in% c(2007:2011)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA)

namevec <- c("BHCMIS.ID", "Year", "NHA", "NHB", "HL", "NHW", "Total", "Eng2ndLang")

#fins.revenue.expenses <- read_csv("FQHC_Revenue_vs_Expenses.csv")
#cw <- read_excel("UDS-990 Crosswalk.xlsx")

```

## Clinic-level in Covariates 
```{r}

# Table 3B

uds.3B.2012 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2013 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)

uds.3B.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table3B", skip = 2) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

uds.3B.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

uds.3B.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

namevec <- c("Year", "BHCMISID", "ModernGranteeID", "NHA", "NHB", "HL", "NHW", "Total", "Eng2ndLang")
uds.3B <- rbind(cbind(Year = 2012, uds.3B.2012),
                cbind(Year = 2013, uds.3B.2013),
                cbind(Year = 2014, uds.3B.2014),
                  cbind(Year = 2015, uds.3B.2015),
                  cbind(Year = 2016, uds.3B.2016),
                  cbind(Year = 2017, uds.3B.2017),

                  cbind(Year = 2018, uds.3B.2018),
                  cbind(Year = 2019, uds.3B.2019), 
                  cbind(Year = 2020, uds.3B.2020),
                  cbind(Year = 2021, uds.3B.2021)) %>%

  rename_all(vars(namevec), function(x) namevec)

uds.3B <- rbind(
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2007)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2008)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA) %>% 
    setNames(namevec),
    uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2009)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2010)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  arrange(BHCMIS.ID, Year) %>% 
  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  filter(Year %in% c(2011)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
    setNames(namevec), 
  uds.3B)
uds.3B %>% 
  arrange(BHCMISID, Year)

# Table 4
uds.4.2012 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb) 
uds.4.2013 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)

uds.4.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb) 
uds.4.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table4", skip = 2) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb) 
uds.4.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)

uds.4.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb) 
uds.4.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb) 
uds.4.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)

uds.4.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb) 
uds.4.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)

namevec <- c("Year", "BHCMISID", "ModernGranteeID", "<100%", "101-150%", "151-200%", ">200%", "Unknown", "FarmWorker", "Homeless", 
             "Uninsured.young", "Uninsured.old", "MCD.young", "MCD.old", "MCR.young", "MCR.old", "OtherPublic.young", "OtherPublic.old", "COM.young", "COM.old")
uds.4 <- rbind(cbind(Year = 2012, uds.4.2012),
               cbind(Year = 2013, uds.4.2013),
               cbind(Year = 2014, uds.4.2014),
                  cbind(Year = 2015, uds.4.2015),
                  cbind(Year = 2016, uds.4.2016),
                  cbind(Year = 2017, uds.4.2017),

                  cbind(Year = 2018, uds.4.2018),
                  cbind(Year = 2019, uds.4.2019), 
                  cbind(Year = 2020, uds.4.2020),
                  cbind(Year = 2021, uds.4.2021)) %>%

  rename_all(vars(namevec), function(x) namevec)

uds.4 <- rbind(
uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table4.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  filter(Year %in% c(2007, 2011)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T4_L1_CA, T4_L2_CA, T4_L3_CA, T4_L4_CA, T4_L5_CA, 
         T4_L16_CA, T4_L23_CA, 
         T4_L7_CA, T4_L7_CB, T4_L8_CA, T4_L8_CB, T4_L9_CA, T4_L9_CB, T4_L10_CA, T4_L10_CB, T4_L11_CA, T4_L11_CB) %>% 
  setNames(namevec), 
uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table4.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  filter(Year %in% c(2008:2010)) %>% 
  select(Year, BHCMIS.ID, ModernGranteeID, T4_L1_CA, T4_L2_CA, T4_L3_CA, T4_L4_CA, T4_L5_CA, 
         T4_L16_CA, T4_L23_CA, 
         T4_L7_CMIA, T4_L7_CMIB, T4_L8_CMIA, T4_L8_CMIB, T4_L9_CMIA, T4_L9_CMIB, T4_L10_CMIA, T4_L10_CMIB, T4_L11_CMIA, T4_L11_CMIB) %>% 
  setNames(namevec), 
uds.4)

uds.4 %>% 
  arrange(BHCMISID, Year)

# Put covariate tables together

uds.covariates <- inner_join(uds.3B, uds.4, by = c("Year","BHCMISID","ModernGranteeID"))

for (i in 4:ncol(uds.covariates)){
  uds.covariates[,i] <- as.numeric(gsub("-", "", uds.covariates[,i]))
}

#uds.covariates %>% filter(`Grant Number` == "H80CS24200")

for (i in 1:nrow(uds.covariates)){
  if (!is.na(uds.covariates[i,]$Total)) {
uds.covariates[i,is.na(uds.covariates[i,])] <- 0
} 
}

uds.covariates <-  uds.covariates %>% 
    mutate(Pct.NHA = NHA / Total * 100,
         Pct.NHB = NHB / Total * 100,
         Pct.HL = HL / Total * 100,
         Pct.NHW = NHW / Total * 100,
         Pct.ESL = Eng2ndLang / Total * 100,
         Pct.LessThan100pctFPL = ifelse(Total == Unknown, 100, `<100%` / (Total- Unknown) * 100),
         Pct.LessThan200pctFPL = ifelse(Total == Unknown, 100, (`<100%` + `101-150%` + `151-200%`) / (Total - Unknown) * 100),
         Pct.FarmWorker = FarmWorker / Total * 100,
         Pct.Homeless = Homeless / Total * 100,
         Pct.None = (Uninsured.young + Uninsured.old) / Total * 100, 
         Pct.MCD = (MCD.young + MCD.old) / Total * 100, 
         Pct.MCR = (MCR.young + MCR.old) / Total * 100, 
         Pct.COM = (COM.young + COM.old) / Total * 100) %>% 
    select(Year:ModernGranteeID, Total, Pct.NHA:Pct.COM)

uds.covariates %>% 
  arrange(BHCMISID, Year)

```

## Table 6A
```{r}
uds.6a.2011andBefore <- uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table6A.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  select(BHCMIS.ID, Year, T6A_L10_CA:T6A_L26D_CB) %>% 
  filter(Year >= 2010) %>% 
  rename(BHCMISID = BHCMIS.ID) %>% 
  rename_all(.funs = toupper)

uds.6a.2012 <- cbind(Year = 2012, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper)
uds.6a.2013 <- cbind(Year = 2013, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper)

uds.6a.2014 <- cbind(Year = 2014, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper)
uds.6a.2015 <- cbind(Year = 2015, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table6A", skip = 2)) %>% rename_all(.funs = toupper)
uds.6a.2016 <- cbind(Year = 2016, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)

uds.6a.2017 <- cbind(Year = 2017, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
uds.6a.2018 <- cbind(Year = 2018, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
uds.6a.2019 <- cbind(Year = 2019, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)

uds.6a.2020 <- cbind(Year = 2020, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
uds.6a.2021 <- cbind(Year = 2021, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper) %>% filter(!is.na(BHCMISID))

uds.6a.2012[,-c(1:3)] <- data.frame(sapply(uds.6a.2012[,-c(1:3)], as.numeric))
uds.6a.2013[,-c(1:3)] <- data.frame(sapply(uds.6a.2013[,-c(1:3)], as.numeric))

uds.6a.2014[,-c(1:3)] <- data.frame(sapply(uds.6a.2014[,-c(1:3)], as.numeric))
uds.6a.2015[,-c(1:3)] <- data.frame(sapply(uds.6a.2015[,-c(1:3)], as.numeric))
uds.6a.2016[,-c(1:3)] <- data.frame(sapply(uds.6a.2016[,-c(1:3)], as.numeric))

uds.6a.2017[,-c(1:3)] <- data.frame(sapply(uds.6a.2017[,-c(1:3)], as.numeric))
uds.6a.2018[,-c(1:3)] <- data.frame(sapply(uds.6a.2018[,-c(1:3)], as.numeric))
uds.6a.2019[,-c(1:3)] <- data.frame(sapply(uds.6a.2019[,-c(1:3)], as.numeric))

uds.6a.2020[,-c(1:3)] <- data.frame(sapply(uds.6a.2020[,-c(1:3)], as.numeric))
uds.6a.2021[,-c(1:3)] <- data.frame(sapply(uds.6a.2021[,-c(1:3)], as.numeric))

uds.6a <- bind_rows(uds.6a.2012, uds.6a.2013, uds.6a.2014,
      uds.6a.2015, uds.6a.2016, uds.6a.2017, uds.6a.2018, uds.6a.2019, uds.6a.2020, uds.6a.2021, uds.6a.2011andBefore) %>% 
  arrange(BHCMISID, YEAR) %>% 
  select(YEAR:T6A_L34_CB)

uds.6a
```

## Table 6B Measures
```{r}

uds.6b.2012 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2013 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

uds.6b.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 1) 
uds.6b.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

uds.6b.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

uds.6b.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

uds.6b.names <- c("BHCMISID","GrantNumber","Imm.Num","Imm.Rate","imm.denom","Pap.Rate","Pap.Num","pap.denom",
                  "crc.rate","crc.num","crc.denom", 
                  "ChildBMI.rate","ChildBMI.num","ChildBMI.denom","AdultBMI.rate","AdultBMI.num","AdultBMI.denom", "asthma.rate","asthma.num","asthma.denom", 
                  "cad.rate","cad.num","cad.denom", "ivd.rate","ivd.num","ivd.denom")

uds.quality.6b <- rbind(
  cbind(Year = 2012, uds.6b.2012[,c(1:8, 30:32, 9:14, 21:29)] %>% setNames(uds.6b.names)),
  cbind(Year = 2013, uds.6b.2013[,c(1:8, 30:32, 9:14, 21:29)] %>% setNames(uds.6b.names)),

  cbind(Year = 2014, uds.6b.2014[,c(1:8, 27:29, 9:14, 18:26)] %>% setNames(uds.6b.names)),
  cbind(Year = 2015, uds.6b.2015[,c(1:8, 27:29, 9:14, 18:26)] %>% setNames(uds.6b.names)),
  cbind(Year = 2016, uds.6b.2016[,c(1:8, 27:29, 9:14, 18:26)] %>% setNames(uds.6b.names)),

  cbind(Year = 2017, uds.6b.2017[,c(1:8, 27:29, 9:14, 18:26)] %>% setNames(uds.6b.names)),
  cbind(Year = 2018, uds.6b.2018[,c(1:8, 27:29, 9:14, 18:26)] %>% setNames(uds.6b.names)),
  cbind(Year = 2019, uds.6b.2019[,c(1:8, 27:29, 9:14, 18:26)] %>% setNames(uds.6b.names)),

  cbind(Year = 2020, cbind(uds.6b.2020[,c(1:8, 27:29, 12:17)], NA, NA, NA, uds.6b.2020[,c(21:26)]) %>% setNames(uds.6b.names)),
  cbind(Year = 2021, cbind(uds.6b.2021[,c(1:8, 27:29, 12:17)], NA, NA, NA, uds.6b.2021[,c(21:26)]) %>% setNames(uds.6b.names))) %>% 
  mutate(imm.rate = as.numeric(Imm.Num) / as.numeric(imm.denom), 
         pap.rate = as.numeric(Pap.Num) / as.numeric(pap.denom), 
         imm.denom = as.numeric(imm.denom), 
         pap.denom = as.numeric(pap.denom), 
         crc.rate = as.numeric(crc.num) / as.numeric(crc.denom), 
         crc.denom = as.numeric(crc.denom), 
         childbmi.rate = as.numeric(as.numeric(ChildBMI.num) / as.numeric(ChildBMI.denom)), 
         childbmi.denom = as.numeric(ChildBMI.denom),
         adultbmi.rate = as.numeric(as.numeric(AdultBMI.num) / as.numeric(AdultBMI.denom)), 
         adultbmi.denom = as.numeric(AdultBMI.denom),
         asthma.rate = as.numeric(as.numeric(asthma.num) / as.numeric(asthma.denom)), 
         cad.rate = as.numeric(as.numeric(cad.num) / as.numeric(cad.denom)), 
         ivd.rate = as.numeric(as.numeric(ivd.num) / as.numeric(ivd.denom)), 
         ) %>% 
  select(Year, BHCMISID, GrantNumber, imm.rate, imm.denom, pap.rate, pap.denom, crc.rate, crc.denom, asthma.rate, cad.rate, ivd.rate, childbmi.rate, childbmi.denom, adultbmi.rate, adultbmi.denom) %>%

  bind_rows(uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table6B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  filter(Year != 2008) %>% 
    arrange(BHCMIS.ID, Year) %>% 
  #select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  #filter(BHCMIS.ID == '010060') %>% 
  select(BHCMIS.ID, Year, T6B_L10_N_CC:T6B_L11_D_CC, T6B_L10_CA:T6B_L11_CC, T6B_L12_CA:T6B_L13_CC) %>% 
  mutate(imm.rate = ifelse(Year == 2009, T6B_L10_N_CC / T6B_L10_D_CC, 
                    ifelse(Year %in% c(2010:2011), T6B_L10_CC / T6B_L10_CB, NA)), 
         imm.denom = ifelse(Year == 2009, T6B_L10_D_CC, 
                     ifelse(Year %in% c(2010:2011), T6B_L10_CA, NA)),
         pap.rate = ifelse(Year == 2009, T6B_L11_N_CC / T6B_L11_D_CC, 
                    ifelse(Year %in% c(2010:2011), T6B_L11_CC / T6B_L11_CB, NA)), 
         pap.denom = ifelse(Year == 2009, T6B_L11_D_CC, 
                     ifelse(Year %in% c(2010:2011), T6B_L11_CA, NA)), 
         childbmi.rate = T6B_L12_CC / T6B_L12_CB, 
         childbmi.denom = T6B_L12_CA, 
         adultbmi.rate = T6B_L13_CC / T6B_L13_CB, 
         adultbmi.denom = T6B_L13_CA ) %>% 
  select(BHCMIS.ID, Year, imm.rate:adultbmi.denom) %>% 
  rename(BHCMISID = BHCMIS.ID)) %>% 
    arrange(BHCMISID, Year)

## Removes FQHCs that were not open during those first 3 years of the study period
uds.quality.6b <- uds.quality.6b %>% 
  inner_join(uds.cw %>% mutate(STATE = toupper(STATE)) %>% unique() %>% mutate(STATE = ifelse(BHCMIS.ID == '010530', 'ME', 
                                                                                       ifelse(BHCMIS.ID == '090090', 'AZ', STATE))) %>% 
               select(BHCMIS.ID, STATE) %>% unique(), by = c("BHCMISID" = "BHCMIS.ID"))

# uds.cw %>% mutate(STATE = toupper(STATE)) %>% 
#   select(BHCMIS.ID, STATE)  %>% unique() %>% 
#   group_by(BHCMIS.ID) %>% 
#   mutate(row = row_number()) %>% 
#   group_by(BHCMIS.ID) %>% 
#   mutate(max.row = max(row)) %>% 
#   filter(max.row > 1)
#
# uds.cw %>% 
#   mutate(STATE = toupper(STATE)) %>% 
#   select(BHCMIS.ID, STATE) %>% 
#   group_by(BHCMIS.ID, STATE) %>% 
#   summarise(n()) %>% 
#   filter(BHCMIS.ID %in% c('010530','090090'))
# 
# uds.cw %>% filter(BHCMIS.ID == '010530')

```

## Table 6B - EHR or Sampling Used
```{r}
vec.years <- 2012:2021
vec.skips <- rep(0, length(vec.years)) 
vec.skips[c(4)] <- 2
vec.skips[c(5,6,7,8,9)] <- 1
vec.files <- paste("//Users/jhm65/Dropbox/Git/UDS/UDS-",vec.years, "-Full-Dataset.xlsx", sep = "")

uds.quality.sampling.v.ehr <- uds.cw %>% 
  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table6B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
  filter(Year != 2008) %>% 
    arrange(BHCMIS.ID, Year) %>% 
  #select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
  #filter(BHCMIS.ID == '010060') %>% 
  #select(BHCMIS.ID, Year, T6B_L10_N_CC:T6B_L11_D_CC, T6B_L10_CA:T6B_L11_CC) %>% 
  select(BHCMIS.ID, Year, T6B_L10_CA, T6B_L10_CB, T6B_L11_CA, T6B_L11_CB, T6B_L12_CA,	T6B_L12_CB, T6B_L13_CA, T6B_L13_CB) %>% 
  cbind(T6B_L19_CA = NA,	T6B_L19_CB = NA) %>% 
  rename(YEAR = Year)

for (i in 1:length(vec.years)){
read_excel(vec.files[i], sheet = "Table6B", skip = vec.skips[i])
temp <- read_excel(vec.files[i], sheet = "Table6B", skip = vec.skips[i])%>% 
  select(BHCMISID, T6b_L10_Ca, T6b_L10_Cb, T6b_L11_Ca, T6b_L11_Cb, T6B_L19_Ca,	T6B_L19_Cb, T6b_L12_Ca,	T6b_L12_Cb, T6b_L13_Ca, T6b_L13_Cb) %>% 
    mutate(Year = vec.years[i])
colnames(temp) <- toupper(colnames(temp))
colnames(temp)[1] <- "BHCMIS.ID"

  uds.quality.sampling.v.ehr <- uds.quality.sampling.v.ehr %>% 
    rbind(temp) %>% 
    arrange(BHCMIS.ID, YEAR)
}

uds.quality.sampling.v.ehr <- uds.quality.sampling.v.ehr %>% 
  mutate(imm.ehr = ifelse(T6B_L10_CA == T6B_L10_CB, 1, 0), 
         pap.ehr = ifelse(T6B_L11_CA == T6B_L11_CB, 1, 0), 
         crc.ehr = ifelse(T6B_L19_CA == T6B_L19_CB, 1, 0),
         childbmi.ehr = ifelse(T6B_L12_CA == T6B_L12_CB, 1, 0), 
         adultbmi.ehr = ifelse(T6B_L13_CA == T6B_L13_CB, 1, 0)) %>% 
  mutate(ehr = imm.ehr + pap.ehr + crc.ehr + childbmi.ehr + adultbmi.ehr)

```

## Table 7 Clinical Measures

```{r}

uds.7.2012 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
uds.7.2013 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0)

uds.7.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
uds.7.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 1) 
uds.7.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0)

uds.7.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
uds.7.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
uds.7.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0)

uds.7.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
uds.7.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 1)

uds.7.names <- c("BHCMISID","GrantNumber","Race","Ethnicity","htn.total","htn.control","dm.total","dm.controlled")

uds.quality.7 <- rbind(
  cbind(Year = 2012, uds.7.2012[,c(1:6, 8:9)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
  cbind(Year = 2013, uds.7.2013[,c(1:6, 8:9)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),

  cbind(Year = 2014, uds.7.2014[,c(1:6, 8:9)] %>% setNames(uds.7.names)),
  cbind(Year = 2015, uds.7.2015[,c(1:4, 8:9, 11, 14)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
  cbind(Year = 2016, uds.7.2016[,c(1:4, 8:9, 11, 14)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),

  cbind(Year = 2017, uds.7.2017[,c(1:4, 8:9, 11, 14)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
  cbind(Year = 2018, uds.7.2018[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
  cbind(Year = 2019, uds.7.2019[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),

  cbind(Year = 2020, uds.7.2020[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
  cbind(Year = 2021, uds.7.2021[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled)))) %>% 
  mutate(htn.rate = as.numeric(htn.control) / as.numeric(htn.total), 
         dm.rate = as.numeric(dm.controlled) / as.numeric(dm.total), 
         htn.total = as.numeric(htn.total), 
         dm.total = as.numeric(dm.total)) %>% 
  select(Year:Ethnicity, htn.total, htn.rate, dm.total, dm.rate) %>%

  bind_rows(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table7clin.csv") %>% 
  select(Year, ModernGranteeID:dm.controlled) %>% 
  rename(GrantNumber = ModernGranteeID) %>% 
    mutate(htn.rate = as.numeric(htn.control) / as.numeric(htn.total), 
         dm.rate = as.numeric(dm.controlled) / as.numeric(dm.total), 
         htn.total = as.numeric(htn.total), 
         dm.total = as.numeric(dm.total)) %>% 
    select(Year:Ethnicity, htn.total, htn.rate, dm.total, dm.rate)) %>% 
    arrange(GrantNumber, Year, Ethnicity, Race)

## Removes FQHCs that were not open during those first 3 years of the study period
uds.quality.7 <- uds.quality.7 %>% 
  inner_join(uds.cw %>% mutate(STATE = toupper(STATE)) %>% unique() %>% mutate(STATE = ifelse(BHCMIS.ID == '010530', 'ME', 
                                                                                       ifelse(BHCMIS.ID == '090090', 'AZ', STATE))) %>% 
               select(ModernGranteeID, STATE) %>% unique(), by = c("GrantNumber" = "ModernGranteeID")) %>% 
  mutate(Race = ifelse(Race == '-', NA, Race),
         Ethnicity = ifelse(Ethnicity == '-', NA, Ethnicity))

uds.quality.7[is.na(uds.quality.7$htn.total),]$htn.total <- 0
uds.quality.7[is.na(uds.quality.7$htn.rate),]$htn.rate <- 0
uds.quality.7[is.na(uds.quality.7$dm.total),]$dm.total <- 0
uds.quality.7[is.na(uds.quality.7$dm.rate),]$dm.rate <- 0

uds.quality.7 <- uds.quality.7 %>% 
   inner_join(uds.cw %>% filter(Year == 2011) %>% unique() %>% select(ModernGranteeID, BHCMIS.ID), by = c("GrantNumber" = "ModernGranteeID")) %>% 
  arrange(Year, BHCMIS.ID, GrantNumber) %>% 
  mutate(BHCMISID = ifelse(is.na(BHCMISID), BHCMIS.ID, BHCMISID))

uds.quality.7 %>% 
  filter(Race == " Total" | is.na(Race))%>% 
  arrange(BHCMISID, Year) %>% 
  group_by(Year, BHCMISID) %>% 
  summarise(htn.rate = sum(htn.rate * htn.total) / sum(htn.total), 
            htn.total = sum(htn.total), 
            dm.rate = sum(dm.rate * dm.total) / sum(dm.total), 
            dm.total = sum(dm.total)) %>% 
  arrange(BHCMISID, Year)
```

```{r}
# df.comp %>% 
#   ggplot(aes(x = Year, y = dm.rate)) + geom_point() + geom_smooth()

```

## Financials
```{r}
cw <- read_excel("/Users/jhm65/Dropbox/Git/Data/UDS-990 Crosswalk.xlsx")

fins.revenue.expenses <- read.csv("//Users/jhm65/Dropbox/Git/Data/FQHC_Revenue_vs_Expenses.csv", header = TRUE)
names(fins.revenue.expenses) <- gsub("^X\\.", "", names(fins.revenue.expenses))
names(fins.revenue.expenses) <- gsub("\\.\\.", "", names(fins.revenue.expenses))

staffing <- read.csv("/Users/jhm65/Dropbox/Git/Data/FQHC_Staffing.csv")

fins.revenue.expenses <- uds.cw %>% filter(Year == 2011) %>% unique() %>% select(ModernGranteeID, BHCMIS.ID) %>% 
  left_join(cw, by = c("ModernGranteeID" = "Grant Number")) %>% 
  left_join(fins.revenue.expenses, by = c("EIN" = "EIN")) %>% 
  select(ModernGranteeID:EIN, form_year:fringe_rate) %>% 
  left_join(staffing %>% select(EIN:Staff), by = c("EIN","form_year" = "Year"))
```

## APM History

```{r}

apm.history <- read_excel("/Users/jhm65/Dropbox/Git/APMs/data_raw/APM_History.xlsx") %>%
 mutate(Class = ifelse(is.na(Year), "0 - Control", Classification))

```

## Full dataset

```{r}

included.years <- 2010:2021
included.treat <- 2013:2021

## Broader definitions 5 / 7 quality measures significant improvements overall
# included.years <- 2009:2021
# included.treat <- 2013:2021

## Original good filters
# included.years <- 2009:2019
# included.treat <- 2013:2019

df.comp <- uds.covariates %>% 
  select(Year:BHCMISID, Total:Pct.COM) %>% 
  inner_join(uds.cw %>% select(BHCMIS.ID, STATE) %>% 
               mutate(STATE = toupper(STATE)) %>% 
               unique() %>% mutate(STATE = ifelse(BHCMIS.ID == '010530', 'ME', ifelse(BHCMIS.ID == '090090', 'AZ', STATE))) %>% unique(), by = c("BHCMISID" = "BHCMIS.ID")) %>% 
  select(BHCMISID, Year, STATE, Total:Pct.COM) %>% 
  arrange(BHCMISID, Year) %>% 
  left_join(uds.6a, by = c("BHCMISID","Year" = "YEAR")) %>% 
  left_join(uds.quality.6b %>% select(Year, BHCMISID, imm.rate:adultbmi.denom), by = c("BHCMISID","Year")) %>% 
  left_join(uds.quality.7 %>% 
  filter(Race == " Total" | is.na(Race)) %>% 
  group_by(Year, BHCMISID) %>% 
  summarise(htn.rate = sum(htn.rate * htn.total) / sum(htn.total), 
            htn.total = sum(htn.total), 
            dm.rate = sum(dm.rate * dm.total) / sum(dm.total), 
            dm.total = sum(dm.total)) %>% 
  arrange(BHCMISID, Year), by = c("BHCMISID","Year")) %>% 
    left_join(fins.revenue.expenses, by = c("BHCMISID" = "BHCMIS.ID", "Year" = "form_year")) %>% 
  inner_join(apm.history %>% rename(att = Year), by = c("STATE" = "Postal Code")) %>% 
  ungroup() %>% 
  mutate(att = ifelse(is.na(att), 0, att)) %>% 
  mutate(ID = as.numeric(as.factor(BHCMISID))) %>% 
  arrange(BHCMISID) %>% 
  mutate(ACA = ifelse((STATE %in% c('MI','NH') & Year >= 2014) |
                    (STATE %in% c('PA','IN','AK') & Year >= 2015) |
                    (STATE %in% c('MT','LA') & Year >= 2016) |
                    (STATE %in% c('VA','ME') & Year >= 2019) |
                    (STATE %in% c('ID','UT','NE') & Year >= 2020) |
                    (STATE %in% c('OK','MO') & Year >= 2021) |
                    (STATE %in% c('AZ','AR','CA','CO','CT','DE','DC','HI','IL','IA','KY','MD','MA','MN','NV','NJ','NM','NY','ND','OH','OR','PA','RI','VT','VA','WA') & Year >= 2014), 1, 0))

class.vec <- rep(sort(unique(df.comp$Classification)), table(df.comp$Classification))

set.seed(123) #432

df.comp <- df.comp %>% 
  group_by(ID) %>% 
  mutate(Class.random = ifelse(Class == "0 - Control", sample(class.vec, size = 1, replace = T), Class), 
         att.random = ifelse(Class == "0 - Control", sample(included.treat, size = 1, replace = T), att)) %>% 
                                 mutate(Tx = ifelse(Year >= att & att > 0, 1, 0)) %>% 
  filter(Year %in% included.years) %>% 
  mutate(year.rel = as.factor(ifelse(att.random > 0, Year - att.random, NA)), 
         Treatment = ifelse(att > 0, 1, 0)) %>% 
  select(BHCMISID:STATE, Name:ID, ACA:Treatment, Total:dm.total, fs_contributions:Staff)

df.comp <- df.comp %>% 
  left_join(df.comp %>% 
  group_by(BHCMISID) %>% 
  summarise(counts = n()) %>% filter(counts == length(included.years)), by = c("BHCMISID")) %>% 
  group_by(BHCMISID) %>% 
  mutate(closed = ifelse(is.na(counts) & Year == max(Year), 1, 0)) #%>%  filter(APM %in% c('Yes','No'))

df.comp$year.rel <- relevel(as.factor(df.comp$year.rel), ref = "-1")

## Filter for balanced panel, remove closures and late openings
df.comp <- df.comp %>%
  left_join(df.comp %>% summarise(Counts = n(), MinYear = min(Year)), by = c("BHCMISID")) %>%
  filter(Counts == length(included.years)) #  filter(Counts < 13 & MinYear == 2009)    filter(Counts == length(included.years))

## Remove some weird shit in CT
df.comp <- df.comp %>% 
  filter(BHCMISID != "01E00010") %>%  #%>%  filter(STATE != 'CT')
select(BHCMISID:FIPS, ID, Total:Pct.COM, imm.rate:MinYear)

```

## Clean up the missing addresses, geocoding

```{r}

tbcoded <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]
coded <- geo(street = tbcoded[c(1:1000),]$`Site Street Address`, 
             city = tbcoded[c(1:1000),]$`Site City`, 
             state = tbcoded[c(1:1000),]$`Site State`, 
             method = "census", 
             full_results = TRUE)

for (g in 1:13){
  g
coded <- rbind(coded, 
               geo(street = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site Street Address`, 
             city = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site City`, 
             state = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site State`, 
             method = "census", 
             full_results = TRUE) )
}

coded <- rbind(coded, 
               geo(street = tbcoded[c(14001:14253),]$`Site Street Address`, 
             city = tbcoded[c(14001:14253),]$`Site City`, 
             state = tbcoded[c(14001:14253),]$`Site State`, 
             method = "census", 
             full_results = TRUE) )

coded[grep(pattern = "[[:digit:]]{5}$", coded$matched_address),]

uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]$Zip <- str_extract(coded$matched_address, pattern = "[[:digit:]]{5}$")
uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]

uds.sites.full.temp <- uds.sites.full

```

```{r}

uds.sites.full <- uds.sites.full.temp

uds.sites.full.temp %>% filter(`Grant Number` %in% c("H80CS00881") & Year == 2016)

chc <- read.csv("//Users/jhm65/Dropbox/Git/Competition/data_raw/chc.csv")

chc %>% filter(Health.Center.Number %in% c("H80CS00881"))

uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] %>%
  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Street Address" = "Site.Address")) %>%
  mutate(Zip = ifelse(is.na(Zip), substr(Health.Center.Organization.ZIP.Code, 1, 5), Zip)) %>%
  select(`BHCMIS ID`:Zip) %>%
  unique()

uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] %>%
  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Name" = "Site.Name")) %>%
  mutate(Zip = ifelse(is.na(Zip), substr(Health.Center.Organization.ZIP.Code, 1, 5), Zip)) %>%
  select(`BHCMIS ID`:Zip) %>%
  unique()

uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]
```

```{r}

table(uds.sites.full.temp$`Location Setting`)

uds.sites.full <- uds.sites.full %>% #filter(`Location Type` == "Permanent" & `Location Setting` %in% c("All Other Clinic Types")) %>% 
  mutate(Access = as.numeric(ifelse(`Total Weekly Hours Of Operation` == "-" & `Operational Schedule` == "Full-Time", 40, 
                  ifelse(`Total Weekly Hours Of Operation` == "-" & `Operational Schedule` == "Part-Time", 10, `Total Weekly Hours Of Operation`))))

uds.sites.full[is.na(uds.sites.full$Zip),]

uds.sites.full %>% 
  arrange(`Total Weekly Hours Of Operation`, `Operational Schedule` )
```

## Classify FQHCs into Treated, control based on zip codes

```{r}

sites.in.zips <- uds.sites.full %>% 
  filter(Year >= included.years[1]) %>% 
  group_by(`BHCMIS ID`, Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  pivot_wider(id_cols = c(Zip, `BHCMIS ID`), names_from = Year, values_from = Counts) %>% 
  pivot_longer(cols = `2010`:`2021`) %>% 
  mutate(value = ifelse(is.na(value), 0, value)) %>% 
  arrange(Zip, name)

clinics.in.zips <- uds.sites.full %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  group_by(Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  pivot_wider(id_cols = c(Zip), names_from = Year, values_from = Counts) %>% 
  pivot_longer(cols = `2011`:`2017`) %>% 
  mutate(value = ifelse(is.na(value), 0, value)) %>% 
  arrange(Zip, name)

sites.in.zips %>% 
  left_join(clinics.in.zips, by = c("Zip","name"))%>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(Clinics = max(Clinics)) 
```

## Write the file
```{r}
#write_csv(df.comp, file = "/Users/jhm65/Dropbox/Projects/Competition/data_processed/analyticalfile.csv")

```

### 2023-08-15 code/analysis_Redo.Rmd
mid session updates
lots of new code

@@
 ```
+
+# Redo the analysis
+
+```{r}
+
+did2s(
+      data = dfc %>% 
+        select(ID, Year, Tx, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate, closed) %>%
+        mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6, 
+               CostPerPat = ngla_expense / Total, 
+               months_of_cash = as.numeric(months_of_cash),
+               quick_ratio = as.numeric(quick_ratio),
+               fringe_rate = as.numeric(fringe_rate)) %>% 
+        inner_join(dfc %>% filter(Year == 2010) #& Total > 20000) 
+                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
+      yname = "closed", 
+      treatment = "Tx",
+        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
+event_study(data = dfc %>% mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate) / 6), 
+  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>%
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)
+
+```

### 2023-08-15 code/data_cleaning_longer.Rmd
lots of new code

@@
 # Data Prep
+
+## Set study period
+```{r}
+
+included.years <- 2010:2021
+included.treat <- 2013:2021
+
+```
 
@@
 
+```
+
+## Clean up the missing addresses, geocoding
+
+```{r}
+
+tbcoded <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]
+coded <- geo(street = tbcoded[c(1:1000),]$`Site Street Address`, 
+             city = tbcoded[c(1:1000),]$`Site City`, 
+             state = tbcoded[c(1:1000),]$`Site State`, 
+             method = "census", 
+             full_results = TRUE)
+
+for (g in 1:13){
+  g
+coded <- rbind(coded, 
+               geo(street = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site Street Address`, 
+             city = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site City`, 
+             state = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site State`, 
+             method = "census", 
+             full_results = TRUE) )
+}
+
+coded <- rbind(coded, 
+               geo(street = tbcoded[c(14001:14253),]$`Site Street Address`, 
+             city = tbcoded[c(14001:14253),]$`Site City`, 
+             state = tbcoded[c(14001:14253),]$`Site State`, 
+             method = "census", 
+             full_results = TRUE) )
+
+coded[grep(pattern = "[[:digit:]]{5}$", coded$matched_address),]
+
+uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]$Zip <- str_extract(coded$matched_address, pattern = "[[:digit:]]{5}$")
+uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]
+
+uds.sites.full.temp <- uds.sites.full
+
+```
+
+```{r}
+
+uds.sites.full <- uds.sites.full.temp
+
+uds.sites.full.temp %>% filter(`Grant Number` %in% c("H80CS00881") & Year == 2016)
+
+chc <- read.csv("//Users/jhm65/Dropbox/Git/Competition/data_raw/chc.csv")
+
+chc %>% filter(Health.Center.Number %in% c("H80CS00881"))
+
+uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] %>%
+  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Street Address" = "Site.Address")) %>%
+  mutate(Zip = ifelse(is.na(Zip), substr(Health.Center.Organization.ZIP.Code, 1, 5), Zip)) %>%
+  select(`BHCMIS ID`:Zip) %>%
+  unique()
+
+uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] %>%
+  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Name" = "Site.Name")) %>%
+  mutate(Zip = ifelse(is.na(Zip), substr(Health.Center.Organization.ZIP.Code, 1, 5), Zip)) %>%
+  select(`BHCMIS ID`:Zip) %>%
+  unique()
+
+uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]
+```
+
+```{r}
+
+table(uds.sites.full.temp$`Location Setting`)
+
+uds.sites.full <- uds.sites.full %>% #filter(`Location Type` == "Permanent" & `Location Setting` %in% c("All Other Clinic Types")) %>% 
+  mutate(Access = as.numeric(ifelse(`Total Weekly Hours Of Operation` == "-" & `Operational Schedule` == "Full-Time", 40, 
+                  ifelse(`Total Weekly Hours Of Operation` == "-" & `Operational Schedule` == "Part-Time", 10, `Total Weekly Hours Of Operation`))))
+
+uds.sites.full[is.na(uds.sites.full$Zip),]
+
+uds.sites.full %>% 
+  arrange(`Total Weekly Hours Of Operation`, `Operational Schedule` )
 ```
@@
 
-included.years <- 2010:2021
-included.treat <- 2013:2021
-
 ## Broader definitions 5 / 7 quality measures significant improvements overall
@@
   filter(BHCMISID != "01E00010") %>%  #%>%  filter(STATE != 'CT')
-select(BHCMISID:FIPS, ID, Total:Pct.COM, imm.rate:MinYear)
+select(BHCMISID:FIPS, Total:Pct.COM, imm.rate:MinYear)
 
-```
-
-## Clean up the missing addresses, geocoding
-
-```{r}
-
-tbcoded <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]
-coded <- geo(street = tbcoded[c(1:1000),]$`Site Street Address`, 
-             city = tbcoded[c(1:1000),]$`Site City`, 
-             state = tbcoded[c(1:1000),]$`Site State`, 
-             method = "census", 
-             full_results = TRUE)
-
-for (g in 1:13){
-  g
-coded <- rbind(coded, 
-               geo(street = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site Street Address`, 
-             city = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site City`, 
-             state = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site State`, 
-             method = "census", 
-             full_results = TRUE) )
-}
-
-coded <- rbind(coded, 
-               geo(street = tbcoded[c(14001:14253),]$`Site Street Address`, 
-             city = tbcoded[c(14001:14253),]$`Site City`, 
-             state = tbcoded[c(14001:14253),]$`Site State`, 
-             method = "census", 
-             full_results = TRUE) )
-
-coded[grep(pattern = "[[:digit:]]{5}$", coded$matched_address),]
-
-uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]$Zip <- str_extract(coded$matched_address, pattern = "[[:digit:]]{5}$")
-uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]
-
-uds.sites.full.temp <- uds.sites.full
-
-```
-
-```{r}
-
-uds.sites.full <- uds.sites.full.temp
-
-uds.sites.full.temp %>% filter(`Grant Number` %in% c("H80CS00881") & Year == 2016)
-
-chc <- read.csv("//Users/jhm65/Dropbox/Git/Competition/data_raw/chc.csv")
-
-chc %>% filter(Health.Center.Number %in% c("H80CS00881"))
-
-uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] %>%
-  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Street Address" = "Site.Address")) %>%
-  mutate(Zip = ifelse(is.na(Zip), substr(Health.Center.Organization.ZIP.Code, 1, 5), Zip)) %>%
-  select(`BHCMIS ID`:Zip) %>%
-  unique()
-
-uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] %>%
-  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Name" = "Site.Name")) %>%
-  mutate(Zip = ifelse(is.na(Zip), substr(Health.Center.Organization.ZIP.Code, 1, 5), Zip)) %>%
-  select(`BHCMIS ID`:Zip) %>%
-  unique()
-
-uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]
-```
-
-```{r}
-
-table(uds.sites.full.temp$`Location Setting`)
-
-uds.sites.full <- uds.sites.full %>% #filter(`Location Type` == "Permanent" & `Location Setting` %in% c("All Other Clinic Types")) %>% 
-  mutate(Access = as.numeric(ifelse(`Total Weekly Hours Of Operation` == "-" & `Operational Schedule` == "Full-Time", 40, 
-                  ifelse(`Total Weekly Hours Of Operation` == "-" & `Operational Schedule` == "Part-Time", 10, `Total Weekly Hours Of Operation`))))
-
-uds.sites.full[is.na(uds.sites.full$Zip),]
-
-uds.sites.full %>% 
-  arrange(`Total Weekly Hours Of Operation`, `Operational Schedule` )
 ```
@@
 
-sites.in.zips <- uds.sites.full %>% 
+clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
   filter(Year >= included.years[1]) %>% 
-  group_by(`BHCMIS ID`, Zip, Year) %>% 
-  summarise(Counts = n()) %>% 
-  pivot_wider(id_cols = c(Zip, `BHCMIS ID`), names_from = Year, values_from = Counts) %>% 
-  pivot_longer(cols = `2010`:`2021`) %>% 
-  mutate(value = ifelse(is.na(value), 0, value)) %>% 
-  arrange(Zip, name)
+  group_by(Zip, Year) %>%
+  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
+  arrange(desc(Clinics))
 
-clinics.in.zips <- uds.sites.full %>% 
+# Identify clinics in competitive zip codes
+clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
   filter(Year >= included.years[1]) %>%
@@
   unique() %>% 
-  group_by(Zip, Year) %>% 
-  summarise(Counts = n()) %>% 
-  pivot_wider(id_cols = c(Zip), names_from = Year, values_from = Counts) %>% 
-  pivot_longer(cols = `2011`:`2017`) %>% 
-  mutate(value = ifelse(is.na(value), 0, value)) %>% 
-  arrange(Zip, name)
+  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
+  group_by(`BHCMIS ID`, Year) %>% 
+  summarise(Clinics = max(Clinics)) %>% 
+  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
+  filter(`2010` == 1 & `2011` == 1 & `2012` == 1) %>%   
+  #filter(`2014` == 1 & `2015` == 1) %>%  
+  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
+  #filter(is.na(NewClinicID)) %>%
+  select(`BHCMIS ID`:`2021`) %>% 
+  pivot_longer(cols = c(`2010`:`2021`)) %>% 
+  group_by(`BHCMIS ID`) %>% 
+  filter(min(value) == 1 ) %>% 
+  #filter(max(value) == last(value)) %>% 
+  mutate(Tx = ifelse(value > 1, 1, 0))
 
-sites.in.zips %>% 
-  left_join(clinics.in.zips, by = c("Zip","name"))%>% 
-  group_by(`Grant Number`, Year) %>% 
-  summarise(Clinics = max(Clinics)) 
+# Classify clinics by introduction of competition
+comp.initial <- clinics.comp %>%  #left_join(clinics.comp %>% mutate(Year = as.numeric(name)), uds.zip.totals, by = c("BHCMIS ID", "name" = "Reporting Year")) %>% 
+  mutate(Year = as.numeric(name)) %>% 
+  left_join(uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
+              filter(Year >= included.years[1]) %>%
+  group_by(`BHCMIS ID`, Year) %>% 
+  summarise(Sites = n()), by = c("BHCMIS ID","Year")) %>% 
+  ungroup() %>% 
+  group_by(`BHCMIS ID`) %>% 
+  mutate(Att = min(ifelse(Tx == 0, 2, 1)*Year, na.rm = TRUE) ) %>% 
+  group_by(`BHCMIS ID`) %>% 
+  mutate(Att = ifelse(Att < 2022, Att, 0)) %>% 
+  ungroup() %>% 
+  mutate(ID = as.numeric(factor(`BHCMIS ID`)))
+
+# Expandors vs Expandees
+comp.initial <- comp.initial %>% 
+  left_join(
+      left_join(comp.initial %>% select(`BHCMIS ID`, Att) %>% unique(), uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
+                  filter(Year >= included.years[1]) %>%
+        select(`BHCMIS ID`, Zip, Year) %>% 
+        group_by(`BHCMIS ID`, Zip) %>% 
+        summarise(YearFirstInZip = min(Year)) %>% 
+        filter(YearFirstInZip %notin% c(2010)) %>% 
+        select(`BHCMIS ID`, YearFirstInZip) %>% 
+        unique(), by = c("BHCMIS ID")) %>% #filter(`BHCMIS ID` == "H80CS00101") %>% 
+        mutate(Expandor = ifelse(is.na(YearFirstInZip) | Att != YearFirstInZip, 0, 1)) %>%  #  is.na(YearFirstInZip) | Att != YearFirstInZip
+        group_by(`BHCMIS ID`) %>% summarise(Expandor = max(Expandor)), by = c("BHCMIS ID")) %>% filter(Expandor == 0)
+
+dfc <- comp.initial %>% 
+  left_join(df.comp, by = c("BHCMIS ID" = "BHCMISID", "Year"))
+```
+
+## Finalize the core set of measures
+```{r}
+
+dfc %>% 
+  mutate(Liabilities = `Liabilities (as pct of assets)` * `Total net assets`, 
+         Staffing = `Total expenses before depreciation` * Personnel, 
+         LBE.pct = `Gross land, buildings and equipment (LBE)` / `Total net assets`, 
+         `Liabilities (as pct of assets)` = `Liabilities (as pct of assets)` * 100, 
+         `Surplus as a pct of before dep expenses` = `Surplus as a pct of before dep expenses` * 100, 
+         Qcomp = (pap.rate + crc.rate + asthma.rate + cad.rate + ivd.rate + childbmi.rate + adultbmi.rate) / 7, 
+         CostOfCare = `Total expenses before depreciation` / Total) %>%
+
+  mutate(Liquidity =  `Total net assets` / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
+         Profitability =  `Unrestricted surplus (deficit) before depreciation` / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
+         Efficiency = (`Total revenue (unrestricted & restricted)` - `Total expenses before depreciation`) / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
+         NetWorth = (100 - `Liabilities (as pct of assets)`) / `Liabilities (as pct of assets)` / 100) %>% 
+  mutate(Altmans.Z = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% # 6.56, 3.26, 6.72, 1.05  OR 0.18, 0.3, 0.81, 0.14
+  mutate(Liquidity = ifelse(Liquidity == 'Inf', NA, Liquidity), 
+         Profitability = ifelse(Profitability == 'Inf', NA, Profitability), 
+         Efficiency = ifelse(Efficiency == 'Inf', NA, Efficiency), 
+         NetWorth = ifelse(NetWorth == 'Inf', NA, NetWorth), 
+         Altmans.Z = ifelse(Altmans.Z == 'Inf', NA, Altmans.Z))
+
 ```
@@
 ```{r}
-#write_csv(df.comp, file = "/Users/jhm65/Dropbox/Projects/Competition/data_processed/analyticalfile.csv")
+#write_csv(dfc, file = "/Users/jhm65/Dropbox/Projects/Competition/data_processed/analyticalfile.csv")
 

### 2023-08-15 code/analysis_Redo.Rmd
updated code

--- 2023-08-14 code/analysis_Redo.Rmd
@@
 ```
+
+# Redo the analysis
+
+## Balance between treated and controls
+```{r}
+
+dfc %>% 
+  filter(Year == 2010) %>% 
+  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
+  select(Treat, Total, Pct.NHA:Pct.COM) %>% 
+  filter(complete.cases(.)) %>% 
+  tbl_summary(by = Treat) %>% 
+  add_p()
+
+```
+
+## Overall Effects on Key Variables
+
+```{r}
+
+did2s(
+      data = dfc %>% 
+        select(ID, Year, Tx, STATE, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate) %>%
+        mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6, 
+               CostPerPat = ngla_expense / Total, 
+               months_of_cash = as.numeric(months_of_cash),
+               quick_ratio = as.numeric(quick_ratio),
+               fringe_rate = as.numeric(fringe_rate)) %>% 
+        inner_join(dfc %>% filter(Year == 2010) #& Total > 20000) 
+                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
+      yname = "Qcomp", 
+      treatment = "Tx",
+        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
+event_study(data = dfc %>% mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate) / 6), 
+  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>%
+  filter(abs(term) <= 5) %>% 
+  #filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)
+
+```

### 2023-08-15 code/analysis_Redo.Rmd
i got some shit here

--- 2023-08-14 code/analysis_Redo.Rmd
@@
 ```
+
+# Redo the analysis
+
+## Balance between treated and controls
+```{r}
+
+dfc %>% 
+  filter(Year == 2010) %>% 
+  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
+  select(Treat, Total, Pct.NHA:Pct.COM) %>% 
+  filter(complete.cases(.)) %>% 
+  tbl_summary(by = Treat, 
+                statistic = list(all_continuous() ~ "{mean} ({sd})")) %>% 
+  add_p()
+
+```
+
+## Overall Effects on Key Variables
+
+```{r}
+
+summary(as.numeric(dfc[dfc$Year == 2010,]$months_of_cash))
+summary(dfc[dfc$Year == 2010,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_revenue)
+
+did2s(
+      data = dfc %>% 
+        select(ID, Year, Tx, STATE, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate) %>%
+        mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6, 
+               CostPerPat = ngla_expense / Total, 
+               months_of_cash = as.numeric(months_of_cash),
+               quick_ratio = as.numeric(quick_ratio),
+               fringe_rate = as.numeric(fringe_rate)) %>% 
+        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03) 
+                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
+      yname = "Qcomp", 
+      treatment = "Tx",
+        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
+event_study(data = dfc %>% mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate) / 6) %>% 
+              inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03)#as.numeric(months_of_cash) < 2)#Total > 10000) 
+                   %>% select(ID) %>% unique() , by = c("ID")), 
+  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>%
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)
+
+```

### 2023-08-15 code/analysis_Redo.Rmd
found an informative split

@@
                quick_ratio = as.numeric(quick_ratio),
-               fringe_rate = as.numeric(fringe_rate)) %>% 
-        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03) 
+               fringe_rate = as.numeric(fringe_rate), 
+               profit_ratio = Sites) %>% 
+        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue < 0.03) 
                    %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
-      yname = "Qcomp", 
+      yname = "Total", 
       treatment = "Tx",
@@
 event_study(data = dfc %>% mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate) / 6) %>% 
-              inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03)#as.numeric(months_of_cash) < 2)#Total > 10000) 
+              inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue < 0.03)#as.numeric(months_of_cash) < 2)#Total > 10000) 
                    %>% select(ID) %>% unique() , by = c("ID")), 

### 2023-08-15 code/analysis_Redo.Rmd
last updates for now, mapping out figures for JMP

--- 2023-08-15 code/analysis_Redo.Rmd
@@
 
+## Overall average effects
+
+## Effects stratified by profitability
+
+## Effects startified by clinic size
+
+## Changes in geographic distribution of resources by Distance to competitive zip
+
+## Rival selecting where to put new site
+
+Splits
+- Total at 10000 and at 25000
+- ngla_net_gain_loss/ngla_revenue at 0.03
+- Months of cash at 2
+
+Significant Variables
+- Qcomp
+- Total
+- Sites
+- Staff
+- Quick-ratio
+
 ```{r}
 
+summary(as.numeric(dfc[dfc$Year == 2010,]$Total))
 summary(as.numeric(dfc[dfc$Year == 2010,]$months_of_cash))
@@
                quick_ratio = as.numeric(quick_ratio),
-               fringe_rate = as.numeric(fringe_rate)) %>% 
-        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03) 
+               fringe_rate = as.numeric(fringe_rate), 
+               profit_ratio = Sites) %>% 
+        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03) #& ngla_net_gain_loss/ngla_revenue < 0.03) 
                    %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
-      yname = "Qcomp", 
+      yname = "Sites", 
       treatment = "Tx",
@@
 event_study(data = dfc %>% mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate) / 6) %>% 
-              inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03)#as.numeric(months_of_cash) < 2)#Total > 10000) 
+              inner_join(dfc %>% filter(Year == 2010 & Total < 10000)# ngla_net_gain_loss/ngla_revenue < 0.03 as.numeric(months_of_cash) < 2)#Total > 10000) 
                    %>% select(ID) %>% unique() , by = c("ID")), 
-  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>%
+  yname = "as.numeric(quick_ratio)", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>%
   filter(abs(term) <= 5) %>% 
-  filter(estimator == "Gardner (2021)") %>% 
+  #filter(estimator == "Gardner (2021)") %>% 
   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +

### 2023-08-15 code/analysis_Redo.Rmd
lots of splits, need to standardize next

--- 2023-08-15 code/analysis_Redo.Rmd
@@
 
+## Overall average effects
+
+## Effects stratified by profitability
+
+## Effects startified by clinic size
+
+## Changes in geographic distribution of resources by Distance to competitive zip
+
+## Rival selecting where to put new site
+
+Splits
+- Total at 10000 and at 25000
+- ngla_net_gain_loss/ngla_revenue at 0.03 (Profitable grow and give up financial footing, unprofitable improve quality)
+- Months of cash at 2
+
+Significant Variables
+- Qcomp
+- Total
+- Sites
+- Staff
+- Quick-ratio
+
 ```{r}
 
+summary(as.numeric(dfc[dfc$Year == 2010,]$Total))
 summary(as.numeric(dfc[dfc$Year == 2010,]$months_of_cash))
@@
       data = dfc %>% 
-        select(ID, Year, Tx, STATE, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate) %>%
+        select(ID, Year, Tx, STATE, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate, Assets, Liabilities) %>%
         mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6, 
@@
                months_of_cash = as.numeric(months_of_cash),
-               quick_ratio = as.numeric(quick_ratio),
-               fringe_rate = as.numeric(fringe_rate)) %>% 
-        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03) 
+               Liquidity = (Assets - Liabilities) / Assets,
+               Profitability = ngla_net_gain_loss / Assets, 
+               Efficiency = ngla_revenue / Assets,
+               NetWorth = (Assets - Liabilities) / Liabilities, 
+               Altman = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% 
+        inner_join(dfc %>% filter(Year == 2010 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                    %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
@@
 event_study(data = dfc %>% mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate) / 6) %>% 
-              inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03)#as.numeric(months_of_cash) < 2)#Total > 10000) 
+              inner_join(dfc %>% filter(Year == 2010 & Total > 10000)# ngla_net_gain_loss/ngla_revenue < 0.03 as.numeric(months_of_cash) < 2)#Total > 10000) 
                    %>% select(ID) %>% unique() , by = c("ID")), 
@@
   filter(abs(term) <= 5) %>% 
-  filter(estimator == "Gardner (2021)") %>% 
+  #filter(estimator == "Gardner (2021)") %>% 
   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +

### 2023-08-15 code/data_cleaning_longer.Rmd
updated code
lots of splits, need to standardize next

@@
 staffing <- read.csv("/Users/jhm65/Dropbox/Git/Data/FQHC_Staffing.csv")
+assliabs <- read.csv("/Users/jhm65/Dropbox/Git/Data/FQHC_Assets_and_Liabilities.csv")
 
@@
   left_join(staffing %>% select(EIN:Staff), by = c("EIN","form_year" = "Year"))
+
+## Fixing some dumb mistake
+
+# fixing.cw <- cbind(NewEINs = EINs[c(1:21, 23:323, 325:499, 501:617, 619:669, 671:738,  740:782, 784:790, 792:819, 821:989, 991:1106, 1108:1184, 1186)], 
+#       assliabs %>% 
+#   mutate(ch = Year - lag(Year)) %>% 
+#   filter(is.na(ch) | ch < 0)) %>% 
+#   mutate(Y = lead(X) - 1) %>% 
+#   select(EIN, NewEINs, X, Y)
+# 
+# 
+# for (k in 1:max(assliabs$X)){
+#   assliabs[k,]$EIN <- assliabs[k,] %>% 
+#     left_join(fixing.cw, by = c("EIN")) %>% 
+#     filter(X.x >= X.y & X.x <= Y) %>% 
+#     select(NewEINs) %>% 
+#     unlist()
+# }
+
+fins.revenue.expenses <- fins.revenue.expenses %>% 
+  left_join(assliabs %>% select(EIN:Liabilities), by = c("EIN","form_year" = "Year"))
+
 ```
@@
          Treatment = ifelse(att > 0, 1, 0)) %>% 
-  select(BHCMISID:STATE, Name:ID, ACA:Treatment, Total:dm.total, fs_contributions:Staff)
+  select(BHCMISID:STATE, Name:ID, ACA:Treatment, Total:dm.total, fs_contributions:Liabilities)
 

### 2023-08-15 code/analysis_Redo.Rmd
tuning parameters

@@
                Altman = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% 
-        inner_join(dfc %>% filter(Year == 2010 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
+        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                    %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
-      yname = "Qcomp", 
+      yname = "Altman", 
       treatment = "Tx",

### 2023-08-15 code/data_cleaning_longer.Rmd
tuning parameters

@@
   pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
-  filter(`2010` == 1 & `2011` == 1 & `2012` == 1) %>%   
+  filter(`2010` == 1 & `2011` == 1 ) %>%   
   #filter(`2014` == 1 & `2015` == 1) %>%  

### 2023-08-16 code/analysis_Redo.Rmd
tracking new docs

@@
 
+```{r}
+
+```
+
 ## Overall average effects
@@
 summary(as.numeric(dfc[dfc$Year == 2010,]$months_of_cash))
-summary(dfc[dfc$Year == 2010,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_revenue)
+quantile(dfc[dfc$Year == 2010,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_revenue, c(0.33, 0.67), na.rm = TRUE)
+
+dfc.new <- dfc %>% 
+        select(ID, Year, Tx, Att, STATE, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate, Assets, Liabilities,
+               Qcomp:Altman)
 
 did2s(
-      data = dfc %>% 
-        select(ID, Year, Tx, STATE, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate, Assets, Liabilities) %>%
-        mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6, 
-               CostPerPat = ngla_expense / Total, 
-               months_of_cash = as.numeric(months_of_cash),
-               Liquidity = (Assets - Liabilities) / Assets,
-               Profitability = ngla_net_gain_loss / Assets, 
-               Efficiency = ngla_revenue / Assets,
-               NetWorth = (Assets - Liabilities) / Liabilities, 
-               Altman = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% 
-        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
+      data = dfc.new %>% 
+        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.083) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                    %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
@@
 
-event_study(data = dfc %>% mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate) / 6) %>% 
-              inner_join(dfc %>% filter(Year == 2010 & Total > 10000)# ngla_net_gain_loss/ngla_revenue < 0.03 as.numeric(months_of_cash) < 2)#Total > 10000) 
+event_study(data = dfc.new %>% left_join(dfc %>% select(ID, Year, Pct.NHA:Pct.COM), by = c("ID","Year")) %>% 
+              inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/Assets < 0.05)# ngla_net_gain_loss/ngla_revenue < 0.03 as.numeric(months_of_cash) < 2)#Total > 10000) 
                    %>% select(ID) %>% unique() , by = c("ID")), 

### 2023-08-16 code/data_cleaning_longer.Rmd
tracking new docs

@@
 
-dfc %>% 
-  mutate(Liabilities = `Liabilities (as pct of assets)` * `Total net assets`, 
-         Staffing = `Total expenses before depreciation` * Personnel, 
-         LBE.pct = `Gross land, buildings and equipment (LBE)` / `Total net assets`, 
-         `Liabilities (as pct of assets)` = `Liabilities (as pct of assets)` * 100, 
-         `Surplus as a pct of before dep expenses` = `Surplus as a pct of before dep expenses` * 100, 
-         Qcomp = (pap.rate + crc.rate + asthma.rate + cad.rate + ivd.rate + childbmi.rate + adultbmi.rate) / 7, 
-         CostOfCare = `Total expenses before depreciation` / Total) %>%
+dfc <- dfc %>% 
+  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6, 
+               CostPerPat = ngla_expense / Total, 
+               months_of_cash = as.numeric(months_of_cash),
+               Liquidity = (Assets - Liabilities) / Assets,
+               Profitability = ngla_net_gain_loss / Assets, 
+               Efficiency = ngla_revenue / Assets,
+               NetWorth = (Assets - Liabilities) / Liabilities, 
+               Altman = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% 
+  mutate(Att.random = ifelse(Att > 0, Att, NA))
 
-  mutate(Liquidity =  `Total net assets` / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
-         Profitability =  `Unrestricted surplus (deficit) before depreciation` / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
-         Efficiency = (`Total revenue (unrestricted & restricted)` - `Total expenses before depreciation`) / (Cash + Investments + Receivables + `Gross land, buildings and equipment (LBE)`), 
-         NetWorth = (100 - `Liabilities (as pct of assets)`) / `Liabilities (as pct of assets)` / 100) %>% 
-  mutate(Altmans.Z = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% # 6.56, 3.26, 6.72, 1.05  OR 0.18, 0.3, 0.81, 0.14
-  mutate(Liquidity = ifelse(Liquidity == 'Inf', NA, Liquidity), 
-         Profitability = ifelse(Profitability == 'Inf', NA, Profitability), 
-         Efficiency = ifelse(Efficiency == 'Inf', NA, Efficiency), 
-         NetWorth = ifelse(NetWorth == 'Inf', NA, NetWorth), 
-         Altmans.Z = ifelse(Altmans.Z == 'Inf', NA, Altmans.Z))
+vec.atts <- rep(c(2012:2021), (table(comp.initial$Att) / 12)[-1])
+
+dfc <- rbind(dfc %>% filter(Att > 0), dfc %>% 
+  filter(Att == 0) %>% 
+  group_by(`BHCMIS ID`) %>% 
+  mutate(Att.random = sample(size = 1, vec.atts, replace = TRUE))) %>% 
+  mutate(year.rel = Year - Att.random)
+
+dfc
 
@@
 ```{r}
-#write_csv(dfc, file = "/Users/jhm65/Dropbox/Projects/Competition/data_processed/analyticalfile.csv")
+#write_csv(dfc, file = "/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
 

### 2023-08-16 code/analysis_Redo.Rmd
Starting to build figures

@@
 
+## Broken down by components
 ```{r}
 
+df.core <- dfc %>% 
+  mutate(MCD = Total * Pct.MCD / 100, 
+         None = Total * Pct.None / 100, 
+         MCR = Total * Pct.MCR / 100, 
+         COM = Total * Pct.COM / 100,
+
+         crc.rate = crc.rate * 100, 
+         pap.rate = pap.rate * 100, 
+         childbmi.rate = childbmi.rate * 100, 
+         adultbmi.rate = adultbmi.rate * 100, 
+         htn.rate = htn.rate * 100, 
+         dm.rate = dm.rate * 100) %>% 
+  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
+         MCD:COM, 
+         crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
+         Liquidity:NetWorth, 
+         Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman)
+
+did.core <- c(0, 0, 0, 0)
+
+for (j in 10:23){
+
+  df.temp <- df.core[,c(1:9, j)]
+  colnames(df.temp)[10] <- "Outcome"
+  outcomes <- did2s(
+      data = df.temp %>% 
+        inner_join(df.core[,c(4, 8, 24:ncol(df.core))] %>% filter(Year == 2010 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
+                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
+  did.core <- rbind(did.core, outcomes$coeftable)
+
+}
+
+did.core <- did.core[-1,]
+rownames(did.core) <- NULL
+
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+
+df.core %>% 
+  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
+         Treated = ifelse(Att > 0, 1, 0)) %>% 
+  group_by(Post, Treated) %>% 
+  select(MCD:NetWorth) %>% 
+  summarise_all(mean.nas) %>% 
+  # summarise(Total = mean(Total, na.rm = TRUE), 
+  #           Quality = mean(Qcomp, na.rm = TRUE), 
+  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
+  pivot_longer(cols = MCD:NetWorth) %>% 
+  mutate(value = round(value, 2)) %>% 
+  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
+  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
+  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
+  cbind(did.core) %>% 
+   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
+  mutate(Estimate = round(Estimate, 2), 
+         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
+         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
+  rename(Outcome = name) %>% 
+  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
+  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
+
 ```
-
-## Overall average effects
 

### 2023-08-16 code/data_cleaning_longer.Rmd
Starting to build figures

@@
 
-## Finalize the core set of measures
+## Finalize the core set of measures, adjust Altman components for inf estimates
 ```{r}
@@
 dfc <- dfc %>% 
-  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6, 
+  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
                CostPerPat = ngla_expense / Total, 
@@
 
+set.seed(123)
 dfc <- rbind(dfc %>% filter(Att > 0), dfc %>% 
@@
 dfc
+######adjust Altman components for inf estimates
 

### 2023-08-16 code/analysis_Redo.Rmd
more figures

@@
 ## Overall Effects on Key Variables
+```{r}
+
+df.core <- dfc %>% 
+  mutate(MCD = Total * Pct.MCD / 100, 
+         None = Total * Pct.None / 100, 
+         MCR = Total * Pct.MCR / 100, 
+         COM = Total * Pct.COM / 100,
+
+         crc.rate = crc.rate * 100, 
+         pap.rate = pap.rate * 100, 
+         childbmi.rate = childbmi.rate * 100, 
+         adultbmi.rate = adultbmi.rate * 100, 
+         htn.rate = htn.rate * 100, 
+         dm.rate = dm.rate * 100) %>% 
+  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
+         Total,Qcomp, Altman, #MCD:COM, 
+         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
+         #Liquidity:NetWorth, 
+         Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman)
+
+did.core <- c(0, 0, 0, 0)
+
+for (j in 10:12){
+
+  df.temp <- df.core[,c(1:9, j)]
+  colnames(df.temp)[10] <- "Outcome"
+  outcomes <- did2s(
+      data = df.temp %>% 
+        inner_join(df.core[,c(4, 8, 13:ncol(df.core))] %>% filter(Year == 2010 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
+                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
+  did.core <- rbind(did.core, outcomes$coeftable)
+
+}
+
+did.core <- did.core[-1,]
+rownames(did.core) <- NULL
+
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+
+df.core %>% 
+  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
+         Treated = ifelse(Att > 0, 1, 0)) %>% 
+  group_by(Post, Treated) %>% 
+  select(Total:Altman) %>% 
+  summarise_all(mean.nas) %>% 
+  # summarise(Total = mean(Total, na.rm = TRUE), 
+  #           Quality = mean(Qcomp, na.rm = TRUE), 
+  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
+  pivot_longer(cols = Total:Altman) %>% 
+  mutate(value = round(value, 2)) %>% 
+  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
+  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
+  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
+  cbind(did.core) %>% 
+   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
+  mutate(Estimate = round(Estimate, 2), 
+         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
+         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
+  rename(Outcome = name) %>% 
+  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
+  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
+
+```
 
@@
 
+```{r}
+
+splits <- quantile(dfc[dfc$Year == 2010,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_revenue, c(0.33, 0.66), na.rm = TRUE)
+
+df.profit <- dfc %>% 
+  mutate(MCD = Total * Pct.MCD / 100, 
+         None = Total * Pct.None / 100, 
+         MCR = Total * Pct.MCR / 100, 
+         COM = Total * Pct.COM / 100,
+
+         crc.rate = crc.rate * 100, 
+         pap.rate = pap.rate * 100, 
+         childbmi.rate = childbmi.rate * 100, 
+         adultbmi.rate = adultbmi.rate * 100, 
+         htn.rate = htn.rate * 100, 
+         dm.rate = dm.rate * 100) %>% 
+  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
+         Total, Qcomp, Altman) %>%  
+  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman)) %>% 
+  ungroup()#, #pap.rate:dm.total, Liquidity:Altman)
+
+df.profit <- df.profit %>% 
+  left_join(dfc %>% filter(Year == 2010) %>% select(ID, ngla_net_gain_loss, ngla_revenue, ngla_expense, Assets, Pct.NHA:Pct.COM) %>% 
+  mutate(profit.class = ifelse(ngla_net_gain_loss / ngla_revenue < 0.017, 1, 
+              ifelse(ngla_net_gain_loss / ngla_revenue >= 0.017 & ngla_net_gain_loss / ngla_revenue <= 0.081, 2, 
+              ifelse(ngla_net_gain_loss / ngla_revenue > 0.081, 3, NA)))) , by = c("ID"))
+
+did.profit <- c(0, 0, 0, 0)
+for (g in 1:3){
+  for (j in 10:12){
+
+  df.temp <- df.profit[,c(1:9, j, 13:ncol(df.profit))] 
+  colnames(df.temp)[10] <- "Outcome"
+  outcomes <- did2s(
+      data = df.temp %>% filter(profit.class == g), 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCR + Pct.None, 
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
+  did.profit <- rbind(did.profit, outcomes$coeftable)
+
+}}
+
+did.profit <- did.profit[-1,]
+rownames(did.profit) <- NULL
+
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+
+  did.profit %>% 
+   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
+  mutate(Estimate = round(Estimate, 2), 
+         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
+         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
+  rename(Outcome = name) %>% 
+  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
+  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
+
+```
+
 ## Effects startified by clinic size
@@
 
+df.temp
+
 did2s(
       data = dfc.new %>% 
-        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.083) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
+        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.081 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                    %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
-      yname = "Altman", 
+      yname = "Total", 
       treatment = "Tx",

### 2023-08-16 code/analysis_Redo.Rmd
got it to work!

@@
   left_join(dfc %>% filter(Year == 2010) %>% select(ID, ngla_net_gain_loss, ngla_revenue, ngla_expense, Assets, Pct.NHA:Pct.COM) %>% 
-  mutate(profit.class = ifelse(ngla_net_gain_loss / ngla_revenue < 0.017, 1, 
-              ifelse(ngla_net_gain_loss / ngla_revenue >= 0.017 & ngla_net_gain_loss / ngla_revenue <= 0.081, 2, 
-              ifelse(ngla_net_gain_loss / ngla_revenue > 0.081, 3, NA)))) , by = c("ID"))
+  mutate(pc = ngla_net_gain_loss / ngla_revenue) , by = c("ID")) %>% 
+  filter(`BHCMIS ID` %notin% c("010450","0438280","070430"))
+
+df.profit <- df.profit %>% 
+  mutate(profit.class = ifelse(pc < 0.017, 1, 
+              ifelse(pc >= 0.017 & pc <= 0.081, 2, 
+              ifelse(pc > 0.081, 3, NA))))
+
+splits1 <- c(min(df.profit$pc, na.rm = TRUE), splits)
+splits2 <- c(splits, max(df.profit$pc, na.rm = TRUE))
 
@@
   outcomes <- did2s(
-      data = df.temp %>% filter(profit.class == g), 
+      data = df.temp %>% filter(pc >= splits1[g] & pc <= splits2[g]), 
       yname = "Outcome", 
@@
 
-  did.profit %>% 
-   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
-  mutate(Estimate = round(Estimate, 2), 
-         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
-         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
-  rename(Outcome = name) %>% 
-  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
-  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
-  kable_styling(latex_options = c("striped")) %>%
-  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
-  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
+data.frame(Subset = c(rep("Low", 3), rep("Medium", 3), rep("High", 3)),
+      Outcome = rep(c("Total","Quality","Financial"), 3),
+      Estimate = as.numeric(did.profit[,1]), 
+      SD = as.numeric(did.profit[,2]))
 
@@
       data = dfc.new %>% 
-        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.081 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
+        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.08 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                    %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 

### 2023-08-16 code/analysis_Redo.Rmd
updated to better sample

@@
 
-splits <- quantile(dfc[dfc$Year == 2010,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_revenue, c(0.33, 0.66), na.rm = TRUE)
+splits <- quantile(dfc[dfc$Year == 2010,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_expense, c(0.33, 0.66), na.rm = TRUE)
 
@@
   left_join(dfc %>% filter(Year == 2010) %>% select(ID, ngla_net_gain_loss, ngla_revenue, ngla_expense, Assets, Pct.NHA:Pct.COM) %>% 
-  mutate(pc = ngla_net_gain_loss / ngla_revenue) , by = c("ID")) %>% 
-  filter(`BHCMIS ID` %notin% c("010450","0438280","070430"))
+  mutate(pc = ngla_net_gain_loss / ngla_expense) , by = c("ID")) %>% 
+  filter(`BHCMIS ID` %notin% c("010450","070430"))
 
@@
 
-splits1 <- c(min(df.profit$pc, na.rm = TRUE), splits)
+splits1 <- c(min(df.profit$pc, na.rm = TRUE)-1, splits)
 splits2 <- c(splits, max(df.profit$pc, na.rm = TRUE))
@@
   outcomes <- did2s(
-      data = df.temp %>% filter(pc >= splits1[g] & pc <= splits2[g]), 
+      data = df.temp %>% filter(pc > splits1[g] & pc <= splits2[g]), 
       yname = "Outcome", 
@@
 
-data.frame(Subset = c(rep("Low", 3), rep("Medium", 3), rep("High", 3)),
+data.frame(Subset = c(rep("01Low", 3), rep("02Medium", 3), rep("03High", 3)),
       Outcome = rep(c("Total","Quality","Financial"), 3),
       Estimate = as.numeric(did.profit[,1]), 
-      SD = as.numeric(did.profit[,2]))
+      SD = as.numeric(did.profit[,2])) %>% 
+  mutate(Subset.f = as.factor(Subset)) %>% 
+  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
+  geom_point() + 
+  xlab("Staggered 2-way DID Estimates") + 
+ylab(NULL) + 
+#adds the CIs
+geom_errorbarh(height=.1) +
+
+#sets the scales
+#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
+#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
+#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
+
+#adding a vertical line at the effect = 0 mark
+geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
+
+#faceting based on my subgroups
+  #facet_wrap(~X1) +
+facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
+      theme_tufte_revised()+
+   theme(strip.placement = "outside") +
+#theme(text=element_text(family="Times",size=12, color="black"))+
+theme(panel.spacing = unit(1, "lines")) + 
+  ggtitle("DID Estimates by Baseline Profitiability")
 
@@
 ## Effects startified by clinic size
+
+```{r}
+
+splits <- quantile(dfc[dfc$Year == 2010,]$Total, c(0.5), na.rm = TRUE)
+
+df.size <- dfc %>% 
+  mutate(MCD = Total * Pct.MCD / 100, 
+         None = Total * Pct.None / 100, 
+         MCR = Total * Pct.MCR / 100, 
+         COM = Total * Pct.COM / 100,
+
+         crc.rate = crc.rate * 100, 
+         pap.rate = pap.rate * 100, 
+         childbmi.rate = childbmi.rate * 100, 
+         adultbmi.rate = adultbmi.rate * 100, 
+         htn.rate = htn.rate * 100, 
+         dm.rate = dm.rate * 100) %>% 
+  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
+         Total, Qcomp, Altman) %>%  
+  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman)) %>% 
+  ungroup()#, #pap.rate:dm.total, Liquidity:Altman)
+
+df.size <- df.size %>% 
+  left_join(dfc %>% filter(Year == 2010) %>% select(ID, Total, Pct.NHA:Pct.COM) %>% 
+  rename(Size = Total) , by = c("ID")) %>% 
+  filter(`BHCMIS ID` %notin% c("010450","070430"))
+
+splits1 <- c(min(df.size$Size, na.rm = TRUE), splits)
+splits2 <- c(splits, max(df.size$Size, na.rm = TRUE)+1)
+
+did.size <- c(0, 0, 0, 0)
+for (g in 1:2){
+  for (j in 10:12){
+
+  df.temp <- df.size[,c(1:9, j, 13:ncol(df.size))] 
+  colnames(df.temp)[10] <- "Outcome"
+  outcomes <- did2s(
+      data = df.temp %>% filter(Size >= splits1[g] & Size < splits2[g]), 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCR + Pct.None, 
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
+  did.size <- rbind(did.size, outcomes$coeftable)
+
+}}
+
+did.size <- did.size[-1,]
+rownames(did.size) <- NULL
+
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+
+data.frame(Subset = c(rep("01Below", 3), rep("02Above", 3)),
+      Outcome = rep(c("Total","Quality","Financial"), 2),
+      Estimate = as.numeric(did.size[,1]), 
+      SD = as.numeric(did.size[,2])) %>% 
+  mutate(Subset.f = as.factor(Subset)) %>% 
+  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.96, xmax = Estimate + SD * 1.96)) + 
+  geom_point() + 
+  xlab("Staggered 2-way DID Estimates") + 
+ylab(NULL) + 
+#adds the CIs
+geom_errorbarh(height=.1) +
+
+#sets the scales
+#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
+#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
+#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
+
+#adding a vertical line at the effect = 0 mark
+geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
+
+#faceting based on my subgroups
+  #facet_wrap(~X1) +
+facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
+      theme_tufte_revised()+
+   theme(strip.placement = "outside") +
+#theme(text=element_text(family="Times",size=12, color="black"))+
+theme(panel.spacing = unit(1, "lines")) + 
+  ggtitle("DID Estimates by Baseline Clinics Size")
+```
 
@@
       data = dfc.new %>% 
-        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.08 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
+        inner_join(dfc %>% filter(Year == 2010 & Total < 14000 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                    %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
-      yname = "Total", 
+      yname = "Altman", 
       treatment = "Tx",

### 2023-08-16 code/data_cleaning_longer.Rmd
updated to better sample

@@
   pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
-  filter(`2010` == 1 & `2011` == 1 ) %>%   
+  filter(`2010` == 1 & `2011` == 1 & `2012` == 1) %>%   
   #filter(`2014` == 1 & `2015` == 1) %>%  
@@
 
-vec.atts <- rep(c(2012:2021), (table(comp.initial$Att) / 12)[-1])
+vec.atts <- rep(c(2013:2021), (table(comp.initial$Att) / 12)[-1])
 

### 2023-08-17 code/analysis_Redo.Rmd
finally working again
Finding my informative splits

--- 2023-08-16 code/analysis_Redo.Rmd
@@
 
+```{r}
+library(readxl)
+library(did2s)
+library(tidyverse)
+
+```
+
+```{r}
+#dfc <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
+```
+
 ## Balance between treated and controls
@@
 
-  df.temp <- df.core[,c(1:9, j)]
+  df.temp <- df.core[,c(1:9, j, 13:ncol(df.core))]
   colnames(df.temp)[10] <- "Outcome"
   outcomes <- did2s(
-      data = df.temp %>% 
-        inner_join(df.core[,c(4, 8, 13:ncol(df.core))] %>% filter(Year == 2010 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
-                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
+      data = df.temp , 
       yname = "Outcome", 
       treatment = "Tx",
-        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year, 
         second_stage = ~ i(Tx, ref = FALSE),
@@
 
-  df.temp <- df.core[,c(1:9, j)]
+  df.temp <- df.core[,c(1:9, j, 24:ncol(df.core))]
   colnames(df.temp)[10] <- "Outcome"
   outcomes <- did2s(
-      data = df.temp %>% 
-        inner_join(df.core[,c(4, 8, 24:ncol(df.core))] %>% filter(Year == 2010 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
-                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
+      data = df.temp, 
       yname = "Outcome", 
       treatment = "Tx",
-        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
         second_stage = ~ i(Tx, ref = FALSE),
@@
 
-splits <- quantile(dfc[dfc$Year == 2010,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_revenue, c(0.33, 0.66), na.rm = TRUE)
+#splits <- quantile(dfc[dfc$Year == 2011,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_expense, c(0.5), na.rm = TRUE)
+splits <- quantile(dfc[dfc$year.rel == -1,]$ngla_net_gain_loss / dfc[dfc$year.rel == -1,]$ngla_expense, c(0.5), na.rm = TRUE)
 
@@
   select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
-         Total, Qcomp, Altman) %>%  
+         Total, Qcomp, Altman, Pct.NHA:Pct.COM) %>%  
   mutate(Altman = ifelse(is.infinite(Altman), NA, Altman)) %>% 
@@
 df.profit <- df.profit %>% 
-  left_join(dfc %>% filter(Year == 2010) %>% select(ID, ngla_net_gain_loss, ngla_revenue, ngla_expense, Assets, Pct.NHA:Pct.COM) %>% 
-  mutate(profit.class = ifelse(ngla_net_gain_loss / ngla_revenue < 0.017, 1, 
-              ifelse(ngla_net_gain_loss / ngla_revenue >= 0.017 & ngla_net_gain_loss / ngla_revenue <= 0.081, 2, 
-              ifelse(ngla_net_gain_loss / ngla_revenue > 0.081, 3, NA)))) , by = c("ID"))
+  left_join(dfc %>% filter(year.rel == -1) %>% select(ID, ngla_net_gain_loss, ngla_revenue, ngla_expense, Assets) %>% 
+  mutate(pc = ngla_net_gain_loss / ngla_expense) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))
+
+splits1 <- c(min(df.profit$pc, na.rm = TRUE)-1, splits)
+splits2 <- c(splits, max(df.profit$pc, na.rm = TRUE))
 
 did.profit <- c(0, 0, 0, 0)
-for (g in 1:3){
+for (g in 1:(length(splits) + 1)){
   for (j in 10:12){
@@
   outcomes <- did2s(
-      data = df.temp %>% filter(profit.class == g), 
+      data = df.temp %>% filter(pc > splits1[g] & pc <= splits2[g]), 
       yname = "Outcome", 
       treatment = "Tx",
-        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCR + Pct.None, 
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
         second_stage = ~ i(Tx, ref = FALSE),
@@
 
-  did.profit %>% 
-   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
-  mutate(Estimate = round(Estimate, 2), 
-         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
-         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
-  rename(Outcome = name) %>% 
-  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
-  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
-  kable_styling(latex_options = c("striped")) %>%
-  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
-  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
+data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
+      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
+      Estimate = as.numeric(did.profit[,1]), 
+      SD = as.numeric(did.profit[,2])) %>% 
+  mutate(Subset.f = as.factor(Subset)) %>% 
+  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
+  geom_point() + 
+  xlab("Staggered 2-way DID Estimates") + 
+ylab(NULL) + 
+#adds the CIs
+geom_errorbarh(height=.1) +
+
+#sets the scales
+#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
+#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
+#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
+
+#adding a vertical line at the effect = 0 mark
+geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
+
+#faceting based on my subgroups
+  #facet_wrap(~X1) +
+facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
+      theme_tufte_revised()+
+   theme(strip.placement = "outside") +
+#theme(text=element_text(family="Times",size=12, color="black"))+
+theme(panel.spacing = unit(1, "lines")) + 
+  ggtitle("DID Estimates by Baseline Profitiability")
 
@@
 ## Effects startified by clinic size
+```{r}
+
+#splits <- quantile(dfc[dfc$Year == 2011,]$Total, c(0.5), na.rm = TRUE)
+splits <- quantile(dfc[dfc$year.rel == -1,]$Total, c(0.5), na.rm = TRUE)
+
+df.size <- dfc %>% 
+  mutate(MCD = Total * Pct.MCD / 100, 
+         None = Total * Pct.None / 100, 
+         MCR = Total * Pct.MCR / 100, 
+         COM = Total * Pct.COM / 100,
+
+         crc.rate = crc.rate * 100, 
+         pap.rate = pap.rate * 100, 
+         childbmi.rate = childbmi.rate * 100, 
+         adultbmi.rate = adultbmi.rate * 100, 
+         htn.rate = htn.rate * 100, 
+         dm.rate = dm.rate * 100) %>% 
+  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
+         Total, Qcomp, Altman, Pct.NHA:Pct.COM) %>%  
+  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman)) %>% 
+  ungroup()#, #pap.rate:dm.total, Liquidity:Altman)
+
+df.size <- df.size %>% 
+  left_join(dfc %>% filter(Year == 2010) %>% select(ID, Total) %>% 
+  mutate(Size = Total) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))
+
+splits1 <- c(min(df.size$Size, na.rm = TRUE)-1, splits)
+splits2 <- c(splits, max(df.size$Size, na.rm = TRUE))
+
+did.size <- c(0, 0, 0, 0)
+for (g in 1:(length(splits) + 1)){
+  for (j in 10:12){
+
+  df.temp <- df.size[,c(1:9, j, 13:ncol(df.size))] 
+  colnames(df.temp)[10] <- "Outcome"
+  outcomes <- did2s(
+      data = df.temp %>% filter(Size > splits1[g] & Size <= splits2[g]), 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
+  did.size <- rbind(did.size, outcomes$coeftable)
+
+}}
+
+did.size <- did.size[-1,]
+rownames(did.size) <- NULL
+
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+
+data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
+      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
+      Estimate = as.numeric(did.size[,1]), 
+      SD = as.numeric(did.size[,2])) %>% 
+  mutate(Subset.f = as.factor(Subset)) %>% 
+  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
+  geom_point() + 
+  xlab("Staggered 2-way DID Estimates") + 
+ylab(NULL) + 
+#adds the CIs
+geom_errorbarh(height=.1) +
+
+#sets the scales
+#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
+#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
+#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
+
+#adding a vertical line at the effect = 0 mark
+geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
+
+#faceting based on my subgroups
+  #facet_wrap(~X1) +
+facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
+      theme_tufte_revised()+
+   theme(strip.placement = "outside") +
+#theme(text=element_text(family="Times",size=12, color="black"))+
+theme(panel.spacing = unit(1, "lines")) + 
+  ggtitle("DID Estimates by Baseline Size")
+
+```
 
@@
       data = dfc.new %>% 
-        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.081 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
+        inner_join(dfc %>% filter(Year == 2010 & Total < 14000 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                    %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
-      yname = "Total", 
+      yname = "Altman", 
       treatment = "Tx",

### 2023-08-17 code/data_cleaning_longer.Rmd
finally working again
Finding my informative splits

--- 2023-08-16 code/data_cleaning_longer.Rmd
@@
 library (readr)
+
+library(did2s)
 
@@
                Efficiency = ngla_revenue / Assets,
-               NetWorth = (Assets - Liabilities) / Liabilities, 
+               NetWorth = (Assets - Liabilities) / Liabilities)
+
+dfc <- dfc %>% 
+  mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity), 
+         Profitability = ifelse(is.infinite(Profitability), NA, Profitability), 
+         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency), 
+         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
          Altman = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% 
@@
 
-dfc
 ######adjust Altman components for inf estimates

### 2023-08-19 code/analysis_Redo.Rmd
added in the geographic analysis

@@
 knitr::opts_chunk$set(echo = TRUE)
-```
-
-```{r}
-
-df.sum <- df.qual.exp %>% #filter(`Grant Number` != "H80CS00225") %>% 
-  ungroup() %>% 
-  #rename(`Grant Number` = Grant.Number, `Surplus as a pct of before dep expenses` = Surplus.as.a.pct.of.after.dep.expenses) %>% 
-  #filter(MarketShare < 0.4) %>%  #median(MarketShare, na.rm = TRUE) - 0.25
-  #inner_join(df.qual.exp %>% filter(Year == 2015 & Total < 15000) %>% select(`Grant Number`), by = c("Grant Number")) %>%  #& Zips < 1.75 or 7.75
-  select(`Grant Number`, Year, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL, Total, IMM2yo:DepScrn) %>%
-  # inner_join(df.qual.exp %>% filter(Year == 2015) %>%
-  #                                           mutate(ZipFilter = ifelse(Total < 12000, 1,
-  #                                                              ifelse(Total > 12000, 2, NA))) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
-  inner_join(df.qual.exp %>% filter(Year == 2016) %>% #mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% 
-               select(`Grant Number`, ZipFilter, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("Grant Number")) %>% 
-  select(`Grant Number`, Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL, Pct.NHA:Pct.Children, MCD, COM, MCR, Total, IMM2yo:DepScrn) %>% 
-  mutate(Tx = ifelse(Year >= Att & Att > 0, 1, 0)) %>% 
-  unique() %>% 
-  mutate(NewQuality = (CRC + ChildBMI + AdultBMI + Tobac + DepScrn) / 5)
-
-#library(did2s)
-
-did2s(
-      data = df.sum %>% inner_join(df.qual.exp %>% filter(MarketShare > 1) %>% select(`Grant Number`) %>% unique(), by = c("Grant Number")), 
-      yname = "Qcomp", 
-      treatment = "Tx",
-        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
-        second_stage = ~ i(Tx, ref = FALSE),
-        cluster_var = "ID",
-      verbose = FALSE
-    )
-
-#select(ID, Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z) %>% left_join(df.qual.exp %>% select(ID, Year, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("ID","Year"))
-out.qual <- event_study(data = df.qual.exp %>% filter(ZipFilter == 1), 
-  yname = "Altmans.Z", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM)
-
-out.qual %>% 
-  filter(estimator %notin% c("Borusyak, Jaravel, Spiess (2021)")) %>% 
-filter(abs(term) <= 3) %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)
-
-```
-
-## Variations
-
-```{r}
-
-did2s(
-      data = df.sum %>% left_join(df.spill2 %>% 
-  group_by(`Grant Number`, Year) %>% 
-  summarise(num = sum((Dist + 1) * Sites), 
-         denom = sum(Sites), 
-         avgdist = num / denom) %>% 
-  filter(Year %in% c(2015, 2019)) %>% 
-  pivot_wider(id_cols = `Grant Number`, names_from = Year, values_from = avgdist) %>% 
-  mutate(ds = `2019` - `2015`) %>% 
-    ungroup() %>% 
-    mutate(filt = ifelse(ds > median(ds, na.rm = TRUE), 1, 0)), by = c("Grant Number")) %>% filter(ds < 1),#%>% filter(ZipFilter == 2), 
-      yname = "NewQuality", 
-      treatment = "Tx",
-        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
-        second_stage = ~ i(Tx, ref = FALSE),
-        cluster_var = "ID",
-      verbose = FALSE
-    )
-
-did2s(
-      data = df.sum %>% left_join(df.spill2 %>% 
-  group_by(`Grant Number`, Year) %>% 
-  summarise(num = sum((Dist + 1) * Sites), 
-         denom = sum(Sites), 
-         avgdist = num / denom) , by = c("Grant Number","Year")) ,#%>% filter(ZipFilter == 2), 
-      yname = "NewQuality", 
-      treatment = "Tx",
-        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
-        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(avgdist / 10) + I(Tx *as.numeric(avgdist / 10)),
-        cluster_var = "ID",
-      verbose = FALSE
-    )
-
-did2s(
-      data = df.sum %>% left_join(df.z.dist %>% select(`Grant Number.y`, DistToClosestSite), by = c("Grant Number" = "Grant Number.y")) %>% filter(is.na(DistToClosestSite) | DistToClosestSite > 5),
-      yname = "Qcomp", 
-      treatment = "Tx",
-        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
-        second_stage = ~ i(Tx, ref = FALSE) ,
-        cluster_var = "ID",
-      verbose = FALSE
-    )
-
-set.seed(345)
-did2s(
-      data = df.sum %>% left_join(df.z.dist %>% select(`Grant Number.y`, DistToClosestSite), by = c("Grant Number" = "Grant Number.y")) %>% 
-        group_by(ID) %>% 
-  mutate(DistToClosestSite = ifelse(is.na(DistToClosestSite), sample(size = 1, df.z.dist$DistToClosestSite, replace = T), DistToClosestSite)),
-      yname = "NewQuality", 
-      treatment = "Tx",
-        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
-        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(DistToClosestSite / 1) + I(Tx *as.numeric(DistToClosestSite / 1)),
-        cluster_var = "ID",
-      verbose = FALSE
-    )
-
 ```
@@
 
-## Changes in geographic distribution of resources by Distance to competitive zip
-
-## Rival selecting where to put new site
+## OTher splits
 
@@
 event_study(data = dfc.new %>% left_join(dfc %>% select(ID, Year, Pct.NHA:Pct.COM), by = c("ID","Year")) %>% 
-              inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/Assets < 0.05)# ngla_net_gain_loss/ngla_revenue < 0.03 as.numeric(months_of_cash) < 2)#Total > 10000) 
+              inner_join(dfc %>% filter(Year == 2010 )# ngla_net_gain_loss/ngla_revenue < 0.03 as.numeric(months_of_cash) < 2)#Total > 10000) 
                    %>% select(ID) %>% unique() , by = c("ID")), 
@@
 ```
+
+## Changes in geographic distribution of resources by Distance to competitive zip
+
+```{r}
+
+## Treatment vs control, only in zip code of interest
+df.z <- left_join(dfc #%>% filter(`Grant Number` != "H80CS00225")
+                  , #uds.zip %>% mutate(Zip = `Zip Code`) %>% select(`Grant Number`, Zip) %>% unique() , by = c("Grant Number")) %>%
+                  uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
+                    filter(Year %in% c(2010:2021)) %>% 
+              select(`BHCMIS ID`, Zip) %>%
+              unique() %>% filter(!is.na(Zip)), by = c("BHCMIS ID")) %>%
+  left_join(uds.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear", "Zip" = "ZipCode")) %>%
+  filter(!is.na(GrantNumber)) %>% 
+  left_join(clinics.in.zips %>% select(Zip:Clinics), by = c("Zip","Year")) %>%
+  mutate(Tx.z = ifelse(Clinics == 1 , 0, 
+                ifelse(is.na(Clinics), NA, 1)), # | is.na(Clinics)
+         ID = as.numeric(factor(paste(`BHCMIS ID`, Zip, sep = "-")))) %>%
+  select(`BHCMIS ID`:Year, Att, ID, Zip:Tx.z) %>%
+  arrange(`BHCMIS ID`, Zip, Year) %>% 
+  unique() #%>%  inner_join(df.qual.exp %>% filter(Year == 2015 & Total > 12050) %>% select(`Grant Number`), by = c("Grant Number"))  #& Zips < 3.75 or 4.75
+  # %>%   filter(MarketShare > median(MarketShare, na.rm = TRUE) - 0.25)
+
+df.z <- df.z %>%
+  left_join(df.z %>%
+            filter(Tx.z == 1) %>%
+            group_by(ID, Zip) %>%
+            summarise(Att.z = min(Year)), by = c("ID", "Zip")) %>%
+  mutate(Att.z = ifelse(is.na(Att.z), 0, Att.z)) #%>%
+# inner_join(df.z %>% filter(!is.na(Clinics)) %>% group_by(ID) %>% summarise(n()) %>% filter(`n()` == length(unique(df.qual.exp$Year))), by = c("ID")) #%>% filter(Att == Att.z)
+
+## Whole zip as one measure
+
+df.z.full <- df.z %>% ############## NOTE: Original +500 effect was recoved with Att.z, not Att
+  select(Zip, Att.z, Year) %>% 
+  unique() %>% 
+  left_join(uds.zip, by = c("Zip" = "ZipCode", "Year" = "ReportingYear")) %>% 
+  left_join(dfc %>% 
+            select(`BHCMIS ID`, Year, Qcomp), by = c("BHCMISID" = "BHCMIS ID", "Year")) %>% 
+  group_by(Zip, Year, Att.z) %>% 
+  summarise(
+    Total.z = sum(NumberofPatients, na.rm = TRUE), 
+    Quality.z = sum(NumberofPatients * Qcomp, na.rm = TRUE) / Total.z) %>% 
+  ungroup() %>% 
+  mutate(ID = as.numeric(as.factor(Zip)))# %>% group_by(`Grant Number`, Year, Att) %>% summarise(ID = min(ID), Total.z = sum(Total.z, na.rm = TRUE)) # %>% filter(Year > 2015),
+
+df.zip.1 <- df.z %>% select(ID, Year, Att, NumberofPatients)
+df.zip.2 <- df.z.full %>% select(ID, Year, Att.z, Total.z:Quality.z)
+
+```
+
+## DIstance Rival Traveled
+```{r}
+
+## Distance of Competitor to New Site
+df.z.dist <- df.z.full %>% 
+  filter(Att.z == Year) %>% 
+  select(Zip:Total.z) %>% 
+  left_join(uds.sites.full %>% select(`BHCMIS ID`, Year, Zip) %>% unique(), by = c("Zip","Year")) %>% 
+  left_join(df.z %>% filter(Tx == 1) %>% select(`BHCMIS ID`, Year, Zip) %>% unique(), by = c("Zip","Year")) %>% 
+  filter(`BHCMIS ID.x` != `BHCMIS ID.y`)
+
+## Read in Centroid Data
+zip.centroids <- read.csv("/Users/jhm65/Dropbox/Git/Data/ZIP_Code_Population_Weighted_Centroids.csv") %>% 
+  mutate(ZipCode = str_pad(STD_ZIP5, 5, pad = "0")) %>% 
+  select(ZipCode, X, Y)
+## Add missing centroids
+zip.centroids <- rbind(zip.centroids, c(ZipCode = "37243", X = -86.783, Y = 36.165), 
+                                      c(ZipCode = "95951", X = -121.98, Y = 39.73), 
+                                      c(ZipCode = "99733", X = -144.166941, Y = 65.799773)) %>% 
+  mutate(X = as.numeric(X), Y = as.numeric(Y))
+
+df.z.dist <- df.z.dist %>% mutate(DistToClosestSite = NA, ZipOfClosestSite = NA)
+
+for (g in 1:nrow(df.z.dist)){
+#g <- 1
+ temp <- rbind(zip.centroids %>% filter(ZipCode == df.z.dist[g,]$Zip), 
+          zip.centroids %>% filter(ZipCode %in% unique(uds.sites.full[uds.sites.full$`BHCMIS ID` == df.z.dist[g,]$`BHCMIS ID.x` & uds.sites.full$Year == df.z.dist[g,]$Year,]$Zip))) %>% 
+   unique()
+  mm <- as.matrix(dist(as.matrix(temp$X, temp$Y), method = "euclidean"))[-1,1]
+  df.z.dist[g,]$DistToClosestSite <-  min(mm) * 111.139
+  df.z.dist[g,]$ZipOfClosestSite  <- ifelse(is.na(temp[2,]$ZipCode), temp[1,]$ZipCode, unlist(temp[-1,]$ZipCode[rank(mm) == 1]))
+}
+
+#df.z.dist[19,]$DistToClosestSite <- 0
+df.z.dist <- df.z.dist %>% 
+  filter(!is.infinite(DistToClosestSite))
+
+df.z.dist <- df.z.dist %>% 
+  inner_join(df.z.dist %>% group_by(`BHCMIS ID.y`) %>% summarise(Att.z = min(Att.z)), by = c("BHCMIS ID.y", "Att.z")) %>% 
+  unique()
+
+mean(df.z.dist$DistToClosestSite)
+quantile(df.z.dist$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))
+
+# mean(df.z.dist[df.z.dist$ZipFilter == 1,]$DistToClosestSite)
+# mean(df.z.dist[df.z.dist$ZipFilter == 2,]$DistToClosestSite)
+# 
+# quantile(df.z.dist[df.z.dist$ZipFilter == 1,]$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))
+# quantile(df.z.dist[df.z.dist$ZipFilter == 2,]$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))
+
+zipsize <- zctas(starts_with = c(df.z.dist$Zip, df.z.dist$ZipOfClosestSite), year = 2010)
+
+## Original Figure
+df.z.dist.plot <- df.z.dist %>% 
+  left_join(zipsize %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
+  left_join(uds.sites.full %>% select(Zip, `Site State`) %>% unique(), by = c("Zip")) %>% 
+  left_join(census %>% select(ZipCode, YEAR, TotalPop), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
+  arrange(desc(DistToClosestSite)) %>% 
+  mutate(Area.SQmiles = ALAND10 / 2.59e6) %>% 
+  mutate(Density.NewZip = TotalPop / Area.SQmiles, 
+         l.density = log(TotalPop / Area.SQmiles)) %>% 
+  unique()
+
+df.z.dist.plot %>% 
+  ggplot(aes(x = log(Density.NewZip), y = DistToClosestSite)) + geom_point(aes(size = Area.SQmiles)) +
+  ggtitle("Distance from Rival's newly competing zip ocde to closest incumbent zip code by Density and Area of newly competing zip code")
+
+summary(lm(DistToClosestSite ~ log(Density.NewZip), data = df.z.dist.plot))
+
+# Updated Figure
+df.z.dist.plot <- df.z.dist.plot %>% 
+  select(Zip:ZipOfClosestSite, Density.NewZip) %>% 
+  left_join(zipsize %>% select(GEOID10, ALAND10), by = c("ZipOfClosestSite" = "GEOID10")) %>% 
+  left_join(uds.sites.full %>% select(Zip, `Site State`) %>% unique(), by = c("ZipOfClosestSite" = "Zip")) %>% 
+  left_join(census %>% select(ZipCode, YEAR, TotalPop), by = c("Year" = "YEAR", "ZipOfClosestSite" = "ZipCode")) %>% 
+  arrange(desc(DistToClosestSite)) %>% 
+  mutate(Area.SQmiles = ALAND10 / 2.59e6) %>% 
+  mutate(Density.Origin = TotalPop / Area.SQmiles)
+
+df.z.dist.plot %>% 
+  ggplot(aes(x = log(Density.NewZip), y = DistToClosestSite, color = log(Density.Origin))) + geom_point() +
+  scale_colour_gradientn(colours = terrain.colors(10))+ theme_minimal()+
+  ylab("Distance from Competative to closest Rival Site (km)") +
+  ggtitle("Distance from newly competative Zip to Rival's closest existing zip, by log Density of areas")
+
+p <- df.z.dist.plot %>% 
+  ggplot(aes(x = log(Density.Origin), y = log(Density.NewZip))) + 
+  geom_point(aes(size = DistToClosestSite, colour = DistToClosestSite)) + 
+  scale_colour_gradientn(colours = c("green","lightblue","purple"),
+                         values = c(1.0,0.7,0.1,0))  +#scale_colour_gradientn(colours = terrain.colors(10))+ 
+  theme_minimal() + ylab("Log Population Density of New Zip Code") + 
+  xlab("Log Population Density of Nearest Service Area Zip Code") + 
+  labs(color = "Distance Travelled to\nOpenNew Site (km)") + 
+  guides(size = FALSE) + xlim(0.5, 11.5) + ylim(0.5, 11.5)
+p
+
+summary(lm(log(Density.Origin) ~ log(Density.NewZip), data = df.z.dist.plot))
+```
+
+## Primary effects by distance rival travelled
+```{r}
+set.seed(123)
+df.dist <- df.core %>% 
+  left_join(df.z.dist.plot %>% select(`BHCMIS ID.y`, DistToClosestSite), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
+  group_by(`BHCMIS ID`) %>% 
+  mutate(Dist.random = sample(size = 1, unique(df.z.dist.plot$DistToClosestSite), replace = TRUE), 
+         Dist.random = ifelse(Att > 0, DistToClosestSite, Dist.random))
+
+#splits <- quantile(dfc[dfc$Year == 2011,]$Total, c(0.5), na.rm = TRUE)
+splits <- quantile(df.dist[df.dist$year.rel == -1,]$Dist.random, c(0.5), na.rm = TRUE)
+
+splits1 <- c(min(df.dist$Dist.random, na.rm = TRUE)-1, splits)
+splits2 <- c(splits, max(df.dist$Dist.random, na.rm = TRUE))
+
+did.dist <- c(0, 0, 0, 0)
+for (g in 1:(length(splits) + 1)){
+  for (j in 10:12){
+
+  df.temp <- df.dist[,c(1:9, j, 13:ncol(df.dist))] 
+  colnames(df.temp)[10] <- "Outcome"
+  outcomes <- did2s(
+      data = df.temp %>% filter(Dist.random > splits1[g] & Dist.random <= splits2[g]), 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
+  did.dist <- rbind(did.dist, outcomes$coeftable)
+
+}}
+
+did.dist <- did.dist[-1,]
+rownames(did.dist) <- NULL
+
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+
+data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
+      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
+      Estimate = as.numeric(did.dist[,1]), 
+      SD = as.numeric(did.dist[,2])) %>% 
+  mutate(Subset.f = as.factor(Subset)) %>% 
+  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
+  geom_point() + 
+  xlab("Staggered 2-way DID Estimates") + 
+ylab(NULL) + 
+#adds the CIs
+geom_errorbarh(height=.1) +
+
+#sets the scales
+#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
+#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
+#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
+
+#adding a vertical line at the effect = 0 mark
+geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
+
+#faceting based on my subgroups
+  #facet_wrap(~X1) +
+facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
+      theme_tufte_revised()+
+   theme(strip.placement = "outside") +
+#theme(text=element_text(family="Times",size=12, color="black"))+
+theme(panel.spacing = unit(1, "lines")) + 
+  ggtitle("DID Estimates by Baseline Size")
+```
+
+## Rival selecting where to put new site, takes 30+ minutes to work
+
+```{r}
+
+## Build the first part of the dataset
+
+df.spill <- df.z %>% 
+  left_join(df.z.dist %>% 
+  select(`BHCMIS ID.y`, Zip) %>% 
+    unique() %>% 
+    rename(ZipOfComp = Zip), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
+  #filter(!is.na(ZipOfComp)) %>% 
+  #mutate(ZipOfComp = ifelse(`BHCMIS ID` == "H80CS00765", 95991, ZipOfComp)) %>% 
+  left_join(zip.centroids, by = c("Zip" = "ZipCode")) %>% 
+  left_join(zip.centroids, by = c("ZipOfComp" = "ZipCode")) %>% 
+  mutate(Dist = sqrt((X.x - X.y) ^ 2 + (Y.x - Y.y) ^ 2) * 111.139) %>% 
+  mutate(Dist.f = ifelse(is.na(Dist), "-1",
+                  ifelse(Dist == 0, 0, 
+                  ifelse(Dist > 0 & Dist < 20, 1, 
+                  ifelse(Dist >= 20 & Dist < 50, 2, 
+                  ifelse(Dist >= 50 & Dist < 100, 3, 4)))))) %>% 
+  #filter(is.na(Dist.f) | Dist.f == 2) %>% 
+  left_join(uds.sites.full %>% 
+              filter(`Location Setting` %in% c("All Other Clinic Types")) %>% 
+              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
+                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
+                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
+                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
+                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
+                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
+              group_by(`BHCMIS ID`, Year, Zip) %>% 
+              summarise(Sites = n(), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
+                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)), by = c("BHCMIS ID","Year", "Zip")) %>% 
+  mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
+         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
+         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
+         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
+         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
+         Calendar = ifelse(is.na(Calendar), 0, Calendar))
+
+dist.vecs <- df.spill[!is.na(df.spill$Dist),]$Dist
+
+df.spill %>% 
+  group_by(Dist.f) %>% 
+  summarise(n())
+
+## Find neighbors based on some circle around FQHC zip
+
+mm <- dist(zip.centroids[,2:3])
+mm <- as.matrix(mm) * 111.139
+
+mm.2 <- mm[zip.centroids$ZipCode %in% unique(df.spill$Zip),]
+
+mm.2 <- as.matrix((mm.2 < 50) + 0 )
+rowSums(mm.2)
+
+mm.3 <- c(CenterZip = 0, Year = 0, Competing.Sites = 0)
+for (g in 1:dim(mm.2)[1]){
+  mm.3 <- rbind(mm.3, cbind(CenterZip = zip.centroids[rownames(mm.2)[g],]$ZipCode, zip.centroids[names(mm.2[g,][which(as.vector(mm.2[g,] == 1))]),]) %>% 
+  left_join(uds.sites.full %>% filter(Year %in% c(2010:2021)) %>% group_by(Year, Zip) %>% summarise(Sites.Total = n()), by = c("ZipCode" = "Zip")) %>% 
+  left_join(df.spill %>% select(`BHCMIS ID`, Year, Zip, Sites), by = c("ZipCode" = "Zip", "Year")) %>% 
+  mutate(Sites.Total = ifelse(is.na(Sites.Total), 0, Sites.Total), 
+         Sites = ifelse(is.na(Sites), 0, Sites), 
+         Competing.Sites = Sites.Total - Sites) %>% 
+  filter(CenterZip != ZipCode) %>% 
+  group_by(CenterZip, Year) %>% 
+  summarise(Competing.Sites = sum(Competing.Sites)) %>% 
+    as.matrix())
+}
+
+mm.3 <- mm.3[-1,]
+
+#mm.100 <- mm.3 %>% data.frame() 
+#mm.60 <- mm.3 %>% data.frame() 
+#mm.50 <- mm.3 %>% data.frame() 
+#mm.20 <- mm.3 %>% data.frame() 
+#mm.10 <- mm.3 %>% data.frame()
+
+#mm.3 <- mm.50
+
+```
+
+## NumberofPatients and Total.Hours are the best cases, controlling for Sites
+```{r}
+
+ i <- 10
+  df.temp <- df.spill2[,c(1:5, 11, i)]
+  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
+  model_feols_clustered <- did2s(
+      data = df.temp, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Sites | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
+  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]
+
+for (i in 12:15){
+  df.temp <- df.spill2[,c(1:5, 11, i)]
+  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
+  model_feols_clustered <- did2s(
+      data = df.temp, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Sites | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
+  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),])
+}
+
+  cbind(Outcome = c("Hours Per Week","Perminance","Weekly Schedule","Calendar Schedule","Total"),   TEs, TEs_Dist)
+```
+
+```{r}
+
+df.spill2 <- df.spill %>% 
+  left_join(mm.3 %>% data.frame() %>% mutate(Year = as.numeric(Year)), by = c("Zip" = "CenterZip","Year")) %>% 
+  mutate(Competing.Sites = as.numeric(ifelse(is.na(Competing.Sites), 0, Competing.Sites)), 
+         D = ifelse(Competing.Sites > 0, 1, 0))
+
+#length(unique(df.spill2[is.na(df.spill2$Dist),]$Zip))  #1893 or 1893 * 5
+
+set.seed(234)  #232
+df.spill2 <- df.spill2 %>% 
+  group_by(Zip) %>% 
+  mutate(Dist = ifelse(is.na(Dist), sample(dist.vecs, 1, replace = T), Dist), 
+                                  Att.viz = ifelse(Att == 0, rep(sample(c(2012:2021), 1, replace = T), each = 1), Att)) %>% 
+  mutate(Dist.rounded = as.factor(ceiling(Dist / 10)))
+
+df.spill2 <- df.spill2 %>% 
+  ungroup() %>% 
+  #filter(MarketShare < median(MarketShare, na.rm = TRUE)) %>% 
+  select(`BHCMIS ID`, Tx, D, Att, Att.viz, Dist, Dist.rounded, Year, Zip, Total.Hours, Sites, Perminance, Schedule, Calendar, NumberofPatients) %>%
+  #inner_join(df.qual.exp %>% filter(Year == 2012) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(`BHCMIS ID`, ZipFilter), by = c("BHCMIS ID")) %>% 
+    select(Tx, D, Dist, Year, Zip, `BHCMIS ID`, Att, Att.viz, Dist.rounded, Total.Hours, Sites, Perminance, Schedule, Calendar, NumberofPatients) # %>% filter(ZipFilter == 2)
+
+  i <- 10
+  df.temp <- df.spill2[,c(1:5, i)]
+  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
+  model_feols_clustered <- feols(Outcome ~ Tx*as.numeric(Dist / 10) + D | Year + Zip, cluster = ~ Zip, data = df.temp)
+  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
+  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]
+
+for (i in 11:15){
+  df.temp <- df.spill2[,c(1:5, i)]
+  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
+  model_feols_clustered <- feols(Outcome ~ Tx*as.numeric(Dist / 10) + D | Year + Zip, cluster = ~ Zip, data = df.temp)
+  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
+  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),])
+}
+
+p.spill <- df.spill2 %>% 
+  mutate(Treats = ifelse(Att == 0 & Year >=  Att.viz, 1, Tx)) %>% 
+  filter(Att > 0) %>% 
+  group_by(Dist.rounded, Treats) %>% 
+  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), NumberofPatients = mean(NumberofPatients, na.rm = TRUE), Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
+  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, Total.Hours)) %>% 
+  mutate(Sites = Sites_1 - Sites_0, 
+         NumberofPatients = NumberofPatients_1 - NumberofPatients_0, 
+         Total.Hours = Total.Hours_1 - Total.Hours_0) %>% 
+  left_join(df.spill2 %>% 
+  mutate(Treats = ifelse(Att == 0 & Year >= Att.viz, 1, Tx)) %>% 
+  filter(Att == 0) %>% 
+  group_by(Dist.rounded, Treats) %>% 
+  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), NumberofPatients = mean(NumberofPatients, na.rm = TRUE), Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
+  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, Total.Hours, Total.Hours)) %>% 
+  mutate(Sites.control = Sites_1 - Sites_0, 
+         NumberofPatients.control = NumberofPatients_1 - NumberofPatients_0, 
+         Total.Hours.control = Total.Hours_1 - Total.Hours_0) %>% 
+    select(Dist.rounded, Sites.control:Total.Hours.control), by = c("Dist.rounded")) %>% 
+  mutate( Locations = Sites - Sites.control, 
+         `Patients` = NumberofPatients - NumberofPatients.control, 
+         `Hours per Week` = Total.Hours - Total.Hours.control) %>% 
+  select(Dist.rounded:Counts_1, `Locations`:`Hours per Week`) %>% 
+  mutate(Dist.rounded = as.numeric(paste(Dist.rounded, 0, sep = ""))) %>% 
+  pivot_longer(cols = c( `Locations`:`Hours per Week`)) %>% 
+  mutate(`Treated Zips` = Counts_0 / 3) %>% 
+  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 200) + 
+  xlab("Kilometers to Competitive Zip") + ylab("Unadjusted Difference-in-differences") + theme_tufte_revised() + 
+  geom_smooth(method = "lm", se = F, quiet = TRUE, formula = "y ~ x", mapping = aes(weight = `Treated Zips`)) + 
+  geom_hline(yintercept=0, linetype = "dashed", color = "grey") + theme(text = element_text(size = 16)) + theme(title = element_text(face = "bold")) + 
+  ggtitle("Figure 4 - Unadjusted DID Estimates by Distance to Competitive Zip")
+
+suppressWarnings(print(p.spill))
+
+output <- cbind(TEs %>% 
+  mutate(`95% LB` = Estimate - `Std..Error` * 1.96, 
+         `95% UB` = Estimate + `Std..Error` * 1.96) %>% 
+    select(Estimate,`95% LB`, `95% UB`) ,
+
+TEs_Dist %>% 
+  mutate(`95% LB` = Estimate - `Std..Error` * 1.96, 
+         `95% UB` = Estimate + `Std..Error` * 1.96) %>% 
+    select(Estimate,`95% LB`, `95% UB`)) 
+rownames(output) <- c("Hours Per Week","Locations","Perminance","Weekly Schedule","Calendar Schedule","Total")
+
+round(output[c(6, 2,3, 1, 4, 5),], digits = 3) %>% 
+  kable("html", booktabs = T, col.names = c("DID Estimate", "95% LB", "95% UB", "DID Estimate", "95% LB", "95% UB")) %>%
+  kable_styling(latex_options = c("striped")) %>%
+  pack_rows(index = c("Patient Panel" = 1, "Extensive Margin" = 2, "Intensive Margin" = 3)) %>% 
+  add_header_above(c(" " = 1, "Treatment Effect" = 3, "Treatment Effect * Distance" = 3)) %>% 
+  add_footnote(c("Treatment Effect is the ATT estimated in the zip code where the rival opens their new location","Treatment Effect * Distance is the change in the ATT for every 10km an outlying zip code in the incumbent's service area is from the competitive zip "))
+
+```

### 2023-08-19 code/data_cleaning_longer.Rmd
added in the geographic analysis

@@
 ## Zips
-locs <- paste("/Users/jhm65/Dropbox/Git/UDS/UDS-", c(2014:2021), "-Full-Dataset.xlsx", sep = "")
-uds.zip <- read_excel(locs[1], sheet = "HealthCenterZipCodes")
-
-new.zip.names <- c("BHCMIS ID", "Grant Number", "Reporting Year" , "Zip Code", "Zip Code Type",  "None_Uninsured Patients" ,  "Medicaid_CHIP_Other Public Patients", "Medicare Patients", "Private Patients", "Total Number of Patients" )
-colnames(uds.zip) <-    new.zip.names
+locs <- paste("/Users/jhm65/Dropbox/Git/UDS/UDS-", c(2012:2021), "-Full-Dataset.xlsx", sep = "")
+uds.zip <- read_excel(locs[1], sheet = "HealthCenterZipCodes")[,c(1:4, 6, 5)]
+
+#new.zip.names <- c("BHCMIS ID", "Grant Number", "Reporting Year" , "Zip Code", "Zip Code Type",  "None_Uninsured Patients" ,  "Medicaid_CHIP_Other Public Patients", "Medicare Patients", "Private Patients", "Total Number of Patients" )
+
+new.zip.names <- colnames(uds.zip)
 
 for(i in 2:length(locs)){
-  temp.zip <- read_excel(locs[i], sheet = "HealthCenterZipCodes")
+  temp.zip <- read_excel(locs[i], sheet = "HealthCenterZipCodes")[,c(1:5, 10)]
+
   colnames(temp.zip) <- new.zip.names
-  uds.zip <- rbind(uds.zip, temp.zip %>% mutate(`Zip Code` = str_pad(`Zip Code`, 5, pad = "0")))
-}
-
-# ## Rename
-# new.zip.names <- c("BHCMIS ID", "Grant Number", "Reporting Year" , "Zip Code", "Zip Code Type",  "None_Uninsured Patients" ,  "Medicaid_CHIP_Other Public Patients", "Medicare Patients", "Private Patients", "Total Number of Patients" )
-# colnames(uds.zip) <-    new.zip.names
+  uds.zip <- rbind(uds.zip, temp.zip %>% mutate(ZipCode = str_pad(ZipCode, 5, pad = "0")))
+}
+
+uds.zip$ReportingYear <- as.numeric(uds.zip$ReportingYear)
+uds.zip$NumberofPatients <- as.numeric(uds.zip$NumberofPatients)
+
+uds.zip[is.na(uds.zip$NumberofPatients),]$NumberofPatients <- 0
+
+uds.zip <- uds.zip[uds.zip$ZipCodeType == "ZipCode",]
+
+```
+
+## Bunk old Zip code code
+
+```{r}
+
+# 
+# # ## Rename
+# # new.zip.names <- c("BHCMIS ID", "Grant Number", "Reporting Year" , "Zip Code", "Zip Code Type",  "None_Uninsured Patients" ,  "Medicaid_CHIP_Other Public Patients", "Medicare Patients", "Private Patients", "Total Number of Patients" )
+# # colnames(uds.zip) <-    new.zip.names
+# # 
+# # 
+# # ## Clean
+# # 
+# # uds.zip[uds.zip$`Total Number of Patients`== '-' | uds.zip$`Total Number of Patients`== '--',]$`Total Number of Patients` <- NA
+# # uds.zip$`Total Number of Patients` <- as.numeric(uds.zip$`Total Number of Patients`)
+# # uds.zip <- uds.zip[!is.na(uds.zip$`Total Number of Patients`),] %>% 
+# #     mutate(`Reporting Year` = as.numeric(`Reporting Year`))
+# # 
+# # uds.zip$`None_Uninsured Patients` <- as.numeric(uds.zip$`None_Uninsured Patients`)
+# # uds.zip$`Medicaid_CHIP_Other Public Patients` <- as.numeric(uds.zip$`Medicaid_CHIP_Other Public Patients`)
+# # uds.zip$`Medicare Patients` <- as.numeric(uds.zip$`Medicare Patients`)
+# # uds.zip$`Private Patients` <- as.numeric(uds.zip$`Private Patients`)
+# # 
+# # 
+# # uds.zip <- cbind(uds.zip, broken.total = rowSums(uds.zip[,c(6:9)], na.rm = TRUE), missings = rowSums(is.na(uds.zip[,c(6:9)]))) %>% 
+# #   mutate(`Total Number of Patients` = as.numeric(`Total Number of Patients`)) %>% 
+# #   mutate(`Total Number of Patients` = ifelse(is.na(`Total Number of Patients`), round(missings*16/4), `Total Number of Patients`)) %>% 
+# #   mutate(`None_Uninsured Patients` = ifelse(is.na(`None_Uninsured Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `None_Uninsured Patients`), 
+# #          `Medicaid_CHIP_Other Public Patients` = ifelse(is.na(`Medicaid_CHIP_Other Public Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Medicaid_CHIP_Other Public Patients`),
+# #          `Medicare Patients` = ifelse(is.na(`Medicare Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Medicare Patients`), 
+# #          `Private Patients` = ifelse(is.na(`Private Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Private Patients`))
 # 
 # 
-# ## Clean
-# 
-# uds.zip[uds.zip$`Total Number of Patients`== '-' | uds.zip$`Total Number of Patients`== '--',]$`Total Number of Patients` <- NA
+# uds.zip$`Reporting Year` <- as.numeric(uds.zip$`Reporting Year`)
 # uds.zip$`Total Number of Patients` <- as.numeric(uds.zip$`Total Number of Patients`)
-# uds.zip <- uds.zip[!is.na(uds.zip$`Total Number of Patients`),] %>% 
-#     mutate(`Reporting Year` = as.numeric(`Reporting Year`))
-# 
 # uds.zip$`None_Uninsured Patients` <- as.numeric(uds.zip$`None_Uninsured Patients`)
@@
 # 
-# uds.zip <- cbind(uds.zip, broken.total = rowSums(uds.zip[,c(6:9)], na.rm = TRUE), missings = rowSums(is.na(uds.zip[,c(6:9)]))) %>% 
-#   mutate(`Total Number of Patients` = as.numeric(`Total Number of Patients`)) %>% 
-#   mutate(`Total Number of Patients` = ifelse(is.na(`Total Number of Patients`), round(missings*16/4), `Total Number of Patients`)) %>% 
-#   mutate(`None_Uninsured Patients` = ifelse(is.na(`None_Uninsured Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `None_Uninsured Patients`), 
-#          `Medicaid_CHIP_Other Public Patients` = ifelse(is.na(`Medicaid_CHIP_Other Public Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Medicaid_CHIP_Other Public Patients`),
-#          `Medicare Patients` = ifelse(is.na(`Medicare Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Medicare Patients`), 
-#          `Private Patients` = ifelse(is.na(`Private Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Private Patients`))
-
-uds.zip$`Reporting Year` <- as.numeric(uds.zip$`Reporting Year`)
-uds.zip$`Total Number of Patients` <- as.numeric(uds.zip$`Total Number of Patients`)
-uds.zip$`None_Uninsured Patients` <- as.numeric(uds.zip$`None_Uninsured Patients`)
-uds.zip$`Medicaid_CHIP_Other Public Patients` <- as.numeric(uds.zip$`Medicaid_CHIP_Other Public Patients`)
-uds.zip$`Medicare Patients` <- as.numeric(uds.zip$`Medicare Patients`)
-uds.zip$`Private Patients` <- as.numeric(uds.zip$`Private Patients`)
-
-uds.zip[is.na(uds.zip$`Total Number of Patients`),]$`Total Number of Patients` <- 0
-uds.zip[grep("-", uds.zip$`None_Uninsured Patients`),]$`None_Uninsured Patients` <- 0
-uds.zip[grep("-", uds.zip$`Medicaid_CHIP_Other Public Patients`),]$`Medicaid_CHIP_Other Public Patients` <- 0
-uds.zip[grep("-", uds.zip$`Medicare Patients`),]$`Medicare Patients` <- 0
-uds.zip[grep("-", uds.zip$`Private Patients`),]$`Private Patients` <- 0
-
-uds.zip.totals <- uds.zip %>%
-  select(`Grant Number`, `Reporting Year`, `None_Uninsured Patients`:`Total Number of Patients`) %>%
-  group_by(`Grant Number`, `Reporting Year`) %>% summarise(None = sum(`None_Uninsured Patients`, na.rm = T),
-                                                           MCR = sum(`Medicare Patients`, na.rm = T),
-                                                           COM = sum(`Private Patients`, na.rm = T),
-                                                           MCD = sum(`Medicaid_CHIP_Other Public Patients`, na.rm = T),
-                                                           Total = sum(`Total Number of Patients`, na.rm = T))
-
-uds.zip <- uds.zip[uds.zip$`Zip Code Type` == "ZipCode",]
+# uds.zip[is.na(uds.zip$`Total Number of Patients`),]$`Total Number of Patients` <- 0
+# uds.zip[grep("-", uds.zip$`None_Uninsured Patients`),]$`None_Uninsured Patients` <- 0
+# uds.zip[grep("-", uds.zip$`Medicaid_CHIP_Other Public Patients`),]$`Medicaid_CHIP_Other Public Patients` <- 0
+# uds.zip[grep("-", uds.zip$`Medicare Patients`),]$`Medicare Patients` <- 0
+# uds.zip[grep("-", uds.zip$`Private Patients`),]$`Private Patients` <- 0
+# 
+# uds.zip.totals <- uds.zip %>%
+#   select(`Grant Number`, `Reporting Year`, `None_Uninsured Patients`:`Total Number of Patients`) %>%
+#   group_by(`Grant Number`, `Reporting Year`) %>% summarise(None = sum(`None_Uninsured Patients`, na.rm = T),
+#                                                            MCR = sum(`Medicare Patients`, na.rm = T),
+#                                                            COM = sum(`Private Patients`, na.rm = T),
+#                                                            MCD = sum(`Medicaid_CHIP_Other Public Patients`, na.rm = T),
+#                                                            Total = sum(`Total Number of Patients`, na.rm = T))
+# 
+# uds.zip <- uds.zip[uds.zip$`Zip Code Type` == "ZipCode",]
+
+```
+
+```{r}
 
@@
   arrange(`Total Weekly Hours Of Operation`, `Operational Schedule` )
+```
+
+## Read in census data for all zip codes
+```{r}
+library(tidycensus)
+
+census <- data.frame(ZipCode = 0, NAME = 0, YEAR = 0, 
+                     TotalPop = 0,
+                     Male = 0, Female = 0, 
+                     AgeUnder18 = 0, Age18to64 = 0, Age65andOver = 0, 
+                     White = 0, Black = 0, AIAN = 0, Asian = 0, MR = 0, Hispanic = 0, EducLow = 0, EducMid = 0, EducHigh = 0, 
+                     PovertyStatusDet = 0, IncomeBelowPoverty = 0, Unemployed = 0, Unemp_denom = 0, 
+                     MCD.denom = 0, Medicaid = 0, Unins.denom = 0, Uninsured = 0)
+
+for (i in 1:10){
+  census <- rbind(census, get_acs(geography = "zcta", survey = "acs5",
+                       variables = c("B01003_001","B17001_001","B17001_002","B01001_002","B01001_026",
+                                     "B02001_002","B02001_003","B02001_004","B02001_005","B02001_006","B02001_008",
+                                     "B03001_003", 
+                                     "B01001_003","B01001_004","B01001_005","B01001_006","B01001_007","B01001_008","B01001_009",
+                                     "B01001_010","B01001_011","B01001_013","B01001_014","B01001_015","B01001_016","B01001_017",
+                                     "B01001_018","B01001_019","B01001_020","B01001_021","B01001_022","B01001_023","B01001_024","B01001_025",
+                                     "B01001_027","B01001_028","B01001_029","B01001_030","B01001_031","B01001_032","B01001_033","B01001_034",
+                                     "B01001_035","B01001_036","B01001_037","B01001_038","B01001_039","B01001_040","B01001_041","B01001_042","B01001_043",
+                                     "B01001_044","B01001_045","B01001_046","B01001_047","B01001_048","B01001_049",
+                                     "B06009_002","B06009_003", "B06009_004","B06009_005","B06009_006",
+                                     "B23025_002","B23025_005",
+                                     "C27007_001", "C27007_004", "C27007_007", "C27007_010", "C27007_014", "C27007_017", "C27007_020",
+                                     "B18135_001","B18135_007","B18135_012","B18135_018","B18135_023","B18135_029","B18135_034"), 
+                       year = 2011 + i) %>% 
+  pivot_wider(id_cols = c(GEOID, NAME), names_from = variable, values_from = estimate) %>% 
+    mutate(YEAR = 2009 + i, TotalPop = B01003_001, PovertyStatusDet = B17001_001, IncomeBelowPoverty = B17001_002,
+           AgeUnder18 = B01001_003 + B01001_004 + B01001_005 + B01001_006 + B01001_027 + B01001_028 + B01001_029 + B01001_030,
+           Age18to64 = B01001_007 + B01001_008 + B01001_009 + B01001_010 + B01001_011 + B01001_013 + B01001_014 + B01001_015 + 
+                       B01001_016 + B01001_017 + B01001_018 + B01001_019 + B01001_031 + B01001_032 + B01001_033 + B01001_034 +
+                       B01001_035 + B01001_036 + B01001_037 + B01001_038 + B01001_039 + B01001_040 + B01001_041 + B01001_042 + B01001_043, 
+           Age65andOver = B01001_020 + B01001_021 + B01001_022 + B01001_023 + B01001_024 + B01001_025 + 
+                          B01001_044 + B01001_045 + B01001_046 + B01001_047 + B01001_048 + B01001_049, 
+           Male = B01001_002, Female = B01001_026, 
+           White = B02001_002, Black = B02001_003, AIAN = B02001_004, Asian = B02001_005 + B02001_006, MR = B02001_008, 
+           Hispanic = B03001_003, 
+           EducLow = B06009_002, EducMid = B06009_003 + B06009_004, EducHigh = B06009_005 + B06009_006,
+           Unemployed = B23025_005, Unemp_denom = B23025_002,
+           MCD.denom = C27007_001	, Medicaid = C27007_004	 + C27007_007 + C27007_010	+ C27007_014 + C27007_017 + C27007_020,
+           Unins.denom = B18135_001, Uninsured = B18135_007 + B18135_012 + B18135_018 + B18135_023 + B18135_029 + B18135_034) %>% 
+    select(ZipCode = GEOID, NAME, YEAR, TotalPop:Uninsured))
+
+  print(i)
+}
+census <- census[-1,]
+
+##########
+census$ZipCode <- substr(census$NAME, 7, 11)
+#census$ZipCode <- str_pad(census$ZipCode, 5, pad = "0")
+
+census %>% 
+  filter(YEAR == 2020) %>% 
+  select(ZipCode) %>% 
+  #unique() %>% 
+  table() %>% 
+  table()
 ```
@@
         mutate(Expandor = ifelse(is.na(YearFirstInZip) | Att != YearFirstInZip, 0, 1)) %>%  #  is.na(YearFirstInZip) | Att != YearFirstInZip
-        group_by(`BHCMIS ID`) %>% summarise(Expandor = max(Expandor)), by = c("BHCMIS ID")) %>% filter(Expandor == 0)
-
-dfc <- comp.initial %>% 
+        group_by(`BHCMIS ID`) %>% summarise(Expandor = max(Expandor)), by = c("BHCMIS ID"))
+
+dfc <- comp.initial %>% filter(Expandor == 0) %>% 
   left_join(df.comp, by = c("BHCMIS ID" = "BHCMISID", "Year"))

### 2023-08-20 code/analysis_Redo.Rmd
updated code, moving toward figures

@@
 
-## NumberofPatients and Total.Hours are the best cases, controlling for Sites
-```{r}
-
- i <- 10
-  df.temp <- df.spill2[,c(1:5, 11, i)]
-  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
-  model_feols_clustered <- did2s(
-      data = df.temp, 
-      yname = "Outcome", 
-      treatment = "Tx",
-        first_stage = ~ Sites | Zip + Year , 
-        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
-        cluster_var = "Zip",
-      verbose = FALSE
-    )
-  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
-  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]
-
-for (i in 12:15){
-  df.temp <- df.spill2[,c(1:5, 11, i)]
-  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
-  model_feols_clustered <- did2s(
-      data = df.temp, 
-      yname = "Outcome", 
-      treatment = "Tx",
-        first_stage = ~ Sites | Zip + Year , 
-        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
-        cluster_var = "Zip",
-      verbose = FALSE
-    )
-  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
-  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),])
-}
-
-  cbind(Outcome = c("Hours Per Week","Perminance","Weekly Schedule","Calendar Schedule","Total"),   TEs, TEs_Dist)
-```
-
 ```{r}
@@
   mutate(`Treated Zips` = Counts_0 / 3) %>% 
-  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 200) + 
+  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 250) + 
   xlab("Kilometers to Competitive Zip") + ylab("Unadjusted Difference-in-differences") + theme_tufte_revised() + 
@@
 ```
+
+## NumberofPatients and Total.Hours are the best cases, controlling for Sites
+```{r}
+
+ i <- 10
+  df.temp <- df.spill2[,c(1:5, 11, i)]
+  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
+  model_feols_clustered <- did2s(
+      data = df.temp, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Sites | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
+  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]
+
+for (i in 12:15){
+  df.temp <- df.spill2[,c(1:5, 11, i)]
+  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
+  model_feols_clustered <- did2s(
+      data = df.temp, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Sites | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
+  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),])
+}
+
+  cbind(Outcome = c("Hours Per Week","Perminance","Weekly Schedule","Calendar Schedule","Total"),   TEs, TEs_Dist)
+```

### 2023-08-21 code/analysis_Redo.Rmd
adding payor to TE*Dist estimates

@@
   select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
-         Total,Qcomp, Altman, #MCD:COM, 
+         Total,Qcomp, Altman, Sites, #MCD:COM, 
          #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
@@
 
-for (j in 10:12){
+for (j in 10:13){
 
@@
       treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year, 
+        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
         second_stage = ~ i(Tx, ref = FALSE),
         cluster_var = "ID",
-      verbose = FALSE
+      verbose = TRUE
     )
-
   did.core <- rbind(did.core, outcomes$coeftable)
-
 }
@@
   group_by(Post, Treated) %>% 
-  select(Total:Altman) %>% 
+  select(Total:Sites) %>% 
   summarise_all(mean.nas) %>% 
@@
   #           Finances = mean(Altman, na.rm = TRUE)) %>% 
-  pivot_longer(cols = Total:Altman) %>% 
+  pivot_longer(cols = Total:Sites) %>% 
   mutate(value = round(value, 2)) %>% 
@@
 #splits <- quantile(dfc[dfc$Year == 2011,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_expense, c(0.5), na.rm = TRUE)
-splits <- quantile(dfc[dfc$year.rel == -1,]$ngla_net_gain_loss / dfc[dfc$year.rel == -1,]$ngla_expense, c(0.5), na.rm = TRUE)
+splits <- quantile(dfc[dfc$year.rel == -1,]$ngla_net_gain_loss / dfc[dfc$year.rel == -1,]$ngla_expense, c(0.25, 0.5, 0.75), na.rm = TRUE)
+
+splits <- c(mean(dfc[dfc$year.rel == -1,]$ngla_net_gain_loss / dfc[dfc$year.rel == -1,]$ngla_expense, na.rm = TRUE))
 
@@
 
+splits <- mean.nas(dfc[dfc$year.rel == -1,]$Total)
+
 df.size <- dfc %>% 
@@
   ggtitle("DID Estimates by Baseline Size")
+
+```
+
+## Effects startified by liquidity
+```{r}
+
+#splits <- quantile(dfc[dfc$Year == 2011,]$Total, c(0.5), na.rm = TRUE)
+splits <- quantile(dfc[dfc$year.rel == -1,]$quick_ratio, c(0.5), na.rm = TRUE)
+
+splits <- mean.nas(dfc[dfc$year.rel == -1,]$quick_ratio)
+
+df.liquid <- dfc %>% 
+  mutate(MCD = Total * Pct.MCD / 100, 
+         None = Total * Pct.None / 100, 
+         MCR = Total * Pct.MCR / 100, 
+         COM = Total * Pct.COM / 100,
+
+         crc.rate = crc.rate * 100, 
+         pap.rate = pap.rate * 100, 
+         childbmi.rate = childbmi.rate * 100, 
+         adultbmi.rate = adultbmi.rate * 100, 
+         htn.rate = htn.rate * 100, 
+         dm.rate = dm.rate * 100) %>% 
+  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
+         Total, Qcomp, Altman, Pct.NHA:Pct.COM) %>%  
+  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman)) %>% 
+  ungroup()#, #pap.rate:dm.total, Liquidity:Altman)
+
+df.liquid <- df.liquid %>% 
+  left_join(dfc %>% filter(Year == 2010) %>% select(ID, quick_ratio) %>% 
+  mutate(liquid = quick_ratio) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))
+
+splits1 <- c(min(df.liquid$liquid, na.rm = TRUE)-1, splits)
+splits2 <- c(splits, max(df.liquid$liquid, na.rm = TRUE))
+
+did.liquid <- c(0, 0, 0, 0)
+for (g in 1:(length(splits) + 1)){
+  for (j in 10:12){
+
+  df.temp <- df.liquid[,c(1:9, j, 13:ncol(df.liquid))] 
+  colnames(df.temp)[10] <- "Outcome"
+  outcomes <- did2s(
+      data = df.temp %>% filter(liquid > splits1[g] & liquid <= splits2[g]), 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = FALSE
+    )
+
+  did.liquid <- rbind(did.liquid, outcomes$coeftable)
+
+}}
+
+did.liquid <- did.liquid[-1,]
+rownames(did.liquid) <- NULL
+
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+
+data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
+      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
+      Estimate = as.numeric(did.liquid[,1]), 
+      SD = as.numeric(did.liquid[,2])) %>% 
+  mutate(Subset.f = as.factor(Subset)) %>% 
+  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
+  geom_point() + 
+  xlab("Staggered 2-way DID Estimates") + 
+ylab(NULL) + 
+#adds the CIs
+geom_errorbarh(height=.1) +
+
+#sets the scales
+#note that I reverse the y axis to correctly order the effect #liquids based on my index variable
+#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
+#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
+
+#adding a vertical line at the effect = 0 mark
+geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
+
+#faceting based on my subgroups
+  #facet_wrap(~X1) +
+facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
+      theme_tufte_revised()+
+   theme(strip.placement = "outside") +
+#theme(text=element_text(family="Times",liquid=12, color="black"))+
+theme(panel.spacing = unit(1, "lines")) + 
+  ggtitle("DID Estimates by Baseline Liquidity")
 
@@
 #splits <- quantile(dfc[dfc$Year == 2011,]$Total, c(0.5), na.rm = TRUE)
-splits <- quantile(df.dist[df.dist$year.rel == -1,]$Dist.random, c(0.5), na.rm = TRUE)
+splits <- quantile(df.dist[df.dist$year.rel == -1,]$Dist.random, c(0.33, 0.66), na.rm = TRUE)
 
@@
   #filter(MarketShare < median(MarketShare, na.rm = TRUE)) %>% 
-  select(`BHCMIS ID`, Tx, D, Att, Att.viz, Dist, Dist.rounded, Year, Zip, Total.Hours, Sites, Perminance, Schedule, Calendar, NumberofPatients) %>%
+  select(`BHCMIS ID`, Tx, D, Att, Att.viz, Dist, Dist.rounded, Year, Zip, Total.Hours, Sites, Perminance, Schedule, Calendar, NumberofPatients:Private) %>%
   #inner_join(df.qual.exp %>% filter(Year == 2012) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(`BHCMIS ID`, ZipFilter), by = c("BHCMIS ID")) %>% 
-    select(Tx, D, Dist, Year, Zip, `BHCMIS ID`, Att, Att.viz, Dist.rounded, Total.Hours, Sites, Perminance, Schedule, Calendar, NumberofPatients) # %>% filter(ZipFilter == 2)
-
-  i <- 10
-  df.temp <- df.spill2[,c(1:5, i)]
-  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
-  model_feols_clustered <- feols(Outcome ~ Tx*as.numeric(Dist / 10) + D | Year + Zip, cluster = ~ Zip, data = df.temp)
-  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
-  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]
-
-for (i in 11:15){
-  df.temp <- df.spill2[,c(1:5, i)]
-  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
-  model_feols_clustered <- feols(Outcome ~ Tx*as.numeric(Dist / 10) + D | Year + Zip, cluster = ~ Zip, data = df.temp)
-  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
-  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),])
-}
+    select(Tx, D, Dist, Year, Zip, `BHCMIS ID`, Att, Att.viz, Dist.rounded, Total.Hours, Sites, Perminance, Schedule, Calendar, NumberofPatients:Private) # %>% filter(ZipFilter == 2)
 
@@
   group_by(Dist.rounded, Treats) %>% 
-  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), NumberofPatients = mean(NumberofPatients, na.rm = TRUE), Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
-  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, Total.Hours)) %>% 
+  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), 
+            NumberofPatients = mean(NumberofPatients, na.rm = TRUE), 
+            NumberofPatients_Medicaid = mean(Medicaid, na.rm = TRUE), 
+            Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
+  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, NumberofPatients_Medicaid, Total.Hours)) %>% 
   mutate(Sites = Sites_1 - Sites_0, 
          NumberofPatients = NumberofPatients_1 - NumberofPatients_0, 
+         NumberofPatients_Medicaid = NumberofPatients_Medicaid_1 - NumberofPatients_Medicaid_0, 
          Total.Hours = Total.Hours_1 - Total.Hours_0) %>% 
@@
   group_by(Dist.rounded, Treats) %>% 
-  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), NumberofPatients = mean(NumberofPatients, na.rm = TRUE), Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
-  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, Total.Hours, Total.Hours)) %>% 
+  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), 
+            NumberofPatients = mean(NumberofPatients, na.rm = TRUE), 
+            NumberofPatients_Medicaid = mean(Medicaid, na.rm = TRUE), 
+            Total.Hours = mean(Total.Hours, na.rm = TRUE))%>% 
+  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, NumberofPatients_Medicaid, Total.Hours)) %>% 
   mutate(Sites.control = Sites_1 - Sites_0, 
          NumberofPatients.control = NumberofPatients_1 - NumberofPatients_0, 
+         NumberofPatients_Medicaid.control = NumberofPatients_Medicaid_1 - NumberofPatients_Medicaid_0, 
          Total.Hours.control = Total.Hours_1 - Total.Hours_0) %>% 
@@
          `Patients` = NumberofPatients - NumberofPatients.control, 
+         `Patients - Medicaid` = NumberofPatients_Medicaid - NumberofPatients_Medicaid.control, 
          `Hours per Week` = Total.Hours - Total.Hours.control) %>% 
@@
 
-output <- cbind(TEs %>% 
-  mutate(`95% LB` = Estimate - `Std..Error` * 1.96, 
-         `95% UB` = Estimate + `Std..Error` * 1.96) %>% 
-    select(Estimate,`95% LB`, `95% UB`) ,
-
-TEs_Dist %>% 
-  mutate(`95% LB` = Estimate - `Std..Error` * 1.96, 
-         `95% UB` = Estimate + `Std..Error` * 1.96) %>% 
-    select(Estimate,`95% LB`, `95% UB`)) 
-rownames(output) <- c("Hours Per Week","Locations","Perminance","Weekly Schedule","Calendar Schedule","Total")
-
-round(output[c(6, 2,3, 1, 4, 5),], digits = 3) %>% 
-  kable("html", booktabs = T, col.names = c("DID Estimate", "95% LB", "95% UB", "DID Estimate", "95% LB", "95% UB")) %>%
-  kable_styling(latex_options = c("striped")) %>%
-  pack_rows(index = c("Patient Panel" = 1, "Extensive Margin" = 2, "Intensive Margin" = 3)) %>% 
-  add_header_above(c(" " = 1, "Treatment Effect" = 3, "Treatment Effect * Distance" = 3)) %>% 
-  add_footnote(c("Treatment Effect is the ATT estimated in the zip code where the rival opens their new location","Treatment Effect * Distance is the change in the ATT for every 10km an outlying zip code in the incumbent's service area is from the competitive zip "))
-
 ```
@@
 ```{r}
+df.spill3 <- df.spill2 %>% 
+  left_join(census %>% select(ZipCode, YEAR, IncomeBelowPoverty, PovertyStatusDet), by = c("Year" = "YEAR", "Zip" = "ZipCode"))#%>% 
+  # mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet, 
+  #        Unemployed = Unemployed / Unemp_denom, 
+  #        Elderly = Age65andOver / TotalPop, 
+  #        Black = Black / TotalPop, 
+  #        Hispanic = Hispanic / TotalPop)
 
  i <- 10
-  df.temp <- df.spill2[,c(1:5, 11, i)]
-  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
+  df.temp <- df.spill3[,c(1:5, 11, i, 16:ncol(df.spill3))]
+  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
   model_feols_clustered <- did2s(
@@
 
-for (i in 12:15){
-  df.temp <- df.spill2[,c(1:5, 11, i)]
-  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
+for (i in 12:19){
+  df.temp <- df.spill3[,c(1:5, 11, i, 16:ncol(df.spill3))]
+  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
   model_feols_clustered <- did2s(
@@
         first_stage = ~ Sites | Zip + Year , 
-        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
+        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),
         cluster_var = "Zip",
@@
   TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
-  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),])
+  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[3,])
 }
 
-  cbind(Outcome = c("Hours Per Week","Perminance","Weekly Schedule","Calendar Schedule","Total"),   TEs, TEs_Dist)
+did.access.figures <- df.spill3 %>% 
+    mutate(Post = ifelse(Att.viz >= Year, 1, 0), 
+         Treated = ifelse(Att > 0, 1, 0)) %>% 
+  group_by(Post, Treated) %>% 
+  select(Total.Hours, Perminance:Private) %>% 
+  summarise_all(mean.nas) %>% 
+  # summarise(Total = mean(Total, na.rm = TRUE), 
+  #           Quality = mean(Qcomp, na.rm = TRUE), 
+  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
+  pivot_longer(cols = Total.Hours:Private) %>% 
+  mutate(value = round(value, 2)) %>% 
+  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
+  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
+  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
+  cbind(Outcome = c("Hours Per Week","Perminance","Weekly Schedule","Calendar Schedule","Total","Uninsured","Medicaid","Medicare","Private")) %>% 
+  select(Outcome, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted) %>% 
+  cbind(TEs %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`)) %>%
+  cbind(TEs_Dist %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`))
+
+did.access.figures <- did.access.figures[c(5:9, 1, 3, 2, 4),]
+rownames(did.access.figures) <- NULL
+
+ did.access.figures %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","Estimate","95% CI")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  pack_rows(index = c("Patients" = 5, "Intensive Margin" = 2, "Extensive Margin" = 2)) %>% 
+  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "TE" = 2,"TE * Distance" = 2))
+
 ```

### 2023-08-21 code/data_cleaning_longer.Rmd
updated code, moving toward figures
adding payor to TE*Dist estimates

@@
 library(did2s)
+library(tidycensus)
 
@@
 
+uds.zip <- cbind(uds.zip, "Uninsured" = NA ,  "Medicaid" = NA, "Medicare" = NA, "Private" = NA)
+
 new.zip.names <- colnames(uds.zip)
@@
 for(i in 2:length(locs)){
-  temp.zip <- read_excel(locs[i], sheet = "HealthCenterZipCodes")[,c(1:5, 10)]
-
-  colnames(temp.zip) <- new.zip.names
+  temp.zip <- read_excel(locs[i], sheet = "HealthCenterZipCodes") #[,c(1:5, 10)]
+
+  colnames(temp.zip) <- new.zip.names[c(1:5, 7:10, 6)]
   uds.zip <- rbind(uds.zip, temp.zip %>% mutate(ZipCode = str_pad(ZipCode, 5, pad = "0")))
@@
 uds.zip$NumberofPatients <- as.numeric(uds.zip$NumberofPatients)
+uds.zip$Uninsured <- as.numeric(uds.zip$Uninsured)
+uds.zip$Medicaid <- as.numeric(uds.zip$Medicaid)
+uds.zip$Medicare <- as.numeric(uds.zip$Medicare)
+uds.zip$Private <- as.numeric(uds.zip$Private)
 
 uds.zip[is.na(uds.zip$NumberofPatients),]$NumberofPatients <- 0
+uds.zip[is.na(uds.zip$Uninsured) & uds.zip$ReportingYear > 2012,]$Uninsured <- 0
+uds.zip[is.na(uds.zip$Medicaid) & uds.zip$ReportingYear > 2012,]$Medicaid <- 0
+uds.zip[is.na(uds.zip$Medicare) & uds.zip$ReportingYear > 2012,]$Medicare <- 0
+uds.zip[is.na(uds.zip$Private) & uds.zip$ReportingYear > 2012,]$Private <- 0
 
 uds.zip <- uds.zip[uds.zip$ZipCodeType == "ZipCode",]
+
+uds.zip
 
@@
 ```{r}
-library(tidycensus)
 
@@
   pivot_wider(id_cols = c(GEOID, NAME), names_from = variable, values_from = estimate) %>% 
-    mutate(YEAR = 2009 + i, TotalPop = B01003_001, PovertyStatusDet = B17001_001, IncomeBelowPoverty = B17001_002,
+    mutate(YEAR = 2011 + i, TotalPop = B01003_001, PovertyStatusDet = B17001_001, IncomeBelowPoverty = B17001_002,
            AgeUnder18 = B01001_003 + B01001_004 + B01001_005 + B01001_006 + B01001_027 + B01001_028 + B01001_029 + B01001_030,
@@
   pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
-  filter(`2010` == 1 & `2011` == 1 ) %>%   
+  filter(`2010` == 1 & `2011` == 1) %>%   
   #filter(`2014` == 1 & `2015` == 1) %>%  
@@
                months_of_cash = as.numeric(months_of_cash),
+               quick_ratio = as.numeric(quick_ratio),
                Liquidity = (Assets - Liabilities) / Assets,

### 2023-08-21 code/analysis_Redo.Rmd
cleaned up grouped analysis

@@
 ```{r}
+
+zipsize2 <- zctas(starts_with = unique(c(df.spill2$Zip)), year = 2010)
+
 df.spill3 <- df.spill2 %>% 
-  left_join(census %>% select(ZipCode, YEAR, IncomeBelowPoverty, PovertyStatusDet), by = c("Year" = "YEAR", "Zip" = "ZipCode"))#%>% 
+  left_join(census %>% select(ZipCode, YEAR, TotalPop, IncomeBelowPoverty, PovertyStatusDet), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
+  left_join(zipsize2 %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
+  mutate(Area.SQmiles = ALAND10 / 2.59e6, 
+         l.popdensity = log(TotalPop / Area.SQmiles))
   # mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet, 
@@
   kable_styling(latex_options = c("striped")) %>%
-  pack_rows(index = c("Patients" = 5, "Intensive Margin" = 2, "Extensive Margin" = 2)) %>% 
+  pack_rows(index = c("Patients" = 5, "Access" = 4)) %>% 
   add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "TE" = 2,"TE * Distance" = 2))

### 2023-08-24 code/analysis_Redo.Rmd
finalize that study sample

@@
 ```{r}
-#dfc <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
+# dfc <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
+# uds.sites.full <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv")
+
 ```
@@
 
+df.core2 <- df.core
+
 did.core <- c(0, 0, 0, 0)
@@
       treatment = "Tx",
-        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
         second_stage = ~ i(Tx, ref = FALSE),
@@
 set.seed(123)
-df.dist <- df.core %>% 
+df.dist <- df.core2 %>% 
   left_join(df.z.dist.plot %>% select(`BHCMIS ID.y`, DistToClosestSite), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 

### 2023-08-24 code/data_cleaning_longer.Rmd
finalize that study sample

@@
   arrange(`Total Weekly Hours Of Operation`, `Operational Schedule` )
+
 ```
@@
   pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
-  filter(`2010` == 1 & `2011` == 1) %>%   
+  filter(`2010` == 1 & `2011` == 1 ) %>%   
   #filter(`2014` == 1 & `2015` == 1) %>%  
@@
   mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
+         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
+           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
                CostPerPat = ngla_expense / Total, 
@@
 ```{r}
-#write_csv(dfc, file = "/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
-
-```
+# write_csv(dfc, file = "/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
+# write.csv(uds.sites.full, file = "/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv")
+```

### 2023-08-25 code/analysis_Redo.Rmd
finalizing contextualizing figures

@@
 library(tidyverse)
-
+library(directlabels)
 ```
@@
   add_p()
+
+```
+
+##  Trends over time
+
+```{r}
+## Plot
+p <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
+  select(`BHCMIS ID`, Zip, Year) %>% 
+  unique() %>% 
+  left_join(clinics.in.zips, by = c("Zip", "Year")) %>%
+  group_by(`BHCMIS ID`, Year) %>%
+  summarise(Clinics = max(Clinics, na.rm = TRUE)) %>%
+  group_by(Year, Clinics) %>% 
+  summarise(Count = n()) %>% 
+  mutate(CompetitorsInArea = factor(ifelse( Clinics < 4, Clinics - 1, "3+"))) %>% 
+  group_by(Year, CompetitorsInArea) %>% 
+  summarise(Count = sum(Count))
+
+plot0 <- p %>% 
+  arrange(CompetitorsInArea) %>% 
+  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
+  geom_point() + geom_line() + theme_tufte_revised() + ggtitle("FQHCs by Number of Rival Clinics") + 
+  geom_dl(label=c(rep("0 Competitors", 25), rep("1 Competitor", 25), rep("2 Competitors", 25), rep("3+ Competitors", 25)), 
+          method = list("last.points", hjust = 1, vjust = c(3, 3.5, 4, -2), cex = 0.75), inherit.aes=T ) + 
+  guides(colour = "none") + ylim(0, 4000)
+
+plot1 <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
+            group_by(Zip, Year) %>% 
+  summarise(Counts = n()) %>% 
+  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
+  ungroup() %>% 
+  group_by(Year, Counts) %>% 
+  summarise(Zips = n()) %>% 
+  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
+  group_by(Counts.f, Year) %>% 
+  summarise(Zips = sum(Zips)) %>% 
+  #filter(Year >= 2010) %>% 
+  ggplot(aes(x = Year, y = Zips, group = Counts.f, color = Counts.f)) + 
+  geom_point() + geom_line() + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
+  geom_dl(label=c(rep("1 Site", 25), rep("2+ Sites", 25)), method = list("last.points", hjust = 1, vjust = -1, cex = 0.75), inherit.aes=T ) + 
+  guides(colour = "none")
+
+p.desc <- ggarrange(plot1, plot0)
+
+annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))
 
@@
   mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
-  cbind(did.core) %>% 
-   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
+  cbind(did.core, NiceName = c("Total","Quality Composite","Altman's Z","Sites")) %>% 
+   select(NiceName, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
   mutate(Estimate = round(Estimate, 2), 
@@
          `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
-  rename(Outcome = name) %>% 
+  rename(Outcome = NiceName) %>% 
   select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
@@
 
-data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
+plot.profit <- data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
       Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
@@
       SD = as.numeric(did.profit[,2])) %>% 
-  mutate(Subset.f = as.factor(Subset)) %>% 
+  #mutate(Subset.f = as.factor(Subset)) %>% 
+  mutate(Subset.f = ifelse(Subset == 2, "Above Average", "Below Average")) %>% 
   ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
@@
 theme(panel.spacing = unit(1, "lines")) + 
+  ylab("Stratified by baseline profitability (% of expenses)") + 
   ggtitle("DID Estimates by Baseline Profitiability")
 
+plot.profit
 ```
@@
       SD = as.numeric(did.size[,2])) %>% 
-  mutate(Subset.f = as.factor(Subset)) %>% 
+  #mutate(Subset.f = as.factor(Subset)) %>% 
+  mutate(Subset.f = ifelse(Subset == 2, "Above Average", "Below Average")) %>% 
   ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
@@
 theme(panel.spacing = unit(1, "lines")) + 
+  ylab("Stratified by baseline clinic population size") + 
   ggtitle("DID Estimates by Baseline Size")
@@
   mutate(`Treated Zips` = Counts_0 / 3) %>% 
-  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 250) + 
+  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 200) + 
   xlab("Kilometers to Competitive Zip") + ylab("Unadjusted Difference-in-differences") + theme_tufte_revised() + 
@@
   geom_hline(yintercept=0, linetype = "dashed", color = "grey") + theme(text = element_text(size = 16)) + theme(title = element_text(face = "bold")) + 
-  ggtitle("Figure 4 - Unadjusted DID Estimates by Distance to Competitive Zip")
+  ggtitle("Unadjusted DID Estimates by Distance to Competitive Zip")
 

### 2023-08-25 code/data_cleaning_longer.Rmd
finalizing contextualizing figures

@@
 clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
-  filter(Year >= included.years[1]) %>% 
+  #filter(Year >= included.years[1]) %>% 
   group_by(Zip, Year) %>%

### 2023-08-28 code/analysis_Redo.Rmd
playing around with the figures and stuff

@@
           method = list("last.points", hjust = 1, vjust = c(3, 3.5, 4, -2), cex = 0.75), inherit.aes=T ) + 
-  guides(colour = "none") + ylim(0, 4000)
+  guides(colour = "none")
 
@@
   geom_dl(label=c(rep("1 Site", 25), rep("2+ Sites", 25)), method = list("last.points", hjust = 1, vjust = -1, cex = 0.75), inherit.aes=T ) + 
-  guides(colour = "none")
+  guides(colour = "none") + ylim(0, 4000)
 
@@
   select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
-         Total,Qcomp, Altman, Sites, #MCD:COM, 
+         Total,Qcomp, Altman, #MCD:COM, 
          #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
@@
 
-for (j in 10:13){
+for (j in 10:12){
 
@@
         second_stage = ~ i(Tx, ref = FALSE),
-        cluster_var = "ID",
+        cluster_var = "STATE",
       verbose = TRUE
@@
   group_by(Post, Treated) %>% 
-  select(Total:Sites) %>% 
+  select(Total:Altman) %>% 
   summarise_all(mean.nas) %>% 
@@
   #           Finances = mean(Altman, na.rm = TRUE)) %>% 
-  pivot_longer(cols = Total:Sites) %>% 
+  pivot_longer(cols = Total:Altman) %>% 
   mutate(value = round(value, 2)) %>% 
-  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
+  filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
   pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
   mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
-  cbind(did.core, NiceName = c("Total","Quality Composite","Altman's Z","Sites")) %>% 
+  cbind(did.core, NiceName = c("Total","Quality Composite","Altman's Z")) %>% 
    select(NiceName, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
@@
       treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
         second_stage = ~ i(Tx, ref = FALSE),
-        cluster_var = "ID",
+        cluster_var = "STATE",
       verbose = FALSE
@@
       treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
         second_stage = ~ i(Tx, ref = FALSE),
-        cluster_var = "ID",
+        cluster_var = "STATE",
       verbose = FALSE
@@
       treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless  | ID + Year , 
         second_stage = ~ i(Tx, ref = FALSE),
-        cluster_var = "ID",
+        cluster_var = "STATE",
       verbose = FALSE
@@
         second_stage = ~ i(Tx, ref = FALSE),
-        cluster_var = "ID",
+        cluster_var = "STATE",
       verbose = FALSE
@@
                    %>% select(ID) %>% unique() , by = c("ID")), 
-  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>%
+  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None) %>%
   filter(abs(term) <= 5) %>% 
@@
 p <- df.z.dist.plot %>% 
+  filter(DistToClosestSite < 200) %>% 
   ggplot(aes(x = log(Density.Origin), y = log(Density.NewZip))) + 
@@
 df.dist <- df.core2 %>% 
-  left_join(df.z.dist.plot %>% select(`BHCMIS ID.y`, DistToClosestSite), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
+  left_join(df.z.dist.plot %>% select(`BHCMIS ID.y`, DistToClosestSite, Density.NewZip), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
   group_by(`BHCMIS ID`) %>% 
-  mutate(Dist.random = sample(size = 1, unique(df.z.dist.plot$DistToClosestSite), replace = TRUE), 
-         Dist.random = ifelse(Att > 0, DistToClosestSite, Dist.random))
+  mutate(Dist.random = sample(size = 1, unique(df.z.dist.plot$DistToClosestSite / df.z.dist.plot$Density.NewZip), replace = TRUE), 
+         Dist.random = ifelse(Att > 0, DistToClosestSite / Density.NewZip, Dist.random))
 
 #splits <- quantile(dfc[dfc$Year == 2011,]$Total, c(0.5), na.rm = TRUE)
-splits <- quantile(df.dist[df.dist$year.rel == -1,]$Dist.random, c(0.33, 0.66), na.rm = TRUE)
+splits <- quantile(df.dist[df.dist$year.rel == -1,]$Dist.random, c(0.5), na.rm = TRUE)
 
@@
 theme(panel.spacing = unit(1, "lines")) + 
-  ggtitle("DID Estimates by Baseline Size")
+  ggtitle("DID Estimates by Distance Traveled")
 ```

### 2023-08-28 code/data_cleaning_longer.Rmd
playing around with the figures and stuff

@@
                months_of_cash = as.numeric(months_of_cash),
+               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
                quick_ratio = as.numeric(quick_ratio),
                Liquidity = (Assets - Liabilities) / Assets,
-               Profitability = ngla_net_gain_loss / Assets, 
-               Efficiency = ngla_revenue / Assets,
-               NetWorth = (Assets - Liabilities) / Liabilities)
+               Profitability = ngla_net_gain_loss / Assets, #Assets, 
+               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
+               NetWorth = (Assets - Liabilities) / Liabilities, 
+            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
+            LiabPctAssets = Liabilities / Assets, 
+            Eff = ngla_prog_serv_revenue / Assets, 
+            LiabPctRev = ngla_prog_serv_revenue / ngla_expense)
 
@@
          NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
-         Altman = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% 
-  mutate(Att.random = ifelse(Att > 0, Att, NA))
+         #Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
+         Altman = 0.18 * quick_ratio + 0.3 * Profitability + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
+  mutate(Att.random = ifelse(Att > 0, Att, NA), 
+         Distress = ifelse(Altman < 2.6, 1, 0))
 

### 2023-08-28 code/data_cleaning_longer.Rmd
looking at TMSIS only sample, really

@@
   pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
-  filter(`2010` == 1 & `2011` == 1  ) %>%   
+  filter(`2010` == 1 & `2011` == 1) %>%  #  & `2012` == 1 & `2013` == 1 & `2014` == 1 & `2015` == 1 & `2016` == 1) %>%   
   #filter(`2014` == 1 & `2015` == 1) %>%  

### 2023-08-29 code/analysis_Redo.Rmd
looking at TMSIS only sample, really
intensity and complexity

@@
 df.core <- dfc %>% 
-  mutate(MCD = Total * Pct.MCD / 100, 
+  mutate( MCD = Total * Pct.MCD / 100,
          None = Total * Pct.None / 100,
@@
 
+## Panel Complexity and Intensity of Care
+```{r}
+
+df.select.stint <- dfc %>% 
+  mutate(MCD = Total * Pct.MCD / 100, 
+         None = Total * Pct.None / 100, 
+         MCR = Total * Pct.MCR / 100, 
+         COM = Total * Pct.COM / 100,
+
+         pap.denom = pap.denom / Total * 100, 
+         crc.denom = crc.denom / Total * 100, 
+         adultbmi.denom = adultbmi.denom / Total * 100, 
+         childbmi.denom = childbmi.denom / Total * 100, 
+         htn.denom = htn.total / Total * 100, 
+         dm.denom = dm.total / Total * 100) %>% 
+  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
+         HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
+         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
+         #Liquidity:NetWorth, 
+         Pct.NHA:Pct.COM) %>% 
+  mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
+         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5)
+
+did.select.stint <- c(0, 0, 0, 0)
+
+for (j in 10:29){
+
+  df.temp <- df.select.stint[,c(1:9, j, 30:ncol(df.select.stint))]
+  colnames(df.temp)[10] <- "Outcome"
+  outcomes <- did2s(
+      data = df.temp  , 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "STATE",
+      verbose = TRUE
+    )
+  did.select.stint <- rbind(did.select.stint, outcomes$coeftable)
+}
+
+did.select.stint <- did.select.stint[-1,]
+rownames(did.select.stint) <- NULL
+
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+
+p <- df.select.stint %>% 
+  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
+         Treated = ifelse(Att > 0, 1, 0)) %>% 
+  group_by(Post, Treated) %>% 
+  select(HIV.prev:dm.denom) %>% 
+  summarise_all(mean.nas) %>% 
+  # summarise(Total = mean(Total, na.rm = TRUE), 
+  #           Quality = mean(Qcomp, na.rm = TRUE), 
+  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
+  pivot_longer(cols = HIV.prev:dm.denom) %>% 
+  mutate(value = round(value, 2)) %>% 
+  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
+  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
+  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
+  cbind(did.select.stint, group =   gsub(x = df.select.stint %>% 
+  select(HIV.prev:dm.denom) %>% 
+  colnames(), pattern = "^[[:alpha:]]+\\.", replacement = "")) %>% 
+  arrange(desc(group)) %>% 
+   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
+  mutate(Estimate = round(Estimate, 2), 
+         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
+         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
+  rename(Outcome = name) %>% 
+  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  pack_rows(index = c("Selection" = 7, "UDS Measure Denom" = 6, "Stinting" = 7)) %>% 
+  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
+
+p
+
+did2s(
+      data = df.select.stint  , 
+      yname = "Complexity", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "STATE",
+      verbose = TRUE
+    )
+
+did2s(
+      data = df.select.stint  , 
+      yname = "Intensity", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "STATE",
+      verbose = TRUE
+    )
+
+```
+
 ## Effects stratified by profitability
@@
 summary(lm(log(Density.Origin) ~ log(Density.NewZip), data = df.z.dist.plot))
+
+df.z.dist.plot %>% 
+  arrange(desc(DistToClosestSite))
 ```

### 2023-08-29 code/data_cleaning_longer.Rmd
intensity and complexity

@@
 df.comp <- df.comp %>% 
-  filter(BHCMISID != "01E00010") %>%  #%>%  filter(STATE != 'CT')
-select(BHCMISID:FIPS, Total:Pct.COM, imm.rate:MinYear)
+  filter(BHCMISID != "01E00010") %>% 
+                mutate(HIV.prev = T6A_L1AND2_CB / Total * 100, 
+         HIV.care = T6A_L1AND2_CA / T6A_L1AND2_CB,
+
+         HepC.prev = T6A_L4B_CB / Total * 100,
+         HepC.care = T6A_L4B_CA / T6A_L4B_CB,
+
+         Asthma.prev = T6A_L5_CB / Total * 100,
+         Asthma.care = T6A_L5_CA / T6A_L5_CB,
+
+         # AbnormalPap.prev = T6A_L8_CB / Total * 100,
+         # AbnormalPap.care = T6A_L8_CA / T6A_L8_CB,
+         #
+         # ImmunizationsGiven.prev = T6A_L24_CB / Total * 100,
+         # ImmunizationsGiven.care = T6A_L24_CA / T6A_L24_CB,
+
+         HeartDisease.prev = T6A_L10_CB / Total * 100, 
+         HeartDisease.care = T6A_L10_CA / T6A_L10_CB,
+
+         # OverweightOrObesity.prev = T6A_L14A_CB / Total * 100, 
+         # OverweightOrObesity.care = T6A_L14A_CA / T6A_L14A_CB,
+
+         Depression.prev = T6A_L19A_CB / Total * 100, 
+         Depression.care = T6A_L19A_CA / T6A_L19A_CB,
+
+         Diabetes.prev = T6A_L9_CB / Total * 100, 
+         Diabetes.care = T6A_L9_CA / T6A_L9_CB,
+
+         Hypertension.prev = T6A_L11_CB / Total * 100, 
+         Hypertension.care = T6A_L11_CA / T6A_L11_CB) %>%  #%>%  filter(STATE != 'CT')
+select(BHCMISID:FIPS, Total:Pct.COM, HIV.prev:Hypertension.care , imm.rate:MinYear)
 

### 2023-08-29 code/analysis_Redo.Rmd
Redefining selection

--- 2023-08-28 code/analysis_Redo.Rmd
@@
 
+## Panel Complexity and Intensity of Care
+```{r}
+
+df.select.stint <- dfc %>% 
+  mutate(MCD = Total * Pct.MCD / 100, 
+         None = Total * Pct.None / 100, 
+         MCR = Total * Pct.MCR / 100, 
+         COM = Total * Pct.COM / 100,
+
+         pap.denom = pap.denom / Total * 100, 
+         crc.denom = crc.denom / Total * 100, 
+         adultbmi.denom = adultbmi.denom / Total * 100, 
+         childbmi.denom = childbmi.denom / Total * 100, 
+         htn.denom = htn.total / Total * 100, 
+         dm.denom = dm.total / Total * 100) %>% 
+  mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
+         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5, 
+         Intensity.w = (HIV.care * HIV.prev + HepC.care * HepC.prev + Asthma.care * Asthma.prev + HeartDisease.care * HeartDisease.prev + Depression.care * Depression.prev + Diabetes.care * Diabetes.prev + Hypertension.care * Hypertension.prev) /
+                  (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev)) %>% 
+  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
+         Complexity, Intensity, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
+         Pct.NHA:Pct.COM)
+
+did.select.stint <- c(0, 0, 0, 0)
+
+for (j in 10:11){
+
+  df.temp <- df.select.stint[,c(1:9, j, 12:ncol(df.select.stint))]
+  colnames(df.temp)[10] <- "Outcome"
+  outcomes <- did2s(
+      data = df.temp  , 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "STATE",
+      verbose = TRUE
+    )
+  did.select.stint <- rbind(did.select.stint, outcomes$coeftable)
+}
+
+did.select.stint <- did.select.stint[-1,]
+rownames(did.select.stint) <- NULL
+
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+
+p <- df.select.stint %>% 
+  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
+         Treated = ifelse(Att > 0, 1, 0)) %>% 
+  group_by(Post, Treated) %>% 
+  select(Complexity:Intensity) %>% 
+  summarise_all(mean.nas) %>% 
+  # summarise(Total = mean(Total, na.rm = TRUE), 
+  #           Quality = mean(Qcomp, na.rm = TRUE), 
+  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
+  pivot_longer(cols = Complexity:Intensity) %>% 
+  mutate(value = round(value, 2)) %>% 
+  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
+  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
+  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
+  cbind(did.select.stint) %>%
+
+  #       , group =   gsub(x = df.select.stint %>% 
+  # select(Complexity:Intensity) %>% 
+  # colnames(), pattern = "^[[:alpha:]]+\\.", replacement = "")) %>% 
+  # arrange(desc(group)) %>% 
+   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
+  mutate(Estimate = round(Estimate, 2), 
+         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
+         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
+  rename(Outcome = name) %>% 
+  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  #pack_rows(index = c("Selection" = 7, "UDS Measure Denom" = 6, "Stinting" = 7)) %>% 
+  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
+
+p
+
+p <- ggarrange(
+  event_study(data = df.select.stint, 
+  yname = "Complexity", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Complexity") , 
+event_study(data = df.select.stint, 
+  yname = "Intensity", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Intensity"), common.legend = TRUE ) 
+p
+
+```
+
 ## Effects stratified by profitability

### 2023-08-29 code/analysis_Redo.Rmd
making event study plots

@@
 
+p0 <- ggarrange(
+  event_study(data = df.core, 
+  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") , 
+event_study(data = df.core, 
+  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite"), 
+event_study(data = df.core, 
+  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience"), common.legend = TRUE ) 
+p0
+
 ```
@@
 
-p <- df.select.stint %>% 
+p1 <- df.select.stint %>% 
   mutate(Post = ifelse(year.rel >= 0, 1, 0), 
@@
 
-p
-
-p <- ggarrange(
+p1
+
+p2 <- ggarrange(
   event_study(data = df.select.stint, 
@@
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Intensity"), common.legend = TRUE ) 
-p
+p2
 

### 2023-08-30 code/analysis_Redo.Rmd
finalizing the figures

@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience"), common.legend = TRUE ) 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience"), common.legend = TRUE, nrow = 1 ) 
 p0

### 2023-08-30 code/analysis_Redo.Rmd
how is the rival affected

@@
          Intensity.w = (HIV.care * HIV.prev + HepC.care * HepC.prev + Asthma.care * Asthma.prev + HeartDisease.care * HeartDisease.prev + Depression.care * Depression.prev + Diabetes.care * Diabetes.prev + Hypertension.care * Hypertension.prev) /
-                  (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev)) %>% 
+                  (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev), 
+         PatientsPerStaff = ngla_prog_serv_revenue / Total, #Total / Staff, 
+         ProgramCostPerPatient = log(ngla_expense / Total)) %>% 
   select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
-         Complexity, Intensity, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
+         Complexity, Intensity, PatientsPerStaff, ProgramCostPerPatient, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
          Pct.NHA:Pct.COM)
@@
 
-for (j in 10:11){
+for (j in 10:12){
 
@@
   group_by(Post, Treated) %>% 
-  select(Complexity:Intensity) %>% 
+  select(Complexity:PatientsPerStaff) %>% 
   summarise_all(mean.nas) %>% 
@@
   #           Finances = mean(Altman, na.rm = TRUE)) %>% 
-  pivot_longer(cols = Complexity:Intensity) %>% 
+  pivot_longer(cols = Complexity:PatientsPerStaff) %>% 
   mutate(value = round(value, 2)) %>% 
@@
 df.spill3 <- df.spill2 %>% 
-  left_join(census %>% select(ZipCode, YEAR, TotalPop, IncomeBelowPoverty, PovertyStatusDet), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
+  left_join(census %>% 
+              mutate(Unins.rate = Uninsured / Unins.denom) %>% 
+              select(ZipCode, YEAR, TotalPop, IncomeBelowPoverty, PovertyStatusDet, Unins.rate), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
   left_join(zipsize2 %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
@@
 
-```
+summary(df.spill3[df.spill3$Att > 0 & df.spill3$Att.viz < df.spill3$Year,]$Unins.rate * df.spill3[df.spill3$Att > 0& df.spill3$Att.viz < df.spill3$Year,]$TotalPop)
+
+```
+
+## Effect of Competition on Rival
+```{r}
+
+df.rival <- dfc %>% 
+    left_join(df.z.dist.plot %>% select(`BHCMIS ID.x`, `BHCMIS ID.y`), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
+    filter(is.na(`BHCMIS ID.x`)) %>% 
+    unique() %>% 
+  bind_rows(dfc %>% 
+    left_join(df.z.dist.plot %>% select(`BHCMIS ID.x`, `BHCMIS ID.y`), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
+    filter(!is.na(`BHCMIS ID.x`)) %>% 
+    unique() %>% 
+    select(`BHCMIS ID.x`, `BHCMIS ID`:Year, Att, ID) %>% 
+    left_join(df.comp%>% 
+  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
+         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
+           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
+               CostPerPat = ngla_expense / Total, 
+               months_of_cash = as.numeric(months_of_cash),
+               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
+               quick_ratio = as.numeric(quick_ratio),
+               Liquidity = (Assets - Liabilities) / Assets,
+               Profitability = ngla_net_gain_loss / Assets, #Assets, 
+               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
+               NetWorth = (Assets - Liabilities) / Liabilities, 
+            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
+            LiabPctAssets = Liabilities / Assets, 
+            Eff = ngla_prog_serv_revenue / Assets, 
+            LiabPctRev = ngla_prog_serv_revenue / ngla_expense) , by = c("BHCMIS ID.x" = "BHCMISID", "Year"))) %>% 
+  mutate(MCD = Total * Pct.MCD / 100, 
+         None = Total * Pct.None / 100, 
+         MCR = Total * Pct.MCR / 100, 
+         COM = Total * Pct.COM / 100) %>% 
+    select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
+         Total,MCD:COM, Pct.MCD, Pct.None, Pct.MCR, Pct.COM, #MCD:COM, 
+         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
+         #Liquidity:NetWorth, 
+         Pct.NHA:Pct.Homeless)
+
+did.rival <- c(0, 0, 0, 0)
+
+for (j in 10:18){
+
+  df.temp <- df.rival[,c(1:9, j, 19:ncol(df.rival))]
+  colnames(df.temp)[10] <- "Outcome"
+  outcomes <- did2s(
+      data = df.temp  , 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "STATE",
+      verbose = TRUE
+    )
+  did.rival <- rbind(did.rival, outcomes$coeftable)
+}
+
+did.rival <- did.rival[-1,]
+rownames(did.rival) <- NULL
+
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+
+df.rival %>% 
+  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
+         Treated = ifelse(Att > 0, 1, 0)) %>% 
+  group_by(Post, Treated) %>% 
+  select(Total:Pct.COM) %>% 
+  summarise_all(mean.nas) %>% 
+  # summarise(Total = mean(Total, na.rm = TRUE), 
+  #           Quality = mean(Qcomp, na.rm = TRUE), 
+  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
+  pivot_longer(cols = Total:Pct.COM) %>% 
+  mutate(value = round(value, 2)) %>% 
+  filter(name %in% c("Total", "MCD","None","MCR","COM","Pct.MCD", "Pct.None","Pct.MCR","Pct.COM")) %>% 
+  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
+  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
+  cbind(did.rival, NiceName = c("Total","Medicaid, total", "Uninsured, total","Medicare, total","Private, total","Medicaid, %", "Uninsured, %","Medicare, %","Private, %")) %>% 
+   select(NiceName, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
+  mutate(Estimate = round(Estimate, 2), 
+         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
+         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
+  rename(Outcome = NiceName) %>% 
+  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  pack_rows(index = c("Total Patients by Insurnace" = 5, "Payor Mix, Proportion" = 4)) %>% 
+  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
+
+event_study(data = df.competitor, 
+  yname = "Pct.None", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients")
+
+```

### 2023-08-31 code/analysis_Redo.Rmd
updating the event studies

@@
 event_study(data = df.competitor, 
-  yname = "Pct.None", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
   filter(abs(term) <= 7) %>% 

### 2023-09-05 code/analysis_Redo.Rmd
playing with the pre-post filters on treatment effect estimates

@@
 df.core <- dfc %>% 
+  #filter(Att %in% c(0, 2016:2021) & Year %in% c(2014:2021)) %>% 
+  #filter(Att %in% c(0, 2012:2015) & Year %in% c(2010:2018)) %>% 
   mutate(MCD = Total * Pct.MCD / 100, 

### 2023-09-05 code/analysis_Redo.Rmd
Early vs later competitive shocks

@@
 p2
+
+```
+
+## Early vs Late competitors (pre-post ACA?)
+
+```{r}
+
+df.ppACA <- df.core2 %>% 
+  mutate(EarlyLate = ifelse(Att == 0, 0, 
+                     ifelse(Att %in% c(2012:2014), 1,# 2))) 
+                     ifelse(Att %in% c(2015:2017), 2, 3))))
+  #filter(Att %in% c(0, 2016:2021) & Year %in% c(2014:2021)) %>% 
+  #filter(Att %in% c(0, 2012:2015) & Year %in% c(2010:2018)) %>%
+
+did.ppACA <- c(0, 0, 0, 0)
+for (i in 1:3){
+for (j in 10:12){
+
+  df.temp <- df.ppACA[,c(1:9, j, 13:ncol(df.ppACA))]
+  colnames(df.temp)[10] <- "Outcome"
+  outcomes <- did2s(
+      data = df.temp %>% filter(EarlyLate %in% c(0, i)) , 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "STATE",
+      verbose = TRUE
+    )
+  did.ppACA <- rbind(did.ppACA, outcomes$coeftable)
+}
+}
+
+did.ppACA <- did.ppACA[-1,]
+rownames(did.ppACA) <- NULL
+
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+
+data.frame(Subset = sort(rep(1:3, 3)),
+      Outcome = rep(c("Total","Quality","Financial"), 3),
+      Estimate = as.numeric(did.ppACA[,1]), 
+      SD = as.numeric(did.ppACA[,2])) %>% 
+  mutate(Subset.f = as.factor(Subset)) %>% 
+  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
+  geom_point() + 
+  xlab("Staggered 2-way DID Estimates") + 
+ylab(NULL) + 
+#adds the CIs
+geom_errorbarh(height=.1) +
+
+#sets the scales
+#note that I reverse the y axis to correctly order the effect #liquids based on my index variable
+#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
+#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
+
+#adding a vertical line at the effect = 0 mark
+geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
+
+#faceting based on my subgroups
+  #facet_wrap(~X1) +
+facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
+      theme_tufte_revised()+
+   theme(strip.placement = "outside") +
+#theme(text=element_text(family="Times",liquid=12, color="black"))+
+theme(panel.spacing = unit(1, "lines")) + 
+  ggtitle("DID Estimates by early vs late adopters")
 

### 2023-09-05 code/analysis_Redo.Rmd
TE by profitability

@@
 
-data.frame(Subset = sort(rep(1:3, 3)),
+data.frame(Subset = sort(rep(c("2012-2014","2015-2017","2018-2021"), 3)),
       Outcome = rep(c("Total","Quality","Financial"), 3),
@@
 theme(panel.spacing = unit(1, "lines")) + 
-  ggtitle("DID Estimates by early vs late adopters")
+  ggtitle("DID Estimates by timeperiod of competitive shocks")
 
@@
 
-#splits <- quantile(dfc[dfc$Year == 2011,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_expense, c(0.5), na.rm = TRUE)
-splits <- quantile(dfc[dfc$year.rel == -1,]$ngla_net_gain_loss / dfc[dfc$year.rel == -1,]$ngla_expense, c(0.25, 0.5, 0.75), na.rm = TRUE)
+#splits <- quantile(dfc[dfc$year.rel == -1,]$ngla_net_gain_loss / dfc[dfc$year.rel == -1,]$ngla_expense, c(0.333, 0.667), na.rm = TRUE)
 
 splits <- c(mean(dfc[dfc$year.rel == -1,]$ngla_net_gain_loss / dfc[dfc$year.rel == -1,]$ngla_expense, na.rm = TRUE))
+
+splits <- c(-0.03, 0.1)
 
@@
       SD = as.numeric(did.profit[,2])) %>% 
-  #mutate(Subset.f = as.factor(Subset)) %>% 
-  mutate(Subset.f = ifelse(Subset == 2, "Above Average", "Below Average")) %>% 
+  mutate(Subset.f = as.factor(Subset)) %>% 
+  #mutate(Subset.f = ifelse(Subset == 2, "Above Average", "Below Average")) %>% 
   ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
@@
 plot.profit
+
+did2s(
+      data = df.profit %>% filter(!is.na(pc)) %>% mutate(pc = pc * 10 ), 
+      yname = "Qcomp", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2),
+        cluster_var = "STATE",
+      verbose = FALSE
+    )
 ```

### 2023-09-09 code/analysis_Redo.Rmd
ATT by mediators

@@
 
-splits <- c(-0.03, 0.1)
+#splits <- c(-0.03, 0.1)
 
@@
         first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
-        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2),
+        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2) ,
         cluster_var = "STATE",

### 2023-09-09 code/analysis_Redo.Rmd
moving around heterogeneity analysis

@@
 plot.profit
-
-did2s(
-      data = df.profit %>% filter(!is.na(pc)) %>% mutate(pc = pc * 10 ), 
-      yname = "Qcomp", 
-      treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
-        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2) ,
-        cluster_var = "STATE",
-      verbose = FALSE
-    )
 ```
@@
   ggtitle("DID Estimates by Baseline Size")
+
+```
+
+## Stratified effects in linearized fashion
+```{r}
+
+did2s(
+      data = df.profit %>% mutate(pc = ngla_net_gain_loss / ngla_expense * 10) %>% filter(!is.na(pc)) , 
+      yname = "Qcomp", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2) ,
+        cluster_var = "STATE",
+      verbose = FALSE
+    )
+
+did2s(
+      data = df.size  %>% mutate(Size = Size / 1000 ), 
+      yname = "Qcomp", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * Size) + I(Tx * Size^2) ,
+        cluster_var = "STATE",
+      verbose = FALSE
+    )
 

### 2023-09-09 code/analysis_Redo.Rmd
more adjustments

@@
 df.size <- df.size %>% 
-  left_join(dfc %>% filter(Year == 2010) %>% select(ID, Total) %>% 
+  left_join(dfc %>% filter(year.rel == -1) %>% select(ID, Total) %>% 
   mutate(Size = Total) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))
@@
 
-## Stratified effects in linearized fashion
-```{r}
-
-did2s(
-      data = df.profit %>% mutate(pc = ngla_net_gain_loss / ngla_expense * 10) %>% filter(!is.na(pc)) , 
-      yname = "Qcomp", 
-      treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
-        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2) ,
-        cluster_var = "STATE",
-      verbose = FALSE
-    )
-
-did2s(
-      data = df.size  %>% mutate(Size = Size / 1000 ), 
-      yname = "Qcomp", 
-      treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
-        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * Size) + I(Tx * Size^2) ,
-        cluster_var = "STATE",
-      verbose = FALSE
-    )
-
-```
-
 ## Effects startified by liquidity
@@
 df.liquid <- df.liquid %>% 
-  left_join(dfc %>% filter(Year == 2010) %>% select(ID, quick_ratio) %>% 
+  left_join(dfc %>% filter(year.rel == -1) %>% select(ID, quick_ratio) %>% 
   mutate(liquid = quick_ratio) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))
@@
 
+```
+
+## Stratified effects in linearized fashion
+```{r}
+
+did2s(
+      data = df.profit %>% mutate(pc = ngla_net_gain_loss / ngla_expense * 10) %>% filter(!is.na(pc)) , 
+      yname = "Qcomp", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2) ,
+        cluster_var = "STATE",
+      verbose = FALSE
+    )
+
+did2s(
+      data = df.size  %>% mutate(Size = Size / 1000 ), 
+      yname = "Qcomp", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * Size) + I(Tx * Size^2) ,
+        cluster_var = "STATE",
+      verbose = FALSE
+    )
+
+did2s(
+      data = df.liquid %>% filter(!is.na(liquid)) , 
+      yname = "Qcomp", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * liquid) + I(Tx * liquid^2) ,
+        cluster_var = "STATE",
+      verbose = FALSE
+    )
 ```

### 2023-09-11 code/analysis_Redo.Rmd
adding analysis of where rival places site

@@
 ```
+
+## Visualizing where the rival places there clinic
+```{r}
+df.places <- df.z.dist %>% 
+  select(Zip:`BHCMIS ID.y`) %>% 
+  pivot_longer(`BHCMIS ID.x`:`BHCMIS ID.y`) %>% 
+  mutate(ClinicType = ifelse(name == "BHCMIS ID.y", "Incumbent", "Rival")) %>% 
+  select(Zip, Year, Att.z, Total.z, ClinicType, value) %>% 
+  left_join(zip.centroids, by = c("Zip" = "ZipCode")) %>% 
+  left_join(uds.sites.full %>% filter(Year >= 2010) , by = c("value" = "BHCMIS ID","Zip"))
+
+places.geo <- geo(street = df.places$`Site Street Address`, 
+             city = df.places$`Site City`, 
+             state = df.places$`Site State`, 
+             method = "census", 
+             full_results = TRUE)
+
+places.geo.3 <- geo(street = df.places$`Site Street Address 3`, 
+             city = df.places$`Site City`, 
+             state = df.places$`Site State`, 
+             method = "census", 
+             full_results = TRUE)
+
+df.places <- df.places %>% 
+  cbind(places.geo %>% select(lat, long, id) %>% rename(lat.1 = lat, long.1 = long)) %>% 
+  cbind(places.geo.3 %>% select(lat, long)) %>% 
+  mutate(lat = ifelse(is.na(lat.1), lat, lat.1), 
+         long = ifelse(is.na(long.1), long, long.1)) %>% 
+  select(Zip:Access, lat, long, id)
+
+df.places[is.na(df.places$lat),] <- df.places[is.na(df.places$lat),] %>%
+  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Street Address" = "Site.Address")) %>%
+  mutate(lat = ifelse(is.na(lat), Geocoding.Artifact.Address.Primary.Y.Coordinate, lat), 
+         long = ifelse(is.na(long), Geocoding.Artifact.Address.Primary.X.Coordinate, long)) %>%
+  select(Zip:id) %>%
+  unique()
+
+df.places[is.na(df.places$lat),] <- df.places[is.na(df.places$lat),] %>%
+  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Name" = "Site.Name")) %>%
+  mutate(lat = ifelse(is.na(lat), Geocoding.Artifact.Address.Primary.Y.Coordinate, lat), 
+         long = ifelse(is.na(long), Geocoding.Artifact.Address.Primary.X.Coordinate, long)) %>%
+  select(Zip:id) %>%
+  unique()
+
+df.p <- df.places %>% 
+  select(Zip:Y, Year.y, long, lat) %>% 
+  left_join(zipsize %>% select(GEOID10, ALAND10, INTPTLON10, INTPTLAT10), by = c("Zip" = "GEOID10")) %>% 
+  mutate(Area.km2 = ALAND10 / 2.59e6 * 2.5889, 
+         Radius = sqrt(Area.km2 / pi), 
+         SquareSide = sqrt(Area.km2)) %>% 
+  mutate(INTPTLON10 = as.numeric(INTPTLON10), 
+         INTPTLAT10 = as.numeric(INTPTLAT10)) %>% 
+  mutate(DistToCenter = sqrt((long - INTPTLON10)^2 + (lat - INTPTLAT10)^2) * 111.139, 
+         xcoor = (long - INTPTLON10) * 111.139, 
+         ycoor = (lat -  INTPTLAT10) * 111.139, 
+         popcenter.x = (X - INTPTLON10) * 111.139, 
+         popcenter.y = (Y - INTPTLAT10) * 111.139)
+
+```
+
+## Scaled model of where Rival places their sites, not different from incumbent
+```{r}
+df.p %>% 
+  filter(Year.y == Att.z) %>% 
+  group_by(ClinicType) %>% 
+  select(Area.km2:popcenter.y) %>% 
+  summarise_all(mean.nas)
+
+t.test(x = df.p[df.p$Year.y == df.p$Att.z & df.p$ClinicType == "Incumbent",]$xcoor, y = df.p[df.p$Year.y == df.p$Att.z & df.p$ClinicType == "Rival",]$xcoor)
+t.test(x = df.p[df.p$Year.y == df.p$Att.z & df.p$ClinicType == "Incumbent",]$ycoor, y = df.p[df.p$Year.y == df.p$Att.z & df.p$ClinicType == "Rival",]$ycoor)
+
+df.p %>% 
+  filter(Year.y == Att.z) %>% 
+  mutate(xcoor = xcoor / Radius, 
+         ycoor = ycoor / Radius, 
+         popcenter.x = popcenter.x / Radius, 
+         popcenter.y = popcenter.y / Radius) %>% 
+  #filter(Zip == "95076") %>% 
+  ggplot(aes(x = xcoor, y = ycoor, color = ClinicType)) + 
+  #geom_rect(aes(xmin = -SquareSide / 2, xmax = SquareSide / 2, ymin = -SquareSide / 2, ymax = SquareSide / 2), fill = "blue", alpha = 0.2, color = NA) + 
+  geom_point(position=position_jitter(width=0.05, height=0.05)) + 
+  xlim(-2, 2) + ylim(-2, 2)
+
+df.p %>% 
+  filter(Year.y == Att.z) %>% 
+  group_by(ClinicType) %>% 
+  select(Area.km2:popcenter.y) %>% 
+  summarise_all(mean.nas)
+```

### 2023-09-11 code/analysis_Redo.Rmd
measures of center

@@
          popcenter.y = popcenter.y / Radius) %>% 
-  #filter(Zip == "95076") %>% 
+  filter(Zip == "43604") %>%  #43604
   ggplot(aes(x = xcoor, y = ycoor, color = ClinicType)) + 
   #geom_rect(aes(xmin = -SquareSide / 2, xmax = SquareSide / 2, ymin = -SquareSide / 2, ymax = SquareSide / 2), fill = "blue", alpha = 0.2, color = NA) + 
-  geom_point(position=position_jitter(width=0.05, height=0.05)) + 
-  xlim(-2, 2) + ylim(-2, 2)
+  geom_rect(aes(xmin = -1, xmax = 1, ymin = -1, ymax = 1), fill = "lightgrey", alpha = 0.2, color = NA) + 
+  geom_point(position=position_jitter(width=0.05, height=0.05)) + xlim(-2, 2) + ylim(-2, 2) + 
+  geom_point(aes(x = popcenter.x, y = popcenter.y), color = "green") #+ facet_wrap(~Zip)
 

### 2023-09-11 code/analysis_Redo.Rmd
triangle of distance

@@
   summarise_all(mean.nas)
-```
+
+df.p %>% 
+  filter(Year.y == Att.z) %>% 
+  filter(ClinicType == "Rival") %>% 
+  mutate(DistRivaltoCenter = sqrt((xcoor - popcenter.x)^2 + (ycoor - popcenter.y)^2)) %>% 
+  #group_by(Zip) %>% 
+  summarise(Radius = mean.nas(Radius), DistRivaltoCenter = mean.nas(DistRivaltoCenter))
+
+df.p %>% 
+  filter(Year.y == Att.z) %>% 
+  filter(ClinicType == "Incumbent") %>% 
+  mutate(DistIncumbtoCenter = sqrt((xcoor - popcenter.x)^2 + (ycoor - popcenter.y)^2)) %>% 
+  #group_by(Zip) %>% 
+  summarise(Radius = mean.nas(Radius), DistIncumbtoCenter = mean.nas(DistIncumbtoCenter))
+
+df.p %>% 
+  filter(Year.y == Att.z) %>% 
+  filter(ClinicType == "Incumbent") %>%
+  select(Zip, xcoor, ycoor) %>% 
+  full_join(df.p %>% 
+  filter(Year.y == Att.z) %>% 
+  filter(ClinicType == "Rival") %>%
+  select(Zip, xcoor, ycoor), by = c("Zip")) %>% 
+  mutate(DistIncumbtoRival = sqrt((xcoor.x - xcoor.y)^2 + (ycoor.x - ycoor.y)^2)) %>% 
+  #group_by(Zip) %>% 
+  summarise(DistIncumbtoRival = mean.nas(DistIncumbtoRival))
+
+```

### 2023-09-23 code/analysis_Redo.Rmd
just playing with some tables

@@
 library(directlabels)
+library(gtsummary)
 ```
@@
   select(Treat, Total, Pct.NHA:Pct.COM) %>% 
-  filter(complete.cases(.)) %>% 
+  #filter(!complete.cases(.)) %>% 
   tbl_summary(by = Treat, 

### 2023-09-23 code/analysis_Redo.Rmd
Cleaning up the code a bit

@@
 library(gtsummary)
+library(kableExtra)
+library(ggpubr)
 ```
@@
                   (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev), 
-         PatientsPerStaff = ngla_prog_serv_revenue / Total, #Total / Staff, 
+         PatientsPerStaff = Staff, #Total / Staff, 
          ProgramCostPerPatient = log(ngla_expense / Total)) %>% 
@@
       treatment = "Tx",
-        first_stage = ~ Sites | Zip + Year , 
+        first_stage = ~ 1 | Zip + Year , 
         second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),

### 2023-09-25 code/analysis_Redo.Rmd
Exploring alternatives

@@
   tbl_summary(by = Treat, 
-                statistic = list(all_continuous() ~ "{mean} ({sd})")) %>% 
+                statistic = list(all_continuous() ~ "{mean} ({sd})"),
+missing = "no") %>% 
   add_p()
@@
   group_by(Year, CompetitorsInArea) %>% 
-  summarise(Count = sum(Count))
+  summarise(Count = sum(Count)) %>% 
+  filter(CompetitorsInArea != "-Inf")
 
@@
       treatment = "Tx",
-        first_stage = ~ 1 | Zip + Year , 
+        first_stage = ~ Sites | Zip + Year , 
         second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),
@@
 summary(df.spill3[df.spill3$Att > 0 & df.spill3$Att.viz < df.spill3$Year,]$Unins.rate * df.spill3[df.spill3$Att > 0& df.spill3$Att.viz < df.spill3$Year,]$TotalPop)
+
+did2s(
+      data = df.spill3 %>% mutate(clust = substr(Zip, 1, 3)), 
+      yname = "Sites", 
+      treatment = "Tx",
+        first_stage = ~ 1 | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)) ,
+        cluster_var = "clust",
+      verbose = FALSE
+    )
 

### 2023-09-25 code/analysis_Redo.Rmd
Cleaning up Access analysis - removing zip codes with small n patients

@@
 library(ggpubr)
+library(tigris)
 ```
@@
 # uds.sites.full <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv")
-
+# clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
+#   #filter(Year >= included.years[1]) %>% 
+#   group_by(Zip, Year) %>%
+#   summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
+#   arrange(desc(Clinics))
 ```
@@
 ## Treatment vs control, only in zip code of interest
-df.z <- left_join(dfc #%>% filter(`Grant Number` != "H80CS00225")
-                  , #uds.zip %>% mutate(Zip = `Zip Code`) %>% select(`Grant Number`, Zip) %>% unique() , by = c("Grant Number")) %>%
-                  uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
-                    filter(Year %in% c(2010:2021)) %>% 
-              select(`BHCMIS ID`, Zip) %>%
-              unique() %>% filter(!is.na(Zip)), by = c("BHCMIS ID")) %>%
+df.z <- left_join(dfc, 
+                  #uds.zip %>% mutate(Zip = `ZipCode`) %>% select(`BHCMISID`, Zip) %>% unique() , by = c("BHCMIS ID" = "BHCMISID")) %>%
+                  uds.sites.full[!is.na(uds.sites.full$Zip),] %>% filter(Year %in% c(2010:2021)) %>% select(`BHCMIS ID`, Zip) %>% unique() %>% filter(!is.na(Zip)), by = c("BHCMIS ID")) %>%
   left_join(uds.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear", "Zip" = "ZipCode")) %>%
@@
 
-df.spill3 <- df.spill2 %>% 
+df.spill3 <- df.spill2 %>% filter(NumberofPatients > 50) %>%
+
   left_join(census %>% 
@@
  i <- 10
-  df.temp <- df.spill3[,c(1:5, 11, i, 16:ncol(df.spill3))]
-  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
+  df.temp <- df.spill3[,c(1:5, i, 16:ncol(df.spill3))]
+  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
   model_feols_clustered <- did2s(
@@
       treatment = "Tx",
-        first_stage = ~ Sites | Zip + Year , 
+        first_stage = ~ 1 | Zip + Year , 
         second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)) ,
@@
 
-for (i in 12:19){
-  df.temp <- df.spill3[,c(1:5, 11, i, 16:ncol(df.spill3))]
-  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
+for (i in 11:19){
+  df.temp <- df.spill3[,c(1:5, i, 16:ncol(df.spill3))]
+  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
   model_feols_clustered <- did2s(
@@
   group_by(Post, Treated) %>% 
-  select(Total.Hours, Perminance:Private) %>% 
+  select(Total.Hours:Private) %>% 
   summarise_all(mean.nas) %>% 
@@
   mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
-  cbind(Outcome = c("Hours Per Week","Perminance","Weekly Schedule","Calendar Schedule","Total","Uninsured","Medicaid","Medicare","Private")) %>% 
+  cbind(Outcome = c("Hours Per Week","Locations","Perminance","Weekly Schedule","Calendar Schedule","Total","Uninsured","Medicaid","Medicare","Private")) %>% 
   select(Outcome, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted) %>% 
@@
 
-did.access.figures <- did.access.figures[c(5:9, 1, 3, 2, 4),]
+did.access.figures <- did.access.figures[c(6:10, 1:5),]
 rownames(did.access.figures) <- NULL
@@
 
+did.access.figures[,c(1, 7:10)] %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI","Estimate","95% CI")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  pack_rows(index = c("Patients" = 5, "Access" = 4)) %>% 
+  add_header_above(c(" " = 1, "TE (Intercept)" = 2,"TE * Distance (Slope)" = 2))
+
 summary(df.spill3[df.spill3$Att > 0 & df.spill3$Att.viz < df.spill3$Year,]$Unins.rate * df.spill3[df.spill3$Att > 0& df.spill3$Att.viz < df.spill3$Year,]$TotalPop)
 
-did2s(
-      data = df.spill3 %>% mutate(clust = substr(Zip, 1, 3)), 
-      yname = "Sites", 
-      treatment = "Tx",
-        first_stage = ~ 1 | Zip + Year , 
-        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)) ,
-        cluster_var = "clust",
-      verbose = FALSE
-    )
+event_study(data = df.spill3, 
+  yname = "Medicaid", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
+  filter(abs(term) <= 7) %>% 
+  #filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients")
 

### 2023-09-26 code/analysis_Redo.Rmd
Cleaning up rival analysis

@@
   mutate(Area.SQmiles = ALAND10 / 2.59e6, 
-         l.popdensity = log(TotalPop / Area.SQmiles))
-  # mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet, 
+         l.popdensity = log(TotalPop / Area.SQmiles)) %>% 
+  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet)
+# ,
 #          Unemployed = Unemployed / Unemp_denom,
@@
 event_study(data = df.spill3, 
-  yname = "Medicaid", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
+  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
   filter(abs(term) <= 7) %>% 
@@
     select(`BHCMIS ID.x`, `BHCMIS ID`:Year, Att, ID) %>% 
-    left_join(df.comp%>% 
+    left_join(df.comp %>% 
   mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
@@
             Eff = ngla_prog_serv_revenue / Assets, 
-            LiabPctRev = ngla_prog_serv_revenue / ngla_expense) , by = c("BHCMIS ID.x" = "BHCMISID", "Year"))) %>% 
+            LiabPctRev = ngla_prog_serv_revenue / ngla_expense, 
+         fs_contributions = as.numeric(fs_contributions), 
+         fs_program_service_revenue = as.numeric(fs_program_service_revenue), 
+         fs_other = as.numeric(fs_other), 
+         fs_miscellaneous = as.numeric(fs_miscellaneous), 
+         ngla_sales_revenue = as.numeric(ngla_sales_revenue), 
+         ngla_admin_expense = as.numeric(ngla_admin_expense), 
+         fringe_rate = as.numeric(fringe_rate)) , by = c("BHCMIS ID.x" = "BHCMISID", "Year"))) %>% 
   mutate(MCD = Total * Pct.MCD / 100, 
@@
   outcomes <- did2s(
-      data = df.temp  , 
+      data = df.temp %>% filter(!is.na(Tx)) , 
       yname = "Outcome", 
@@
 
-event_study(data = df.competitor, 
+event_study(data = df.rival, 
   yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 

### 2023-09-28 code/analysis_Redo.Rmd
Changes in access in far-away zip codes

@@
          l.popdensity = log(TotalPop / Area.SQmiles)) %>% 
-  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet)
+  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet) #%>% filter(Zip != '04401')
 # ,
@@
   model_feols_clustered <- did2s(
-      data = df.temp, 
+      data = df.temp , 
       yname = "Outcome", 
@@
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients")
-
+```
+
+## Access by quantile
+```{r}
+qnats1 <- c(0, 0.2, 0.4, 0.6, 0.8)
+qnats2 <- c(0.2, 0.4, 0.6, 0.8, 1)
+
+qnats1 <- seq(0, 0.8, by = 0.2)
+qnats2 <- seq(0.2, 1, by = 0.2)
+
+   model.dist.quants <-  did2s(
+      data = df.spill3 %>% filter(Dist > quantile(Dist, qnats1[1]) & Dist < quantile(Dist, qnats2[1])), 
+      yname = "Total.Hours", 
+      treatment = "Tx",
+        first_stage = ~ 1 | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE)  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+    TEs <- data.frame(model.dist.quants$coeftable)[1,]
+
+  for (i in 2:5){
+      model.dist.quants <-  did2s(
+      data = df.spill3 %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist < quantile(Dist, qnats2[i])), 
+      yname = "Total.Hours", 
+      treatment = "Tx",
+        first_stage = ~ 1 | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE)  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    ) 
+      TEs <- rbind(TEs, data.frame(model.dist.quants$coeftable)[1,])
+  }
+
+    TEs
+
+    df.spill3 %>% filter(Zip != '04401')
 ```
@@
          popcenter.y = popcenter.y / Radius) %>% 
-  filter(Zip == "43604") %>%  #43604
+ #filter(Zip == "43604") %>%  #43604
   ggplot(aes(x = xcoor, y = ycoor, color = ClinicType)) + 
@@
   geom_point(position=position_jitter(width=0.05, height=0.05)) + xlim(-2, 2) + ylim(-2, 2) + 
-  geom_point(aes(x = popcenter.x, y = popcenter.y), color = "green") #+ facet_wrap(~Zip)
+  geom_point(aes(x = popcenter.x, y = popcenter.y), color = "green") + facet_wrap(~Zip)
 

### 2023-09-28 code/analysis_Redo.Rmd
comparing features of rivals versus incumbents

@@
 
-```
+ df.comp %>% 
+   mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100) %>% 
+  inner_join(df.p %>% select(ClinicType, value, Year.x) %>% unique(), by = c("BHCMISID" = "value", "Year" = "Year.x")) %>% 
+  ungroup() %>% 
+  select(ClinicType, Qcomp, Total) %>% 
+  tbl_summary(by = ClinicType, 
+                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
+  add_p()
+
+    df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.y" = "BHCMISID", "Year")) %>% 
+      mutate(Type = "Incumbent") %>% 
+      rbind(df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.x" = "BHCMISID", "Year")) %>% mutate(Type = "Rival")) %>% 
+        mutate(Quality = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100) %>% 
+      mutate(quick_ratio = as.numeric(quick_ratio),
+             Liquidity = (Assets - Liabilities) / Assets,
+               Profitability = ngla_net_gain_loss / Assets, #Assets, 
+               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
+               NetWorth = (Assets - Liabilities) / Liabilities) %>% 
+      mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity), 
+         Profitability = ifelse(is.infinite(Profitability), NA, Profitability), 
+         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency), 
+         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
+         #Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
+         Altman = 0.18 * quick_ratio + 0.3 * Profitability + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
+      select(Type, Quality, Total, Altman) %>% 
+          tbl_summary(by = Type, 
+                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
+  add_p()
+
+```

### 2023-10-12 code/analysis_Redo.Rmd
small changes
adding lots of new event study plots for Access analysis

@@
 ```{r}
-# dfc <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
-# uds.sites.full <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv")
-# clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
-#   #filter(Year >= included.years[1]) %>% 
-#   group_by(Zip, Year) %>%
-#   summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
-#   arrange(desc(Clinics))
+dfc <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
+uds.sites.full <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
+  mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 40, Access))
+clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
+  #filter(Year >= included.years[1]) %>%
+  group_by(Zip, Year) %>%
+  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
+  arrange(desc(Clinics))
+
+uds.sites.full %>%
+  filter(is.na(Zip))
 ```
@@
 
-df.temp
-
 did2s(
       data = dfc.new %>% 
-        inner_join(dfc %>% filter(Year == 2010 & Total < 14000 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
+        inner_join(dfc %>% filter(Year == 2010 & Total > 14000 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                    %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
-      yname = "Altman", 
+      yname = "Qcomp", 
       treatment = "Tx",
@@
 
-set.seed(234)  #232
+set.seed(234)  #234
 df.spill2 <- df.spill2 %>% 
@@
   mutate(`Treated Zips` = Counts_0 / 3) %>% 
-  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 200) + 
+  filter(Dist.rounded < 210) %>% 
+  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + #xlim(0, 200) + 
   xlab("Kilometers to Competitive Zip") + ylab("Unadjusted Difference-in-differences") + theme_tufte_revised() + 
@@
          l.popdensity = log(TotalPop / Area.SQmiles)) %>% 
+  #mutate(Sites = log(Sites + 1)) %>% 
   mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet) #%>% filter(Zip != '04401')
@@
 
-event_study(data = df.spill3, 
-  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
-  filter(abs(term) <= 7) %>% 
-  #filter(estimator %in% c("Gardner (2021)")) %>% 
+```
+
+## Event study plots
+```{r}
+
+ev.pop1 <- event_study(data = df.spill3, 
+  yname = "Medicaid", idname = "Zip", tname = "Year", gname = "Att", estimator = "did2s") %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients")
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Medicaid")
+ev.pop2 <- event_study(data = df.spill3, 
+  yname = "Medicare", idname = "Zip", tname = "Year", gname = "Att", estimator = "did2s") %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Medicare")
+ev.pop3 <- event_study(data = df.spill3, 
+  yname = "Uninsured", idname = "Zip", tname = "Year", gname = "Att", estimator = "did2s") %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Uninsured")
+ev.pop4 <- event_study(data = df.spill3, 
+  yname = "Private", idname = "Zip", tname = "Year", gname = "Att", estimator = "did2s") %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Private")
+
+ggarrange(ev.pop1, ev.pop2, ev.pop3, ev.pop4, common.legend = TRUE, ncol = 1)
+
 ```
@@
 ```{r}
-qnats1 <- c(0, 0.2, 0.4, 0.6, 0.8)
-qnats2 <- c(0.2, 0.4, 0.6, 0.8, 1)
-
-qnats1 <- seq(0, 0.8, by = 0.2)
-qnats2 <- seq(0.2, 1, by = 0.2)
+qnats1 <- seq(0, 0.75, by = 0.25)
+qnats2 <- seq(0.25, 1, by = 0.25)
 
    model.dist.quants <-  did2s(
-      data = df.spill3 %>% filter(Dist > quantile(Dist, qnats1[1]) & Dist < quantile(Dist, qnats2[1])), 
-      yname = "Total.Hours", 
+      data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)), 
+      yname = "Sites", 
       treatment = "Tx",
@@
 
-  for (i in 2:5){
+  for (i in 1:4){
       model.dist.quants <-  did2s(
-      data = df.spill3 %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist < quantile(Dist, qnats2[i])), 
-      yname = "Total.Hours", 
+      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]))%>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
+      yname = "SL", 
       treatment = "Tx",
@@
 
-    df.spill3 %>% filter(Zip != '04401')
+zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)), 
+  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Sites in Farthest 20% of Zips")
+
+zp2 <- event_study(data = df.spill3 %>% filter(Dist == 0), 
+  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Sites in Competitive Zip")
+
+zp3 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
+  yname = "Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Hours in Farthest 20% of Zips")
+
+zp4 <- event_study(data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
+  yname = "Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Hours in Competitive Zip")
+
+zp <- ggarrange(zp1, zp2, zp3, zp4, common.legend = TRUE)
+zp
+
+did2s(
+      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i])) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
+      yname = "Total.Hours", 
+      treatment = "Tx",
+        first_stage = ~ 1 | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE)  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+
+df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i])) %>% 
+  group_by(Tx) %>% 
+  summarise(mean(Sites))
+
 ```
@@
   #group_by(Zip) %>% 
-  summarise(Radius = mean.nas(Radius), DistRivaltoCenter = mean.nas(DistRivaltoCenter))
+  summarise(Radius = mean.nas(Radius), SD = sd(DistRivaltoCenter, na.rm = TRUE), DistRivaltoCenter = mean.nas(DistRivaltoCenter))
 
@@
   #group_by(Zip) %>% 
-  summarise(Radius = mean.nas(Radius), DistIncumbtoCenter = mean.nas(DistIncumbtoCenter))
+  summarise(Radius = mean.nas(Radius), SD = sd(DistIncumbtoCenter, na.rm = TRUE), DistIncumbtoCenter = mean.nas(DistIncumbtoCenter))
 
@@
   #group_by(Zip) %>% 
-  summarise(DistIncumbtoRival = mean.nas(DistIncumbtoRival))
+  summarise(SD = sd(DistIncumbtoRival, na.rm = TRUE), DistIncumbtoRival = mean.nas(DistIncumbtoRival))
 

### 2023-10-13 code/analysis_Redo.Rmd
friday commit
Cleaning up the code for final analysis

@@
 ```{r}
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+```
+
+```{r}
 dfc <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
 uds.sites.full <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
-  mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 40, Access))
+  mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 4, Access))
 clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
@@
   filter(is.na(Zip))
+
 ```
@@
 
+summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Total ~ Treated*year.rel))$coeff[4,]
+summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Qcomp ~ Treated*year.rel))$coeff[4,]
+summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Altman ~ Treated*year.rel))$coeff[4,]
 ```
@@
 ```{r}
-
-df.core <- dfc %>% 
-  mutate( MCD = Total * Pct.MCD / 100,
-         None = Total * Pct.None / 100,
-         MCR = Total * Pct.MCR / 100,
-         COM = Total * Pct.COM / 100,
-
-         crc.rate = crc.rate * 100, 
-         pap.rate = pap.rate * 100, 
-         childbmi.rate = childbmi.rate * 100, 
-         adultbmi.rate = adultbmi.rate * 100, 
-         htn.rate = htn.rate * 100, 
-         dm.rate = dm.rate * 100) %>% 
-  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
-         MCD:COM, 
-         crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
-         Liquidity:NetWorth, 
-         Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman)
-
-did.core <- c(0, 0, 0, 0)
-
-for (j in 10:23){
-
-  df.temp <- df.core[,c(1:9, j, 24:ncol(df.core))]
-  colnames(df.temp)[10] <- "Outcome"
-  outcomes <- did2s(
-      data = df.temp, 
-      yname = "Outcome", 
-      treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
-        second_stage = ~ i(Tx, ref = FALSE),
-        cluster_var = "STATE",
-      verbose = FALSE
-    )
-
-  did.core <- rbind(did.core, outcomes$coeftable)
-
-}
-
-did.core <- did.core[-1,]
-rownames(did.core) <- NULL
-
-mean.nas<- function(x){ mean(x, na.rm = TRUE)}
-
-options(scipen=999)
-
-df.core %>% 
-  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
-         Treated = ifelse(Att > 0, 1, 0)) %>% 
-  group_by(Post, Treated) %>% 
-  select(MCD:NetWorth) %>% 
-  summarise_all(mean.nas) %>% 
-  # summarise(Total = mean(Total, na.rm = TRUE), 
-  #           Quality = mean(Qcomp, na.rm = TRUE), 
-  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
-  pivot_longer(cols = MCD:NetWorth) %>% 
-  mutate(value = round(value, 2)) %>% 
-  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
-  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
-  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
-  cbind(did.core) %>% 
-   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
-  mutate(Estimate = round(Estimate, 2), 
-         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
-         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
-  rename(Outcome = name) %>% 
-  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
-  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
-  kable_styling(latex_options = c("striped")) %>%
-  pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
-  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
-
-```
-
-## Panel Complexity and Intensity of Care
+# 
+# df.core <- dfc %>% 
+#   mutate( MCD = Total * Pct.MCD / 100,
+#          None = Total * Pct.None / 100,
+#          MCR = Total * Pct.MCR / 100,
+#          COM = Total * Pct.COM / 100,
+#          
+#          crc.rate = crc.rate * 100, 
+#          pap.rate = pap.rate * 100, 
+#          childbmi.rate = childbmi.rate * 100, 
+#          adultbmi.rate = adultbmi.rate * 100, 
+#          htn.rate = htn.rate * 100, 
+#          dm.rate = dm.rate * 100) %>% 
+#   select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
+#          MCD:COM, 
+#          crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
+#          Liquidity:NetWorth, 
+#          Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman) 
+#   
+# 
+# 
+# 
+# did.core <- c(0, 0, 0, 0)
+# 
+# for (j in 10:23){
+#   
+#   df.temp <- df.core[,c(1:9, j, 24:ncol(df.core))]
+#   colnames(df.temp)[10] <- "Outcome"
+#   outcomes <- did2s(
+#       data = df.temp, 
+#       yname = "Outcome", 
+#       treatment = "Tx",
+#         first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
+#         second_stage = ~ i(Tx, ref = FALSE),
+#         cluster_var = "STATE",
+#       verbose = FALSE
+#     )
+#   
+#   did.core <- rbind(did.core, outcomes$coeftable)
+#   
+#   
+# }
+# 
+# 
+# did.core <- did.core[-1,]
+# rownames(did.core) <- NULL
+#
+
+# 
+# df.core %>% 
+#   mutate(Post = ifelse(year.rel >= 0, 1, 0), 
+#          Treated = ifelse(Att > 0, 1, 0)) %>% 
+#   group_by(Post, Treated) %>% 
+#   select(MCD:NetWorth) %>% 
+#   summarise_all(mean.nas) %>% 
+#   # summarise(Total = mean(Total, na.rm = TRUE), 
+#   #           Quality = mean(Qcomp, na.rm = TRUE), 
+#   #           Finances = mean(Altman, na.rm = TRUE)) %>% 
+#   pivot_longer(cols = MCD:NetWorth) %>% 
+#   mutate(value = round(value, 2)) %>% 
+#   #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
+#   pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
+#   mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
+#   cbind(did.core) %>% 
+#    select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
+#   mutate(Estimate = round(Estimate, 2), 
+#          `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
+#          `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
+#   rename(Outcome = name) %>% 
+#   select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
+#   kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
+#   kable_styling(latex_options = c("striped")) %>%
+#   pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
+#   add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
+# 
+#
+
+```
+
+## Patient Selection on Panel Complexity and Intensity of Care
 ```{r}
@@
 p2
+
+summary(lm(data = df.select.stint %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Complexity ~ Treated*year.rel))$coeff[4,]
+summary(lm(data = df.select.stint %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Intensity ~ Treated*year.rel))$coeff[4,]
+
+```
+
+## Patient Selection on Payer Mix
+```{r}
+
+df.select.payer <- dfc %>% 
+  mutate( MCD = Total * Pct.MCD / 100,
+         None = Total * Pct.None / 100,
+         MCR = Total * Pct.MCR / 100,
+         COM = Total * Pct.COM / 100,
+
+         crc.rate = crc.rate * 100, 
+         pap.rate = pap.rate * 100, 
+         childbmi.rate = childbmi.rate * 100, 
+         adultbmi.rate = adultbmi.rate * 100, 
+         htn.rate = htn.rate * 100, 
+         dm.rate = dm.rate * 100) %>% 
+  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
+         MCD:COM, Pct.MCD, Pct.None, Pct.MCR, Pct.COM, 
+         Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman)
+
+did.select.payer <- c(0, 0, 0, 0)
+
+for (j in 10:17){
+
+  df.temp <- df.select.payer[,c(1:9, j, 18:ncol(df.select.payer))]
+  colnames(df.temp)[10] <- "Outcome"
+  outcomes <- did2s(
+      data = df.temp, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "STATE",
+      verbose = FALSE
+    )
+
+  did.select.payer <- rbind(did.select.payer, outcomes$coeftable)
+
+}
+
+did.select.payer <- did.select.payer[-1,]
+rownames(did.select.payer) <- NULL
+
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+
+df.select.payer %>% 
+  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
+         Treated = ifelse(Att > 0, 1, 0)) %>% 
+  group_by(Post, Treated) %>% 
+  select(MCD:Pct.COM) %>% 
+  summarise_all(mean.nas) %>% 
+  # summarise(Total = mean(Total, na.rm = TRUE), 
+  #           Quality = mean(Qcomp, na.rm = TRUE), 
+  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
+  pivot_longer(cols = MCD:Pct.COM) %>% 
+  mutate(value = round(value, 2)) %>% 
+  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
+  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
+  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
+  cbind(did.select.payer) %>% 
+   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
+  mutate(Estimate = round(Estimate, 2), 
+         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
+         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
+  rename(Outcome = name) %>% 
+  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  pack_rows(index = c("Total Patients by Payer" = 4, "Payer Mix, %" = 4)) %>% 
+  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
+
+pm1 <- event_study(data = df.select.payer, 
+  yname = "MCD", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Medicaid") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")
+
+pm2 <- event_study(data = df.select.payer, 
+  yname = "COM", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Private") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")
+
+pm3 <- event_study(data = df.select.payer, 
+  yname = "MCR", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Medicare") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")
+
+pm4 <- event_study(data = df.select.payer, 
+  yname = "None", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Uninsured") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")
+
+pm <- ggarrange(pm1, pm2, pm3, pm4, common.legend = TRUE)
+pm
+
+summary(lm(data = df.select.payer %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), MCD ~ Treated*year.rel))$coeff[4,]
+summary(lm(data = df.select.payer %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), None ~ Treated*year.rel))$coeff[4,]
+summary(lm(data = df.select.payer %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), MCR ~ Treated*year.rel))$coeff[4,]
+summary(lm(data = df.select.payer %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), COM ~ Treated*year.rel))$coeff[4,]
 
@@
 
-df.spill3 <- df.spill2 %>% filter(NumberofPatients > 50) %>%
+df.spill3 <- df.spill2 %>% filter(NumberofPatients > 50 ) %>% 
+  #group_by(Zip) %>% mutate(MaxNum = max(NumberofPatients)) %>% filter(MaxNum > 50) %>%
 
@@
   #mutate(Sites = log(Sites + 1)) %>% 
-  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet) #%>% filter(Zip != '04401')
+  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet) #%>% filter(NumberofPatients > 100 | NumberofPatients / TotalPop > 0.01)
+
+#%>% filter(Zip != '04401')
 # ,
@@
     )
-    TEs <- data.frame(model.dist.quants$coeftable)[1,]
+    tes <- data.frame(model.dist.quants$coeftable)[1,]
 
@@
       data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]))%>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
-      yname = "SL", 
+      yname = "Sites", 
       treatment = "Tx",
@@
     ) 
-      TEs <- rbind(TEs, data.frame(model.dist.quants$coeftable)[1,])
+      tes <- rbind(tes, data.frame(model.dist.quants$coeftable)[1,])
   }
 
-    TEs
+    tes
 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Sites in Farthest 20% of Zips")
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")
 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Sites in Competitive Zip")
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")
 
 zp3 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
-  yname = "Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
+  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
   filter(abs(term) < 7) %>% 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Hours in Farthest 20% of Zips")
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")
 
 zp4 <- event_study(data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
-  yname = "Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
+  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
   filter(abs(term) < 7) %>% 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Hours in Competitive Zip")
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")
 
@@
 
-event_study(data = df.rival, 
-  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
-  filter(abs(term) <= 7) %>% 
+rpm1 <- event_study(data = df.rival, 
+  yname = "MCD", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) < 7) %>% 
   filter(estimator %in% c("Gardner (2021)")) %>% 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients")
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Medicaid") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")
+
+rpm2 <- event_study(data = df.rival, 
+  yname = "COM", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Private") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")
+
+rpm3 <- event_study(data = df.rival, 
+  yname = "MCR", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Medicare") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")
+
+rpm4 <- event_study(data = df.rival, 
+  yname = "None", idname = "ID", tname = "Year", gname = "Att", estimator = "did2s", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) < 7) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Uninsured") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")
+
+rpm <- ggarrange(rpm1, rpm2, rpm3, rpm4, common.legend = TRUE)
+rpm
+
+summary(lm(data = df.rival %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), COM ~ Treated*year.rel))
 
@@
 ```
+
+## Benjamini-Hochberg Correction - BEWARE did.core and TEs/TEs_DIST
+```{r}
+
+## All Hypotheses tested
+data.frame(rbind(did.core, did.select.stint, did.select.payer, did.rival)) %>% 
+  rbind(TEs) %>% rbind(TEs_Dist) %>% 
+  arrange(`Pr...t..`) %>% 
+  cbind(c(1:43) / 43 * 0.1) %>% 
+  mutate(Row = row_number()) %>% 
+  ggplot(aes(x = Row, y = `Pr...t..`)) + geom_point() + 
+  ylab("p-values") + xlab("Significance Rank") + geom_abline(slope = 1/43 * 0.1, intercept = 0, color="red", linetype="dashed", alpha=.5) + theme_minimal()
+
+```

### 2023-10-16 code/analysis_Redo.Rmd
Making nicer figures

@@
 library(tigris)
+library(usmap)
 ```
@@
   filter(abs(term) <= 5) %>% 
-  filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") , 
+  #filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
 event_study(data = df.core, 
@@
   filter(abs(term) <= 5) %>% 
-  filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite"), 
+  #filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
 event_study(data = df.core, 
@@
   filter(abs(term) <= 5) %>% 
-  filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience"), common.legend = TRUE, nrow = 1 ) 
+  #filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, nrow = 1 )
 p0
@@
 p <- df.z.dist.plot %>% 
-  filter(DistToClosestSite < 200) %>% 
+  filter(DistToClosestSite > 25) %>% 
   ggplot(aes(x = log(Density.Origin), y = log(Density.NewZip))) + 
@@
   arrange(desc(DistToClosestSite))
-```
-
-## Primary effects by distance rival travelled
-```{r}
-set.seed(123)
-df.dist <- df.core2 %>% 
-  left_join(df.z.dist.plot %>% select(`BHCMIS ID.y`, DistToClosestSite, Density.NewZip), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
-  group_by(`BHCMIS ID`) %>% 
-  mutate(Dist.random = sample(size = 1, unique(df.z.dist.plot$DistToClosestSite / df.z.dist.plot$Density.NewZip), replace = TRUE), 
-         Dist.random = ifelse(Att > 0, DistToClosestSite / Density.NewZip, Dist.random))
-
-#splits <- quantile(dfc[dfc$Year == 2011,]$Total, c(0.5), na.rm = TRUE)
-splits <- quantile(df.dist[df.dist$year.rel == -1,]$Dist.random, c(0.5), na.rm = TRUE)
-
-splits1 <- c(min(df.dist$Dist.random, na.rm = TRUE)-1, splits)
-splits2 <- c(splits, max(df.dist$Dist.random, na.rm = TRUE))
-
-did.dist <- c(0, 0, 0, 0)
-for (g in 1:(length(splits) + 1)){
-  for (j in 10:12){
-
-  df.temp <- df.dist[,c(1:9, j, 13:ncol(df.dist))] 
-  colnames(df.temp)[10] <- "Outcome"
-  outcomes <- did2s(
-      data = df.temp %>% filter(Dist.random > splits1[g] & Dist.random <= splits2[g]), 
-      yname = "Outcome", 
-      treatment = "Tx",
-        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
-        second_stage = ~ i(Tx, ref = FALSE),
-        cluster_var = "STATE",
-      verbose = FALSE
-    )
-
-  did.dist <- rbind(did.dist, outcomes$coeftable)
-
-}}
-
-did.dist <- did.dist[-1,]
-rownames(did.dist) <- NULL
-
-mean.nas<- function(x){ mean(x, na.rm = TRUE)}
-
-options(scipen=999)
-
-data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
-      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
-      Estimate = as.numeric(did.dist[,1]), 
-      SD = as.numeric(did.dist[,2])) %>% 
-  mutate(Subset.f = as.factor(Subset)) %>% 
-  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
-  geom_point() + 
-  xlab("Staggered 2-way DID Estimates") + 
-ylab(NULL) + 
-#adds the CIs
-geom_errorbarh(height=.1) +
-
-#sets the scales
-#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
-#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
-#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
-
-#adding a vertical line at the effect = 0 mark
-geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
-
-#faceting based on my subgroups
-  #facet_wrap(~X1) +
-facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
-      theme_tufte_revised()+
-   theme(strip.placement = "outside") +
-#theme(text=element_text(family="Times",size=12, color="black"))+
-theme(panel.spacing = unit(1, "lines")) + 
-  ggtitle("DID Estimates by Distance Traveled")
 ```
@@
   #mutate(Sites = log(Sites + 1)) %>% 
-  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet) #%>% filter(NumberofPatients > 100 | NumberofPatients / TotalPop > 0.01)
+  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet) %>% 
+  mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites))#%>% filter(NumberofPatients > 100 | NumberofPatients / TotalPop > 0.01)
 
@@
 zp <- ggarrange(zp1, zp2, zp3, zp4, common.legend = TRUE)
+zp <- ggarrange(zp3, zp4, common.legend = TRUE)
 zp
@@
 
+p.rival.dist <- df.z.dist %>% 
+  arrange(DistToClosestSite) %>% 
+    ggplot(aes(x=DistToClosestSite)) + geom_histogram(binwidth = 1, fill="lightgrey", color="white") + xlim(0,150) + 
+  #ylim(0, 25) + 
+   #scale_x_log10(name = 'Number of planned tours', breaks=c(1,5,10,50,100,200))+
+   stat_bin(aes(y=cumsum(..count..)/10), binwidth = 1, geom="line",color="blue") + 
+   scale_y_continuous(name = 'Number of Rivals', sec.axis = sec_axis(~./81*1000, name = "Cummulative percentage (%)")) + 
+  theme_tufte_revised() + ggtitle("FQHC Rivals by Distance from Service Area to New Competitive Zip") + xlab("Distance Travelled (km)")
+
+p.rival.dist
+
+```
+
+## Map of where competitive zip codes are
+
+```{r}
+
+#eq_transformed <- usmap_transform(earthquakes)
+
+eq_transformed <- usmap_transform(df.z.dist %>% 
+  left_join(zip.centroids %>% rename(lon = X, lat = Y) , by = c("Zip" = "ZipCode"))) %>% 
+  mutate(`Distance Travelled` = ifelse(DistToClosestSite > 25, ">25km", "<25km"))
+
+plot_usmap() +
+  geom_point(data = eq_transformed, aes(x = x, y = y, color = `Distance Travelled`)) +
+  labs(title = "Competitive Zip Codes",
+       subtitle = "By Distance Traveled by Rival") +
+  theme(legend.position = "right")
 ```
@@
   geom_rect(aes(xmin = -1, xmax = 1, ymin = -1, ymax = 1), fill = "lightgrey", alpha = 0.2, color = NA) + 
-  geom_point(position=position_jitter(width=0.05, height=0.05)) + xlim(-2, 2) + ylim(-2, 2) + 
-  geom_point(aes(x = popcenter.x, y = popcenter.y), color = "green") + facet_wrap(~Zip)
+  geom_point(position=position_jitter(width=0.05, height=0.05)) + xlim(-2, 2) + ylim(-2, 2) #+ 
+  #geom_point(aes(x = popcenter.x, y = popcenter.y), color = "green") #+ facet_wrap(~Zip)
 
@@
          Altman = 0.18 * quick_ratio + 0.3 * Profitability + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
-      select(Type, Quality, Total, Altman) %>% 
+      select(Type, Quality, Total, Altman, Pct.NHA:Pct.COM) %>% 
           tbl_summary(by = Type, 

### 2023-10-23 code/analysis_Redo.Rmd
Add resources tables to Utilization Analysis

@@
 summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Altman ~ Treated*year.rel))$coeff[4,]
+```
+
+## Resources to support utilization
+
+```{r}
+
+df.util <- dfc %>% 
+  inner_join(uds.sites.full %>% 
+             filter(`Location Setting` %in% c("All Other Clinic Types","School") | is.na(`Location Setting`)) %>% 
+              #filter(`Location Setting` %in% c("All Other Clinic Types","School")) %>% 
+              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
+                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
+                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
+                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
+                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
+                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
+              group_by(`BHCMIS ID`, Year) %>% 
+              summarise(Sites = n_distinct(`Site Name`), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
+                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)) %>% 
+                mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
+         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
+         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
+         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
+         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
+         Calendar = ifelse(is.na(Calendar), 0, Calendar)), by = c("BHCMIS ID","Year")) %>% 
+  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
+         Staff, Assets, Sites.y, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
+         Pct.NHA:Pct.COM)
+
+did.util <- c(0, 0, 0, 0)
+
+for (j in 10:12){
+
+  df.temp <- df.util[,c(1:9, j, 12:ncol(df.util))]
+  colnames(df.temp)[10] <- "Outcome"
+  outcomes <- did2s(
+      data = df.temp  , 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "STATE",
+      verbose = TRUE
+    )
+  did.util <- rbind(did.util, outcomes$coeftable)
+}
+
+did.util <- did.util[-1,]
+rownames(did.util) <- NULL
+
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+
+p1 <- df.util %>% 
+  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
+         Treated = ifelse(Att > 0, 1, 0)) %>% 
+  group_by(Post, Treated) %>% 
+  select(Staff:Sites.y) %>% 
+  summarise_all(mean.nas) %>% 
+  # summarise(Total = mean(Total, na.rm = TRUE), 
+  #           Quality = mean(Qcomp, na.rm = TRUE), 
+  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
+  pivot_longer(cols = Staff:Sites.y) %>% 
+  mutate(value = round(value, 2)) %>% 
+  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
+  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
+  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
+  cbind(did.util) %>%
+
+  #       , group =   gsub(x = df.util %>% 
+  # select(Complexity:Intensity) %>% 
+  # colnames(), pattern = "^[[:alpha:]]+\\.", replacement = "")) %>% 
+  # arrange(desc(group)) %>% 
+   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
+  mutate(Estimate = round(Estimate, 2), 
+         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
+         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
+  rename(Outcome = name) %>% 
+  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  #pack_rows(index = c("Selection" = 7, "UDS Measure Denom" = 6, "Stinting" = 7)) %>% 
+  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
+
+p1
+
+p2 <- ggarrange(
+  event_study(data = df.util, 
+  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Staff") , 
+  event_study(data = df.util, 
+  yname = "Assets", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Assets") ,
+event_study(data = df.util, 
+  yname = "Sites.y", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Sites"), common.legend = TRUE ) 
+p2
+
+summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Assets ~ Treated*year.rel))$coeff[4,]
+summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Staff ~ Treated*year.rel))$coeff[4,]
+summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Sites.y ~ Treated*year.rel))$coeff[4,]
+
 ```
@@
 
-## Effects stratified by profitability
+## Effects stratified by profitability or Quality
 
@@
 
-splits <- c(mean(dfc[dfc$year.rel == -1,]$ngla_net_gain_loss / dfc[dfc$year.rel == -1,]$ngla_expense, na.rm = TRUE))
+splits <- c(mean(dfc[dfc$year.rel == -1,]$Qcomp, na.rm = TRUE))
+
+splits <- quantile(dfc[dfc$year.rel == -1,]$Qcomp, c(0.5), na.rm = TRUE)
 
@@
 df.profit <- df.profit %>% 
-  left_join(dfc %>% filter(year.rel == -1) %>% select(ID, ngla_net_gain_loss, ngla_revenue, ngla_expense, Assets) %>% 
-  mutate(pc = ngla_net_gain_loss / ngla_expense) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))
+  left_join(dfc %>% filter(year.rel == -1) %>% select(ID, Qcomp, ngla_net_gain_loss, ngla_revenue, ngla_expense, Assets) %>% 
+  mutate(pc = Qcomp) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))
 
@@
   left_join(uds.sites.full %>% 
-              filter(`Location Setting` %in% c("All Other Clinic Types")) %>% 
+              #filter(`Location Setting` %in% c("All Other Clinic Types")) %>% 
+              filter(`Location Setting` %in% c("All Other Clinic Types","School") | is.na(`Location Setting`)) %>% 
               mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
@@
 
-summary(df.spill3[df.spill3$Att > 0 & df.spill3$Att.viz < df.spill3$Year,]$Unins.rate * df.spill3[df.spill3$Att > 0& df.spill3$Att.viz < df.spill3$Year,]$TotalPop)
+summary(df.spill3[df.spill3$Att > 0 & df.spill3$Att.viz < df.spill3$Year,]$Unins.rate * df.spill3[df.spill3$Att > 0 & df.spill3$Att.viz < df.spill3$Year,]$TotalPop)
 

### 2023-10-25 code/analysis_Redo.Rmd
Adding rival capacity

@@
   select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
-         Staff, Assets, Sites.y, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
+         Staff, #Assets, 
+         Sites.y, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
          Pct.NHA:Pct.COM)
@@
 
-for (j in 10:12){
+for (j in 10:11){
 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) +
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Staff") , 
-  event_study(data = df.util, 
-  yname = "Assets", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
-  filter(abs(term) <= 5) %>% 
-  filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Assets") ,
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Staff") + xlab("Year Relative to Competitive Shock") + ylab("Sites"),
+  # event_study(data = df.util, 
+  # yname = "Assets", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  # filter(abs(term) <= 5) %>% 
+  # filter(estimator == "Gardner (2021)") %>% 
+  # ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  # #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  # theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  # geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Assets") + xlab("Year Relative to Competitive Shock"),
 event_study(data = df.util, 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Sites"), common.legend = TRUE ) 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Sites") + xlab("Year Relative to Competitive Shock"), common.legend = TRUE ) 
 p2
@@
          #Liquidity:NetWorth, 
-         Pct.NHA:Pct.Homeless)
+         Pct.NHA:Pct.Homeless, Assets, Staff)
 
@@
 
+## Rival Capacity
+```{r}
+
+df.rival.util <- df.rival %>% 
+  inner_join(uds.sites.full %>% 
+             filter(`Location Setting` %in% c("All Other Clinic Types","School") | is.na(`Location Setting`)) %>% 
+              #filter(`Location Setting` %in% c("All Other Clinic Types","School")) %>% 
+              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
+                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
+                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
+                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
+                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
+                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
+              group_by(`BHCMIS ID`, Year) %>% 
+              summarise(Sites = n_distinct(`Site Name`), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
+                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)) %>% 
+                mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
+         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
+         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
+         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
+         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
+         Calendar = ifelse(is.na(Calendar), 0, Calendar)), by = c("BHCMIS ID","Year")) %>% 
+  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
+         Staff, #Assets, 
+         Sites, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
+          Pct.MCD:Pct.Homeless)
+
+did.rival.util <- c(0, 0, 0, 0)
+
+for (j in 10:11){
+
+  df.temp <- df.rival.util[,c(1:9, j, 13:ncol(df.rival.util))]
+  colnames(df.temp)[10] <- "Outcome"
+  outcomes <- did2s(
+      data = df.temp  , 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "STATE",
+      verbose = TRUE
+    )
+  did.rival.util <- rbind(did.rival.util, outcomes$coeftable)
+}
+
+did.rival.util <- did.rival.util[-1,]
+rownames(did.rival.util) <- NULL
+
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+
+options(scipen=999)
+
+p1 <- df.rival.util %>% 
+  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
+         Treated = ifelse(Att > 0, 1, 0)) %>% 
+  group_by(Post, Treated) %>% 
+  select(Staff:Sites) %>% 
+  summarise_all(mean.nas) %>% 
+  # summarise(Total = mean(Total, na.rm = TRUE), 
+  #           Quality = mean(Qcomp, na.rm = TRUE), 
+  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
+  pivot_longer(cols = Staff:Sites) %>% 
+  mutate(value = round(value, 2)) %>% 
+  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
+  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
+  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
+  cbind(did.rival.util) %>%
+
+  #       , group =   gsub(x = df.rival.util %>% 
+  # select(Complexity:Intensity) %>% 
+  # colnames(), pattern = "^[[:alpha:]]+\\.", replacement = "")) %>% 
+  # arrange(desc(group)) %>% 
+   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
+  mutate(Estimate = round(Estimate, 2), 
+         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
+         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
+  rename(Outcome = name) %>% 
+  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  #pack_rows(index = c("Selection" = 7, "UDS Measure Denom" = 6, "Stinting" = 7)) %>% 
+  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
+
+p1
+
+p2 <- ggarrange(
+  event_study(data = df.rival.util, 
+  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Staff") , 
+  # event_study(data = df.rival.util, 
+  # yname = "Assets", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  # filter(abs(term) <= 5) %>% 
+  # filter(estimator == "Gardner (2021)") %>% 
+  # ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  # #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  # theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  # geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Assets") ,
+event_study(data = df.rival.util, 
+  yname = "Sites", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Sites"), common.legend = TRUE ) 
+p2
+
+#summary(lm(data = df.rival.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Assets ~ Treated*year.rel))$coeff[4,]
+summary(lm(data = df.rival.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Staff ~ Treated*year.rel))$coeff[4,]
+summary(lm(data = df.rival.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Sites ~ Treated*year.rel))$coeff[4,]
+
+```
+
 ## Visualizing where the rival places there clinic

### 2023-10-26 code/analysis_Redo.Rmd
Seeing changes in rival's complexity

@@
       data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)), 
-      yname = "Sites", 
+      yname = "Medicaid", 
       treatment = "Tx",
@@
       data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]))%>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
-      yname = "Sites", 
+      yname = "Medicaid", 
       treatment = "Tx",
@@
       data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i])) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
-      yname = "Total.Hours", 
+      yname = "NumberofPatients", 
       treatment = "Tx",
@@
          COM = Total * Pct.COM / 100) %>% 
+    mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
+         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5) %>% 
     select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
@@
          #Liquidity:NetWorth, 
-         Pct.NHA:Pct.Homeless, Assets, Staff)
+         Pct.NHA:Pct.Homeless, Assets, Staff, Complexity, Intensity)
 

### 2023-10-27 code/analysis_Redo.Rmd
making figures

@@
 
-annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))
+p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))
+
+ggsave(filename = "Picture1.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 16, height = 9)
 
@@
   filter(abs(term) <= 5) %>% 
-  #filter(estimator == "Gardner (2021)") %>% 
+  filter(estimator == "Gardner (2021)") %>% 
   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
@@
 summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Altman ~ Treated*year.rel))$coeff[4,]
+
+#ggsave(filename = "Picture3a.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 16, height = 9)
+
 ```
@@
 summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Sites.y ~ Treated*year.rel))$coeff[4,]
+
+)
 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Complexity") , 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Complexity") + xlab("Year Relative to Competitive Shock")  + ylab("Prevalence"), 
 event_study(data = df.select.stint, 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Intensity"), common.legend = TRUE ) 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Intensity") + xlab("Year Relative to Competitive Shock") + ylab("Visits"), common.legend = TRUE ) 
 p2
@@
 
-data.frame(Subset = sort(rep(c("2012-2014","2015-2017","2018-2021"), 3)),
+p3 <- data.frame(Subset = sort(rep(c("2012-2014","2015-2017","2018-2021"), 3)),
       Outcome = rep(c("Total","Quality","Financial"), 3),
@@
 theme(panel.spacing = unit(1, "lines")) + 
-  ggtitle("DID Estimates by timeperiod of competitive shocks")
+  ggtitle("DID Estimates by Timeperiod of Competitive Shocks")
 
@@
   left_join(uds.sites.full %>% 
-              #filter(`Location Setting` %in% c("All Other Clinic Types")) %>% 
-              filter(`Location Setting` %in% c("All Other Clinic Types","School") | is.na(`Location Setting`)) %>% 
+              filter(`Location Setting` %in% c("All Other Clinic Types")) %>% 
+              #filter(`Location Setting` %in% c("All Other Clinic Types","School") | is.na(`Location Setting`)) %>% 
               mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
@@
   ggtitle("Unadjusted DID Estimates by Distance to Competitive Zip")
-
-suppressWarnings(print(p.spill))
 
@@
 rpm <- ggarrange(rpm1, rpm2, rpm3, rpm4, common.legend = TRUE)
-rpm
 
@@
 
-plot_usmap() +
+mapps <- plot_usmap() +
   geom_point(data = eq_transformed, aes(x = x, y = y, color = `Distance Travelled`)) +
@@
   theme(legend.position = "right")
+
+ggsave(filename = "Picture11.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = mapps, width = 16, height = 9)
 ```

### 2023-10-27 code/analysis_Redo.Rmd
more figure updates

@@
 
-p.desc <- ggarrange(plot1, plot0)
+p.desc <- ggarrange(plot1, plot0, ncol = 1)
 
@@
 
-ggsave(filename = "Picture1.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 16, height = 9)
+ggsave(filename = "Picture1.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 11, height = 15)
 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, nrow = 1 )
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, ncol = 1 )
 p0
@@
 summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Sites.y ~ Treated*year.rel))$coeff[4,]
-
-)
 
@@
 zp <- ggarrange(zp3, zp4, common.legend = TRUE)
-zp
 
@@
 
+#ggsave(filename = "Picture13.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = zp, width = 16, height = 9)
 ```
@@
 
-ggsave(filename = "Picture11.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = mapps, width = 16, height = 9)
+#ggsave(filename = "Picture11.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = mapps, width = 16, height = 9)
 ```
@@
 ## All Hypotheses tested
-data.frame(rbind(did.core, did.select.stint, did.select.payer, did.rival)) %>% 
+bhoch <- data.frame(rbind(did.core, did.select.stint, did.select.payer, did.rival)) %>% 
   rbind(TEs) %>% rbind(TEs_Dist) %>% 
@@
 
-```
+#ggsave(filename = "Picture12.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = bhoch, width = 16, height = 9)
+
+```

### 2023-10-27 code/analysis_Redo.Rmd
clustering analysis of incumbents and rivals

@@
 
+## Ratio of Distance between incumbent sites and rival
+```{r}
+
+mm.dist <-   df.p %>% 
+  filter(Year.y == Att.z) %>% 
+  filter(ClinicType == "Incumbent") %>% 
+  select(Zip, value, ClinicType, long, lat) %>% 
+  unique() %>% 
+  arrange(Zip)
+
+vec <- 0
+for (k in 1:length(unique(mm.dist$Zip))){
+
+ mm.temp <- mm.dist %>% filter(Zip == unique(mm.dist$Zip)[k]) %>% select(long, lat)
+ mm.temp <- dist(mm.temp, upper = FALSE)
+ vec <- c(vec, mean(mm.temp, na.rm = TRUE))
+}
+
+inc.dist <- data.frame(Zip = unique(mm.dist$Zip), DistIncs = vec[-1]* 111.139)
+
+mm.dist <-   df.p %>% 
+  filter(Year.y == Att.z) %>% 
+  filter(ClinicType == "Rival") %>% 
+  select(Zip, value, ClinicType, long, lat) %>% 
+  unique() %>% 
+  arrange(Zip)
+
+vec <- 0
+for (k in 1:length(unique(mm.dist$Zip))){
+
+ mm.temp <- mm.dist %>% filter(Zip == unique(mm.dist$Zip)[k]) %>% select(long, lat)
+ mm.temp <- dist(mm.temp, upper = FALSE)
+ vec <- c(vec, mean(mm.temp, na.rm = TRUE))
+}
+
+rival.dist <- data.frame(Zip = unique(mm.dist$Zip), DistRivals = vec[-1]* 111.139)
+
+df.p %>% 
+  filter(Year.y == Att.z) %>% 
+  filter(ClinicType == "Incumbent") %>%
+  select(Zip, xcoor, ycoor, Radius) %>% 
+  full_join(df.p %>% 
+  filter(Year.y == Att.z) %>% 
+  filter(ClinicType == "Rival") %>%
+  select(Zip, xcoor, ycoor), by = c("Zip")) %>% 
+  mutate(DistIncumbtoRival = sqrt((xcoor.x - xcoor.y)^2 + (ycoor.x - ycoor.y)^2)) %>% 
+  group_by(Zip) %>% 
+  summarise(SD = sd(DistIncumbtoRival, na.rm = TRUE), DistIncumbtoRival = mean.nas(DistIncumbtoRival), Radius = mean(Radius)) %>% 
+  left_join(inc.dist, by = c("Zip")) %>% 
+  left_join(rival.dist, by = c("Zip")) %>% 
+  mutate(DistIncs = DistIncs / Radius, DistRivals = ifelse(DistRivals == "NaN", NA, DistRivals / Radius)) %>% 
+  select(DistIncumbtoRival, DistIncs, DistRivals) %>% 
+  tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no")
+  #summarise(mean.nas(DistIncumbtoRival), mean.nas(DistIncs ), mean.nas(DistRivals ))
+
+```
+
 ## Benjamini-Hochberg Correction - BEWARE did.core and TEs/TEs_DIST

### 2023-10-28 code/analysis_Redo.Rmd
test
adding digits

@@
                 statistic = list(all_continuous() ~ "{mean} ({sd})"),
-missing = "no") %>% 
-  add_p()
+missing = "no", digits = list(everything() ~ c(2))) %>% 
+  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))
 

### 2023-11-26 code/analysis_Redo.Rmd
test
update usethis
changing figs

@@
 ggsave(filename = "Picture1.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 11, height = 15)
+
+p.desc <- ggarrange(plot1, plot0, ncol = 2)
+
+p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))
+
+ggsave(filename = "Picture1h.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 16, height = 9)
 
@@
 
+p0 <- ggarrange(
+  event_study(data = df.core, 
+  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
+event_study(data = df.core, 
+  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
+event_study(data = df.core, 
+  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, ncol = 3 )
+p0
+
+ggsave(filename = "Picture3ah.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 17, height = 9)
 ```
@@
 
-summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Assets ~ Treated*year.rel))$coeff[4,]
+#summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Assets ~ Treated*year.rel))$coeff[4,]
 summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Staff ~ Treated*year.rel))$coeff[4,]
@@
 
-did2s(
-      data = df.profit %>% mutate(pc = ngla_net_gain_loss / ngla_expense * 10) %>% filter(!is.na(pc)) , 
-      yname = "Qcomp", 
-      treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
-        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2) ,
-        cluster_var = "STATE",
-      verbose = FALSE
-    )
+# did2s(
+#       data = df.profit %>% mutate(pc = ngla_net_gain_loss / ngla_expense * 10) %>% filter(!is.na(pc)) , 
+#       yname = "Qcomp", 
+#       treatment = "Tx",
+#         first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
+#         second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2) ,
+#         cluster_var = "STATE",
+#       verbose = FALSE
+#     )
 

### 2023-11-28 code/analysis_Redo.Rmd
changes
check
updating the code

@@
                   (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev), 
-         PatientsPerStaff = Staff, #Total / Staff, 
+         PatientsPerStaff = log(Total / Staff), 
          ProgramCostPerPatient = log(ngla_expense / Total)) %>% 

### 2023-12-27 code/analysis_Redo.Rmd
harmonizing color schemes

@@
 ggsave(filename = "Picture3ah.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 17, height = 9)
-```
-
-## Resources to support utilization
+
+p0.simple <- ggarrange(
+event_study(data = df.core, 
+  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
+event_study(data = df.core, 
+  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Altman's Z Score") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, ncol = 2, legend = F)
+p0.simple
+
+ggsave(filename = "Picture3ahSimple.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0.simple, width = 17, height = 9)
+
+```
+
+## Resources to support utilization, capacity
 
@@
          Calendar = ifelse(is.na(Calendar), 0, Calendar)), by = c("BHCMIS ID","Year")) %>% 
+  mutate(logPatsPerStaff = log(Total / Staff)) %>% 
   select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
@@
          Sites.y, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
+         logPatsPerStaff, 
          Pct.NHA:Pct.COM)
@@
 
-for (j in 10:11){
-
-  df.temp <- df.util[,c(1:9, j, 12:ncol(df.util))]
+for (j in 10:12){
+
+  df.temp <- df.util[,c(1:9, j, 13:ncol(df.util))]
   colnames(df.temp)[10] <- "Outcome"
@@
   group_by(Post, Treated) %>% 
-  select(Staff:Sites.y) %>% 
+  select(Staff:logPatsPerStaff) %>% 
   summarise_all(mean.nas) %>% 
@@
   #           Finances = mean(Altman, na.rm = TRUE)) %>% 
-  pivot_longer(cols = Staff:Sites.y) %>% 
+  pivot_longer(cols = Staff:logPatsPerStaff) %>% 
   mutate(value = round(value, 2)) %>% 
@@
 summary(lm(data = df.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Sites.y ~ Treated*year.rel))$coeff[4,]
+
+did2s(
+      data = dfc %>% mutate(outcome = log(Total / Staff)) %>% filter(outcome < 8 & !is.infinite(outcome)), 
+      yname = "outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "STATE",
+      verbose = TRUE
+    )
+
+exp(0.042076)
+exp(0.19)
+
+hist((dfc$Total / dfc$Staff))
+summary(log(dfc$Total / dfc$Staff))
+
+p14 <- event_study(data = dfc %>% mutate(outcome = log(Total / Staff)) %>% filter(outcome < 10),
+  yname = "outcome", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
+  #mutate(estimate = exp(estimate), std.error = exp(std.error)) %>% 
+  filter(abs(term) <= 5) %>%
+  filter(estimator == "Gardner (2021)") %>%
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold'))+ 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Event Study - Effects of Competitive Shock on log Ratio of Patients Per Staff Member") + xlab("Year Relative to Competitive Shock") + ylab("log Patients")
+
+p14
+
+ggsave(filename = "Picture14.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p14, width = 17, height = 9)
 
@@
 # 
-
+# 
 # 
@@
 #   add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
-# 
-#
 
@@
   filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold'))+ 
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Complexity") + xlab("Year Relative to Competitive Shock")  + ylab("Prevalence"), 
@@
   filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Intensity") + xlab("Year Relative to Competitive Shock") + ylab("Visits"), common.legend = TRUE ) 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold'))+ 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Intensity") + xlab("Year Relative to Competitive Shock") + ylab("Visits"), common.legend = TRUE, legend = F) 
 p2
@@
 summary(lm(data = df.select.stint %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Intensity ~ Treated*year.rel))$coeff[4,]
+
+ggsave(filename = "Picture4.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p2, width = 17, height = 9)
 
@@
 
+ggsave(filename = "Picture5.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = pm, width = 17, height = 9)
 ```
@@
   filter(estimator %in% c("Gardner (2021)")) %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")
@@
   filter(estimator %in% c("Gardner (2021)")) %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")
@@
   filter(estimator %in% c("Gardner (2021)")) %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")
@@
   filter(estimator %in% c("Gardner (2021)")) %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")

### 2023-12-28 code/analysis_Redo.Rmd
more harmonization

@@
   filter(estimator %in% c("Gardner (2021)")) %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold'))+ 
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Medicaid") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")
@@
   filter(estimator %in% c("Gardner (2021)")) %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold'))+ 
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Private") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")
@@
   filter(estimator %in% c("Gardner (2021)")) %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold'))+ 
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Medicare") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")
@@
   filter(estimator %in% c("Gardner (2021)")) %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold'))+ 
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Uninsured") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients")
@@
 
-ggsave(filename = "Picture5.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = pm, width = 17, height = 9)
+#ggsave(filename = "Picture5.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = pm, width = 17, height = 9)
 ```

### 2023-12-30 code/analysis_Redo.Rmd
bit of exploration

@@
 did2s(
-      data = dfc %>% mutate(outcome = log(Total / Staff)) %>% filter(outcome < 8 & !is.infinite(outcome)), 
+      data = dfc %>% mutate(outcome = log(ngla_revenue / Staff)) %>% filter(outcome < 15 & !is.infinite(outcome)), 
       yname = "outcome", 
@@
 summary(log(dfc$Total / dfc$Staff))
+
+hist(log(dfc$ngla_revenue / dfc$Staff))
+summary(log(dfc$ngla_revenue / dfc$Staff))
 

### 2023-12-31 code/analysis_Redo.Rmd
updating heterogeneity access analysis

@@
       data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)), 
-      yname = "Medicaid", 
+      yname = "NumberofPatients", 
       treatment = "Tx",
@@
       data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]))%>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
-      yname = "Medicaid", 
+      yname = "NumberofPatients", 
       treatment = "Tx",
@@
 
-zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)), 
-  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
+zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.9)), 
+  yname = "NumberofPatients", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
   filter(abs(term) < 7) %>% 
@@
 zp2 <- event_study(data = df.spill3 %>% filter(Dist == 0), 
-  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
+  yname = "NumberofPatients", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
   filter(abs(term) < 7) %>% 
@@
 
-zp3 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
+zp3 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.9)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
   yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 10% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")
 
@@
 zp <- ggarrange(zp1, zp2, zp3, zp4, common.legend = TRUE)
+
 zp <- ggarrange(zp3, zp4, common.legend = TRUE)

### 2023-12-31 code/analysis_Redo.Rmd
better stratified access analysis

@@
   yname = "NumberofPatients", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
-  filter(abs(term) < 7) %>% 
+  filter(abs(term) < 6) %>% 
   filter(estimator %in% c("Gardner (2021)")) %>% 
@@
   yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
-  filter(abs(term) < 7) %>% 
+  filter(abs(term) < 6) %>% 
   filter(estimator %in% c("Gardner (2021)")) %>% 
@@
     )
+
+```
+
+## Stratified analysis instead for Access
+```{r}
+
+#### STRATIFEID ANALYSIS INSTEAD
+
+model <- did2s(
+      data = df.spill3  %>% filter((Dist >= quantile(Dist, 0.9) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
+      yname = "Total.Hours", 
+      treatment = "Tx",
+        first_stage = ~ 1 | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE)  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+
+TEs.strat.far <- data.frame(model$coeftable)[1,]
+
+for (i in 11:19){
+  df.temp <- df.spill3 %>% filter((Dist >= quantile(Dist, 0.9) & Att > 0) | Att == 0 )
+  df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
+  names(df.temp)[1:6] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
+  model <- did2s(
+      data = df.temp , 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ 1 | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE)  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    ) 
+  TEs.strat.far <- rbind(TEs.strat.far, data.frame(model$coeftable)[1,])
+}
+
+model <- did2s(
+      data = df.spill3  %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
+      yname = "Total.Hours", 
+      treatment = "Tx",
+        first_stage = ~ 1 | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE)  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+
+TEs.strat.close <- data.frame(model$coeftable)[1,]
+
+for (i in 11:19){
+  df.temp <- df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0 )
+  df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
+  names(df.temp)[1:6] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
+  model <- did2s(
+      data = df.temp , 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ 1 | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE)  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    ) 
+  TEs.strat.close <- rbind(TEs.strat.close, data.frame(model$coeftable)[1,])
+}
+
+cbind(colnames(df.spill3)[10:19], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[6:10,]
+
+df.spill3  %>% filter(Dist > quantile(Dist, 0.9) ) %>% 
+  filter(Att > 0) %>% 
+  group_by(Tx) %>% 
+  summarise(mean(Total.Hours))
+
+df.spill3 %>% filter(Dist < quantile(Dist, 0.2)) %>% 
+  filter(Att > 0) %>%
+  summarise(mean(Total.Hours))
+
+summary(lm(data = df.spill3 %>% filter(Att > 0 & Dist < 200), Total.Hours ~ Dist))
+
+summary(df.spill3[df.spill3$Att > 0,]$Dist)
+
+### REALLY IMPORTANT BACK OF THE ENVELOP CALCULATION
+
+sum(df.spill3 %>% filter(Att > 0 & Dist < 200 & Dist > 40 & Year == Att - 1) %>% select(Total.Hours))
+
+# Funcationl form of ATT x distance for total hours.... 1.64 - 0.041 * DIST... which integrated from 40km to 200km is about 524 lost hours
+# Divide that by the proceeding line leads to ~ 5% reallocation of resources
 

### 2024-01-01 code/analysis_Redo.Rmd
more updates to stratified analysis access

@@
 
-zp3 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.9)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
+zp3 <- event_study(data = df.spill3 %>% filter((Dist >= quantile(Dist, 0.9) & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
   yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
@@
 
-zp4 <- event_study(data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
+zp4 <- event_study(data = df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
   yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
@@
 
-#ggsave(filename = "Picture13.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = zp, width = 16, height = 9)
 ```

### 2024-01-01 code/analysis_Redo.Rmd
Evalauting the anticpation effects

@@
   select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
-         Total,Qcomp, Altman, #MCD:COM, 
+         Total, Qcomp, Altman, #MCD:COM, 
          #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
@@
 
+did.util
+
 did.util <- did.util[-1,]
@@
 did2s(
-      data = dfc %>% mutate(outcome = log(ngla_revenue / Staff)) %>% filter(outcome < 15 & !is.infinite(outcome)), 
-      yname = "outcome", 
+      data = dfc %>% mutate(outcome = log(ngla_revenue / Staff)) %>% #filter(outcome < 15 & !is.infinite(outcome)) %>% 
+        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)), 
+      yname = "Staff", 
       treatment = "Tx",
@@
   outcomes <- did2s(
-      data = df.temp, 
+      data = df.temp  , 
       yname = "Outcome", 
@@
 df.spill3 <- df.spill2 %>% filter(NumberofPatients > 50 ) %>%
+
   #group_by(Zip) %>% mutate(MaxNum = max(NumberofPatients)) %>% filter(MaxNum > 50) %>%
@@
 
-ev.pop1 <- event_study(data = df.spill3, 
+ev.pop1 <- event_study(data = df.spill3 , 
   yname = "Medicaid", idname = "Zip", tname = "Year", gname = "Att", estimator = "did2s") %>% 

### 2024-01-01 code/analysis_Redo.Rmd
cleaned up code

@@
 
-## Access by quantile
-```{r}
-qnats1 <- seq(0, 0.75, by = 0.25)
-qnats2 <- seq(0.25, 1, by = 0.25)
+## Access shifts by quantiles, event studies
+```{r}
+
+zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.9)), 
+  yname = "NumberofPatients", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
+  filter(abs(term) < 6) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")
+
+zp2 <- event_study(data = df.spill3 %>% filter(Dist == 0), 
+  yname = "NumberofPatients", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
+  filter(abs(term) < 6) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")
+
+zp3 <- event_study(data = df.spill3 %>% filter((Dist >= quantile(Dist, 0.9) & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
+  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
+  filter(abs(term) < 6) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 10% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")
+
+zp4 <- event_study(data = df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
+  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
+  filter(abs(term) < 6) %>% 
+  filter(estimator %in% c("Gardner (2021)")) %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")
+
+zp <- ggarrange(zp1, zp2, zp3, zp4, common.legend = TRUE)
+
+zp <- ggarrange(zp3, zp4, common.legend = TRUE)
+
+did2s(
+      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i])) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
+      yname = "NumberofPatients", 
+      treatment = "Tx",
+        first_stage = ~ 1 | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE)  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+
+#ggsave(filename = "Picture13.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = zp, width = 16, height = 9)
+```
+
+## Acces shifts by quantiles
+```{r}
+qnats1 <- seq(0, 0.833333, by = 0.166666)
+qnats2 <- seq(0.16666, 1, by = 0.1666666)
 
    model.dist.quants <-  did2s(
-      data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)), 
+      data = df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)),
       yname = "NumberofPatients", 
@@
 
-  for (i in 1:4){
+  for (i in 1:6){
       model.dist.quants <-  did2s(
-      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]))%>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
+      data = df.spill3  %>% filter((Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]) & Att > 0 ) | Att == 0)%>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) ,
       yname = "NumberofPatients", 
@@
 
-zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.9)), 
-  yname = "NumberofPatients", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
-  filter(abs(term) < 6) %>% 
-  filter(estimator %in% c("Gardner (2021)")) %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")
-
-zp2 <- event_study(data = df.spill3 %>% filter(Dist == 0), 
-  yname = "NumberofPatients", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
-  filter(abs(term) < 6) %>% 
-  filter(estimator %in% c("Gardner (2021)")) %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")
-
-zp3 <- event_study(data = df.spill3 %>% filter((Dist >= quantile(Dist, 0.9) & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
-  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
-  filter(abs(term) < 6) %>% 
-  filter(estimator %in% c("Gardner (2021)")) %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 10% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")
-
-zp4 <- event_study(data = df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
-  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
-  filter(abs(term) < 6) %>% 
-  filter(estimator %in% c("Gardner (2021)")) %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")
-
-zp <- ggarrange(zp1, zp2, zp3, zp4, common.legend = TRUE)
-
-zp <- ggarrange(zp3, zp4, common.legend = TRUE)
-
-did2s(
-      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i])) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
-      yname = "NumberofPatients", 
-      treatment = "Tx",
-        first_stage = ~ 1 | Zip + Year , 
-        second_stage = ~ i(Tx, ref = FALSE)  ,
-        cluster_var = "Zip",
-      verbose = FALSE
-    )
-
-#ggsave(filename = "Picture13.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = zp, width = 16, height = 9)
+zp.pats <- tes[-1,] %>% 
+  cbind(Quantile = 1:6) %>% 
+  ggplot(aes(x = Quantile, y = Estimate)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=Estimate-1.96*Std..Error, ymax=Estimate+1.96*Std..Error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Effects on Total Patients, by Quantile from Competitive Shock")+ xlab("Quantile of Zip Codes by Distance from Competitive Shock, adjusting for 1 year anticipation") + ylab("Effect Size")
+
+zp.pats
+
+#ggsave(filename = "Picture13pats.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = zp.pats, width = 16, height = 9)
 ```
@@
 model <- did2s(
-      data = df.spill3  %>% filter((Dist >= quantile(Dist, 0.9) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
+      data = df.spill3  %>% filter((Dist >= quantile(Dist, 0.9) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
+        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))  , 
       yname = "Total.Hours", 
@@
 for (i in 11:19){
-  df.temp <- df.spill3 %>% filter((Dist >= quantile(Dist, 0.9) & Att > 0) | Att == 0 )
+  df.temp <- df.spill3 %>% filter((Dist >= quantile(Dist, 0.9) & Att > 0) | Att == 0 )%>% 
+        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
   df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
@@
 model <- did2s(
-      data = df.spill3  %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
+      data = df.spill3  %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
+        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))  , 
       yname = "Total.Hours", 
@@
 for (i in 11:19){
-  df.temp <- df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0 )
+  df.temp <- df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% 
+        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
   df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
@@
 summary(df.spill3[df.spill3$Att > 0,]$Dist)
+
+quantile(df.spill3[df.spill3$Att > 0,]$Dist, 0.17)
 

### 2024-01-02 code/analysis_Redo.Rmd
cleaned up filtering in zip code analysis

@@
 
-df.spill3 <- df.spill2 %>% filter(NumberofPatients > 50 ) %>%
+df.spill3 <- df.spill2 %>% #filter(NumberofPatients > 50 ) %>%
+
+  # inner_join(df.spill2 %>% 
+  # group_by(Zip, `BHCMIS ID`) %>% 
+  # summarise(maxmax = min(NumberofPatients)) %>% 
+  #   filter(maxmax > 100), by = c("Zip","BHCMIS ID"))  %>%
+
+  inner_join(df.spill2 %>% 
+  group_by(Zip, `BHCMIS ID`) %>% 
+  summarise(counts = n()) %>% 
+    filter(counts == 10), by = c("Zip","BHCMIS ID"))  %>%
 
@@
 
-zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.9)), 
+zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.87)), 
   yname = "NumberofPatients", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
@@
 
-zp3 <- event_study(data = df.spill3 %>% filter((Dist >= quantile(Dist, 0.9) & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
+zp3 <- event_study(data = df.spill3 %>% filter((Dist > quantile(Dist, 0.87) & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
   yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 10% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 13% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")
 
@@
 
+zp
+
+# did2s(
+#       data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i])) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
+#       yname = "NumberofPatients", 
+#       treatment = "Tx",
+#         first_stage = ~ 1 | Zip + Year , 
+#         second_stage = ~ i(Tx, ref = FALSE)  ,
+#         cluster_var = "Zip",
+#       verbose = FALSE
+#     )
+
 did2s(
-      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i])) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
-      yname = "NumberofPatients", 
+      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.87) & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
+      yname = "Total.Hours", 
       treatment = "Tx",
@@
 ```{r}
-qnats1 <- seq(0, 0.833333, by = 0.166666)
-qnats2 <- seq(0.16666, 1, by = 0.1666666)
+qnats1 <- seq(0, 0.875, by = 0.125)
+qnats2 <- seq(0.125, 1, by = 0.125)
+
+qnats1 <- seq(0, 5/6, by = 1/6)
+qnats2 <- seq(1/6, 1, by = 1/6)
 
    model.dist.quants <-  did2s(
-      data = df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)),
+      data = df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year & Att > 0, 1, Tx)),
       yname = "NumberofPatients", 
@@
       model.dist.quants <-  did2s(
-      data = df.spill3  %>% filter((Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]) & Att > 0 ) | Att == 0)%>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) ,
+      data = df.spill3  %>% filter((Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]) & Att > 0 ) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year & Att > 0 , 1, Tx)) ,
       yname = "NumberofPatients", 
@@
 
-zp.pats <- tes[-1,] %>% 
-  cbind(Quantile = 1:6) %>% 
+zp.pats <- tes %>% #tes[-1,] %>% 
+  cbind(Quantile = 1:8) %>% 
   ggplot(aes(x = Quantile, y = Estimate)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=Estimate-1.96*Std..Error, ymax=Estimate+1.96*Std..Error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
@@
 model <- did2s(
-      data = df.spill3  %>% filter((Dist >= quantile(Dist, 0.9) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
+      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.87) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
         mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))  , 
@@
 for (i in 11:19){
-  df.temp <- df.spill3 %>% filter((Dist >= quantile(Dist, 0.9) & Att > 0) | Att == 0 )%>% 
+  df.temp <- df.spill3 %>% filter((Dist > quantile(Dist, 0.87) & Att > 0) | Att == 0 )%>% 
         mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
@@
 
-sum(df.spill3 %>% filter(Att > 0 & Dist < 200 & Dist > 40 & Year == Att - 1) %>% select(Total.Hours))
+sum(df.spill3 %>% filter(Att > 0 & Dist < 200 & Dist > 62 & Year == Att - 1) %>% select(Total.Hours))
 
@@
 # Divide that by the proceeding line leads to ~ 5% reallocation of resources
+## UPDATED FORM : 3.37 - 0.054x from 62km through 200 is 7%
 

### 2024-01-03 code/analysis_Redo.Rmd
balanced panel only

@@
     filter(counts == 10), by = c("Zip","BHCMIS ID"))  %>%
+  filter(Att == 0 | Att > 2013) %>%
 
@@
 
-zp.pats <- tes %>% #tes[-1,] %>% 
-  cbind(Quantile = 1:8) %>% 
+zp.pats <- tes[-1,] %>% 
+  cbind(Quantile = 1:6) %>% 
   ggplot(aes(x = Quantile, y = Estimate)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=Estimate-1.96*Std..Error, ymax=Estimate+1.96*Std..Error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
@@
 zp.pats
+
+quantile(df.spill3[df.spill3$Att > 0,]$Dist, 1/3)
+quantile(df.spill3[df.spill3$Att > 0,]$Dist, 2/3)
 

### 2024-01-04 code/analysis_Redo.Rmd
fixing descriptive figures, updating plots

@@
   ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
-  geom_point() + geom_line() + theme_tufte_revised() + ggtitle("FQHCs by Number of Rival Clinics") + 
+  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Rival Clinics") + 
   geom_dl(label=c(rep("0 Competitors", 25), rep("1 Competitor", 25), rep("2 Competitors", 25), rep("3+ Competitors", 25)), 
-          method = list("last.points", hjust = 1, vjust = c(3, 3.5, 4, -2), cex = 0.75), inherit.aes=T ) + 
+          method = list("last.points", hjust = 1, vjust = c(3, 3.5, 4, -2), cex = 1), inherit.aes=T ) + 
   guides(colour = "none")
@@
   ggplot(aes(x = Year, y = Zips, group = Counts.f, color = Counts.f)) + 
-  geom_point() + geom_line() + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
-  geom_dl(label=c(rep("1 Site", 25), rep("2+ Sites", 25)), method = list("last.points", hjust = 1, vjust = -1, cex = 0.75), inherit.aes=T ) + 
+  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
+  geom_dl(label=c(rep("1 Site", 25), rep("2+ Sites", 25)), method = list("last.points", hjust = 1, vjust = -1, cex = 1), inherit.aes=T ) + 
   guides(colour = "none") + ylim(0, 4000)
@@
 
+p.desc
 ```
@@
          dm.rate = dm.rate * 100) %>% 
+  #mutate(Qcomp = (htn.rate + dm.rate) / 2) %>% 
   select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
@@
   filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
@@
   filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
@@
   filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, ncol = 1 )
@@
 
-#ggsave(filename = "Picture3a.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 16, height = 9)
+ggsave(filename = "Picture3a.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 9, height =16)
 
@@
   filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, ncol = 3 )
@@
   outcomes <- did2s(
-      data = df.temp  , 
+      data = df.temp %>% mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))  , 
       yname = "Outcome", 
@@
 mean.nas<- function(x){ mean(x, na.rm = TRUE)}
+mean.inf<- function(x){ mean(ifelse(is.infinite(x), NA, x), na.rm = TRUE)}
 
@@
   select(Staff:logPatsPerStaff) %>% 
-  summarise_all(mean.nas) %>% 
+  summarise_all(mean.inf) %>% 
   # summarise(Total = mean(Total, na.rm = TRUE), 
@@
 
+TEs
+TEs_Dist
+
 ```
@@
 
-cbind(colnames(df.spill3)[10:19], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[6:10,]
+cbind(colnames(df.spill3)[10:19], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[c(6:10, 1:2),]
 
@@
 ## All Hypotheses tested
-bhoch <- data.frame(rbind(did.core, did.select.stint, did.select.payer, did.rival)) %>% 
+bhoch <- data.frame(rbind(did.core, did.select.stint, did.select.payer, did.util)) %>% 
   rbind(TEs) %>% rbind(TEs_Dist) %>% 
   arrange(`Pr...t..`) %>% 
-  cbind(c(1:43) / 43 * 0.1) %>% 
+  cbind(c(1:37) / 37 * 0.1) %>% 
   mutate(Row = row_number()) %>% 
   ggplot(aes(x = Row, y = `Pr...t..`)) + geom_point() + 
-  ylab("p-values") + xlab("Significance Rank") + geom_abline(slope = 1/43 * 0.1, intercept = 0, color="red", linetype="dashed", alpha=.5) + theme_minimal()
+  ylab("p-values") + xlab("Significance Rank") + geom_abline(slope = 1/37 * 0.1, intercept = 0, color="red", linetype="dashed", alpha=.5) + theme_minimal()
 

### 2024-01-04 code/analysis_Redo.Rmd
testing other quality effects

@@
          dm.rate = dm.rate * 100) %>% 
-  #mutate(Qcomp = (htn.rate + dm.rate) / 2) %>% 
+  #mutate(Qcomp = (crc.rate + pap.rate + adultbmi.rate + childbmi.rate) / 4) %>% 
   select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 

### 2024-01-14 code/analysis_Redo.Rmd
cleaning up the descriptive figures

@@
   geom_dl(label=c(rep("0 Competitors", 25), rep("1 Competitor", 25), rep("2 Competitors", 25), rep("3+ Competitors", 25)), 
-          method = list("last.points", hjust = 1, vjust = c(3, 3.5, 4, -2), cex = 1), inherit.aes=T ) + 
+          method = list("last.points", hjust = 1, vjust = c(3, 3.5, 4, -2), cex = 1.5), inherit.aes=T ) + 
   guides(colour = "none")
@@
   geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
-  geom_dl(label=c(rep("1 Site", 25), rep("2+ Sites", 25)), method = list("last.points", hjust = 1, vjust = -1, cex = 1), inherit.aes=T ) + 
+  geom_dl(label=c(rep("1 Site", 25), rep("2+ Sites", 25)), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
   guides(colour = "none") + ylim(0, 4000)
@@
   theme_tufte_revised() + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Effects on Total Patients, by Quantile from Competitive Shock")+ xlab("Quantile of Zip Codes by Distance from Competitive Shock, adjusting for 1 year anticipation") + ylab("Effect Size")
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Effects on Total Patients, by Quantile from Competitive Shock")+ xlab("Quantile of Zip Codes by Distance from Competitive Shock, adjusting for 1 year anticipation") + ylab("Effect Estimate")
 

### 2024-01-17 code/analysis_Redo.Rmd
adding names to descriptive figures

@@
   ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
-  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Rival Clinics") + 
+  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
   geom_dl(label=c(rep("0 Competitors", 25), rep("1 Competitor", 25), rep("2 Competitors", 25), rep("3+ Competitors", 25)), 
@@
 ggsave(filename = "Picture14.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p14, width = 17, height = 9)
+
+ event_study(data = dfc %>% mutate(outcome = ngla_revenue / Total),
+  yname = "outcome", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
+  #mutate(estimate = exp(estimate), std.error = exp(std.error)) %>% 
+  filter(abs(term) <= 5) %>%
+  filter(estimator == "Gardner (2021)") %>%
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold'))+ 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Event Study - Effects of Competitive Shock on log Ratio of Patients Per Staff Member") + xlab("Year Relative to Competitive Shock") + ylab("log Patients")
 

### 2024-01-23 code/analysis_Redo.Rmd
update figures with pooled estimates

@@
 
-p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))
+p.desc <- annotate_figure(p.desc, fig.lab = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))
 
@@
 
+label1 <- 'beta[pooled] == "2.24**"'
+label2 <- 'beta[pooled] == "-0.21**"'
+
 p0.simple <- ggarrange(
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points") +
+  annotate("text", x=2, y=-2.2, label= label1, parse = TRUE, size = unit(10, "pt")), 
 event_study(data = df.core, 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Altman's Z Score") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, ncol = 2, legend = F)
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Altman's Z Score") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units") +
+  annotate("text", x=2, y=0.4, label= label2, parse = TRUE, size = unit(10, "pt")), common.legend = TRUE, ncol = 2, legend = F) 
 p0.simple

### 2024-01-24 code/analysis_Redo.Rmd
cleaning up the figures

--- 2024-01-17 code/analysis_Redo.Rmd
@@
           method = list("last.points", hjust = 1, vjust = c(3, 3.5, 4, -2), cex = 1.5), inherit.aes=T ) + 
-  guides(colour = "none")
+  guides(colour = "none") +theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=14,face="bold"))
 
@@
   geom_dl(label=c(rep("1 Site", 25), rep("2+ Sites", 25)), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
-  guides(colour = "none") + ylim(0, 4000)
+  guides(colour = "none") + ylim(0, 4000) +theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=14,face="bold"))
 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points") +
+  annotate("text", x=2, y=-2.2, label= label1, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=14,face="bold")), 
 event_study(data = df.core, 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Altman's Z Score") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, ncol = 2, legend = F)
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Altman's Z Score") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units") +
+  annotate("text", x=2, y=0.4, label= label2, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=14,face="bold")), common.legend = TRUE, ncol = 2, legend = F) 
 p0.simple
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold'))+ 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Complexity") + xlab("Year Relative to Competitive Shock")  + ylab("Prevalence"), 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Complexity") + xlab("Year Relative to Competitive Shock")  + ylab("Prevalence")+theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=14,face="bold")), 
 event_study(data = df.select.stint, 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold'))+ 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Intensity") + xlab("Year Relative to Competitive Shock") + ylab("Visits"), common.legend = TRUE, legend = F) 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Intensity") + xlab("Year Relative to Competitive Shock") + ylab("Visits")+theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=14,face="bold")), common.legend = TRUE, legend = F) 
 p2
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 13% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 13% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")+theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=14,face="bold"))
 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")+theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=14,face="bold"))
 

### 2024-08-26 code/manuscript_data_cleaning.Rmd
larger data file, more detailed analysis, new temp files

--- 2023-08-29 code/data_cleaning_longer.Rmd
@@
 
-included.years <- 2010:2021
-included.treat <- 2013:2021
+included.years <- 2010:2023
+included.treat <- 2013:2023
 
@@
 ## Zips
-locs <- paste("/Users/jhm65/Dropbox/Git/UDS/UDS-", c(2012:2021), "-Full-Dataset.xlsx", sep = "")
+locs <- paste("/Users/markow/Dropbox/Git/UDS/UDS-", c(2012:2023), "-Full-Dataset.xlsx", sep = "")
 uds.zip <- read_excel(locs[1], sheet = "HealthCenterZipCodes")[,c(1:4, 6, 5)]
@@
 uds.zip <- uds.zip[uds.zip$ZipCodeType == "ZipCode",]
-
-uds.zip
 
@@
 ## Sites
-locs <- paste("/Users/jhm65/Dropbox/Git/UDS/UDS-", c(2012:2021), "-Full-Dataset.xlsx", sep = "")
+locs <- paste("/Users/markow/Dropbox/Git/UDS/UDS-", c(2012:2023), "-Full-Dataset.xlsx", sep = "")
 
@@
 
-for(i in 4:(length(locs)-1)){
+for(i in 4:(length(locs)-3)){
   uds.sites <- rbind(uds.sites, read_excel(locs[i], sheet = "HealthCenterSiteInfo") %>% 
@@
 
+## 2021
 temp.sites <- read_excel(locs[i+1], sheet = "HealthCenterSiteInfo" )%>% 
@@
 
-uds.sites.old <- read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Sites.csv", colClasses = "character") %>% 
+## 2022
+temp.sites <- read_excel(locs[i+2], sheet = "HealthCenterSiteInfo" )%>% 
+  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>%
+  mutate(Year = 2022)
+colnames(temp.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")
+
+uds.sites <- rbind(uds.sites, temp.sites)
+
+## 2023
+temp.sites <- read_excel(locs[i+3], sheet = "HealthCenterSiteInfo" )%>% 
+  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>%
+  mutate(Year = 2023)
+colnames(temp.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")
+
+uds.sites <- rbind(uds.sites, temp.sites)
+
+uds.sites.old <- read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Sites.csv", colClasses = "character") %>% 
   mutate(Year = as.numeric(Year))
@@
 
-#write.csv(x = uds.sites.full, file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Sites96to21.csv")
+#write.csv(x = uds.sites.full, file = "//Users/markow/Dropbox/Git/APMs/data_processed/Sites96to21.csv")
+
+uds.sites %>% 
+  filter(Year %in% c(2021, 2022, 2023)) %>% 
+  arrange(`Grant Number`, Year)
 
@@
 
-for (g in 1:13){
+for (g in 1:16){
   g
@@
 coded <- rbind(coded, 
-               geo(street = tbcoded[c(14001:14253),]$`Site Street Address`, 
-             city = tbcoded[c(14001:14253),]$`Site City`, 
-             state = tbcoded[c(14001:14253),]$`Site State`, 
+               geo(street = tbcoded[c(17001:17152),]$`Site Street Address`, 
+             city = tbcoded[c(17001:17152),]$`Site City`, 
+             state = tbcoded[c(17001:17152),]$`Site State`, 
              method = "census", 
@@
 
-chc <- read.csv("//Users/jhm65/Dropbox/Git/Competition/data_raw/chc.csv")
+chc <- read.csv("//Users/markow/Dropbox/Git/Competition/data_raw/chc.csv")
 
@@
 
-for (i in 1:10){
+for (i in 1:11){
   census <- rbind(census, get_acs(geography = "zcta", survey = "acs5",
@@
 census %>% 
-  filter(YEAR == 2020) %>% 
+  filter(YEAR == 2022) %>% 
   select(ZipCode) %>% 
@@
 ```{r}
-uds.cw <- read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_CW.csv", colClasses = "character") %>% 
+uds.cw <- read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_CW.csv", colClasses = "character") %>% 
   mutate(link.ID = ifelse(is.na(ModernGranteeID) & !is.na(LongGrantID) & Year != 2010, LongGrantID, 
@@
 uds.cw %>% 
-  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
+  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
   arrange(BHCMIS.ID, Year) %>% 
@@
 
-uds.3B.2012 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
-uds.3B.2013 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
-
-uds.3B.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
-uds.3B.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table3B", skip = 2) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
-uds.3B.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-
-uds.3B.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-uds.3B.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-uds.3B.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-
-uds.3B.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-uds.3B.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
+uds.3B.2012 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
+uds.3B.2013 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
+
+uds.3B.2014 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
+uds.3B.2015 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table3B", skip = 2) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
+uds.3B.2016 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
+
+uds.3B.2017 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
+uds.3B.2018 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
+uds.3B.2019 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
+
+uds.3B.2020 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
+uds.3B.2021 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
+uds.3B.2022 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2022-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
+uds.3B.2023 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2023-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
 
@@
                   cbind(Year = 2020, uds.3B.2020),
-                  cbind(Year = 2021, uds.3B.2021)) %>%
+                  cbind(Year = 2021, uds.3B.2021),
+
+                  cbind(Year = 2022, uds.3B.2022),
+                  cbind(Year = 2023, uds.3B.2023)) %>%
 
@@
   uds.cw %>% 
-  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
+  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
   arrange(BHCMIS.ID, Year) %>% 
@@
     uds.cw %>% 
-  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
+  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
   arrange(BHCMIS.ID, Year) %>% 
@@
 # Table 4
-uds.4.2012 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-uds.4.2013 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-
-uds.4.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-uds.4.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table4", skip = 2) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-uds.4.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-
-uds.4.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-uds.4.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-uds.4.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-
-uds.4.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-uds.4.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
+uds.4.2012 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
+uds.4.2013 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
+
+uds.4.2014 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
+uds.4.2015 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table4", skip = 2) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
+uds.4.2016 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
+
+uds.4.2017 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
+uds.4.2018 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
+uds.4.2019 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
+
+uds.4.2020 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
+uds.4.2021 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
+uds.4.2022 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2022-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
+uds.4.2023 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2023-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
 
@@
                   cbind(Year = 2020, uds.4.2020),
-                  cbind(Year = 2021, uds.4.2021)) %>%
+                  cbind(Year = 2021, uds.4.2021),
+                  cbind(Year = 2022, uds.4.2022),
+                  cbind(Year = 2023, uds.4.2023)) %>%
 
@@
 uds.cw %>% 
-  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table4.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
+  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table4.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
   filter(Year %in% c(2007, 2011)) %>% 
@@
 uds.cw %>% 
-  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table4.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
+  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table4.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
   filter(Year %in% c(2008:2010)) %>% 
@@
 uds.6a.2011andBefore <- uds.cw %>% 
-  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table6A.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
+  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table6A.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
   select(BHCMIS.ID, Year, T6A_L10_CA:T6A_L26D_CB) %>% 
@@
 
-uds.6a.2012 <- cbind(Year = 2012, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper)
-uds.6a.2013 <- cbind(Year = 2013, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper)
-
-uds.6a.2014 <- cbind(Year = 2014, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper)
-uds.6a.2015 <- cbind(Year = 2015, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table6A", skip = 2)) %>% rename_all(.funs = toupper)
-uds.6a.2016 <- cbind(Year = 2016, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
-
-uds.6a.2017 <- cbind(Year = 2017, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
-uds.6a.2018 <- cbind(Year = 2018, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
-uds.6a.2019 <- cbind(Year = 2019, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
-
-uds.6a.2020 <- cbind(Year = 2020, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
-uds.6a.2021 <- cbind(Year = 2021, read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper) %>% filter(!is.na(BHCMISID))
+uds.6a.2012 <- cbind(Year = 2012, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper)
+uds.6a.2013 <- cbind(Year = 2013, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper)
+
+uds.6a.2014 <- cbind(Year = 2014, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper)
+uds.6a.2015 <- cbind(Year = 2015, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table6A", skip = 2)) %>% rename_all(.funs = toupper)
+uds.6a.2016 <- cbind(Year = 2016, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
+
+uds.6a.2017 <- cbind(Year = 2017, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
+uds.6a.2018 <- cbind(Year = 2018, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
+uds.6a.2019 <- cbind(Year = 2019, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
+
+uds.6a.2020 <- cbind(Year = 2020, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
+uds.6a.2021 <- cbind(Year = 2021, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper) %>% filter(!is.na(BHCMISID))
+
+uds.6a.2022 <- cbind(Year = 2022, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2022-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper) %>% filter(!is.na(BHCMISID))
+uds.6a.2023 <- cbind(Year = 2023, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2023-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper) %>% filter(!is.na(BHCMISID))
 
@@
 uds.6a.2021[,-c(1:3)] <- data.frame(sapply(uds.6a.2021[,-c(1:3)], as.numeric))
+uds.6a.2022[,-c(1:3)] <- data.frame(sapply(uds.6a.2022[,-c(1:3)], as.numeric))
+uds.6a.2023[,-c(1:3)] <- data.frame(sapply(uds.6a.2023[,-c(1:3)], as.numeric))
 
 uds.6a <- bind_rows(uds.6a.2012, uds.6a.2013, uds.6a.2014,
-      uds.6a.2015, uds.6a.2016, uds.6a.2017, uds.6a.2018, uds.6a.2019, uds.6a.2020, uds.6a.2021, uds.6a.2011andBefore) %>% 
+      uds.6a.2015, uds.6a.2016, uds.6a.2017, uds.6a.2018, uds.6a.2019, uds.6a.2020, uds.6a.2021, uds.6a.2022, uds.6a.2023, uds.6a.2011andBefore) %>% 
   arrange(BHCMISID, YEAR) %>% 
@@
 
-uds.6b.2012 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2013 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
-
-uds.6b.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 1) 
-uds.6b.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
-
-uds.6b.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
-
-uds.6b.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
+uds.6b.2012 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
+uds.6b.2013 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
+
+uds.6b.2014 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
+uds.6b.2015 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 1) 
+uds.6b.2016 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
+
+uds.6b.2017 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
+uds.6b.2018 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
+uds.6b.2019 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
+
+uds.6b.2020 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
+uds.6b.2021 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
+uds.6b.2022 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2022-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
+uds.6b.2023 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2023-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
 
@@
   cbind(Year = 2020, cbind(uds.6b.2020[,c(1:8, 27:29, 12:17)], NA, NA, NA, uds.6b.2020[,c(21:26)]) %>% setNames(uds.6b.names)),
-  cbind(Year = 2021, cbind(uds.6b.2021[,c(1:8, 27:29, 12:17)], NA, NA, NA, uds.6b.2021[,c(21:26)]) %>% setNames(uds.6b.names))) %>% 
+  cbind(Year = 2021, cbind(uds.6b.2021[,c(1:8, 27:29, 12:17)], NA, NA, NA, uds.6b.2021[,c(21:26)]) %>% setNames(uds.6b.names)),
+
+  cbind(Year = 2022, cbind(uds.6b.2022[,c(1:8, 27:29, 12:17)], NA, NA, NA, uds.6b.2022[,c(21:26)]) %>% setNames(uds.6b.names)),
+  cbind(Year = 2023, cbind(uds.6b.2023[,c(1:8, 27:29, 12:17)], NA, NA, NA, uds.6b.2023[,c(21:26)]) %>% setNames(uds.6b.names))) %>%
+
   mutate(imm.rate = as.numeric(Imm.Num) / as.numeric(imm.denom), 
@@
   bind_rows(uds.cw %>% 
-  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table6B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
+  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table6B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
   filter(Year != 2008) %>% 
@@
 ```{r}
-vec.years <- 2012:2021
+vec.years <- 2012:2023
 vec.skips <- rep(0, length(vec.years)) 
@@
 vec.skips[c(5,6,7,8,9)] <- 1
-vec.files <- paste("//Users/jhm65/Dropbox/Git/UDS/UDS-",vec.years, "-Full-Dataset.xlsx", sep = "")
+vec.files <- paste("//Users/markow/Dropbox/Git/UDS/UDS-",vec.years, "-Full-Dataset.xlsx", sep = "")
 
 uds.quality.sampling.v.ehr <- uds.cw %>% 
-  inner_join(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table6B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
+  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table6B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
   filter(Year != 2008) %>% 
@@
 
-uds.7.2012 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
-uds.7.2013 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0)
-
-uds.7.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
-uds.7.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 1) 
-uds.7.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0)
-
-uds.7.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
-uds.7.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
-uds.7.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0)
-
-uds.7.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
-uds.7.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 1)
+uds.7.2012 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
+uds.7.2013 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0)
+
+uds.7.2014 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
+uds.7.2015 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 1) 
+uds.7.2016 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0)
+
+uds.7.2017 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
+uds.7.2018 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
+uds.7.2019 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0)
+
+uds.7.2020 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
+uds.7.2021 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 1) 
+uds.7.2022 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2022-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 1) 
+uds.7.2023 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2023-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 1)
 
@@
   cbind(Year = 2020, uds.7.2020[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
-  cbind(Year = 2021, uds.7.2021[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled)))) %>% 
+  cbind(Year = 2021, uds.7.2021[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
+  cbind(Year = 2022, uds.7.2022[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
+  cbind(Year = 2023, uds.7.2023[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled)))) %>% 
   mutate(htn.rate = as.numeric(htn.control) / as.numeric(htn.total), 
@@
 
-  bind_rows(read.csv(file = "//Users/jhm65/Dropbox/Git/APMs/data_processed/Merged_Table7clin.csv") %>% 
+  bind_rows(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table7clin.csv") %>% 
   select(Year, ModernGranteeID:dm.controlled) %>% 
@@
 ```{r}
-cw <- read_excel("/Users/jhm65/Dropbox/Git/Data/UDS-990 Crosswalk.xlsx")
-
-fins.revenue.expenses <- read.csv("//Users/jhm65/Dropbox/Git/Data/FQHC_Revenue_vs_Expenses.csv", header = TRUE)
+cw <- read_excel("/Users/markow/Dropbox/Git/Data/UDS-990 Crosswalk.xlsx")
+
+fins.revenue.expenses <- read.csv("//Users/markow/Dropbox/Git/Data/FQHC_Revenue_vs_Expenses.csv", header = TRUE)
 names(fins.revenue.expenses) <- gsub("^X\\.", "", names(fins.revenue.expenses))
@@
 
-staffing <- read.csv("/Users/jhm65/Dropbox/Git/Data/FQHC_Staffing.csv")
-assliabs <- read.csv("/Users/jhm65/Dropbox/Git/Data/FQHC_Assets_and_Liabilities.csv")
+staffing <- read.csv("/Users/markow/Dropbox/Git/Data/FQHC_Staffing.csv")
+assliabs <- read.csv("/Users/markow/Dropbox/Git/Data/FQHC_Assets_and_Liabilities.csv")
 
@@
 
-apm.history <- read_excel("/Users/jhm65/Dropbox/Git/APMs/data_raw/APM_History.xlsx") %>%
+apm.history <- read_excel("/Users/markow/Dropbox/Git/APMs/data_raw/APM_History.xlsx") %>%
  mutate(Class = ifelse(is.na(Year), "0 - Control", Classification))
@@
   group_by(`BHCMIS ID`) %>% 
-  mutate(Att = ifelse(Att < 2022, Att, 0)) %>% 
+  mutate(Att = ifelse(Att < 2024, Att, 0)) %>% 
   ungroup() %>% 
@@
 ```{r}
-# write_csv(dfc, file = "/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
-# write.csv(uds.sites.full, file = "/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv")
-```
+# write_csv(dfc, file = "/Users/markow/Dropbox/Git/Competition/data_processed/manuscript_analyticalfile.csv")
+# write.csv(uds.sites.full, file = "/Users/markow/Dropbox/Git/Competition/data_processed/manuscript_sites_geocoded.csv")
+```

### 2024-08-26 code/analysis_Redo.Rmd
begin updating to work on new storage

@@
 ```{r}
-dfc <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
-uds.sites.full <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
+dfc <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
+uds.sites.full <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
   mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 4, Access))
@@
 
-ggsave(filename = "Picture1.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 11, height = 15)
+#ggsave(filename = "Picture1.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 11, height = 15)
 
@@
 
-ggsave(filename = "Picture1h.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 16, height = 9)
+#ggsave(filename = "Picture1h.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 16, height = 9)
 
@@
 
-ggsave(filename = "Picture3a.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 9, height =16)
+#ggsave(filename = "Picture3a.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 9, height =16)
 
@@
 
-ggsave(filename = "Picture3ah.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 17, height = 9)
+#ggsave(filename = "Picture3ah.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 17, height = 9)
 
@@
 
-ggsave(filename = "Picture3ahSimple.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0.simple, width = 17, height = 9)
+#ggsave(filename = "Picture3ahSimple.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0.simple, width = 17, height = 9)
 

### 2024-08-26 code/manuscript_analysis.Rmd
stick to the original sample, just reconfigure visuals to tell story

--- 2024-08-26 code/analysis_Redo.Rmd
@@
 dfc %>% 
-  filter(Year == 2010) %>% 
+  filter(Year == 2011) %>% 
   mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
@@
   geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
-  geom_dl(label=c(rep("0 Competitors", 25), rep("1 Competitor", 25), rep("2 Competitors", 25), rep("3+ Competitors", 25)), 
+  geom_dl(label=c(rep("0 Competitors", length(unique(p$Year))), rep("1 Competitor", length(unique(p$Year))), rep("2 Competitors", length(unique(p$Year))), rep("3+ Competitors", length(unique(p$Year)))),
           method = list("last.points", hjust = 1, vjust = c(3, 3.5, 4, -2), cex = 1.5), inherit.aes=T ) + 
@@
   geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
-  geom_dl(label=c(rep("1 Site", 25), rep("2+ Sites", 25)), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
+  geom_dl(label=c(rep("1 Site", length(unique(p$Year))), rep("2+ Sites", length(unique(p$Year)))), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
   guides(colour = "none") + ylim(0, 4000) +theme(axis.text=element_text(size=12),
@@
 p.desc
+
 ```
@@
 
-ggsave(filename = "Picture14.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p14, width = 17, height = 9)
+#ggsave(filename = "Picture14.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p14, width = 17, height = 9)
 
@@
 
-ggsave(filename = "Picture4.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p2, width = 17, height = 9)
+#ggsave(filename = "Picture4.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p2, width = 17, height = 9)
 
@@
 ## Read in Centroid Data
-zip.centroids <- read.csv("/Users/jhm65/Dropbox/Git/Data/ZIP_Code_Population_Weighted_Centroids.csv") %>% 
+zip.centroids <- read.csv("/Users/markow/Dropbox/Git/Data/ZIP_Code_Population_Weighted_Centroids.csv") %>% 
   mutate(ZipCode = str_pad(STD_ZIP5, 5, pad = "0")) %>% 
@@
 
-## Rival selecting where to put new site, takes 30+ minutes to work
+## Rival selecting where to put new site, takes 15+ minutes to work
 

### 2024-08-26 code/manuscript_data_cleaning.Rmd
stick to the original sample, just reconfigure visuals to tell story

@@
 
+ included.years <- 2014:2023
+ included.treat <- 2016:2023
+
 df.comp <- uds.covariates %>% 
@@
   pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
-  filter(`2010` == 1 & `2011` == 1) %>%  #  & `2012` == 1 & `2013` == 1 & `2014` == 1 & `2015` == 1 & `2016` == 1) %>%   
-  #filter(`2014` == 1 & `2015` == 1) %>%  
+  #filter(`2011` == 1 & `2012` == 1 ) %>%  #  & `2012` == 1 & `2013` == 1 & `2014` == 1 & `2015` == 1 & `2016` == 1) %>%   
+  filter(`2014` == 1 & `2015` == 1) %>%  
   #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
   #filter(is.na(NewClinicID)) %>%
-  select(`BHCMIS ID`:`2021`) %>% 
-  pivot_longer(cols = c(`2010`:`2021`)) %>% 
+  select(`BHCMIS ID`:`2023`) %>% 
+  pivot_longer(cols = c(`2014`:`2023`)) %>% 
   group_by(`BHCMIS ID`) %>% 
@@
   group_by(`BHCMIS ID`) %>% 
-  mutate(Att = ifelse(Att < 2024, Att, 0)) %>% 
+  mutate(Att = ifelse(Att < max(included.treat)+1, Att, 0)) %>% 
   ungroup() %>% 
@@
         summarise(YearFirstInZip = min(Year)) %>% 
-        filter(YearFirstInZip %notin% c(2010)) %>% 
+        filter(YearFirstInZip %notin% min(included.years)) %>% 
         select(`BHCMIS ID`, YearFirstInZip) %>% 
@@
 
-vec.atts <- rep(c(2012:2021), (table(comp.initial$Att) / 12)[-1])
+vec.atts <- rep(included.treat, (table(comp.initial$Att) / 12)[-1])
 
@@
 # write.csv(uds.sites.full, file = "/Users/markow/Dropbox/Git/Competition/data_processed/manuscript_sites_geocoded.csv")
-```
+
+```

### 2024-08-26 code/manuscript_analysis.Rmd
NBew Table 1

@@
          htn.rate = htn.rate * 100, 
-         dm.rate = dm.rate * 100) %>% 
+         dm.rate = dm.rate * 100, 
+         logPatsPerStaff = log(Total / Staff), 
+         logPatsPerStaff = ifelse(log(Total / Staff) > quantile(logPatsPerStaff, 0.975, na.rm = T), quantile(logPatsPerStaff, 0.975, na.rm = T), 
+                                  ifelse(log(Total / Staff) < quantile(logPatsPerStaff, 0.025, na.rm = T), quantile(logPatsPerStaff, 0.025, na.rm = T), log(Total / Staff)))) %>% 
   #mutate(Qcomp = (crc.rate + pap.rate + adultbmi.rate + childbmi.rate) / 4) %>% 
   select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
-         Total, Qcomp, Altman, #MCD:COM, 
+         Qcomp, Altman, logPatsPerStaff, #MCD:COM, 
          #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
@@
   group_by(Post, Treated) %>% 
-  select(Total:Altman) %>% 
+  select(Qcomp:logPatsPerStaff) %>% 
   summarise_all(mean.nas) %>% 
@@
   #           Finances = mean(Altman, na.rm = TRUE)) %>% 
-  pivot_longer(cols = Total:Altman) %>% 
+  pivot_longer(cols = Qcomp:logPatsPerStaff) %>% 
   mutate(value = round(value, 2)) %>% 
-  filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
+  filter(name %in% c("Qcomp", "Altman","logPatsPerStaff")) %>% 
   pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
   mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
-  cbind(did.core, NiceName = c("Total","Quality Composite","Altman's Z")) %>% 
+  cbind(did.core, NiceName = c("Quality of Care","Financial Resilience","Operational Efficiency")) %>% 
    select(NiceName, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
@@
   event_study(data = df.core, 
-  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
   filter(abs(term) <= 5) %>% 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
+event_study(data = df.core, 
+  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), 
+event_study(data = df.core, 
+  yname = "logPatsPerStaff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  filter(abs(term) <= 5) %>% 
+  filter(estimator == "Gardner (2021)") %>% 
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("log Ratio Patients-to-Staff"), common.legend = TRUE, ncol = 1 )
+p0
+
+summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Qcomp ~ Treated*year.rel))$coeff[4,]
+summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Altman ~ Treated*year.rel))$coeff[4,]
+summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)) %>% filter(!is.infinite(logPatsPerStaff)), logPatsPerStaff ~ Treated*year.rel))$coeff[4,]
+
+#ggsave(filename = "Picture3a.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 9, height =16)
+
+p0 <- ggarrange(
   event_study(data = df.core, 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
 event_study(data = df.core, 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, ncol = 1 )
-p0
-
-summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Total ~ Treated*year.rel))$coeff[4,]
-summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Qcomp ~ Treated*year.rel))$coeff[4,]
-summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Altman ~ Treated*year.rel))$coeff[4,]
-
-#ggsave(filename = "Picture3a.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 9, height =16)
-
-p0 <- ggarrange(
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), 
 event_study(data = df.core, 
-  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+  yname = "logPatsPerStaff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
   filter(abs(term) <= 5) %>% 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
-event_study(data = df.core, 
-  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
-  filter(abs(term) <= 5) %>% 
-  filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
-event_study(data = df.core, 
-  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
-  filter(abs(term) <= 5) %>% 
-  filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, ncol = 3 )
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("log Ratio Patients-to-Staff"), common.legend = TRUE, ncol = 3 )
 p0
@@
 
-label1 <- 'beta[pooled] == "2.24**"'
-label2 <- 'beta[pooled] == "-0.21**"'
-
-p0.simple <- ggarrange(
-event_study(data = df.core, 
-  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
-  filter(abs(term) <= 5) %>% 
-  filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points") +
-  annotate("text", x=2, y=-2.2, label= label1, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
-        axis.title=element_text(size=14,face="bold")), 
-event_study(data = df.core, 
-  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
-  filter(abs(term) <= 5) %>% 
-  filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Altman's Z Score") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units") +
-  annotate("text", x=2, y=0.4, label= label2, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
-        axis.title=element_text(size=14,face="bold")), common.legend = TRUE, ncol = 2, legend = F) 
-p0.simple
+# label1 <- 'beta[pooled] == "2.24**"'
+# label2 <- 'beta[pooled] == "-0.21**"'
+# 
+# p0.simple <- ggarrange(
+# event_study(data = df.core, 
+#   yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+#   filter(abs(term) <= 5) %>% 
+#   filter(estimator == "Gardner (2021)") %>% 
+#   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+#   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
+#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points") +
+#   annotate("text", x=2, y=-2.2, label= label1, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
+#         axis.title=element_text(size=14,face="bold")), 
+# event_study(data = df.core, 
+#   yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+#   filter(abs(term) <= 5) %>% 
+#   filter(estimator == "Gardner (2021)") %>% 
+#   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+#   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
+#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Altman's Z Score") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units") +
+#   annotate("text", x=2, y=0.4, label= label2, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
+#         axis.title=element_text(size=14,face="bold")), common.legend = TRUE, ncol = 2, legend = F) 
+# p0.simple
 

### 2024-08-26 code/manuscript_analysis.Rmd
windsorize data when poor quality, lots of variation due to noise (total hours of access, efficiency)

@@
 did2s(
-      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.87) & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
+      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
+        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
+      yname = "Total.Hours", 
+      treatment = "Tx",
+        first_stage = ~ 1 | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE)  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+
+did2s(
+      data = df.spill3  %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
+        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
       yname = "Total.Hours", 

### 2024-08-26 code/manuscript_analysis.Rmd
better breaks

@@
 
-qnats1 <- seq(0, 5/6, by = 1/6)
-qnats2 <- seq(1/6, 1, by = 1/6)
+qnats1 <- seq(0, 4/5, by = 1/5)
+qnats2 <- seq(1/5, 1, by = 1/5)
 
@@
 
+quantile(df.spill3$Dist, 0.15, na.rm = TRUE)
+
 model <- did2s(
-      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.87) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
-        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))  , 
+      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
+        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
       yname = "Total.Hours", 
@@
 for (i in 11:19){
-  df.temp <- df.spill3 %>% filter((Dist > quantile(Dist, 0.87) & Att > 0) | Att == 0 )%>% 
+  df.temp <- df.spill3 %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 )%>% 
         mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
@@
       data = df.spill3  %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
-        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))  , 
+        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
       yname = "Total.Hours", 

### 2024-08-27 code/manuscript_analysis.Rmd
remove anticipation from model

--- 2024-08-26 code/manuscript_analysis.Rmd
@@
 
-qnats1 <- seq(0, 5/6, by = 1/6)
-qnats2 <- seq(1/6, 1, by = 1/6)
+qnats1 <- seq(0, 4/5, by = 1/5)
+qnats2 <- seq(1/5, 1, by = 1/5)
 
    model.dist.quants <-  did2s(
-      data = df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year & Att > 0, 1, Tx)),
+      data = df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year & Att > 0, 1, Tx))%>%
+        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))),  
       yname = "NumberofPatients", 
@@
 
-  for (i in 1:6){
+  for (i in 1:5){
       model.dist.quants <-  did2s(
-      data = df.spill3  %>% filter((Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]) & Att > 0 ) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year & Att > 0 , 1, Tx)) ,
+      data = df.spill3  %>% filter((Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]) & Att > 0 ) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year & Att > 0 , 1, Tx)) %>%
+        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
       yname = "NumberofPatients", 
@@
 zp.pats <- tes[-1,] %>% 
-  cbind(Quantile = 1:6) %>% 
+  cbind(Quantile = 1:5) %>% 
   ggplot(aes(x = Quantile, y = Estimate)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=Estimate-1.96*Std..Error, ymax=Estimate+1.96*Std..Error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
@@
 
+quantile(df.spill3$Dist, 0.15, na.rm = TRUE)
+
 model <- did2s(
-      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.87) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
-        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))  , 
+      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
+        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
+        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
       yname = "Total.Hours", 
@@
 for (i in 11:19){
-  df.temp <- df.spill3 %>% filter((Dist > quantile(Dist, 0.87) & Att > 0) | Att == 0 )%>% 
-        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
+  df.temp <- df.spill3 %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) #%>% 
+        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
   df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
@@
 model <- did2s(
-      data = df.spill3  %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
-        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))  , 
+      data = df.spill3  %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
+        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
+        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
       yname = "Total.Hours", 
@@
 for (i in 11:19){
-  df.temp <- df.spill3 %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% 
-        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
+  df.temp <- df.spill3 %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0 ) #%>%  mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
   df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
@@
 ## UPDATED FORM : 3.37 - 0.054x from 62km through 200 is 7%
-
-df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i])) %>% 
-  group_by(Tx) %>% 
-  summarise(mean(Sites))
 

### 2024-08-27 code/manuscript_analysis.Rmd
make figures for manuscript

@@
   geom_dl(label=c(rep("0 Competitors", length(unique(p$Year))), rep("1 Competitor", length(unique(p$Year))), rep("2 Competitors", length(unique(p$Year))), rep("3+ Competitors", length(unique(p$Year)))),
-          method = list("last.points", hjust = 1, vjust = c(3, 3.5, 4, -2), cex = 1.5), inherit.aes=T ) + 
+          method = list("last.points", hjust = 1, vjust = c(2, 2.5, 2.5, -1), cex = 1.5), inherit.aes=T ) + 
   guides(colour = "none") +theme(axis.text=element_text(size=12),
-        axis.title=element_text(size=14,face="bold"))
+        axis.title=element_text(size=12,face="bold"))
 
@@
   guides(colour = "none") + ylim(0, 4000) +theme(axis.text=element_text(size=12),
-        axis.title=element_text(size=14,face="bold"))
+        axis.title=element_text(size=12,face="bold"))
 
@@
 
-#ggsave(filename = "Picture1.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 11, height = 15)
-
-p.desc <- ggarrange(plot1, plot0, ncol = 2)
-
-p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))
+ggsave(filename = "Figure1.png", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Figures", plot = p.desc, width = 8, height = 11)
+
+# p.desc <- ggarrange(plot1, plot0, ncol = 2) 
+# 
+# p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))
 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Quality Composite") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"),
 event_study(data = df.core,
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), 
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience")+ xlab("Year Relative to Competitive Shock") + ylab("Risk Units"),
 event_study(data = df.core,
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("log Ratio Patients-to-Staff"), common.legend = TRUE, ncol = 1 )
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Operational Efficiency") + xlab("Year Relative to Competitive Shock") + ylab("log Ratio Patients-to-Staff") , common.legend = TRUE, ncol = 1 )
 p0
@@
 
-#ggsave(filename = "Picture3a.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 9, height =16)
-
-p0 <- ggarrange(
-  event_study(data = df.core, 
-  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
-  filter(abs(term) <= 5) %>% 
-  filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
-event_study(data = df.core, 
-  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
-  filter(abs(term) <= 5) %>% 
-  filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), 
-event_study(data = df.core, 
-  yname = "logPatsPerStaff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
-  filter(abs(term) <= 5) %>% 
-  filter(estimator == "Gardner (2021)") %>% 
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("log Ratio Patients-to-Staff"), common.legend = TRUE, ncol = 3 )
-p0
-
-#ggsave(filename = "Picture3ah.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 17, height = 9)
-
-# label1 <- 'beta[pooled] == "2.24**"'
-# label2 <- 'beta[pooled] == "-0.21**"'
-# 
-# p0.simple <- ggarrange(
+ggsave(filename = "Figure2.png", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Figures", plot = p0, width = 9, height =16)
+
+label1 <- 'beta[pooled] == "2.24**"'
+label2 <- 'beta[pooled] == "-0.21**"'
+label3 <- 'beta[pooled] == "0.05**"'
+
+# p0 <- ggarrange(
 #   event_study(data = df.core, 
@@
 #   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points") +
-#   annotate("text", x=2, y=-2.2, label= label1, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
+#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Quality Composite") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")+ 
+#      annotate("text", x=2, y=-2, label= label1, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
 #      axis.title=element_text(size=14,face="bold")), 
@@
 #   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
-#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Altman's Z Score") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units") +
-#   annotate("text", x=2, y=0.4, label= label2, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
-#         axis.title=element_text(size=14,face="bold")), common.legend = TRUE, ncol = 2, legend = F) 
-# p0.simple
-
-#ggsave(filename = "Picture3ahSimple.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0.simple, width = 17, height = 9)
+#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
+#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience")+ xlab("Year Relative to Competitive Shock") + ylab("Risk Units")+ 
+#      annotate("text", x=-2, y=-0.3, label= label2, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
+#      axis.title=element_text(size=14,face="bold")), 
+# event_study(data = df.core, 
+#   yname = "logPatsPerStaff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
+#   filter(abs(term) <= 5) %>% 
+#   filter(estimator == "Gardner (2021)") %>% 
+#   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
+#   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
+#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Operational Efficiency") + xlab("Year Relative to Competitive Shock") + ylab("log Ratio Patients-to-Staff") + 
+#      annotate("text", x=2, y=-0.05, label= label3, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
+#      axis.title=element_text(size=14,face="bold")) , common.legend = TRUE, ncol = 3 ) 
+# p0
+
+#ggsave(filename = "Picture3ah.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 17, height = 9)
 
@@
 
-#ggsave(filename = "Picture4.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p2, width = 17, height = 9)
+ggsave(filename = "Figure3.png", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Figures", plot = p2, width = 17, height = 9)
 
@@
 
-  for (i in 1:5){
+  for (i in 1:(length(qnats1))){
       model.dist.quants <-  did2s(
@@
 zp.pats <- tes[-1,] %>% 
-  cbind(Quantile = 1:5) %>% 
+  cbind(Quantile = 1:(length(qnats1))) %>% 
   ggplot(aes(x = Quantile, y = Estimate)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=Estimate-1.96*Std..Error, ymax=Estimate+1.96*Std..Error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
@@
 #ggsave(filename = "Picture13pats.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = zp.pats, width = 16, height = 9)
+
+summary(df.spill3$l.popdensity)
 ```
@@
 cbind(colnames(df.spill3)[10:19], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[c(6:10, 1:2),]
-
-df.spill3  %>% filter(Dist > quantile(Dist, 0.9) ) %>% 
+```
+
+## Back of the envelop calculation, how much resources are reallocated?
+```{r}
+
+df.spill3  %>% filter(Dist > quantile(Dist, 0.8) ) %>% 
   filter(Att > 0) %>% 
@@
   filter(Att > 0) %>%
+  group_by(Tx) %>% 
   summarise(mean(Total.Hours))
@@
 
-sum(df.spill3 %>% filter(Att > 0 & Dist < 200 & Dist > 62 & Year == Att - 1) %>% select(Total.Hours))
+sum(df.spill3 %>% filter(Att > 0 & Dist < 200 & Dist > 0 & Year == Att - 1) %>% select(Total.Hours))
 
@@
 ## UPDATED FORM : 3.37 - 0.054x from 62km through 200 is 7%
+
+#UPDATED AGAIN : 2.167812	* 	-0.427669x where X is in 10km increments
+
+integrand <- function(x) {2.167812 + -0.0427669*x}
+cutpoint <- 2.167812 / 0.0427669
+
+areaUnder <- integrate(f = integrand, lower = cutpoint, upper = 200)
+areaUnder$value / sum(df.spill3 %>% filter(Att > 0 & Dist < 200 & Dist > cutpoint & Year == Att - 1) %>% select(Total.Hours))
+
+areaUnder <- integrate(f = integrand, lower = 0, upper = cutpoint)
+areaUnder$value / sum(df.spill3 %>% filter(Att > 0 & Dist < cutpoint & Dist > 0 & Year == Att - 1) %>% select(Total.Hours))
+
+did2s(
+      data = df.spill3 %>% 
+        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
+      yname = "Total.Hours", 
+      treatment = "Tx",
+        first_stage = ~ 1 | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+
+```
+
+## Alternative Spec
+
+Checking robustness of primary findings, allowing each FQHC to make shifting decisions within their own boarders... what happens? Simiarl story
+
+```{r}
+did2s(
+      data = df.spill3 %>% 
+        group_by(`BHCMIS ID`) %>% 
+        arrange(`BHCMIS ID`, Dist) %>% 
+        mutate(QuantClose = quantile(Dist, 0.333), 
+               QuantFar = quantile(Dist, 0.666), 
+               QuantMid = quantile(Dist, 0.5), 
+               Denom = length(unique(Dist)), 
+               Num = rank(Dist), 
+               Quant = as.numeric((Dist - min(Dist)) / max(Dist)), 
+               PopDensity = max(l.popdensity, na.rm = TRUE)) %>% filter(!is.na(Quant)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
+        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
+        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) %>% 
+        mutate(MedicaidRate = Medicaid / NumberofPatients * 100, 
+               UninsuredRate = Uninsured / NumberofPatients * 100), 
+      yname = "Total.Hours", 
+      treatment = "Tx",
+        first_stage = ~ Sites| Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * as.numeric(Quant) * 10),
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+
+## More Urban Centers
+did2s(
+      data = df.spill3 %>% 
+        group_by(`BHCMIS ID`) %>% 
+        arrange(`BHCMIS ID`, Dist) %>% 
+        mutate(QuantClose = quantile(Dist, 0.333), 
+               QuantFar = quantile(Dist, 0.666), 
+               QuantMid = quantile(Dist, 0.5), 
+               Denom = length(unique(Dist)), 
+               Num = rank(Dist), 
+               Quant = as.numeric((Dist - min(Dist)) / max(Dist)), 
+               PopDensity = max(l.popdensity, na.rm = TRUE)) %>% filter(!is.na(Quant)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
+        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
+        filter(PopDensity > 6.572) %>% 
+        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) %>% 
+        mutate(MedicaidRate = Medicaid / NumberofPatients * 100, 
+               UninsuredRate = Uninsured / NumberofPatients * 100), 
+      yname = "MedicaidRate", 
+      treatment = "Tx",
+        first_stage = ~ 1 | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * as.numeric(Quant) * 10),
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+
+## More Rural Centers
+did2s(
+      data = df.spill3 %>% 
+        group_by(`BHCMIS ID`) %>% 
+        arrange(`BHCMIS ID`, Dist) %>% 
+        mutate(QuantClose = quantile(Dist, 0.333), 
+               QuantFar = quantile(Dist, 0.666), 
+               QuantMid = quantile(Dist, 0.5), 
+               Denom = length(unique(Dist)), 
+               Num = rank(Dist), 
+               Quant = as.numeric((Dist - min(Dist)) / max(Dist)), 
+               PopDensity = max(l.popdensity, na.rm = TRUE)) %>% filter(!is.na(Quant)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
+        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
+        filter(PopDensity < 6.572) %>% 
+        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) %>% 
+        mutate(MedicaidRate = Medicaid / NumberofPatients * 100, 
+               UninsuredRate = Uninsured / NumberofPatients * 100), 
+      yname = "Total.Hours", 
+      treatment = "Tx",
+        first_stage = ~ Sites | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * as.numeric(Quant) * 10),
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+
+df.spill3 %>% 
+  group_by(`BHCMIS ID`) %>% 
+  mutate(maxPopDens = max(l.popdensity, na.rm = TRUE)) %>% 
+    unique() %>% 
+    ungroup() %>% 
+  select(maxPopDens)%>% unlist() %>% 
+  as.numeric() %>% 
+  summary()
+
+```
+
+## Are the closer and farther areas different?
+```{r}
+
+df.spill3 %>% 
+   mutate(DistFilter = ifelse(Dist < quantile(Dist, 0.15), "Near", 
+                              ifelse(Dist > quantile(Dist, 0.85), "Far", NA))) %>% 
+  filter(!is.na(DistFilter) & Year == 2012) %>% 
+  select(DistFilter, Tx:NumberofPatients, ALAND10:l.popdensity) %>% 
+  inner_join(census, by = c("Zip" = "ZipCode", "Year" = "YEAR")) %>% 
+  select(DistFilter, TotalPop:Uninsured) %>% 
+  mutate(PctMedicaid = Medicaid / MCD.denom * 100, 
+         PctUninsured = Uninsured / Unins.denom * 100, 
+         PctPoverty = IncomeBelowPoverty / PovertyStatusDet * 100, 
+         PctBlack = Black / TotalPop * 100, 
+         PctHispanic = Hispanic / TotalPop * 100) %>% 
+    tbl_summary(by = DistFilter, 
+                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
+  add_p()
 

### 2024-08-27 code/manuscript_analysis.Rmd
alternative back of the envelop calc

@@
 
+df.spill3 %>% 
+  filter(Year == Att - 1) %>% 
+  mutate(EstimatedChange = 2.167812 + -0.0427669*Dist) %>% 
+  summarise(sum(abs(EstimatedChange)) / sum(Total.Hours))
+
 did2s(
-      data = df.spill3 %>% 
+      data = df.spill3 %>% #filter((Dist > quantile(Dist, 0.4) & Dist < quantile(Dist, 0.6) & Att > 0) | Att == 0 ) %>% 
         mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
@@
     )
+
+## Alternative Calculation
+
+mean(df.spill3[df.spill3$Dist < quantile(df.spill3$Dist, probs = c(0.15)),]$Dist)
+mean(df.spill3[df.spill3$Dist > quantile(df.spill3$Dist, probs = c(0.85)),]$Dist)
+
+df.spill3 %>% filter(Att > 0 & Dist < 0.33476343 & Year == Att - 1) %>% summarise(sum(Total.Hours), n())
+df.spill3 %>% filter(Att > 0 & Dist > 157.1606 & Year == Att - 1) %>% summarise(sum(Total.Hours), n())
+
+df.spill3 %>% 
+  filter(Year == Att - 1) %>% 
+  mutate(EstimatedChange = 6 + -0.039*Dist) %>% 
+  summarise(sum(abs(EstimatedChange)) / sum(Total.Hours))
 

### 2024-09-03 code/manuscript_analysis.Rmd
new figures

@@
 
+## Distribution of FQHC sites nationwide
+
+```{r}
+
+p.grant <- census %>% 
+  filter(YEAR == 2021) %>% 
+  group_by(ZipCode, YEAR) %>% 
+  summarise(Pct.Poverty = IncomeBelowPoverty / PovertyStatusDet * 100, 
+            Pct.MCD = Medicaid / MCD.denom * 100, 
+            Pct.Unins = Uninsured / Unins.denom * 100) %>% 
+  left_join(uds.sites.full %>% 
+  filter(Year == 2021) %>% 
+  group_by(Zip, Year) %>% 
+  summarise(Counts = n()), by = c("ZipCode" = "Zip", "YEAR" = "Year")) %>% 
+  mutate(Counts = ifelse(is.na(Counts), 0, Counts), 
+         Counts_Bin = ifelse(Counts == 0, 0, 100), 
+         `Poverty, %` = round(Pct.Poverty, digits = -1),
+         `Medicaid, %` = round(Pct.MCD, digits = -1), 
+         `Uninsured, %` = round(Pct.Unins, digits = -1)) %>% 
+  pivot_longer( `Poverty, %`:`Uninsured, %`) %>% 
+  ungroup() %>% group_by(name, value) %>% 
+  summarise(`# Zip Codes` = n(), PropWithCHC = mean(Counts_Bin)) %>% 
+  filter(!is.na(value)) %>% 
+  rename(Measure = name) %>% 
+  ggplot(aes(x = value, y = PropWithCHC, group_by(Measure))) + geom_point(aes(size =`# Zip Codes`, color = Measure)) + geom_line(aes(group = Measure, color = Measure))+
+  theme_tufte_revised() + xlab("Percent, %") + ylab("Zips with a CHC, %") + ylim(0, 37) + #facet_wrap(~Measure) +
+  theme(axis.text=element_text(size=10), axis.title=element_text(size=10,face="bold"), strip.text = element_text(size=12,face="bold"))
+p.grant
+
+```
+
 ## Ratio of Distance between incumbent sites and rival

### 2024-09-05 code/manuscript_analysis.Rmd
remove prelim stuff
making more figures

--- 2024-08-27 code/manuscript_analysis.Rmd
@@
                                     ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
-      yname = "Total.Hours", 
+      yname = "Hours", 
       treatment = "Tx",
@@
 
-cbind(colnames(df.spill3)[10:19], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[c(6:10, 1:2),]
+cbind(colnames(df.spill3)[10:19], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[c(6:10, 1:5),]
 ```
@@
                               ifelse(Dist > quantile(Dist, 0.85), "Far", NA))) %>% 
-  filter(!is.na(DistFilter) & Year == 2012) %>% 
+  filter(!is.na(DistFilter) & Year < 2013) %>% 
   select(DistFilter, Tx:NumberofPatients, ALAND10:l.popdensity) %>% 
@@
 
+ggsave(filename = "AppendixFigures10.png", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Figures", plot = p.rival.dist, width = 10, height = 6)
 ```
@@
 
-    df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.y" = "BHCMISID", "Year")) %>% 
+    df.z.dist %>% 
+      mutate(Year = Year - 1) %>% 
+      left_join(df.comp, by = c("BHCMIS ID.y" = "BHCMISID", "Year")) %>% 
       mutate(Type = "Incumbent") %>% 
@@
                Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
-               NetWorth = (Assets - Liabilities) / Liabilities) %>% 
+               NetWorth = (Assets - Liabilities) / Liabilities, 
+             logPatsPerStaff = log(Total / Staff)) %>% 
       mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity), 
@@
          Altman = 0.18 * quick_ratio + 0.3 * Profitability + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
-      select(Type, Quality, Total, Altman, Pct.NHA:Pct.COM) %>% 
+      select(Type, Quality, Total, Altman, logPatsPerStaff, Pct.NHA:Pct.COM) %>% 
           tbl_summary(by = Type, 
-                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
-  add_p()
+                statistic = list(all_continuous() ~ "{mean} ({sd})"), 
+                digits = list(everything() ~ c(1)), 
+                missing = "no") %>% 
+  add_p(test = everything() ~ "t.test", pvalue_fun = function(x) style_pvalue(x, digits = 3))
 

### 2024-09-05 code/manuscript_analysis.Rmd
remove winsoring, cleaner estimation of distance effects

@@
 model <- did2s(
-      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
+      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)),# %>% 
         #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
-        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
-                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
+        #mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+        #                            ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
       yname = "Hours", 
@@
 
-for (i in 11:19){
+for (i in 10:19){
   df.temp <- df.spill3 %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) #%>% 
@@
 model <- did2s(
-      data = df.spill3  %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
+      data = df.spill3  %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)),# %>% 
         #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
-        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
-                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
+       # mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+        #                            ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
       yname = "Hours", 
@@
 
-for (i in 11:19){
+for (i in 10:19){
   df.temp <- df.spill3 %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0 ) #%>%  mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
@@
 
-cbind(colnames(df.spill3)[10:19], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[c(6:10, 1:5),]
+cbind(colnames(df.spill3)[c(30, 10:19)], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[c(7:11, 2, 1, 3:6),]
+
+did2s(
+      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
+        mutate(Outcome = ifelse(Sites == 0, 0, Schedule / Sites)), 
+        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
+       # mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+        #                            ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ 1 | Zip + Year , 
+        second_stage = ~ i(Tx, ref = FALSE)  ,
+        cluster_var = "Zip",
+      verbose = FALSE
+    )
+
 ```
@@
 did2s(
-      data = df.spill3 %>% #filter((Dist > quantile(Dist, 0.4) & Dist < quantile(Dist, 0.6) & Att > 0) | Att == 0 ) %>% 
-        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
-                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
+      data = df.spill3, #%>% #filter((Dist > quantile(Dist, 0.4) & Dist < quantile(Dist, 0.6) & Att > 0) | Att == 0 ) %>% 
+        #mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
+       #                             ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
       yname = "Total.Hours", 
@@
 
-mean(df.spill3[df.spill3$Dist < quantile(df.spill3$Dist, probs = c(0.15)),]$Dist)
-mean(df.spill3[df.spill3$Dist > quantile(df.spill3$Dist, probs = c(0.85)),]$Dist)
-
-df.spill3 %>% filter(Att > 0 & Dist < 0.33476343 & Year == Att - 1) %>% summarise(sum(Total.Hours), n())
-df.spill3 %>% filter(Att > 0 & Dist > 157.1606 & Year == Att - 1) %>% summarise(sum(Total.Hours), n())
+dist.close <- mean(df.spill3[df.spill3$Dist < quantile(df.spill3$Dist, probs = c(0.15)),]$Dist)
+dist.far <- mean(df.spill3[df.spill3$Dist > quantile(df.spill3$Dist, probs = c(0.85)),]$Dist)
+
+df.spill3 %>% filter(Att > 0 & Dist < quantile(df.spill3$Dist, probs = c(0.15)) & Year == Att - 1) %>% summarise(sum(Total.Hours), n())
+df.spill3 %>% filter(Att > 0 & Dist > quantile(df.spill3$Dist, probs = c(0.85)) & Year == Att - 1) %>% summarise(sum(Total.Hours), n())
 
@@
   filter(Year == Att - 1) %>% 
-  mutate(EstimatedChange = 6 + -0.039*Dist) %>% 
+  mutate(EstimatedChange =  TEs.strat.close[2,1] + (TEs.strat.far[2,1] - TEs.strat.close[2,1]) / (dist.far - dist.close)*Dist) %>% 
   summarise(sum(abs(EstimatedChange)) / sum(Total.Hours))

### 2024-09-06 code/manuscript_analysis.Rmd
clean up the code

@@
 
-did2s(
-      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
-        mutate(Outcome = ifelse(Sites == 0, 0, Schedule / Sites)), 
-        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
-       # mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
-        #                            ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
-      yname = "Outcome", 
-      treatment = "Tx",
-        first_stage = ~ 1 | Zip + Year , 
-        second_stage = ~ i(Tx, ref = FALSE)  ,
-        cluster_var = "Zip",
-      verbose = FALSE
-    )
-
 ```

### 2024-09-06 code/manuscript_data_cleaning.Rmd
new figures
getting right time period
new addons

@@
 
+## Total Patients served by Year
+```{r}
+read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv") %>% 
+  select(Year, T3B_L4_CA) %>% 
+  group_by(Year) %>% 
+  summarise(sum(T3B_L4_CA, na.rm = TRUE))
+
+```
+
 ## Clinic-level in Covariates 
@@
 fins.revenue.expenses <- read.csv("//Users/markow/Dropbox/Git/Data/FQHC_Revenue_vs_Expenses.csv", header = TRUE)
+table(fins.revenue.expenses$X.form_year..)
 names(fins.revenue.expenses) <- gsub("^X\\.", "", names(fins.revenue.expenses))
@@
 
- included.years <- 2014:2023
- included.treat <- 2016:2023
+included.years <- 2010:2021
+included.treat <- 2013:2019
 

### 2024-10-01 code/manuscript_altanalysis.Rmd
alt spec

--- 2024-08-26 code/manuscript_data_cleaning.Rmd
@@
 ---
-title: "data_cleaning_longer_period"
+title: "Untitled"
 author: "Justin"
-date: "2023-08-15"
+date: "2024-10-01"
 output: html_document
@@
 
-# Libraries
 ```{r}
+library(readxl)
+library(did2s)
+library(tidyverse)
+library(directlabels)
+library(gtsummary)
+library(kableExtra)
+library(ggpubr)
 library(tigris)
-library(tidygeocoder)
+library(usmap)
+```
 
-library(tidyverse)
-library(readxl)
-library(did)
-library(Matching)
-library(gtsummary)
-library(RODBC)
-library(ggpubr)
-library(fixest)
-library(kableExtra)
-library(usmap)
-library(did2s)
-library(formattable)
-library (readr)
+```{r}
+mean.nas<- function(x){ mean(x, na.rm = TRUE)}
 
-library(did2s)
-library(tidycensus)
+options(scipen=999)
+```
 
-`%notin%` <- Negate(`%in%`)
-select <- dplyr::select
+```{r}
+dfc <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
+uds.sites.full <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
+  mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 4, Access))
+clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
+  #filter(Year >= included.years[1]) %>%
+  group_by(Zip, Year) %>%
+  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
+  arrange(desc(Clinics))
+
+ uds.sites.full %>%
+   filter(is.na(Zip))
 
@@
 
-## Formating plots
+# Build Variables
 
-```{r, echo = FALSE, results = "asis", message=FALSE, warning = FALSE, fig.align="center"}
-
-is.extrafont.installed <- function(){
-  if(is.element("extrafont", installed.packages()[,1])){
-    library(extrafont)
-    # probably need something here to run font_import()
-    return(T)
-  }else{
-    warning("Library extrafont installed; using system sans/serif libraries as fallback fonts. 
-    To enable full font support, run: 
-      install.packages('extrafont') 
-      font_import()")
-    return(F)
-  }
-}
-
-# set font
-base_font_family_tufte <- function(){
-  if(is.extrafont.installed()){
-    library(extrafont)
-    tuftefont <- choose_font(c("Gill Sans MT", "Gill Sans", "GillSans", "Verdana", "serif"), quiet = FALSE)   #
-  }else{
-    tuftefont <- "serif"
-  }
-  return(tuftefont)
-}
-
-theme_tufte_revised <- function(base_size = 11, base_family = base_font_family_tufte(), ticks = TRUE) {
-
-  ret <- theme_bw(base_family = base_family, base_size = base_size) + 
-    theme(
-      axis.line = element_line(color = 'black'),
-      axis.title.x = element_text(vjust = -0.3), 
-      axis.title.y = element_text(vjust = 0.8),
-      legend.background = element_blank(), 
-      legend.key = element_blank(), 
-      legend.title = element_text(face="plain"),
-      panel.background = element_blank(), 
-      panel.border = element_blank(),
-      panel.grid = element_blank(),
-      plot.background = element_blank(),
-      strip.background = element_blank()
-    )
-
-  if (!ticks) {
-    ret <- ret + theme(axis.ticks = element_blank())
-  }
-
-  ret
-}
-
-```
-
-# Data Prep
-
-## Set study period
-```{r}
-
-included.years <- 2010:2023
-included.treat <- 2013:2023
-
-```
-
-## Sites and ZipCodes
-```{r}
-
-## Zips
-locs <- paste("/Users/markow/Dropbox/Git/UDS/UDS-", c(2012:2023), "-Full-Dataset.xlsx", sep = "")
-uds.zip <- read_excel(locs[1], sheet = "HealthCenterZipCodes")[,c(1:4, 6, 5)]
-
-#new.zip.names <- c("BHCMIS ID", "Grant Number", "Reporting Year" , "Zip Code", "Zip Code Type",  "None_Uninsured Patients" ,  "Medicaid_CHIP_Other Public Patients", "Medicare Patients", "Private Patients", "Total Number of Patients" )
-
-uds.zip <- cbind(uds.zip, "Uninsured" = NA ,  "Medicaid" = NA, "Medicare" = NA, "Private" = NA)
-
-new.zip.names <- colnames(uds.zip)
-
-for(i in 2:length(locs)){
-  temp.zip <- read_excel(locs[i], sheet = "HealthCenterZipCodes") #[,c(1:5, 10)]
-
-  colnames(temp.zip) <- new.zip.names[c(1:5, 7:10, 6)]
-  uds.zip <- rbind(uds.zip, temp.zip %>% mutate(ZipCode = str_pad(ZipCode, 5, pad = "0")))
-}
-
-uds.zip$ReportingYear <- as.numeric(uds.zip$ReportingYear)
-uds.zip$NumberofPatients <- as.numeric(uds.zip$NumberofPatients)
-uds.zip$Uninsured <- as.numeric(uds.zip$Uninsured)
-uds.zip$Medicaid <- as.numeric(uds.zip$Medicaid)
-uds.zip$Medicare <- as.numeric(uds.zip$Medicare)
-uds.zip$Private <- as.numeric(uds.zip$Private)
-
-uds.zip[is.na(uds.zip$NumberofPatients),]$NumberofPatients <- 0
-uds.zip[is.na(uds.zip$Uninsured) & uds.zip$ReportingYear > 2012,]$Uninsured <- 0
-uds.zip[is.na(uds.zip$Medicaid) & uds.zip$ReportingYear > 2012,]$Medicaid <- 0
-uds.zip[is.na(uds.zip$Medicare) & uds.zip$ReportingYear > 2012,]$Medicare <- 0
-uds.zip[is.na(uds.zip$Private) & uds.zip$ReportingYear > 2012,]$Private <- 0
-
-uds.zip <- uds.zip[uds.zip$ZipCodeType == "ZipCode",]
-
-```
-
-## Bunk old Zip code code
-
-```{r}
-
-# 
-# # ## Rename
-# # new.zip.names <- c("BHCMIS ID", "Grant Number", "Reporting Year" , "Zip Code", "Zip Code Type",  "None_Uninsured Patients" ,  "Medicaid_CHIP_Other Public Patients", "Medicare Patients", "Private Patients", "Total Number of Patients" )
-# # colnames(uds.zip) <-    new.zip.names
-# # 
-# # 
-# # ## Clean
-# # 
-# # uds.zip[uds.zip$`Total Number of Patients`== '-' | uds.zip$`Total Number of Patients`== '--',]$`Total Number of Patients` <- NA
-# # uds.zip$`Total Number of Patients` <- as.numeric(uds.zip$`Total Number of Patients`)
-# # uds.zip <- uds.zip[!is.na(uds.zip$`Total Number of Patients`),] %>% 
-# #     mutate(`Reporting Year` = as.numeric(`Reporting Year`))
-# # 
-# # uds.zip$`None_Uninsured Patients` <- as.numeric(uds.zip$`None_Uninsured Patients`)
-# # uds.zip$`Medicaid_CHIP_Other Public Patients` <- as.numeric(uds.zip$`Medicaid_CHIP_Other Public Patients`)
-# # uds.zip$`Medicare Patients` <- as.numeric(uds.zip$`Medicare Patients`)
-# # uds.zip$`Private Patients` <- as.numeric(uds.zip$`Private Patients`)
-# # 
-# # 
-# # uds.zip <- cbind(uds.zip, broken.total = rowSums(uds.zip[,c(6:9)], na.rm = TRUE), missings = rowSums(is.na(uds.zip[,c(6:9)]))) %>% 
-# #   mutate(`Total Number of Patients` = as.numeric(`Total Number of Patients`)) %>% 
-# #   mutate(`Total Number of Patients` = ifelse(is.na(`Total Number of Patients`), round(missings*16/4), `Total Number of Patients`)) %>% 
-# #   mutate(`None_Uninsured Patients` = ifelse(is.na(`None_Uninsured Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `None_Uninsured Patients`), 
-# #          `Medicaid_CHIP_Other Public Patients` = ifelse(is.na(`Medicaid_CHIP_Other Public Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Medicaid_CHIP_Other Public Patients`),
-# #          `Medicare Patients` = ifelse(is.na(`Medicare Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Medicare Patients`), 
-# #          `Private Patients` = ifelse(is.na(`Private Patients`), (`Total Number of Patients` - broken.total) * 1/missings, `Private Patients`))
-# 
-# 
-# uds.zip$`Reporting Year` <- as.numeric(uds.zip$`Reporting Year`)
-# uds.zip$`Total Number of Patients` <- as.numeric(uds.zip$`Total Number of Patients`)
-# uds.zip$`None_Uninsured Patients` <- as.numeric(uds.zip$`None_Uninsured Patients`)
-# uds.zip$`Medicaid_CHIP_Other Public Patients` <- as.numeric(uds.zip$`Medicaid_CHIP_Other Public Patients`)
-# uds.zip$`Medicare Patients` <- as.numeric(uds.zip$`Medicare Patients`)
-# uds.zip$`Private Patients` <- as.numeric(uds.zip$`Private Patients`)
-# 
-# 
-# uds.zip[is.na(uds.zip$`Total Number of Patients`),]$`Total Number of Patients` <- 0
-# uds.zip[grep("-", uds.zip$`None_Uninsured Patients`),]$`None_Uninsured Patients` <- 0
-# uds.zip[grep("-", uds.zip$`Medicaid_CHIP_Other Public Patients`),]$`Medicaid_CHIP_Other Public Patients` <- 0
-# uds.zip[grep("-", uds.zip$`Medicare Patients`),]$`Medicare Patients` <- 0
-# uds.zip[grep("-", uds.zip$`Private Patients`),]$`Private Patients` <- 0
-# 
-# uds.zip.totals <- uds.zip %>%
-#   select(`Grant Number`, `Reporting Year`, `None_Uninsured Patients`:`Total Number of Patients`) %>%
-#   group_by(`Grant Number`, `Reporting Year`) %>% summarise(None = sum(`None_Uninsured Patients`, na.rm = T),
-#                                                            MCR = sum(`Medicare Patients`, na.rm = T),
-#                                                            COM = sum(`Private Patients`, na.rm = T),
-#                                                            MCD = sum(`Medicaid_CHIP_Other Public Patients`, na.rm = T),
-#                                                            Total = sum(`Total Number of Patients`, na.rm = T))
-# 
-# uds.zip <- uds.zip[uds.zip$`Zip Code Type` == "ZipCode",]
-
-```
-
-```{r}
-
-## Sites
-locs <- paste("/Users/markow/Dropbox/Git/UDS/UDS-", c(2012:2023), "-Full-Dataset.xlsx", sep = "")
-
-uds.sites <- read_excel(locs[1], sheet = "HealthCenterSiteInfo") %>% 
-  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>%
-  mutate(Year = 2012)
-
-colnames(uds.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")
-
-for(i in 2:3){
-site.temp <- read_excel(locs[i], sheet = "HealthCenterSiteInfo") %>% 
-                       select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, 
-                              SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>%
-  mutate(Year = 2011 + i)
-
-colnames(site.temp) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")
-
-   uds.sites <-  rbind(uds.sites, site.temp)
-}
-
-for(i in 4:(length(locs)-3)){
-  uds.sites <- rbind(uds.sites, read_excel(locs[i], sheet = "HealthCenterSiteInfo") %>% 
-                       select("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code") %>%
-  mutate(Year = 2011 + i))
-}
-
-## 2021
-temp.sites <- read_excel(locs[i+1], sheet = "HealthCenterSiteInfo" )%>% 
-  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>%
-  mutate(Year = 2021)
-colnames(temp.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")
-
-uds.sites <- rbind(uds.sites, temp.sites)
-
-## 2022
-temp.sites <- read_excel(locs[i+2], sheet = "HealthCenterSiteInfo" )%>% 
-  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>%
-  mutate(Year = 2022)
-colnames(temp.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")
-
-uds.sites <- rbind(uds.sites, temp.sites)
-
-## 2023
-temp.sites <- read_excel(locs[i+3], sheet = "HealthCenterSiteInfo" )%>% 
-  select(BHCMISID, GrantNumber, HealthCenterName, SiteName, SiteType, LocationType, LocationSetting, OperationalSchedule, CalendarSchedule, TotalWeeklyHoursOfOperation, SiteStreetAddress, SiteCity, SiteState, SiteZIPCode) %>%
-  mutate(Year = 2023)
-colnames(temp.sites) <- c("BHCMIS ID", "Grant Number", "Health Center Name", "Site Name", "Site Type", "Location Type", "Location Setting", "Operational Schedule", "Calendar Schedule", "Total Weekly Hours Of Operation", "Site Street Address", "Site City", "Site State", "Site ZIP Code", "Year")
-
-uds.sites <- rbind(uds.sites, temp.sites)
-
-uds.sites.old <- read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Sites.csv", colClasses = "character") %>% 
-  mutate(Year = as.numeric(Year))
-
-colnames(uds.sites.old) <- c("BHCMIS ID", "Health Center Name", "Site Name", "Site Street Address", "Site Street Address 2", "Site State", "Site ZIP Code", "Year", "GranteeID", "Site Street Address 3","Site City","ModernGrateeID")
-
-uds.sites.full <- bind_rows(uds.sites, uds.sites.old) %>% 
-  arrange(`BHCMIS ID`, Year) %>% 
-  select(`BHCMIS ID`:`Health Center Name`, Year, `Site Name`, `Site Street Address`, `Site Street Address 2`, `Site Street Address 3`, `Site City`, `Site State`, `Site ZIP Code` , `Site Type`:`Total Weekly Hours Of Operation`)
-
-uds.sites.full$Zip <- substr(uds.sites.full$`Site ZIP Code`, 1, 5)
-
-uds.sites.full <- uds.sites.full %>% 
-  filter(`Site State` %notin% c('GU','VI','PW','MH','AS','FM','PR','MP')) #'AK','HI',
-
-uds.sites.full[grep(pattern = "-", uds.sites.full$Zip),]$Zip <- NA
-
-#write.csv(x = uds.sites.full, file = "//Users/markow/Dropbox/Git/APMs/data_processed/Sites96to21.csv")
-
-uds.sites %>% 
-  filter(Year %in% c(2021, 2022, 2023)) %>% 
-  arrange(`Grant Number`, Year)
-
-```
-
-## Clean up the missing addresses, geocoding
-
-```{r}
-
-tbcoded <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]
-coded <- geo(street = tbcoded[c(1:1000),]$`Site Street Address`, 
-             city = tbcoded[c(1:1000),]$`Site City`, 
-             state = tbcoded[c(1:1000),]$`Site State`, 
-             method = "census", 
-             full_results = TRUE)
-
-for (g in 1:16){
-  g
-coded <- rbind(coded, 
-               geo(street = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site Street Address`, 
-             city = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site City`, 
-             state = tbcoded[c((1 + g*1000):((g+1)*1000)),]$`Site State`, 
-             method = "census", 
-             full_results = TRUE) )
-}
-
-coded <- rbind(coded, 
-               geo(street = tbcoded[c(17001:17152),]$`Site Street Address`, 
-             city = tbcoded[c(17001:17152),]$`Site City`, 
-             state = tbcoded[c(17001:17152),]$`Site State`, 
-             method = "census", 
-             full_results = TRUE) )
-
-coded[grep(pattern = "[[:digit:]]{5}$", coded$matched_address),]
-
-uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]$Zip <- str_extract(coded$matched_address, pattern = "[[:digit:]]{5}$")
-uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]
-
-uds.sites.full.temp <- uds.sites.full
-
-```
-
-```{r}
-
-uds.sites.full <- uds.sites.full.temp
-
-uds.sites.full.temp %>% filter(`Grant Number` %in% c("H80CS00881") & Year == 2016)
-
-chc <- read.csv("//Users/markow/Dropbox/Git/Competition/data_raw/chc.csv")
-
-chc %>% filter(Health.Center.Number %in% c("H80CS00881"))
-
-uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] %>%
-  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Street Address" = "Site.Address")) %>%
-  mutate(Zip = ifelse(is.na(Zip), substr(Health.Center.Organization.ZIP.Code, 1, 5), Zip)) %>%
-  select(`BHCMIS ID`:Zip) %>%
-  unique()
-
-uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] <- uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],] %>%
-  left_join(chc, by = c("Grant Number" = "Health.Center.Number", "Site Name" = "Site.Name")) %>%
-  mutate(Zip = ifelse(is.na(Zip), substr(Health.Center.Organization.ZIP.Code, 1, 5), Zip)) %>%
-  select(`BHCMIS ID`:Zip) %>%
-  unique()
-
-uds.sites.full[is.na(uds.sites.full$Zip) & uds.sites.full$Year >= included.years[1],]
-```
-
-```{r}
-
-table(uds.sites.full.temp$`Location Setting`)
-
-uds.sites.full <- uds.sites.full %>% #filter(`Location Type` == "Permanent" & `Location Setting` %in% c("All Other Clinic Types")) %>% 
-  mutate(Access = as.numeric(ifelse(`Total Weekly Hours Of Operation` == "-" & `Operational Schedule` == "Full-Time", 40, 
-                  ifelse(`Total Weekly Hours Of Operation` == "-" & `Operational Schedule` == "Part-Time", 10, `Total Weekly Hours Of Operation`))))
-
-uds.sites.full[is.na(uds.sites.full$Zip),]
-
-uds.sites.full %>% 
-  arrange(`Total Weekly Hours Of Operation`, `Operational Schedule` )
-
-```
-
-## Read in census data for all zip codes
-```{r}
-
-census <- data.frame(ZipCode = 0, NAME = 0, YEAR = 0, 
-                     TotalPop = 0,
-                     Male = 0, Female = 0, 
-                     AgeUnder18 = 0, Age18to64 = 0, Age65andOver = 0, 
-                     White = 0, Black = 0, AIAN = 0, Asian = 0, MR = 0, Hispanic = 0, EducLow = 0, EducMid = 0, EducHigh = 0, 
-                     PovertyStatusDet = 0, IncomeBelowPoverty = 0, Unemployed = 0, Unemp_denom = 0, 
-                     MCD.denom = 0, Medicaid = 0, Unins.denom = 0, Uninsured = 0)
-
-for (i in 1:11){
-  census <- rbind(census, get_acs(geography = "zcta", survey = "acs5",
-                       variables = c("B01003_001","B17001_001","B17001_002","B01001_002","B01001_026",
-                                     "B02001_002","B02001_003","B02001_004","B02001_005","B02001_006","B02001_008",
-                                     "B03001_003", 
-                                     "B01001_003","B01001_004","B01001_005","B01001_006","B01001_007","B01001_008","B01001_009",
-                                     "B01001_010","B01001_011","B01001_013","B01001_014","B01001_015","B01001_016","B01001_017",
-                                     "B01001_018","B01001_019","B01001_020","B01001_021","B01001_022","B01001_023","B01001_024","B01001_025",
-                                     "B01001_027","B01001_028","B01001_029","B01001_030","B01001_031","B01001_032","B01001_033","B01001_034",
-                                     "B01001_035","B01001_036","B01001_037","B01001_038","B01001_039","B01001_040","B01001_041","B01001_042","B01001_043",
-                                     "B01001_044","B01001_045","B01001_046","B01001_047","B01001_048","B01001_049",
-                                     "B06009_002","B06009_003", "B06009_004","B06009_005","B06009_006",
-                                     "B23025_002","B23025_005",
-                                     "C27007_001", "C27007_004", "C27007_007", "C27007_010", "C27007_014", "C27007_017", "C27007_020",
-                                     "B18135_001","B18135_007","B18135_012","B18135_018","B18135_023","B18135_029","B18135_034"), 
-                       year = 2011 + i) %>% 
-  pivot_wider(id_cols = c(GEOID, NAME), names_from = variable, values_from = estimate) %>% 
-    mutate(YEAR = 2011 + i, TotalPop = B01003_001, PovertyStatusDet = B17001_001, IncomeBelowPoverty = B17001_002,
-           AgeUnder18 = B01001_003 + B01001_004 + B01001_005 + B01001_006 + B01001_027 + B01001_028 + B01001_029 + B01001_030,
-           Age18to64 = B01001_007 + B01001_008 + B01001_009 + B01001_010 + B01001_011 + B01001_013 + B01001_014 + B01001_015 + 
-                       B01001_016 + B01001_017 + B01001_018 + B01001_019 + B01001_031 + B01001_032 + B01001_033 + B01001_034 +
-                       B01001_035 + B01001_036 + B01001_037 + B01001_038 + B01001_039 + B01001_040 + B01001_041 + B01001_042 + B01001_043, 
-           Age65andOver = B01001_020 + B01001_021 + B01001_022 + B01001_023 + B01001_024 + B01001_025 + 
-                          B01001_044 + B01001_045 + B01001_046 + B01001_047 + B01001_048 + B01001_049, 
-           Male = B01001_002, Female = B01001_026, 
-           White = B02001_002, Black = B02001_003, AIAN = B02001_004, Asian = B02001_005 + B02001_006, MR = B02001_008, 
-           Hispanic = B03001_003, 
-           EducLow = B06009_002, EducMid = B06009_003 + B06009_004, EducHigh = B06009_005 + B06009_006,
-           Unemployed = B23025_005, Unemp_denom = B23025_002,
-           MCD.denom = C27007_001	, Medicaid = C27007_004	 + C27007_007 + C27007_010	+ C27007_014 + C27007_017 + C27007_020,
-           Unins.denom = B18135_001, Uninsured = B18135_007 + B18135_012 + B18135_018 + B18135_023 + B18135_029 + B18135_034) %>% 
-    select(ZipCode = GEOID, NAME, YEAR, TotalPop:Uninsured))
-
-  print(i)
-}
-census <- census[-1,]
-
-##########
-census$ZipCode <- substr(census$NAME, 7, 11)
-#census$ZipCode <- str_pad(census$ZipCode, 5, pad = "0")
-
-census %>% 
-  filter(YEAR == 2022) %>% 
-  select(ZipCode) %>% 
-  #unique() %>% 
-  table() %>% 
-  table()
-```
-
-## Merge with Older UDSs 1996-2011
-```{r}
-uds.cw <- read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_CW.csv", colClasses = "character") %>% 
-  mutate(link.ID = ifelse(is.na(ModernGranteeID) & !is.na(LongGrantID) & Year != 2010, LongGrantID, 
-                   ifelse(is.na(ModernGranteeID) & !is.na(GranteeID), GranteeID, BHCMIS.ID)), 
-         Year = as.integer(Year))
-
-uds.cw %>% 
-  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
-  arrange(BHCMIS.ID, Year) %>% 
-  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
-  filter(BHCMIS.ID == '010060' & Year %in% c(2007:2011)) %>% 
-  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA)
-
-namevec <- c("BHCMIS.ID", "Year", "NHA", "NHB", "HL", "NHW", "Total", "Eng2ndLang")
-
-#fins.revenue.expenses <- read_csv("FQHC_Revenue_vs_Expenses.csv")
-#cw <- read_excel("UDS-990 Crosswalk.xlsx")
-
-```
-
-## Clinic-level in Covariates 
-```{r}
-
-# Table 3B
-
-uds.3B.2012 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
-uds.3B.2013 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
-
-uds.3B.2014 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
-uds.3B.2015 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table3B", skip = 2) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
-uds.3B.2016 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-
-uds.3B.2017 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-uds.3B.2018 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-uds.3B.2019 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-
-uds.3B.2020 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-uds.3B.2021 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-uds.3B.2022 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2022-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-uds.3B.2023 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2023-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(BHCMISID, GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
-
-namevec <- c("Year", "BHCMISID", "ModernGranteeID", "NHA", "NHB", "HL", "NHW", "Total", "Eng2ndLang")
-uds.3B <- rbind(cbind(Year = 2012, uds.3B.2012),
-                cbind(Year = 2013, uds.3B.2013),
-                cbind(Year = 2014, uds.3B.2014),
-                  cbind(Year = 2015, uds.3B.2015),
-                  cbind(Year = 2016, uds.3B.2016),
-                  cbind(Year = 2017, uds.3B.2017),
-
-                  cbind(Year = 2018, uds.3B.2018),
-                  cbind(Year = 2019, uds.3B.2019), 
-                  cbind(Year = 2020, uds.3B.2020),
-                  cbind(Year = 2021, uds.3B.2021),
-
-                  cbind(Year = 2022, uds.3B.2022),
-                  cbind(Year = 2023, uds.3B.2023)) %>%
-
-  rename_all(vars(namevec), function(x) namevec)
-
-uds.3B <- rbind(
-  uds.cw %>% 
-  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
-  arrange(BHCMIS.ID, Year) %>% 
-  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
-  filter(Year %in% c(2007)) %>% 
-  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA) %>% 
-    setNames(namevec), 
-  uds.cw %>% 
-  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
-  arrange(BHCMIS.ID, Year) %>% 
-  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
-  filter(Year %in% c(2008)) %>% 
-  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L5A_CA, T3B_L6_CA, T3B_L1_CA, T3B_L8_CA, T3B_L4_CA, T3B_L12_CA) %>% 
-    setNames(namevec),
-    uds.cw %>% 
-  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
-  arrange(BHCMIS.ID, Year) %>% 
-  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
-  filter(Year %in% c(2009)) %>% 
-  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
-    setNames(namevec), 
-  uds.cw %>% 
-  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
-  arrange(BHCMIS.ID, Year) %>% 
-  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
-  filter(Year %in% c(2010)) %>% 
-  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
-    setNames(namevec), 
-  uds.cw %>% 
-  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
-  arrange(BHCMIS.ID, Year) %>% 
-  select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
-  filter(Year %in% c(2011)) %>% 
-  select(Year, BHCMIS.ID, ModernGranteeID, T3B_L1_CB, T3B_L3_CB, T3B_L8_CA, T3B_L5_CB, T3B_L8_CD, T3B_L12_CA) %>% 
-    setNames(namevec), 
-  uds.3B)
-uds.3B %>% 
-  arrange(BHCMISID, Year)
-
-# Table 4
-uds.4.2012 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-uds.4.2013 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-
-uds.4.2014 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-uds.4.2015 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table4", skip = 2) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-uds.4.2016 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-
-uds.4.2017 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-uds.4.2018 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-uds.4.2019 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-
-uds.4.2020 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-uds.4.2021 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-uds.4.2022 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2022-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-uds.4.2023 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2023-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(BHCMISID, GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L7_Ca, T4_L7_Cb, T4_L8_Ca, T4_L8_Cb, T4_L9_Ca, T4_L9_Cb, T4_L10_Ca, T4_L10_Cb, T4_L11_Ca, T4_L11_Cb)
-
-namevec <- c("Year", "BHCMISID", "ModernGranteeID", "<100%", "101-150%", "151-200%", ">200%", "Unknown", "FarmWorker", "Homeless", 
-             "Uninsured.young", "Uninsured.old", "MCD.young", "MCD.old", "MCR.young", "MCR.old", "OtherPublic.young", "OtherPublic.old", "COM.young", "COM.old")
-uds.4 <- rbind(cbind(Year = 2012, uds.4.2012),
-               cbind(Year = 2013, uds.4.2013),
-               cbind(Year = 2014, uds.4.2014),
-                  cbind(Year = 2015, uds.4.2015),
-                  cbind(Year = 2016, uds.4.2016),
-                  cbind(Year = 2017, uds.4.2017),
-
-                  cbind(Year = 2018, uds.4.2018),
-                  cbind(Year = 2019, uds.4.2019), 
-                  cbind(Year = 2020, uds.4.2020),
-                  cbind(Year = 2021, uds.4.2021),
-                  cbind(Year = 2022, uds.4.2022),
-                  cbind(Year = 2023, uds.4.2023)) %>%
-
-  rename_all(vars(namevec), function(x) namevec)
-
-uds.4 <- rbind(
-uds.cw %>% 
-  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table4.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
-  filter(Year %in% c(2007, 2011)) %>% 
-  select(Year, BHCMIS.ID, ModernGranteeID, T4_L1_CA, T4_L2_CA, T4_L3_CA, T4_L4_CA, T4_L5_CA, 
-         T4_L16_CA, T4_L23_CA, 
-         T4_L7_CA, T4_L7_CB, T4_L8_CA, T4_L8_CB, T4_L9_CA, T4_L9_CB, T4_L10_CA, T4_L10_CB, T4_L11_CA, T4_L11_CB) %>% 
-  setNames(namevec), 
-uds.cw %>% 
-  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table4.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
-  filter(Year %in% c(2008:2010)) %>% 
-  select(Year, BHCMIS.ID, ModernGranteeID, T4_L1_CA, T4_L2_CA, T4_L3_CA, T4_L4_CA, T4_L5_CA, 
-         T4_L16_CA, T4_L23_CA, 
-         T4_L7_CMIA, T4_L7_CMIB, T4_L8_CMIA, T4_L8_CMIB, T4_L9_CMIA, T4_L9_CMIB, T4_L10_CMIA, T4_L10_CMIB, T4_L11_CMIA, T4_L11_CMIB) %>% 
-  setNames(namevec), 
-uds.4)
-
-uds.4 %>% 
-  arrange(BHCMISID, Year)
-
-# Put covariate tables together
-
-uds.covariates <- inner_join(uds.3B, uds.4, by = c("Year","BHCMISID","ModernGranteeID"))
-
-for (i in 4:ncol(uds.covariates)){
-  uds.covariates[,i] <- as.numeric(gsub("-", "", uds.covariates[,i]))
-}
-
-#uds.covariates %>% filter(`Grant Number` == "H80CS24200")
-
-for (i in 1:nrow(uds.covariates)){
-  if (!is.na(uds.covariates[i,]$Total)) {
-uds.covariates[i,is.na(uds.covariates[i,])] <- 0
-} 
-}
-
-uds.covariates <-  uds.covariates %>% 
-    mutate(Pct.NHA = NHA / Total * 100,
-         Pct.NHB = NHB / Total * 100,
-         Pct.HL = HL / Total * 100,
-         Pct.NHW = NHW / Total * 100,
-         Pct.ESL = Eng2ndLang / Total * 100,
-         Pct.LessThan100pctFPL = ifelse(Total == Unknown, 100, `<100%` / (Total- Unknown) * 100),
-         Pct.LessThan200pctFPL = ifelse(Total == Unknown, 100, (`<100%` + `101-150%` + `151-200%`) / (Total - Unknown) * 100),
-         Pct.FarmWorker = FarmWorker / Total * 100,
-         Pct.Homeless = Homeless / Total * 100,
-         Pct.None = (Uninsured.young + Uninsured.old) / Total * 100, 
-         Pct.MCD = (MCD.young + MCD.old) / Total * 100, 
-         Pct.MCR = (MCR.young + MCR.old) / Total * 100, 
-         Pct.COM = (COM.young + COM.old) / Total * 100) %>% 
-    select(Year:ModernGranteeID, Total, Pct.NHA:Pct.COM)
-
-uds.covariates %>% 
-  arrange(BHCMISID, Year)
-
-```
-
-## Table 6A
-```{r}
-uds.6a.2011andBefore <- uds.cw %>% 
-  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table6A.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
-  select(BHCMIS.ID, Year, T6A_L10_CA:T6A_L26D_CB) %>% 
-  filter(Year >= 2010) %>% 
-  rename(BHCMISID = BHCMIS.ID) %>% 
-  rename_all(.funs = toupper)
-
-uds.6a.2012 <- cbind(Year = 2012, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper)
-uds.6a.2013 <- cbind(Year = 2013, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper)
-
-uds.6a.2014 <- cbind(Year = 2014, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper)
-uds.6a.2015 <- cbind(Year = 2015, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table6A", skip = 2)) %>% rename_all(.funs = toupper)
-uds.6a.2016 <- cbind(Year = 2016, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
-
-uds.6a.2017 <- cbind(Year = 2017, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
-uds.6a.2018 <- cbind(Year = 2018, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
-uds.6a.2019 <- cbind(Year = 2019, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
-
-uds.6a.2020 <- cbind(Year = 2020, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table6A", skip = 1)) %>% rename_all(.funs = toupper)
-uds.6a.2021 <- cbind(Year = 2021, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper) %>% filter(!is.na(BHCMISID))
-
-uds.6a.2022 <- cbind(Year = 2022, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2022-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper) %>% filter(!is.na(BHCMISID))
-uds.6a.2023 <- cbind(Year = 2023, read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2023-Full-Dataset.xlsx", sheet = "Table6A", skip = 0)) %>% rename_all(.funs = toupper) %>% filter(!is.na(BHCMISID))
-
-uds.6a.2012[,-c(1:3)] <- data.frame(sapply(uds.6a.2012[,-c(1:3)], as.numeric))
-uds.6a.2013[,-c(1:3)] <- data.frame(sapply(uds.6a.2013[,-c(1:3)], as.numeric))
-
-uds.6a.2014[,-c(1:3)] <- data.frame(sapply(uds.6a.2014[,-c(1:3)], as.numeric))
-uds.6a.2015[,-c(1:3)] <- data.frame(sapply(uds.6a.2015[,-c(1:3)], as.numeric))
-uds.6a.2016[,-c(1:3)] <- data.frame(sapply(uds.6a.2016[,-c(1:3)], as.numeric))
-
-uds.6a.2017[,-c(1:3)] <- data.frame(sapply(uds.6a.2017[,-c(1:3)], as.numeric))
-uds.6a.2018[,-c(1:3)] <- data.frame(sapply(uds.6a.2018[,-c(1:3)], as.numeric))
-uds.6a.2019[,-c(1:3)] <- data.frame(sapply(uds.6a.2019[,-c(1:3)], as.numeric))
-
-uds.6a.2020[,-c(1:3)] <- data.frame(sapply(uds.6a.2020[,-c(1:3)], as.numeric))
-uds.6a.2021[,-c(1:3)] <- data.frame(sapply(uds.6a.2021[,-c(1:3)], as.numeric))
-uds.6a.2022[,-c(1:3)] <- data.frame(sapply(uds.6a.2022[,-c(1:3)], as.numeric))
-uds.6a.2023[,-c(1:3)] <- data.frame(sapply(uds.6a.2023[,-c(1:3)], as.numeric))
-
-uds.6a <- bind_rows(uds.6a.2012, uds.6a.2013, uds.6a.2014,
-      uds.6a.2015, uds.6a.2016, uds.6a.2017, uds.6a.2018, uds.6a.2019, uds.6a.2020, uds.6a.2021, uds.6a.2022, uds.6a.2023, uds.6a.2011andBefore) %>% 
-  arrange(BHCMISID, YEAR) %>% 
-  select(YEAR:T6A_L34_CB)
-
-uds.6a
-```
-
-## Table 6B Measures
-```{r}
-
-uds.6b.2012 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2013 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
-
-uds.6b.2014 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2015 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 1) 
-uds.6b.2016 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
-
-uds.6b.2017 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2018 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2019 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
-
-uds.6b.2020 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2021 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2022 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2022-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
-uds.6b.2023 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2023-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)
-
-uds.6b.names <- c("BHCMISID","GrantNumber","Imm.Num","Imm.Rate","imm.denom","Pap.Rate","Pap.Num","pap.denom",
-                  "crc.rate","crc.num","crc.denom", 
-                  "ChildBMI.rate","ChildBMI.num","ChildBMI.denom","AdultBMI.rate","AdultBMI.num","AdultBMI.denom", "asthma.rate","asthma.num","asthma.denom", 
-                  "cad.rate","cad.num","cad.denom", "ivd.rate","ivd.num","ivd.denom")
-
-uds.quality.6b <- rbind(
-  cbind(Year = 2012, uds.6b.2012[,c(1:8, 30:32, 9:14, 21:29)] %>% setNames(uds.6b.names)),
-  cbind(Year = 2013, uds.6b.2013[,c(1:8, 30:32, 9:14, 21:29)] %>% setNames(uds.6b.names)),
-
-  cbind(Year = 2014, uds.6b.2014[,c(1:8, 27:29, 9:14, 18:26)] %>% setNames(uds.6b.names)),
-  cbind(Year = 2015, uds.6b.2015[,c(1:8, 27:29, 9:14, 18:26)] %>% setNames(uds.6b.names)),
-  cbind(Year = 2016, uds.6b.2016[,c(1:8, 27:29, 9:14, 18:26)] %>% setNames(uds.6b.names)),
-
-  cbind(Year = 2017, uds.6b.2017[,c(1:8, 27:29, 9:14, 18:26)] %>% setNames(uds.6b.names)),
-  cbind(Year = 2018, uds.6b.2018[,c(1:8, 27:29, 9:14, 18:26)] %>% setNames(uds.6b.names)),
-  cbind(Year = 2019, uds.6b.2019[,c(1:8, 27:29, 9:14, 18:26)] %>% setNames(uds.6b.names)),
-
-  cbind(Year = 2020, cbind(uds.6b.2020[,c(1:8, 27:29, 12:17)], NA, NA, NA, uds.6b.2020[,c(21:26)]) %>% setNames(uds.6b.names)),
-  cbind(Year = 2021, cbind(uds.6b.2021[,c(1:8, 27:29, 12:17)], NA, NA, NA, uds.6b.2021[,c(21:26)]) %>% setNames(uds.6b.names)),
-
-  cbind(Year = 2022, cbind(uds.6b.2022[,c(1:8, 27:29, 12:17)], NA, NA, NA, uds.6b.2022[,c(21:26)]) %>% setNames(uds.6b.names)),
-  cbind(Year = 2023, cbind(uds.6b.2023[,c(1:8, 27:29, 12:17)], NA, NA, NA, uds.6b.2023[,c(21:26)]) %>% setNames(uds.6b.names))) %>%
-
-  mutate(imm.rate = as.numeric(Imm.Num) / as.numeric(imm.denom), 
-         pap.rate = as.numeric(Pap.Num) / as.numeric(pap.denom), 
-         imm.denom = as.numeric(imm.denom), 
-         pap.denom = as.numeric(pap.denom), 
-         crc.rate = as.numeric(crc.num) / as.numeric(crc.denom), 
-         crc.denom = as.numeric(crc.denom), 
-         childbmi.rate = as.numeric(as.numeric(ChildBMI.num) / as.numeric(ChildBMI.denom)), 
-         childbmi.denom = as.numeric(ChildBMI.denom),
-         adultbmi.rate = as.numeric(as.numeric(AdultBMI.num) / as.numeric(AdultBMI.denom)), 
-         adultbmi.denom = as.numeric(AdultBMI.denom),
-         asthma.rate = as.numeric(as.numeric(asthma.num) / as.numeric(asthma.denom)), 
-         cad.rate = as.numeric(as.numeric(cad.num) / as.numeric(cad.denom)), 
-         ivd.rate = as.numeric(as.numeric(ivd.num) / as.numeric(ivd.denom)), 
-         ) %>% 
-  select(Year, BHCMISID, GrantNumber, imm.rate, imm.denom, pap.rate, pap.denom, crc.rate, crc.denom, asthma.rate, cad.rate, ivd.rate, childbmi.rate, childbmi.denom, adultbmi.rate, adultbmi.denom) %>%
-
-  bind_rows(uds.cw %>% 
-  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table6B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
-  filter(Year != 2008) %>% 
-    arrange(BHCMIS.ID, Year) %>% 
-  #select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
-  #filter(BHCMIS.ID == '010060') %>% 
-  select(BHCMIS.ID, Year, T6B_L10_N_CC:T6B_L11_D_CC, T6B_L10_CA:T6B_L11_CC, T6B_L12_CA:T6B_L13_CC) %>% 
-  mutate(imm.rate = ifelse(Year == 2009, T6B_L10_N_CC / T6B_L10_D_CC, 
-                    ifelse(Year %in% c(2010:2011), T6B_L10_CC / T6B_L10_CB, NA)), 
-         imm.denom = ifelse(Year == 2009, T6B_L10_D_CC, 
-                     ifelse(Year %in% c(2010:2011), T6B_L10_CA, NA)),
-         pap.rate = ifelse(Year == 2009, T6B_L11_N_CC / T6B_L11_D_CC, 
-                    ifelse(Year %in% c(2010:2011), T6B_L11_CC / T6B_L11_CB, NA)), 
-         pap.denom = ifelse(Year == 2009, T6B_L11_D_CC, 
-                     ifelse(Year %in% c(2010:2011), T6B_L11_CA, NA)), 
-         childbmi.rate = T6B_L12_CC / T6B_L12_CB, 
-         childbmi.denom = T6B_L12_CA, 
-         adultbmi.rate = T6B_L13_CC / T6B_L13_CB, 
-         adultbmi.denom = T6B_L13_CA ) %>% 
-  select(BHCMIS.ID, Year, imm.rate:adultbmi.denom) %>% 
-  rename(BHCMISID = BHCMIS.ID)) %>% 
-    arrange(BHCMISID, Year)
-
-## Removes FQHCs that were not open during those first 3 years of the study period
-uds.quality.6b <- uds.quality.6b %>% 
-  inner_join(uds.cw %>% mutate(STATE = toupper(STATE)) %>% unique() %>% mutate(STATE = ifelse(BHCMIS.ID == '010530', 'ME', 
-                                                                                       ifelse(BHCMIS.ID == '090090', 'AZ', STATE))) %>% 
-               select(BHCMIS.ID, STATE) %>% unique(), by = c("BHCMISID" = "BHCMIS.ID"))
-
-# uds.cw %>% mutate(STATE = toupper(STATE)) %>% 
-#   select(BHCMIS.ID, STATE)  %>% unique() %>% 
-#   group_by(BHCMIS.ID) %>% 
-#   mutate(row = row_number()) %>% 
-#   group_by(BHCMIS.ID) %>% 
-#   mutate(max.row = max(row)) %>% 
-#   filter(max.row > 1)
-#
-# uds.cw %>% 
-#   mutate(STATE = toupper(STATE)) %>% 
-#   select(BHCMIS.ID, STATE) %>% 
-#   group_by(BHCMIS.ID, STATE) %>% 
-#   summarise(n()) %>% 
-#   filter(BHCMIS.ID %in% c('010530','090090'))
-# 
-# uds.cw %>% filter(BHCMIS.ID == '010530')
-
-```
-
-## Table 6B - EHR or Sampling Used
-```{r}
-vec.years <- 2012:2023
-vec.skips <- rep(0, length(vec.years)) 
-vec.skips[c(4)] <- 2
-vec.skips[c(5,6,7,8,9)] <- 1
-vec.files <- paste("//Users/markow/Dropbox/Git/UDS/UDS-",vec.years, "-Full-Dataset.xlsx", sep = "")
-
-uds.quality.sampling.v.ehr <- uds.cw %>% 
-  inner_join(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table6B.csv"), by = c("link.ID" = "BHCMIS.ID", "Year")) %>% 
-  filter(Year != 2008) %>% 
-    arrange(BHCMIS.ID, Year) %>% 
-  #select(BHCMIS.ID:link.ID, T3B_L1_CA:T3B_L7_CC) %>% 
-  #filter(BHCMIS.ID == '010060') %>% 
-  #select(BHCMIS.ID, Year, T6B_L10_N_CC:T6B_L11_D_CC, T6B_L10_CA:T6B_L11_CC) %>% 
-  select(BHCMIS.ID, Year, T6B_L10_CA, T6B_L10_CB, T6B_L11_CA, T6B_L11_CB, T6B_L12_CA,	T6B_L12_CB, T6B_L13_CA, T6B_L13_CB) %>% 
-  cbind(T6B_L19_CA = NA,	T6B_L19_CB = NA) %>% 
-  rename(YEAR = Year)
-
-for (i in 1:length(vec.years)){
-read_excel(vec.files[i], sheet = "Table6B", skip = vec.skips[i])
-temp <- read_excel(vec.files[i], sheet = "Table6B", skip = vec.skips[i])%>% 
-  select(BHCMISID, T6b_L10_Ca, T6b_L10_Cb, T6b_L11_Ca, T6b_L11_Cb, T6B_L19_Ca,	T6B_L19_Cb, T6b_L12_Ca,	T6b_L12_Cb, T6b_L13_Ca, T6b_L13_Cb) %>% 
-    mutate(Year = vec.years[i])
-colnames(temp) <- toupper(colnames(temp))
-colnames(temp)[1] <- "BHCMIS.ID"
-
-  uds.quality.sampling.v.ehr <- uds.quality.sampling.v.ehr %>% 
-    rbind(temp) %>% 
-    arrange(BHCMIS.ID, YEAR)
-}
-
-uds.quality.sampling.v.ehr <- uds.quality.sampling.v.ehr %>% 
-  mutate(imm.ehr = ifelse(T6B_L10_CA == T6B_L10_CB, 1, 0), 
-         pap.ehr = ifelse(T6B_L11_CA == T6B_L11_CB, 1, 0), 
-         crc.ehr = ifelse(T6B_L19_CA == T6B_L19_CB, 1, 0),
-         childbmi.ehr = ifelse(T6B_L12_CA == T6B_L12_CB, 1, 0), 
-         adultbmi.ehr = ifelse(T6B_L13_CA == T6B_L13_CB, 1, 0)) %>% 
-  mutate(ehr = imm.ehr + pap.ehr + crc.ehr + childbmi.ehr + adultbmi.ehr)
-
-```
-
-## Table 7 Clinical Measures
-
-```{r}
-
-uds.7.2012 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
-uds.7.2013 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2013-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0)
-
-uds.7.2014 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
-uds.7.2015 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 1) 
-uds.7.2016 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0)
-
-uds.7.2017 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
-uds.7.2018 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
-uds.7.2019 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0)
-
-uds.7.2020 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 0) 
-uds.7.2021 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 1) 
-uds.7.2022 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2022-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 1) 
-uds.7.2023 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2023-Full-Dataset.xlsx", sheet = "Table7Clinicalmeasures", skip = 1)
-
-uds.7.names <- c("BHCMISID","GrantNumber","Race","Ethnicity","htn.total","htn.control","dm.total","dm.controlled")
-
-uds.quality.7 <- rbind(
-  cbind(Year = 2012, uds.7.2012[,c(1:6, 8:9)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
-  cbind(Year = 2013, uds.7.2013[,c(1:6, 8:9)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
-
-  cbind(Year = 2014, uds.7.2014[,c(1:6, 8:9)] %>% setNames(uds.7.names)),
-  cbind(Year = 2015, uds.7.2015[,c(1:4, 8:9, 11, 14)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
-  cbind(Year = 2016, uds.7.2016[,c(1:4, 8:9, 11, 14)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
-
-  cbind(Year = 2017, uds.7.2017[,c(1:4, 8:9, 11, 14)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
-  cbind(Year = 2018, uds.7.2018[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
-  cbind(Year = 2019, uds.7.2019[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
-
-  cbind(Year = 2020, uds.7.2020[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
-  cbind(Year = 2021, uds.7.2021[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
-  cbind(Year = 2022, uds.7.2022[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled))),
-  cbind(Year = 2023, uds.7.2023[,c(1:4, 8:9, 11:12)] %>% setNames(uds.7.names) %>% mutate(dm.controlled = as.numeric(dm.total) - as.numeric(dm.controlled)))) %>% 
-  mutate(htn.rate = as.numeric(htn.control) / as.numeric(htn.total), 
-         dm.rate = as.numeric(dm.controlled) / as.numeric(dm.total), 
-         htn.total = as.numeric(htn.total), 
-         dm.total = as.numeric(dm.total)) %>% 
-  select(Year:Ethnicity, htn.total, htn.rate, dm.total, dm.rate) %>%
-
-  bind_rows(read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table7clin.csv") %>% 
-  select(Year, ModernGranteeID:dm.controlled) %>% 
-  rename(GrantNumber = ModernGranteeID) %>% 
-    mutate(htn.rate = as.numeric(htn.control) / as.numeric(htn.total), 
-         dm.rate = as.numeric(dm.controlled) / as.numeric(dm.total), 
-         htn.total = as.numeric(htn.total), 
-         dm.total = as.numeric(dm.total)) %>% 
-    select(Year:Ethnicity, htn.total, htn.rate, dm.total, dm.rate)) %>% 
-    arrange(GrantNumber, Year, Ethnicity, Race)
-
-## Removes FQHCs that were not open during those first 3 years of the study period
-uds.quality.7 <- uds.quality.7 %>% 
-  inner_join(uds.cw %>% mutate(STATE = toupper(STATE)) %>% unique() %>% mutate(STATE = ifelse(BHCMIS.ID == '010530', 'ME', 
-                                                                                       ifelse(BHCMIS.ID == '090090', 'AZ', STATE))) %>% 
-               select(ModernGranteeID, STATE) %>% unique(), by = c("GrantNumber" = "ModernGranteeID")) %>% 
-  mutate(Race = ifelse(Race == '-', NA, Race),
-         Ethnicity = ifelse(Ethnicity == '-', NA, Ethnicity))
-
-uds.quality.7[is.na(uds.quality.7$htn.total),]$htn.total <- 0
-uds.quality.7[is.na(uds.quality.7$htn.rate),]$htn.rate <- 0
-uds.quality.7[is.na(uds.quality.7$dm.total),]$dm.total <- 0
-uds.quality.7[is.na(uds.quality.7$dm.rate),]$dm.rate <- 0
-
-uds.quality.7 <- uds.quality.7 %>% 
-   inner_join(uds.cw %>% filter(Year == 2011) %>% unique() %>% select(ModernGranteeID, BHCMIS.ID), by = c("GrantNumber" = "ModernGranteeID")) %>% 
-  arrange(Year, BHCMIS.ID, GrantNumber) %>% 
-  mutate(BHCMISID = ifelse(is.na(BHCMISID), BHCMIS.ID, BHCMISID))
-
-uds.quality.7 %>% 
-  filter(Race == " Total" | is.na(Race))%>% 
-  arrange(BHCMISID, Year) %>% 
-  group_by(Year, BHCMISID) %>% 
-  summarise(htn.rate = sum(htn.rate * htn.total) / sum(htn.total), 
-            htn.total = sum(htn.total), 
-            dm.rate = sum(dm.rate * dm.total) / sum(dm.total), 
-            dm.total = sum(dm.total)) %>% 
-  arrange(BHCMISID, Year)
-```
-
-```{r}
-# df.comp %>% 
-#   ggplot(aes(x = Year, y = dm.rate)) + geom_point() + geom_smooth()
-
-```
-
-## Financials
-```{r}
-cw <- read_excel("/Users/markow/Dropbox/Git/Data/UDS-990 Crosswalk.xlsx")
-
-fins.revenue.expenses <- read.csv("//Users/markow/Dropbox/Git/Data/FQHC_Revenue_vs_Expenses.csv", header = TRUE)
-names(fins.revenue.expenses) <- gsub("^X\\.", "", names(fins.revenue.expenses))
-names(fins.revenue.expenses) <- gsub("\\.\\.", "", names(fins.revenue.expenses))
-
-staffing <- read.csv("/Users/markow/Dropbox/Git/Data/FQHC_Staffing.csv")
-assliabs <- read.csv("/Users/markow/Dropbox/Git/Data/FQHC_Assets_and_Liabilities.csv")
-
-fins.revenue.expenses <- uds.cw %>% filter(Year == 2011) %>% unique() %>% select(ModernGranteeID, BHCMIS.ID) %>% 
-  left_join(cw, by = c("ModernGranteeID" = "Grant Number")) %>% 
-  left_join(fins.revenue.expenses, by = c("EIN" = "EIN")) %>% 
-  select(ModernGranteeID:EIN, form_year:fringe_rate) %>% 
-  left_join(staffing %>% select(EIN:Staff), by = c("EIN","form_year" = "Year"))
-
-## Fixing some dumb mistake
-
-# fixing.cw <- cbind(NewEINs = EINs[c(1:21, 23:323, 325:499, 501:617, 619:669, 671:738,  740:782, 784:790, 792:819, 821:989, 991:1106, 1108:1184, 1186)], 
-#       assliabs %>% 
-#   mutate(ch = Year - lag(Year)) %>% 
-#   filter(is.na(ch) | ch < 0)) %>% 
-#   mutate(Y = lead(X) - 1) %>% 
-#   select(EIN, NewEINs, X, Y)
-# 
-# 
-# for (k in 1:max(assliabs$X)){
-#   assliabs[k,]$EIN <- assliabs[k,] %>% 
-#     left_join(fixing.cw, by = c("EIN")) %>% 
-#     filter(X.x >= X.y & X.x <= Y) %>% 
-#     select(NewEINs) %>% 
-#     unlist()
-# }
-
-fins.revenue.expenses <- fins.revenue.expenses %>% 
-  left_join(assliabs %>% select(EIN:Liabilities), by = c("EIN","form_year" = "Year"))
-
-```
-
-## APM History
-
-```{r}
-
-apm.history <- read_excel("/Users/markow/Dropbox/Git/APMs/data_raw/APM_History.xlsx") %>%
- mutate(Class = ifelse(is.na(Year), "0 - Control", Classification))
-
-```
-
-## Full dataset
-
-```{r}
-
-## Broader definitions 5 / 7 quality measures significant improvements overall
-# included.years <- 2009:2021
-# included.treat <- 2013:2021
-
-## Original good filters
-# included.years <- 2009:2019
-# included.treat <- 2013:2019
-
- included.years <- 2014:2023
- included.treat <- 2016:2023
-
-df.comp <- uds.covariates %>% 
-  select(Year:BHCMISID, Total:Pct.COM) %>% 
-  inner_join(uds.cw %>% select(BHCMIS.ID, STATE) %>% 
-               mutate(STATE = toupper(STATE)) %>% 
-               unique() %>% mutate(STATE = ifelse(BHCMIS.ID == '010530', 'ME', ifelse(BHCMIS.ID == '090090', 'AZ', STATE))) %>% unique(), by = c("BHCMISID" = "BHCMIS.ID")) %>% 
-  select(BHCMISID, Year, STATE, Total:Pct.COM) %>% 
-  arrange(BHCMISID, Year) %>% 
-  left_join(uds.6a, by = c("BHCMISID","Year" = "YEAR")) %>% 
-  left_join(uds.quality.6b %>% select(Year, BHCMISID, imm.rate:adultbmi.denom), by = c("BHCMISID","Year")) %>% 
-  left_join(uds.quality.7 %>% 
-  filter(Race == " Total" | is.na(Race)) %>% 
-  group_by(Year, BHCMISID) %>% 
-  summarise(htn.rate = sum(htn.rate * htn.total) / sum(htn.total), 
-            htn.total = sum(htn.total), 
-            dm.rate = sum(dm.rate * dm.total) / sum(dm.total), 
-            dm.total = sum(dm.total)) %>% 
-  arrange(BHCMISID, Year), by = c("BHCMISID","Year")) %>% 
-    left_join(fins.revenue.expenses, by = c("BHCMISID" = "BHCMIS.ID", "Year" = "form_year")) %>% 
-  inner_join(apm.history %>% rename(att = Year), by = c("STATE" = "Postal Code")) %>% 
-  ungroup() %>% 
-  mutate(att = ifelse(is.na(att), 0, att)) %>% 
-  mutate(ID = as.numeric(as.factor(BHCMISID))) %>% 
-  arrange(BHCMISID) %>% 
-  mutate(ACA = ifelse((STATE %in% c('MI','NH') & Year >= 2014) |
-                    (STATE %in% c('PA','IN','AK') & Year >= 2015) |
-                    (STATE %in% c('MT','LA') & Year >= 2016) |
-                    (STATE %in% c('VA','ME') & Year >= 2019) |
-                    (STATE %in% c('ID','UT','NE') & Year >= 2020) |
-                    (STATE %in% c('OK','MO') & Year >= 2021) |
-                    (STATE %in% c('AZ','AR','CA','CO','CT','DE','DC','HI','IL','IA','KY','MD','MA','MN','NV','NJ','NM','NY','ND','OH','OR','PA','RI','VT','VA','WA') & Year >= 2014), 1, 0))
-
-class.vec <- rep(sort(unique(df.comp$Classification)), table(df.comp$Classification))
-
-set.seed(123) #432
-
-df.comp <- df.comp %>% 
-  group_by(ID) %>% 
-  mutate(Class.random = ifelse(Class == "0 - Control", sample(class.vec, size = 1, replace = T), Class), 
-         att.random = ifelse(Class == "0 - Control", sample(included.treat, size = 1, replace = T), att)) %>% 
-                                 mutate(Tx = ifelse(Year >= att & att > 0, 1, 0)) %>% 
-  filter(Year %in% included.years) %>% 
-  mutate(year.rel = as.factor(ifelse(att.random > 0, Year - att.random, NA)), 
-         Treatment = ifelse(att > 0, 1, 0)) %>% 
-  select(BHCMISID:STATE, Name:ID, ACA:Treatment, Total:dm.total, fs_contributions:Liabilities)
-
-df.comp <- df.comp %>% 
-  left_join(df.comp %>% 
-  group_by(BHCMISID) %>% 
-  summarise(counts = n()) %>% filter(counts == length(included.years)), by = c("BHCMISID")) %>% 
-  group_by(BHCMISID) %>% 
-  mutate(closed = ifelse(is.na(counts) & Year == max(Year), 1, 0)) #%>%  filter(APM %in% c('Yes','No'))
-
-df.comp$year.rel <- relevel(as.factor(df.comp$year.rel), ref = "-1")
-
-## Filter for balanced panel, remove closures and late openings
-df.comp <- df.comp %>%
-  left_join(df.comp %>% summarise(Counts = n(), MinYear = min(Year)), by = c("BHCMISID")) %>%
-  filter(Counts == length(included.years)) #  filter(Counts < 13 & MinYear == 2009)    filter(Counts == length(included.years))
-
-## Remove some weird shit in CT
-df.comp <- df.comp %>% 
-  filter(BHCMISID != "01E00010") %>% 
-                mutate(HIV.prev = T6A_L1AND2_CB / Total * 100, 
-         HIV.care = T6A_L1AND2_CA / T6A_L1AND2_CB,
-
-         HepC.prev = T6A_L4B_CB / Total * 100,
-         HepC.care = T6A_L4B_CA / T6A_L4B_CB,
-
-         Asthma.prev = T6A_L5_CB / Total * 100,
-         Asthma.care = T6A_L5_CA / T6A_L5_CB,
-
-         # AbnormalPap.prev = T6A_L8_CB / Total * 100,
-         # AbnormalPap.care = T6A_L8_CA / T6A_L8_CB,
-         #
-         # ImmunizationsGiven.prev = T6A_L24_CB / Total * 100,
-         # ImmunizationsGiven.care = T6A_L24_CA / T6A_L24_CB,
-
-         HeartDisease.prev = T6A_L10_CB / Total * 100, 
-         HeartDisease.care = T6A_L10_CA / T6A_L10_CB,
-
-         # OverweightOrObesity.prev = T6A_L14A_CB / Total * 100, 
-         # OverweightOrObesity.care = T6A_L14A_CA / T6A_L14A_CB,
-
-         Depression.prev = T6A_L19A_CB / Total * 100, 
-         Depression.care = T6A_L19A_CA / T6A_L19A_CB,
-
-         Diabetes.prev = T6A_L9_CB / Total * 100, 
-         Diabetes.care = T6A_L9_CA / T6A_L9_CB,
-
-         Hypertension.prev = T6A_L11_CB / Total * 100, 
-         Hypertension.care = T6A_L11_CA / T6A_L11_CB) %>%  #%>%  filter(STATE != 'CT')
-select(BHCMISID:FIPS, Total:Pct.COM, HIV.prev:Hypertension.care , imm.rate:MinYear)
-
-```
-
-## Classify FQHCs into Treated, control based on zip codes
+## Z
 
@@
   #filter(`2011` == 1 & `2012` == 1 ) %>%  #  & `2012` == 1 & `2013` == 1 & `2014` == 1 & `2015` == 1 & `2016` == 1) %>%   
-  filter(`2014` == 1 & `2015` == 1) %>%  
+  #filter(`2010` == 1 & `2011` == 1 & `2012` == 1) %>%  
   #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
   #filter(is.na(NewClinicID)) %>%
-  select(`BHCMIS ID`:`2023`) %>% 
-  pivot_longer(cols = c(`2014`:`2023`)) %>% 
+  select(`BHCMIS ID`:`2021`) %>% 
+  pivot_longer(cols = c(`2010`:`2021`)) %>% 
   group_by(`BHCMIS ID`) %>% 
-  filter(min(value) == 1 ) %>% 
+  #filter(min(value) == 1 ) %>% 
   #filter(max(value) == last(value)) %>% 
@@
   left_join(df.comp, by = c("BHCMIS ID" = "BHCMISID", "Year"))
+
+table(table(dfc$`BHCMIS ID`))
 ```
-
-## Finalize the core set of measures, adjust Altman components for inf estimates
-```{r}
-
-dfc <- dfc %>% 
-  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
-         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
-           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
-               CostPerPat = ngla_expense / Total, 
-               months_of_cash = as.numeric(months_of_cash),
-               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
-               quick_ratio = as.numeric(quick_ratio),
-               Liquidity = (Assets - Liabilities) / Assets,
-               Profitability = ngla_net_gain_loss / Assets, #Assets, 
-               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
-               NetWorth = (Assets - Liabilities) / Liabilities, 
-            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
-            LiabPctAssets = Liabilities / Assets, 
-            Eff = ngla_prog_serv_revenue / Assets, 
-            LiabPctRev = ngla_prog_serv_revenue / ngla_expense)
-
-dfc <- dfc %>% 
-  mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity), 
-         Profitability = ifelse(is.infinite(Profitability), NA, Profitability), 
-         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency), 
-         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
-         #Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
-         Altman = 0.18 * quick_ratio + 0.3 * Profitability + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
-  mutate(Att.random = ifelse(Att > 0, Att, NA), 
-         Distress = ifelse(Altman < 2.6, 1, 0))
-
-vec.atts <- rep(included.treat, (table(comp.initial$Att) / 12)[-1])
-
-set.seed(123)
-dfc <- rbind(dfc %>% filter(Att > 0), dfc %>% 
-  filter(Att == 0) %>% 
-  group_by(`BHCMIS ID`) %>% 
-  mutate(Att.random = sample(size = 1, vec.atts, replace = TRUE))) %>% 
-  mutate(year.rel = Year - Att.random)
-
-######adjust Altman components for inf estimates
-
-```
-
-## Write the file
-```{r}
-# write_csv(dfc, file = "/Users/markow/Dropbox/Git/Competition/data_processed/manuscript_analyticalfile.csv")
-# write.csv(uds.sites.full, file = "/Users/markow/Dropbox/Git/Competition/data_processed/manuscript_sites_geocoded.csv")
-
-```

### 2024-10-01 code/manuscript_altanalysis.Rmd
more new analysis

@@
 library(usmap)
+library(ivreg)
+library(fixest)
+library(sandwich)
+library(lmtest)
 ```
@@
 
-## Z
+## Z: Competitive Shocks and Y: Outcomes
+
+```{r}
+
+## Broader definitions 5 / 7 quality measures significant improvements overall
+# included.years <- 2009:2021
+# included.treat <- 2013:2021
+
+## Original good filters
+# included.years <- 2009:2019
+# included.treat <- 2013:2019
+
+included.years <- 2010:2023
+included.treat <- 2013:2023
+
+df.comp <- uds.covariates %>% 
+  select(Year:BHCMISID, Total:Pct.COM) %>% 
+  select(BHCMISID, Year, Total:Pct.COM) %>% 
+  arrange(BHCMISID, Year) %>% 
+  left_join(uds.6a, by = c("BHCMISID","Year" = "YEAR")) %>% 
+  left_join(uds.quality.6b %>% select(Year, BHCMISID, imm.rate:adultbmi.denom), by = c("BHCMISID","Year")) %>% 
+  left_join(uds.quality.7 %>% 
+  filter(Race == " Total" | is.na(Race)) %>% 
+  group_by(Year, BHCMISID) %>% 
+  summarise(htn.rate = sum(htn.rate * htn.total) / sum(htn.total), 
+            htn.total = sum(htn.total), 
+            dm.rate = sum(dm.rate * dm.total) / sum(dm.total), 
+            dm.total = sum(dm.total)) %>% 
+  arrange(BHCMISID, Year), by = c("BHCMISID","Year")) %>% 
+    left_join(fins.revenue.expenses, by = c("BHCMISID" = "BHCMIS.ID", "Year" = "form_year")) %>%
+
+  mutate(ID = as.numeric(as.factor(BHCMISID))) %>% 
+  arrange(BHCMISID)
+
+df.comp <- df.comp %>% 
+  left_join(df.comp %>% 
+  group_by(BHCMISID) %>% 
+  summarise(counts = n()) %>% filter(counts == length(included.years)), by = c("BHCMISID")) %>% 
+  group_by(BHCMISID) %>% 
+  mutate(closed = ifelse(is.na(counts) & Year == max(Year), 1, 0)) #%>%  filter(APM %in% c('Yes','No'))
+
+#df.comp$year.rel <- relevel(as.factor(df.comp$year.rel), ref = "-1")
+
+## Filter for balanced panel, remove closures and late openings
+df.comp <- df.comp %>%
+  left_join(df.comp %>% summarise(Counts = n(), MinYear = min(Year)), by = c("BHCMISID")) #%>%  filter(Counts == length(included.years)) #  filter(Counts < 13 & MinYear == 2009)    filter(Counts == length(included.years))
+
+## Remove some weird shit in CT
+df.comp <- df.comp %>% 
+  filter(BHCMISID != "01E00010") %>% 
+                mutate(HIV.prev = T6A_L1AND2_CB / Total * 100, 
+         HIV.care = T6A_L1AND2_CA / T6A_L1AND2_CB,
+
+         HepC.prev = T6A_L4B_CB / Total * 100,
+         HepC.care = T6A_L4B_CA / T6A_L4B_CB,
+
+         Asthma.prev = T6A_L5_CB / Total * 100,
+         Asthma.care = T6A_L5_CA / T6A_L5_CB,
+
+         # AbnormalPap.prev = T6A_L8_CB / Total * 100,
+         # AbnormalPap.care = T6A_L8_CA / T6A_L8_CB,
+         #
+         # ImmunizationsGiven.prev = T6A_L24_CB / Total * 100,
+         # ImmunizationsGiven.care = T6A_L24_CA / T6A_L24_CB,
+
+         HeartDisease.prev = T6A_L10_CB / Total * 100, 
+         HeartDisease.care = T6A_L10_CA / T6A_L10_CB,
+
+         # OverweightOrObesity.prev = T6A_L14A_CB / Total * 100, 
+         # OverweightOrObesity.care = T6A_L14A_CA / T6A_L14A_CB,
+
+         Depression.prev = T6A_L19A_CB / Total * 100, 
+         Depression.care = T6A_L19A_CA / T6A_L19A_CB,
+
+         Diabetes.prev = T6A_L9_CB / Total * 100, 
+         Diabetes.care = T6A_L9_CA / T6A_L9_CB,
+
+         Hypertension.prev = T6A_L11_CB / Total * 100, 
+         Hypertension.care = T6A_L11_CA / T6A_L11_CB) %>%  #%>%  filter(STATE != 'CT')
+select(BHCMISID:Year, Total:Pct.COM, HIV.prev:Hypertension.care , imm.rate:MinYear)
+
+```
 
@@
 
+dfc <- dfc %>% 
+  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate + cad.rate + asthma.rate + ivd.rate ) / 9 * 100, 
+         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
+           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
+               CostPerPat = ngla_expense / Total, 
+               months_of_cash = as.numeric(months_of_cash),
+               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
+               quick_ratio = as.numeric(quick_ratio),
+               Liquidity = (Assets - Liabilities) / Assets,
+               Profitability = ngla_net_gain_loss / Assets, #Assets, 
+               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
+               NetWorth = (Assets - Liabilities) / Liabilities, 
+            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
+            LiabPctAssets = Liabilities / Assets, 
+            Eff = ngla_prog_serv_revenue / Assets, 
+            LiabPctRev = ngla_prog_serv_revenue / ngla_expense)
+
+dfc <- dfc %>% 
+  mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity), 
+         Profitability = ifelse(is.infinite(Profitability), NA, Profitability), 
+         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency), 
+         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
+         #Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
+         Altman = 0.18 * quick_ratio + 0.3 * Profitability + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
+  mutate(Att.random = ifelse(Att > 0, Att, NA), 
+         Distress = ifelse(Altman < 2.6, 1, 0))
+
 table(table(dfc$`BHCMIS ID`))
 ```
+
+## D: HHI, and Bring them Together
+
+```{r}
+
+df.zip <- uds.zip %>% 
+  inner_join(clinics.in.zips, by = c("ZipCode" = "Zip","ReportingYear" = "Year")) %>% 
+  select(BHCMISID, GrantNumber, ReportingYear, ZipCode, NumberofPatients)
+
+df.zip.totals <- df.zip %>% 
+  group_by( ReportingYear, ZipCode) %>% 
+  summarise(Totals = sum(NumberofPatients))
+
+df.zip <- df.zip %>% 
+  left_join(df.zip.totals, by = c("ZipCode","ReportingYear")) %>% 
+  group_by(BHCMISID, GrantNumber, ReportingYear) %>% 
+  summarise(MS_num = sum(NumberofPatients, na.rm = TRUE), 
+            MS_denom = sum(Totals, na.rm = TRUE)) %>% 
+  mutate(MS = 100 - (MS_num / MS_denom * 100))
+
+df.mt <- dfc %>% 
+  left_join(df.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear")) %>% 
+  mutate(logPatsPerStaff = ifelse(is.infinite(log(Total / Staff)), NA, log(Total / Staff))) %>% 
+  mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
+         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5, 
+         Intensity.w = (HIV.care * HIV.prev + HepC.care * HepC.prev + Asthma.care * Asthma.prev + HeartDisease.care * HeartDisease.prev + Depression.care * Depression.prev + Diabetes.care * Diabetes.prev + Hypertension.care * Hypertension.prev) /
+                  (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev)) %>% 
+  mutate(dm.rate = dm.rate * 100, 
+         htn.rate = htn.rate * 100, 
+         pap.rate = pap.rate * 100, 
+         crc.rate = crc.rate * 100, 
+         childbmi.rate = childbmi.rate * 100, 
+         adultbmi.rate = adultbmi.rate * 100, 
+         asthma.rate = asthma.rate * 100, 
+         cad.rate = cad.rate * 100, 
+         ivd.rate = ivd.rate * 100)
+```
+
+# Analysis
+
+## Model
+
+```{r}
+
+df.temptemp <- df.mt %>% 
+  rename(ID = ID.x) %>% 
+  mutate(Closed = ifelse(lead(is.na(Sites)), 1, 0)) %>% 
+  select(value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Complexity, Intensity, Pct.None:Pct.COM, CostPerPat, Altman) %>% 
+  unique() %>% 
+  filter(Year >= 2012)
+
+coeffs <- c(0,0,0,0)
+
+for (k in 1:(ncol(df.temptemp)-13)){
+
+  df.temptemptemp <- df.temptemp
+  colnames(df.temptemptemp)[(13+k)] <- "Outcome"
+  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless  | I(MS/10) ~ value + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
+
+  coeffs <- rbind(coeffs, model$coeftable[2,])
+
+}
+data.frame(cbind(colnames(df.temptemp)[14:ncol(df.temptemp)], (coeffs[-1,])))
+
+```
+
+```{r}
+df.mt %>% 
+  filter(Year >= 2012) %>% 
+  mutate(value = ifelse(value > 6, 6, value)) %>% 
+  group_by(value) %>% 
+  summarise(n(), mean(MS, na.rm = TRUE), mean(Complexity, na.rm = TRUE))
+```

### 2024-10-02 code/manuscript_altanalysis.Rmd
try again

@@
 dfc <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
-uds.sites.full <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
-  mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 4, Access))
+#uds.sites.full <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
+#  mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 4, Access))
 clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
@@
 
-## Z: Competitive Shocks and Y: Outcomes
-
+## Build List of ALL CHCs, star constructing variables
 ```{r}
@@
 
+## Z: Competitive Shocks and Y: Outcomes
+
 ```{r}
@@
   #filter(is.na(NewClinicID)) %>%
-  select(`BHCMIS ID`:`2021`) %>% 
-  pivot_longer(cols = c(`2010`:`2021`)) %>% 
+  select(`BHCMIS ID`:`2023`) %>% 
+  pivot_longer(cols = c(`2010`:`2023`)) %>% 
   group_by(`BHCMIS ID`) %>% 
@@
 dfc <- dfc %>% 
-  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate + cad.rate + asthma.rate + ivd.rate ) / 9 * 100, 
+  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
          Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
@@
 table(table(dfc$`BHCMIS ID`))
+
+dfc %>% filter(ID.x == "90")
 ```
@@
          ivd.rate = ivd.rate * 100)
+
 ```
@@
   mutate(Closed = ifelse(lead(is.na(Sites)), 1, 0)) %>% 
-  select(value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Complexity, Intensity, Pct.None:Pct.COM, CostPerPat, Altman) %>% 
-  unique() %>% 
-  filter(Year >= 2012)
+  select(value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Complexity, Intensity, Pct.None:Pct.COM, CostPerPat, Altman, Staff) %>% 
+  unique()
+
+df.temptemp <- df.temptemp %>% 
+  group_by(ID) %>% 
+  mutate(value_min = min(value, na.rm = TRUE), value_max = max(value, na.rm = TRUE), value_last = last(value, na_rm = TRUE), value_first = first(value, na_rm = TRUE)) %>% 
+  mutate(Tx = value - value_min) %>% 
+  filter(value_min == value_max | value_last > value_first)
 
@@
 
-for (k in 1:(ncol(df.temptemp)-13)){
+for (k in 1:10){
 
@@
 }
-data.frame(cbind(colnames(df.temptemp)[14:ncol(df.temptemp)], (coeffs[-1,])))
+data.frame(cbind(colnames(df.temptemp)[14:23], (coeffs[-1,])))
 
@@
 
+## BY Hand
 ```{r}
-df.mt %>% 
-  filter(Year >= 2012) %>% 
-  mutate(value = ifelse(value > 6, 6, value)) %>% 
-  group_by(value) %>% 
-  summarise(n(), mean(MS, na.rm = TRUE), mean(Complexity, na.rm = TRUE))
+
+df.temptemptemp <- df.temptemp %>% select(Qcomp, MS, value, Year, ID, Pct.NHA:Pct.COM) %>% ungroup() %>% filter(complete.cases(.))
+
+reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
+firststage <- lm(data = df.temptemptemp, I(MS/10) ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
+
+model <- lm(data = df.temptemptemp, Qcomp ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless)
+summary(model)
+
 ```

### 2024-10-02 code/manuscript_data_cleaning.Rmd
alt spec
more new analysis
try again

@@
 
-included.years <- 2010:2021
-included.treat <- 2013:2019
+included.years <- 2010:2023
+included.treat <- 2013:2023
 
@@
   #filter(`2011` == 1 & `2012` == 1 ) %>%  #  & `2012` == 1 & `2013` == 1 & `2014` == 1 & `2015` == 1 & `2016` == 1) %>%   
-  filter(`2014` == 1 & `2015` == 1) %>%  
+  #filter(`2014` == 1 & `2015` == 1) %>%  
   #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
@@
   select(`BHCMIS ID`:`2023`) %>% 
-  pivot_longer(cols = c(`2014`:`2023`)) %>% 
+  pivot_longer(cols = c(`2010`:`2023`)) %>% 
   group_by(`BHCMIS ID`) %>% 
@@
 
-vec.atts <- rep(included.treat, (table(comp.initial$Att) / 12)[-1])
+#vec.atts <- rep(included.treat, (table(comp.initial$Att) / 15)[-1])
+vec.atts <- included.treat
 

### 2024-10-03 code/manuscript_altanalysis.Rmd
better measures, geographic piece too

@@
 ```{r}
-dfc <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
+#dfc <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
 #uds.sites.full <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
@@
                Liquidity = (Assets - Liabilities) / Assets,
-               Profitability = ngla_net_gain_loss / Assets, #Assets, 
+               Profitability = ngla_net_gain_loss / ngla_expense * 100, #Assets, 
                Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
@@
             Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
-            LiabPctAssets = Liabilities / Assets, 
+            LiabPctAssets = Liabilities / Assets * 100, 
             Eff = ngla_prog_serv_revenue / Assets, 
@@
 
+df.zip.HHI <- df.zip %>% 
+  group_by(BHCMISID, ReportingYear, ZipCode) %>% 
+  summarise(ZipTotal = sum(NumberofPatients)) %>% 
+  left_join(df.zip.totals, by = c("ReportingYear","ZipCode")) %>% 
+  mutate(MS = ZipTotal / Totals * 100) %>% 
+  ungroup() %>% 
+  arrange(ZipCode, ReportingYear) %>% 
+  group_by(ZipCode, ReportingYear) %>% 
+  mutate(ZipHHI = sum(MS ^2)) %>% 
+  group_by(BHCMISID, ReportingYear) %>% 
+  mutate(ClinicTotal = sum(ZipTotal), 
+         ClinicHHI = sum(ZipHHI * ZipTotal / ClinicTotal)) %>% 
+  arrange(BHCMISID, ReportingYear, ZipCode)
+
 df.zip <- df.zip %>% 
@@
             MS_denom = sum(Totals, na.rm = TRUE)) %>% 
-  mutate(MS = 100 - (MS_num / MS_denom * 100))
+  mutate(MS = 100 - (MS_num / MS_denom * 100)) %>% 
+  left_join(df.zip.HHI %>% select(BHCMISID, ReportingYear, ClinicHHI) %>% unique(), by = c("BHCMISID","ReportingYear"))
 
@@
   mutate(Closed = ifelse(lead(is.na(Sites)), 1, 0)) %>% 
-  select(value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Complexity, Intensity, Pct.None:Pct.COM, CostPerPat, Altman, Staff) %>% 
+  select(ClinicHHI, Att, `BHCMIS ID`, value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Total, Altman, 
+         htn.rate, dm.rate, pap.rate, crc.rate, childbmi.rate, adultbmi.rate, Complexity, Intensity, Pct.MCD, Pct.MCR, Pct.COM, Pct.None, CostPerPat, ngla_revenue, ngla_expense, Profitability, LiabPctAssets, Staff) %>%
   unique()
+
+## htn.total, dm.total, pap.denom, crc.denom, childbmi.denom, adultbmi.denom
 
@@
   mutate(Tx = value - value_min) %>%
-  filter(value_min == value_max | value_last > value_first)
+
+  filter(value_min == value_max | value_last > value_first) %>% 
+  mutate(value = ifelse(value >= 6, 6, value))
+
+# %>% 
+#   group_by(ID) %>% 
+#   mutate(Strata = min(Profitability, na.rm = TRUE)) %>% 
+#   filter(Strata < 0)
 
@@
 
-for (k in 1:10){
+for (k in 1:21){
 
-  df.temptemptemp <- df.temptemp
-  colnames(df.temptemptemp)[(13+k)] <- "Outcome"
-  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless  | I(MS/10) ~ value + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
 
@@
 }
-data.frame(cbind(colnames(df.temptemp)[14:23], (coeffs[-1,])))
+
+core.iv.estimates <- data.frame(cbind(colnames(df.temptemp)[17:37], (coeffs[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  select(V1, Estimate, `95% CI`)
+
+core.iv.estimates <- core.iv.estimates
+rownames(core.iv.estimates) <- NULL
+
+core.iv.estimates %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  pack_rows(index = c("Overall Impacts" = 3, "Quality of Care" = 6, "Patient Complexity" = 2, "Payer Mix" = 4, "Finances" = 6)) %>% 
+  add_header_above(c("IV-Estimated LATE Effects of Competitive Shocks on Incumbent Clinics" = 3))
+
+```
+
+## First Stage DID Estimates
+
+```{r}
+ did2s(
+      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))  , 
+      yname = "ClinicHHI", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+```
+
+## First Stage DID Event Study
+```{r}
+
+ event_study(data = df.temptemp ,
+  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
+  filter(abs(term) <= 5) %>%
+  #filter(estimator == "Gardner (2021)") %>%
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
 
@@
 
-df.temptemptemp <- df.temptemp %>% select(Qcomp, MS, value, Year, ID, Pct.NHA:Pct.COM) %>% ungroup() %>% filter(complete.cases(.))
+df.temptemptemp <- df.temptemp %>% select(ClinicHHI, Qcomp, MS, value, Year, ID, Pct.NHA:Pct.COM) %>% ungroup() %>% filter(complete.cases(.))
 
 reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
-firststage <- lm(data = df.temptemptemp, I(MS/10) ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
+firststage <- lm(data = df.temptemptemp, I((10000 - ClinicHHI)/1000) ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
 
 model <- lm(data = df.temptemptemp, Qcomp ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless)
-summary(model)
+
+m1coeffs_cl <- coeftest(model, vcov = vcovCL, cluster = ~ID)
+m1coeffs_cl
 
 ```
+
+## Why are the signs funky? 
+We are likely picking up shifting trends in the level differences across values.
+
+```{r}
+df.temptemp %>% #left_join(df.temptemp %>% filter(Tx == 1) %>% summarise(Att = min(Year)), by = c("ID")) %>% 
+               mutate(Att = ifelse(is.na(Att), 0, Att)) %>% 
+  mutate(value = ifelse(value >= 6, 6, value)) %>% 
+  group_by(value, Year) %>% 
+  summarise(MS = mean(MS, na.rm = TRUE)) %>% 
+  ggplot(aes(x = Year, y = MS, group = value, color = as.factor(value))) + geom_point() + geom_line()
+```
+
+## Balance between treated and controls
+```{r}
+
+df.temptemp %>% 
+  filter(Year == 2012) %>% 
+  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
+  select(Treat, Total, Pct.NHA:Staff) %>% 
+  #filter(!complete.cases(.)) %>% 
+  tbl_summary(by = Treat, 
+                statistic = list(all_continuous() ~ "{mean} ({sd})"),
+missing = "no", digits = list(everything() ~ c(2))) %>% 
+  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))
+
+```
+
+##  Trends over time, figure 1
+
+```{r}
+## Plot
+p <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
+  select(`BHCMIS ID`, Zip, Year) %>% 
+  unique() %>% 
+  left_join(clinics.in.zips, by = c("Zip", "Year")) %>%
+  group_by(`BHCMIS ID`, Year) %>%
+  summarise(Clinics = max(Clinics, na.rm = TRUE)) %>%
+  group_by(Year, Clinics) %>% 
+  summarise(Count = n()) %>% 
+  mutate(CompetitorsInArea = factor(ifelse( Clinics < 4, Clinics - 1, "3+"))) %>% 
+  group_by(Year, CompetitorsInArea) %>% 
+  summarise(Count = sum(Count)) %>% 
+  filter(CompetitorsInArea != "-Inf")
+
+plot0 <- p %>% 
+  arrange(CompetitorsInArea) %>% 
+  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
+  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
+  geom_dl(label=c(rep("0 Competitors", length(unique(p$Year))), rep("1 Competitor", length(unique(p$Year))), rep("2 Competitors", length(unique(p$Year))), rep("3+ Competitors", length(unique(p$Year)))),
+          method = list("last.points", hjust = 1, vjust = c(2, 2.5, 2.5, -1), cex = 1.5), inherit.aes=T ) + 
+  guides(colour = "none") +theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=12,face="bold"))
+
+plot1 <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
+            group_by(Zip, Year) %>% 
+  summarise(Counts = n()) %>% 
+  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
+  ungroup() %>% 
+  group_by(Year, Counts) %>% 
+  summarise(Zips = n()) %>% 
+  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
+  group_by(Counts.f, Year) %>% 
+  summarise(Zips = sum(Zips)) %>% 
+  #filter(Year >= 2010) %>% 
+  ggplot(aes(x = Year, y = Zips, group = Counts.f, color = Counts.f)) + 
+  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
+  geom_dl(label=c(rep("1 Site", length(unique(p$Year))), rep("2+ Sites", length(unique(p$Year)))), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
+  guides(colour = "none") + ylim(0, 4000) +theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=12,face="bold"))
+
+p.desc <- ggarrange(plot1, plot0, ncol = 1)
+
+p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))
+
+#ggsave(filename = "Figure1.png", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Figures", plot = p.desc, width = 8, height = 11)
+
+# p.desc <- ggarrange(plot1, plot0, ncol = 2) 
+# 
+# p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))
+
+#ggsave(filename = "Picture1h.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 16, height = 9)
+
+p.desc
+
+```
+
+## Changes in geographic distribution of resources by Distance to competitive zip
+
+```{r}
+
+## Treatment vs control, only in zip code of interest
+df.z <- left_join(df.temptemp, 
+                  #uds.zip %>% mutate(Zip = `ZipCode`) %>% select(`BHCMISID`, Zip) %>% unique() , by = c("BHCMIS ID" = "BHCMISID")) %>%
+                  uds.sites.full[!is.na(uds.sites.full$Zip),] %>% filter(Year %in% c(2010:2023)) %>% select(`BHCMIS ID`, Zip) %>% unique() %>% filter(!is.na(Zip)), by = c("BHCMIS ID")) %>%
+  left_join(uds.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear", "Zip" = "ZipCode")) %>%
+
+  ungroup() %>% 
+  ###### MAJOR CHANGE: remove those CHCS wtih missing market share MS from GrantNumber
+ #filter(!is.na(`MS`)) %>% 
+  left_join(clinics.in.zips %>% select(Zip:Clinics), by = c("Zip","Year")) %>%
+  rename(ID.chc = ID) %>% 
+  mutate(Tx.z = ifelse(Clinics == 1 , 0, 
+                ifelse(is.na(Clinics), NA, 1)), # | is.na(Clinics)
+         ID = as.numeric(factor(paste(`BHCMIS ID`, Zip, sep = "-")))) %>%
+  select(`BHCMIS ID`:Year, Att, ID, Zip:Tx.z) %>%
+  arrange(`BHCMIS ID`, Zip, Year) %>% 
+  unique() #%>%  inner_join(df.qual.exp %>% filter(Year == 2015 & Total > 12050) %>% select(`Grant Number`), by = c("Grant Number"))  #& Zips < 3.75 or 4.75
+  # %>%   filter(MarketShare > median(MarketShare, na.rm = TRUE) - 0.25)
+
+length(unique(df.z$ID))
+
+df.z <- df.z %>% 
+  left_join(df.z %>%
+            filter(Tx.z == 1) %>%
+            group_by(ID, Zip) %>%
+            summarise(Att.z = min(Year)), by = c("ID", "Zip")) %>%
+  mutate(Att.z = ifelse(is.na(Att.z), 0, Att.z)) #%>%
+# inner_join(df.z %>% filter(!is.na(Clinics)) %>% group_by(ID) %>% summarise(n()) %>% filter(`n()` == length(unique(df.qual.exp$Year))), by = c("ID")) #%>% filter(Att == Att.z)
+
+length(unique(df.z$ID))
+
+df.z <- df.z %>% 
+    left_join(uds.sites.full %>% 
+              filter(`Location Setting` %in% c("All Other Clinic Types")) %>% 
+              #filter(`Location Setting` %in% c("All Other Clinic Types","School") | is.na(`Location Setting`)) %>% 
+              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
+                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
+                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
+                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
+                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
+                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
+              group_by(`BHCMIS ID`, Year, Zip) %>% 
+              summarise(Sites = n(), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
+                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)), by = c("BHCMIS ID","Year", "Zip")) %>% 
+  mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
+         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
+         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
+         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
+         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
+         Calendar = ifelse(is.na(Calendar), 0, Calendar))
+
+df.z <- df.z %>% 
+  left_join(df.zip.totals, by = c("Zip" = "ZipCode","Year" = "ReportingYear")) %>% 
+  mutate(MS = 100 - (NumberofPatients / Totals * 100)) %>% 
+  left_join(df.zip.HHI, by = c("BHCMIS ID" = "BHCMISID","Year" = "ReportingYear","Zip" = "ZipCode"))
+
+df.z
+
+```
+
+## Spatial Analysis
+
+```{r}
+
+df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
+        mutate(Pct.MCD = Medicaid / NumberofPatients * 100, 
+               Pct.MCR = Medicare / NumberofPatients * 100, 
+               Pct.COM = Private / NumberofPatients * 100,
+               Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
+  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year)
+
+coeffs <- c(0,0,0,0, 0, 0, 0, 0)
+
+for (k in 1:8){
+
+  df.z.temp2 <- df.z.temp
+  colnames(df.z.temp2)[k] <- "Outcome"
+  model <-  did2s(
+      data = df.z.temp2, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ 1 | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
+        second_stage = ~ i(Tx, ref = FALSE)  + I(Tx * DirectlyTreated),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+  coeffs <- rbind(coeffs, c(model$coeftable[2,], model$coeftable[1,]))
+
+}
+
+zip.estimates <- data.frame(cbind(colnames(df.z.temp)[1:8], (coeffs[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>%
+  select(V1, Estimate, `95% CI`, Estimate.1, `95% CI.1`)
+
+zip.estimates <- zip.estimates[c(1, 6, 2:5, 7:8),]
+rownames(zip.estimates) <- NULL
+
+zip.estimates %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI","Estimate","95% CI")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  pack_rows(index = c("Overall Impacts" = 2, "Patient and Payer Mix" = 4, "Access" = 2)) %>% 
+  add_header_above(c(" " = 1, "Directly Competitive" = 2, "Indirectly Competitive" = 2)) %>% 
+  add_header_above(c("DID-Estimated Effects of Competitive Shocks on Zip Codes in Incumbent Clinics' Service Area" = 5))
+
+```

### 2024-10-04 code/manuscript_altanalysis.Rmd
closures too!

@@
 library(did2s)
+library(did)
 library(tidyverse)
@@
                Liquidity = (Assets - Liabilities) / Assets,
-               Profitability = ngla_net_gain_loss / ngla_expense * 100, #Assets, 
+               Profitability = ngla_revenue / ngla_expense * 100, #Assets, 
                Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
@@
   mutate(Closed = ifelse(lead(is.na(Sites)), 1, 0)) %>% 
-  select(ClinicHHI, Att, `BHCMIS ID`, value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Total, Altman, 
-         htn.rate, dm.rate, pap.rate, crc.rate, childbmi.rate, adultbmi.rate, Complexity, Intensity, Pct.MCD, Pct.MCR, Pct.COM, Pct.None, CostPerPat, ngla_revenue, ngla_expense, Profitability, LiabPctAssets, Staff) %>%
+  select(ClinicHHI, Att, `BHCMIS ID`, value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Total, Altman, logPatsPerStaff, 
+         htn.rate, dm.rate, pap.rate, crc.rate, childbmi.rate, adultbmi.rate, Complexity, Intensity, Pct.MCD, Pct.MCR, Pct.COM, Pct.None, CostPerPat, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff, Closed) %>%
   unique()
@@
   filter(value_min == value_max | value_last > value_first) %>% 
-  mutate(value = ifelse(value >= 6, 6, value))
+  mutate(value = ifelse(value >= 6, 6, value)) #%>% filter(Year < 2020)
 
@@
 
-for (k in 1:21){
+for (k in 1:22){
 
@@
 
-core.iv.estimates <- data.frame(cbind(colnames(df.temptemp)[17:37], (coeffs[-1,]))) %>% 
+core.iv.estimates <- data.frame(cbind(colnames(df.temptemp)[17:38], (coeffs[-1,]))) %>% 
   #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
@@
   kable_styling(latex_options = c("striped")) %>%
-  pack_rows(index = c("Overall Impacts" = 3, "Quality of Care" = 6, "Patient Complexity" = 2, "Payer Mix" = 4, "Finances" = 6)) %>% 
+  pack_rows(index = c("Overall Impacts" = 4, "Quality of Care" = 6, "Patient Complexity" = 2, "Payer Mix" = 4, "Finances" = 6)) %>% 
   add_header_above(c("IV-Estimated LATE Effects of Competitive Shocks on Incumbent Clinics" = 3))
+
+feols(I(Closed * 100) ~  Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemp)
 
@@
 
-## First Stage DID Estimates
+## First Stage DID Estimates and Event Study
 
@@
 
-```
-
-## First Stage DID Event Study
-```{r}
-
  event_study(data = df.temptemp ,
   yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
-  filter(abs(term) <= 5) %>%
+  filter(abs(term) <= 6) %>%
   #filter(estimator == "Gardner (2021)") %>%
+  filter(estimator == "Callaway and Sant'Anna (2020)") %>%
   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
@@
 
-df.temptemptemp <- df.temptemp %>% select(ClinicHHI, Qcomp, MS, value, Year, ID, Pct.NHA:Pct.COM) %>% ungroup() %>% filter(complete.cases(.))
+## TWFE First Stage
+df.temptemptemp <- df.temptemp %>% select(ClinicHHI, Qcomp, MS, value, Year, ID, Pct.NHA:Pct.None) %>% ungroup() %>% filter(complete.cases(.))
 
@@
 m1coeffs_cl
+
+# ## Callaway-Sant'Anna First Stage
+# 
+# example_attgt <- att_gt(yname = "ClinicHHI",
+#                         tname = "Year",
+#                         idname = "ID",
+#                         gname = "Att",
+#                         xformla = ~Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless,
+#                         data = df.temptemp, 
+#                         clustervars = "ID"
+#                         )
+# 
+# # summarize the results
+# aggte(example_attgt)
 
@@
   group_by(value, Year) %>% 
-  summarise(MS = mean(MS, na.rm = TRUE)) %>% 
-  ggplot(aes(x = Year, y = MS, group = value, color = as.factor(value))) + geom_point() + geom_line()
+  summarise(HHI = mean(ClinicHHI, na.rm = TRUE)) %>% 
+  ggplot(aes(x = Year, y = HHI, group = value, color = as.factor(value))) + geom_point() + geom_line()
 ```
@@
 
-df.z
-
 ```
@@
 df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
+  filter(!(Att == 0 & DirectlyTreated == 1)) %>% 
         mutate(Pct.MCD = Medicaid / NumberofPatients * 100, 
@@
                Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
-  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year)
+  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att)
 
@@
 
-  df.z.temp2 <- df.z.temp
+  df.z.temp2 <- df.z.temp #%>% filter(Att == 0 | Att > 2010)
   colnames(df.z.temp2)[k] <- "Outcome"
@@
         first_stage = ~ 1 | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
-        second_stage = ~ i(Tx, ref = FALSE)  + I(Tx * DirectlyTreated),
+        second_stage = ~ i(Tx * (1 - DirectlyTreated), ref = FALSE)  + I(Tx * DirectlyTreated),
         cluster_var = "ID",
@@
 
+## WATCH OUT FOR THE INTERACTION INTERPRETATION
+
 ```
+
+## Event Study
+
+```{r}
+ event_study(data = df.z.temp %>% filter(Att == 0 | DirectlyTreated == 0),
+  yname = "Total.Hours", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~1) %>%
+  filter(abs(term) <= 6) %>%
+  filter(estimator == "Gardner (2021)") %>%
+  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
+
+ event_study(data = df.z.temp %>% filter(Att == 0 | DirectlyTreated == 1),
+  yname = "Total.Hours", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~1) %>%
+  filter(abs(term) <= 6) %>%
+  filter(estimator == "Gardner (2021)") %>%
+  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
+
+```
+
+## Are the closer and farther areas different?
+```{r}
+
+df.z.temp %>% 
+  #select(Zip, Year, DirectlyTreated, Att) %>% 
+  mutate(Status = ifelse(Att == 0, NA, 
+                         ifelse(Att > 0 & DirectlyTreated == 0, "IndirectlyTreated","DirectlyTreated"))) %>% 
+  inner_join(census, by = c("Zip" = "ZipCode", "Year" = "YEAR")) %>% 
+  filter(Year == 2012) %>% 
+  mutate(PctMedicaid = Medicaid / MCD.denom * 100, 
+         PctUninsured = Uninsured / Unins.denom * 100, 
+         PctPoverty = IncomeBelowPoverty / PovertyStatusDet * 100, 
+         PctBlack = Black / TotalPop * 100, 
+         PctHispanic = Hispanic / TotalPop * 100) %>% 
+    select(Status, TotalPop, PctMedicaid:PctHispanic) %>% 
+    tbl_summary(by = Status, 
+                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
+  add_p()
+
+```

### 2024-10-11 code/manuscript_altanalysis.Rmd
more analysis

@@
 
+```{r}
+uds.covariates %>% 
+  filter(`BHCMISID` == "010180")
+```
+
 ## D: HHI, and Bring them Together
@@
 
-# Analysis
-
-## Model
-
+## More Cleaning
 ```{r}
@@
     rename(ID = ID.x) %>% 
-  mutate(Closed = ifelse(lead(is.na(Sites)), 1, 0)) %>% 
+    group_by(ID) %>% 
+  mutate(Closed = ifelse(lead(is.na(Sites)), 100, 0)) %>% 
   select(ClinicHHI, Att, `BHCMIS ID`, value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Total, Altman, logPatsPerStaff, 
@@
   filter(value_min == value_max | value_last > value_first) %>% 
-  mutate(value = ifelse(value >= 6, 6, value)) #%>% filter(Year < 2020)
+  mutate(value = ifelse(value >= 6, 6, value)) #%>% group_by(ID) %>% mutate(max_Closures = max(Closed)) %>% filter(max_Closures == 0)
+
+df.temptemp <- df.temptemp %>% 
+  left_join (df.temptemp %>% 
+  filter(value > value_min) %>% 
+  group_by(ID) %>% 
+  summarise(Att = min(Year)), by = c("ID")) %>% 
+  mutate(Att = ifelse(!is.na(Att.y), Att.y, Att.x)) %>% 
+  select(ClinicHHI, Att, `BHCMIS ID`, value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Total, Altman, logPatsPerStaff, 
+         htn.rate, dm.rate, pap.rate, crc.rate, childbmi.rate, adultbmi.rate, Complexity, Intensity, Pct.MCD, Pct.MCR, Pct.COM, Pct.None, CostPerPat, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff, Closed:Tx) %>%
+  unique()
+
+```
+
+# Analysis
+
+## Model
+
+```{r}
 
@@
 
-feols(I(Closed * 100) ~  Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemp)
+model <- feols(Complexity ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx  + factor(Year) + factor(ID), cluster = "ID", data = df.temptemp)
+summary(model)
+
+model <- lm(data = df.temptemp, Pct.None ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   + Tx + factor(Year) + factor(ID) )
+summary(model)
 
@@
  did2s(
-      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))  , 
-      yname = "ClinicHHI", 
+      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)  )   , 
+      yname = "Complexity", 
       treatment = "Tx",
@@
   #filter(estimator == "Gardner (2021)") %>%
-  filter(estimator == "Callaway and Sant'Anna (2020)") %>%
+  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
@@
   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
+
+```
+
+## Alt DID estimates
+
+```{r}
+
+coeffs.did <- c(0,0,0,0)
+
+for (k in 1:22){
+
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  model <-  did2s(
+      data = df.temptemptemp, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+  coeffs.did <- rbind(coeffs.did, model$coeftable[1,])
+
+}
+
+core.did.estimates <- data.frame(cbind(colnames(df.temptemp)[17:38], (coeffs.did[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  select(V1, Estimate, `95% CI`)
+
+core.did.estimates <- core.did.estimates
+rownames(core.did.estimates) <- NULL
+
+core.did.estimates %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  pack_rows(index = c("Overall Impacts" = 4, "Quality of Care" = 6, "Patient Complexity" = 2, "Payer Mix" = 4, "Finances" = 6)) %>% 
+  add_header_above(c("IV-Estimated LATE Effects of Competitive Shocks on Incumbent Clinics" = 3))
 
@@
                Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
-  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att)
+  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att, `BHCMIS ID`)
 

### 2024-10-11 code/manuscript_data_cleaning.Rmd
more analysis

@@
   arrange(BHCMISID, Year)
+uds.covariates %>% 
+  filter(Pct.Homeless > 99)
 
@@
   left_join(assliabs %>% select(EIN:Liabilities), by = c("EIN","form_year" = "Year"))
+
+## Add updated data
+ufins.revenue.expenses <- read.csv("//Users/markow/Dropbox/Git/Data/Updated_FQHC_Revenue_vs_Expenses.csv", header = TRUE)
+table(ufins.revenue.expenses$X.form_year..)
+names(ufins.revenue.expenses) <- gsub("^X\\.", "", names(ufins.revenue.expenses))
+names(ufins.revenue.expenses) <- gsub("\\.\\.", "", names(ufins.revenue.expenses))
+
+ustaffing <- read.csv("/Users/markow/Dropbox/Git/Data/Updated_FQHC_Staffing.csv")
+uassliabs <- read.csv("/Users/markow/Dropbox/Git/Data/Updated_FQHC_Assets_and_Liabilities.csv")
+
+ufins <- uds.cw %>% filter(Year == 2011) %>% unique() %>% select(ModernGranteeID, BHCMIS.ID) %>% 
+  left_join(cw, by = c("ModernGranteeID" = "Grant Number")) %>% 
+  left_join(ufins.revenue.expenses, by = c("EIN" = "EIN")) %>% 
+  select(ModernGranteeID:EIN, form_year:fringe_rate) %>% 
+  left_join(ustaffing %>% select(EIN:Staff), by = c("EIN","form_year" = "Year")) %>% 
+  left_join(uassliabs %>% select(EIN:Liabilities), by = c("EIN","form_year" = "Year"))
+
+fins.revenue.expenses <- ufins
 

### 2024-10-11 code/manuscript_tryagain.Rmd
more analysis

---
title: "Untitled"
output: html_document
date: "2024-10-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Library

# Another Go

```{r}
year.zip.clinic <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
  #filter(Year >= included.years[1]) %>%
  group_by(Zip, Year, `BHCMIS ID`) %>%
  summarise(Sites = n()) %>%
  arrange(Zip, Year, `BHCMIS ID`) %>% 
  arrange(Year) %>% 
  filter(Year >= 2012) %>% 
  pivot_wider(id_cols = c(Zip, `BHCMIS ID`), names_from = Year, values_from = Sites) %>% 
  select(Zip, `BHCMIS ID`, `2012`:`2023`) %>% 
  pivot_longer(cols = c(`2012`:`2023`)) %>% 
  mutate(value = ifelse(is.na(value), 0, value))

zip.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
  #filter(Year >= included.years[1]) %>%
  group_by(Zip, Year) %>%
  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>% 
  arrange(Year) %>% 
  filter(Year >= 2012) %>% 
  pivot_wider(id_cols = Zip, names_from = Year, values_from = Clinics) %>% 
  select(Zip, `2012`:`2023`) %>% 
  pivot_longer(cols = c(`2012`:`2023`)) %>% 
  mutate(value = ifelse(is.na(value), 0, value))

df.master <- zip.comp %>% 
  inner_join(year.zip.clinic, by = c("Zip","name")) %>% 
  rename(nClinicsInZipYear = value.x, nSitesByClinicZipYear = value.y, BHCMISID = `BHCMIS ID`) %>% 
  mutate(Year = as.numeric(name)) %>% 
  select(Zip, Year, BHCMISID, nClinicsInZipYear, nSitesByClinicZipYear)

df.master <- df.master %>% 
  left_join(df.master %>% 
  group_by(BHCMISID, Zip) %>% 
  filter(nSitesByClinicZipYear > 0) %>% 
  mutate(YearFirstInZip = min(Year), YearLastInZip = max(Year)) %>% 
    select(Zip, BHCMISID, YearFirstInZip, YearLastInZip) %>% unique(), by = c("Zip","BHCMISID")) %>% 
  filter(Zip != "00000")

```

## Show Distribution
```{r}

df.master %>% 
  group_by(YearFirstInZip, YearLastInZip) %>% 
  summarise(Obs = n()) %>% 
  pivot_wider(id_cols = YearFirstInZip, names_from = YearLastInZip, values_from = Obs) %>% 
  as.matrix()

df.master <- df.master %>% 
  arrange(Zip, Year, BHCMISID) %>% 
  group_by(Zip, BHCMISID) %>% 
  mutate(Change = nClinicsInZipYear - lag(nClinicsInZipYear), 
         ChangeThemselves = nSitesByClinicZipYear - lag(nSitesByClinicZipYear)) %>% 
  mutate(ShockUp = ifelse(nSitesByClinicZipYear > 0 & Change > 0 & ChangeThemselves == 0, 1, 0), 
         ShockDown = ifelse(nSitesByClinicZipYear > 0 & Change < 0 & ChangeThemselves == 0, 1, 0))

## Floating, changing boundaries of service area 
df.countingRivals <- df.master %>% 
  #filter(nSitesByClinicZipYear > 0) %>% 
  select(BHCMISID, Year, Zip) %>% 
  unique() %>% 
  arrange(BHCMISID, Year, Zip) %>% 
  left_join(df.master %>% 
  filter(nSitesByClinicZipYear > 0) %>% 
  select(BHCMISID, Year, Zip) %>% 
  unique() %>% 
  arrange(BHCMISID, Year, Zip), by = c("Zip","Year")) %>% 
  #filter(BHCMISID.x != BHCMISID.y) %>% 
  ungroup() %>% 
  select(BHCMISID.x, Year, BHCMISID.y) %>% 
  rename(Incumbent = BHCMISID.x, Rival = BHCMISID.y) %>% 
  unique() %>% 
  group_by(Incumbent, Year) %>% 
  summarise(nRivals = n() - 1) %>% 
  ungroup() %>% 
  group_by(Incumbent) %>% 
  mutate(nRivals_min = min(nRivals), nRivals_max = max(nRivals))

df.master <- df.master %>% 
  left_join(df.countingRivals, by = c("BHCMISID" = "Incumbent","Year")) %>% 
  select(Zip, Year, BHCMISID, nRivals, nRivals_min, nRivals_max, nClinicsInZipYear:ShockDown)

# uds.sites.full %>% 
#   filter(`BHCMIS ID` == "010030")
# 
# 
# df.master %>% 
#   filter(`BHCMISID` == "010030")
# 
# 
# uds.sites.full %>% 
#   filter(Zip == "01040")

```

## Taking it further
```{r}

df.zip <- df.master %>% 
  left_join(uds.sites.full %>% 
              filter(`Location Setting` %in% c("All Other Clinic Types")) %>% 
              #filter(`Location Setting` %in% c("All Other Clinic Types","School") | is.na(`Location Setting`)) %>% 
              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
              group_by(`BHCMIS ID`, Year, Zip) %>% 
              summarise(Sites = n(), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)), by = c("BHCMISID" = "BHCMIS ID","Year", "Zip")) %>% 
  mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
         Calendar = ifelse(is.na(Calendar), 0, Calendar))

df.zip %>% 
  mutate(Tx = nRivals - nRivals_min) %>% 
  filter(nRivals_max >= nRivals_min) %>% 
  filter(Zip == "01040")

```

## Zip Analysis
```{r}

did2s(
      data = df.zip %>% 
  mutate(Tx = nRivals - nRivals_min) %>% 
  filter(nRivals_max >= nRivals_min) %>% 
    mutate(Tx = ifelse(Tx > 0, 1, 0)) %>% 
    filter(Tx >= 0) %>% ungroup() %>% mutate(ID = as.numeric(factor(paste(`BHCMISID`, Zip, sep = "-")))), 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx , ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

```

### 2024-10-17 code/manuscript_altanalysis.Rmd
Distance Instrument

@@
   select(ClinicHHI, Att, `BHCMIS ID`, value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Total, Altman, logPatsPerStaff, 
-         htn.rate, dm.rate, pap.rate, crc.rate, childbmi.rate, adultbmi.rate, Complexity, Intensity, Pct.MCD, Pct.MCR, Pct.COM, Pct.None, CostPerPat, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff, Closed) %>%
+         htn.rate, dm.rate, pap.rate, crc.rate, childbmi.rate, adultbmi.rate, Complexity, Intensity, Pct.MCD, Pct.MCR, Pct.COM, Pct.None, CostPerPat, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff, Closed, pap.denom, crc.denom, childbmi.denom, adultbmi.denom, htn.total, dm.total, asthma.rate, cad.rate, ivd.rate, ngla_net_gain_loss, Liquidity, Efficiency, NetWorth, Liabilities) %>%
   unique()
@@
 
+# df.temptemp <- df.temptemp %>% 
+#   left_join(uds.cw %>% filter(Year == 2011) %>% select(BHCMIS.ID:PH), by = c("BHCMIS ID" = "BHCMIS.ID")) %>% 
+#   mutate(ACA = ifelse((STATE %in% c('MI','NH') & Year >= 2014) |
+#                     (STATE %in% c('PA','IN','AK') & Year >= 2015) |
+#                     (STATE %in% c('MT','LA') & Year >= 2016) |
+#                     (STATE %in% c('VA','ME') & Year >= 2019) |
+#                     (STATE %in% c('ID','UT','NE') & Year >= 2020) |
+#                     (STATE %in% c('OK','MO') & Year >= 2021) |
+#                     (STATE %in% c('AZ','AR','CA','CO','CT','DE','DC','HI','IL','IA','KY','MD','MA','MN','NV','NJ','NM','NY','ND','OH','OR','PA','RI','VT','VA','WA') & Year >= 2014), 1, 0))
+
 ```
@@
 
-for (k in 1:22){
+for (k in 1:28){
 
@@
   colnames(df.temptemptemp)[(16+k)] <- "Outcome"
-  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
-
-  coeffs <- rbind(coeffs, model$coeftable[2,])
+  #model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
+  #coeffs <- rbind(coeffs, model$coeftable[2,])
+  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + MHC + HO + PH | ID + Year | I((10000 - ClinicHHI)/1000) ~ value, cluster = "ID", data = df.temptemptemp)
+  coeffs <- rbind(coeffs, model$coeftable[1,])
 
@@
 
-core.iv.estimates <- data.frame(cbind(colnames(df.temptemp)[17:38], (coeffs[-1,]))) %>% 
+core.iv.estimates <- data.frame(cbind(colnames(df.temptemp)[17:44], (coeffs[-1,]))) %>% 
   #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
@@
 
-model <- feols(Complexity ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx  + factor(Year) + factor(ID), cluster = "ID", data = df.temptemp)
-summary(model)
-
-model <- lm(data = df.temptemp, Pct.None ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   + Tx + factor(Year) + factor(ID) )
-summary(model)
+summary(feols(df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)), I( Pct.None  ) ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year | I((10000 - ClinicHHI)/100) ~ Tx, cluster = "ID"))
 
@@
       data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)  ) , 
-      yname = "Complexity", 
+      yname = "ClinicHHI", 
       treatment = "Tx",
@@
 
- event_study(data = df.temptemp ,
+    event_study(data = df.temptemp,
   yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
   filter(abs(term) <= 6) %>%
-  #filter(estimator == "Gardner (2021)") %>%
+  filter(estimator == "Gardner (2021)") %>%
+  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
+
+```
+
+## Heterogeneity by Starting Point
+```{r}
+
+ event_study(data = df.temptemp %>% filter(value_min == 1),
+  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
+  filter(abs(term) <= 6) %>%
+  filter(estimator == "Gardner (2021)") %>%
+  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
+
+ event_study(data = df.temptemp,
+  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
+  filter(abs(term) <= 8) %>%
+  filter(estimator == "Gardner (2021)") %>%
+  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
+
+  event_study(data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Att = ifelse(Att == 2010, 0, Att)),
+  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
+  filter(abs(term) <= 8) %>%
+  filter(estimator == "Gardner (2021)") %>%
   #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
@@
 
-  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
   colnames(df.temptemptemp)[(16+k)] <- "Outcome"
@@
       treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
         second_stage = ~ i(Tx, ref = FALSE),
@@
   pack_rows(index = c("Overall Impacts" = 4, "Quality of Care" = 6, "Patient Complexity" = 2, "Payer Mix" = 4, "Finances" = 6)) %>% 
-  add_header_above(c("IV-Estimated LATE Effects of Competitive Shocks on Incumbent Clinics" = 3))
+  add_header_above(c("DID-Estimated Effects of Competitive Shocks on Incumbent Clinics" = 3))
+
+did2s(
+      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% filter(Year < 2020 ), 
+      yname = "Closed", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+df.temptemp %>% 
+    ungroup() %>% 
+  group_by(Tx) %>% 
+  summarise(mean(Qcomp, na.rm = TRUE))
 
@@
 ## TWFE First Stage
-df.temptemptemp <- df.temptemp %>% select(ClinicHHI, Qcomp, MS, value, Year, ID, Pct.NHA:Pct.None) %>% ungroup() %>% filter(complete.cases(.))
+df.temptemptemp <- df.temptemp %>% select(ClinicHHI, Qcomp, MS, value, Year, ID, Pct.NHA:Pct.None, Tx) %>% ungroup() %>% filter(complete.cases(.))
 
@@
 
-model <- lm(data = df.temptemptemp, Qcomp ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless)
+model <- lm(data = df.temptemptemp, Complexity ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless+ factor(Year) + factor(ID))
 
@@
 
+## Basic Linear Reg
+```{r}
+
+reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
+head(summary(reduced)$coeff) %>% as.data.frame()
+
+reduced <- lm(data = df.temptemptemp, Complexity ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
+head(summary(reduced)$coeff) %>% as.data.frame()
+
+reduced <- lm(data = df.temptemptemp, Closed ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
+head(summary(reduced)$coeff) %>% as.data.frame()
+
+```
+
 ## Why are the signs funky? 
@@
   ggplot(aes(x = Year, y = HHI, group = value, color = as.factor(value))) + geom_point() + geom_line()
+
+df.temptemp %>% #left_join(df.temptemp %>% filter(Tx == 1) %>% summarise(Att = min(Year)), by = c("ID")) %>% 
+               mutate(Att = ifelse(is.na(Att), 0, Att)) %>% 
+  mutate(value = ifelse(value >= 6, 6, value)) %>% 
+  group_by(value, Year) %>% 
+  summarise(Quality = mean(Qcomp, na.rm = TRUE)) %>% 
+  ggplot(aes(x = Year, y = Quality, group = value, color = as.factor(value))) + geom_point() + geom_line()
 ```
@@
   add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))
+
+df.temptemp %>% 
+  filter(Year == 2023) %>% 
+  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
+  select(Treat, Total, Pct.NHA:Staff) %>% 
+  ungroup() %>% 
+  summarise(n(), sum(Total, na.rm = TRUE))
 
@@
 
-df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
+df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 >= 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z >= 2010, 1, 0)) %>% 
+  #df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
   filter(!(Att == 0 & DirectlyTreated == 1)) %>% 
@@
 ```{r}
- event_study(data = df.z.temp %>% filter(Att == 0 | DirectlyTreated == 0),
+ event_study(data = df.z.temp %>% filter(Att == 0 | (Att > 0 & DirectlyTreated == 0)),
   yname = "Total.Hours", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~1) %>%
-  filter(abs(term) <= 6) %>%
+  filter(abs(term) <= 8) %>%
   filter(estimator == "Gardner (2021)") %>%
@@
 
- event_study(data = df.z.temp %>% filter(Att == 0 | DirectlyTreated == 1),
+ event_study(data = df.z.temp %>% filter(Att == 0 | (Att > 0 & DirectlyTreated == 1)),
   yname = "Total.Hours", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~1) %>%
-  filter(abs(term) <= 6) %>%
+  filter(abs(term) <= 8) %>%
   filter(estimator == "Gardner (2021)") %>%
@@
 ```
+
+## Auditing
+
+```{r}
+
+df.z.temp %>% 
+  select(`BHCMIS ID`, Year, Zip, Att, DirectlyTreated)
+
+uds.sites.full %>% 
+  filter(Zip == "02301") %>% 
+  select(Year, `BHCMIS ID`) %>% 
+  unique() %>% 
+  filter(Year >= 2010) %>% 
+  arrange(Year, `BHCMIS ID`)
+
+df.z %>% mutate(Tx = ifelse(value - 1 >= 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z >= 2010, 1, 0))
+
+```
+
+# Distance Intrustment
+
+```{r}
+
+## Treatment vs control, only in zip code of interest
+df.z <- left_join(df.temptemp, 
+                  #uds.zip %>% mutate(Zip = `ZipCode`) %>% select(`BHCMISID`, Zip) %>% unique() , by = c("BHCMIS ID" = "BHCMISID")) %>%
+                  uds.sites.full[!is.na(uds.sites.full$Zip),] %>% filter(Year %in% c(2010:2021)) %>% select(`BHCMIS ID`, Zip) %>% unique() %>% filter(!is.na(Zip)), by = c("BHCMIS ID")) %>%
+  left_join(uds.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear", "Zip" = "ZipCode")) %>%
+  filter(!is.na(GrantNumber)) %>% 
+  left_join(clinics.in.zips %>% select(Zip:Clinics), by = c("Zip","Year")) %>%
+  mutate(Tx.z = ifelse(Clinics == 1 , 0, 
+                ifelse(is.na(Clinics), NA, 1)), # | is.na(Clinics)
+         ID = as.numeric(factor(paste(`BHCMIS ID`, Zip, sep = "-")))) %>%
+  select(`BHCMIS ID`:Year, Att, ID, Zip:Tx.z, Tx) %>%
+  arrange(`BHCMIS ID`, Zip, Year) %>% 
+  unique() #%>%  inner_join(df.qual.exp %>% filter(Year == 2015 & Total > 12050) %>% select(`Grant Number`), by = c("Grant Number"))  #& Zips < 3.75 or 4.75
+  # %>%   filter(MarketShare > median(MarketShare, na.rm = TRUE) - 0.25)
+
+df.z <- df.z %>% 
+  left_join(df.z %>%
+            filter(Tx.z == 1) %>%
+            group_by(ID, Zip) %>%
+            summarise(Att.z = min(Year)), by = c("ID", "Zip")) %>%
+  mutate(Att.z = ifelse(is.na(Att.z), 0, Att.z)) #%>%
+# inner_join(df.z %>% filter(!is.na(Clinics)) %>% group_by(ID) %>% summarise(n()) %>% filter(`n()` == length(unique(df.qual.exp$Year))), by = c("ID")) #%>% filter(Att == Att.z)
+
+## Whole zip as one measure
+
+df.z.full <- df.z %>% ############## NOTE: Original +500 effect was recoved with Att.z, not Att
+  select(Zip, Att.z, Year) %>% 
+  unique() %>% 
+  left_join(uds.zip, by = c("Zip" = "ZipCode", "Year" = "ReportingYear")) %>% 
+  left_join(df.temptemp %>% 
+            select(`BHCMIS ID`, Year, Qcomp), by = c("BHCMISID" = "BHCMIS ID", "Year")) %>% 
+  group_by(Zip, Year, Att.z) %>% 
+  summarise(
+    Total.z = sum(NumberofPatients, na.rm = TRUE), 
+    Quality.z = sum(NumberofPatients * Qcomp, na.rm = TRUE) / Total.z) %>% 
+  ungroup() %>% 
+  mutate(ID = as.numeric(as.factor(Zip)))# %>% group_by(`Grant Number`, Year, Att) %>% summarise(ID = min(ID), Total.z = sum(Total.z, na.rm = TRUE)) # %>% filter(Year > 2015),
+
+df.zip.1 <- df.z %>% select(ID, Year, Att, NumberofPatients)
+df.zip.2 <- df.z.full %>% select(ID, Year, Att.z, Total.z:Quality.z)
+
+```
+
+## Edit Centroids
+
+```{r}
+## Read in Centroid Data
+zip.centroids <- read.csv("/Users/markow/Dropbox/Git/Data/ZIP_Code_Population_Weighted_Centroids.csv") %>% 
+  mutate(ZipCode = str_pad(STD_ZIP5, 5, pad = "0")) %>% 
+  select(ZipCode, X, Y)
+## Add missing centroids
+zip.centroids <- rbind(zip.centroids, c(ZipCode = "37243", X = -86.783, Y = 36.165), 
+                                      c(ZipCode = "95951", X = -121.98, Y = 39.73), 
+                                      c(ZipCode = "99733", X = -144.166941, Y = 65.799773),
+
+                                      c(ZipCode = "04341", X = -69.4277, Y = 55.3255), 
+                                      c(ZipCode = "04935", X = -69.5995, Y = 44.5884)
+                      ) %>% 
+  mutate(X = as.numeric(X), Y = as.numeric(Y))
+```
+
+## Describe where the rivals came from
+```{r}
+
+## Distance of Competitor to New Site
+df.z.dist <- df.z.full %>% 
+  filter(Att.z == Year) %>% 
+  select(Zip:Total.z) %>% 
+  left_join(uds.sites.full %>% select(`BHCMIS ID`, Year, Zip) %>% unique(), by = c("Zip","Year")) %>% 
+  left_join(df.z %>% filter(Tx == 1) %>% select(`BHCMIS ID`, Year, Zip) %>% unique(), by = c("Zip","Year")) %>% 
+  filter(`BHCMIS ID.x` != `BHCMIS ID.y`)
+
+df.z.dist <- df.z.dist %>% mutate(DistToClosestSite = NA, ZipOfClosestSite = NA)
+
+for (g in 1:nrow(df.z.dist)){
+#g <- 1
+ temp <- rbind(zip.centroids %>% filter(ZipCode == df.z.dist[g,]$Zip), 
+          zip.centroids %>% filter(ZipCode %in% unique(uds.sites.full[uds.sites.full$`BHCMIS ID` == df.z.dist[g,]$`BHCMIS ID.x` & uds.sites.full$Year == df.z.dist[g,]$Year,]$Zip))) %>% 
+   unique()
+  mm <- as.matrix(dist(as.matrix(temp$X, temp$Y), method = "euclidean"))[-1,1]
+  df.z.dist[g,]$DistToClosestSite <-  min(mm) * 111.139
+  df.z.dist[g,]$ZipOfClosestSite  <- ifelse(is.na(temp[2,]$ZipCode), temp[1,]$ZipCode, unlist(temp[-1,]$ZipCode[rank(mm) == 1]))
+}
+
+#df.z.dist[19,]$DistToClosestSite <- 0
+df.z.dist <- df.z.dist %>% 
+  filter(!is.infinite(DistToClosestSite))
+
+df.z.dist <- df.z.dist %>% 
+  inner_join(df.z.dist %>% group_by(`BHCMIS ID.y`) %>% summarise(Att.z = min(Att.z)), by = c("BHCMIS ID.y", "Att.z")) %>% 
+  unique()
+
+mean(df.z.dist$DistToClosestSite)
+quantile(df.z.dist$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))
+
+# mean(df.z.dist[df.z.dist$ZipFilter == 1,]$DistToClosestSite)
+# mean(df.z.dist[df.z.dist$ZipFilter == 2,]$DistToClosestSite)
+# 
+# quantile(df.z.dist[df.z.dist$ZipFilter == 1,]$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))
+# quantile(df.z.dist[df.z.dist$ZipFilter == 2,]$DistToClosestSite, probs = c(0, 0.1, 0.25, 0.5, 0.75, 0.9, 1))
+
+zipsize <- zctas(starts_with = c(df.z.dist$Zip, df.z.dist$ZipOfClosestSite), year = 2010)
+
+## Original Figure
+df.z.dist.plot <- df.z.dist %>% 
+  left_join(zipsize %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
+  left_join(uds.sites.full %>% select(Zip, `Site State`) %>% unique(), by = c("Zip")) %>% 
+  left_join(census %>% select(ZipCode, YEAR, TotalPop), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
+  arrange(desc(DistToClosestSite)) %>% 
+  mutate(Area.SQmiles = ALAND10 / 2.59e6) %>% 
+  mutate(Density.NewZip = TotalPop / Area.SQmiles, 
+         l.density = log(TotalPop / Area.SQmiles)) %>% 
+  unique()
+
+df.z.dist.plot %>% 
+  ggplot(aes(x = log(Density.NewZip), y = DistToClosestSite)) + geom_point(aes(size = Area.SQmiles)) +
+  ggtitle("Distance from Rival's newly competing zip ocde to closest incumbent zip code by Density and Area of newly competing zip code")
+
+summary(lm(DistToClosestSite ~ log(Density.NewZip), data = df.z.dist.plot))
+
+# Updated Figure
+df.z.dist.plot <- df.z.dist.plot %>% 
+  select(Zip:ZipOfClosestSite, Density.NewZip) %>% 
+  left_join(zipsize %>% select(GEOID10, ALAND10), by = c("ZipOfClosestSite" = "GEOID10")) %>% 
+  left_join(uds.sites.full %>% select(Zip, `Site State`) %>% unique(), by = c("ZipOfClosestSite" = "Zip")) %>% 
+  left_join(census %>% select(ZipCode, YEAR, TotalPop), by = c("Year" = "YEAR", "ZipOfClosestSite" = "ZipCode")) %>% 
+  arrange(desc(DistToClosestSite)) %>% 
+  mutate(Area.SQmiles = ALAND10 / 2.59e6) %>% 
+  mutate(Density.Origin = TotalPop / Area.SQmiles)
+
+df.z.dist.plot %>% 
+  ggplot(aes(x = log(Density.NewZip), y = DistToClosestSite, color = log(Density.Origin))) + geom_point() +
+  scale_colour_gradientn(colours = terrain.colors(10))+ theme_minimal()+
+  ylab("Distance from Competative to closest Rival Site (km)") +
+  ggtitle("Distance from newly competative Zip to Rival's closest existing zip, by log Density of areas")
+
+p <- df.z.dist.plot %>% 
+  #filter(DistToClosestSite < 25) %>% 
+  ggplot(aes(x = log(Density.Origin), y = log(Density.NewZip))) + 
+  geom_point(aes(size = DistToClosestSite, colour = DistToClosestSite)) + 
+  scale_colour_gradientn(colours = c("green","lightblue","purple"),
+                         values = c(1.0,0.7,0.1,0))  +#scale_colour_gradientn(colours = terrain.colors(10))+ 
+  theme_minimal() + ylab("Log Population Density of New Zip Code") + 
+  xlab("Log Population Density of Nearest Service Area Zip Code") + 
+  labs(color = "Distance Travelled to\nOpenNew Site (km)") + 
+  guides(size = FALSE) + xlim(0.5, 11.5) + ylim(0.5, 11.5)
+p
+
+summary(lm(log(Density.Origin) ~ log(Density.NewZip), data = df.z.dist.plot))
+
+df.z.dist.plot %>% 
+  arrange(desc(DistToClosestSite)) %>% 
+  select(ZipOfClosestSite) %>% unlist()
+
+quantile(df.z.dist.plot$DistToClosestSite)
+quantile(df.z.dist.plot$DistToClosestSite, probs = 0.95)
+
+```
+
+## Find distance to rival for all CHCs in sample
+
+Takes a fair bit to run (~ 15 minutes)
+```{r}
+
+zipdist <- uds.zip %>% 
+  filter(ReportingYear == 2012) %>% 
+  select(BHCMISID, GrantNumber, ZipCode) %>% 
+  unique() %>% 
+  left_join(df.z.temp %>% filter(Year == 2012), by = c("BHCMISID" = "BHCMIS ID", "ZipCode" = "Zip")) %>% 
+  filter(is.na(ID)) %>% 
+  select(`BHCMISID`:ZipCode) %>% 
+  left_join(uds.zip %>% filter(ReportingYear ==2012), by = c("ZipCode")) %>% 
+  select(ZipCode, BHCMISID.x, BHCMISID.y) %>% 
+  filter(BHCMISID.x != BHCMISID.y)
+
+## This next line takes a minute to run
+zipdist <- df.z.temp %>%
+  left_join(zipdist %>%
+  select(BHCMISID.x, ZipCode) %>%
+  unique(), by = c("BHCMIS ID" = "BHCMISID.x")) %>%
+  select(`BHCMIS ID`, Zip, Att, DirectlyTreated, Tx, ZipCode) %>%
+  unique()
+
+zipdist <- zipdist %>% 
+  #group_by(`BHCMIS ID`) %>% 
+  mutate(CountingIDs = as.numeric(as.factor(`BHCMIS ID`))) %>% 
+  group_by(CountingIDs)
+
+zipdist <- zipdist %>% mutate(DistToClosestSite = NA)
+
+for (g in c(1:695, 697:795, 797:800, 802:847, 849:852)){
+
+  temp1 <- zipdist %>% 
+  filter(CountingIDs == g)
+
+  leaveout <- length(unique(temp1$Zip))
+  temp <- zip.centroids %>% filter(ZipCode %in% c(unique(temp1$Zip), unique(temp1$ZipCode)))
+
+  mm <- as.matrix(dist(as.matrix(temp$X, temp$Y), method = "euclidean", diag = TRUE))[-c(1:leaveout),c(1:leaveout)]
+  zipdist[zipdist$CountingIDs == g,]$DistToClosestSite <-  min(mm) * 111.139
+
+}
+
+zipdist
+
+length(unique(zipdist$`BHCMIS ID`))
+
+```
+
+## Find closest baseline distance
+
+```{r}
+
+df.iv <- df.temptemp %>% 
+  mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% 
+  filter(!is.na(Tx)) %>% 
+  left_join(zipdist %>% 
+  group_by(`BHCMIS ID`) %>% 
+  mutate(DistToClosestSite = min(DistToClosestSite, na.rm = TRUE)) %>% 
+  select(`BHCMIS ID`, DistToClosestSite) %>% 
+  unique(), by = c("BHCMIS ID")) %>% 
+  mutate(Z = log(1 / DistToClosestSite)) %>% 
+  filter(!is.infinite(Z))
+
+# %>%  
+#   ungroup()%>% 
+#   select(Qcomp, Complexity, Pct.NHA:Pct.COM, Tx, ID, ClinicHHI, MHC, HO, PH, Z, Year) %>% 
+#   filter(complete.cases(.))
+
+iv_model <- feols(df.iv, Qcomp ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + MHC + HO + PH | Year | I((10000 - ClinicHHI)/1000) ~ Z, cluster = "ID")
+
+summary(iv_model)
+
+```
+
+# Alt analysis
+
+## Core Estimates
+
+```{r}
+coeffs <- c(0,0,0,0)
+
+for (k in 1:28){
+
+  df.temptemptemp <- df.iv
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  #model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
+  #coeffs <- rbind(coeffs, model$coeftable[2,])
+  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless  | Year | I((10000 - ClinicHHI)/1000) ~ Z, cluster = "ID", data = df.temptemptemp)
+  coeffs <- rbind(coeffs, model$coeftable[1,])
+
+}
+
+core.iv.estimates.alt <- data.frame(cbind(colnames(df.temptemp)[17:44], (coeffs[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  select(V1, Estimate, `95% CI`)
+
+rownames(core.iv.estimates.alt) <- NULL
+
+core.iv.estimates.alt %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  pack_rows(index = c("Overall Impacts" = 4, "Quality of Care" = 6, "Patient Complexity" = 2, "Payer Mix" = 4, "Finances" = 6)) %>% 
+  add_header_above(c("IV-Estimated LATE Effects of Competitive Shocks on Incumbent Clinics" = 3))
+
+```
+
+## Alt Spatial Analysis
+
+```{r}
+
+df.z.temp2 <- df.z.temp %>% 
+  left_join(df.iv %>% ungroup() %>%  select(`BHCMIS ID`, Z, MHC, HO, PH) %>% unique(), by = c("BHCMIS ID")) %>% 
+  left_join(df.temptemp %>% ungroup() %>% select(`BHCMIS ID`, Year, ClinicHHI), by = c("BHCMIS ID", "Year"))
+
+```

### 2024-10-23 code/manuscript_altanalysis.Rmd
making figures

@@
 
-# df.temptemp <- df.temptemp %>% 
-#   left_join(uds.cw %>% filter(Year == 2011) %>% select(BHCMIS.ID:PH), by = c("BHCMIS ID" = "BHCMIS.ID")) %>% 
-#   mutate(ACA = ifelse((STATE %in% c('MI','NH') & Year >= 2014) |
-#                     (STATE %in% c('PA','IN','AK') & Year >= 2015) |
-#                     (STATE %in% c('MT','LA') & Year >= 2016) |
-#                     (STATE %in% c('VA','ME') & Year >= 2019) |
-#                     (STATE %in% c('ID','UT','NE') & Year >= 2020) |
-#                     (STATE %in% c('OK','MO') & Year >= 2021) |
-#                     (STATE %in% c('AZ','AR','CA','CO','CT','DE','DC','HI','IL','IA','KY','MD','MA','MN','NV','NJ','NM','NY','ND','OH','OR','PA','RI','VT','VA','WA') & Year >= 2014), 1, 0))
+coredata <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2012-Full-Dataset.xlsx", sheet = "HealthCenterInfo", skip = 0) %>% select(GrantNumber, FundingCHC:UrbanRuralFlag)
+
+df.temptemp <- df.temptemp %>%
+  left_join(uds.cw %>% filter(Year == 2011) %>% select(ModernGranteeID, BHCMIS.ID:PH), by = c("BHCMIS ID" = "BHCMIS.ID")) %>%
+  left_join(coredata %>% select(GrantNumber, UrbanRuralFlag), by = c("ModernGranteeID" = "GrantNumber")) %>% 
+  mutate(ACA = ifelse((STATE %in% c('MI','NH') & Year >= 2014) |
+                    (STATE %in% c('PA','IN','AK') & Year >= 2015) |
+                    (STATE %in% c('MT','LA') & Year >= 2016) |
+                    (STATE %in% c('VA','ME') & Year >= 2019) |
+                    (STATE %in% c('ID','UT','NE') & Year >= 2020) |
+                    (STATE %in% c('OK','MO') & Year >= 2021) |
+                    (STATE %in% c('AZ','AR','CA','CO','CT','DE','DC','HI','IL','IA','KY','MD','MA','MN','NV','NJ','NM','NY','ND','OH','OR','PA','RI','VT','VA','WA') & Year >= 2014), 1, 0))
 
@@
   #coeffs <- rbind(coeffs, model$coeftable[2,])
-  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + MHC + HO + PH | ID + Year | I((10000 - ClinicHHI)/1000) ~ value, cluster = "ID", data = df.temptemptemp)
+  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + MHC + HO + PH + UrbanRuralFlag| ID + Year | I((10000 - ClinicHHI)/1000) ~ value, cluster = "ID", data = df.temptemptemp)
   coeffs <- rbind(coeffs, model$coeftable[1,])
@@
 
-summary(feols(df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)), I( Pct.None  ) ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year | I((10000 - ClinicHHI)/100) ~ Tx, cluster = "ID"))
+summary(feols(df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% filter(value_min <= 2), 
+              Qcomp ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year | I((10000 - ClinicHHI)/100) ~ Tx, cluster = "ID"))
 
@@
  did2s(
-      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)  ) , 
+      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)  ), 
       yname = "ClinicHHI", 
       treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
         second_stage = ~ i(Tx, ref = FALSE),
@@
     event_study(data = df.temptemp,
-  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
+  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
   filter(abs(term) <= 6) %>%
@@
  event_study(data = df.temptemp %>% filter(value_min == 1),
-  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
+  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
   filter(abs(term) <= 6) %>%
@@
  event_study(data = df.temptemp,
-  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
+  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
   filter(abs(term) <= 8) %>%
@@
   event_study(data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Att = ifelse(Att == 2010, 0, Att)),
-  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
+  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
   filter(abs(term) <= 8) %>%
@@
       treatment = "Tx",
-        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
         second_stage = ~ i(Tx, ref = FALSE),
@@
 did2s(
-      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% filter(Year < 2020 ), 
-      yname = "Closed", 
+      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% filter(Year < 2020 ) %>% mutate(Urban = ifelse(UrbanRuralFlag == "Urban", 1, 0)) %>% filter(!is.na(Urban)),
+      yname = "Staff", 
       treatment = "Tx",
         first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
-        second_stage = ~ i(Tx, ref = FALSE),
+        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * value),
         cluster_var = "ID",
@@
 
+## Event Study
+
+```{r}
+
+es.direct <- did2s(
+  data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% mutate(Urban = ifelse(UrbanRuralFlag == "Urban", 1, 0))  %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) ,
+  yname = "Qcomp", 
+  treatment = "Tx",
+  first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year, 
+    second_stage = ~ i(rel_year, ref = c(-1, Inf)) ,
+    cluster_var = "ID", 
+  verbose = TRUE)
+
+cbind(YearRel = gsub("rel_year::", "", rownames(es.direct$coeftable)), 
+      cbind(Group = "Direct",es.direct$coeftable)) %>% 
+  data.frame() %>% 
+  mutate(estimate = as.numeric(Estimate), 
+         std.error = as.numeric(Std..Error), 
+         YearRel = as.numeric(YearRel)) %>% 
+  filter(abs(YearRel) <= 6) %>% 
+ ggplot(aes(x = YearRel, y = estimate, color = Group)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
+
+```
+
 ## BY Hand
@@
 ## TWFE First Stage
-df.temptemptemp <- df.temptemp %>% select(ClinicHHI, Qcomp, MS, value, Year, ID, Pct.NHA:Pct.None, Tx) %>% ungroup() %>% filter(complete.cases(.))
-
-reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
-firststage <- lm(data = df.temptemptemp, I((10000 - ClinicHHI)/1000) ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
-
-model <- lm(data = df.temptemptemp, Complexity ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless+ factor(Year) + factor(ID))
+df.temptemptemp <- df.temptemp %>% select(ClinicHHI, Qcomp, MS, value, Year, ID, Pct.NHA:Pct.None, Tx, UrbanRuralFlag) %>% ungroup() %>% filter(complete.cases(.))
+
+reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
+firststage <- lm(data = df.temptemptemp, I((10000 - ClinicHHI)/1000) ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless+ UrbanRuralFlag )
+
+model <- lm(data = df.temptemptemp, Complexity ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag+ factor(Year) + factor(ID))
 
@@
 
-reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
+reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
 head(summary(reduced)$coeff) %>% as.data.frame()
 
-reduced <- lm(data = df.temptemptemp, Complexity ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
+reduced <- lm(data = df.temptemptemp, Complexity ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
 head(summary(reduced)$coeff) %>% as.data.frame()
 
-reduced <- lm(data = df.temptemptemp, Closed ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
+reduced <- lm(data = df.temptemptemp, Closed ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
 head(summary(reduced)$coeff) %>% as.data.frame()
@@
          ID = as.numeric(factor(paste(`BHCMIS ID`, Zip, sep = "-")))) %>%
-  select(`BHCMIS ID`:Year, Att, ID, Zip:Tx.z) %>%
+  select(`BHCMIS ID`:Year, Att, ID, Zip:Tx.z, UrbanRuralFlag) %>%
   arrange(`BHCMIS ID`, Zip, Year) %>% 
@@
                Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
-  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att, `BHCMIS ID`)
+  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att, `BHCMIS ID`, UrbanRuralFlag)
 
@@
         second_stage = ~ i(Tx * (1 - DirectlyTreated), ref = FALSE)  + I(Tx * DirectlyTreated),
+      #second_stage = ~ i(Tx , ref = FALSE)  + I(Tx * DirectlyTreated),
         cluster_var = "ID",
@@
   mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>%
-  select(V1, Estimate, `95% CI`, Estimate.1, `95% CI.1`)
+  select(V1, Estimate, `95% CI`, `Pr...t..`, Estimate.1, `95% CI.1`, `Pr...t...1`)
 
@@
 zip.estimates %>% 
-  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI","Estimate","95% CI")) %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI","p-value", "Estimate","95% CI", "p-value")) %>% 
   kable_styling(latex_options = c("striped")) %>%
   pack_rows(index = c("Overall Impacts" = 2, "Patient and Payer Mix" = 4, "Access" = 2)) %>% 
-  add_header_above(c(" " = 1, "Directly Competitive" = 2, "Indirectly Competitive" = 2)) %>% 
-  add_header_above(c("DID-Estimated Effects of Competitive Shocks on Zip Codes in Incumbent Clinics' Service Area" = 5))
+  add_header_above(c(" " = 1, "Directly Competitive" = 3, "Indirectly Competitive" = 3)) %>% 
+  add_header_above(c("DID-Estimated Effects of Competitive Shocks on Zip Codes in Incumbent Clinics' Service Area" = 7))
 
@@
 ```{r}
- event_study(data = df.z.temp %>% filter(Att == 0 | (Att > 0 & DirectlyTreated == 0)),
-  yname = "Total.Hours", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~1) %>%
-  filter(abs(term) <= 8) %>%
-  filter(estimator == "Gardner (2021)") %>%
-  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
-
- event_study(data = df.z.temp %>% filter(Att == 0 | (Att > 0 & DirectlyTreated == 1)),
-  yname = "Total.Hours", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~1) %>%
-  filter(abs(term) <= 8) %>%
-  filter(estimator == "Gardner (2021)") %>%
-  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+
+es.direct <- did2s(
+  data = df.z.temp2 %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 1), 
+  yname = "Sites", 
+  treatment = "Tx",
+  first_stage = ~ 0 | ID + Year, 
+    second_stage = ~ i(rel_year, ref = c(-1, Inf)) ,
+    cluster_var = "ID", 
+  verbose = FALSE)
+
+es.indirect <- did2s(
+  data = df.z.temp2 %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 0), 
+  yname = "Sites", 
+  treatment = "Tx",
+  first_stage = ~ 0 | ID + Year, 
+    second_stage = ~ i(rel_year, ref = c(-1, Inf)) ,
+    cluster_var = "ID", 
+  verbose = FALSE)
+
+cbind(YearRel = c(gsub("rel_year::", "", rownames(es.direct$coeftable)), gsub("rel_year::", "", rownames(es.indirect$coeftable))), 
+      rbind(cbind(Group = "Direct",es.direct$coeftable), cbind(Group = "Indirect",es.indirect$coeftable))) %>% 
+  data.frame() %>% 
+  mutate(estimate = as.numeric(Estimate), 
+         std.error = as.numeric(Std..Error), 
+         YearRel = as.numeric(YearRel)) %>% 
+  filter(abs(YearRel) <= 6) %>% 
+ ggplot(aes(x = YearRel, y = estimate, color = Group)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
@@
          ID = as.numeric(factor(paste(`BHCMIS ID`, Zip, sep = "-")))) %>%
-  select(`BHCMIS ID`:Year, Att, ID, Zip:Tx.z, Tx) %>%
+  select(`BHCMIS ID`:Year, Att, ID, Zip:Tx.z, Tx, UrbanRuralFlag) %>%
   arrange(`BHCMIS ID`, Zip, Year) %>% 
@@
 
-df.zip.1 <- df.z %>% select(ID, Year, Att, NumberofPatients)
+df.zip.1 <- df.z %>% select(ID, Year, Att, NumberofPatients, UrbanRuralFlag)
 df.zip.2 <- df.z.full %>% select(ID, Year, Att.z, Total.z:Quality.z)
@@
 
-Takes a fair bit to run (~ 15 minutes)
 ```{r}
@@
   unique(), by = c("BHCMIS ID" = "BHCMISID.x")) %>%
-  select(`BHCMIS ID`, Zip, Att, DirectlyTreated, Tx, ZipCode) %>%
+  select(`BHCMIS ID`, Zip, Att, DirectlyTreated, Tx, ZipCode, UrbanRuralFlag) %>%
   unique()
@@
 
-zipdist <- zipdist %>% mutate(DistToClosestSite = NA)
+zipdist <- zipdist %>% mutate(DistToClosestSite = NA, ZiplevelDistToClosestSite = NA, DistToFarthestSite = NA)
 
@@
 
-  mm <- as.matrix(dist(as.matrix(temp$X, temp$Y), method = "euclidean", diag = TRUE))[-c(1:leaveout),c(1:leaveout)]
+    ## Calc Farthest Site Distance
+  mm <- as.matrix(dist(as.matrix(temp$X, temp$Y), method = "euclidean", diag = TRUE))[c(1:leaveout),-c(1:leaveout)]
+  zipdist[zipdist$CountingIDs == g,]$DistToFarthestSite <-  max(mm) * 111.139
+
+  ## Calc Closest Site Distance
+  mm <- as.matrix(dist(as.matrix(temp$X, temp$Y), method = "euclidean", diag = TRUE))[c(1:leaveout),-c(1:leaveout)]
   zipdist[zipdist$CountingIDs == g,]$DistToClosestSite <-  min(mm) * 111.139
 
+## Calc Closest Site Distance by zip
+  if (is.null(dim(mm))) {
+          ZipLevel <- data.frame(Zip = unique(temp1$Zip), ZiplevelDistToClosestSite = min(mm, na.rm = TRUE) * 111.139)
+  }else{
+      ZipLevel <- data.frame(Zip = unique(temp1$Zip), ZiplevelDistToClosestSite = apply(mm, 1, FUN = min, na.rm = TRUE) * 111.139)
   }
 
+  zipdist[zipdist$Zip %in% ZipLevel$Zip & zipdist$CountingIDs == g,]$ZiplevelDistToClosestSite <- zipdist[zipdist$Zip %in% ZipLevel$Zip & zipdist$CountingIDs == g,] %>% 
+        ungroup() %>% 
+    select(`BHCMIS ID`:DistToClosestSite) %>% 
+    left_join(ZipLevel, by = c("Zip")) %>% 
+    select(ZiplevelDistToClosestSite) %>% 
+    unlist()
+
+  if (as.integer(g/100) == g/100) {print(g)}
+
+}
+
 zipdist
@@
 length(unique(zipdist$`BHCMIS ID`))
+
+```
+
+## Alt by year
+Takes a couple minutes to run (~ 15)
+
+```{r}
+
+# zipdist <- uds.zip %>%
+#  # filter(ReportingYear == 2012) %>%
+#   select(BHCMISID, GrantNumber, ZipCode, ReportingYear) %>%
+#   unique() %>%
+#   left_join(df.z.temp , by = c("BHCMISID" = "BHCMIS ID", "ZipCode" = "Zip","ReportingYear" = "Year")) %>%
+#   filter(is.na(ID)) %>%
+#   select(`BHCMISID`:ZipCode, ReportingYear) %>%
+#   left_join(uds.zip, by = c("ZipCode","ReportingYear")) %>%
+#   select(ZipCode, BHCMISID.x, BHCMISID.y, ReportingYear) %>%
+#   filter(BHCMISID.x != BHCMISID.y)
+# 
+# inclusion <- zipdist %>%
+#   select(BHCMISID.x, ZipCode, ReportingYear) %>%
+#   unique()
+# 
+# 
+# ## This next line takes a minute to run
+# zipdist <- df.z.temp %>%
+#   left_join(inclusion, by = c("BHCMIS ID" = "BHCMISID.x", "Year" = "ReportingYear")) %>%
+#   select(`BHCMIS ID`, Zip, Att, DirectlyTreated, Tx, ZipCode, Year) %>%
+#   unique()
+# 
+# 
+# 
+# zipdist <- zipdist %>%
+#   filter(Year >= 2012) %>%
+#   #group_by(`BHCMIS ID`) %>%
+#   mutate(CountingIDs = as.numeric(factor(paste(`BHCMIS ID`, Year, sep = "-"))))
+# 
+# 
+# length(unique(zipdist$CountingIDs))
+# 
+# 
+# zipdist <- zipdist %>% mutate(DistToClosestSite = NA)
+# 
+# for (g in c(1:9301)){
+# 
+#   temp1 <- zipdist %>%
+#   filter(CountingIDs == g)
+# 
+#   leaveout <- length(unique(temp1$Zip))
+#   temp <- zip.centroids %>% filter(ZipCode %in% c(unique(temp1$Zip), unique(temp1$ZipCode)))
+# 
+#   mm <- as.matrix(dist(as.matrix(temp$X, temp$Y), method = "euclidean", diag = TRUE))[-c(1:leaveout),c(1:leaveout)]
+#   zipdist[zipdist$CountingIDs == g,]$DistToClosestSite <-  min(mm) * 111.139
+# 
+#   if (as.integer(g/100) == g/100) {print(g)}
+# }
+# 
+# 
+# zipdist
 
@@
   left_join(zipdist %>%
-  group_by(`BHCMIS ID`) %>% 
-  mutate(DistToClosestSite = min(DistToClosestSite, na.rm = TRUE)) %>% 
-  select(`BHCMIS ID`, DistToClosestSite) %>% 
+  select(`BHCMIS ID`, DistToClosestSite, ZiplevelDistToClosestSite, DistToFarthestSite) %>%
   unique(), by = c("BHCMIS ID")) %>%
-  mutate(Z = log(1 / DistToClosestSite)) %>% 
+  #mutate(DistToClosestSite = ifelse(DistToClosestSite > 100, 100, DistToClosestSite)) %>% 
+  mutate(Z = log(1 / (DistToClosestSite / DistToFarthestSite))) %>%
   filter(!is.infinite(Z))
+
+iv_model <- feols(df.iv, Pct.None ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | Year | I((10000 - ClinicHHI)/1000) ~ Z , cluster = "ID")
+summary(iv_model)
+
+summary(lm(data = df.iv, Tx ~ Z))
+
+# df.iv <- df.temptemp %>% 
+#   mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% 
+#   filter(!is.na(Tx)) %>% 
+#   left_join(zipdist %>% 
+#   group_by(`BHCMIS ID`, Year) %>% 
+#   mutate(DistToClosestSite = min(DistToClosestSite, na.rm = TRUE)) %>% 
+# select(`BHCMIS ID`, Year, DistToClosestSite) %>% 
+# unique(), by = c("BHCMIS ID", "Year")) %>% 
+#   mutate(Z = log(1 / DistToClosestSite)) %>% 
+#   filter(!is.infinite(Z))
 
@@
 
-iv_model <- feols(df.iv, Qcomp ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + MHC + HO + PH | Year | I((10000 - ClinicHHI)/1000) ~ Z, cluster = "ID")
-
-summary(iv_model)
+hist(df.iv$Z, na.rm = T)
 
@@
   #coeffs <- rbind(coeffs, model$coeftable[2,])
-  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless  | Year | I((10000 - ClinicHHI)/1000) ~ Z, cluster = "ID", data = df.temptemptemp)
+  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | Year | I((10000 - ClinicHHI)/1000) ~ Z, cluster = "ID", data = df.temptemptemp)
   coeffs <- rbind(coeffs, model$coeftable[1,])
@@
 
+did2s(
+      data = df.iv,
+      yname = "Total",
+      treatment = "Tx",
+        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
 ```
@@
 df.z.temp2 <- df.z.temp %>% 
-  left_join(df.iv %>% ungroup() %>%  select(`BHCMIS ID`, Z, MHC, HO, PH) %>% unique(), by = c("BHCMIS ID")) %>% 
-  left_join(df.temptemp %>% ungroup() %>% select(`BHCMIS ID`, Year, ClinicHHI), by = c("BHCMIS ID", "Year"))
-
-```
+  left_join(df.iv %>% ungroup() %>%  select(`BHCMIS ID`, Z, MHC, HO, PH, value) %>% unique(), by = c("BHCMIS ID"))
+
+feols(Sites ~ 1 |  Year | Tx*DirectlyTreated ~  Z, cluster = "ID", data = df.z.temp2)
+
+did2s(
+      data = df.z.temp2,
+      yname = "NumberofPatients",
+      treatment = "Tx",
+        first_stage = ~ 1 | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx * (1 - DirectlyTreated), ref = FALSE)  + I(Tx * DirectlyTreated),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+```

### 2024-10-30 code/manuscript_altanalysis.Rmd
finalize tables and figures

@@
 library(lmtest)
+library("viridis")
+
 ```
@@
 
-included.years <- 2010:2023
-included.treat <- 2013:2023
+included.years <- 2009:2023
+included.treat <- 2011:2023
 
@@
   select(`BHCMIS ID`:`2023`) %>% 
-  pivot_longer(cols = c(`2010`:`2023`)) %>% 
+  pivot_longer(cols = c(`2009`:`2023`)) %>% 
   group_by(`BHCMIS ID`) %>% 
@@
 dfc %>% filter(ID.x == "90")
+
 ```
@@
   left_join(df.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear")) %>% 
-  mutate(logPatsPerStaff = ifelse(is.infinite(log(Total / Staff)), NA, log(Total / Staff))) %>% 
+  mutate(logPatsPerStaff = ifelse(is.infinite(log(Total / Staff)), NA, (Total / Staff))) %>% 
   mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
@@
 
+df.temptemp <- df.temptemp %>% 
+  left_join(df.temptemp %>% 
+  group_by(ID) %>% 
+  summarise(n()) %>% 
+  filter(`n()` != length(included.years)), by = c("ID")) %>% 
+  filter(is.na(`n()`))
+
+possible.vecs <- rep(included.treat, df.temptemp %>% 
+  filter(Tx == 1 & Year > 2010) %>% 
+  summarise(EarlyTx = min(Year)) %>% 
+  select(EarlyTx) %>% 
+  unlist() %>% 
+  table() )
+
+# 
+# df.temptemp <- df.temptemp %>% 
+#   left_join(df.temptemp %>% 
+#   #filter(Year == 2012) %>% 
+#   mutate(Treat = ifelse(Att > 0 & value_last - value_first > 0, "Treated", "Control")) %>% 
+#   select(Treat, ID, Tx, Att, value_min, value_max, value_first, value_last) %>% 
+#   group_by(Treat, ID, Att, value_min, value_max, value_first, value_last) %>% 
+#   summarise(max(Tx, na.rm = TRUE)) %>% 
+#   arrange(Att), by = c("ID"))
+# #
+
+set.seed(123)
+df.temptemp <- df.temptemp %>% 
+  #filter(Year == 2012) %>% 
+  mutate(Treat = ifelse(Att > 2009 & value_last - value_first > 0, "Treated", "Control")) %>% 
+  mutate(Att.random = ifelse(Treat == "Control", sample(possible.vecs, size = 1, replace = T), Att)) %>% 
+  mutate(year.rel = Year - Att.random) %>% 
+  mutate(Att = ifelse(Att == 2009, 0, Att))
+
+df.temptemp <- df.temptemp #%>% filter(Att %notin% c(2011))
+
+table(df.temptemp$Att)
+
 ```
@@
 
-## Model
-
-```{r}
-
-# %>% 
-#   group_by(ID) %>% 
-#   mutate(Strata = min(Profitability, na.rm = TRUE)) %>% 
-#   filter(Strata < 0)
-
-coeffs <- c(0,0,0,0)
-
-for (k in 1:28){
-
-  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
-  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
-  #model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
-  #coeffs <- rbind(coeffs, model$coeftable[2,])
-  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + MHC + HO + PH + UrbanRuralFlag| ID + Year | I((10000 - ClinicHHI)/1000) ~ value, cluster = "ID", data = df.temptemptemp)
-  coeffs <- rbind(coeffs, model$coeftable[1,])
-
-}
-
-core.iv.estimates <- data.frame(cbind(colnames(df.temptemp)[17:44], (coeffs[-1,]))) %>% 
-  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
-  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
-  select(V1, Estimate, `95% CI`)
-
-core.iv.estimates <- core.iv.estimates
-rownames(core.iv.estimates) <- NULL
-
-core.iv.estimates %>% 
-  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI")) %>% 
-  kable_styling(latex_options = c("striped")) %>%
-  pack_rows(index = c("Overall Impacts" = 4, "Quality of Care" = 6, "Patient Complexity" = 2, "Payer Mix" = 4, "Finances" = 6)) %>% 
-  add_header_above(c("IV-Estimated LATE Effects of Competitive Shocks on Incumbent Clinics" = 3))
-
-summary(feols(df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% filter(value_min <= 2), 
-              Qcomp ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year | I((10000 - ClinicHHI)/100) ~ Tx, cluster = "ID"))
-
-```
-
-## First Stage DID Estimates and Event Study
-
-```{r}
- did2s(
-      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)  ), 
-      yname = "ClinicHHI", 
-      treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
-        second_stage = ~ i(Tx, ref = FALSE),
-        cluster_var = "ID",
-      verbose = TRUE
-    )
-
-    event_study(data = df.temptemp,
-  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
-  filter(abs(term) <= 6) %>%
-  filter(estimator == "Gardner (2021)") %>%
-  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
-
-```
-
-## Heterogeneity by Starting Point
-```{r}
-
- event_study(data = df.temptemp %>% filter(value_min == 1),
-  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
-  filter(abs(term) <= 6) %>%
-  filter(estimator == "Gardner (2021)") %>%
-  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
-
- event_study(data = df.temptemp,
-  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
-  filter(abs(term) <= 8) %>%
-  filter(estimator == "Gardner (2021)") %>%
-  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
-
-  event_study(data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Att = ifelse(Att == 2010, 0, Att)),
-  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
-  filter(abs(term) <= 8) %>%
-  filter(estimator == "Gardner (2021)") %>%
-  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
-
-```
-
-## Alt DID estimates
-
-```{r}
-
-coeffs.did <- c(0,0,0,0)
-
-for (k in 1:22){
-
-  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
-  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
-  model <-  did2s(
-      data = df.temptemptemp, 
-      yname = "Outcome", 
-      treatment = "Tx",
-        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
-        second_stage = ~ i(Tx, ref = FALSE),
-        cluster_var = "ID",
-      verbose = TRUE
-    )
-
-  coeffs.did <- rbind(coeffs.did, model$coeftable[1,])
-
-}
-
-core.did.estimates <- data.frame(cbind(colnames(df.temptemp)[17:38], (coeffs.did[-1,]))) %>% 
-  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
-  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
-  select(V1, Estimate, `95% CI`)
-
-core.did.estimates <- core.did.estimates
-rownames(core.did.estimates) <- NULL
-
-core.did.estimates %>% 
-  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI")) %>% 
-  kable_styling(latex_options = c("striped")) %>%
-  pack_rows(index = c("Overall Impacts" = 4, "Quality of Care" = 6, "Patient Complexity" = 2, "Payer Mix" = 4, "Finances" = 6)) %>% 
-  add_header_above(c("DID-Estimated Effects of Competitive Shocks on Incumbent Clinics" = 3))
-
-did2s(
-      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% filter(Year < 2020 ) %>% mutate(Urban = ifelse(UrbanRuralFlag == "Urban", 1, 0)) %>% filter(!is.na(Urban)),
-      yname = "Staff", 
-      treatment = "Tx",
-        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
-        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * value),
-        cluster_var = "ID",
-      verbose = TRUE
-    )
-
-df.temptemp %>% 
-    ungroup() %>% 
-  group_by(Tx) %>% 
-  summarise(mean(Qcomp, na.rm = TRUE))
-
-```
-
-## Event Study
-
-```{r}
-
-es.direct <- did2s(
-  data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% mutate(Urban = ifelse(UrbanRuralFlag == "Urban", 1, 0))  %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) ,
-  yname = "Qcomp", 
-  treatment = "Tx",
-  first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year, 
-    second_stage = ~ i(rel_year, ref = c(-1, Inf)) ,
-    cluster_var = "ID", 
-  verbose = TRUE)
-
-cbind(YearRel = gsub("rel_year::", "", rownames(es.direct$coeftable)), 
-      cbind(Group = "Direct",es.direct$coeftable)) %>% 
-  data.frame() %>% 
-  mutate(estimate = as.numeric(Estimate), 
-         std.error = as.numeric(Std..Error), 
-         YearRel = as.numeric(YearRel)) %>% 
-  filter(abs(YearRel) <= 6) %>% 
- ggplot(aes(x = YearRel, y = estimate, color = Group)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
-
-```
-
-## BY Hand
-```{r}
-
-## TWFE First Stage
-df.temptemptemp <- df.temptemp %>% select(ClinicHHI, Qcomp, MS, value, Year, ID, Pct.NHA:Pct.None, Tx, UrbanRuralFlag) %>% ungroup() %>% filter(complete.cases(.))
-
-reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
-firststage <- lm(data = df.temptemptemp, I((10000 - ClinicHHI)/1000) ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless+ UrbanRuralFlag )
-
-model <- lm(data = df.temptemptemp, Complexity ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag+ factor(Year) + factor(ID))
-
-m1coeffs_cl <- coeftest(model, vcov = vcovCL, cluster = ~ID)
-m1coeffs_cl
-
-# ## Callaway-Sant'Anna First Stage
-# 
-# example_attgt <- att_gt(yname = "ClinicHHI",
-#                         tname = "Year",
-#                         idname = "ID",
-#                         gname = "Att",
-#                         xformla = ~Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless,
-#                         data = df.temptemp, 
-#                         clustervars = "ID"
-#                         )
-# 
-# # summarize the results
-# aggte(example_attgt)
-
-```
-
-## Basic Linear Reg
-```{r}
-
-reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
-head(summary(reduced)$coeff) %>% as.data.frame()
-
-reduced <- lm(data = df.temptemptemp, Complexity ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
-head(summary(reduced)$coeff) %>% as.data.frame()
-
-reduced <- lm(data = df.temptemptemp, Closed ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
-head(summary(reduced)$coeff) %>% as.data.frame()
-
-```
-
-## Why are the signs funky? 
-We are likely picking up shifting trends in the level differences across values.
-
-```{r}
-df.temptemp %>% #left_join(df.temptemp %>% filter(Tx == 1) %>% summarise(Att = min(Year)), by = c("ID")) %>% 
-               mutate(Att = ifelse(is.na(Att), 0, Att)) %>% 
-  mutate(value = ifelse(value >= 6, 6, value)) %>% 
-  group_by(value, Year) %>% 
-  summarise(HHI = mean(ClinicHHI, na.rm = TRUE)) %>% 
-  ggplot(aes(x = Year, y = HHI, group = value, color = as.factor(value))) + geom_point() + geom_line()
-
-df.temptemp %>% #left_join(df.temptemp %>% filter(Tx == 1) %>% summarise(Att = min(Year)), by = c("ID")) %>% 
-               mutate(Att = ifelse(is.na(Att), 0, Att)) %>% 
-  mutate(value = ifelse(value >= 6, 6, value)) %>% 
-  group_by(value, Year) %>% 
-  summarise(Quality = mean(Qcomp, na.rm = TRUE)) %>% 
-  ggplot(aes(x = Year, y = Quality, group = value, color = as.factor(value))) + geom_point() + geom_line()
-```
+## Demographics
 
@@
   filter(Year == 2012) %>% 
-  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
+  mutate(Treat = ifelse(Att > 0 & value_last - value_first > 0, "Treated", "Control")) %>% 
   select(Treat, Total, Pct.NHA:Staff) %>% 
@@
   summarise(n(), sum(Total, na.rm = TRUE))
+
+df.temptemp %>% 
+  filter(Year == 2012) %>% 
+  ungroup() %>% 
+  mutate(Change = value_last - value_first) %>% 
+  select(value_first, Change) %>% 
+  table()
+
+## Final Data
+demo1 <- df.temptemp %>% 
+  filter(year.rel %in% c(-1, 0)) %>% 
+  ungroup() %>% 
+  mutate(Gx = paste(Treat, year.rel, sep = ": Year Relative ")) %>% 
+  select(Gx, Pct.NHA:Pct.Homeless, UrbanRuralFlag) %>% 
+  tbl_summary(by = Gx, 
+              missing = "no", # don't list missing data separately
+      statistic = all_continuous() ~ "{mean} ({sd})",
+      digits = all_continuous() ~ c(2,2)
+    )
+
+demo2 <- df.temptemp %>% 
+  filter(year.rel %in% c(-1, 0)) %>% 
+   ungroup() %>% 
+  mutate(Gx = paste(Treat, year.rel, sep = ": Year Relative ")) %>% 
+  select(year.rel, ID, Treat, Total, Pct.NHA:Pct.Homeless, UrbanRuralFlag) %>% 
+  pivot_longer(c(Total:Pct.Homeless)) %>% 
+  pivot_wider(id_cols = c(ID, name, Treat), names_from = year.rel, values_from = value) %>% 
+  mutate(diff = `0` - `-1`) %>% 
+  select(ID, name, Treat, diff) %>% 
+  pivot_wider(id_cols = c(ID, Treat), names_from = name, values_from = diff) %>% 
+  ungroup() %>% 
+  select(Treat, Pct.NHA:Pct.Homeless) %>% 
+  tbl_summary(by = Treat, 
+              missing = "no", # don't list missing data separately
+      statistic = all_continuous() ~ "{mean} ({sd})",
+      digits = all_continuous() ~ c(2,2)
+    ) %>% 
+  add_difference()
+
+tbl_merge(tbls = list(demo1, demo2)) %>%
+  modify_spanning_header(everything() ~ NA_character_)
 
@@
   geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
-  geom_dl(label=c(rep("0 Competitors", length(unique(p$Year))), rep("1 Competitor", length(unique(p$Year))), rep("2 Competitors", length(unique(p$Year))), rep("3+ Competitors", length(unique(p$Year)))),
-          method = list("last.points", hjust = 1, vjust = c(2, 2.5, 2.5, -1), cex = 1.5), inherit.aes=T ) + 
+  geom_dl(label=c(rep("0 Rivals", length(unique(p$Year))), rep("1 Rival", length(unique(p$Year))), rep("2 Rivals", length(unique(p$Year))), rep("3+ Rivals", length(unique(p$Year)))), 
+          method = list("last.points", hjust = 1, vjust = c(1.5, 2.5, 2.5, -1), cex = 1.5), inherit.aes=T ) + 
   guides(colour = "none") +theme(axis.text=element_text(size=12),
@@
 
+```
+
+##  Trends over time, figure 1 - black and white for milbank
+
+```{r}
+
+plot0 <- p %>% 
+  arrange(CompetitorsInArea) %>% 
+  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, linetype = CompetitorsInArea)) + ylab("FQHCs") + 
+  #geom_point(size = 1.1) + 
+  geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
+  #geom_dl(label=c(rep("0 Rivals", length(unique(p$Year))), rep("1 Rival", length(unique(p$Year))), rep("2 Rivals", length(unique(p$Year))), rep("3+ Rivals", length(unique(p$Year)))), 
+   #       method = list("last.points", hjust = 1, vjust = c(-3, 2, 2.5, -1), cex = 1.5), inherit.aes=T ) + 
+  #guides(linetype = "none") + 
+  guides(linetype = guide_legend(title = "# other CHCs\nin Incumbent's\nService Area")) + 
+  scale_linetype_manual(values=c(1,2,3, 4)) + 
+  theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=12,face="bold"))
+
+plot1 <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
+            group_by(Zip, Year) %>% 
+  summarise(Counts = n()) %>% 
+  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
+  ungroup() %>% 
+  group_by(Year, Counts) %>% 
+  summarise(Zips = n()) %>% 
+  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
+  group_by(Counts.f, Year) %>% 
+  summarise(Zips = sum(Zips)) %>% 
+  #filter(Year >= 2010) %>% 
+  ggplot(aes(x = Year, y = Zips, group = Counts.f, linetype = Counts.f)) + 
+  #geom_point(size = 1.1) + 
+  geom_line(size = 1.1) + theme_tufte_revised() + 
+  ggtitle("Zip Codes by Number of FQHC Sites") + 
+  #geom_dl(label=c(rep("1 Site", length(unique(p$Year))), rep("2+ Sites", length(unique(p$Year)))), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
+  #guides(linetype = "none") + 
+  ylim(0, 4000) +theme(axis.text=element_text(size=12),
+        axis.title=element_text(size=12,face="bold")) + 
+  scale_linetype_manual(values=c(5, 6)) + 
+  guides(linetype = guide_legend(title = "# CHC Sites by\nZip Code"))
+
+p.desc <- ggarrange(plot1, plot0, ncol = 1)
+
+p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))
+
+#ggsave(filename = "Figure1.png", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Figures", plot = p.desc, width = 8, height = 11)
+
+# p.desc <- ggarrange(plot1, plot0, ncol = 2) 
+# 
+# p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))
+
+#ggsave(filename = "Picture1h.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 16, height = 9)
+
+p.desc
+
+```
+
+## Model
+
+```{r}
+
+# %>% 
+#   group_by(ID) %>% 
+#   mutate(Strata = min(Profitability, na.rm = TRUE)) %>% 
+#   filter(Strata < 0)
+
+coeffs <- c(0,0,0,0)
+
+for (k in 1:28){
+
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  #model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
+  #coeffs <- rbind(coeffs, model$coeftable[2,])
+  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + MHC + HO + PH + UrbanRuralFlag| ID + Year | I((10000 - ClinicHHI)/1000) ~ value, cluster = "ID", data = df.temptemptemp)
+  coeffs <- rbind(coeffs, model$coeftable[1,])
+
+}
+
+core.iv.estimates <- data.frame(cbind(colnames(df.temptemp)[17:44], (coeffs[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  select(V1, Estimate, `95% CI`)
+
+core.iv.estimates <- core.iv.estimates
+rownames(core.iv.estimates) <- NULL
+
+core.iv.estimates %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  pack_rows(index = c("Overall Impacts" = 4, "Quality of Care" = 6, "Patient Complexity" = 2, "Payer Mix" = 4, "Finances" = 6)) %>% 
+  add_header_above(c("IV-Estimated LATE Effects of Competitive Shocks on Incumbent Clinics" = 3))
+
+summary(feols(df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% filter(value_min <= 2), 
+              Qcomp ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year | I((10000 - ClinicHHI)/100) ~ Tx, cluster = "ID"))
+
+```
+
+## First Stage DID Estimates and Event Study
+
+```{r}
+ did2s(
+      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)  ), 
+      yname = "ClinicHHI", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+    event_study(data = df.temptemp,
+  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
+  filter(abs(term) <= 6) %>%
+  filter(estimator == "Gardner (2021)") %>%
+  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
+
+```
+
+## Heterogeneity by Starting Point
+```{r}
+
+ event_study(data = df.temptemp %>% filter(value_min == 1),
+  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
+  filter(abs(term) <= 6) %>%
+  filter(estimator == "Gardner (2021)") %>%
+  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
+
+ event_study(data = df.temptemp,
+  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
+  filter(abs(term) <= 8) %>%
+  filter(estimator == "Gardner (2021)") %>%
+  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
+
+  event_study(data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Att = ifelse(Att == 2010, 0, Att)),
+  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
+  filter(abs(term) <= 8) %>%
+  filter(estimator == "Gardner (2021)") %>%
+  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("FirstStage: ") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
+
+   event_study(data = df.temptemp %>% mutate(ifelse(Att == 2009, 0, Att)),
+  yname = "Complexity", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
+  filter(abs(term) <= 8) %>%
+  filter(estimator == "Gardner (2021)") %>%
+  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
+  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Outcomes") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
+
+```
+
+## Alt DID estimates
+
+```{r}
+
+coeffs.did <- c(0,0,0,0)
+
+for (k in 1:22){
+
+  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  # Winsorized
+  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
+  df.temptemptemp <- df.temptemptemp %>% 
+    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
+                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
+  model <-  did2s(
+      data = df.temptemptemp, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+  coeffs.did <- rbind(coeffs.did, model$coeftable[1,])
+
+}
+
+core.did.estimates <- data.frame(cbind(colnames(df.temptemp)[17:38], (coeffs.did[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  select(V1, Estimate, `95% CI`, Pr...t..)
+
+core.did.estimates <- core.did.estimates
+rownames(core.did.estimates) <- NULL
+
+df.temptemp %>% 
+  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
+  group_by(Post, Treat) %>% 
+  select(Qcomp:Staff) %>% 
+  summarise_all(mean.nas) %>% 
+  # summarise(Total = mean(Total, na.rm = TRUE), 
+  #           Quality = mean(Qcomp, na.rm = TRUE), 
+  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
+  pivot_longer(cols = Qcomp:Staff) %>% 
+  mutate(value = round(value, 2)) %>% 
+  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
+  pivot_wider(id_cols = name, names_from = c(Treat, Post), values_from = value) %>% 
+  mutate(Unadjusted = (Treated_1 - Treated_0) - (Control_1 - Control_0)) %>% 
+  cbind(core.did.estimates) %>% 
+   select(name, `Control_0`, `Control_1`, `Treated_0`, `Treated_1`, Unadjusted, Estimate, `95% CI`, Pr...t..) %>% 
+  mutate(`% Change` = round(Estimate / `Treated_0` * 100, 1)) %>% 
+  rename(Outcome = name) %>% 
+  select(Outcome:Estimate, `95% CI`, Pr...t.., `% Change`) %>% 
+  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","p-value", "% Change")) %>% 
+  kable_styling(latex_options = c("striped")) %>%
+  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
+  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 4))
+
+```
+
+## Event Study
+
+```{r}
+
+# es.direct <- did2s(
+#   data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% mutate(Urban = ifelse(UrbanRuralFlag == "Urban", 1, 0))  %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) ,
+#   yname = "Complexity", 
+#   treatment = "Tx",
+#   first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year, 
+#     second_stage = ~ i(rel_year, ref = c(-1, Inf)) ,
+#     cluster_var = "ID", 
+#   verbose = TRUE)
+# 
+# 
+#  
+# cbind(YearRel = gsub("rel_year::", "", rownames(es.direct$coeftable)), 
+#       cbind(Group = "Direct",es.direct$coeftable)) %>% 
+#   data.frame() %>% 
+#   mutate(estimate = as.numeric(Estimate), 
+#          std.error = as.numeric(Std..Error), 
+#          YearRel = as.numeric(YearRel)) %>% 
+#   filter(abs(YearRel) <= 6) %>% 
+#  ggplot(aes(x = YearRel, y = estimate, color = Group)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+#   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
+#
+
+```
+
+## BY Hand
+```{r}
+
+## TWFE First Stage
+df.temptemptemp <- df.temptemp %>% select(ClinicHHI, Qcomp, MS, value, Year, ID, Pct.NHA:Pct.None, Tx, UrbanRuralFlag) %>% ungroup() %>% filter(complete.cases(.))
+
+reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
+firststage <- lm(data = df.temptemptemp, I((10000 - ClinicHHI)/1000) ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless+ UrbanRuralFlag )
+
+model <- lm(data = df.temptemptemp, Complexity ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag+ factor(Year) + factor(ID))
+
+m1coeffs_cl <- coeftest(model, vcov = vcovCL, cluster = ~ID)
+
+# ## Callaway-Sant'Anna First Stage
+# 
+# example_attgt <- att_gt(yname = "ClinicHHI",
+#                         tname = "Year",
+#                         idname = "ID",
+#                         gname = "Att",
+#                         xformla = ~Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless,
+#                         data = df.temptemp, 
+#                         clustervars = "ID"
+#                         )
+# 
+# # summarize the results
+# aggte(example_attgt)
+
+```
+
+## Basic Linear Reg
+```{r}
+
+reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
+head(summary(reduced)$coeff) %>% as.data.frame()
+
+reduced <- lm(data = df.temptemptemp, Complexity ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
+head(summary(reduced)$coeff) %>% as.data.frame()
+
+# reduced <- lm(data = df.temptemptemp, Closed ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
+# head(summary(reduced)$coeff) %>% as.data.frame()
+
+```
+
+## Why are the signs funky? 
+We are likely picking up shifting trends in the level differences across values.
+
+```{r}
+df.temptemp %>% #left_join(df.temptemp %>% filter(Tx == 1) %>% summarise(Att = min(Year)), by = c("ID")) %>% 
+               mutate(Att = ifelse(is.na(Att), 0, Att)) %>% 
+  mutate(value = ifelse(value >= 6, 6, value)) %>% 
+  group_by(value, Year) %>% 
+  summarise(HHI = mean(ClinicHHI, na.rm = TRUE)) %>% 
+  ggplot(aes(x = Year, y = HHI, group = value, color = as.factor(value))) + geom_point() + geom_line()
+
+df.temptemp %>% #left_join(df.temptemp %>% filter(Tx == 1) %>% summarise(Att = min(Year)), by = c("ID")) %>% 
+               mutate(Att = ifelse(is.na(Att), 0, Att)) %>% 
+  mutate(value = ifelse(value >= 6, 6, value)) %>% 
+  group_by(value, Year) %>% 
+  summarise(Quality = mean(Qcomp, na.rm = TRUE)) %>% 
+  ggplot(aes(x = Year, y = Quality, group = value, color = as.factor(value))) + geom_point() + geom_line()
 ```
@@
                Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
-  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att, `BHCMIS ID`, UrbanRuralFlag)
+  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, ZipHHI, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att, `BHCMIS ID`, UrbanRuralFlag) %>% 
+  ### DATA ERRORS
+  filter(Total.Hours <= 1344.00)
 
@@
 
-for (k in 1:8){
-
-  df.z.temp2 <- df.z.temp #%>% filter(Att == 0 | Att > 2010)
+for (k in 1:9){
+
+  df.z.temp2 <- df.z.temp %>% filter(Year >= 2012) #%>% 
+  #   inner_join(df.z.temp %>%
+  # filter(Year >= 2012) %>%
+  # select(ID) %>%
+  # group_by(ID) %>%
+  # summarise(Counts = n()) %>%
+  # filter(Counts == 12), by = c("ID"))
+
+  #%>% filter(Att == 0 | Att > 2010)
+
+  df.z.temp2 <- df.z.temp %>% filter(Year >= 2012) %>% filter(Att %notin% c(2011))
+
   colnames(df.z.temp2)[k] <- "Outcome"
+
+  # 
+  #   outlier.vals <- quantile(df.z.temp2$Outcome, p = c(0.005, 0.995), na.rm = TRUE)
+  # df.z.temp2 <- df.z.temp2 %>% 
+  #   mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
+  #                           ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
+
   model <-  did2s(
@@
 
-zip.estimates <- data.frame(cbind(colnames(df.z.temp)[1:8], (coeffs[-1,]))) %>% 
+zip.estimates <- data.frame(cbind(colnames(df.z.temp)[1:9], (coeffs[-1,]))) %>% 
   #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
@@
 
-zip.estimates <- zip.estimates[c(1, 6, 2:5, 7:8),]
+zip.estimates <- zip.estimates[c(9, 1, 6, 2:5, 7:8),]
 rownames(zip.estimates) <- NULL
@@
   kable_styling(latex_options = c("striped")) %>%
-  pack_rows(index = c("Overall Impacts" = 2, "Patient and Payer Mix" = 4, "Access" = 2)) %>% 
+  pack_rows(index = c("Overall Impacts" = 3, "Patient and Payer Mix" = 4, "Access" = 2)) %>% 
   add_header_above(c(" " = 1, "Directly Competitive" = 3, "Indirectly Competitive" = 3)) %>% 
@@
 es.direct <- did2s(
-  data = df.z.temp2 %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 1), 
-  yname = "Sites", 
+  data = df.z.temp %>% filter(Year >= 2012) %>% filter(Att %notin% c(2011)) %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 1), 
+  yname = "Total.Hours", 
   treatment = "Tx",
@@
 es.indirect <- did2s(
-  data = df.z.temp2 %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 0), 
-  yname = "Sites", 
+  data = df.z.temp %>% filter(Year >= 2012) %>% filter(Att %notin% c(2011)) %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 0), 
+  yname = "Total.Hours", 
   treatment = "Tx",
@@
 p <- df.z.dist.plot %>% 
+  filter(!is.na(Density.NewZip) & !is.na(Density.Origin)) %>% 
   #filter(DistToClosestSite < 25) %>% 
@@
                          values = c(1.0,0.7,0.1,0))  +#scale_colour_gradientn(colours = terrain.colors(10))+ 
-  theme_minimal() + ylab("Log Population Density of New Zip Code") + 
-  xlab("Log Population Density of Nearest Service Area Zip Code") + 
-  labs(color = "Distance Travelled to\nOpenNew Site (km)") + 
-  guides(size = FALSE) + xlim(0.5, 11.5) + ylim(0.5, 11.5)
+  theme_minimal() + ylab("Log Population Density of Newly Competitive Zip Code") + 
+  xlab("Log Population Density of Nearest Zip Code in Rival's Service Area") + 
+  labs(color = "Distance Travelled to\nOpen New Site (km)") + 
+  ggtitle("Population Density and Distance Rival Traveled to Open Competitive Care Delivery Location") + 
+  #guides(size = FALSE) + 
+  xlim(0, 12) + ylim(0, 12) + 
+theme_tufte_revised()
 p
 
-summary(lm(log(Density.Origin) ~ log(Density.NewZip), data = df.z.dist.plot))
+p <- df.z.dist.plot %>% 
+  filter(!is.na(Density.NewZip) & !is.na(Density.Origin)) %>% 
+  #filter(DistToClosestSite < 25) %>% 
+  ggplot(aes(x = log(Density.Origin), y = log(Density.NewZip))) + 
+  geom_point(aes(colour = DistToClosestSite, alpha = sqrt(DistToClosestSite)), size = 3) + 
+  scale_color_viridis(option = "D", direction = -1) + 
+  scale_colour_gradientn(colours = c("brown","darkorange", "gold","darkgreen"),
+                         values = c(1.0,0.7,0.3, 0.1,0)) + 
+  #scale_colour_gradientn(colours = c("green","royalblue","purple"),
+  #                       values = c(1.0,0.7,0.2, 0))  +#scale_colour_gradientn(colours = terrain.colors(10))+ 
+  theme_minimal() + ylab("Log Population Density of Newly Competitive Zip Code") + 
+  xlab("Log Population Density of Nearest Zip Code in Rival's Service Area") + 
+  labs(color = "Distance Travelled to\nOpen New Site (km)") + 
+  ggtitle("Population Density and Distance Rival Traveled to Open Competitive Care Delivery Location") + 
+  guides(alpha = FALSE) + 
+  xlim(0, 12) + ylim(0, 12) + 
+theme_tufte_revised()
+p
+
+# p <- df.z.dist.plot %>% 
+#   filter(!is.na(Density.NewZip) & !is.na(Density.Origin)) %>% 
+#   #filter(DistToClosestSite < 25) %>% 
+#   ggplot(aes(x = log(Density.Origin), y = log(Density.NewZip))) + 
+#   geom_point(aes(colour = DistToClosestSite, alpha = sqrt(DistToClosestSite), size = DistToClosestSite)) + 
+#   scale_color_viridis(option = "D", direction = -1) + 
+#   scale_colour_gradientn(colours = c("brown","darkorange", "gold","darkgreen"),
+#                          values = c(1.0,0.7,0.3, 0.1,0)) + 
+#   #scale_colour_gradientn(colours = c("green","royalblue","purple"),
+#   #                       values = c(1.0,0.7,0.2, 0))  +#scale_colour_gradientn(colours = terrain.colors(10))+ 
+#   theme_minimal() + ylab("Log Population Density of Newly Competitive Zip Code") + 
+#   xlab("Log Population Density of Nearest Zip Code in Rival's Service Area") + 
+#   labs(color = "Distance Travelled to\nOpen New Site (km)", size = "Distance Travelled to\nOpen New Site (km)") + 
+#   ggtitle("Population Density and Distance Rival Traveled to Open Competitive Care Delivery Location") + 
+#   guides(alpha = FALSE) + 
+#   xlim(0, 12) + ylim(0, 12) + 
+# theme_tufte_revised()
+# p
+
+ggsave(filename = "Figure2.png", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Figures", plot = p, width = 11, height = 8)
+
+summary(lm(log(Density.NewZip) ~ log(Density.Origin) * I(DistToClosestSite / 10), data = df.z.dist.plot))
 
@@
 quantile(df.z.dist.plot$DistToClosestSite, probs = 0.95)
+
+nrow(df.z.dist.plot[df.z.dist.plot$DistToClosestSite < 10,])/nrow(df.z.dist.plot)
+hist(df.z.dist.plot$DistToClosestSite, breaks = 50, xlim = c(0, 100))
 

### 2024-11-01 code/manuscript_altanalysis.Rmd
stratified analysis

@@
 
-         # OverweightOrObesity.prev = T6A_L14A_CB / Total * 100, 
-         # OverweightOrObesity.care = T6A_L14A_CA / T6A_L14A_CB,
+          OverweightOrObesity.prev = T6A_L14A_CB / Total * 100, 
+          OverweightOrObesity.care = T6A_L14A_CA / T6A_L14A_CB,
 
@@
          NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
-         #Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
-         Altman = 0.18 * quick_ratio + 0.3 * Profitability + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
+         Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
+         #Altman = 0.18 * quick_ratio + 0.3 * Profitability/100 + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
   mutate(Att.random = ifelse(Att > 0, Att, NA), 
@@
 dfc %>% filter(ID.x == "90")
+
+dfc %>% 
+  filter(`BHCMIS ID` == "012070")
 
@@
   left_join(df.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear")) %>% 
-  mutate(logPatsPerStaff = ifelse(is.infinite(log(Total / Staff)), NA, (Total / Staff))) %>% 
-  mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
-         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5, 
+  mutate(logPatsPerStaff = ifelse(is.infinite(log(Total / Staff)) | Staff < 5, NA, (Total / Staff))) %>% 
+  mutate(Complexity = (HIV.prev + Asthma.prev + HeartDisease.prev +  Diabetes.prev + Hypertension.prev) / 5, 
+         Intensity = (HIV.care + Asthma.care + HeartDisease.care +  Diabetes.care + Hypertension.care) / 5, 
          Intensity.w = (HIV.care * HIV.prev + HepC.care * HepC.prev + Asthma.care * Asthma.prev + HeartDisease.care * HeartDisease.prev + Depression.care * Depression.prev + Diabetes.care * Diabetes.prev + Hypertension.care * Hypertension.prev) /
@@
 
+df.mt[df.mt$Year >= 2010,]$Complexity <- df.mt[df.mt$Year >= 2010,] %>% 
+  select(HIV.prev, Depression.prev, HeartDisease.prev, Diabetes.prev, Hypertension.prev) %>% 
+  rowMeans(na.rm = TRUE)
+
+df.mt[df.mt$Year >= 2010,]$Intensity <- df.mt[df.mt$Year >= 2010,] %>% 
+  select(HIV.care, Depression.care, HeartDisease.care, Diabetes.care, Hypertension.care) %>% 
+  rowMeans(na.rm = TRUE)
+
 ```
@@
   mutate(value_min = min(value, na.rm = TRUE), value_max = max(value, na.rm = TRUE), value_last = last(value, na_rm = TRUE), value_first = first(value, na_rm = TRUE)) %>% 
-  mutate(Tx = value - value_min) %>%
+  mutate(Tx = value - value_first) %>%
 
@@
   #filter(Year == 2012) %>% 
-  mutate(Treat = ifelse(Att > 2009 & value_last - value_first > 0, "Treated", "Control")) %>% 
+  mutate(Treat = ifelse(Att > 2009 & value_last - value_first > 0 , "Treated", "Control")) %>% 
   mutate(Att.random = ifelse(Treat == "Control", sample(possible.vecs, size = 1, replace = T), Att)) %>% 
   mutate(year.rel = Year - Att.random) %>% 
-  mutate(Att = ifelse(Att == 2009, 0, Att))
-
-df.temptemp <- df.temptemp #%>% filter(Att %notin% c(2011))
-
-table(df.temptemp$Att)
+  mutate(Att = ifelse(value_min == value_max, 0, Att))
+
+df.temptemp <- df.temptemp %>% 
+  filter(!(Treat == "Control" & Att == 2009))
 
@@
 df.temptemp %>% 
-  filter(Year == 2012) %>% 
+  filter(Year == 2009) %>% 
   ungroup() %>% 
+  select(Treat, value_first, value_last) %>% 
   mutate(Change = value_last - value_first) %>% 
@@
   modify_spanning_header(everything() ~ NA_character_)
+
+df.temptemp %>% 
+  filter(Year == 2009) %>% 
+  ungroup() %>% 
+  select(`BHCMIS ID`, ID, Treat, value_first, value_last) %>% 
+  mutate(Change = value_last - value_first) %>% 
+  filter(Treat == "Control") %>% 
+  arrange(desc(Change))
 
@@
 
-  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
+  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx))
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx))
   colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
+  df.temptemptemp <- df.temptemptemp %>% 
+    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
+                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
   #model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless   | I((10000 - ClinicHHI)/1000) ~ Tx + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)
   #coeffs <- rbind(coeffs, model$coeftable[2,])
-  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + MHC + HO + PH + UrbanRuralFlag| ID + Year | I((10000 - ClinicHHI)/1000) ~ value, cluster = "ID", data = df.temptemptemp)
+  model <- feols(Outcome ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year | I((10000 - ClinicHHI)/1000) ~ Tx*value, cluster = "ID", data = df.temptemptemp)
   coeffs <- rbind(coeffs, model$coeftable[1,])
@@
   add_header_above(c("IV-Estimated LATE Effects of Competitive Shocks on Incumbent Clinics" = 3))
-
-summary(feols(df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% filter(value_min <= 2), 
-              Qcomp ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year | I((10000 - ClinicHHI)/100) ~ Tx, cluster = "ID"))
 
@@
 
-   event_study(data = df.temptemp %>% mutate(ifelse(Att == 2009, 0, Att)),
-  yname = "Complexity", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
-  filter(abs(term) <= 8) %>%
+  outlier.vals <- quantile(df.temptemp$Total, p = c(0.01, 0.99), na.rm = TRUE)
+   event_study(data = df.temptemp %>% mutate(ifelse(Att == 2009, 0, Att)) %>% mutate(Total = ifelse(Total <= outlier.vals[1], outlier.vals[1], 
+                            ifelse(Total >= outlier.vals[2], outlier.vals[2], Total))),
+  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
+  filter(abs(term) <= 7) %>%
   filter(estimator == "Gardner (2021)") %>%
@@
 
-for (k in 1:22){
+for (k in 1:23){
 
@@
       treatment = "Tx",
-        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
         second_stage = ~ i(Tx, ref = FALSE),
@@
 
-core.did.estimates <- data.frame(cbind(colnames(df.temptemp)[17:38], (coeffs.did[-1,]))) %>% 
+core.did.estimates <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did[-1,]))) %>% 
   #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
@@
   group_by(Post, Treat) %>% 
-  select(Qcomp:Staff) %>% 
+  select(Qcomp:Closed) %>% 
   summarise_all(mean.nas) %>% 
@@
   #           Finances = mean(Altman, na.rm = TRUE)) %>% 
-  pivot_longer(cols = Qcomp:Staff) %>% 
+  pivot_longer(cols = Qcomp:Closed) %>% 
   mutate(value = round(value, 2)) %>% 
@@
 
+df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) %>% 
+  ungroup() %>% 
+  filter(!is.na(value)) %>% 
+  select(Year, Closed) %>% 
+  group_by(Year) %>% 
+  summarize(mean(Closed))
+
+```
+
+## Stratified by Baseline Market Density
+
+```{r}
+
+coeffs.did.strat <- c(0,0,0,0, 0, 0, 0, 0, 0, 0, 0, 0)
+
+for (k in 1:23){
+
+  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  # Winsorized
+  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
+  df.temptemptemp <- df.temptemptemp %>% 
+    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
+                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
+  model <-  did2s(
+      data = df.temptemptemp, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min==2, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min>= 3, 1, 0), ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+  coeffs.did.strat <- rbind(coeffs.did.strat, c(model$coeftable[1,], model$coeftable[2,], model$coeftable[3,]))
+
+}
+
+core.did.estimates.strat <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.strat[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(EstimateFirst = round(as.numeric(Estimate), 2), `95% CI First` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(Std..Error), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(Std..Error), 2), sep = "")) %>%
+  mutate(EstimateSecond = round(as.numeric(Estimate.1), 2), `95% CI Second` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(Std..Error.1), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(Std..Error.1), 2), sep = "")) %>%
+  mutate(EstimateMore = round(as.numeric(Estimate.2), 2), `95% CI More` = paste(round(as.numeric(Estimate.2) - 1.96 * as.numeric(Std..Error.2), 2), ", ", round(as.numeric(Estimate.2) + 1.96 * as.numeric(Std..Error.2), 2), sep = "")) %>%
+  select(V1, EstimateFirst, `95% CI First`, Pr...t.., EstimateSecond, `95% CI Second`, Pr...t...1, EstimateMore, `95% CI More`, Pr...t...2)
+
+core.did.estimates.strat <- core.did.estimates.strat
+rownames(core.did.estimates.strat) <- NULL
+
+core.did.estimates.strat
+
+did2s(
+      data = df.temptemptemp, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage =~ i(Tx*as.numeric(value_first)) ,
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
 ```
@@
 
-# es.direct <- did2s(
-#   data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% mutate(Urban = ifelse(UrbanRuralFlag == "Urban", 1, 0))  %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) ,
-#   yname = "Complexity", 
-#   treatment = "Tx",
-#   first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year, 
-#     second_stage = ~ i(rel_year, ref = c(-1, Inf)) ,
-#     cluster_var = "ID", 
-#   verbose = TRUE)
-# 
-# 
-#  
-# cbind(YearRel = gsub("rel_year::", "", rownames(es.direct$coeftable)), 
-#       cbind(Group = "Direct",es.direct$coeftable)) %>% 
-#   data.frame() %>% 
-#   mutate(estimate = as.numeric(Estimate), 
-#          std.error = as.numeric(Std..Error), 
-#          YearRel = as.numeric(YearRel)) %>% 
-#   filter(abs(YearRel) <= 6) %>% 
-#  ggplot(aes(x = YearRel, y = estimate, color = Group)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
-#   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
-#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
-#
+es.direct <- did2s(
+  data = df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx))  %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | value_first == 1),
+  yname = "Qcomp", 
+  treatment = "Tx",
+  first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year, 
+    second_stage = ~ i(rel_year, ref = c(-7, Inf)) ,
+    cluster_var = "ID", 
+  verbose = FALSE)
+
+es.indirect <- did2s(
+  data = df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx))  %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | value_first >= 2),
+  yname = "Qcomp", 
+  treatment = "Tx",
+  first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year, 
+    second_stage = ~ i(rel_year, ref = c(-7, Inf)) ,
+    cluster_var = "ID", 
+  verbose = FALSE)
+
+cbind(YearRel = c(gsub("rel_year::", "", rownames(es.direct$coeftable)), gsub("rel_year::", "", rownames(es.indirect$coeftable))), 
+      rbind(cbind(Group = "Direct",es.direct$coeftable), cbind(Group = "Indirect",es.indirect$coeftable))) %>% 
+  data.frame() %>% 
+  mutate(estimate = as.numeric(Estimate), 
+         std.error = as.numeric(Std..Error), 
+         YearRel = as.numeric(YearRel)) %>% 
+  filter(abs(YearRel) <= 6) %>% 
+ ggplot(aes(x = YearRel, y = estimate, color = Group)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
 
@@
 
-df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 >= 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z >= 2010, 1, 0)) %>% 
+df.z.temp <- df.z %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% #mutate(Tx = ifelse(value - 1 >= 1, 1, value - 1)) %>% 
+  filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z >= 2010, 1, 0)) %>% 
   #df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
@@
 
-  df.z.temp2 <- df.z.temp %>% filter(Year >= 2012) %>% filter(Att %notin% c(2011))
+  df.z.temp2 <- df.z.temp %>% filter(Year >= 2012) %>% filter(Att %notin% c(2009:2012))
 
@@
 
+did2s(
+      data = df.z.temp2 %>% filter(Year >= 2012)   %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% left_join(df.temptemp %>% ungroup() %>% select(`BHCMIS ID`, value_min, value_first) %>% unique(), by = c("BHCMIS ID"))
+      %>% filter(Att == 0 | DirectlyTreated == 0), 
+      yname = "Sites", 
+      treatment = "Tx",
+        first_stage = ~ 0 | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
+        second_stage = ~ i(Tx*ifelse(value_first==1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_first>=2, 1, 0), ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
 ```
@@
 es.direct <- did2s(
-  data = df.z.temp %>% filter(Year >= 2012) %>% filter(Att %notin% c(2011)) %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 1), 
-  yname = "Total.Hours", 
+  data = df.z.temp %>% filter(Year >= 2012)   %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 1), 
+  yname = "Sites", 
   treatment = "Tx",
   first_stage = ~ 0 | ID + Year, 
-    second_stage = ~ i(rel_year, ref = c(-1, Inf)) ,
+    second_stage = ~ i(rel_year, ref = c(-7, Inf)) ,
     cluster_var = "ID", 
@@
 es.indirect <- did2s(
-  data = df.z.temp %>% filter(Year >= 2012) %>% filter(Att %notin% c(2011)) %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 0), 
-  yname = "Total.Hours", 
+  data = df.z.temp%>% filter(Year >= 2012)   %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 0), 
+  yname = "Sites", 
   treatment = "Tx",
   first_stage = ~ 0 | ID + Year, 
-    second_stage = ~ i(rel_year, ref = c(-1, Inf)) ,
+    second_stage = ~ i(rel_year, ref = c(-7, Inf)) ,
     cluster_var = "ID", 
@@
 
-nrow(df.z.dist.plot[df.z.dist.plot$DistToClosestSite < 10,])/nrow(df.z.dist.plot)
+nrow(df.z.dist.plot[df.z.dist.plot$DistToClosestSite < 16.09,])/nrow(df.z.dist.plot)
 hist(df.z.dist.plot$DistToClosestSite, breaks = 50, xlim = c(0, 100))
+
+df.z.dist.plot[df.z.dist.plot$DistToClosestSite > 16.09,] %>% 
+  summarise(median((Density.NewZip), na.rm = TRUE), median((Density.Origin), na.rm = TRUE)) %>% 
+  unlist()
+
+df.z.dist.plot[df.z.dist.plot$DistToClosestSite > 16.09,] %>% 
+  left_join(df.temptemp %>% filter(Year == 2011), by = c("BHCMIS ID.y" = "BHCMIS ID"))
 
@@
   #coeffs <- rbind(coeffs, model$coeftable[2,])
-  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | Year | I((10000 - ClinicHHI)/1000) ~ Z, cluster = "ID", data = df.temptemptemp)
+  model <- feols(Outcome ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | Year | I((10000 - ClinicHHI)/1000) ~ Z, cluster = "ID", data = df.temptemptemp)
   coeffs <- rbind(coeffs, model$coeftable[1,])
@@
   add_header_above(c("IV-Estimated LATE Effects of Competitive Shocks on Incumbent Clinics" = 3))
-
-did2s(
-      data = df.iv,
-      yname = "Total",
-      treatment = "Tx",
-        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
-        second_stage = ~ i(Tx, ref = FALSE),
-        cluster_var = "ID",
-      verbose = TRUE
-    )
 

### 2024-11-01 code/manuscript_altanalysis.Rmd
finalized stratified analysis

@@
   group_by(Post, Treat) %>% 
-  select(Qcomp:Closed) %>% 
+  select(Qcomp:Staff) %>% 
   summarise_all(mean.nas) %>% 
@@
   #           Finances = mean(Altman, na.rm = TRUE)) %>% 
-  pivot_longer(cols = Qcomp:Closed) %>% 
+  pivot_longer(cols = Qcomp:Staff) %>% 
   mutate(value = round(value, 2)) %>% 
@@
   mutate(Unadjusted = (Treated_1 - Treated_0) - (Control_1 - Control_0)) %>% 
+  rbind(
+
+    cbind(name = "Closed", 
+    df.temptemp %>% 
+  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
+  filter(!is.na(value)) %>% 
+  group_by(Post, Treat) %>% 
+  select(Closed) %>% 
+  summarise_all(mean.nas) %>% 
+  # summarise(Total = mean(Total, na.rm = TRUE), 
+  #           Quality = mean(Qcomp, na.rm = TRUE), 
+  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
+  #mutate(value = round(value, 2)) %>% 
+  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
+  pivot_wider(names_from = c(Treat, Post), values_from = Closed) %>% 
+  mutate(Unadjusted = (Treated_1 - Treated_0) - (Control_1 - Control_0)))
+
+  ) %>%
+
   cbind(core.did.estimates) %>% 
@@
 
-df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) %>% 
-  ungroup() %>% 
-  filter(!is.na(value)) %>% 
-  select(Year, Closed) %>% 
-  group_by(Year) %>% 
-  summarize(mean(Closed))
-
 ```
@@
 
-coeffs.did.strat <- c(0,0,0,0, 0, 0, 0, 0, 0, 0, 0, 0)
+coeffs.did.strat <- c(0,0,0,0, 0, 0, 0, 0)
 
@@
                             ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
+
    model <-  did2s(
@@
         first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
-        second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min==2, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min>= 3, 1, 0), ref = FALSE),
+        second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min>=2, 1, 0), ref = FALSE),
+        #second_stage =~ i(Tx, ref = FALSE) + I(as.numeric(Tx) * as.numeric(value_min)) ,
         cluster_var = "ID",
@@
 
-  coeffs.did.strat <- rbind(coeffs.did.strat, c(model$coeftable[1,], model$coeftable[2,], model$coeftable[3,]))
+  coeffs.did.strat <- rbind(coeffs.did.strat, c(model$coeftable[1,], model$coeftable[2,]))
 
@@
   mutate(EstimateSecond = round(as.numeric(Estimate.1), 2), `95% CI Second` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(Std..Error.1), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(Std..Error.1), 2), sep = "")) %>%
-  mutate(EstimateMore = round(as.numeric(Estimate.2), 2), `95% CI More` = paste(round(as.numeric(Estimate.2) - 1.96 * as.numeric(Std..Error.2), 2), ", ", round(as.numeric(Estimate.2) + 1.96 * as.numeric(Std..Error.2), 2), sep = "")) %>%
-  select(V1, EstimateFirst, `95% CI First`, Pr...t.., EstimateSecond, `95% CI Second`, Pr...t...1, EstimateMore, `95% CI More`, Pr...t...2)
+  select(V1, EstimateFirst, `95% CI First`, Pr...t.., EstimateSecond, `95% CI Second`, Pr...t...1)
 
@@
 
-core.did.estimates.strat
+core.did.estimates.strat[c(1, 2, 3, 4, 11:13, 16:23),]
+
+#   model <-  did2s(
+#       data = df.temptemptemp,
+#       yname = "Outcome",
+#       treatment = "Tx",
+#         first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+#         second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min==2, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min>= 3, 1, 0), ref = FALSE),
+#         cluster_var = "ID",
+#       verbose = TRUE
+#     )
+# 
+#   coeffs.did.strat <- rbind(coeffs.did.strat, c(model$coeftable[1,], model$coeftable[2,], model$coeftable[3,]))
+# 
+# 
+# }
+# 
+# 
+# core.did.estimates.strat <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.strat[-1,]))) %>%
+#   #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>%
+#   mutate(EstimateFirst = round(as.numeric(Estimate), 2), `95% CI First` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(Std..Error), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(Std..Error), 2), sep = "")) %>%
+#   mutate(EstimateSecond = round(as.numeric(Estimate.1), 2), `95% CI Second` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(Std..Error.1), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(Std..Error.1), 2), sep = "")) %>%
+#   mutate(EstimateMore = round(as.numeric(Estimate.2), 2), `95% CI More` = paste(round(as.numeric(Estimate.2) - 1.96 * as.numeric(Std..Error.2), 2), ", ", round(as.numeric(Estimate.2) + 1.96 * as.numeric(Std..Error.2), 2), sep = "")) %>%
+#   select(V1, EstimateFirst, `95% CI First`, Pr...t.., EstimateSecond, `95% CI Second`, Pr...t...1, EstimateMore, `95% CI More`, Pr...t...2)
+# 
+# core.did.estimates.strat <- core.did.estimates.strat
+# rownames(core.did.estimates.strat) <- NULL
+# 
+# core.did.estimates.strat[c(1, 2, 3, 4, 11:13, 16:23),]
 
@@
       data = df.temptemptemp, 
-      yname = "Outcome", 
+      yname = "Qcomp", 
       treatment = "Tx",
         first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
-        second_stage =~ i(Tx*as.numeric(value_first)) ,
+        second_stage =~ i(Tx, ref = FALSE) + I(as.numeric(Tx) * as.numeric(value_first - 1)) ,
         cluster_var = "ID",

### 2024-11-05 code/manuscript_altanalysis.Rmd
more figures

@@
          PctPoverty = IncomeBelowPoverty / PovertyStatusDet * 100, 
+         PctUnemployed = Unemployed / Unemp_denom * 100, 
          PctBlack = Black / TotalPop * 100, 
-         PctHispanic = Hispanic / TotalPop * 100) %>% 
-    select(Status, TotalPop, PctMedicaid:PctHispanic) %>% 
+         PctHispanic = Hispanic / TotalPop * 100, 
+         PctChildren = AgeUnder18 / TotalPop * 100, 
+         PctElderly = Age65andOver / TotalPop * 100, 
+         PctEducLow = EducLow / TotalPop * 100) %>% 
+    select(Status, TotalPop, PctMedicaid:PctEducLow, UrbanRuralFlag) %>% 
     tbl_summary(by = Status, 
@@
 
+df.z.dist %>% 
+  arrange(DistToClosestSite) %>% 
+  ggplot(aes(x=DistToClosestSite)) + 
+  geom_histogram(binwidth = 1, fill="lightgrey", color="white") + 
+  xlim(0, 100) +
+  stat_bin(aes(y=cumsum(..count..)/sum(..count..)*100 *3/2), binwidth = 1, geom="line", color="blue") + 
+  scale_y_continuous(name = 'Number of Rivals', 
+                     sec.axis = sec_axis(~.*2/3, name = "Cumulative percentage (%)")) + 
+  theme_tufte_revised() + 
+  ggtitle("FQHC Rivals by Distance from Service Area to New Competitive Zip") + 
+  xlab("Distance Travelled (km)")
+
 ```
@@
 ```
+
+# Save Datasets
+```{r}
+#df.z.temp %>% write_csv("/Users/markow/Dropbox/Git/Competition/data_processed/final_manuscript_allocation.csv")
+#df.temptemp %>% write_csv("/Users/markow/Dropbox/Git/Competition/data_processed/final_manuscript_core.csv")
+```

### 2024-11-08 code/manuscript_altanalysis.Rmd
more figures

@@
 library("viridis")
+library(DescTools)
 
@@
 
-p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))
+p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2023", face = "bold", size = 14))
 
@@
 
+winsors <- function(x){ Winsorize(x, val = quantile(x, probs = c(0.01, 0.99), na.rm = TRUE))}
+
 df.temptemp %>% 
   mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
+  select(Post, Treat) %>% 
+  cbind(
+df.temptemp %>% 
+  ungroup() %>% 
+  select(Qcomp:Staff) %>% 
+  summarise_all(winsors)
+) %>% 
   group_by(Post, Treat) %>%
-  select(Qcomp:Staff) %>% 
+
   summarise_all(mean.nas) %>% 
@@
 
+## Benjamini Hochberg
+```{r}
+core.did.estimates %>% 
+  arrange(`Pr...t..`) %>% 
+  mutate(`Pr...t..` = as.numeric(`Pr...t..`)) %>% 
+  cbind(c(1:nrow(core.did.estimates)) / nrow(core.did.estimates) * 0.1) %>% 
+  mutate(Row = row_number()) %>% 
+  ggplot(aes(x = Row, y = `Pr...t..`)) + geom_point() + 
+  ylab("p-values") + xlab("Significance Rank") + geom_abline(slope = 1/nrow(core.did.estimates) * 0.1, intercept = 0, color="red", linetype="dashed", alpha=.5) + theme_minimal()
+
+```
+
 ## Stratified by Baseline Market Density
@@
 
-did2s(
+df.temptemp %>% 
+  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
+  filter(!is.na(value) & value_min > 1) %>% 
+  group_by(Post, Treat) %>% 
+  select(Closed) %>% 
+  summarise_all(mean.nas)
+
+```
+
+## Compared to pre-2020 estimates
+```{r}
+
+coeffs.did.pre2020 <- c(0,0,0,0)
+
+for (k in 1:23){
+
+  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx) & Year < 2020) #%>% filter(Att %notin% c(2011))
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  # Winsorized
+  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
+  df.temptemptemp <- df.temptemptemp %>% 
+    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
+                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
+  model <-  did2s(
       data = df.temptemptemp, 
-      yname = "Qcomp", 
+      yname = "Outcome", 
       treatment = "Tx",
         first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
-        second_stage =~ i(Tx, ref = FALSE) + I(as.numeric(Tx) * as.numeric(value_first - 1)) ,
+        second_stage = ~ i(Tx, ref = FALSE),
         cluster_var = "ID",
@@
     )
+
+  coeffs.did.pre2020 <- rbind(coeffs.did.pre2020, model$coeftable[1,])
+
+}
+
+core.did.estimates.pre2020 <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.pre2020[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  select(V1, Estimate, `95% CI`, Pr...t..)
+
+core.did.estimates.pre2020 <- core.did.estimates.pre2020
+rownames(core.did.estimates) <- NULL
+
+cbind(core.did.estimates, core.did.estimates.pre2020)
 
@@
   ggplot(aes(x = Year, y = Quality, group = value, color = as.factor(value))) + geom_point() + geom_line()
+```
+
+## Closures? Mergers?
+
+```{r}
+
+df.temptemp %>% 
+  filter(Closed == 100 & !is.na(Tx)) %>% 
+  select(ModernGranteeID, `BHCMIS ID`, Year)
+
+H80CS00003
 ```
@@
 ```
+## Back of the envelop
+
+```{r}
+
+asdf <- df.z.temp %>% 
+  filter(Year == 2012) %>% 
+  filter(Att > 0) %>% 
+  group_by(DirectlyTreated) %>% 
+  summarise(Counts = n(), Hours = mean.nas(Total.Hours)) %>% 
+  cbind(Changes = c(zip.estimates[3,5], zip.estimates[3,2])) %>% 
+  summarise(Num = abs(Changes * Counts), Denom = Hours * Counts) %>% 
+  colSums()
+
+asdf[1] / asdf[2]
+
+```
 

### 2024-11-08 code/manuscript_altanalysis.Rmd
estimate of change

@@
   select(Closed) %>% 
-  summarise_all(mean.nas)
+  summarise(mean.nas, n())
+
+df.temptemp %>% 
+  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
+  filter(!is.na(value) & value_min > 1) %>% 
+  group_by(Post, Treat) %>% 
+  select(Closed) %>% 
+  summarise(n())
+
+df.temptemp %>% 
+  filter(Tx == 1 & Closed == 100 & value > 2)
 

### 2024-11-13 code/manuscript_altanalysis.Rmd
Appendix Figures

@@
 
-  outlier.vals <- quantile(df.temptemp$Total, p = c(0.01, 0.99), na.rm = TRUE)
-   event_study(data = df.temptemp %>% mutate(ifelse(Att == 2009, 0, Att)) %>% mutate(Total = ifelse(Total <= outlier.vals[1], outlier.vals[1], 
-                            ifelse(Total >= outlier.vals[2], outlier.vals[2], Total))),
-  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
+  outlier.vals <- quantile(df.temptemp$Altman, p = c(0.01, 0.99), na.rm = TRUE)
+   event_study(data = df.temptemp %>% mutate(ifelse(Att == 2009, 0, Att)) %>% mutate(Altman = ifelse(Altman <= outlier.vals[1], outlier.vals[1], 
+                            ifelse(Altman >= outlier.vals[2], outlier.vals[2], Altman))),
+  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
   filter(abs(term) <= 7) %>%
   filter(estimator == "Gardner (2021)") %>%
-  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
+  #filter(estimator != "Callaway and Sant'Anna (2020)") %>%
   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +

### 2024-11-19 code/manuscript_altanalysis.Rmd
new figures

@@
 
+## Formal Pre-trends
+
+```{r}
+
+pretrends <- c(0,0,0,0,0)
+for (k in 1:23){
+
+  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  # Winsorized
+  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
+  df.temptemptemp <- df.temptemptemp %>% 
+    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
+                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
+  model <-  did2s(
+      data = df.temptemptemp, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(year.rel, ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+pretrends <- rbind(pretrends, cbind(Outcome = colnames(df.temptemp[,(16+k)]), model$coeftable))
+}
+
+pretrends <- pretrends[-1,]
+
+rownames(pretrends)
+ordering <- as.numeric(gsub(pattern = "year.rel::", replacement = "", rownames(pretrends)))
+
+cbind(ordering, data.frame(pretrends))[order(ordering),] %>% 
+  filter(ordering %in% c(-6:-2)) %>% 
+  filter(Outcome %notin% c("htn.rate","dm.rate","pap.rate","crc.rate","childbmi.rate","adultbmi.rate")) %>% 
+  arrange(`Pr...t..`) %>% 
+  mutate(P.value = as.numeric(`Pr...t..`)) %>% 
+  cbind(c(1:85) / 85 * 0.1) %>% 
+  mutate(Row = row_number()) %>% 
+  ggplot(aes(x = Row, y = P.value)) + geom_point() + 
+  ylab("p-values") + xlab("Significance Rank") + geom_abline(slope = 1/85 * 0.1, intercept = 0, color="red", linetype="dashed", alpha=.5) + theme_minimal() + 
+  geom_abline(slope = 1/85, intercept = 0, color="blue", linetype="dashed", alpha=.5)
+
+```
+
 ## Stratified by Baseline Market Density
@@
   filter(Tx == 1 & Closed == 100 & value > 2)
+```
+
+## Stratified figure instead of table 
+```{r}
+
+strat.temp <- coeffs.did.strat
+strat.temp[3,] <- strat.temp[3,] / 1000
+strat.temp[23,] <- strat.temp[23,] / 100
+strat.temp[18,] <- strat.temp[18,] / 100
+
+strat.temp <- (cbind(core.did.estimates.strat[,1], strat.temp[-1,c(1:2)]) %>% 
+  data.frame() %>% 
+  mutate(Estimate = as.numeric(Estimate), 
+         `Std..Error` = as.numeric(Std..Error)) %>% 
+  mutate(LB = Estimate - Std..Error * 1.96, 
+         UB = Estimate + Std..Error * 1.96) %>% 
+  rename(Outcome = V1) %>% 
+  mutate(Class = "First Shock"))[c(1, 2, 3, 4, 11:13, 16:23),c(1,2, 4:6)] %>% 
+  rbind((cbind(core.did.estimates.strat[,1], strat.temp[-1,c(5:6)]) %>% 
+  data.frame() %>% 
+  mutate(Estimate = as.numeric(Estimate), 
+         `Std..Error` = as.numeric(Std..Error)) %>% 
+  mutate(LB = Estimate - Std..Error * 1.96, 
+         UB = Estimate + Std..Error * 1.96) %>% 
+  rename(Outcome = V1) %>% 
+  mutate(Class = "Multiple Shocks"))[c(1, 2, 3, 4, 11:13, 16:23),c(1,2, 4:6)])
+
+strat.temp %>% 
+  mutate(Measure = ifelse(Outcome %in% c("Qcomp","Total","Altman","logPatsPerStaff","Staff","Closed"), "Overall Metrics", 
+                          ifelse(Outcome %in% c("Pct.MCD","Pct.None","Complexity","Intensity"), "Patient Mix", "Financials"))) %>%
+
+ggplot(aes(y=Outcome, x=Estimate, xmin=LB, xmax=UB)) +
+geom_point() +
+
+#this changes the features of the overall effects
+#one could resize, reshape, or recolor these points if desired
+xlab("Effect Estimates") + 
+ylab(NULL) + 
+#adds the CIs
+geom_errorbarh(height=.1) +
+
+#sets the scales
+#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
+#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
+#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
+
+#adding a vertical line at the effect = 0 mark
+geom_vline(xintercept=0, color="black", linetype="dashed", alpha= 1)+
+
+#faceting based on my subgroups
+  #facet_wrap(~X1) +
+facet_grid(Measure~Class, scales= "free_y", switch = 'y', space = "free_y") +
+
+#thematic stuff
+#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
+theme_tufte_revised()+
+   theme(strip.placement = "outside") +
+#theme(text=element_text(family="Times",size=12, color="black"))+
+theme(panel.spacing = unit(1, "lines"))
+
+#core.did.estimates.strat[,1] <- c("Composite Quality of Care, %","Total Patients, No.","Financial Resilience","Operational Efficiency","Clinical Complexity","Intensity","Medicaid, %","Uninsured, %","Cost Per Patient")
 
@@
 
+## Sites and Zips per clinic
+```{r}
+
+df.z.temp %>% 
+  filter(Year == 2012) %>% 
+  mutate(Treat = ifelse(Att > 0, 1, 0)) %>% 
+  group_by(`BHCMIS ID`) %>% #, Treat
+  filter(Sites > 0) %>% 
+  summarise(Zips = n(), Sites = sum(Sites, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  #group_by(Treat) %>% 
+  summarise(mean(Zips), mean(Sites))
+
+```
+
 ## Event Study

### 2024-11-19 code/manuscript_altanalysis.Rmd
Better Stratified Figure

@@
   rename(Outcome = V1) %>% 
-  mutate(Class = "Multiple Shocks"))[c(1, 2, 3, 4, 11:13, 16:23),c(1,2, 4:6)])
-
-strat.temp %>% 
+  mutate(Class = "Multiple Shocks"))[c(1, 2, 3, 4, 11:13, 16:23),c(1,2, 4:6)]) %>% 
   mutate(Measure = ifelse(Outcome %in% c("Qcomp","Total","Altman","logPatsPerStaff","Staff","Closed"), "Overall Metrics", 
-                          ifelse(Outcome %in% c("Pct.MCD","Pct.None","Complexity","Intensity"), "Patient Mix", "Financials"))) %>%
+                          ifelse(Outcome %in% c("Pct.MCD","Pct.None","Complexity","Intensity"), "Patient Mix", "Financials")))
+
+strat.temp$Outcome <- rep(c("Composite Quality of Care, %", "Total Patients Served, No.","Financial resilience,\nAltman’s Z Score", "Patient-to-Staff Ratio","Average prevalence of\nselect chronic conditions, %","Intensity", "Medicaid, %","Uninsured, %","CostPerPat","Quick Ratio, %","Months of Cash Available", "Revenue-to-Expenses, Ratio %","Liabilities-to-Assets, Ratio %","Staff, No.","Closure, Acquisition or\nloss of FQHC status, %"), 2)
+
+p <- strat.temp  %>% 
+  filter(Outcome %notin% c("Intensity","CostPerPat")) %>%
 
@@
 #adding a vertical line at the effect = 0 mark
-geom_vline(xintercept=0, color="black", linetype="dashed", alpha= 1)+
+geom_vline(xintercept=0, color="black", linetype="dashed", alpha= 1) +
 
@@
 
-#core.did.estimates.strat[,1] <- c("Composite Quality of Care, %","Total Patients, No.","Financial Resilience","Operational Efficiency","Clinical Complexity","Intensity","Medicaid, %","Uninsured, %","Cost Per Patient")
+p + theme(panel.spacing = unit(1, "lines"),  strip.text = element_text(face = "bold", size = 12))
 

### 2024-11-21 code/manuscript_altanalysis.Rmd
i promise, final figures

@@
 
-  outlier.vals <- quantile(df.temptemp$Altman, p = c(0.01, 0.99), na.rm = TRUE)
-   event_study(data = df.temptemp %>% mutate(ifelse(Att == 2009, 0, Att)) %>% mutate(Altman = ifelse(Altman <= outlier.vals[1], outlier.vals[1], 
-                            ifelse(Altman >= outlier.vals[2], outlier.vals[2], Altman))),
-  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
-  filter(abs(term) <= 7) %>%
-  filter(estimator == "Gardner (2021)") %>%
-  #filter(estimator != "Callaway and Sant'Anna (2020)") %>%
-  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
-  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
-  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Outcomes") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
-
 ```
@@
 
+## Final DID Event Studies and Alt Estimate Models (Sun-Abraham, TWFE)
+
+```{r}
+
+es.data <- data.frame(estimator = 0, term = 0, estimate = 0, std.error = 0, Measure = 0)
+
+for (k in 1:23){
+
+  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  # Winsorized
+  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
+  df.temptemptemp <- df.temptemptemp %>% 
+    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
+                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
+
+  model <-  event_study(data = df.temptemptemp,
+  yname = "Outcome", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
+  filter(abs(term) <= 7)
+
+  es.data <- rbind(es.data, data.frame(model, Measure = colnames(df.temptemp)[(16+k)]))
+
+}
+
+ess <- es.data[-1,] %>%
+
+  #filter(estimator %notin% c("Callaway and Sant'Anna (2020)","Roth and Sant'Anna (2021)")) %>% 
+  filter(estimator == "Gardner (2021)") %>%
+
+  filter(Measure %in% c('Total','Staff','Altman','Pct.MCD','Pct.None','Complexity')) %>% 
+  mutate(Group = ifelse(Measure %in% c('Total','Staff','logPatsPerStaff','Qcomp'), "Operational Metrics", 
+                        ifelse(Measure %in% c('Altman','LiabPctAssets','months_of_cash'), 'Financial Metrics', 'Selection Metrics'))) %>% 
+  rename(Year = term) %>% 
+  ggplot(aes(x = Year, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
+  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
+  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + 
+  facet_wrap(Group~Measure, scales = "free_y", ncol = 2)
+
+ess + theme(legend.position="none")
+ess + theme(legend.position="bottom")
+
+```
+
 ## Benjamini Hochberg
@@
   select(Closed) %>% 
-  summarise(mean.nas, n())
+  summarise(mean.nas(Closed), n())
 
@@
 
-H80CS00003
+#H80CS00003
 ```
@@
 ```
+
+## Comparing Rivals with Incumbents
+```{r}
+  df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.y" = "BHCMISID", "Year")) %>% 
+      mutate(Type = "Incumbent") %>% 
+      rbind(df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.x" = "BHCMISID", "Year")) %>% mutate(Type = "Rival")) %>% 
+        mutate(Quality = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100) %>% 
+      mutate(quick_ratio = as.numeric(quick_ratio),
+             Liquidity = (Assets - Liabilities) / Assets,
+               Profitability = ngla_net_gain_loss / Assets, #Assets, 
+               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
+               NetWorth = (Assets - Liabilities) / Liabilities) %>% 
+      mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity), 
+         Profitability = ifelse(is.infinite(Profitability), NA, Profitability), 
+         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency), 
+         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
+         #Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
+         Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
+      select(Type, Quality, Total, Altman, Pct.NHA:Pct.COM) %>% 
+          tbl_summary(by = Type, 
+                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
+  add_p()
+
+  df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.y" = "BHCMISID", "Year")) %>% 
+      mutate(Type = "Incumbent") %>% 
+    group_by(`BHCMIS ID.y`)
+
+  length(unique(df.z.temp2$`BHCMIS ID`))
+
+```
+
+## Stratified Figure
+
+```{r}
+coeffs.strat <- coeffs
+coeffs.strat[2,] <- coeffs.strat[2,] / 100
+
+strat.zip.temp <- data.frame(cbind(colnames(df.z.temp)[1:9], (coeffs.strat[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>%
+  filter(V1 != "ZipHHI") %>% 
+   mutate(LB = Estimate - as.numeric(Std..Error) * 1.96, 
+         UB = Estimate + as.numeric(Std..Error) * 1.96) %>% 
+  select(V1, Estimate, LB, UB) %>% 
+    mutate(Class = "Directly Competitive")%>% 
+  rbind(data.frame(cbind(colnames(df.z.temp)[1:9], (coeffs.strat[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>%
+  filter(V1 != "ZipHHI") %>% 
+   mutate(LB = Estimate.1 - as.numeric(Std..Error.1) * 1.96, 
+          UB = Estimate.1 + as.numeric(Std..Error.1) * 1.96) %>% 
+    select(V1, Estimate.1, LB, UB) %>% 
+    rename(Estimate = Estimate.1) %>% 
+    mutate(Class = "Indirectly Competitive")) %>% 
+  rename(Outcome = V1) %>% 
+  filter(Outcome != "Total.Hours") %>% 
+  mutate(Measure = ifelse(Outcome %in% c("Sites","Mean.Hours"), "Access to Care", "Patients and Payer Mix"))
+
+strat.zip.temp$Outcome <- as.factor(strat.zip.temp$Outcome)
+
+p <- strat.zip.temp  %>% 
+  filter(Outcome %notin% c("Intensity","CostPerPat")) %>%
+
+ggplot(aes(y=Outcome, x=Estimate, xmin=LB, xmax=UB)) +
+geom_point() +
+
+#this changes the features of the overall effects
+#one could resize, reshape, or recolor these points if desired
+xlab("Effect Estimates") + 
+ylab(NULL) + 
+#adds the CIs
+geom_errorbarh(height=.1) +
+
+#sets the scales
+#note that I reverse the y axis to correctly order the effect #sizes based on my index variable
+#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
+#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+
+
+#adding a vertical line at the effect = 0 mark
+geom_vline(xintercept=0, color="black", linetype="dashed", alpha= 1) +
+
+#faceting based on my subgroups
+  #facet_wrap(~X1) +
+facet_grid(Measure~Class, scales= "free_y", switch = 'y', space = "free_y") +
+
+#thematic stuff
+#ggtitle("Figure 3 - ATT Estimates by SubGroups")+
+theme_tufte_revised()+
+   theme(strip.placement = "outside") +
+#theme(text=element_text(family="Times",size=12, color="black"))+
+theme(panel.spacing = unit(1, "lines"))
+
+p + theme(panel.spacing = unit(1, "lines"),  strip.text = element_text(face = "bold", size = 12))
+
+```
+
 ## Back of the envelop
@@
   data = df.z.temp %>% filter(Year >= 2012)   %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 1), 
-  yname = "Sites", 
+  yname = "Pct.None", 
   treatment = "Tx",
@@
   data = df.z.temp%>% filter(Year >= 2012)   %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 0), 
-  yname = "Sites", 
+  yname = "Pct.None", 
   treatment = "Tx",
@@
 
-cbind(YearRel = c(gsub("rel_year::", "", rownames(es.direct$coeftable)), gsub("rel_year::", "", rownames(es.indirect$coeftable))), 
-      rbind(cbind(Group = "Direct",es.direct$coeftable), cbind(Group = "Indirect",es.indirect$coeftable))) %>% 
+es.zips.none <- cbind(YearRel = c(gsub("rel_year::", "", rownames(es.direct$coeftable)), gsub("rel_year::", "", rownames(es.indirect$coeftable))), 
+      rbind(cbind(Group = "Directly",es.direct$coeftable), cbind(Group = "Indirectly",es.indirect$coeftable))) %>% 
   data.frame() %>% 
@@
   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
-  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
+  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points") + ggtitle("Uninsured, %")
+
+ggarrange(es.zips.hours, es.zips.sites, es.zips.mcd, es.zips.none, nrow = 2, ncol = 2, common.legend = TRUE)
 

### 2024-11-25 code/manuscript_altanalysis.Rmd
submitted figures

@@
   group_by(Post, Treat) %>% 
-  select(Closed) %>% 
-  summarise(mean.nas(Closed), n())
+  select(Closed, Complexity) %>% 
+  summarise(mean.nas(Closed), n(), mean.nas(Complexity))
 
@@
 strat.temp[3,] <- strat.temp[3,] / 1000
-strat.temp[23,] <- strat.temp[23,] / 100
+strat.temp[23,] <- strat.temp[23,] / 10
 strat.temp[18,] <- strat.temp[18,] / 100
+
+#strat.temp[12,] <- strat.temp[12,] / 5.5 * 100
+
+strat.temp <- coeffs.did.strat
+
+strat.temp <- (strat.temp/(df.temptemp %>% 
+  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
+  filter(!is.na(value) & value_min > 1) %>% 
+  group_by(Post, Treat) %>% 
+  select(Qcomp:Closed) %>% 
+  summarise_all(mean.nas) %>% 
+  filter(Post == 0 & Treat == "Treated") %>% 
+  t())[-c(2)] %>% 
+  as.numeric() * 100)[-24,] %>% 
+  rbind(coeffs.did.strat[24,])
 
@@
 
-strat.temp$Outcome <- rep(c("Composite Quality of Care, %", "Total Patients Served, No.","Financial resilience,\nAltman’s Z Score", "Patient-to-Staff Ratio","Average prevalence of\nselect chronic conditions, %","Intensity", "Medicaid, %","Uninsured, %","CostPerPat","Quick Ratio, %","Months of Cash Available", "Revenue-to-Expenses, Ratio %","Liabilities-to-Assets, Ratio %","Staff, No.","Closure, Acquisition or\nloss of FQHC status, %"), 2)
+strat.temp$Outcome <- rep(c("Composite Quality of Care", "Total Patients Served","Financial resilience,\nAltman’s Z Score", "Patient-to-Staff Ratio","Average prevalence of\nselect chronic conditions","Intensity", "Medicaid","Uninsured","CostPerPat","Quick Ratio","Months of Cash Available", "Revenue-to-Expenses","Liabilities-to-Assets","Staff","Closure, Acquisition or\nloss of FQHC status"), 2)
 
 p <- strat.temp  %>% 
-  filter(Outcome %notin% c("Intensity","CostPerPat")) %>%
+  filter(Outcome %notin% c("Intensity","CostPerPat","Months of Cash Available")) %>%
 
@@
 #one could resize, reshape, or recolor these points if desired
-xlab("Effect Estimates") + 
+xlab("Effect Estimates (% change)") + 
 ylab(NULL) + 
@@
 p + theme(panel.spacing = unit(1, "lines"),  strip.text = element_text(face = "bold", size = 12))
+
+colnames(df.temptemp)[17:39]
 

### 2025-02-11 code/manuscript_altanalysis.Rmd
checking pushing
add controls for ACA MCD expansion

@@
 
-## Compared to pre-2020 estimates
-```{r}
+## Compared to pre-2020 estimates and Controlling for ACA
+```{r}
+
+coeffs.did.ACA <- c(0,0,0,0)
+
+for (k in 1:23){
+
+  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  # Winsorized
+  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
+  df.temptemptemp <- df.temptemptemp %>% 
+    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
+                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
+  model <-  did2s(
+      data = df.temptemptemp, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag + ACA | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+  coeffs.did.ACA <- rbind(coeffs.did.ACA, model$coeftable[1,])
+
+}
+
+core.did.estimates.ACA <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.ACA[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  select(V1, Estimate, `95% CI`, Pr...t..)
+
+core.did.estimates.ACA <- core.did.estimates.ACA
+#rownames(core.did.estimates) <- NULL
 
@@
 
-cbind(core.did.estimates, core.did.estimates.pre2020)
+cbind(core.did.estimates[,c(1,2,4)], core.did.estimates.pre2020[,c(2,4)], core.did.estimates.ACA[,c(2,4)])
 

### 2025-02-21 code/manuscript_altanalysis.Rmd
final code updates

@@
 
+length(unique(uds.covariates$BHCMISID))
+
 df.comp <- uds.covariates %>% 
@@
 select(BHCMISID:Year, Total:Pct.COM, HIV.prev:Hypertension.care , imm.rate:MinYear)
+
+length(unique(df.comp[df.comp$Year %in% included.years,]$BHCMISID))
+
+df.comp %>% 
+    filter(Year == 2022) %>% 
+    mutate(Missing = ifelse(is.na(ngla_net_gain_loss), "Missing", "Have")) %>% 
+    ungroup() %>% 
+    select(Missing, Total, Pct.NHA:Pct.COM) %>% 
+    #filter(!complete.cases(.)) %>% 
+    tbl_summary(by = Missing, 
+                  statistic = list(all_continuous() ~ "{mean} ({sd})"),
+  missing = "no", digits = list(everything() ~ c(2))) %>% 
+    add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))
 
@@
 
-table(table(dfc$`BHCMIS ID`))
-
-dfc %>% filter(ID.x == "90")
-
-dfc %>% 
-  filter(`BHCMIS ID` == "012070")
+# table(table(dfc$`BHCMIS ID`))
+# 
+# 
+# 
+# dfc %>% filter(ID.x == "90")
+# 
+# dfc %>% 
+#   filter(`BHCMIS ID` == "012070")
+
+length(unique(dfc$`BHCMIS ID`))
 
@@
 
+length(unique(dfc$`BHCMIS ID`))
+
 ```
@@
 ```{r}
+
+length(unique(df.mt$`BHCMIS ID`))
 
@@
   mutate(value = ifelse(value >= 6, 6, value)) #%>% group_by(ID) %>% mutate(max_Closures = max(Closed)) %>% filter(max_Closures == 0)
+
+length(unique(df.temptemp$`BHCMIS ID`))
 
@@
 
+length(unique(df.temptemp$`BHCMIS ID`))
+
 possible.vecs <- rep(included.treat, df.temptemp %>% 
@@
   filter(!(Treat == "Control" & Att == 2009))
+
+length(unique(df.temptemp$`BHCMIS ID`))
 
@@
 
+summary(df.temptemp[df.temptemp$Year == 2022 & df.temptemp$Closed == 0,])
+
+df.temptemp[df.temptemp$Closed == 0,]
+
+# 
+# fullfins <- ufins2 %>%
+#   mutate(months_of_cash = as.numeric(months_of_cash),
+#                ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
+#                quick_ratio = as.numeric(quick_ratio),
+#                Liquidity = (Assets - Liabilities) / Assets,
+#                Profitability = ngla_revenue / ngla_expense * 100, #Assets,
+#                Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
+#                NetWorth = (Assets - Liabilities) / Liabilities,
+#             Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense,
+#             LiabPctAssets = Liabilities / Assets * 100,
+#             Eff = ngla_prog_serv_revenue / Assets,
+#             LiabPctRev = ngla_prog_serv_revenue / ngla_expense) %>%
+#   mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity),
+#          Profitability = ifelse(is.infinite(Profitability), NA, Profitability),
+#          Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency),
+#          NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth),
+#          Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>%
+#   select(BHCMIS.ID, form_year, Altman, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff, ngla_net_gain_loss )
+# 
+# 
+# 
+# 
+# df.temptemp <- df.temptemp %>%
+#   left_join(fullfins %>% unique(), by = c("BHCMIS ID" = "BHCMIS.ID","Year" = "form_year")) %>%
+#   unique() %>%
+#   mutate(Altman.x = ifelse(is.na(Altman.x), Altman.y, Altman.x),
+#          quick_ratio.x = ifelse(is.na(quick_ratio.x), quick_ratio.y, quick_ratio.x),
+#          months_of_cash.x = ifelse(is.na(months_of_cash.x), months_of_cash.y, months_of_cash.x),
+#          Profitability.x = ifelse(is.na(Profitability.x), Profitability.y, Profitability.x),
+#          LiabPctAssets.x = ifelse(is.na(LiabPctAssets.x), LiabPctAssets.y, LiabPctAssets.x),
+#          Staff.x = ifelse(is.na(Staff.x), Staff.y, Staff.x),
+#          ngla_net_gain_loss.x = ifelse(is.na(ngla_net_gain_loss.x), ngla_net_gain_loss.y, ngla_net_gain_loss.x)) %>%
+#   rename(Altman = Altman.x,
+#          quick_ratio = quick_ratio.x,
+#          months_of_cash = months_of_cash.x,
+#          Profitability = Profitability.x,
+#          LiabPctAssets = LiabPctAssets.x,
+#          Staff = Staff.x,
+#          ngla_net_gain_loss = ngla_net_gain_loss.x) %>%
+#   unique()
+
+df.temptemp %>% 
+  filter(Year == 2022) %>% 
+  mutate(Missing = ifelse(is.na(Qcomp), "Missing", "Have")) %>% 
+  select(Missing, Total, Pct.NHA:Staff) %>% 
+  #filter(!complete.cases(.)) %>% 
+  tbl_summary(by = Missing, 
+                statistic = list(all_continuous() ~ "{mean} ({sd})"),
+missing = "no", digits = list(everything() ~ c(2))) %>% 
+  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))
+
+df.temptemp %>% 
+  filter(Year == 2022) %>% 
+  mutate(Missing = ifelse(is.na(Altman), "Missing", "Have")) %>% 
+  select(Missing, Total, Pct.NHA:Staff) %>% 
+  #filter(!complete.cases(.)) %>% 
+  tbl_summary(by = Missing, 
+                statistic = list(all_continuous() ~ "{mean} ({sd})"),
+missing = "no", digits = list(everything() ~ c(2))) %>% 
+  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))
+
+```
+
+## Balance by 990 vs non990 data CHCs
+```{r}
+
+df.temptemp %>% 
+  filter(Year == 2010) %>% 
+  mutate(Missing = ifelse(is.na(Altman), "Missing", "Have")) %>% 
+  select(Missing, Total, Pct.NHA:Staff) %>% 
+  #filter(!complete.cases(.)) %>% 
+  tbl_summary(by = Missing, 
+                statistic = list(all_continuous() ~ "{mean} ({sd})"),
+missing = "no", digits = list(everything() ~ c(2))) %>% 
+  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))
+
+fullfins <- ufins2 %>%
+  mutate(months_of_cash = as.numeric(months_of_cash),
+               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
+               quick_ratio = as.numeric(quick_ratio),
+               Liquidity = (Assets - Liabilities) / Assets,
+               Profitability = ngla_revenue / ngla_expense * 100, #Assets,
+               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
+               NetWorth = (Assets - Liabilities) / Liabilities,
+            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense,
+            LiabPctAssets = Liabilities / Assets * 100,
+            Eff = ngla_prog_serv_revenue / Assets,
+            LiabPctRev = ngla_prog_serv_revenue / ngla_expense) %>%
+  mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity),
+         Profitability = ifelse(is.infinite(Profitability), NA, Profitability),
+         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency),
+         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth),
+         Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>%
+  select(BHCMIS.ID, form_year, Altman, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff, ngla_net_gain_loss )
+
+df.temptemp <- df.temptemp %>%
+  left_join(fullfins %>% unique() %>%
+  filter(!(`BHCMIS.ID` == "03E00494" & form_year == 2010) & 
+           !(`BHCMIS.ID` == "03E01039" & form_year ==	2015)& 
+           !(`BHCMIS.ID` == "05E00445" & form_year ==	2015)& 
+           !(`BHCMIS.ID` == "05E00499" & form_year ==	2013)&
+
+           !(`BHCMIS.ID` == "06E00500" & form_year ==	2016)& 
+           !(`BHCMIS.ID` == "07E00486" & form_year ==	2014)& 
+           !(`BHCMIS.ID` == "07E00514" & form_year ==	2014)& 
+           !(`BHCMIS.ID` == "10E00136" & form_year ==	2013)), by = c("BHCMIS ID" = "BHCMIS.ID","Year" = "form_year"))  %>% 
+  unique() %>%
+  mutate(Altman.x = ifelse(is.na(Altman.x), Altman.y, Altman.x),
+         quick_ratio.x = ifelse(is.na(quick_ratio.x), quick_ratio.y, quick_ratio.x),
+         months_of_cash.x = ifelse(is.na(months_of_cash.x), months_of_cash.y, months_of_cash.x),
+         Profitability.x = ifelse(is.na(Profitability.x), Profitability.y, Profitability.x),
+         LiabPctAssets.x = ifelse(is.na(LiabPctAssets.x), LiabPctAssets.y, LiabPctAssets.x),
+         Staff.x = ifelse(is.na(Staff.x), Staff.y, Staff.x),
+         ngla_net_gain_loss.x = ifelse(is.na(ngla_net_gain_loss.x), ngla_net_gain_loss.y, ngla_net_gain_loss.x)) %>%
+  rename(Altman = Altman.x,
+         quick_ratio = quick_ratio.x,
+         months_of_cash = months_of_cash.x,
+         Profitability = Profitability.x,
+         LiabPctAssets = LiabPctAssets.x,
+         Staff = Staff.x,
+         ngla_net_gain_loss = ngla_net_gain_loss.x) %>%
+  unique()
+
+df.temptemp %>% 
+  filter(Year == 2010) %>% 
+  select(Altman, Pct.NHA:Pct.Homeless, Pct.MCD:Pct.None) %>% 
+  mutate(Missing = ifelse(is.na(Altman), "Missing", "Have")) %>% 
+  #filter(!complete.cases(.)) %>% 
+  tbl_summary(by = Missing, 
+                statistic = list(all_continuous() ~ "{mean} ({sd})"),
+missing = "no", digits = list(everything() ~ c(2))) %>% 
+  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))
+
+# 
+# fullfins %>% 
+#     filter(`BHCMIS.ID` %in% names(table(df.temptemp$`BHCMIS ID`)[table(df.temptemp$`BHCMIS ID`) != 15]))
+# 
+# df.temptemp %>% 
+#   filter(`BHCMIS ID` %in% names(table(df.temptemp$`BHCMIS ID`)[table(df.temptemp$`BHCMIS ID`) != 15]))
+
+```
+
+```{r}
+uds.6b.2022 %>% 
+  filter(BHCMISID == "01E01088")
+
+uds.quality.6b %>% 
+  filter(BHCMISID == "01E01088")
+
+df.temptemp %>% 
+  filter(`BHCMIS ID` == "01E01088")
 ```
@@
   arrange(CompetitorsInArea) %>% 
-  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, linetype = CompetitorsInArea)) + ylab("FQHCs") + 
+  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, linetype = CompetitorsInArea)) + ylab("CHCs") + 
   #geom_point(size = 1.1) + 
-  geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
+  geom_line(size = 1.1)  + theme_tufte_revised() + ggtitle("CHCs by Number of Colocated CHCs") + 
   #geom_dl(label=c(rep("0 Rivals", length(unique(p$Year))), rep("1 Rival", length(unique(p$Year))), rep("2 Rivals", length(unique(p$Year))), rep("3+ Rivals", length(unique(p$Year)))), 
@@
   #filter(Year >= 2010) %>% 
-  ggplot(aes(x = Year, y = Zips, group = Counts.f, linetype = Counts.f)) + 
+  ggplot(aes(x = Year, y = Zips)) + 
   #geom_point(size = 1.1) + 
-  geom_line(size = 1.1) + theme_tufte_revised() + 
-  ggtitle("Zip Codes by Number of FQHC Sites") + 
+  geom_line(size = 1.1, aes(linetype = Counts.f)) + theme_tufte_revised() +
+  ggtitle("Zip Codes by Number of CHC Sites") + 
   #geom_dl(label=c(rep("1 Site", length(unique(p$Year))), rep("2+ Sites", length(unique(p$Year)))), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
@@
         axis.title=element_text(size=12,face="bold")) + 
-  scale_linetype_manual(values=c(5, 6)) + 
+  scale_linetype_manual(values=c(7, 8)) + 
   guides(linetype = guide_legend(title = "# CHC Sites by\nZip Code"))
@@
 
-p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2023", face = "bold", size = 14))
+p.desc <- annotate_figure(p.desc, top = text_grob("CHC Growth and Density by Zip and Clinic, UDS 1996 to 2023", face = "bold", size = 14))
 
@@
   #coeffs <- rbind(coeffs, model$coeftable[2,])
-  model <- feols(Outcome ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year | I((10000 - ClinicHHI)/1000) ~ Tx*value, cluster = "ID", data = df.temptemptemp)
+  model <- feols(Outcome ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless  | ID + Year | I((10000 - ClinicHHI)/1000) ~ Tx, cluster = "ID", data = df.temptemptemp)
   coeffs <- rbind(coeffs, model$coeftable[1,])
@@
     event_study(data = df.temptemp,
-  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
+  yname = "ClinicHHI", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
   filter(abs(term) <= 6) %>%
@@
       treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
         second_stage = ~ i(Tx, ref = FALSE),
@@
                         ifelse(Measure %in% c('Altman','LiabPctAssets','months_of_cash'), 'Financial Metrics', 'Selection Metrics'))) %>% 
+  mutate(Measure = ifelse(Measure == "Altman", "Financial resilience, Altman’s Z Score", 
+                   ifelse(Measure == "Staff", "CHC Staff, No.",
+                   ifelse(Measure == "Total", "Total Patients Served, No.", 
+                   ifelse(Measure == "Complexity", "Average prevalence of select chronic conditions, %", 
+                   ifelse(Measure == "Pct.MCD", "Payer Mix - % Medicaid", 
+                   ifelse(Measure == "Pct.None", "Payer Mix - % Uninsured", Measure))))))) %>%
   rename(Year = term) %>% 
@@
       treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
         second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min>=2, 1, 0), ref = FALSE),
@@
 cbind(core.did.estimates[,c(1,2,4)], core.did.estimates.pre2020[,c(2,4)], core.did.estimates.ACA[,c(2,4)])
+
+```
+
+## Evaluating Missingness
+
+```{r}
+
+coeffs.did.missingButBaseline <- c(0,0,0,0)
+
+for (k in 1:22){
+
+  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) %>% select(ClinicHHI:ACA, Treat:year.rel) %>% ungroup() %>% # filter(!is.na(Altman))
+    inner_join(df.temptemp %>% filter(Year == 2010) %>% ungroup() %>% mutate(Missing = ifelse(is.na(Altman), "Missing", "Have")) %>% select(`BHCMIS ID`, Missing), by = c("BHCMIS ID")) %>% filter(Missing == "Have") %>%
+    filter(!complete.cases(.)) 
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  # Winsorized
+  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
+  df.temptemptemp <- df.temptemptemp %>% 
+    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
+                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
+  model <-  did2s(
+      data = df.temptemptemp, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+  coeffs.did.missingButBaseline <- rbind(coeffs.did.missingButBaseline, model$coeftable[1,])
+
+}
+
+core.did.estimates.missingBugBaseline <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.missingButBaseline[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  select(V1, Estimate, `95% CI`, Pr...t..)
+
+nrow(df.temptemptemp)
+
+coeffs.did.notmissing <- c(0,0,0,0)
+
+for (k in 1:22){
+
+  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) %>% select(ClinicHHI:ACA, Treat:year.rel) %>% ungroup() %>% # filter(!is.na(Altman))
+    inner_join(df.temptemp %>% filter(Year == 2010) %>% ungroup() %>% mutate(Missing = ifelse(is.na(Altman), "Missing", "Have")) %>% select(`BHCMIS ID`, Missing), by = c("BHCMIS ID")) %>% filter(Missing == "Have") %>%
+    filter(complete.cases(.))
+
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  # Winsorized
+  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
+  df.temptemptemp <- df.temptemptemp %>% 
+    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
+                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
+
+ if (sum(is.na(df.temptemptemp$Outcome)) > 2500) {
+   coeffs.did.notmissing <- rbind(coeffs.did.notmissing, c(NA, NA, NA, NA))
+
+ } else {
+   model <-  did2s(
+      data = df.temptemptemp, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+  coeffs.did.notmissing <- rbind(coeffs.did.notmissing, model$coeftable[1,])
+
+ }
+
+}
+
+core.did.estimates.notmissing <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.notmissing[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  select(V1, Estimate, `95% CI`, Pr...t..)
+
+nrow(df.temptemptemp)
+
+coeffs.did.missing <- c(0,0,0,0)
+
+for (k in 1:22){
+
+  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) %>% select(ClinicHHI:ACA, Treat:year.rel) %>% ungroup() %>% # filter(!is.na(Altman))
+    inner_join(df.temptemp %>% filter(Year == 2010) %>% ungroup() %>% mutate(Missing = ifelse(is.na(Altman), "Missing", "Have")) %>% select(`BHCMIS ID`, Missing), by = c("BHCMIS ID")) %>% filter(Missing == "Missing")
+
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  # Winsorized
+  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
+  df.temptemptemp <- df.temptemptemp %>% 
+    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
+                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
+
+ if (sum(is.na(df.temptemptemp$Outcome)) > 2500) {
+   coeffs.did.missing <- rbind(coeffs.did.missing, c(NA, NA, NA, NA))
+
+ } else {
+   model <-  did2s(
+      data = df.temptemptemp, 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage = ~ i(Tx, ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+  coeffs.did.missing <- rbind(coeffs.did.missing, model$coeftable[1,])
+
+ }
+
+}
+
+core.did.estimates.missing <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.missing[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  select(V1, Estimate, `95% CI`, Pr...t..)
+
+nrow(df.temptemptemp)
+
+cbind(core.did.estimates.missingBugBaseline[,c(1,2,3, 4)], core.did.estimates.notmissing[,c(2,3, 4)], core.did.estimates.missing[,c(2,3,4)])
 
@@
 
-  df.z.temp2 <- df.z.temp %>% filter(Year >= 2012) %>% filter(Att %notin% c(2009:2012))
+  df.z.temp2 <- df.z.temp %>% filter(Year >= 2012) %>% filter(Att %notin% c(2009:2012)) %>% 
+      left_join(census, by = c("Zip" = "ZipCode", "Year" = "YEAR")) %>% 
+  mutate(PctMedicaid = Medicaid / MCD.denom * 100, 
+         PctUninsured = Uninsured / Unins.denom * 100, 
+         PctPoverty = IncomeBelowPoverty / PovertyStatusDet * 100, 
+         PctUnemployed = Unemployed / Unemp_denom * 100, 
+         PctBlack = Black / TotalPop * 100, 
+         PctHispanic = Hispanic / TotalPop * 100, 
+         PctChildren = AgeUnder18 / TotalPop * 100, 
+         PctElderly = Age65andOver / TotalPop * 100, 
+         PctEducLow = EducLow / TotalPop * 100)
 
@@
       treatment = "Tx",
-        first_stage = ~ 1 | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
+        first_stage = ~ 1 | ID + Year ,
+        #first_stage = ~ TotalPop + PctMedicaid + PctUninsured + PctPoverty + PctBlack + PctHispanic + PctChildren + PctElderly | ID + Year ,
         second_stage = ~ i(Tx * (1 - DirectlyTreated), ref = FALSE)  + I(Tx * DirectlyTreated),
@@
   inner_join(census, by = c("Zip" = "ZipCode", "Year" = "YEAR")) %>% 
-  filter(Year == 2012) %>% 
+  filter(Year %in% c(2012)) %>% 
   mutate(PctMedicaid = Medicaid / MCD.denom * 100, 
@@
          PctEducLow = EducLow / TotalPop * 100) %>% 
-    select(Status, TotalPop, PctMedicaid:PctEducLow, UrbanRuralFlag) %>% 
+    select(Status, Year, TotalPop, PctMedicaid:PctEducLow, UrbanRuralFlag) %>% 
      tbl_summary(by = Status, 
                 statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
+  add_p()
+
+df.z.temp %>% 
+  #select(Zip, Year, DirectlyTreated, Att) %>% 
+  mutate(Status = ifelse(Att == 0, NA, 
+                         ifelse(Att > 0 & DirectlyTreated == 0, "IndirectlyTreated","DirectlyTreated"))) %>% 
+  inner_join(census, by = c("Zip" = "ZipCode", "Year" = "YEAR")) %>% 
+  filter(Year %in% c(2012, 2022)) %>% 
+  mutate(PctMedicaid = Medicaid / MCD.denom * 100, 
+         PctUninsured = Uninsured / Unins.denom * 100, 
+         PctPoverty = IncomeBelowPoverty / PovertyStatusDet * 100, 
+         PctUnemployed = Unemployed / Unemp_denom * 100, 
+         PctBlack = Black / TotalPop * 100, 
+         PctHispanic = Hispanic / TotalPop * 100, 
+         PctChildren = AgeUnder18 / TotalPop * 100, 
+         PctElderly = Age65andOver / TotalPop * 100, 
+         PctEducLow = EducLow / TotalPop * 100) %>% 
+    select(Zip, Status, Year, TotalPop, PctMedicaid:PctEducLow) %>% 
+   #group_by(Zip) %>% 
+  pivot_longer(cols = TotalPop:PctEducLow) %>% 
+  filter(!is.na(Status)) %>% 
+  unique() %>% 
+  pivot_wider(id_cols = c(Zip, name, Status), names_from = Year, values_from = value) %>% 
+  mutate(diff = `2022` - `2012`) %>% 
+  pivot_wider(id_cols = c(Zip, Status), names_from = name, values_from = diff) %>% 
+  select(Status:PctEducLow) %>% 
+       tbl_summary(by = Status, 
+                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no" ) %>% 
   add_p()
@@
 
-ggsave(filename = "Figure2.png", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Figures", plot = p, width = 11, height = 8)
+#ggsave(filename = "Figure2.png", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Figures", plot = p, width = 11, height = 8)
 
@@
 ```{r}
-#df.z.temp %>% write_csv("/Users/markow/Dropbox/Git/Competition/data_processed/final_manuscript_allocation.csv")
-#df.temptemp %>% write_csv("/Users/markow/Dropbox/Git/Competition/data_processed/final_manuscript_core.csv")
-```
+# df.z.temp %>% write_csv("/Users/markow/Dropbox/Git/Competition/data_processed/finalfinal_manuscript_allocation.csv")
+# df.temptemp %>% write_csv("/Users/markow/Dropbox/Git/Competition/data_processed/finalfinal_manuscript_core.csv")
+```

### 2025-02-21 code/manuscript_data_cleaning.Rmd
final code updates

@@
   table()
+
+#write_csv(census, "/Users/jhm65/Dropbox/OtherData/Emergency/ACS - Tract/ACS_zips.csv")
 ```
@@
 uds.quality.6b <- uds.quality.6b %>% 
-  inner_join(uds.cw %>% mutate(STATE = toupper(STATE)) %>% unique() %>% mutate(STATE = ifelse(BHCMIS.ID == '010530', 'ME', 
+  left_join(uds.cw %>% mutate(STATE = toupper(STATE)) %>% unique() %>% mutate(STATE = ifelse(BHCMIS.ID == '010530', 'ME', 
                                                                                        ifelse(BHCMIS.ID == '090090', 'AZ', STATE))) %>% 
@@
 uds.quality.7 <- uds.quality.7 %>% 
-  inner_join(uds.cw %>% mutate(STATE = toupper(STATE)) %>% unique() %>% mutate(STATE = ifelse(BHCMIS.ID == '010530', 'ME', 
+  left_join(uds.cw %>% mutate(STATE = toupper(STATE)) %>% unique() %>% mutate(STATE = ifelse(BHCMIS.ID == '010530', 'ME', 
                                                                                        ifelse(BHCMIS.ID == '090090', 'AZ', STATE))) %>% 
@@
 uds.quality.7 <- uds.quality.7 %>% 
-   inner_join(uds.cw %>% filter(Year == 2011) %>% unique() %>% select(ModernGranteeID, BHCMIS.ID), by = c("GrantNumber" = "ModernGranteeID")) %>% 
+   left_join(uds.cw %>% filter(Year == 2011) %>% unique() %>% select(ModernGranteeID, BHCMIS.ID), by = c("GrantNumber" = "ModernGranteeID")) %>% 
   arrange(Year, BHCMIS.ID, GrantNumber) %>% 
@@
 
+ufins2 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2022-Full-Dataset.xlsx", sheet = "HealthCenterInfo", skip = 0) %>% select( `GrantNumber`, `BHCMISID`) %>%
+  left_join(cw, by = c("GrantNumber" = "Grant Number")) %>%
+  left_join(ufins.revenue.expenses, by = c("EIN" = "EIN")) %>%
+  select(`GrantNumber`:EIN, form_year:fringe_rate) %>%
+  left_join(ustaffing %>% select(EIN:Staff), by = c("EIN","form_year" = "Year")) %>%
+  left_join(uassliabs %>% select(EIN:Liabilities), by = c("EIN","form_year" = "Year")) %>%
+  rename(ModernGranteeID = `GrantNumber`,
+         BHCMIS.ID = `BHCMISID`)
+
 ufins <- uds.cw %>% filter(Year == 2011) %>% unique() %>% select(ModernGranteeID, BHCMIS.ID) %>%
@@
 
-fins.revenue.expenses <- ufins
+length(unique(ufins.revenue.expenses$EIN))
+
+fins.revenue.expenses <- ufins #rbind(ufins, ufins2) %>% unique()
+
+uds.sites %>% 
+  select(`BHCMIS ID`, `Grant Number`, `Health Center Name`)
 
@@
 # write.csv(uds.sites.full, file = "/Users/markow/Dropbox/Git/Competition/data_processed/manuscript_sites_geocoded.csv")
-
-```
+#dfc %>% filter(Year == 2023) %>% write_csv("/Users/markow/Dropbox/Teaching/25 - Spring - MHA Quant Methods/Week 6/Week6LabData.csv")
+```

### 2025-03-03 code/manuscript_altanalysis.Rmd
final changes

@@
       treatment = "Tx",
-        first_stage = ~ 1 | ID + Year ,
-        #first_stage = ~ TotalPop + PctMedicaid + PctUninsured + PctPoverty + PctBlack + PctHispanic + PctChildren + PctElderly | ID + Year ,
+        #first_stage = ~ 1 | ID + Year ,
+        first_stage = ~ TotalPop + PctMedicaid + PctUninsured + PctPoverty + PctBlack + PctHispanic + PctChildren + PctElderly | ID + Year ,
         second_stage = ~ i(Tx * (1 - DirectlyTreated), ref = FALSE)  + I(Tx * DirectlyTreated),

### 2025-03-11 code/manuscript_altanalysis.Rmd
final figures

@@
                     (STATE %in% c('ID','UT','NE') & Year >= 2020) |
-                    (STATE %in% c('OK','MO') & Year >= 2021) |
-                    (STATE %in% c('AZ','AR','CA','CO','CT','DE','DC','HI','IL','IA','KY','MD','MA','MN','NV','NJ','NM','NY','ND','OH','OR','PA','RI','VT','VA','WA') & Year >= 2014), 1, 0))
+                    (STATE %in% c('OK','MO','AR') & Year >= 2021) |
+                    (STATE %in% c('SD','NC') & Year >= 2023) | 
+                    (STATE %in% c('AZ','CA','CO','CT','DE','DC','HI','IL','IA','KY','MD','MA','MN','NV','NJ','NM','NY','ND','OH','OR','PA','RI','VT','VA','WA') & Year >= 2014), 1, 0))
 
@@
 
+#ggsave(filename = "Figure1.pdf", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Revision 1", plot = p.desc, width = 7, height = 10)
 ```
@@
 
+ggsave(filename = "Figure2.pdf", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Revision 1", plot = ess + theme(legend.position="none"), width = 8, height = 10)
+
 ```
@@
       treatment = "Tx",
-        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
         second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min>=2, 1, 0), ref = FALSE),
@@
 
-## Stratified figure instead of table 
+## Stratified figure instead of table - optional
 ```{r}
@@
 
+strat.temp <- strat.temp %>% 
+  select(Outcome) %>% 
+  cbind(data.frame(rbind(c(1.82, -0.4, 4.04),
+      c(-448, -2513, 1617), 
+      c(-0.08, -0.33, 0.16), 
+      c(6.30, 0.4, 12.2), 
+      c(-0.18, -0.71, 0.34),
+
+      c(NA, NA, NA), 
+      c(2.33, 0.03, 4.63), 
+      c(-2.92, -5.4, -0.44), 
+      c(NA, NA, NA), 
+      c(-0.25, -0.73, 0.23),
+
+      c(-0.31, -0.75, 0.14), 
+      c(-0.37, -2.42, 1.68), 
+      c(4.75, -0.64, 10.14), 
+      c(2.49, -18.84, 23.82), 
+      c(-1.22, -3.48, 1.03),
+
+      c(-3.31, -5.65, -0.96), 
+      c(4701, 1533, 7869) , 
+      c(-0.37, -0.65, -0.09), 
+      c(4.43, -1.92, 10.78), 
+      c(-0.69, -1.08, -0.31),
+
+      c(NA, NA, NA), 
+      c(5.75, 3.46, 8.04), 
+      c(-3.17, -5.32, -1.01), 
+      c(NA, NA, NA), 
+      c(-0.99, -1.50, -0.48),
+
+      c(-0.67, -1.09, -0.24), 
+      c(-1.25, -2.87, 0.37), 
+      c(5.36, 1.62, 9.11), 
+      c(81.13, 46.12, 116.14), 
+      c(1.67, 0.62, 2.73)))  * 100 / as.numeric((df.temptemp %>% 
+  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
+  filter(!is.na(value) & value_min > 1) %>% 
+  group_by(Post, Treat) %>% 
+  select(Qcomp, Total, Altman, logPatsPerStaff, Complexity, Intensity, Pct.MCD, Pct.None, CostPerPat, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff) %>% 
+  summarise_all(mean.nas) %>% 
+  filter(Post == 0 & Treat == "Treated") %>% 
+  t() %>% 
+    rbind(100))[-c(1,2),])
+
+) %>% 
+  rename(Estimate = X1, 
+         LB = X2, UB = X3) %>% 
+  cbind(strat.temp %>% 
+  select(Class, Measure))
+
 p <- strat.temp  %>% 
@@
 colnames(df.temptemp)[17:39]
+
+ggsave(filename = "Figure3.pdf", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Revision 1", plot = p + theme(panel.spacing = unit(1, "lines"),  strip.text = element_text(face = "bold", size = 12)), width = 8, height = 10)
 
@@
 cbind(core.did.estimates[,c(1,2,4)], core.did.estimates.pre2020[,c(2,4)], core.did.estimates.ACA[,c(2,4)])
+
+```
+
+```{r}
+
+coeffs.did.ACA <- rep(0, 8)
+
+for (k in 1:23){
+
+  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  # Winsorized
+  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
+  df.temptemptemp <- df.temptemptemp %>% 
+    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
+                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
+  model <-  did2s(
+      data = df.temptemptemp %>% inner_join(df.temptemptemp %>% group_by(`BHCMIS ID`) %>% summarise(ACA = max(ACA)) %>% filter(ACA == 1), by = c("BHCMIS ID")) %>% filter(Year < 2024),  
+      #data = df.temptemptemp %>% filter(ACA == 0 & Year <= 2024), 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min >= 2, 1, 0), ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+  coeffs.did.ACA <- rbind(coeffs.did.ACA, c(model$coeftable[1,], model$coeftable[2,]))
+
+}
+
+core.did.estimates.ACA <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.ACA[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>%
+  select(V1, Estimate, `95% CI`, Pr...t.., Estimate.1, `95% CI.1`, `Pr...t...1`)
+
+core.did.estimates.ACA <- core.did.estimates.ACA
+#rownames(core.did.estimates) <- NULL
+
+coeffs.did.nonACA <- rep(0, 8)
+
+for (k in 1:23){
+
+  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
+  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
+  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
+  # Winsorized
+  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
+  df.temptemptemp <- df.temptemptemp %>% 
+    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
+                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
+  model <-  did2s(
+      data = df.temptemptemp %>% inner_join(df.temptemptemp %>% group_by(`BHCMIS ID`) %>% summarise(ACA = max(ACA)) %>% filter(ACA == 0), by = c("BHCMIS ID")) %>% filter(Year < 2024),  
+      #data = df.temptemptemp %>% filter(ACA == 0 & Year <= 2024), 
+      yname = "Outcome", 
+      treatment = "Tx",
+        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
+        second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min >= 2, 1, 0), ref = FALSE),
+        cluster_var = "ID",
+      verbose = TRUE
+    )
+
+  coeffs.did.nonACA <- rbind(coeffs.did.nonACA, c(model$coeftable[1,], model$coeftable[2,]))
+
+}
+
+core.did.estimates.nonACA <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.nonACA[-1,]))) %>% 
+  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
+  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>%
+  mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>%
+  select(V1, Estimate, `95% CI`, Pr...t.., Estimate.1, `95% CI.1`, `Pr...t...1`)
+
+core.did.estimates.nonACA <- core.did.estimates.nonACA
+#rownames(core.did.estimates) <- NULL
+
+cbind(core.did.estimates.ACA, core.did.estimates.nonACA)
+
+df.temptemptemp %>% inner_join(df.temptemptemp %>% group_by(`BHCMIS ID`) %>% summarise(ACA = max(ACA)), by = c("BHCMIS ID")) %>% 
+  mutate(value = ifelse(value_min == 1, 0, 1)) %>% 
+  ungroup() %>% 
+  select(ACA.y, value) %>% 
+  group_by(ACA.y, value) %>% 
+  summarise(n())
 
